### 2017-03-08 paq/parenting_obs_paq.Rmd
analysis of parenting_obs questionnaire data

---
title: "PAQ for parenting observational study"
author: "Emily"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_float: true
    number_sections: true
---

# Data preprocessing

Preliminaries.

```{r echo=FALSE}
knitr::opts_chunk$set(fig.width=8, fig.height=5, 
                      echo=TRUE, warning=FALSE, message=FALSE, cache=FALSE)
suppressPackageStartupMessages(c("dplyr","langcog","tidyr","ggplot2","lme4"))
library(psych)
library(langcog)
library(tidyverse)
library(ggthemes)
library(rjson)
library(stringr)
library(forcats)
library(tibble)

select <- dplyr::select # masked by MASS

theme_set(theme_few())
```

Read in participant data.

```{r}
files <- dir("parenting_obs_paq_online/")
attitudes <- data.frame()

#from online version
for (f in files) {
  jf <- paste("parenting_obs_paq_online/",f,sep="")
  jd <- fromJSON(paste(readLines(jf), collapse=""))

  attitudes_id <- data.frame(workerid = f, 
                   sent = jd$data$sentence[2:25],
                   rating = jd$data$rating[1:24])

  attitudes <- bind_rows(attitudes, attitudes_id)}

#from paper version
paq <- read.csv('parenting_obs_paq_paper.csv')
sents <- read.csv('sent_forms_paper.csv')

paq <- paq %>%
  gather(ques, rating, Q1:Q24)%>%
  mutate(workerid = Sub_ID)%>%
  left_join(sents)%>%
  select(workerid, sent, rating)

paq$rating <- as.integer(paq$rating)
attitudes$rating <- as.integer(attitudes$rating)

attitudes <- bind_rows(attitudes, paq)
```

Read in trial info and questionnaire labels.

```{r}
labels <- read.csv("sent_forms.csv")
labels$sent <- as.character(labels$sent)
```

Clean up labels.

```{r}
attitudes$sent <- str_replace_all(as.character(attitudes$sent), "[â‘”“’']", "")
```

# Data Frames and Exclusions

## Make data frames.

Questionnaire attitude means.

```{r}
dq <- attitudes %>%
  left_join(labels)

dq$rating <- as.numeric(dq$rating)

dq$rating[dq$reverse_code == 1] <- 6 - dq$rating[dq$reverse_code == 1]

atts <- dq %>%
  group_by(workerid, category) %>% 
  summarise(rating = mean(rating))
```

# Questionnaire

Look at mean ratings across sentences.

```{r}
ms <- dq %>%
  group_by(category, short_sent, reverse_code) %>%
  multi_boot_standard(col = "rating", na.rm = TRUE) %>%
  arrange(category, desc(mean))

ms$short_sent_ord <- factor(ms$short_sent, 
                             levels = ms$short_sent)
```

Plot responses to individual questionnaire items.

```{r}
qplot(short_sent_ord, mean, col = category,
      ymin = ci_lower, ymax = ci_upper, pch = factor(reverse_code),
      geom = "pointrange",
      data = ms) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5)) +
  xlab("") + 
  ylab("Mean Rating") + 
  ylim(c(0,6)) + 
  scale_colour_solarized()
```

Plot mean subscale scores.

```{r}
atts_m <- dq %>%
  group_by(category) %>%
  multi_boot_standard(col = "rating", na.rm = TRUE) %>%
  arrange(category, desc(mean))

ggplot(atts_m, aes(x = category, y = mean)) + 
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))
```

### 2017-03-08 paq/parenting_obs_paq.Rmd
added parent_ed analysis

@@
 
-  attitudes_id <- data.frame(workerid = f, 
+  attitudes_id <- data.frame(sid = f, 
                    sent = jd$data$sentence[2:25],
@@
   attitudes <- bind_rows(attitudes, attitudes_id)}
+
+attitudes$sid <- str_replace(attitudes$sid, "parenting_proj_", "")
+attitudes$sid <- str_replace(attitudes$sid, ".json", "")
 
@@
   gather(ques, rating, Q1:Q24)%>%
-  mutate(workerid = Sub_ID)%>%
+  mutate(sid = Sub_ID)%>%
   left_join(sents)%>%
-  select(workerid, sent, rating)
+  select(sid, sent, rating)
 
@@
 
+Read in demographics.
+
+```{r}
+demo <- read.csv("../parenting_proj_emilyhembacher_demo2016.csv")
+
+demo <- demo %>%
+  mutate(sid = SID)%>%
+  select(sid, ethnicity, parent_ed)
+
+attitudes <- left_join(attitudes, demo)
+```
+
 # Data Frames and Exclusions
@@
 atts <- dq %>%
-  group_by(workerid, category) %>% 
+  group_by(sid, category) %>% 
   summarise(rating = mean(rating))
@@
 ```
+```{r}
+dq$parent_ed <- as.factor(dq$parent_ed)
+
+mss <- dq %>%
+  group_by(sid, parent_ed) %>%
+  filter(!is.na(parent_ed))%>%
+  multi_boot_standard(col = "rating", na.rm = TRUE)
+
+qplot(parent_ed, data=mss)
+
+ms <- dq %>%
+  group_by(parent_ed, category) %>%
+  filter(!is.na(parent_ed))%>%
+  multi_boot_standard(col = "rating", na.rm = TRUE)
+
+ggplot(ms, aes(category, mean, fill=parent_ed)) +
+  geom_bar(stat="identity", position = "dodge") + 
+  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
+             position = position_dodge(width = .9)) + 
+  scale_fill_solarized()
+```

### 2017-03-23 paq/parenting_obs_paq.Rmd
lex diversity script

@@
 library(tibble)
+library(lme4)
 
@@
   scale_fill_solarized()
+
+da <- dq %>%
+  group_by(sid, parent_ed, category) %>%
+  filter(!is.na(parent_ed))%>%
+  multi_boot_standard(col = "rating", na.rm = TRUE)
+
+da$parent_ed <- as.numeric(da$parent_ed)
 ```
+Stats
+```{r eval = FALSE}
+mod <- lmer(mean ~ parent_ed *  category +
+                           (1 | sid), 
+                         data = da)
+summary(mod)
+```

### 2017-03-23 type_token_ratio.py
lex diversity script

@@ -1,0 +1,47 @@
+#!/usr/bin/python
+
+from __future__ import print_function
+import collections #has counter function
+import sys
+import string
+import csv
+
+def checkline(): #define a function that counts words in a line
+    global l
+    global wordcount
+    global words
+
+    w = l.split()     #flines[1].split()   # this splits the string at all the white space and makes an array of the words
+    w = [x.lower() for x in w]   # convert everything to lowercase
+    wordcount += len(w)
+    if 'words' in globals():     # combine all the lines into one list
+        words += w
+    else:
+        words = w
+
+#need to cycle through all files in a folder here instead of just grabbing the file in the argument.
+
+wordcount = 0              # initialize the variable
+SID = "SID" # need to set this to file name
+f = open(sys.argv[1])      # open the file
+flines = f.readlines()     # read in the lines of the file
+#linecount = len(flines)    # count the lines
+for l in flines:           # for each line 
+
+
+#need to add qualification here *MOT
+
+
+     checkline()            # combine the lines and split into words
+
+# remove all punctuations #
+for place, item in enumerate(words):
+    for c in string.punctuation:
+        words[place] = words[place].replace(c,'')
+
+repeated_words = collections.Counter(words)
+uniqueWords = list(set(words))
+
+c = csv.writer(open("data.csv", "wb"))
+c.writerow(["SID", "Word count","Token count","Lexical diversity"])
+c.writerow([str(SID), str(wordcount), str(len(repeated_words)), str(len(repeated_words)/float(len(words)))])

### 2017-05-31 joint_attention/parenting_obs_JA.Rmd
updated analysis for JA

---
title: "Parenting Observational Study"
author: "Emily"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    number_sections: true
---

<style type="text/css">
body, td {
   font-size: 14px;
}
code {
  font-size: 11px;
}
pre {
  font-size: 11px;
}
</style>

Data analysis of social referencing and uncertainty study.

# Data preprocessing

Preliminaries.

```{r echo=FALSE}
rm(list=ls())
knitr::opts_chunk$set(fig.width=8, fig.height=5, 
                      echo=TRUE, warning=FALSE, message=FALSE, cache=TRUE)
library(tidyverse)
library(lme4)
library(knitr)
library(markdown)
library(lmerTest)
library(stringr)
library(langcog)
theme_set(theme_bw())
```

Read in files and consolidate to the same directory.

```{r}
d.raw <- data.frame()
files <- dir("data/")

for (f in files) {
  jf <- paste("data/",f,sep="")
  jd <- read.csv(jf)

  SID <- str_replace(f, ".csv", "")
  line <- jd$JointAttention.ordinal
  phase_onset <- jd$JointAttention.onset
  phase_offset <- jd$JointAttention.offset
  pja <- jd$JointAttention.pJA
  cja <- jd$JointAttention.cJA
  bid <- jd$JointAttention.bids

  id <- data.frame(SID = SID,
                   line = line,
                   phase_onset = phase_onset,
                   phase_offset = phase_offset, 
                   pja = pja,
                   cja = cja,
                   bid = bid)

  l_pja <- id%>%
    mutate(phase_length = phase_offset - phase_onset)%>%
    filter(pja == 1)%>%
    group_by(SID, pja)%>%
    summarise(pja_length = sum(phase_length))%>%
    select(-pja)

  l_cja <- id%>%
    mutate(phase_length = phase_offset - phase_onset)%>%
    filter(cja == 1)%>%
    group_by(SID, cja)%>%
    summarise(cja_length = sum(phase_length))%>%
    select(-cja)

  c_pja <- id%>%
    group_by(SID)%>%
    summarise(pja = sum(pja))

  c_cja <- id%>%
    group_by(SID)%>%
    summarise(cja = sum(cja))

  c_bids <- id%>%
    group_by(SID)%>%
    summarise(bids = sum(bid))

  sd <- c_bids%>%
    left_join(c_cja)%>%
    left_join(c_pja)%>%
    left_join(c_cja)%>%
    left_join(l_pja)%>%
    left_join(l_cja)

sd$pja_length[is.na(sd$pja_length)] <- 0
sd$cja_length[is.na(sd$cja_length)] <- 0

sd <- sd %>%
  mutate(total_ja = pja + cja)%>%
  mutate(total_lja = pja_length + cja_length)

d.raw <- bind_rows(d.raw, sd)
}
```

Read in trial info and demographics.

```{r}
# demo <- read.csv("../parenting_obs_demo.csv")
conditions <- read.csv("conditions.csv")

d <- d.raw %>%
  left_join(conditions)%>%
  mutate(bids_tot = bids + cja + pja)
```

```{r}
#total  # episodes of JA
ms_total_ja <- d %>%
  group_by(Condition) %>%
  multi_boot_standard(col = "total_ja")

ggplot(ms_total_ja, aes(x = Condition, y = mean)) + 
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9)) +
  xlab("Condition") + 
  ylab("Episodes Joint Attention") 
```

```{r}
#total time JA
ms_total_lja <- d %>%
  group_by(Condition) %>%
  multi_boot_standard(col = "total_lja")

#plot length of joint attention.
ggplot(ms_total_lja, aes(x = Condition, y = mean)) + 
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9)) +
  xlab("Condition") + 
  ylab("Time Spent in Joint Attention") 
```

```{r}
#unsuccessful bids
ms_bids <- d %>%
  group_by(Condition) %>%
  multi_boot_standard(col = "bids")

ggplot(ms_bids, aes(x = Condition, y = mean)) + 
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))+
  xlab("Condition") + 
  ylab("Unsuccessful bids for Joint Attention") 
```

```{r}
# total bids
ms_bids <- d %>%
  group_by(Condition) %>%
  multi_boot_standard(col = "bids_tot")

ggplot(ms_bids, aes(x = Condition, y = mean)) + 
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))+
  xlab("Condition") + 
  ylab("Total bids for Joint Attention") 
```

```{r}
#pja
ms_pja <- d %>%
  group_by(Condition) %>%
  multi_boot_standard(col = "pja")

ggplot(ms_pja, aes(x = Condition, y = mean)) + 
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))+
  xlab("Condition") + 
  ylab("Episodes of Passive Joint Attention") 
```

```{r}
#cja
ms_cja <- d %>%
  group_by(Condition) %>%
  multi_boot_standard(col = "cja")

ggplot(ms_cja, aes(x = Condition, y = mean)) + 
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))+
  xlab("Condition") + 
  ylab("Episodes of Coordinated Joint Attention") 
```

```{r}
#cja
ms_lcja <- d %>%
  filter(!is.na(Condition))%>%
  group_by(Condition) %>%
  multi_boot_standard(col = "cja_length")

ggplot(ms_lcja, aes(x = Condition, y = mean)) + 
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))+
  xlab("Condition") + 
  ylab("Total time Spent in Coordinated Joint Attention") 
```

```{r}
#cja
ms_lpja <- d %>%
  filter(!is.na(Condition))%>%
  group_by(Condition) %>%
  multi_boot_standard(col = "pja_length")

#plot 
ggplot(ms_lpja, aes(x = Condition, y = mean)) + 
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))+
  xlab("Condition") + 
  ylab("Total time Spent in Passive Joint Attention") 
```

#Analysis

T-tests
```{r}
t.test(d$bids[d$Condition == "exp"],d$bids[d$Condition == "con"])
t.test(d$bids_tot[d$Condition == "exp"],d$bids_tot[d$Condition == "con"])
t.test(d$cja[d$Condition == "exp"],d$cja[d$Condition == "con"])
t.test(d$pja[d$Condition == "exp"],d$pja[d$Condition == "con"])
t.test(d$pja_length[d$Condition == "exp"],d$pja_length[d$Condition == "con"])
t.test(d$cja_length[d$Condition == "exp"],d$cja_length[d$Condition == "con"])
t.test(d$total_ja[d$Condition == "exp"],d$total_ja[d$Condition == "con"])
t.test(d$total_lja[d$Condition == "exp"],d$total_lja[d$Condition == "con"])
```

Significant effect of condition on total number of bids and unsuccessful bids (most bids are unsuccessful).

Mixed effects models.

```{r}
bids <- lmer(bids_tot ~ Condition  +
                           (1 | SID) + (1 | Video),
                         data = d)
```

```{r eval = FALSE}
maximal_mod <- lmer(l_pja ~ condition * EL_score +
                           (condition * EL_score | SID), 
                         data = lmer_data)

maximal_mod <- lmer(l_cja ~ condition * EL_score +
                           (condition * EL_score | SID), 
                         data = lmer_data)

maximal_mod <- lmer(c_bids ~ condition * EL_score +
                           (condition * EL_score | SID), 
                         data = lmer_data)

maximal_mod <- lmer(c_pja ~ condition * EL_score +
                           (condition * EL_score | SID), 
                         data = lmer_data)

maximal_mod <- lmer(c_cja ~ condition * EL_score +
                           (condition * EL_score | SID), 
                         data = lmer_data)
```

### 2017-05-31 paq/parenting_obs_paq.Rmd
updated analysis for JA

@@
 ```
+
+Demographics
 ```{r}

### 2017-05-31 joint_attention/parenting_obs_JA.Rmd
added demographics to ja analysis

@@
 ```{r}
-# demo <- read.csv("../parenting_obs_demo.csv")
 conditions <- read.csv("conditions.csv")
+
+load("../paq/paq_demo.RData")
+
+ids$SID <- ids$sid
 
@@
   left_join(conditions)%>%
-  mutate(bids_tot = bids + cja + pja)
+  mutate(bids_tot = bids + cja + pja)%>%
+  left_join(ids)
 ```
@@
 ggplot(ms_bids, aes(x = Condition, y = mean)) + 
+  geom_bar(stat="identity") + 
+  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
+             position = position_dodge(width = .9))+
+  xlab("Condition") + 
+  ylab("Total bids for Joint Attention") 
+```
+
+```{r}
+# total bids
+ms_bids <- d %>%
+  group_by(Condition) %>%
+  multi_boot_standard(col = "bids_tot")
+
+ggplot(ms_bids, aes(x = Condition, y = mean, fill=gender)) + 
   geom_bar(stat="identity") + 

### 2017-05-31 paq/parenting_obs_paq.Rmd
added demographics to ja analysis

@@
 
+paq_gd <- read.csv('paq_gdrive.csv')
+
 paq <- paq %>%
@@
   mutate(sid = SID)%>%
-  select(sid, ethnicity, parent_ed)
+  select(sid, ethnicity, parent_ed, num_lang, gender, age)
 
@@
 ```
+
+Get data for individual differences analysis.
+```{r}
+ids <- dq %>%
+  group_by(sid, category) %>%
+  multi_boot_standard(col = "rating", na.rm = TRUE)%>%
+  select(sid, category, mean)%>%
+  spread(category, mean)%>%
+  left_join(demo)
+
+save(ids, file = "paq_demo.RData")
+```

### 2017-05-31 joint_attention/parenting_obs_JA.Rmd
JA code working

--- 2017-05-31 joint_attention/parenting_obs_JA.Rmd
@@
 
-Data analysis of social referencing and uncertainty study.
+Looking at the effect of electronically-delivered parenting interventions on parent-child interactions.
+Parents in the experimental condition viewed a video (designed for a parenting app) demonstrating an activity they could do with their child.
+Parents in the control condition did not view a video.
+Both groups of parents were asked to play with their child for 3 minutes with a set of props that matched the video demonstration they had seen.
+Children were 6-24 months of age.
+There were 6 videos total (2 per age group).
+Assignment to videos/sets of toys was counterbalanced within age groups.
+Parents also completed the Parenting Attitudes Questionnaire.
+Videos of the play sessions were coded for bids for joint attention, episodes of passive joint attention, and episodes of coordinated joint attention.
 
@@
 ```{r}
-# demo <- read.csv("../parenting_obs_demo.csv")
 conditions <- read.csv("conditions.csv")
+
+load("../paq/paq_demo.RData")
+load("../paq/obs_demo.RData")
+
+ids <- ids%>%
+  mutate(SID = sid)%>%
+  select(-sid)
+
+demo <- demo%>%
+  mutate(SID = sid)%>%
+  select(-sid)%>%
+  mutate(age_months = age * 12)
+
+demo$age_group[demo$age_months <= 12] <- "6"
+demo$age_group[demo$age_months > 12 & demo$age_months <= 18 ] <- "12"
+demo$age_group[demo$age_months > 18] <- "18"
 
@@
   left_join(conditions)%>%
-  mutate(bids_tot = bids + cja + pja)
+  mutate(bids_tot = bids + cja + pja)%>%
+  left_join(demo)%>%
+  left_join(ids)%>%
+  select(-sid)
 ```
 
+#Plots
+
+Total number of bids (successful and unsuccessful)
 ```{r}
-#total  # episodes of JA
-ms_total_ja <- d %>%
-  group_by(Condition) %>%
-  multi_boot_standard(col = "total_ja")
-
-ggplot(ms_total_ja, aes(x = Condition, y = mean)) + 
-  geom_bar(stat="identity") + 
-  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
-             position = position_dodge(width = .9)) +
-  xlab("Condition") + 
-  ylab("Episodes Joint Attention") 
-```
-
-```{r}
-#total time JA
-ms_total_lja <- d %>%
-  group_by(Condition) %>%
-  multi_boot_standard(col = "total_lja")
-
-#plot length of joint attention.
-ggplot(ms_total_lja, aes(x = Condition, y = mean)) + 
-  geom_bar(stat="identity") + 
-  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
-             position = position_dodge(width = .9)) +
-  xlab("Condition") + 
-  ylab("Time Spent in Joint Attention") 
-```
-
-```{r}
-#unsuccessful bids
-ms_bids <- d %>%
-  group_by(Condition) %>%
-  multi_boot_standard(col = "bids")
-
-ggplot(ms_bids, aes(x = Condition, y = mean)) + 
-  geom_bar(stat="identity") + 
-  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
-             position = position_dodge(width = .9))+
-  xlab("Condition") + 
-  ylab("Unsuccessful bids for Joint Attention") 
-```
-
-```{r}
-# total bids
 ms_bids <- d %>%
@@
 
+Episodes of passive joint attention.
 ```{r}
-#pja
 ms_pja <- d %>%
@@
 
+Episodes of coordinated joint attention
 ```{r}
-#cja
 ms_cja <- d %>%
@@
 
+Total duration of passive joint attention.
 ```{r}
-#cja
+ms_lpja <- d %>%
+  filter(!is.na(Condition))%>%
+  group_by(Condition) %>%
+  multi_boot_standard(col = "pja_length")
+
+ggplot(ms_lpja, aes(x = Condition, y = mean)) + 
+  geom_bar(stat="identity") + 
+  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
+             position = position_dodge(width = .9))+
+  xlab("Condition") + 
+  ylab("Total Duration Passive Joint Attention") 
+```
+
+Total duration of coordinated joint attention.
+```{r}
 ms_lcja <- d %>%
@@
   xlab("Condition") + 
-  ylab("Total time Spent in Coordinated Joint Attention") 
+  ylab("Total Duration Coordinated Joint Attention") 
 ```
 
+##Demographics
+
+###Child gender
+
+Total bids by gender.
 ```{r}
-#cja
-ms_lpja <- d %>%
-  filter(!is.na(Condition))%>%
-  group_by(Condition) %>%
-  multi_boot_standard(col = "pja_length")
+# total bids
+ms_bids <- d %>%
+  group_by(Condition, gender) %>%
+  multi_boot_standard(col = "bids_tot")
 
-#plot 
-ggplot(ms_lpja, aes(x = Condition, y = mean)) + 
-  geom_bar(stat="identity") + 
+ggplot(ms_bids, aes(x = Condition, y = mean, fill=gender)) + 
+  geom_bar(stat="identity", position = "dodge") + 
   geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
@@
   xlab("Condition") + 
-  ylab("Total time Spent in Passive Joint Attention") 
+  ylab("Total bids for Joint Attention") 
+```
+
+Total duration of passive joint attention by gender
+```{r}
+ms_lpja <- d %>%
+  filter(!is.na(Condition))%>%
+  group_by(Condition, gender) %>%
+  multi_boot_standard(col = "pja_length")
+
+ggplot(ms_lpja, aes(x = Condition, y = mean, fill=gender)) + 
+  geom_bar(stat="identity", position = "dodge") + 
+  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
+             position = position_dodge(width = .9))+
+  xlab("Condition") + 
+  ylab("Total Duration Passive Joint Attention") 
+```
+
+Total duration of coordinated joint attention by gender
+```{r}
+ms_lcja <- d %>%
+  filter(!is.na(Condition))%>%
+  group_by(Condition, gender) %>%
+  multi_boot_standard(col = "cja_length")
+
+ggplot(ms_lcja, aes(x = Condition, y = mean, fill=gender)) + 
+  geom_bar(stat="identity", position = "dodge") + 
+  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
+             position = position_dodge(width = .9))+
+  xlab("Condition") + 
+  ylab("Total Duration Coordinated Joint Attention") 
+```
+
+###Child age
+
+Children were separated into 3 age groups: 6-12 months, 12-18 months, and 18-24 months.
+
+Total bids by age.
+```{r}
+# total bids
+ms_bids <- d %>%
+  group_by(Condition, age_group) %>%
+  multi_boot_standard(col = "bids_tot")
+
+ms_bids$age_group <- factor(ms_bids$age_group , levels = c("6","12", "18"))
+
+ggplot(ms_bids, aes(x = Condition, y = mean, fill=age_group)) + 
+  geom_bar(stat="identity", position= "dodge") + 
+  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
+             position = position_dodge(width = .9))+
+  xlab("Condition") + 
+  ylab("Total bids for Joint Attention") 
+```
+
+Total duration of passive joint attention by age
+```{r}
+ms_lpja <- d %>%
+  filter(!is.na(Condition))%>%
+  group_by(Condition, age_group) %>%
+  multi_boot_standard(col = "pja_length")
+
+ggplot(ms_lpja, aes(x = Condition, y = mean, fill = age_group)) + 
+  geom_bar(stat="identity", position = "dodge") + 
+  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
+             position = position_dodge(width = .9))+
+  xlab("Condition") + 
+  ylab("Total Duration Passive Joint Attention") 
+```
+
+Total duration of coordinated joint attention by age
+```{r}
+ms_lcja <- d %>%
+  filter(!is.na(Condition))%>%
+  group_by(Condition, age_group) %>%
+  multi_boot_standard(col = "cja_length")
+
+ggplot(ms_lcja, aes(x = Condition, y = mean, fill = age_group)) + 
+  geom_bar(stat="identity", position = "dodge") + 
+  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
+             position = position_dodge(width = .9))+
+  xlab("Condition") + 
+  ylab("Total Duration Coordinated Joint Attention") 
+```
+
+###Parenting attitudes and education
+
+Do PAQ scores predict the number of bids for joint attention by parents?
+```{r}
+d_plot <- d %>%
+  gather("subscale","score", AA:RR)
+
+ggplot(d_plot, aes(x = score, y = bids_tot, col = subscale)) +
+  geom_jitter() + 
+  xlim(0,6) +
+  geom_smooth(method="lm", se=FALSE)  + 
+  facet_wrap(~Condition)+
+  ggthemes::theme_few() +
+  langcog::scale_colour_solarized() 
+```
+
+Does parent education predict the number of bids for joint attention by parents?
+```{r}
+d_plot <- d %>%
+  gather("subscale","score", AA:RR)
+
+ggplot(d_plot, aes(x = parent_ed, y = bids_tot)) +
+  geom_jitter() + 
+  xlim(0,6) +
+  geom_smooth(method="lm", se=FALSE)  + 
+  facet_wrap(~Condition)+
+  ggthemes::theme_few() +
+  langcog::scale_colour_solarized() 
 ```
@@
 
-T-tests
+Mixed effects models.
+
+Prepare data.
 ```{r}
-t.test(d$bids[d$Condition == "exp"],d$bids[d$Condition == "con"])
-t.test(d$bids_tot[d$Condition == "exp"],d$bids_tot[d$Condition == "con"])
-t.test(d$cja[d$Condition == "exp"],d$cja[d$Condition == "con"])
-t.test(d$pja[d$Condition == "exp"],d$pja[d$Condition == "con"])
-t.test(d$pja_length[d$Condition == "exp"],d$pja_length[d$Condition == "con"])
-t.test(d$cja_length[d$Condition == "exp"],d$cja_length[d$Condition == "con"])
-t.test(d$total_ja[d$Condition == "exp"],d$total_ja[d$Condition == "con"])
-t.test(d$total_lja[d$Condition == "exp"],d$total_lja[d$Condition == "con"])
+lmer_data <- d %>%
+  filter(!is.na(AA), !is.na(EL), !is.na(RR))%>%
+  mutate(Condition = factor(Condition), 
+         bids_tot = as.numeric(bids_tot),
+         EL = as.numeric(langcog::scale(EL, scale=FALSE)),
+         AA = as.numeric(langcog::scale(AA, scale=FALSE)),
+         RR = as.numeric(langcog::scale(RR, scale=FALSE)),
+         age = as.numeric(langcog::scale(age, scale=FALSE)),
+         gender = as.factor(gender),
+         Video = as.factor(Video))
 ```
 
-Significant effect of condition on total number of bids and unsuccessful bids (most bids are unsuccessful).
-
-Mixed effects models.
-
+Total number of bids
 ```{r}
-bids <- lmer(bids_tot ~ Condition  +
-                           (1 | SID) + (1 | Video),
-                         data = d)
+maximal_mod <- lmer(bids_tot ~ Condition *  EL  + Condition * AA + Condition * RR + age + gender +
+                           (1| Video), 
+                         data = lmer_data)
+summary(maximal_mod)
 ```
 
-```{r eval = FALSE}
-maximal_mod <- lmer(l_pja ~ condition * EL_score +
-                           (condition * EL_score | SID), 
+Episodes of coordinated joint attention.
+```{r}
+maximal_mod <- lmer(cja ~ Condition *  EL  + Condition * AA + Condition * RR  + age + gender +
+                           (1| Video), 
                          data = lmer_data)
+summary(maximal_mod)
+```
 
-maximal_mod <- lmer(l_cja ~ condition * EL_score +
-                           (condition * EL_score | SID), 
+Episodes of passive joint attention.
+```{r}
+maximal_mod <- lmer(pja ~ Condition *  EL  + Condition * AA + Condition * RR  + age + gender +
+                           (1| Video), 
                          data = lmer_data)
+summary(maximal_mod)
+```
 
-maximal_mod <- lmer(c_bids ~ condition * EL_score +
-                           (condition * EL_score | SID), 
+Total duration of passive joint attention.
+```{r}
+maximal_mod <- lmer(pja_length ~ Condition *  EL  + Condition * AA + Condition * RR  + age + gender +
+                           (1| Video), 
                          data = lmer_data)
+summary(maximal_mod)
+```
 
-maximal_mod <- lmer(c_pja ~ condition * EL_score +
-                           (condition * EL_score | SID), 
+Total duration of coordinated joint attention.
+```{r}
+maximal_mod <- lmer(cja_length ~ Condition *  EL  + Condition * AA + Condition * RR  + age + gender +
+                           (1| Video), 
                          data = lmer_data)
+summary(maximal_mod)
+```
 
-maximal_mod <- lmer(c_cja ~ condition * EL_score +
-                           (condition * EL_score | SID), 
-                         data = lmer_data)
-```
+#Conclusions

### 2017-06-01 joint_attention/parenting_obs_JA.Rmd
updated JA code with conclusions

@@
 
-ggplot(ms_bids, aes(x = Condition, y = mean)) + 
+ggplot(ms_bids, aes(x = Condition, y = mean, fill = Condition)) + 
   geom_bar(stat="identity") + 
@@
   xlab("Condition") + 
-  ylab("Total bids for Joint Attention")
+  ylab("Total bids for Joint Attention") +
+  langcog::scale_colour_solarized()  +
+  ggthemes::theme_few() 
 ```
@@
 
-ggplot(ms_pja, aes(x = Condition, y = mean)) + 
+ggplot(ms_pja, aes(x = Condition, y = mean, fill = Condition)) + 
   geom_bar(stat="identity") + 
@@
   xlab("Condition") + 
-  ylab("Episodes of Passive Joint Attention") 
+  ylab("Episodes of Passive Joint Attention")  +
+  langcog::scale_colour_solarized()  +
+  ggthemes::theme_few() 
 ```
@@
 
-ggplot(ms_cja, aes(x = Condition, y = mean)) + 
+ggplot(ms_cja, aes(x = Condition, y = mean, fill = Condition)) + 
   geom_bar(stat="identity") + 
@@
   xlab("Condition") + 
-  ylab("Episodes of Coordinated Joint Attention") 
+  ylab("Episodes of Coordinated Joint Attention")  +
+  langcog::scale_colour_solarized()  +
+  ggthemes::theme_few() 
 ```
@@
 
-ggplot(ms_lpja, aes(x = Condition, y = mean)) + 
+ggplot(ms_lpja, aes(x = Condition, y = mean, fill = Condition)) + 
   geom_bar(stat="identity") + 
@@
   xlab("Condition") + 
-  ylab("Total Duration Passive Joint Attention") 
+  ylab("Total Duration Passive Joint Attention")  +
+  langcog::scale_colour_solarized()  +
+  ggthemes::theme_few() 
 ```
@@
 
-ggplot(ms_lcja, aes(x = Condition, y = mean)) + 
+ggplot(ms_lcja, aes(x = Condition, y = mean, fill = Condition)) + 
   geom_bar(stat="identity") + 
@@
   xlab("Condition") + 
-  ylab("Total Duration Coordinated Joint Attention") 
+  ylab("Total Duration Coordinated Joint Attention")  +
+  langcog::scale_colour_solarized()  +
+  ggthemes::theme_few() 
 ```
@@
   xlab("Condition") + 
-  ylab("Total bids for Joint Attention") 
+  ylab("Total bids for Joint Attention")  +
+  langcog::scale_colour_solarized()  +
+  ggthemes::theme_few() 
 ```
@@
 #Conclusions
+
+There is a main effect of condition on total bids for joint attention.
+Parents in the experimental condition (i.e., those who saw a video demonstrating an activity) made a greater number of bids for joint attention with their child.
+
+There was no effect of condition on the number of episodes of either passive or coordinated joint attention, or the duration of these episodes.
+
+There is a marginal effect of gender on bids for joint attention, with parents of males producing more bids.
+There is a marginal interaction between RR scores and condition on passive joint attention, such that the experimental condition increased the number of episodes of PJA to a greater extent for people with high RR scores.
+
+While the electronically-delivered parenting advice increased the number of bids for joint attention by parents, it did not significantly effect the number or duration of episodes of joint attention.
+One possibility is that child variables had a comparatively larger impact on the attainment of joint attention.

### 2017-06-01 joint_attention/parenting_obs_JA.Rmd
added demo tables

@@
 library(langcog)
+library(xtable)
 theme_set(theme_bw())
@@
 
-demo$age_group[demo$age_months <= 12] <- "6"
-demo$age_group[demo$age_months > 12 & demo$age_months <= 18 ] <- "12"
-demo$age_group[demo$age_months > 18] <- "18"
+demo$age_group[demo$age_months < 12] <- "6"
+demo$age_group[demo$age_months >= 12 & demo$age_months < 18 ] <- "12"
+demo$age_group[demo$age_months >= 18] <- "18"
 
@@
 ```
+
+#Demographics
+
+```{r}
+demos <- conditions%>%
+  left_join(demo)
+
+demos$parent_ed[demos$parent_ed == 1] <- 8
+demos$parent_ed[demos$parent_ed == 2] <- 12
+demos$parent_ed[demos$parent_ed == 3] <- 14
+demos$parent_ed[demos$parent_ed == 4] <- 18
+demos$parent_ed[demos$parent_ed == 5] <- 20
+demos$parent_ed[demos$parent_ed == 6] <- 22
+
+#child gender
+table(demos$Condition, demos$gender)
+#ethnicity
+table(demos$Condition, demos$ethnicity)
+#years of education
+table(demos$Condition, demos$parent_ed)
+```
+
+#Reliability
+
+Import reliability coder's data (20 participants were coded for reliability).
+```{r}
+d.raw_rel <- data.frame()
+files <- dir("rel_data/")
+
+for (f in files) {
+  jf <- paste("rel_data/",f,sep="")
+  jd <- read.csv(jf)
+
+  SID <- str_replace(f, ".csv", "")
+  line <- jd$JointAttention.ordinal
+  phase_onset <- jd$JointAttention.onset
+  phase_offset <- jd$JointAttention.offset
+  pja <- jd$JointAttention.pJA
+  cja <- jd$JointAttention.cJA
+  bid <- jd$JointAttention.bids
+
+  id <- data.frame(SID = SID,
+                   line = line,
+                   phase_onset = phase_onset,
+                   phase_offset = phase_offset, 
+                   pja = pja,
+                   cja = cja,
+                   bid = bid)
+
+  l_pja <- id%>%
+    mutate(phase_length = phase_offset - phase_onset)%>%
+    filter(pja == 1)%>%
+    group_by(SID, pja)%>%
+    summarise(pja_length = sum(phase_length))%>%
+    select(-pja)
+
+  l_cja <- id%>%
+    mutate(phase_length = phase_offset - phase_onset)%>%
+    filter(cja == 1)%>%
+    group_by(SID, cja)%>%
+    summarise(cja_length = sum(phase_length))%>%
+    select(-cja)
+
+  c_pja <- id%>%
+    group_by(SID)%>%
+    summarise(pja = sum(pja))
+
+  c_cja <- id%>%
+    group_by(SID)%>%
+    summarise(cja = sum(cja))
+
+  c_bids <- id%>%
+    group_by(SID)%>%
+    summarise(bids = sum(bid))
+
+  sd <- c_bids%>%
+    left_join(c_cja)%>%
+    left_join(c_pja)%>%
+    left_join(c_cja)%>%
+    left_join(l_pja)%>%
+    left_join(l_cja)
+
+sd$pja_length[is.na(sd$pja_length)] <- 0
+sd$cja_length[is.na(sd$cja_length)] <- 0
+
+sd <- sd %>%
+  mutate(total_ja = pja + cja)%>%
+  mutate(total_lja = pja_length + cja_length)
+
+d.raw_rel <- bind_rows(d.raw_rel, sd)
+}
+```
+
+Reliability.
+```{r}
+d.raw_rel <- d.raw_rel%>%
+  mutate(bids_rel = bids, pja_rel = pja, cja_rel = cja)%>%
+  select(SID, bids_rel, pja_rel, cja_rel)
+
+bids_mat <- d.raw_rel%>%
+  left_join(d.raw)%>%
+  select(bids, bids_rel)
+
+psych::ICC(bids_mat, missing = FALSE, alpha = 0.05)
+
+pja_mat <- d.raw_rel%>%
+  left_join(d.raw)%>%
+  select(pja, pja_rel)
+
+psych::ICC(pja_mat, missing = FALSE, alpha = 0.05)
+
+cja_mat <- d.raw_rel%>%
+  left_join(d.raw)%>%
+  select(cja, cja_rel)
+
+psych::ICC(cja_mat, missing = FALSE, alpha = 0.05)
+```
+
+Inter-rater reliability is very high for number of bids, high for number of episodes of coordinated joint attention, but there is less agreement for episodes passive joint attention.
 
@@
 ```{r}
-maximal_mod <- lmer(bids_tot ~ Condition *  EL  + Condition * AA + Condition * RR + age + gender +
+maximal_mod <- lmer(bids_tot ~ Condition *  EL  + Condition * AA + Condition * RR + age + gender + parent_ed +
                            (1| Video), 
@@
 ```{r}
-maximal_mod <- lmer(cja ~ Condition *  EL  + Condition * AA + Condition * RR  + age + gender +
+maximal_mod <- lmer(cja ~ Condition *  EL  + Condition * AA + Condition * RR  + age + gender + parent_ed +
                            (1| Video), 
@@
 ```{r}
-maximal_mod <- lmer(pja ~ Condition *  EL  + Condition * AA + Condition * RR  + age + gender +
+maximal_mod <- lmer(pja ~ Condition *  EL  + Condition * AA + Condition * RR  + age + gender + parent_ed +
                            (1| Video), 
@@
 ```{r}
-maximal_mod <- lmer(pja_length ~ Condition *  EL  + Condition * AA + Condition * RR  + age + gender +
+maximal_mod <- lmer(pja_length ~ Condition *  EL  + Condition * AA + Condition * RR  + age + gender + parent_ed +
                            (1| Video), 
@@
 ```{r}
-maximal_mod <- lmer(cja_length ~ Condition *  EL  + Condition * AA + Condition * RR  + age + gender +
+maximal_mod <- lmer(cja_length ~ Condition *  EL  + Condition * AA + Condition * RR  + age + gender + parent_ed +
                            (1| Video), 

### 2017-06-05 joint_attention/parenting_obs_JA.Rmd
fixed age plots
added age corr

@@
 library(xtable)
+library(Hmisc)
 theme_set(theme_bw())
@@
 d.raw_rel <- d.raw_rel%>%
-  mutate(bids_rel = bids, pja_rel = pja, cja_rel = cja)%>%
-  select(SID, bids_rel, pja_rel, cja_rel)
+  mutate(bids_rel = bids, pja_rel = pja, cja_rel = cja, l_pja_rel = pja_length, l_cja_rel = cja_length)%>%
+  select(SID, bids_rel, pja_rel, cja_rel, l_cja_rel, l_pja_rel)
 
@@
 psych::ICC(cja_mat, missing = FALSE, alpha = 0.05)
+
+l_pja_mat <- d.raw_rel%>%
+  left_join(d.raw)%>%
+  select(pja_length, l_pja_rel)
+
+psych::ICC(l_pja_mat, missing = FALSE, alpha = 0.05)
+
+l_cja_mat <- d.raw_rel%>%
+  left_join(d.raw)%>%
+  select(cja_length, l_cja_rel)
+
+psych::ICC(l_cja_mat, missing = FALSE, alpha = 0.05)
 ```
@@
 
+ms_lpja$age_group <- factor(ms_lpja$age_group , levels = c("6","12", "18"))
+
 ggplot(ms_lpja, aes(x = Condition, y = mean, fill = age_group)) + 
@@
   multi_boot_standard(col = "cja_length")
+
+ms_lcja$age_group <- factor(ms_lcja$age_group , levels = c("6","12", "18"))
 
@@
 #Analysis
+
+Is the duration of joint attention correlated with age in months?
+
+```{r}
+cormat <- d %>%
+  select(age_months, pja_length, cja_length, total_lja)
+rcorr(as.matrix(cormat))
+
+```
 

### 2017-06-28 parenting_obs_ling.Rmd
ling analysis

---
title: "parenting_obs_ling"
author: "Emily"
date: "6/23/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(psych)
library(langcog)
library(ggthemes)
library(lme4)
library(lmerTest)
library(tidytext)
```

# Data preprocessing

Preliminaries.
```{r}
files <- dir("trans_out")

f <- files[1]

for (f in files) {
  jf <- paste("trans_out/",f,sep="")
  tex <- read.table(jf, skip = 19)

  text <-  read.table(jf, header = FALSE, sep = "", quote = "\"'",
           na.strings = "NA",
           skip = 30, 
           strip.white = FALSE, blank.lines.skip = TRUE,
           comment.char = "#",
           allowEscapes = FALSE, flush = FALSE,
           stringsAsFactors = default.stringsAsFactors(),
           fileEncoding = "", encoding = "unknown", text, skipNul = TRUE)

  #paq answers
  attitudes_id <- data.frame(sid = as.factor(jd$WorkerId), 
               sent = jd$answers$data$sentence[1:24],
               rating = as.numeric(jd$answers$data$rating[1:24]))

  attitudes <- bind_rows(attitudes, attitudes_id)
}

```

```{r}
library(janeaustenr)
library(dplyr)
library(stringr)

original_books <- austen_books() %>%
  group_by(book) %>%
  mutate(linenumber = row_number(),
         chapter = cumsum(str_detect(text, regex("^chapter [\\divxlc]",
                                                 ignore_case = TRUE)))) %>%
  ungroup()

original_books
```

### 2017-06-28 type_token_ratio.py

@@ -1,47 +1,98 @@
-#!/usr/bin/python
-
 from __future__ import print_function
-import collections #has counter function
+
+import collections
+import os
 import sys
 import string
 import csv
+import re
 
-def checkline(): #define a function that counts words in a line
-    global l
-    global wordcount
-    global words
+def main(speech_dir,rel_file):
+    abso_file = speech_dir+rel_file
+    with open(abso_file) as f:
+        flines = f.readlines()
+        n_lines = len(flines)
+        words = []
+        for line in flines:
+            line = re.sub('\t+','\t',line) #condenses multiple tabs into one
+            splitline = line.strip().split('\t') #splits lines based on tabs
+            #print(splitline[0], len(splitline))
+            if len(splitline)!=2: 
+                continue
+            speaker = splitline[0].strip()
+            if (speaker!='*MOT:' and speaker!='*FAT:'):
+                continue
+            #print(speaker!='*MOT:' and speaker!='*FAT:',splitline[1])
+            new_words = splitline[1].split()
+            words += [word.lower() for word in new_words]
 
-    w = l.split()     #flines[1].split()   # this splits the string at all the white space and makes an array of the words
-    w = [x.lower() for x in w]   # convert everything to lowercase
-    wordcount += len(w)
-    if 'words' in globals():     # combine all the lines into one list
-        words += w
-    else:
-        words = w
+    n_words = len(words)
+    #print(words)
 
-#need to cycle through all files in a folder here instead of just grabbing the file in the argument.
+    # remove all punctuations
+    for i in range(n_words):
+        for c in string.punctuation:
+            words[i] = words[i].replace(c,'')
 
-wordcount = 0              # initialize the variable
-SID = "SID" # need to set this to file name
-f = open(sys.argv[1])      # open the file
-flines = f.readlines()     # read in the lines of the file
-#linecount = len(flines)    # count the lines
-for l in flines:           # for each line 
+    # remove empty words
+    words = list(filter(None, words))
+    n_words = len(words)
+
+    # count each word
+    word_count = collections.Counter(words)
+
+    # get the sorted list of unique words
+    unique_words = list(word_count.keys())
+    unique_words.sort()
+
+    n_unique = len(unique_words)
[…]

### 2017-07-07 parenting_obs_lexdiv.Rmd
linguistic analysis of transcripts added

---
title: "Parenting observation lexical diversity"
author: "Emily"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_float: true
    number_sections: true
---

# Data preprocessing

Preliminaries.

```{r echo=FALSE}
knitr::opts_chunk$set(fig.width=8, fig.height=5, 
                      echo=TRUE, warning=FALSE, message=FALSE, cache=FALSE)
suppressPackageStartupMessages(c("dplyr","langcog","tidyr","ggplot2","lme4"))
library(psych)
library(langcog)
library(tidyverse)
library(ggthemes)
library(lme4)
library(lmerTest)

select <- dplyr::select # masked by MASS
theme_set(theme_few())
```

Read in participant data.

```{r}
data <- read.csv("data.csv", header =TRUE)
dem <- read.csv("parenting_proj_emilyhembacher_demo2016.csv", header =TRUE)
conditions <- read.csv("joint_attention/conditions.csv")

#fix ids
data$SID <- stringr::str_trim(data$SID)
data$SID <- stringr::str_replace(data$SID, "_cut.txt", "")
data$SID <- stringr::str_replace(data$SID, "8283_", "")
data$SID <- stringr::str_replace(data$SID, "283_", "")
data$SID <- stringr::str_replace(data$SID, "_cut_save.txt", "")
data$SID <- stringr::str_replace(data$SID, "_cut_save", "")
data$SID <- stringr::str_replace(data$SID, "_cutsave.txt", "")
data$SID <- stringr::str_replace(data$SID, "parenting_obs_", "0")
data$SID <- stringr::str_replace(data$SID, "_cut_m4a.txt", "")

data$SID <- stringr::str_replace(data$SID, "05116_05", "050116_05")
data$SID <- stringr::str_replace(data$SID, "05116_2", "050116_02")
```

Make data frames.

```{r}
d <- left_join(data, conditions)%>%
  left_join(dem)%>%
  transmute(SID=SID, 
            types = Type.count, 
            tokens = Token.count, 
            lexdiv = Lexical.diversity, 
            condition= Condition, 
            video = Video, 
            age = age,
            gender = gender,
            parent_ed = parent_ed)%>%
  filter(!is.na(condition))
```

Plots.

Lexical Diversity.
```{r}
ms_lex <- d %>%
  group_by(condition) %>%
  multi_boot_standard(col = "lexdiv")

ggplot(ms_lex, aes(x = condition, y = mean, fill = condition)) + 
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))+
  xlab("Condition") + 
  ylab("Lexical Diversity") +
  langcog::scale_colour_solarized()  +
  ggthemes::theme_few() 
```

Number of Tokens.
```{r}
ms_tok <- d %>%
  group_by(condition) %>%
  multi_boot_standard(col = "tokens")

ggplot(ms_tok, aes(x = condition, y = mean, fill = condition)) + 
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))+
  xlab("Condition") + 
  ylab("Total Number of Word Tokens") +
  langcog::scale_colour_solarized()  +
  ggthemes::theme_few() 
```

Number of Word Types.
```{r}
ms_type <- d %>%
  group_by(condition) %>%
  multi_boot_standard(col = "types")

ggplot(ms_tok, aes(x = condition, y = mean, fill = condition)) + 
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))+
  xlab("Condition") + 
  ylab("Total Number of Word Types") +
  langcog::scale_colour_solarized()  +
  ggthemes::theme_few() 
```

### 2017-07-07 parenting_obs_lexdiv.Rmd
add analyses for prereg

@@
 conditions <- read.csv("joint_attention/conditions.csv")
+load("paq/paq_demo.RData")
 
@@
   left_join(dem)%>%
-  transmute(SID=SID, 
+  transmute(sid=SID, 
             types = Type.count, 
@@
             parent_ed = parent_ed)%>%
+  left_join(ids)%>%
   filter(!is.na(condition))
@@
 ```
+
+Analyses.
+
+Prepare data.
+```{r}
+lmer_data <- d %>%
+  filter(!is.na(AA), !is.na(EL), !is.na(RR))%>%
+  mutate(condition = factor(condition), 
+         lexdiv = as.numeric(lexdiv),
+         EL = as.numeric(langcog::scale(EL, scale=FALSE)),
+         AA = as.numeric(langcog::scale(AA, scale=FALSE)),
+         RR = as.numeric(langcog::scale(RR, scale=FALSE)),
+         age = as.numeric(langcog::scale(age, scale=FALSE)),
+         gender = as.factor(gender),
+         video = as.factor(video))
+```
+
+Predicting lexical diversity based on experimental condition, PAQ, demographics. 
+```{r}
+maximal_mod <- lmer(lexdiv ~ condition *  EL  + condition * AA + condition * RR  + age + gender + parent_ed +
+                           (1| video), 
+                         data = lmer_data)
+summary(maximal_mod)
+```
+
+Predicting the number of word tokens based on experimental condition, PAQ, demographics.  
+```{r}
+maximal_mod <- lmer(tokens ~ condition *  EL  + condition * AA + condition * RR  + age + gender + parent_ed +
+                           (1| video), 
+                         data = lmer_data)
+summary(maximal_mod)
+```
+
+Predicting the number of word types based on experimental condition, PAQ, demographics.  
+```{r}
+maximal_mod <- lmer(types ~ condition *  EL  + condition * AA + condition * RR  + age + gender + parent_ed +
+                           (1| video), 
+                         data = lmer_data)
+summary(maximal_mod)
+```

### 2017-07-07 parenting_obs_lexdiv.Rmd
get rid of old files

@@
 
-Plots.
+#Plots
 
-Lexical Diversity.
+##Lexical Diversity
 ```{r}
@@
 
-Number of Tokens.
+##Word Tokens
 ```{r}
@@
 
-Number of Word Types.
+##Word Types
 ```{r}
@@
 
-Analyses.
+#Analyses
 
@@
 
+##Lexical diversity
 Predicting lexical diversity based on experimental condition, PAQ, demographics. 
@@
 
+##Word tokens
 Predicting the number of word tokens based on experimental condition, PAQ, demographics.  
@@
 
+##Word types
 Predicting the number of word types based on experimental condition, PAQ, demographics.  
@@
 ```
+
+#Conclusions
+
+Both the number of tokens and types are higher in the experimental condition, while lexical diversity (type-token ratio) is higher in the control condition.
+Parents may be relatively more repetetive in the experimental condition since they are attempting to stick to a specific prescribed task, but they talk more overall!
+Demographics and PAQ do not interact with condition, but there is a marginal effect of RR score on lexical diversity (lower ld for higher RR scores), and marginal effects of parent education on word types and tokens (more types and tokens for higher parent ed).

### 2017-07-20 parenting_obs_lexdiv.Rmd
update readme

@@
 ```{r}
-data <- read.csv("data.csv", header =TRUE)
+data <- read.csv("lexdiv_data.csv", header =TRUE)
 dem <- read.csv("parenting_proj_emilyhembacher_demo2016.csv", header =TRUE)

### 2017-07-20 type_token_ratio.py

@@ -86,7 +86,7 @@ def main(speech_dir,rel_file):
 if __name__ == '__main__':
     d = sys.argv[1] #directory name
     filelist = os.listdir(d)
-    c = csv.writer(open("data.csv", "wb"))
+    c = csv.writer(open("lexdiv_data.csv", "wb"))
     c.writerow(["SID", "Type count","Token count","Lexical diversity"])
 
     for rf in filelist:

### 2017-11-09 parenting_obs_e1/joint_attention/parenting_obs_JA.Rmd
reorganize file structure

--- 2017-06-05 joint_attention/parenting_obs_JA.Rmd
@@
 
+ms_bids$Condition <- factor(ms_bids$Condition,
+levels = c("con", "exp"),
+labels = c("control", "video"))
+
 ggplot(ms_bids, aes(x = Condition, y = mean, fill = Condition)) + 
@@
   langcog::scale_colour_solarized()  +
-  ggthemes::theme_few() 
+  ggthemes::theme_few() + 
+  theme(legend.title = element_text(size=18), 
+        legend.text = element_text(size=16), 
+        axis.text.x  = element_text(vjust=0.5, size=16),
+        axis.title.x = element_text(size=18), 
+        axis.text.y  = element_text(vjust=0.5, size=16),
+        axis.title.y = element_text(size=18))
+```
+
+Total episodes of joint attention.
+
+```{r}
+ms_tja <- d %>%
+  group_by(Condition) %>%
+  multi_boot_standard(col = "total_ja")
+
+ms_tja$Condition <- factor(ms_tja$Condition,
+levels = c("con", "exp"),
+labels = c("control", "video"))
+
+ggplot(ms_tja, aes(x = Condition, y = mean, fill = Condition)) + 
+  geom_bar(stat="identity") + 
+  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
+             position = position_dodge(width = .9))+
+  xlab("Condition") + 
+  ylab("Total episodes of Joint Attention") +
+  langcog::scale_colour_solarized()  +
+  ggthemes::theme_few() + 
+  theme(legend.title = element_text(size=18), 
+        legend.text = element_text(size=16), 
+        axis.text.x  = element_text(vjust=0.5, size=16),
+        axis.title.x = element_text(size=18), 
+        axis.text.y  = element_text(vjust=0.5, size=16),
+        axis.title.y = element_text(size=18))
 ```
@@
   langcog::scale_colour_solarized() + 
-  ggthemes::theme_few() 
+  theme(legend.title = element_text(size=18), 
+        legend.text = element_text(size=16), 
+        axis.text.x  = element_text(vjust=0.5, size=16),
+        axis.title.x = element_text(size=18), 
+        axis.text.y  = element_text(vjust=0.5, size=16),
+        axis.title.y = element_text(size=18))
 ```
@@
   langcog::scale_colour_solarized()  + 
-  ggthemes::theme_few() 
+  theme(legend.title = element_text(size=18), 
+        legend.text = element_text(size=16), 
+        axis.text.x  = element_text(vjust=0.5, size=16),
+        axis.title.x = element_text(size=18), 
+        axis.text.y  = element_text(vjust=0.5, size=16),
+        axis.title.y = element_text(size=18))
 ```

### 2018-08-31 type_token_ratio.py
added notes about mtld

@@ -1,98 +1,0 @@
-from __future__ import print_function
-
-import collections
-import os
-import sys
-import string
-import csv
-import re
-
-def main(speech_dir,rel_file):
-    abso_file = speech_dir+rel_file
-    with open(abso_file) as f:
-        flines = f.readlines()
-        n_lines = len(flines)
-        words = []
-        for line in flines:
-            line = re.sub('\t+','\t',line) #condenses multiple tabs into one
-            splitline = line.strip().split('\t') #splits lines based on tabs
-            #print(splitline[0], len(splitline))
-            if len(splitline)!=2: 
-                continue
-            speaker = splitline[0].strip()
-            if (speaker!='*MOT:' and speaker!='*FAT:'):
-                continue
-            #print(speaker!='*MOT:' and speaker!='*FAT:',splitline[1])
-            new_words = splitline[1].split()
-            words += [word.lower() for word in new_words]
-
-    n_words = len(words)
-    #print(words)
-
-    # remove all punctuations
-    for i in range(n_words):
-        for c in string.punctuation:
-            words[i] = words[i].replace(c,'')
-
-    # remove empty words
-    words = list(filter(None, words))
-    n_words = len(words)
-
-    # count each word
-    word_count = collections.Counter(words)
-
-    # get the sorted list of unique words
-    unique_words = list(word_count.keys())
-    unique_words.sort()
-
-    n_unique = len(unique_words)
-    ttr = len(word_count)/float(len(words))
-
-    """
-    out_fname = '{}_out.txt'.format(os.path.splitext(speech_sample)[0])
-
-    out_lines = []
-    out_lines.append('Type-Token Ratio (U/T):           {:0.4f}\n'.format(ttr))
-    out_lines.append('Number of Utterances:             {}\n'.format(n_lines))
-    out_lines.append('Total Number of Words (T):        {}\n'.format(n_words))
-    out_lines.append('Total Number of Unique Words (U): {}\n'.format(n_unique))
-
-    out_lines.append('\nUnique Words (frequency):\n')
-    for word, count in word_count.most_common():
-        out_lines.append('{}\t{}\n'.format(count, word))
-
-    out_lines.append('\nUnique Words (alphabetical):\n')
-    for word in unique_words:
-        out_lines.append('{}\t{}\n'.format(word_count[word], word))
-    """
-
[…]

### 2018-08-31 parenting_obs_e1/joint_attention/parenting_obs_JA.Rmd
add notes about converting word to text

@@
 for (f in files) {
+
   jf <- paste("data/",f,sep="")
@@
 
+#note from Emily- I calculated total bids by adding unsuccessful bids + episodes of joint attention that were acheived.
+In retrospect, this assumes that all episodes of JA were initiated by parent, which is probably false.
+Next time, code all parent bids rather than only unsuccessful ones.
 d <- d.raw %>%

### 2019-01-08 parenting_obs_e2/Lexical_Diversity_Analysis.Rmd
Add files via upload

---
title: "Compare Lexical Diversity Measurements: MTLD and HD-D
author: "Vivian"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_float: true
    number_sections: true
---

# Data preprocessing

Preliminaries.

```{r echo=FALSE}
knitr::opts_chunk$set(fig.width=8, fig.height=5, 
                      echo=TRUE, warning=FALSE, message=FALSE, cache = TRUE)
suppressPackageStartupMessages(c("dplyr","langcog","tidyr","ggplot2","lme4"))
library(psych)
library(langcog)
library(tidyverse)
library(ggthemes)
library(lme4)
library(lmerTest)

select <- dplyr::select # masked by MASS
theme_set(theme_few())
```

Read in participant data.

```{r}
data <- read.csv("MTLD_HDD.csv", header =TRUE)
# dem <- read.csv("parenting_proj_emilyhembacher_demo2016.csv", header =TRUE)
conditions <- read.csv("conditions.csv")
```

Make data frames.

```{r}
d <- left_join(data, conditions, by = "sid")
d$condition [d$sid=="111517_3"] = "exp"
d$video [d$sid=="111517_3"] = "big_small"
d$age [d$sid=="111517_3"] = "2"

```

#Plots

##TTR
```{r}
ms_lex <- d %>%
  group_by(condition) %>%
  multi_boot_standard(col = "TTR")

lex_means <- d%>%
  group_by(condition)%>%
  summarise(mean = mean(TTR))

lex_sds <- d%>%
  group_by(condition)%>%
  summarise(sd = sd(TTR))

ms_lex$condition <- factor(ms_lex$condition,
levels = c("con", "exp"),
labels = c("control", "video"))

ggplot(ms_lex, aes(x = condition, y = mean, fill = condition)) + 
  ylim(0.0, 0.6)+
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))+
  xlab("Condition") + 
  ylab("TTR") +
  langcog::scale_colour_solarized()  +
  ggthemes::theme_few() + 
  theme(legend.title = element_text(size=18), 
        legend.text = element_text(size=16), 
        axis.text.x  = element_text(vjust=0.5, size=16),
        axis.title.x = element_text(size=18), 
        axis.text.y  = element_text(vjust=0.5, size=16),
        axis.title.y = element_text(size=18))
```
## MTLD
```{r}
ms_lex <- d %>%
  group_by(condition) %>%
  multi_boot_standard(col = "MTLD")

lex_means <- d%>%
  group_by(condition)%>%
  summarise(mean = mean(MTLD))

lex_sds <- d%>%
  group_by(condition)%>%
  summarise(sd = sd(MTLD))

ms_lex$condition <- factor(ms_lex$condition,
levels = c("con", "exp"),
labels = c("control", "video"))

ggplot(ms_lex, aes(x = condition, y = mean, fill = condition)) + 
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))+
  xlab("Condition") + 
  ylab("MTLD") +
  langcog::scale_colour_solarized()  +
  ggthemes::theme_few() + 
  theme(legend.title = element_text(size=18), 
        legend.text = element_text(size=16), 
        axis.text.x  = element_text(vjust=0.5, size=16),
        axis.title.x = element_text(size=18), 
        axis.text.y  = element_text(vjust=0.5, size=16),
        axis.title.y = element_text(size=18))
```
## HDD
```{r}
ms_lex <- d %>%
  group_by(condition) %>%
  multi_boot_standard(col = "HDD")

lex_means <- d%>%
  group_by(condition)%>%
  summarise(mean = mean(HDD))

lex_sds <- d%>%
  group_by(condition)%>%
  summarise(sd = sd(HDD))

ms_lex$condition <- factor(ms_lex$condition,
levels = c("con", "exp"),
labels = c("control", "video"))

ggplot(ms_lex, aes(x = condition, y = mean, fill = condition)) + 
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))+
  xlab("Condition") + 
  ylab("HD-D") +
  langcog::scale_colour_solarized()  +
  ggthemes::theme_few() + 
  theme(legend.title = element_text(size=18), 
        legend.text = element_text(size=16), 
        axis.text.x  = element_text(vjust=0.5, size=16),
        axis.title.x = element_text(size=18), 
        axis.text.y  = element_text(vjust=0.5, size=16),
        axis.title.y = element_text(size=18))
```
##Word Tokens
```{r}
ms_tok <- d %>%
  group_by(condition) %>%
  multi_boot_standard(col = "tokens")

ms_tok$condition <- factor(ms_tok$condition,
levels = c("con", "exp"),
labels = c("control", "video"))

ggplot(ms_tok, aes(x = condition, y = mean, fill = condition)) + 
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))+
  xlab("Condition") + 
  ylab("Total Number of Word Tokens") +
  langcog::scale_colour_solarized()  +
  ggthemes::theme_few() + 
  theme(legend.title = element_text(size=18), 
        legend.text = element_text(size=16), 
        axis.text.x  = element_text(vjust=0.5, size=16),
        axis.title.x = element_text(size=18), 
        axis.text.y  = element_text(vjust=0.5, size=16),
        axis.title.y = element_text(size=18))
```

##Word Types
```{r}
ms_type <- d %>%
  group_by(condition) %>%
  multi_boot_standard(col = "types")

ms_type$condition <- factor(ms_type$condition,
levels = c("con", "exp"),
labels = c("control", "video"))

ggplot(ms_type, aes(x = condition, y = mean, fill = condition)) +
  ylim(0, 100)+
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))+
  xlab("Condition") + 
  ylab("Total Number of Word Types") +
  langcog::scale_colour_solarized()  +
  ggthemes::theme_few() + 
  theme(legend.title = element_text(size=18), 
        legend.text = element_text(size=16), 
        axis.text.x  = element_text(vjust=0.5, size=16),
        axis.title.x = element_text(size=18), 
        axis.text.y  = element_text(vjust=0.5, size=16),
        axis.title.y = element_text(size=18))
```

##Sentences Length
```{r}
ms_length <- d %>%
  group_by(condition) %>%
  multi_boot_standard(col = "len_sentence")

ms_length$condition <- factor(ms_length$condition,
levels = c("con", "exp"),
labels = c("control", "video"))

ggplot(ms_length, aes(x = condition, y = mean, fill = condition)) +
  ylim(0,4.5)+
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))+
  xlab("Condition") + 
  ylab("Average Sentence Length") +
  langcog::scale_colour_solarized()  +
  ggthemes::theme_few() + 
  theme(legend.title = element_text(size=18), 
        legend.text = element_text(size=16), 
        axis.text.x  = element_text(vjust=0.5, size=16),
        axis.title.x = element_text(size=18), 
        axis.text.y  = element_text(vjust=0.5, size=16),
        axis.title.y = element_text(size=18))
```
##Sentences Length by videos
```{r}
ms_length <- d %>%
  group_by(video) %>%
  multi_boot_standard(col = "len_sentence")

ms_length$video <- factor(ms_length$video,
levels = c("give_me_toy", "big or small", "puzzle", "Hamlin", "Feigenson", "Gopnik","big_small", "orchestra","color", "Lany", "Warneken", "Adolph"),
labels = c("give_me_toy", "big or small_young", "puzzle", "Hamlin", "Feigenson", "Gopnik","big_small_old", "orchestra","color", "Lany", "Warneken", "Adolph"))

ggplot(ms_length, aes(x = video, y = mean, fill = video)) +
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))+
  xlab("Videos") + 
  ylab("Average Sentence Length") +
  langcog::scale_colour_solarized()  +
  ggthemes::theme_few() + 
  theme(legend.title = element_text(size=18), 
        legend.text = element_text(size=16), 
        axis.text.x  = element_text(vjust=0.5, size=16),
        axis.title.x = element_text(size=18), 
        axis.text.y  = element_text(vjust=0.5, size=16),
        axis.title.y = element_text(size=18))
```
##Sentences Length by age
```{r}
ms_length <- d %>%
  group_by(age) %>%
  multi_boot_standard(col = "len_sentence")

ms_length$age <- factor(ms_length$age,
levels = c("1", "2"),
labels = c("12-18month", "18-24month"))

ggplot(ms_length, aes(x = age, y = mean, fill = age)) +
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))+
  xlab("Age") + 
  ylab("Average Sentence Length") +
  langcog::scale_colour_solarized()  +
  ggthemes::theme_few() + 
  theme(legend.title = element_text(size=18), 
        legend.text = element_text(size=16), 
        axis.text.x  = element_text(vjust=0.5, size=16),
        axis.title.x = element_text(size=18), 
        axis.text.y  = element_text(vjust=0.5, size=16),
        axis.title.y = element_text(size=18))
```

## Interindex correlations

```{r}

cor(d$ttr, d$mtld)
cor(d$ttr, d$hdd)
cor(d$mtld, d$hdd)

```

#Conclusions
In McCarthy-Jarvis2010 paper, MTLD and HD-D has a correlation of r = .800; 
MTLD and TTR r =.322;
HD-D and TTR r = -.051 (N = 1584). 
In our result, MTLD and HD-D are the best correlated, although r = .621; MTLD and ttr has r = .543, which is higher than what M-J2010 reported.

All of the measure show that control group has higher lexical diversity than experimental group, with MTLD showing the biggest contrast and HD-D smallest.

### 2019-01-08 parenting_obs_e2/get_all_parent_speech.py

@@ -1,0 +1,107 @@
+import os
+import string
+import pandas as pd
+from lexical_diversity import mtld, hdd
+import nltk
+from nltk.stem import WordNetLemmatizer
+from nltk import tokenize
+from statistics import mean
+lemmatizer = WordNetLemmatizer()
+
+# a function to clean texts in brackets
+def clean(string):
+    ret = ''
+    skip1c = 0
+    for i in string:
+        if i == '[':
+            skip1c += 1
+        elif i == ']' and skip1c > 0:
+            skip1c -= 1
+        elif skip1c == 0:
+            ret += i
+    return ret
+
+
+# formatted mother utterances (each utterance should be in the same one paragraph) by hand
+# "Female speaker" "*Other Child" "*OTH" "*BOTH" "*ADF,ADM" are what used to refer to other speakers than parent or child
+# should replace all "CHI 2:" with "CHI:"
+# get conditions.csv from google sheet instead of by hand
+
+# creat a dataframe for calculation results
+col_names = ['sid', 'MTLD', 'HDD', 'types', 'tokens', 'TTR', 'len_sentence']
+results = pd.DataFrame(columns = col_names)
+
+files = os.listdir("trans_out_txt/")
+files.remove('.DS_Store')
+all_dat = {}
+# print (files)
+for fname in files:
+    folder = "trans_out_txt/"
+    name =  fname
+    path = "".join((folder,name))
+    fr = open(path, 'r')
+    print (fr)
+    lines = []
+    for line in fr:
+        spm = line.split('*MOT:')
+        spm_1 = line.split('MOT:')
+        spd = line.split('*FAT:')
+        spd_1 = line.split('FAT:')
+        if len(spm)>1:
+            lines.append(spm[1]) # found mother speech, grab it
+        elif len(spd)>1:
+            lines.append(spd[1]) # found father speech, grab it
+        elif len(spd_1)>1:
+                lines.append(spd_1[1])
+        elif len(spm_1)>1:
+            lines.append(spm_1[1])
+    lines_str = " ".join(lines)
+    lines_str = lines_str.replace ('\n', '')
+    lines_str = lines_str.replace ('\t', '')
+    text_ready = clean(lines_str)
+#   print (repr(text_ready))
+    all_dat[fname] = text_ready
+
+# call MTLD and HDD functions and calculate
+    id = fname[6:14]
+    print (len(str.split(text_ready)))
+    if (len(str.split(text_ready)))>50:
[…]

### 2019-01-08 parenting_obs_e2/lexical_diversity.py

@@ -1,0 +1,102 @@
+#Copyright 2017 John Frens
+#
+#Permission is hereby granted, free of charge, to any person obtaining a copy of this software and associated documentation files (the "Software"), to deal in the Software without restriction, including without limitation the rights to use, copy, modify, merge, publish, distribute, sublicense, and/or sell copies of the Software, and to permit persons to whom the Software is furnished to do so, subject to the following conditions:
+#
+#The above copyright notice and this permission notice shall be included in all copies or substantial portions of the Software.
+#
+#THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY, FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM, OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE SOFTWARE.
+
+import string
+
+# Global trandform for removing punctuation from words
+remove_punctuation = str.maketrans('', '', string.punctuation)
+
+# MTLD internal implementation
+def mtld_calc(word_array, ttr_threshold):
+    current_ttr = 1.0
+    token_count = 0
+    type_count = 0
+    types = set()
+    factors = 0.0
+    
+    for token in word_array:
+        token = token.translate(remove_punctuation).lower() # trim punctuation, make lowercase
+        token_count += 1
+        if token not in types:
+            type_count +=1
+            types.add(token)
+        current_ttr = type_count / token_count
+        if current_ttr <= ttr_threshold:
+            factors += 1
+            token_count = 0
+            type_count = 0
+            types = set()
+            current_ttr = 1.0
+    
+    excess = 1.0 - current_ttr
+    excess_val = 1.0 - ttr_threshold
+    factors += excess / excess_val
+    if factors != 0:
+        return len(word_array) / factors
+    return -1
+
+# MTLD implementation
+def mtld(word_array, ttr_threshold=0.72):
+    if isinstance(word_array, str):
+        raise ValueError("Input should be a list of strings, rather than a string. Try using string.split()")
+    if len(word_array) < 50:
[…]

### 2019-01-09 paper/cogsci2019/cogsci2019.Rmd
ported TeX draft to Rmd

---
title: "Understanding the impact of electronically-delivered parenting advice"
bibliography: library.bib
csl: apa6.csl
document-params: "10pt, letterpaper"

author-information: > 
    \author{{\large \bf Hanwen Vivian~Zhang (vivian3@stanford.edu)} \\ Department of Psychology, Stanford University \\ Palo Alto, CA 94301 USA
    \AND {\large \bf George~Kachergis (george.kachergis@gmail.com)} \\ \\ Department of Psychology, Stanford University \\ Palo Alto, CA 94301 USA
    \AND {\large \bf Michael C.~Frank (mcfrank@stanford.edu)} \\ \\ Department of Psychology, Stanford University \\ Palo Alto, CA 94301 USA}

abstract: >
    Early parenting practices play an important role in shaping the future 
    outcomes of young children [@Hart1995; @Heckman2006]. 
    In particular, high quality early interactions and early language input appear to 
    facilitate more effective language learning and higher levels of school performance. 
    The rise in electronic parenting applications ("apps") holds the promise of delivering 
    low-cost, positive interventions on parenting style to a variety of different populations. 
    Of special interest are the parents of very young children, who are often difficult to reach in other ways. 
    Yet little is known about the effects of communicating to parents through app-based interventions.
    MTLD, types and tokens, joint attention, proportion of nouns/verbs/adjectives, 
    affect, concreteness, mean length of utterance...

keywords: >
    digital parenting advice; joint action; lexical diversity; guided play;

output: cogsci2016::cogsci_paper
#final-submission: \cogscifinalcopy
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=3, fig.height=3, fig.crop = F, 
                      fig.pos = "tb", fig.path='figs/',
                      echo=F, warning=F, cache=F, 
                      message=F, sanitize = T)
```

```{r, libraries}
library(png)
library(grid)
library(ggplot2)
library(xtable)
```

# Introduction

- children learn through play -- physics, object features

## Guided Play Scaffolds Learning
- guided play activities can scaffold children's language and reasoning

## Improving Parenting Practices and Language Use
- early interventions on parenting practices can help children's outcomes

## Effectiveness of Digital Delivery
apps are an easy way to deliver curated, age-appropriate parenting advice — but can we measure an influence on parent's language? and do the interventions lead to children paying more attention?

The quality of parent-child interactions can be measured by both the social engagement of parents (e.g., joint attention to objects in the environment) and the quality of language (e.g., vocabulary diversity). 
Although digitally-delivered activities are designed to promote learning and cognitive development, it is unclear how they might affect these dimensions of parent-child interactions. 
How does digital scaffolding of activities affect the social and linguistic characteristics of parents' speech to their children?

# Experiment 1

In Experiment 1, we invited parents of 6- to 24-month-old infants visiting the Children's Discovery Museum in San Jose to complete activities from the Kinedu app. 
Parents were randomly assigned to the video group or the control group; parents in the video group watched a video from the Kinedu app (matched to their child's age), and then performed the activity with their child using the props from the video. 
Parents in the control group did not watch a Kinedu video, instead they were given the same props and were told to play with their infants as they would at home. 
We found that compared to the control group, parents who watched a Kinedu video spoke more words overall, but had lower lexical diversity. 
They also made more bids for joint attention with their infants, although these bids did not result in more episodes of joint attention compared to the control group. 
In summary, following digitally-scaffolded activities may cause parents to engage with and speak more to children overall, but speak more repetitively.

## Method

### Participants. 
60 infants aged 6-24 months and their parents participated in a museum in northern California. We included infants who were exposed to English at least 50 percent of the time or who were exposed less but whose participating parent reported that they primarily speak English with their child at home.
[include specific demo info here?] - good to include now, and we can comment it out if it's too much (the full report/paper will have it)

### Materials.
Stimuli included videos from a commercial parenting application, Kinedu Inc. The videos were designed to show activities parents could perform with their child to foster cognitive and physical development, and were targeted to the child's age and development. In each video, an adult and child perform the activity while a narrator explains the activity and its purpose. We selected two videos for each of three age groups in our sample (6-11.9 months, 12-17.9 months, 18-23.94 months). More information about the specific videos is available in the Appendix. Participants were also given a set of props corresponding to those in the video they watched, so that they could complete the activity. The props associated with each video are listed in the Appendix.

Participants were randomly assigned to an Activity Video condition or No-Video Control condition. Participants in the Activity Video condition were assigned to one of the two videos available for their child's age group. The No-Video Control condition was yoked to the Activity Video condition such that for every participant in the Activity Video condition who saw a particular video and received the associated props, a participant in the No-Video Control condition received the same props but did not watch the corresponding video.
Parents also completed the Parenting Attitudes Questionnaire (PAQ). The PAQ measures parents' attitudes about parenting and child development along three dimensions: rules and respect, early learning, and affection and attachment.

## Procedure.
After providing informed consent, parents in the Activity Video condition watched the assigned video on a laptop with headphones.
To ensure that parents could give the video their full attention, the experimenter played with the infant with a set of toys (different from the experimental props used in the study) while the video was being played. 
Immediately following the video, each parent-child dyad was provided with the props to complete the activity they had viewed. 
The toys were placed on a large foam mat, and parents were instructed to sit on the mat with their child and re-create the activity they had viewed for a period of three minutes.
In the No-Video control condition, after consenting parents were told to play with their child as they would at home with the provided props for a period of three minutes. 
They were not given any additional instructions about how to use the props.

In both conditions, two video cameras were used to record the play session from different angles, and parents were fitted with a wireless audio recorder to record their speech to their child. After three minutes of play had elapsed, parents were told they could stop playing and cameras and audio were turned off. Parents were then asked to complete the PAQ before being debriefed.

### Joint Attention Coding Procedure.
Video of each session was coded for episodes of joint attention using Datavyu software. 
The video taken at floor level was coded by default, but the other video was referred to if the participants were not visible or if there was a technological error with the first camera. For each participant we coded for episodes of coordinated joint attention, episodes of passive joint attention, and parental bids for joint attention. 
We defined parental bids for joint attention as any attempt to initiate joint attention (i.e label, point, or otherwise draw attention to an object) that does not result in passive or coordinated joint attention. 
If more than 3 seconds elapsed between bids, they were coded as separate attempts. 
An episode of joint attention was considered passive if both participants visually focused on an object for a minimum of 3 seconds but the child did not acknowledge the parent. 
If either participant looked away from the object for less than 3 seconds and then returned to the same object it was considered part of the same period of joint attention. 
Episodes joint attention were considered coordinated if  both participants visually focused on an object for a minimum of 3 seconds and at some point in the interaction the child indicated awareness of interaction with some overt behavior toward the parent. 
This could be looks to the parent's face, gestures, vocalizations, or turn-taking. 
If either participant looked away for less than 3 seconds and then returned to the same object, it was coded as part of the same period of joint attention. 
A second coder independently coded a third of the videos (i.e., 20 of the 60 videos, approximately equally distributed across ages) to establish reliability. % report reliability

# Results

## Lexical Diversity

## Joint Attention

# Experiment 2

In Experiment 2 we attempt to replicate the findings from Experiment 1 with a restricted number of preregistered predictions. 
We will additionally include a second control condition, in which the same activities are described in written form, rather than being demonstrated in video. 
This manipulation will help determine what the contribution of the video demonstration is in producing the observed effects on parent-child interactions.

## Method

### Participants. 
84 infants aged 12-24 months and their parents participated in the same museum as Experiment 1. We included infants who were exposed to English at least 75 percent of the time or who were exposed less but whose participating parent reported that they primarily speak English with their child at home. [specific demo info]

### Materials. 
The design of Experiment 2 was similar to that of Experiment 1, except that instead of a No-Video control condition, parents instead watched a video that was generally related to child development research, but did not give any specific instructions about how to interact with infants or children. 
This was to control for the possibility that differences in language output and joint attention in Experiment 1 could be due to simply cuing parents to think about infants' learning and cognitive development. 
The videos presented in the Control Video condition were media clips (available on YouTube) of developmental psychologists explaining their research interleaved with footage of infants or toddlers engaged in developmental research studies. 
Thus, the content of the videos superficially matched those in the Activity Video condition, but did not suggest any particular activities.
The videos were trimmed to approximately match the average video length in the Activity Video condition (2 minutes ??).

### Procedure. 
The procedure for Experiment 2 matched that of Experiment 1, except that parents in the Control Video condition watched a control video before the play session. 
Consistent with the No-Video control condition in Experiment 1, parents in the Control Video condition were told to play with their child as they would at home, and were not given additional instructions.

# Results

## Lexical Diversity

## Joint Attention

# Discussion

For more information on citations in RMarkdown, see **[here](http://rmarkdown.rstudio.com/authoring_bibliographies_and_citations.html#citations).**

## Footnotes

Indicate footnotes with a number\footnote{Sample of the first
footnote.} in the text. Place the footnotes in 9 point type at the
bottom of the page on which they appear. Precede the footnote with a
horizontal rule.\footnote{Sample of the second footnote.} You can also use 
markdown formatting to include footnotes using this syntax [^1].

[^1]: Sample of a markdown footnote.

## Two-column images

You can read local images using png package for example and plot 
it like a regular plot using grid.raster from the grid package. 
With this method you have full control of the size of your image. **Note: Image must be in .png file format for the readPNG function to work.**

You might want to display a wide figure across both columns. To do this, you change the `fig.env` chunk option to `figure*`. To align the image in the center of the page, set `fig.align` option to `center`. To format the width of your caption text, you set the `num.cols.cap` option to `2`.

```{r 2-col-image, fig.env = "figure*", fig.pos = "h", fig.width=4, fig.height=2, fig.align = "center", set.cap.width=T, num.cols.cap=2, fig.cap = "This image spans both columns. And the caption text is limited to 0.8 of the width of the document."}
img <- png::readPNG("figs/walrus.png")
grid::grid.raster(img)
```

## One-column images

Single column is the default option, but if you want set it explicitly, set `fig.env` to `figure`. Notice that the `num.cols` option for the caption width is set to `1`.

```{r image, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=2, fig.height=2, set.cap.width=T, num.cols.cap=1, fig.cap = "One column image."}
img <- png::readPNG("figs/lab_logo_stanford.png")
grid::grid.raster(img)
```

## R Plots

You can use R chunks directly to plot graphs. And you can use latex floats in the
fig.pos chunk option to have more control over the location of your plot on the page. For more information on latex placement specifiers see **[here](https://en.wikibooks.org/wiki/LaTeX/Floats,_Figures_and_Captions)**

```{r plot, fig.env="figure", fig.pos = "H", fig.align = "center", fig.width=2, fig.height=2, fig.cap = "R plot" }
x <- 0:100
y <- 2 * (x + rnorm(length(x), sd = 3) + 3)

ggplot2::ggplot(data = data.frame(x, y), 
       aes(x = x, y = y)) + 
  geom_point() + 
  geom_smooth(method = "lm")
```

## Tables

Number tables consecutively; place the table number and title (in
10 point) above the table with one line space above the caption and
one line space below it, as in Table 1. You may float
tables to the top or bottom of a column, set wide tables across both
columns.

You can use the xtable function in the xtable package.

```{r xtable, results="asis"}
n <- 100
x <- rnorm(n)
y <- 2*x + rnorm(n)
out <- lm(y ~ x)

tab1 <- xtable::xtable(summary(out)$coef, digits=c(0, 2, 2, 1, 2), 
                      caption = "This table prints across one column.")

print(tab1, type="latex", comment = F, table.placement = "H")
```

# Acknowledgements

Place acknowledgments (including funding information) in a section at
the end of the paper.

# References

```{r}
# References will be generated automatically by Pandoc and included here.
# The following code is some latex to format the bibliography. Do not remove it.
```

\setlength{\parindent}{-0.1in} 
\setlength{\leftskip}{0.125in}
\noindent

### 2019-01-09 paper/cogsci2019/cogsci2019.tex
ported TeX draft to Rmd

--- 2019-01-09 paper/cogsci2019/cogsci2019.Rmd
@@
----
-title: "Understanding the impact of electronically-delivered parenting advice"
-bibliography: library.bib
-csl: apa6.csl
-document-params: "10pt, letterpaper"
+% Template for Cogsci submission with R Markdown
 
-author-information: > 
-    \author{{\large \bf Hanwen Vivian~Zhang (vivian3@stanford.edu)} \\ Department of Psychology, Stanford University \\ Palo Alto, CA 94301 USA
-    \AND {\large \bf George~Kachergis (george.kachergis@gmail.com)} \\ \\ Department of Psychology, Stanford University \\ Palo Alto, CA 94301 USA
-    \AND {\large \bf Michael C.~Frank (mcfrank@stanford.edu)} \\ \\ Department of Psychology, Stanford University \\ Palo Alto, CA 94301 USA}
+% Stuff changed from original Markdown PLOS Template
+\documentclass[10pt, letterpaper]{article}
 
-abstract: >
+\usepackage{cogsci}
+\usepackage{pslatex}
+\usepackage{float}
+\usepackage{caption}
+
+% amsmath package, useful for mathematical formulas
+\usepackage{amsmath}
+
+% amssymb package, useful for mathematical symbols
+\usepackage{amssymb}
+
+% hyperref package, useful for hyperlinks
+\usepackage{hyperref}
+
+% graphicx package, useful for including eps and pdf graphics
+% include graphics with the command \includegraphics
+\usepackage{graphicx}
+
+% Sweave(-like)
+\usepackage{fancyvrb}
+\DefineVerbatimEnvironment{Sinput}{Verbatim}{fontshape=sl}
+\DefineVerbatimEnvironment{Soutput}{Verbatim}{}
+\DefineVerbatimEnvironment{Scode}{Verbatim}{fontshape=sl}
+\newenvironment{Schunk}{}{}
+\DefineVerbatimEnvironment{Code}{Verbatim}{}
+\DefineVerbatimEnvironment{CodeInput}{Verbatim}{fontshape=sl}
+\DefineVerbatimEnvironment{CodeOutput}{Verbatim}{}
+\newenvironment{CodeChunk}{}{}
+
+% cite package, to clean up citations in the main text. Do not remove.
+\usepackage{apacite}
+
+% KM added 1/4/18 to allow control of blind submission
+
+\usepackage{color}
+
+% Use doublespacing - comment out for single spacing
+%\usepackage{setspace}
+%\doublespacing
+
+% % Text layout
+% \topmargin 0.0cm
+% \oddsidemargin 0.5cm
+% \evensidemargin 0.5cm
+% \textwidth 16cm
+% \textheight 21cm
+
+\title{Understanding the impact of electronically-delivered parenting advice}
+
+\author{{\large \bf Hanwen Vivian~Zhang (vivian3@stanford.edu)} \\ Department of Psychology, Stanford University \\ Palo Alto, CA 94301 USA \AND {\large \bf George~Kachergis (george.kachergis@gmail.com)} \\ \\ Department of Psychology, Stanford University \\ Palo Alto, CA 94301 USA \AND {\large \bf Michael C.~Frank (mcfrank@stanford.edu)} \\ \\ Department of Psychology, Stanford University \\ Palo Alto, CA 94301 USA}
+
+\begin{document}
+
+\maketitle
+
+\begin{abstract}
 Early parenting practices play an important role in shaping the future
-    outcomes of young children [@Hart1995; @Heckman2006]. 
-    In particular, high quality early interactions and early language input appear to 
-    facilitate more effective language learning and higher levels of school performance. 
-    The rise in electronic parenting applications ("apps") holds the promise of delivering 
-    low-cost, positive interventions on parenting style to a variety of different populations. 
-    Of special interest are the parents of very young children, who are often difficult to reach in other ways. 
-    Yet little is known about the effects of communicating to parents through app-based interventions.
-    MTLD, types and tokens, joint attention, proportion of nouns/verbs/adjectives, 
-    affect, concreteness, mean length of utterance...
+outcomes of young children (Hart \& Risley, 1995; Heckman, 2006). In
+particular, high quality early interactions and early language input
+appear to facilitate more effective language learning and higher levels
+of school performance. The rise in electronic parenting applications
+(``apps'') holds the promise of delivering low-cost, positive
+interventions on parenting style to a variety of different populations.
+Of special interest are the parents of very young children, who are
+often difficult to reach in other ways. Yet little is known about the
+effects of communicating to parents through app-based interventions.
+MTLD, types and tokens, joint attention, proportion of
+nouns/verbs/adjectives, affect, concreteness, mean length of
+utterance\ldots{}
 
-keywords: >
+\textbf{Keywords:}
 digital parenting advice; joint action; lexical diversity; guided play;
+\end{abstract}
 
-output: cogsci2016::cogsci_paper
-#final-submission: \cogscifinalcopy
----
+\section{Introduction}\label{introduction}
 
-```{r global_options, include=FALSE}
-knitr::opts_chunk$set(fig.width=3, fig.height=3, fig.crop = F, 
-                      fig.pos = "tb", fig.path='figs/',
-                      echo=F, warning=F, cache=F, 
-                      message=F, sanitize = T)
-```
+\begin{itemize}
+\tightlist
+\item
+  children learn through play -- physics, object features
+\end{itemize}
 
-```{r, libraries}
-library(png)
-library(grid)
-library(ggplot2)
-library(xtable)
-```
+\subsection{Guided Play Scaffolds
+Learning}\label{guided-play-scaffolds-learning}
 
-# Introduction
+\begin{itemize}
+\tightlist
+\item
+  guided play activities can scaffold children's language and reasoning
+\end{itemize}
 
-- children learn through play -- physics, object features
+\subsection{Improving Parenting Practices and Language
+Use}\label{improving-parenting-practices-and-language-use}
 
-## Guided Play Scaffolds Learning
-- guided play activities can scaffold children's language and reasoning
+\begin{itemize}
+\tightlist
+\item
+  early interventions on parenting practices can help children's
+  outcomes
+\end{itemize}
 
-## Improving Parenting Practices and Language Use
-- early interventions on parenting practices can help children's outcomes
+\subsection{Effectiveness of Digital
+Delivery}\label{effectiveness-of-digital-delivery}
 
-## Effectiveness of Digital Delivery
-apps are an easy way to deliver curated, age-appropriate parenting advice — but can we measure an influence on parent's language? and do the interventions lead to children paying more attention?
+apps are an easy way to deliver curated, age-appropriate parenting
+advice --- but can we measure an influence on parent's language? and do
+the interventions lead to children paying more attention?
 
-The quality of parent-child interactions can be measured by both the social engagement of parents (e.g., joint attention to objects in the environment) and the quality of language (e.g., vocabulary diversity).
-Although digitally-delivered activities are designed to promote learning and cognitive development, it is unclear how they might affect these dimensions of parent-child interactions. 
-How does digital scaffolding of activities affect the social and linguistic characteristics of parents' speech to their children?
+The quality of parent-child interactions can be measured by both the
+social engagement of parents (e.g., joint attention to objects in the
+environment) and the quality of language (e.g., vocabulary diversity).
+Although digitally-delivered activities are designed to promote learning
+and cognitive development, it is unclear how they might affect these
+dimensions of parent-child interactions. How does digital scaffolding of
+activities affect the social and linguistic characteristics of parents'
+speech to their children?
 
-# Experiment 1
+\section{Experiment 1}\label{experiment-1}
 
-In Experiment 1, we invited parents of 6- to 24-month-old infants visiting the Children's Discovery Museum in San Jose to complete activities from the Kinedu app. 
-Parents were randomly assigned to the video group or the control group; parents in the video group watched a video from the Kinedu app (matched to their child's age), and then performed the activity with their child using the props from the video.
-Parents in the control group did not watch a Kinedu video, instead they were given the same props and were told to play with their infants as they would at home. 
-We found that compared to the control group, parents who watched a Kinedu video spoke more words overall, but had lower lexical diversity. 
-They also made more bids for joint attention with their infants, although these bids did not result in more episodes of joint attention compared to the control group. 
-In summary, following digitally-scaffolded activities may cause parents to engage with and speak more to children overall, but speak more repetitively.
+In Experiment 1, we invited parents of 6- to 24-month-old infants
+visiting the Children's Discovery Museum in San Jose to complete
+activities from the Kinedu app. Parents were randomly assigned to the
+video group or the control group; parents in the video group watched a
+video from the Kinedu app (matched to their child's age), and then
+performed the activity with their child using the props from the video.
+Parents in the control group did not watch a Kinedu video, instead they
+were given the same props and were told to play with their infants as
+they would at home. We found that compared to the control group, parents
+who watched a Kinedu video spoke more words overall, but had lower
+lexical diversity. They also made more bids for joint attention with
+their infants, although these bids did not result in more episodes of
+joint attention compared to the control group. In summary, following
+digitally-scaffolded activities may cause parents to engage with and
+speak more to children overall, but speak more repetitively.
 
-## Method
+\subsection{Method}\label{method}
 
-### Participants. 
-60 infants aged 6-24 months and their parents participated in a museum in northern California.
-We included infants who were exposed to English at least 50 percent of the time or who were exposed less but whose participating parent reported that they primarily speak English with their child at home.
-[include specific demo info here?] - good to include now, and we can comment it out if it's too much (the full report/paper will have it)
+\subsubsection{Participants.}\label{participants.}
 
-### Materials.
-Stimuli included videos from a commercial parenting application, Kinedu Inc.
-The videos were designed to show activities parents could perform with their child to foster cognitive and physical development, and were targeted to the child's age and development.
-In each video, an adult and child perform the activity while a narrator explains the activity and its purpose.
-We selected two videos for each of three age groups in our sample (6-11.9 months, 12-17.9 months, 18-23.94 months).
-More information about the specific videos is available in the Appendix.
-Participants were also given a set of props corresponding to those in the video they watched, so that they could complete the activity.
-The props associated with each video are listed in the Appendix.
+60 infants aged 6-24 months and their parents participated in a museum
+in northern California. We included infants who were exposed to English
+at least 50 percent of the time or who were exposed less but whose
+participating parent reported that they primarily speak English with
+their child at home. {[}include specific demo info here?{]} - good to
+include now, and we can comment it out if it's too much (the full
+report/paper will have it)
 
-Participants were randomly assigned to an Activity Video condition or No-Video Control condition.
-Participants in the Activity Video condition were assigned to one of the two videos available for their child's age group.
-The No-Video Control condition was yoked to the Activity Video condition such that for every participant in the Activity Video condition who saw a particular video and received the associated props, a participant in the No-Video Control condition received the same props but did not watch the corresponding video.
-Parents also completed the Parenting Attitudes Questionnaire (PAQ).
-The PAQ measures parents' attitudes about parenting and child development along three dimensions: rules and respect, early learning, and affection and attachment.
+\subsubsection{Materials.}\label{materials.}
 
-## Procedure.
-After providing informed consent, parents in the Activity Video condition watched the assigned video on a laptop with headphones.
-To ensure that parents could give the video their full attention, the experimenter played with the infant with a set of toys (different from the experimental props used in the study) while the video was being played.
-Immediately following the video, each parent-child dyad was provided with the props to complete the activity they had viewed. 
-The toys were placed on a large foam mat, and parents were instructed to sit on the mat with their child and re-create the activity they had viewed for a period of three minutes.
-In the No-Video control condition, after consenting parents were told to play with their child as they would at home with the provided props for a period of three minutes. 
-They were not given any additional instructions about how to use the props.
+Stimuli included videos from a commercial parenting application, Kinedu
+Inc. The videos were designed to show activities parents could perform
+with their child to foster cognitive and physical development, and were
+targeted to the child's age and development. In each video, an adult and
+child perform the activity while a narrator explains the activity and
+its purpose. We selected two videos for each of three age groups in our
+sample (6-11.9 months, 12-17.9 months, 18-23.94 months). More
+information about the specific videos is available in the Appendix.
+Participants were also given a set of props corresponding to those in
+the video they watched, so that they could complete the activity. The
+props associated with each video are listed in the Appendix.
 
-In both conditions, two video cameras were used to record the play session from different angles, and parents were fitted with a wireless audio recorder to record their speech to their child.
-After three minutes of play had elapsed, parents were told they could stop playing and cameras and audio were turned off.
-Parents were then asked to complete the PAQ before being debriefed.
+Participants were randomly assigned to an Activity Video condition or
+No-Video Control condition. Participants in the Activity Video condition
+were assigned to one of the two videos available for their child's age
+group. The No-Video Control condition was yoked to the Activity Video
+condition such that for every participant in the Activity Video
+condition who saw a particular video and received the associated props,
+a participant in the No-Video Control condition received the same props
+but did not watch the corresponding video. Parents also completed the
+Parenting Attitudes Questionnaire (PAQ). The PAQ measures parents'
+attitudes about parenting and child development along three dimensions:
+rules and respect, early learning, and affection and attachment.
 
-### Joint Attention Coding Procedure.
-Video of each session was coded for episodes of joint attention using Datavyu software. 
-The video taken at floor level was coded by default, but the other video was referred to if the participants were not visible or if there was a technological error with the first camera.
-For each participant we coded for episodes of coordinated joint attention, episodes of passive joint attention, and parental bids for joint attention.
-We defined parental bids for joint attention as any attempt to initiate joint attention (i.e label, point, or otherwise draw attention to an object) that does not result in passive or coordinated joint attention.
-If more than 3 seconds elapsed between bids, they were coded as separate attempts. 
-An episode of joint attention was considered passive if both participants visually focused on an object for a minimum of 3 seconds but the child did not acknowledge the parent. 
-If either participant looked away from the object for less than 3 seconds and then returned to the same object it was considered part of the same period of joint attention. 
-Episodes joint attention were considered coordinated if  both participants visually focused on an object for a minimum of 3 seconds and at some point in the interaction the child indicated awareness of interaction with some overt behavior toward the parent.
-This could be looks to the parent's face, gestures, vocalizations, or turn-taking. 
-If either participant looked away for less than 3 seconds and then returned to the same object, it was coded as part of the same period of joint attention. 
-A second coder independently coded a third of the videos (i.e., 20 of the 60 videos, approximately equally distributed across ages) to establish reliability. % report reliability
+\subsection{Procedure.}\label{procedure.}
 
-# Results
+After providing informed consent, parents in the Activity Video
+condition watched the assigned video on a laptop with headphones. To
+ensure that parents could give the video their full attention, the
+experimenter played with the infant with a set of toys (different from
+the experimental props used in the study) while the video was being
+played. Immediately following the video, each parent-child dyad was
+provided with the props to complete the activity they had viewed. The
+toys were placed on a large foam mat, and parents were instructed to sit
+on the mat with their child and re-create the activity they had viewed
+for a period of three minutes. In the No-Video control condition, after
+consenting parents were told to play with their child as they would at
+home with the provided props for a period of three minutes. They were
+not given any additional instructions about how to use the props.
 
-## Lexical Diversity
+In both conditions, two video cameras were used to record the play
+session from different angles, and parents were fitted with a wireless
+audio recorder to record their speech to their child. After three
+minutes of play had elapsed, parents were told they could stop playing
+and cameras and audio were turned off. Parents were then asked to
+complete the PAQ before being debriefed.
 
-## Joint Attention
+\subsubsection{Joint Attention Coding
+Procedure.}\label{joint-attention-coding-procedure.}
 
-# Experiment 2
+Video of each session was coded for episodes of joint attention using
+Datavyu software. The video taken at floor level was coded by default,
+but the other video was referred to if the participants were not visible
+or if there was a technological error with the first camera. For each
+participant we coded for episodes of coordinated joint attention,
+episodes of passive joint attention, and parental bids for joint
+attention. We defined parental bids for joint attention as any attempt
+to initiate joint attention (i.e label, point, or otherwise draw
+attention to an object) that does not result in passive or coordinated
+joint attention. If more than 3 seconds elapsed between bids, they were
+coded as separate attempts. An episode of joint attention was considered
+passive if both participants visually focused on an object for a minimum
+of 3 seconds but the child did not acknowledge the parent. If either
+participant looked away from the object for less than 3 seconds and then
+returned to the same object it was considered part of the same period of
+joint attention. Episodes joint attention were considered coordinated if
+both participants visually focused on an object for a minimum of 3
+seconds and at some point in the interaction the child indicated
+awareness of interaction with some overt behavior toward the parent.
+This could be looks to the parent's face, gestures, vocalizations, or
+turn-taking. If either participant looked away for less than 3 seconds
+and then returned to the same object, it was coded as part of the same
+period of joint attention. A second coder independently coded a third of
+the videos (i.e., 20 of the 60 videos, approximately equally distributed
+across ages) to establish reliability. \% report reliability
 
-In Experiment 2 we attempt to replicate the findings from Experiment 1 with a restricted number of preregistered predictions. 
-We will additionally include a second control condition, in which the same activities are described in written form, rather than being demonstrated in video. 
-This manipulation will help determine what the contribution of the video demonstration is in producing the observed effects on parent-child interactions.
+\section{Results}\label{results}
 
-## Method
+\subsection{Lexical Diversity}\label{lexical-diversity}
 
-### Participants. 
-84 infants aged 12-24 months and their parents participated in the same museum as Experiment 1.
-We included infants who were exposed to English at least 75 percent of the time or who were exposed less but whose participating parent reported that they primarily speak English with their child at home.
-[specific demo info]
+\subsection{Joint Attention}\label{joint-attention}
 
-### Materials. 
-The design of Experiment 2 was similar to that of Experiment 1, except that instead of a No-Video control condition, parents instead watched a video that was generally related to child development research, but did not give any specific instructions about how to interact with infants or children.
-This was to control for the possibility that differences in language output and joint attention in Experiment 1 could be due to simply cuing parents to think about infants' learning and cognitive development.
-The videos presented in the Control Video condition were media clips (available on YouTube) of developmental psychologists explaining their research interleaved with footage of infants or toddlers engaged in developmental research studies.
-Thus, the content of the videos superficially matched those in the Activity Video condition, but did not suggest any particular activities.
-The videos were trimmed to approximately match the average video length in the Activity Video condition (2 minutes ??).
+\section{Experiment 2}\label{experiment-2}
 
-### Procedure. 
-The procedure for Experiment 2 matched that of Experiment 1, except that parents in the Control Video condition watched a control video before the play session. 
-Consistent with the No-Video control condition in Experiment 1, parents in the Control Video condition were told to play with their child as they would at home, and were not given additional instructions.
+In Experiment 2 we attempt to replicate the findings from Experiment 1
+with a restricted number of preregistered predictions. We will
+additionally include a second control condition, in which the same
+activities are described in written form, rather than being demonstrated
+in video. This manipulation will help determine what the contribution of
+the video demonstration is in producing the observed effects on
+parent-child interactions.
 
-# Results
+\subsection{Method}\label{method-1}
 
-## Lexical Diversity
+\subsubsection{Participants. 84 infants aged 12-24 months and their
+parents participated in the same museum as Experiment 1. We included
+infants who were exposed to English at least 75 percent of the time or
+who were exposed less but whose participating parent reported that they
+primarily speak English with their child at home. {[}specific demo
+info{]}}\label{participants.-84-infants-aged-12-24-months-and-their-parents-participated-in-the-same-museum-as-experiment-1.-we-included-infants-who-were-exposed-to-english-at-least-75-percent-of-the-time-or-who-were-exposed-less-but-whose-participating-parent-reported-that-they-primarily-speak-english-with-their-child-at-home.-specific-demo-info}
 
-## Joint Attention
+\subsubsection{Materials.}\label{materials.-1}
 
-# Discussion
+The design of Experiment 2 was similar to that of Experiment 1, except
+that instead of a No-Video control condition, parents instead watched a
+video that was generally related to child development research, but did
+not give any specific instructions about how to interact with infants or
+children. This was to control for the possibility that differences in
+language output and joint attention in Experiment 1 could be due to
+simply cuing parents to think about infants' learning and cognitive
+development. The videos presented in the Control Video condition were
+media clips (available on YouTube) of developmental psychologists
+explaining their research interleaved with footage of infants or
+toddlers engaged in developmental research studies. Thus, the content of
+the videos superficially matched those in the Activity Video condition,
+but did not suggest any particular activities. The videos were trimmed
+to approximately match the average video length in the Activity Video
+condition (2 minutes ??).
 
-For more information on citations in RMarkdown, see **[here](http://rmarkdown.rstudio.com/authoring_bibliographies_and_citations.html#citations).**
+\subsubsection{Procedure.}\label{procedure.-1}
 
-## Footnotes
+The procedure for Experiment 2 matched that of Experiment 1, except that
+parents in the Control Video condition watched a control video before
+the play session. Consistent with the No-Video control condition in
+Experiment 1, parents in the Control Video condition were told to play
+with their child as they would at home, and were not given additional
+instructions.
+
+\section{Results}\label{results-1}
+
+\subsection{Lexical Diversity}\label{lexical-diversity-1}
+
+\subsection{Joint Attention}\label{joint-attention-1}
+
+\section{Discussion}\label{discussion}
+
+For more information on citations in RMarkdown, see
+\textbf{\href{http://rmarkdown.rstudio.com/authoring_bibliographies_and_citations.html\#citations}{here}.}
+
+\subsection{Footnotes}\label{footnotes}
 
@@
 bottom of the page on which they appear. Precede the footnote with a
-horizontal rule.\footnote{Sample of the second footnote.} You can also use 
-markdown formatting to include footnotes using this syntax [^1].
+horizontal rule.\footnote{Sample of the second footnote.} You can also
+use markdown formatting to include footnotes using this
+syntax.\footnote{Sample of a markdown footnote.}
 
-[^1]: Sample of a markdown footnote.
+\subsection{Two-column images}\label{two-column-images}
 
-## Two-column images
+You can read local images using png package for example and plot it like
+a regular plot using grid.raster from the grid package. With this method
+you have full control of the size of your image. \textbf{Note: Image
+must be in .png file format for the readPNG function to work.}
 
-You can read local images using png package for example and plot 
-it like a regular plot using grid.raster from the grid package. 
-With this method you have full control of the size of your image. **Note: Image must be in .png file format for the readPNG function to work.**
+You might want to display a wide figure across both columns. To do this,
+you change the \texttt{fig.env} chunk option to \texttt{figure*}. To
+align the image in the center of the page, set \texttt{fig.align} option
+to \texttt{center}. To format the width of your caption text, you set
+the \texttt{num.cols.cap} option to \texttt{2}.
 
-You might want to display a wide figure across both columns.
-To do this, you change the `fig.env` chunk option to `figure*`.
-To align the image in the center of the page, set `fig.align` option to `center`.
-To format the width of your caption text, you set the `num.cols.cap` option to `2`.
+\begin{CodeChunk}
+\begin{figure*}[h]
 
-```{r 2-col-image, fig.env = "figure*", fig.pos = "h", fig.width=4, fig.height=2, fig.align = "center", set.cap.width=T, num.cols.cap=2, fig.cap = "This image spans both columns.
-And the caption text is limited to 0.8 of the width of the document."}
-img <- png::readPNG("figs/walrus.png")
-grid::grid.raster(img)
-```
+{\centering \includegraphics{figs/2-col-image-1}
 
-## One-column images
+}
 
-Single column is the default option, but if you want set it explicitly, set `fig.env` to `figure`. Notice that the `num.cols` option for the caption width is set to `1`.
+\caption[This image spans both columns]{This image spans both columns. And the caption text is limited to 0.8 of the width of the document.}\label{fig:2-col-image}
+\end{figure*}
+\end{CodeChunk}
 
-```{r image, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=2, fig.height=2, set.cap.width=T, num.cols.cap=1, fig.cap = "One column image."}
-img <- png::readPNG("figs/lab_logo_stanford.png")
-grid::grid.raster(img)
-```
+\subsection{One-column images}\label{one-column-images}
 
-## R Plots
+Single column is the default option, but if you want set it explicitly,
+set \texttt{fig.env} to \texttt{figure}. Notice that the
+\texttt{num.cols} option for the caption width is set to \texttt{1}.
 
-You can use R chunks directly to plot graphs. And you can use latex floats in the
-fig.pos chunk option to have more control over the location of your plot on the page.
-For more information on latex placement specifiers see **[here](https://en.wikibooks.org/wiki/LaTeX/Floats,_Figures_and_Captions)**
+\begin{CodeChunk}
+\begin{figure}[H]
 
-```{r plot, fig.env="figure", fig.pos = "H", fig.align = "center", fig.width=2, fig.height=2, fig.cap = "R plot" }
-x <- 0:100
-y <- 2 * (x + rnorm(length(x), sd = 3) + 3)
+{\centering \includegraphics{figs/image-1}
 
-ggplot2::ggplot(data = data.frame(x, y), 
-       aes(x = x, y = y)) + 
-  geom_point() + 
-  geom_smooth(method = "lm")
-```
+}
 
-## Tables
+\caption[One column image]{One column image.}\label{fig:image}
+\end{figure}
+\end{CodeChunk}
 
-Number tables consecutively; place the table number and title (in
-10 point) above the table with one line space above the caption and
-one line space below it, as in Table 1. You may float
-tables to the top or bottom of a column, set wide tables across both
-columns.
+\subsection{R Plots}\label{r-plots}
+
+You can use R chunks directly to plot graphs. And you can use latex
+floats in the fig.pos chunk option to have more control over the
+location of your plot on the page. For more information on latex
+placement specifiers see
+\textbf{\href{https://en.wikibooks.org/wiki/LaTeX/Floats,_Figures_and_Captions}{here}}
+
+\begin{CodeChunk}
+\begin{figure}[H]
+
+{\centering \includegraphics{figs/plot-1}
+
+}
+
+\caption[R plot]{R plot}\label{fig:plot}
+\end{figure}
+\end{CodeChunk}
+
+\subsection{Tables}\label{tables}
+
+Number tables consecutively; place the table number and title (in 10
+point) above the table with one line space above the caption and one
+line space below it, as in Table 1. You may float tables to the top or
+bottom of a column, set wide tables across both columns.
 
@@
 
-```{r xtable, results="asis"}
-n <- 100
-x <- rnorm(n)
-y <- 2*x + rnorm(n)
-out <- lm(y ~ x)
+\begin{table}[H]
+\centering
+\begin{tabular}{rrrrr}
+  \hline
+ & Estimate & Std. Error & t value & Pr($>$$|$t$|$) \\ 
+  \hline
+(Intercept) & 0.04 & 0.11 & 0.3 & 0.74 \\ 
+  x & 2.05 & 0.11 & 18.0 & 0.00 \\ 
+   \hline
+\end{tabular}
+\caption{This table prints across one column.} 
+\end{table}
 
-tab1 <- xtable::xtable(summary(out)$coef, digits=c(0, 2, 2, 1, 2), 
-                      caption = "This table prints across one column.")
-
-print(tab1, type="latex", comment = F, table.placement = "H")
-```
-
-# Acknowledgements
+\section{Acknowledgements}\label{acknowledgements}
 
@@
 
-# References
+\section{References}\label{references}
 
-```{r}
-# References will be generated automatically by Pandoc and included here.
-# The following code is some latex to format the bibliography. Do not remove it.
-```
+\setlength{\parindent}{-0.1in} \setlength{\leftskip}{0.125in} \noindent
 
-\setlength{\parindent}{-0.1in} 
-\setlength{\leftskip}{0.125in}
-\noindent
+\hypertarget{refs}{}
+\hypertarget{ref-Hart1995}{}
+Hart, B., \& Risley, T. R. (1995). \emph{Meaningful differences in the
+everyday experience of young american children}. Baltimore, MD: Brookes.
+
+\hypertarget{ref-Heckman2006}{}
+Heckman, J. J. (2006). Skill formation and the economics of investing in
+disadvantaged children. \emph{Science}, \emph{312}(5782), 1900--1902.
+\url{http://doi.org/10.1126/science.1128898}
+
+\bibliographystyle{apacite}
+
+\end{document}

### 2019-01-09 paper/cogsci2019/cogsci2019.Rmd
saving smaller graphs, writing

@@
 
+The data was analyzed according to our preregistration. [link]
+
 ## Lexical Diversity
+
+- calculate Type/Token Ratio (TTR)
+
+Fig 1 - TTR, maybe also Total Tokens and Total Types (if subfigures fit)
+(otherwise a table with mean and SD of tokens, types, and TTR)
+However, note that TTR is a measure that is correlated with the length of a text. ... 
+According to [@Jarvis2010], MTLD is a better measure of lexical diversity.
 

### 2019-01-09 parenting_obs_e1/parenting_obs_lexdiv.Rmd
saving smaller graphs, writing

--- 2017-07-07 parenting_obs_lexdiv.Rmd
@@
 title: "Parenting observation lexical diversity"
-author: "Emily"
+author: "Vivian, George, and Emily"
 date: "`r Sys.Date()`"
@@
 knitr::opts_chunk$set(fig.width=8, fig.height=5, 
-                      echo=TRUE, warning=FALSE, message=FALSE, cache=FALSE)
+                      echo=TRUE, warning=FALSE, message=FALSE, cache = TRUE)
 suppressPackageStartupMessages(c("dplyr","langcog","tidyr","ggplot2","lme4"))
@@
 ```{r}
-data <- read.csv("data.csv", header =TRUE)
-dem <- read.csv("parenting_proj_emilyhembacher_demo2016.csv", header =TRUE)
+data <- read.csv("lexdiv_data.csv", header =TRUE)
+#dem <- read.csv("parenting_proj_emilyhembacher_demo2016.csv", header =TRUE) # anonymized demographics data
+#dem_anon = dem[,c("SID","age","gender","ethnicity","english","parent_ed","num_lang","Exclude")]
+#write.csv(dem_anon, file="anonymized_demographics_parenting_obs_e1.csv")
+dem <- read.csv("anonymized_demographics_parenting_obs_e1.csv", header=T)
 conditions <- read.csv("joint_attention/conditions.csv")
@@
   group_by(condition) %>%
-  multi_boot_standard(col = "lexdiv")
+  multi_boot_standard(col = "lexdiv") # Type/Token Ratio
+
+lex_means <- d%>%
+  group_by(condition)%>%
+  summarise(mean = mean(lexdiv))
+
+lex_sds <- d%>%
+  group_by(condition)%>%
+  summarise(sd = sd(lexdiv))
+
+ms_lex$condition <- factor(ms_lex$condition,
+levels = c("con", "exp"),
+labels = c("Control", "Video"))
 
@@
   xlab("Condition") + 
-  ylab("Lexical Diversity") +
+  ylab("Type/Token Ratio (TTR)") +
   langcog::scale_colour_solarized()  +
   ggthemes::theme_few() 
+ggsave(file="e1_TTR.pdf", width=3, height=3)
 ```
@@
   multi_boot_standard(col = "tokens")
+
+ms_tok$condition <- factor(ms_tok$condition,
+levels = c("con", "exp"),
+labels = c("Control", "Video"))
 
@@
   ggthemes::theme_few() 
+ggsave(file="e1_word_tokens.pdf", width=3, height=3)
 ```
@@
   multi_boot_standard(col = "types")
+
+ms_type$condition <- factor(ms_type$condition,
+levels = c("con", "exp"),
+labels = c("Control", "Video"))
 
@@
   ggthemes::theme_few()
+ggsave(file="e1_word_types.pdf", width=3, height=3)
 ```
@@
 ```{r}
-maximal_mod <- lmer(lexdiv ~ condition *  EL  + condition * AA + condition * RR  + age + gender + parent_ed +
+maximal_mod <- lmer(lexdiv ~ condition  + age + gender + parent_ed +
                            (1| video), 
@@
 summary(maximal_mod)
+
+#get effect size
+
+M1 <- lex_means$mean[1]
+M2 <- lex_means$mean[2]
+SD1 <- lex_sds$sd[1]
+SD2 <- lex_sds$sd[2]
+
+cohens_d <- (M2 - M1)/(sqrt(SD1^2 + SD2^2)/2)
 ```

### 2019-01-09 parenting_obs_e2/Lexical_Diversity_Analysis.Rmd
saving smaller graphs, writing

@@
 ```{r}
-data <- read.csv("MTLD_HDD.csv", header =TRUE)
+data <- read.csv("MTLD_HDD.csv", header =TRUE) # generated by gen_
 # dem <- read.csv("parenting_proj_emilyhembacher_demo2016.csv", header =TRUE)
@@
   langcog::scale_colour_solarized()  +
-  ggthemes::theme_few() + 
-  theme(legend.title = element_text(size=18), 
-        legend.text = element_text(size=16), 
-        axis.text.x  = element_text(vjust=0.5, size=16),
-        axis.title.x = element_text(size=18), 
-        axis.text.y  = element_text(vjust=0.5, size=16),
-        axis.title.y = element_text(size=18))
+  ggthemes::theme_few() 
+ggsave(file="e2_TTR.pdf", width=3, height=3)
 ```

### 2019-01-10 parenting_obs_e1/parenting_obs_lexdiv.Rmd
lexical diversity analyses and figures

@@
 ---
-title: "Parenting observation lexical diversity"
+title: "Parenting observation lexical diversity - Exp 1"
 author: "Vivian, George, and Emily"
@@
 ```{r}
-data <- read.csv("lexdiv_data.csv", header =TRUE)
+#data <- read.csv("lexdiv_data.csv", header=TRUE) # Emily's TTR calculation
+data <- read.csv("MTLD_HDD.csv", header=TRUE) # Vivian's new TTR, MTLD, and HDD pipeline (generated by get_all_parent_speech.py)
+data$SID = data$sid
+data$sid = NULL
+data$X = NULL
 #dem <- read.csv("parenting_proj_emilyhembacher_demo2016.csv", header =TRUE) # anonymized demographics data
@@
 conditions <- read.csv("joint_attention/conditions.csv")
-load("paq/paq_demo.RData")
+load("paq/paq_demo.RData") # do we use this??
 
@@
   transmute(sid=SID, 
-            types = Type.count, 
-            tokens = Token.count, 
-            lexdiv = Lexical.diversity, 
-            condition= Condition, 
+            types = types,
+            tokens = tokens, 
+            TTR = TTR, 
+            MTLD = MTLD,
+            condition = Condition, 
             video = Video, 
@@
 ##Lexical Diversity
+### TTR
 ```{r}
@@
   group_by(condition) %>%
-  multi_boot_standard(col = "lexdiv") # Type/Token Ratio
+  multi_boot_standard(col = "TTR") # Type/Token Ratio
 
@@
   group_by(condition)%>%
-  summarise(mean = mean(lexdiv))
+  summarise(mean = mean(TTR), sd = sd(TTR))
 
-lex_sds <- d%>%
-  group_by(condition)%>%
-  summarise(sd = sd(lexdiv))
+# report table with lex_means lex_sds
 
@@
   ggthemes::theme_few() 
-ggsave(file="e1_TTR.pdf", width=3, height=3)
+ggsave(file="figs/e1_TTR.pdf", width=3, height=3)
+```
+
+###MTLD
+```{r}
+ms_lex_mtld <- d %>%
+  group_by(condition) %>%
+  multi_boot_standard(col = "MTLD")
+
+lex_means <- d%>%
+  group_by(condition)%>%
+  summarise(mean = mean(MTLD), sd = sd(MTLD))
+
+# report table with lex_means lex_sds
+
+ms_lex_mtld$condition <- factor(ms_lex_mtld$condition,
+levels = c("con", "exp"),
+labels = c("Control", "Video"))
+
+ggplot(ms_lex_mtld, aes(x = condition, y = mean, fill = condition)) + 
+  geom_bar(stat="identity") + 
+  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
+             position = position_dodge(width = .9))+
+  xlab("Condition") + 
+  ylab("MTLD") +
+  langcog::scale_colour_solarized()  +
+  ggthemes::theme_few() 
+ggsave(file="figs/e1_MTLD.pdf", width=3, height=3)
 ```
@@
   ggthemes::theme_few() 
-ggsave(file="e1_word_tokens.pdf", width=3, height=3)
+ggsave(file="figs/e1_word_tokens.pdf", width=3, height=3)
 ```
@@
   ggthemes::theme_few()
-ggsave(file="e1_word_types.pdf", width=3, height=3)
+ggsave(file="figs/e1_word_types.pdf", width=3, height=3)
 ```

### 2019-01-10 parenting_obs_e2/Lexical_Diversity_Analysis.Rmd
lexical diversity analyses and figures

@@
 ---
-title: "Compare Lexical Diversity Measurements: MTLD and HD-D
-author: "Vivian"
+title: "Parenting Observation Experiment 2 Lexical Diversity Analysis"
+author: "Vivian & George"
 date: "`r Sys.Date()`"
@@
 ```{r}
-data <- read.csv("MTLD_HDD.csv", header =TRUE) # generated by gen_
+data <- read.csv("MTLD_HDD.csv", header =TRUE) # generated by get_all_parent_speech.py
 # dem <- read.csv("parenting_proj_emilyhembacher_demo2016.csv", header =TRUE)
@@
 ##TTR
-```{r}
+```{r echo=FALSE}
 ms_lex <- d %>%
@@
 
-lex_means <- d%>%
+lex_mean_TTR <- d%>%
   group_by(condition)%>%
-  summarise(mean = mean(TTR))
-
-lex_sds <- d%>%
-  group_by(condition)%>%
-  summarise(sd = sd(TTR))
+  summarise(mean = mean(TTR), sd = sd(TTR))
 
@@
 levels = c("con", "exp"),
-labels = c("control", "video"))
+labels = c("Control", "Video"))
 
@@
   ggthemes::theme_few() 
-ggsave(file="e2_TTR.pdf", width=3, height=3)
+ggsave(file="figs/e2_TTR.pdf", width=3, height=3)
 ```
 ## MTLD
-```{r}
+```{r echo=FALSE}
 ms_lex <- d %>%
@@
 
-lex_means <- d%>%
+lex_mean_MTLD <- d%>%
   group_by(condition)%>%
-  summarise(mean = mean(MTLD))
-
-lex_sds <- d%>%
-  group_by(condition)%>%
-  summarise(sd = sd(MTLD))
+  summarise(mean = mean(MTLD), sd=sd(MTLD))
 
@@
   langcog::scale_colour_solarized()  +
-  ggthemes::theme_few() + 
-  theme(legend.title = element_text(size=18), 
-        legend.text = element_text(size=16), 
-        axis.text.x  = element_text(vjust=0.5, size=16),
-        axis.title.x = element_text(size=18), 
-        axis.text.y  = element_text(vjust=0.5, size=16),
-        axis.title.y = element_text(size=18))
+  ggthemes::theme_few() 
+ggsave(file="figs/e2_MTLD.pdf", width=3, height=3)
 ```
-## HDD
-```{r}
+## HD-D
+```{r echo=FALSE}
 ms_lex <- d %>%
@@
   langcog::scale_colour_solarized()  +
-  ggthemes::theme_few() + 
-  theme(legend.title = element_text(size=18), 
-        legend.text = element_text(size=16), 
-        axis.text.x  = element_text(vjust=0.5, size=16),
-        axis.title.x = element_text(size=18), 
-        axis.text.y  = element_text(vjust=0.5, size=16),
-        axis.title.y = element_text(size=18))
+  ggthemes::theme_few()
+ggsave(file="figs/e2_HDD.pdf", width=3, height=3)
 ```
 ##Word Tokens
-```{r}
+```{r echo=FALSE}
 ms_tok <- d %>%
@@
   langcog::scale_colour_solarized()  +
-  ggthemes::theme_few() + 
-  theme(legend.title = element_text(size=18), 
-        legend.text = element_text(size=16), 
-        axis.text.x  = element_text(vjust=0.5, size=16),
-        axis.title.x = element_text(size=18), 
-        axis.text.y  = element_text(vjust=0.5, size=16),
-        axis.title.y = element_text(size=18))
+  ggthemes::theme_few() 
+ggsave(file="figs/e2_tokens.pdf", width=3, height=3)
 ```
@@
 ##Word Types
-```{r}
+```{r echo=FALSE}
 ms_type <- d %>%
@@
   langcog::scale_colour_solarized()  +
-  ggthemes::theme_few() + 
-  theme(legend.title = element_text(size=18), 
-        legend.text = element_text(size=16), 
-        axis.text.x  = element_text(vjust=0.5, size=16),
-        axis.title.x = element_text(size=18), 
-        axis.text.y  = element_text(vjust=0.5, size=16),
-        axis.title.y = element_text(size=18))
+  ggthemes::theme_few() 
+ggsave(file="figs/e2_types.pdf", width=3, height=3)
 ```
 
-##Sentences Length
-```{r}
+##Sentence Length
+```{r echo=FALSE}
 ms_length <- d %>%
@@
   langcog::scale_colour_solarized()  +
-  ggthemes::theme_few() + 
-  theme(legend.title = element_text(size=18), 
-        legend.text = element_text(size=16), 
-        axis.text.x  = element_text(vjust=0.5, size=16),
-        axis.title.x = element_text(size=18), 
-        axis.text.y  = element_text(vjust=0.5, size=16),
-        axis.title.y = element_text(size=18))
+  ggthemes::theme_few()
+ggsave(file="figs/e2_sentence_length.pdf", width=3, height=3)
 ```
-##Sentences Length by videos
-```{r}
+
+###Sentence Length by videos
+
+```{r echo=FALSE}
 ms_length <- d %>%
@@
 ```
-##Sentences Length by age
-```{r}
+
+###Sentence Length by age
+(Maybe do a scatterplot with continuous scatterplot)
+
+```{r echo=FALSE}
 ms_length <- d %>%
@@
 levels = c("1", "2"),
-labels = c("12-18month", "18-24month"))
+labels = c("12-18", "18-24"))
 
@@
              position = position_dodge(width = .9))+
-  xlab("Age") + 
+  xlab("Age (months)") + 
   ylab("Average Sentence Length") +
@@
 
-cor(d$ttr, d$mtld)
-cor(d$ttr, d$hdd)
-cor(d$mtld, d$hdd)
+round(cor(d[,c("TTR","MTLD","HDD","len_sentence")]), 3)
 
@@
 HD-D and TTR r = -.051 (N = 1584). 
-In our result, MTLD and HD-D are the best correlated, although r = .621; MTLD and ttr has r = .543, which is higher than what M-J2010 reported.
+In our results, MTLD and HD-D have the highest correlation (r = .714). Meanwhile, MTLD and TTR has r = .270, a bit lower than what M-J2010 reported. TTR and HDD are also modestly correlated (r = .426)
 
-All of the measure show that control group has higher lexical diversity than experimental group, with MTLD showing the biggest contrast and HD-D smallest.
+All of the measures suggest that the control group has higher lexical diversity than experimental group, with HD-D showing the biggest contrast and MTLD the smallest.

### 2019-01-10 parenting_obs_e1/get_all_parent_speech.py

@@ -31,7 +31,7 @@ def clean(string):
 col_names = ['sid', 'MTLD', 'HDD', 'types', 'tokens', 'TTR', 'len_sentence']
 results = pd.DataFrame(columns = col_names)
 
-files = os.listdir("trans_out_txt/")
+files = os.listdir("trans_out/")
 try:
     files.remove('.DS_Store')
 except:
@@ -39,7 +39,7 @@ except:
 all_dat = {}
 # print (files)
 for fname in files:
-    folder = "trans_out_txt/"
+    folder = "trans_out/"
     name =  fname
     path = "".join((folder,name))
     fr = open(path, 'r')
@@ -66,7 +66,7 @@ for fname in files:
     all_dat[fname] = text_ready
 
 # call MTLD and HDD functions and calculate
-    id = fname[6:14]
+    id = fname
     print (len(str.split(text_ready)))
     if (len(str.split(text_ready)))>50:
         mtld_value = mtld(text_ready.split())

### 2019-01-11 paper/cogsci2019/cogsci2019.Rmd
adding figs

@@
 However, note that TTR is a measure that is correlated with the length of a text. ... 
-According to [@Jarvis2010], MTLD is a better measure of lexical diversity.
+According to Jarvis2010, MTLD is a better measure of lexical diversity.
 
@@
 
+```{r e2TTR, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=2, fig.height=2, set.cap.width=T, num.cols.cap=1, fig.cap = "How to do subfigures?"}
+img <- png::readPNG("figs/e2_TTR.png")
+grid::grid.raster(img)
+```
+
+```{r e2MTLD, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=2, fig.height=2, set.cap.width=T, num.cols.cap=1, fig.cap = "One column image."}
+img <- png::readPNG("figs/e2_MTLD.png")
+grid::grid.raster(img)
+```
+
 ## Lexical Diversity
@@
 Indicate footnotes with a number\footnote{Sample of the first
-footnote.} in the text. Place the footnotes in 9 point type at the
-bottom of the page on which they appear. Precede the footnote with a
-horizontal rule.\footnote{Sample of the second footnote.} You can also use 
+footnote.} in the text. You can also use 
 markdown formatting to include footnotes using this syntax [^1].
@@
 To format the width of your caption text, you set the `num.cols.cap` option to `2`.
-
-```{r 2-col-image, fig.env = "figure*", fig.pos = "h", fig.width=4, fig.height=2, fig.align = "center", set.cap.width=T, num.cols.cap=2, fig.cap = "This image spans both columns.
-And the caption text is limited to 0.8 of the width of the document."}
-img <- png::readPNG("figs/walrus.png")
-grid::grid.raster(img)
-```
 

### 2019-01-11 paper/cogsci2019/cogsci2019.tex
adding figs

@@
 
+The data was analyzed according to our preregistration. {[}link{]}
+
 \subsection{Lexical Diversity}\label{lexical-diversity}
+
+\begin{itemize}
+\tightlist
+\item
+  calculate Type/Token Ratio (TTR)
+\end{itemize}
+
+Fig 1 - TTR, maybe also Total Tokens and Total Types (if subfigures fit)
+(otherwise a table with mean and SD of tokens, types, and TTR) However,
+note that TTR is a measure that is correlated with the length of a text.
+\ldots{} According to Jarvis2010, MTLD is a better measure of lexical
+diversity.
 
@@
 
-\subsubsection{Participants. 84 infants aged 12-24 months and their
-parents participated in the same museum as Experiment 1. We included
-infants who were exposed to English at least 75 percent of the time or
-who were exposed less but whose participating parent reported that they
-primarily speak English with their child at home. {[}specific demo
-info{]}}\label{participants.-84-infants-aged-12-24-months-and-their-parents-participated-in-the-same-museum-as-experiment-1.-we-included-infants-who-were-exposed-to-english-at-least-75-percent-of-the-time-or-who-were-exposed-less-but-whose-participating-parent-reported-that-they-primarily-speak-english-with-their-child-at-home.-specific-demo-info}
+\subsubsection{Participants.}\label{participants.-1}
+
+84 infants aged 12-24 months and their parents participated in the same
+museum as Experiment 1. We included infants who were exposed to English
+at least 75 percent of the time or who were exposed less but whose
+participating parent reported that they primarily speak English with
+their child at home. {[}specific demo info{]}
 
@@
 \section{Results}\label{results-1}
+
+\begin{CodeChunk}
+\begin{figure}[H]
+
+{\centering \includegraphics{figs/e2TTR-1}
+
+}
+
+\caption[How to do subfigures?]{How to do subfigures?}\label{fig:e2TTR}
+\end{figure}
+\end{CodeChunk}
+
+\begin{CodeChunk}
+\begin{figure}[H]
+
+{\centering \includegraphics{figs/e2MTLD-1}
+
+}
+
+\caption[One column image]{One column image.}\label{fig:e2MTLD}
+\end{figure}
+\end{CodeChunk}
 
@@
 the \texttt{num.cols.cap} option to \texttt{2}.
-
-\begin{CodeChunk}
-\begin{figure*}[h]
-
-{\centering \includegraphics{figs/2-col-image-1}
-
-}
-
-\caption[This image spans both columns]{This image spans both columns. And the caption text is limited to 0.8 of the width of the document.}\label{fig:2-col-image}
-\end{figure*}
-\end{CodeChunk}
 
@@
   \hline
-(Intercept) & 0.04 & 0.11 & 0.3 & 0.74 \\ 
-  x & 2.05 & 0.11 & 18.0 & 0.00 \\ 
+(Intercept) & -0.06 & 0.11 & -0.6 & 0.58 \\ 
+  x & 2.19 & 0.10 & 21.0 & 0.00 \\ 
    \hline

### 2019-01-17 paper/cogsci2019/cogsci2019.Rmd
first draft of intro

@@
 keywords: >
-    digital parenting advice; joint action; lexical diversity; guided play;
+    digital parenting advice; joint attention; lexical diversity; guided play;
 
@@
 - children learn through play -- physics, object features
-
+Children want and need to play a lot: 
+by interacting with other people or physcial objects, they explore, experiment and build up their understandings of how the world functions. 
+Researches have suggested that play is important to learning,
+"allowing children to imitate adult behaviors, practice motor skills, process emotional events, and learn much about their world."(Hirsh,2008)
 ## Guided Play Scaffolds Learning
 - guided play activities can scaffold children's language and reasoning
+What we cannot ignore, however,
+is that children's efforts to explore the world are often "assisted and fostered by others who are more skillful than they are"(Kaye, 1970). 
+With the help of an adult or "expert", children are able to engage with more advanced play and explore the functions of objects more.
+These tutorial interactions have been shown to be a "a crucial feature of infancy and childhood"(Wood, 1970).
+Thus, with the knowledge of both play and tutorial interactions, guided play, "where children actively engage in pleasurable and seemingly spontaneous activities under the direction of adults"(Hirsh,2008),
+have drawn researchers' interest. 
+Weisberg showed that, with preschoolders, guided play scaffolds the environment while still allowing children to maintain a large degree of control, 
+and it outperforms direct-instruction approaches in encouraging a variety of positive academic outcomes (Weisberg,Hirsh&Golinkoff, 2013).
+Massey specifically showed that guided play could facilitate children's vocabulary and comprehensive language development and subsequent literacy skills (Massey, 2013).
 
@@
 - early interventions on parenting practices can help children's outcomes
+Thus, including guided play in parenting practices early on is important and should help with children's later performances.
+Suskind did a parent-directed home-visiting intervention experiment in 2015,
+and found that parents in experimental group have greater knowledge of language development and this effect sustained after the experiment is done. 
+However, more interactive outcomes, like parent word type and token numbers, child word types, conversational turn counts and child vocalization counts, 
+increased during the home-visiting but did not sustain after four months of intervention [there are more detailed sustainibility differences of these measure.
+should I make it more clear?] (Suskind, 2015).
+The fact that changes did not sustain could be due to the intervention itself, 
+or could merely be that home-visiting is not sustainable enough for parents to easily and constantly get parenting advice.
 
 ## Effectiveness of Digital Delivery
-apps are an easy way to deliver curated, age-appropriate parenting advice — but can we measure an influence on parent's language? and do the interventions lead to children paying more attention?
+-apps are an easy way to deliver curated, age-appropriate parenting advice — but can we measure an influence on parent's language? and do the interventions lead to children paying more attention?
+
+Digitally-delivered methods could address some logistic barriers to face-to-face delivery methods. 
+Bretenstein reviewed 11 studies on them and showed good promise for the efficacy of interventions using digitally-delivered methods. 
+However, the parent and child outcomes assessed in the review (e.g.infant positive behaviors, satisfaction, emotional symptoms etc.) did not address the nature or quality of parent-infant interactions at a detailed level,
+like if the interventions lead to children paying more attention, or vocabulary changes in parents' language usages. 
+Thus, we want to conduct this experiment to explore if and how digital scaffolding of activities affect the social and linguistic characteristics of parent-child ineractions.
 

### 2019-01-24 paper/cogsci2019/cogsci2019.Rmd
rewriting intro

@@
 
-- children learn through play -- physics, object features
-Children want and need to play a lot: 
-by interacting with other people or physcial objects, they explore, experiment and build up their understandings of how the world functions. 
-Researches have suggested that play is important to learning,
-"allowing children to imitate adult behaviors, practice motor skills, process emotional events, and learn much about their world."(Hirsh,2008)
+Children spend a large portion of their waking time at play in their environment.
+Playing with objects may allow them to discover hidden features, as well as to build a causal understanding of how the objects interact. 
+Beyond learning object features, the laws of physics, and causal relationships (CITE), during play children practice motor skills that help them effectively navigate their world (Hirsh, 2008).
+Social play can help children learn about human relationships, both through imitation of adult behaviors and by experiencing and learning to process emotional events (Hirsh, 2008).
+
 ## Guided Play Scaffolds Learning
-- guided play activities can scaffold children's language and reasoning
-What we cannot ignore, however,
-is that children's efforts to explore the world are often "assisted and fostered by others who are more skillful than they are"(Kaye, 1970). 
-With the help of an adult or "expert", children are able to engage with more advanced play and explore the functions of objects more.
-These tutorial interactions have been shown to be a "a crucial feature of infancy and childhood"(Wood, 1970).
-Thus, with the knowledge of both play and tutorial interactions, guided play, "where children actively engage in pleasurable and seemingly spontaneous activities under the direction of adults"(Hirsh,2008),
+Children's early play behaviors are often assisted by more skilled and knowledgeable play partners such as their caregivers and older siblings (Kaye, 1970). 
+Under such expert guidance, children are encouraged and motivated to engage in more advanced play, undertaking explorations that push the boundaries of what they would be able to do unaided (Vygotsky, 197X).
+These tutorial interactions have been shown to be a "a crucial feature of infancy and childhood" (Wood, 1970).
+Thus, with the knowledge of both play and tutorial interactions, guided play, "where children actively engage in pleasurable and seemingly spontaneous activities under the direction of adults" (Hirsh, 2008),
 have drawn researchers' interest. 
-Weisberg showed that, with preschoolders, guided play scaffolds the environment while still allowing children to maintain a large degree of control, 
-and it outperforms direct-instruction approaches in encouraging a variety of positive academic outcomes (Weisberg,Hirsh&Golinkoff, 2013).
+Weisberg showed that, with preschoolers, guided play scaffolds the environment while still allowing children to maintain a large degree of control, 
+and it outperforms direct-instruction approaches in encouraging a variety of positive academic outcomes (Weisberg, Hirsh and Golinkoff, 2013).
 Massey specifically showed that guided play could facilitate children's vocabulary and comprehensive language development and subsequent literacy skills (Massey, 2013).

### 2019-02-08 paper/cogsci2019/cogsci2019.Rmd
cleaning up, merging analysis into writeup

@@
 Playing with objects may allow them to discover hidden features, as well as to build a causal understanding of how the objects interact. 
-Beyond learning object features, the laws of physics, and causal relationships (CITE), during play children practice motor skills that help them effectively navigate their world (Hirsh, 2008).
-Social play can help children learn about human relationships, both through imitation of adult behaviors and by experiencing and learning to process emotional events (Hirsh, 2008).
+Beyond learning object features, the laws of physics, and causal relationships [e.g., @Schulz2007], during play children practice motor skills that help them effectively navigate their world [@Singer2006].
+Social play can help children learn about human relationships, both through imitation of adult behaviors and by experiencing and learning to process emotional events [@Singer2006].
 
@@
 These tutorial interactions have been shown to be a "a crucial feature of infancy and childhood" (Wood, 1970).
-Thus, with the knowledge of both play and tutorial interactions, guided play, "where children actively engage in pleasurable and seemingly spontaneous activities under the direction of adults" (Hirsh, 2008),
+Thus, with the knowledge of both play and tutorial interactions, guided play, "where children actively engage in pleasurable and seemingly spontaneous activities under the direction of adults" (Hirsh-Pasek, 2008),
 have drawn researchers' interest. 
 Weisberg showed that, with preschoolers, guided play scaffolds the environment while still allowing children to maintain a large degree of control, 
-and it outperforms direct-instruction approaches in encouraging a variety of positive academic outcomes (Weisberg, Hirsh and Golinkoff, 2013).
+and it outperforms direct-instruction approaches in encouraging a variety of positive academic outcomes (Weisberg, Hirsh-Pasek and Golinkoff, 2013).
 Massey specifically showed that guided play could facilitate children's vocabulary and comprehensive language development and subsequent literacy skills (Massey, 2013).
@@
 ## Improving Parenting Practices and Language Use
-- early interventions on parenting practices can help children's outcomes
+(early interventions on parenting practices can help children's outcomes)
 Thus, including guided play in parenting practices early on is important and should help with children's later performances.
@@
 However, more interactive outcomes, like parent word type and token numbers, child word types, conversational turn counts and child vocalization counts, 
-increased during the home-visiting but did not sustain after four months of intervention [there are more detailed sustainibility differences of these measure.
-should I make it more clear?] (Suskind, 2015).
+increased during the home-visiting but did not sustain after four months of intervention (there are more detailed sustainibility differences of these measure.
+should I make it more clear?) [@Suskind2015].
 The fact that changes did not sustain could be due to the intervention itself, 
@@
 ## Effectiveness of Digital Delivery
--apps are an easy way to deliver curated, age-appropriate parenting advice — but can we measure an influence on parent's language? and do the interventions lead to children paying more attention?
+(apps are an easy way to deliver curated, age-appropriate parenting advice — but can we measure an influence on parent's language? and do the interventions lead to children paying more attention?)
 
@@
 ## Method
+
+```{r, echo=F}
+e1path = "../../parenting_obs_e1/"
+load(paste(e1path,"Exp1_cleaned_data.RData",sep=''))
+
+```
 
@@
 
-The data was analyzed according to our preregistration. [link]
+The data was analyzed according to our preregistration: [link](https://osf.io/2bpdf/).
 
@@
 
-- calculate Type/Token Ratio (TTR)
+We first calculated Type/Token Ratio (TTR) for each transcript. ..
 
@@
 However, note that TTR is a measure that is correlated with the length of a text. ... 
-According to Jarvis2010, MTLD is a better measure of lexical diversity.
+MTLD is a better measure of lexical diversity [@McCarthy2010].
 
@@
 ## Method
+
+```{r, echo=F}
+e2path = "../../parenting_obs_e2/"
+#load(paste(e2path,"Exp2_cleaned_data.RData",sep=''))
+e2d <- read.csv(paste(e2path,"MTLD_HDD.csv",sep=''), header=TRUE) 
+```
 
@@
 
-```{r image, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=2, fig.height=2, set.cap.width=T, num.cols.cap=1, fig.cap = "One column image."}
-img <- png::readPNG("figs/lab_logo_stanford.png")
-grid::grid.raster(img)
-```
-
-## R Plots
-
-You can use R chunks directly to plot graphs. And you can use latex floats in the
-fig.pos chunk option to have more control over the location of your plot on the page.
-For more information on latex placement specifiers see **[here](https://en.wikibooks.org/wiki/LaTeX/Floats,_Figures_and_Captions)**
-
-```{r plot, fig.env="figure", fig.pos = "H", fig.align = "center", fig.width=2, fig.height=2, fig.cap = "R plot" }
-x <- 0:100
-y <- 2 * (x + rnorm(length(x), sd = 3) + 3)
-
-ggplot2::ggplot(data = data.frame(x, y), 
-       aes(x = x, y = y)) + 
-  geom_point() + 
-  geom_smooth(method = "lm")
-```
-
 ## Tables
@@
 You can use the xtable function in the xtable package.
-
-```{r xtable, results="asis"}
-n <- 100
-x <- rnorm(n)
-y <- 2*x + rnorm(n)
-out <- lm(y ~ x)
-
-tab1 <- xtable::xtable(summary(out)$coef, digits=c(0, 2, 2, 1, 2), 
-                      caption = "This table prints across one column.")
-
-print(tab1, type="latex", comment = F, table.placement = "H")
-```
-
-# Acknowledgements
-
-Place acknowledgments (including funding information) in a section at
-the end of the paper.
 

### 2019-02-08 paper/cogsci2019/cogsci2019.tex
cleaning up, merging analysis into writeup

@@
 \textbf{Keywords:}
-digital parenting advice; joint action; lexical diversity; guided play;
+digital parenting advice; joint attention; lexical diversity; guided
+play;
 \end{abstract}
@@
 
-\begin{itemize}
-\tightlist
-\item
-  children learn through play -- physics, object features
-\end{itemize}
+Children spend a large portion of their waking time at play in their
+environment. Playing with objects may allow them to discover hidden
+features, as well as to build a causal understanding of how the objects
+interact. Beyond learning object features, the laws of physics, and
+causal relationships (e.g., Schulz \& Bonawitz, 2007), during play
+children practice motor skills that help them effectively navigate their
+world (Singer, Golinkoff, \& Hirsh-Pasek, 2006). Social play can help
+children learn about human relationships, both through imitation of
+adult behaviors and by experiencing and learning to process emotional
+events (Singer et al., 2006).
 
@@
 
-\begin{itemize}
-\tightlist
-\item
-  guided play activities can scaffold children's language and reasoning
-\end{itemize}
+Children's early play behaviors are often assisted by more skilled and
+knowledgeable play partners such as their caregivers and older siblings
+(Kaye, 1970). Under such expert guidance, children are encouraged and
+motivated to engage in more advanced play, undertaking explorations that
+push the boundaries of what they would be able to do unaided (Vygotsky,
+197X). These tutorial interactions have been shown to be a ``a crucial
+feature of infancy and childhood'' (Wood, 1970). Thus, with the
+knowledge of both play and tutorial interactions, guided play, ``where
+children actively engage in pleasurable and seemingly spontaneous
+activities under the direction of adults'' (Hirsh-Pasek, 2008), have
+drawn researchers' interest. Weisberg showed that, with preschoolers,
+guided play scaffolds the environment while still allowing children to
+maintain a large degree of control, and it outperforms
+direct-instruction approaches in encouraging a variety of positive
+academic outcomes (Weisberg, Hirsh-Pasek and Golinkoff, 2013). Massey
+specifically showed that guided play could facilitate children's
+vocabulary and comprehensive language development and subsequent
+literacy skills (Massey, 2013).
 
@@
 
-\begin{itemize}
-\tightlist
-\item
-  early interventions on parenting practices can help children's
-  outcomes
-\end{itemize}
+(early interventions on parenting practices can help children's
+outcomes) Thus, including guided play in parenting practices early on is
+important and should help with children's later performances. Suskind
+did a parent-directed home-visiting intervention experiment in 2015, and
+found that parents in experimental group have greater knowledge of
+language development and this effect sustained after the experiment is
+done. However, more interactive outcomes, like parent word type and
+token numbers, child word types, conversational turn counts and child
+vocalization counts, increased during the home-visiting but did not
+sustain after four months of intervention (there are more detailed
+sustainibility differences of these measure. should I make it more
+clear?) (Susking et al., 2015). The fact that changes did not sustain
+could be due to the intervention itself, or could merely be that
+home-visiting is not sustainable enough for parents to easily and
+constantly get parenting advice.
 
@@
 
-apps are an easy way to deliver curated, age-appropriate parenting
+(apps are an easy way to deliver curated, age-appropriate parenting
 advice --- but can we measure an influence on parent's language? and do
-the interventions lead to children paying more attention?
+the interventions lead to children paying more attention?)
+
+Digitally-delivered methods could address some logistic barriers to
+face-to-face delivery methods. Bretenstein reviewed 11 studies on them
+and showed good promise for the efficacy of interventions using
+digitally-delivered methods. However, the parent and child outcomes
+assessed in the review (e.g.infant positive behaviors, satisfaction,
+emotional symptoms etc.) did not address the nature or quality of
+parent-infant interactions at a detailed level, like if the
+interventions lead to children paying more attention, or vocabulary
+changes in parents' language usages. Thus, we want to conduct this
+experiment to explore if and how digital scaffolding of activities
+affect the social and linguistic characteristics of parent-child
+ineractions.
 
@@
 
-The data was analyzed according to our preregistration. {[}link{]}
+The data was analyzed according to our preregistration:
+\href{https://osf.io/2bpdf/}{link}.
 
@@
 
-\begin{itemize}
-\tightlist
-\item
-  calculate Type/Token Ratio (TTR)
-\end{itemize}
+We first calculated Type/Token Ratio (TTR) for each transcript. ..
 
@@
 note that TTR is a measure that is correlated with the length of a text.
-\ldots{} According to Jarvis2010, MTLD is a better measure of lexical
-diversity.
+\ldots{} MTLD is a better measure of lexical diversity (McCarthy \&
+Jarvis, 2010).
 
@@
 Indicate footnotes with a number\footnote{Sample of the first
-footnote.} in the text. Place the footnotes in 9 point type at the
-bottom of the page on which they appear. Precede the footnote with a
-horizontal rule.\footnote{Sample of the second footnote.} You can also
-use markdown formatting to include footnotes using this
-syntax.\footnote{Sample of a markdown footnote.}
+footnote.} in the text. You can also use markdown formatting to include
+footnotes using this syntax.\footnote{Sample of a markdown footnote.}
 
@@
 
-\begin{CodeChunk}
-\begin{figure}[H]
-
-{\centering \includegraphics{figs/image-1}
-
-}
-
-\caption[One column image]{One column image.}\label{fig:image}
-\end{figure}
-\end{CodeChunk}
-
-\subsection{R Plots}\label{r-plots}
-
-You can use R chunks directly to plot graphs. And you can use latex
-floats in the fig.pos chunk option to have more control over the
-location of your plot on the page. For more information on latex
-placement specifiers see
-\textbf{\href{https://en.wikibooks.org/wiki/LaTeX/Floats,_Figures_and_Captions}{here}}
-
-\begin{CodeChunk}
-\begin{figure}[H]
-
-{\centering \includegraphics{figs/plot-1}
-
-}
-
-\caption[R plot]{R plot}\label{fig:plot}
-\end{figure}
-\end{CodeChunk}
-
 \subsection{Tables}\label{tables}
@@
 You can use the xtable function in the xtable package.
-
-\begin{table}[H]
-\centering
-\begin{tabular}{rrrrr}
-  \hline
- & Estimate & Std. Error & t value & Pr($>$$|$t$|$) \\ 
-  \hline
-(Intercept) & -0.06 & 0.11 & -0.6 & 0.58 \\ 
-  x & 2.19 & 0.10 & 21.0 & 0.00 \\ 
-   \hline
-\end{tabular}
-\caption{This table prints across one column.} 
-\end{table}
-
-\section{Acknowledgements}\label{acknowledgements}
-
-Place acknowledgments (including funding information) in a section at
-the end of the paper.
 
@@
 
+\hypertarget{ref-McCarthy2010}{}
+McCarthy, P. M., \& Jarvis, S. (2010). MTLD, vocd-d, and hd-d: A
+validation study of sophisticated approaches to lexical diversity
+assessment. \emph{Behavior Research Methods}, \emph{42}(2), 381--392.
+
+\hypertarget{ref-Schulz2007}{}
+Schulz, L., \& Bonawitz, E. (2007). Serious fun: Preschoolers engage in
+more exploratory play when evidence is confounded. \emph{Developmental
+Psychology}, \emph{43}(4), 1045--1050.
+
+\hypertarget{ref-Singer2006}{}
+Singer, D. G., Golinkoff, R. M., \& Hirsh-Pasek, K. (Eds.). (2006).
+\emph{Play = learning: How play motivates and enhances children's
+cognitive and social-emotional growth}. New York, NY: Oxford University
+Press.
+
+\hypertarget{ref-Suskind2015}{}
+Susking, D. L., Leffel, K. R., Graf, E., Hernandez, M. W., Gunderson, E.
+A., Sapolich, S. G., \ldots{} Levine, S. C. (2015). A parent-directed
+language intervention for children of low socioeconomic status: A
+randomized controlled pilot study. \emph{Journal of Child Language}.
+\url{http://doi.org/10.1017/S0305000915000033}
+
 \bibliographystyle{apacite}

### 2019-02-08 paper/cogsci2019/cogsci2019.Rmd
exp1 lexical diversity results integrated

@@
 author-information: > 
-    \author{{\large \bf Hanwen Vivian~Zhang (vivian3@stanford.edu)} \\ Department of Psychology, Stanford University \\ Palo Alto, CA 94301 USA
-    \AND {\large \bf George~Kachergis (george.kachergis@gmail.com)} \\ \\ Department of Psychology, Stanford University \\ Palo Alto, CA 94301 USA
-    \AND {\large \bf Michael C.~Frank (mcfrank@stanford.edu)} \\ \\ Department of Psychology, Stanford University \\ Palo Alto, CA 94301 USA}
+    \author{{\large\bf Hanwen Vivian~Zhang} (\texttt{vivian3@stanford.edu}) \\
+    {\large\bf George~Kachergis} (\texttt{george.kachergis@gmail.com}) \\
+    {\large\bf Michael C.~Frank} (\texttt{mcfrank@stanford.edu}) \\ 
+    Department of Psychology, Stanford University \\ 
+    Palo Alto, CA 94301 USA}
 
@@
 output: cogsci2016::cogsci_paper
-#final-submission: \cogscifinalcopy
+final-submission: \cogscifinalcopy
 ---
@@
 
-```{r, libraries}
+```{r libraries, echo=F, include=F}
+suppressPackageStartupMessages(c("dplyr","langcog","tidyr","ggplot2","lme4"))
 library(png)
@@
 library(xtable)
+library(psych)
+library(langcog)
+library(tidyverse)
+library(ggthemes)
+library(lme4)
+library(lmerTest)
+source("multiplot.R")
+
+select <- dplyr::select # masked by MASS
+theme_set(theme_few())
 ```
@@
 e1path = "../../parenting_obs_e1/"
-load(paste(e1path,"Exp1_cleaned_data.RData",sep=''))
+load(paste(e1path,"Exp1_cleaned_data.RData",sep='')) # merged dataframe ready for plotting
 
@@
 
+```{r e1lex_div, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.5, fig.height=3.1, set.cap.width=T, num.cols.cap=1, fig.cap = "Mean lexical diversity scores by condition (left: Type/Token ratio, right: MTLD) in Experiment 1."}
+d$Condition = factor(d$condition, levels = c("con", "exp"), labels = c("Control", "Video"))
+
+ms_lex <- d %>%
+  group_by(Condition) %>%
+  multi_boot_standard(col="TTR") # Type/Token Ratio
+
+ttr_means <- d%>%
+  group_by(Condition)%>%
+  summarise(mean = mean(TTR), sd = sd(TTR))
+
+# report table with ttr_means lex_sds
+
+e1ttr <- ggplot(ms_lex, aes(x=Condition, y=mean, fill=Condition)) + geom_bar(stat="identity") + 
+  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
+  xlab("Condition") + ylab("Type/Token Ratio (TTR)") +
+  langcog::scale_colour_solarized() + ggthemes::theme_few() +
+  theme(legend.position="none")
+
+ms_lex_mtld <- d %>%
+  group_by(Condition) %>%
+  multi_boot_standard(col="MTLD")
+
+mtld_means <- d %>%
+  group_by(Condition)%>%
+  summarise(mean = mean(MTLD), sd=sd(MTLD))
+
+# report table with mtld_means _sds
+
+e1mtld <- ggplot(ms_lex_mtld, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
+  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9))+
+  xlab("Condition") + ylab("MTLD") +
+  langcog::scale_colour_solarized() + ggthemes::theme_few() + 
+  theme(legend.position="none")
+
+multiplot(e1ttr, e1mtld, cols=2)
+```
+
+Word tokens and word types
+
+```{r e1token_type, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.5, fig.height=3.1, set.cap.width=T, num.cols.cap=1, fig.cap = "Mean number of word types and word tokens by condition in Experiment 1."}
+ms_tok <- d %>% group_by(Condition) %>%
+  multi_boot_standard(col = "tokens")
+
+e1tokens <- ggplot(ms_tok, aes(x=Condition, y = mean, fill = Condition)) +geom_bar(stat="identity") + 
+  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9))+
+  xlab("Condition") + ylab("Total Number of Word Tokens") +
+  langcog::scale_colour_solarized() + ggthemes::theme_few() +
+  theme(legend.position="none")
+
+ms_type <- d %>% group_by(Condition) %>%
+  multi_boot_standard(col = "types")
+
+e1types <- ggplot(ms_type, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
+  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
+             position = position_dodge(width = .9))+
+  xlab("Condition") + ylab("Total Number of Word Types") +
+  langcog::scale_colour_solarized() + ggthemes::theme_few() +
+  theme(legend.position="none")
+
+multiplot(e1tokens, e1types, cols=2)
+```
+
 ## Joint Attention
@@
 
-For more information on citations in RMarkdown, see **[here](http://rmarkdown.rstudio.com/authoring_bibliographies_and_citations.html#citations).**
-
 ## Footnotes
@@
 
-You can read local images using png package for example and plot 
-it like a regular plot using grid.raster from the grid package. 
-With this method you have full control of the size of your image. **Note: Image must be in .png file format for the readPNG function to work.**
-
 You might want to display a wide figure across both columns.
@@
 To format the width of your caption text, you set the `num.cols.cap` option to `2`.
-
-## One-column images
-
-Single column is the default option, but if you want set it explicitly, set `fig.env` to `figure`. Notice that the `num.cols` option for the caption width is set to `1`.
 

### 2019-02-08 paper/cogsci2019/cogsci2019.tex
exp1 lexical diversity results integrated

@@
 % KM added 1/4/18 to allow control of blind submission
+\cogscifinalcopy
 
@@
 
-\author{{\large \bf Hanwen Vivian~Zhang (vivian3@stanford.edu)} \\ Department of Psychology, Stanford University \\ Palo Alto, CA 94301 USA \AND {\large \bf George~Kachergis (george.kachergis@gmail.com)} \\ \\ Department of Psychology, Stanford University \\ Palo Alto, CA 94301 USA \AND {\large \bf Michael C.~Frank (mcfrank@stanford.edu)} \\ \\ Department of Psychology, Stanford University \\ Palo Alto, CA 94301 USA}
+\author{{\large\bf Hanwen Vivian~Zhang} (\texttt{vivian3@stanford.edu}) \\ {\large\bf George~Kachergis} (\texttt{george.kachergis@gmail.com}) \\ {\large\bf Michael C.~Frank} (\texttt{mcfrank@stanford.edu}) \\  Department of Psychology, Stanford University \\  Palo Alto, CA 94301 USA}
 
@@
 
+\begin{CodeChunk}
+\begin{figure}[H]
+
+{\centering \includegraphics{figs/e1lex_div-1}
+
+}
+
+\caption[Mean lexical diversity scores by condition (left]{Mean lexical diversity scores by condition (left: Type/Token ratio, right: MTLD) in Experiment 1.}\label{fig:e1lex_div}
+\end{figure}
+\end{CodeChunk}
+
+Word tokens and word types
+
+\begin{CodeChunk}
+\begin{figure}[H]
+
+{\centering \includegraphics{figs/e1token_type-1}
+
+}
+
+\caption[Mean number of word types and word tokens by condition in Experiment 1]{Mean number of word types and word tokens by condition in Experiment 1.}\label{fig:e1token_type}
+\end{figure}
+\end{CodeChunk}
+
 \subsection{Joint Attention}\label{joint-attention}
@@
 
-For more information on citations in RMarkdown, see
-\textbf{\href{http://rmarkdown.rstudio.com/authoring_bibliographies_and_citations.html\#citations}{here}.}
-
 \subsection{Footnotes}\label{footnotes}
@@
 
-You can read local images using png package for example and plot it like
-a regular plot using grid.raster from the grid package. With this method
-you have full control of the size of your image. \textbf{Note: Image
-must be in .png file format for the readPNG function to work.}
-
 You might want to display a wide figure across both columns. To do this,
@@
 the \texttt{num.cols.cap} option to \texttt{2}.
-
-\subsection{One-column images}\label{one-column-images}
-
-Single column is the default option, but if you want set it explicitly,
-set \texttt{fig.env} to \texttt{figure}. Notice that the
-\texttt{num.cols} option for the caption width is set to \texttt{1}.
 

### 2019-02-08 parenting_obs_e1/parenting_obs_lexdiv.Rmd
exp1 lexical diversity results integrated

@@
 conditions <- read.csv("joint_attention/conditions.csv")
-load("paq/paq_demo.RData") # do we use this??
+load("paq/paq_demo.RData") # do we use this?? GK: yes, see left_join on line 76
 
@@
   filter(!is.na(condition))
+
+save(d, file="Exp1_cleaned_data.RData") # for use in paper.Rmd
 ```
@@
 
-ggplot(ms_tok, aes(x = condition, y = mean, fill = condition)) + 
+ggplot(ms_type, aes(x = condition, y = mean, fill = condition)) + 
   geom_bar(stat="identity") + 
@@
   mutate(condition = factor(condition), 
-         lexdiv = as.numeric(lexdiv),
+         MTLD = as.numeric(MTLD),
          EL = as.numeric(langcog::scale(EL, scale=FALSE)),
@@
 ```{r}
-maximal_mod <- lmer(lexdiv ~ condition  + age + gender + parent_ed +
+maximal_mod <- lmer(MTLD ~ condition  + age + gender + parent_ed +
                            (1| video), 
@@
 M2 <- lex_means$mean[2]
-SD1 <- lex_sds$sd[1]
-SD2 <- lex_sds$sd[2]
+SD1 <- lex_means$sd[1]
+SD2 <- lex_means$sd[2]
 

### 2019-02-08 paper/cogsci2019/cogsci2019.Rmd
integrated lexical diversity graphs for both Exp 1 and Exp 2

@@
 
+lmer_data <- d %>%
+  filter(!is.na(AA), !is.na(EL), !is.na(RR))%>%
+  mutate(condition = factor(condition), 
+         MTLD = as.numeric(MTLD),
+         EL = as.numeric(langcog::scale(EL, scale=FALSE)),
+         AA = as.numeric(langcog::scale(AA, scale=FALSE)),
+         RR = as.numeric(langcog::scale(RR, scale=FALSE)),
+         age = as.numeric(langcog::scale(age, scale=FALSE)),
+         gender = as.factor(gender),
+         video = as.factor(video))
 ```
@@
 ### Participants. 
-60 infants aged 6-24 months and their parents participated in a museum in northern California. 
+`r nrow(d)` infants aged 6-24 months and their parents participated in a museum in northern California. 
 We included infants who were exposed to English at least 50 percent of the time or who were exposed less but whose participating parent reported that they primarily speak English with their child at home.
-[include specific demo info here?] - good to include now, and we can comment it out if it's too much (the full report/paper will have it)
+*INCLUDE FULL DEMOGRAPHIC INFO*
 
@@
 
-Participants were randomly assigned to an Activity Video condition or No-Video Control condition. 
+Participants were randomly assigned to either the Activity *Video* condition or the No-Video *Control* condition. 
 Participants in the Activity Video condition were assigned to one of the two videos available for their child's age group. 
@@
 ### Joint Attention Coding Procedure.
-Video of each session was coded for episodes of joint attention using Datavyu software. 
+The video of each session was manually coded for episodes of joint attention using the Datavyu software. 
 The video taken at floor level was coded by default, but the other video was referred to if the participants were not visible or if there was a technological error with the first camera. 
@@
 If either participant looked away for less than 3 seconds and then returned to the same object, it was coded as part of the same period of joint attention. 
-A second coder independently coded a third of the videos (i.e., 20 of the 60 videos, approximately equally distributed across ages) to establish reliability. % report reliability
+A second coder independently coded a third of the videos (i.e., 20 of the 60 videos, approximately equally distributed across ages) to establish reliability. *REPORT RELIABILITY*
 
@@
 
-```{r e1lex_div, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.5, fig.height=3.1, set.cap.width=T, num.cols.cap=1, fig.cap = "Mean lexical diversity scores by condition (left: Type/Token ratio, right: MTLD) in Experiment 1."}
+```{r, e1-lexdiv-regressions, echo=F, include=F}
+# Predicting lexical diversity based on experimental condition, PAQ, demographics. 
+maximal_mod <- lmer(MTLD ~ condition + age + gender + parent_ed + (1| video), data = lmer_data)
+summary(maximal_mod)
+
+# predict word tokesn
+tokens_mod <- lmer(tokens ~ condition*EL + condition*AA + condition*RR + age + gender + parent_ed + (1| video), 
+                         data = lmer_data)
+summary(tokens_mod)
+
+# predict word types
+types_mod <- lmer(types ~ condition*EL + condition*AA + condition*RR  + age + gender + parent_ed + (1| video), 
+                         data = lmer_data)
+summary(types_mod)
+```
+
+```{r e1lex_div, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.5, fig.height=3.0, set.cap.width=T, num.cols.cap=1, fig.cap = "Mean lexical diversity scores by condition (left: Type/Token ratio, right: MTLD) in Experiment 1."}
 d$Condition = factor(d$condition, levels = c("con", "exp"), labels = c("Control", "Video"))
+
+# all at once, but there are NAs in SD cols ?
+e1 <- d %>% group_by(Condition) %>%
+  summarise(TTR=mean(TTR), TTRsd=sd(TTR),
+            MTLD=mean(MTLD), MTLDsd=sd(MTLD),
+            types=mean(types), types.sd=sd(types),
+            tokens = mean(tokens), tokens.sd=sd(tokens))
 
@@
 
-# report table with mtld_means _sds
+# report table with mtld_means
 
@@
 
-```{r e1token_type, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.5, fig.height=3.1, set.cap.width=T, num.cols.cap=1, fig.cap = "Mean number of word types and word tokens by condition in Experiment 1."}
+```{r e1token_type, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.5, fig.height=3.0, set.cap.width=T, num.cols.cap=1, fig.cap = "Mean number of word types and word tokens by condition in Experiment 1."}
 ms_tok <- d %>% group_by(Condition) %>%
@@
 
+```{r, e1-effect-size, echo=F}
+cohens_d <- diff(ttr_means$mean) / (sqrt(sum(ttr_means$sd^2)) / 2)
+```
+
 ## Joint Attention
+
+## Discussion
+
+Both the number of tokens and types are higher in the experimental condition, while lexical diversity (Type/Token ratio) is higher in the control condition. 
+Parents may be relatively more repetetive in the experimental condition since they are attempting to stick to a specific prescribed task, but they talk more overall.
+Demographics and PAQ do not interact with condition, but there is a marginal effect of RR score on lexical diversity (lower diversity for higher RR scores), and marginal effects of parent education on word types and tokens (more types and tokens for higher parent education).
 
@@
 e2path = "../../parenting_obs_e2/"
-#load(paste(e2path,"Exp2_cleaned_data.RData",sep=''))
-e2d <- read.csv(paste(e2path,"MTLD_HDD.csv",sep=''), header=TRUE) 
+load(paste(e2path,"Exp2_cleaned_data.RData",sep=''))
+
 ```
@@
 ### Participants. 
-84 infants aged 12-24 months and their parents participated in the same museum as Experiment 1. 
+`r nrow(d)` infants aged 12-24 months and their parents participated in the same museum as Experiment 1. 
 We included infants who were exposed to English at least 75 percent of the time or who were exposed less but whose participating parent reported that they primarily speak English with their child at home.
@@
 
-```{r e2TTR, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=2, fig.height=2, set.cap.width=T, num.cols.cap=1, fig.cap = "How to do subfigures?"}
-img <- png::readPNG("figs/e2_TTR.png")
-grid::grid.raster(img)
+## Lexical Diversity
+
+```{r e2lexdiv, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.5, fig.height=3, set.cap.width=T, num.cols.cap=1, fig.cap = "Mean lexical diversity scores by condition (left: Type/Token ratio, right: MTLD) in Experiment 2."}
+ms_lex <- d %>% group_by(Condition) %>%
+  multi_boot_standard(col="TTR") 
+ttr_mean <- d%>% group_by(Condition)%>%
+  summarise(mean=mean(TTR), sd=sd(TTR))
+
+e2ttr <- ggplot(ms_lex, aes(x=Condition, y=mean, fill=Condition)) + ylim(0.0, 0.6) + geom_bar(stat="identity") + 
+  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
+  xlab("Condition") + ylab("TTR") +
+  langcog::scale_colour_solarized() + ggthemes::theme_few() +
+  theme(legend.position="none")
+
+ms_lex <- d %>% group_by(Condition) %>%
+  multi_boot_standard(col="MTLD") 
+mltd_mean <- d %>% group_by(Condition)%>%
+  summarise(mean = mean(MTLD), sd=sd(MTLD))
+
+e2mtld <- ggplot(ms_lex, aes(x = Condition, y = mean, fill = Condition)) + 
+  geom_bar(stat="identity") + 
+  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9))+
+  xlab("Condition") + ylab("MTLD") +
+  langcog::scale_colour_solarized() + ggthemes::theme_few() +
+  theme(legend.position="none")
+
+multiplot(e2ttr, e2mtld, cols=2)
 ```
 
-```{r e2MTLD, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=2, fig.height=2, set.cap.width=T, num.cols.cap=1, fig.cap = "One column image."}
-img <- png::readPNG("figs/e2_MTLD.png")
-grid::grid.raster(img)
+```{r e2token-type, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.5, fig.height=3, set.cap.width=T, num.cols.cap=1, fig.cap = "Mean number of word types and word tokens by condition in Experiment 2."}
+ms_tok <- d %>% group_by(Condition) %>%
+  multi_boot_standard(col = "tokens")
+
+e2tokens <- ggplot(ms_tok, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
+  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9))+
+  xlab("Condition") + ylab("Total Number of Word Tokens") +
+  langcog::scale_colour_solarized() + ggthemes::theme_few() +
+  theme(legend.position="none")
+
+ms_typ <- d %>% group_by(Condition) %>%
+  multi_boot_standard(col = "types")
+
+e2types <- ggplot(ms_typ, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
+  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9))+
+  xlab("Condition") + ylab("Total Number of Word Types") +
+  langcog::scale_colour_solarized() + ggthemes::theme_few() +
+  theme(legend.position="none")
+
+multiplot(e2tokens, e2types, cols=2)
 ```
-
-## Lexical Diversity
 
@@
 
-## Tables
-
-Number tables consecutively; place the table number and title (in
-10 point) above the table with one line space above the caption and
-one line space below it, as in Table 1. You may float
-tables to the top or bottom of a column, set wide tables across both
-columns.
-
-You can use the xtable function in the xtable package.
-
 # References

### 2019-02-08 paper/cogsci2019/cogsci2019.tex
integrated lexical diversity graphs for both Exp 1 and Exp 2

@@
 
-60 infants aged 6-24 months and their parents participated in a museum
+59 infants aged 6-24 months and their parents participated in a museum
 in northern California. We included infants who were exposed to English
@@
 participating parent reported that they primarily speak English with
-their child at home. {[}include specific demo info here?{]} - good to
-include now, and we can comment it out if it's too much (the full
-report/paper will have it)
+their child at home. \emph{INCLUDE FULL DEMOGRAPHIC INFO}
 
@@
 
-Participants were randomly assigned to an Activity Video condition or
-No-Video Control condition. Participants in the Activity Video condition
-were assigned to one of the two videos available for their child's age
-group. The No-Video Control condition was yoked to the Activity Video
-condition such that for every participant in the Activity Video
-condition who saw a particular video and received the associated props,
-a participant in the No-Video Control condition received the same props
-but did not watch the corresponding video. Parents also completed the
-Parenting Attitudes Questionnaire (PAQ). The PAQ measures parents'
-attitudes about parenting and child development along three dimensions:
-rules and respect, early learning, and affection and attachment.
+Participants were randomly assigned to either the Activity \emph{Video}
+condition or the No-Video \emph{Control} condition. Participants in the
+Activity Video condition were assigned to one of the two videos
+available for their child's age group. The No-Video Control condition
+was yoked to the Activity Video condition such that for every
+participant in the Activity Video condition who saw a particular video
+and received the associated props, a participant in the No-Video Control
+condition received the same props but did not watch the corresponding
+video. Parents also completed the Parenting Attitudes Questionnaire
+(PAQ). The PAQ measures parents' attitudes about parenting and child
+development along three dimensions: rules and respect, early learning,
+and affection and attachment.
 
@@
 
-Video of each session was coded for episodes of joint attention using
-Datavyu software. The video taken at floor level was coded by default,
-but the other video was referred to if the participants were not visible
-or if there was a technological error with the first camera. For each
-participant we coded for episodes of coordinated joint attention,
-episodes of passive joint attention, and parental bids for joint
-attention. We defined parental bids for joint attention as any attempt
-to initiate joint attention (i.e label, point, or otherwise draw
-attention to an object) that does not result in passive or coordinated
-joint attention. If more than 3 seconds elapsed between bids, they were
-coded as separate attempts. An episode of joint attention was considered
-passive if both participants visually focused on an object for a minimum
-of 3 seconds but the child did not acknowledge the parent. If either
-participant looked away from the object for less than 3 seconds and then
-returned to the same object it was considered part of the same period of
-joint attention. Episodes joint attention were considered coordinated if
-both participants visually focused on an object for a minimum of 3
-seconds and at some point in the interaction the child indicated
-awareness of interaction with some overt behavior toward the parent.
-This could be looks to the parent's face, gestures, vocalizations, or
-turn-taking. If either participant looked away for less than 3 seconds
-and then returned to the same object, it was coded as part of the same
-period of joint attention. A second coder independently coded a third of
-the videos (i.e., 20 of the 60 videos, approximately equally distributed
-across ages) to establish reliability. \% report reliability
+The video of each session was manually coded for episodes of joint
+attention using the Datavyu software. The video taken at floor level was
+coded by default, but the other video was referred to if the
+participants were not visible or if there was a technological error with
+the first camera. For each participant we coded for episodes of
+coordinated joint attention, episodes of passive joint attention, and
+parental bids for joint attention. We defined parental bids for joint
+attention as any attempt to initiate joint attention (i.e label, point,
+or otherwise draw attention to an object) that does not result in
+passive or coordinated joint attention. If more than 3 seconds elapsed
+between bids, they were coded as separate attempts. An episode of joint
+attention was considered passive if both participants visually focused
+on an object for a minimum of 3 seconds but the child did not
+acknowledge the parent. If either participant looked away from the
+object for less than 3 seconds and then returned to the same object it
+was considered part of the same period of joint attention. Episodes
+joint attention were considered coordinated if both participants
+visually focused on an object for a minimum of 3 seconds and at some
+point in the interaction the child indicated awareness of interaction
+with some overt behavior toward the parent. This could be looks to the
+parent's face, gestures, vocalizations, or turn-taking. If either
+participant looked away for less than 3 seconds and then returned to the
+same object, it was coded as part of the same period of joint attention.
+A second coder independently coded a third of the videos (i.e., 20 of
+the 60 videos, approximately equally distributed across ages) to
+establish reliability. \emph{REPORT RELIABILITY}
 
@@
 \subsection{Joint Attention}\label{joint-attention}
+
+\subsection{Discussion}\label{discussion}
+
+Both the number of tokens and types are higher in the experimental
+condition, while lexical diversity (Type/Token ratio) is higher in the
+control condition. Parents may be relatively more repetetive in the
+experimental condition since they are attempting to stick to a specific
+prescribed task, but they talk more overall. Demographics and PAQ do not
+interact with condition, but there is a marginal effect of RR score on
+lexical diversity (lower diversity for higher RR scores), and marginal
+effects of parent education on word types and tokens (more types and
+tokens for higher parent education).
 
@@
 
+\subsection{Lexical Diversity}\label{lexical-diversity-1}
+
 \begin{CodeChunk}
@@
 
-{\centering \includegraphics{figs/e2TTR-1}
+{\centering \includegraphics{figs/e2lexdiv-1}
 
@@
 
-\caption[How to do subfigures?]{How to do subfigures?}\label{fig:e2TTR}
+\caption[Mean lexical diversity scores by condition (left]{Mean lexical diversity scores by condition (left: Type/Token ratio, right: MTLD) in Experiment 2.}\label{fig:e2lexdiv}
 \end{figure}
@@
 
-{\centering \includegraphics{figs/e2MTLD-1}
+{\centering \includegraphics{figs/e2token-type-1}
 
@@
 
-\caption[One column image]{One column image.}\label{fig:e2MTLD}
+\caption[Mean number of word types and word tokens by condition in Experiment 2]{Mean number of word types and word tokens by condition in Experiment 2.}\label{fig:e2token-type}
 \end{figure}
@@
 
-\subsection{Lexical Diversity}\label{lexical-diversity-1}
-
 \subsection{Joint Attention}\label{joint-attention-1}
 
-\section{Discussion}\label{discussion}
+\section{Discussion}\label{discussion-1}
 
@@
 the \texttt{num.cols.cap} option to \texttt{2}.
-
-\subsection{Tables}\label{tables}
-
-Number tables consecutively; place the table number and title (in 10
-point) above the table with one line space above the caption and one
-line space below it, as in Table 1. You may float tables to the top or
-bottom of a column, set wide tables across both columns.
-
-You can use the xtable function in the xtable package.
 

### 2019-02-09 paper/cogsci2019/cogsci2019.Rmd
added JA analysis for Exp 1 to the paper

@@
 
+```{r, e1ja-regressions, echo=F, include=F}
+load(paste(e1path,"joint_attention/Exp1_joint_attention_data.RData",sep=''))
+d$Condition <- factor(d$Condition, levels = c("con","exp"), labels = c("Control","Video"))
+
+lmer_data <- d %>%
+  filter(!is.na(AA), !is.na(EL), !is.na(RR))%>%
+  mutate(Condition = factor(Condition), 
+         bids_tot = as.numeric(bids_tot),
+         EL = as.numeric(langcog::scale(EL, scale=FALSE)),
+         AA = as.numeric(langcog::scale(AA, scale=FALSE)),
+         RR = as.numeric(langcog::scale(RR, scale=FALSE)),
+         age = as.numeric(langcog::scale(age, scale=FALSE)),
+         gender = as.factor(gender),
+         Video = as.factor(Video))
+
+# Total number of bids
+bids_mod <- lmer(bids_tot ~ Condition *  EL  + Condition * AA + Condition * RR + age + gender + parent_ed +
+                           (1| Video), data = lmer_data)
+summary(bids_mod)
+
+# Episodes of coordinated joint attention.
+cja_mod <- lmer(cja ~ Condition * EL + Condition * AA + Condition * RR  + age + gender + parent_ed +
+                           (1| Video), data = lmer_data)
+summary(cja_mod)
+
+# Episodes of passive joint attention.
+pja_mod <- lmer(pja ~ Condition * EL + Condition * AA + Condition * RR  + age + gender + parent_ed +
+                           (1| Video), data = lmer_data)
+summary(pja_mod)
+
+# Total duration of passive joint attention.
+pja_time_mod <- lmer(pja_length ~ Condition * EL + Condition * AA + Condition * RR  + age + gender + parent_ed +
+                           (1| Video), data = lmer_data)
+summary(pja_time_mod)
+
+# Total duration of coordinated joint attention.
+cja_time_mod <- lmer(cja_length ~ Condition * EL + Condition * AA + Condition * RR  + age + gender + parent_ed +
+                           (1| Video), data = lmer_data)
+summary(cja_time_mod)
+```
+
+```{r e1ja-graphs, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.5, fig.height=3.0, set.cap.width=T, num.cols.cap=1, fig.cap = "Mean number of bids and episodes of Joint Attention in Experiment 1."}
+
+ms_bids <- d %>% group_by(Condition) %>%
+  multi_boot_standard(col="bids_tot")
+
+e1bids <- ggplot(ms_bids, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
+  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
+  xlab("Condition") + ylab("Total Bids for Joint Attention") +
+  langcog::scale_colour_solarized() + ggthemes::theme_few() + 
+  theme(legend.position="none")
+
+# total joint attention episodes
+ms_tja <- d %>% group_by(Condition) %>%
+  multi_boot_standard(col = "total_ja")
+
+e1tja <- ggplot(ms_tja, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
+  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9))+
+  xlab("Condition") + ylab("Total Episodes of Joint Attention") +
+  langcog::scale_colour_solarized() + ggthemes::theme_few() + 
+  theme(legend.position="none")
+
+multiplot(e1bids, e1tja, cols=2)
+```
+
+```{r e1ja-graphs-pass-coord, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.5, fig.height=3.0, set.cap.width=T, num.cols.cap=1, fig.cap = "Average number of passive and coordinated episodes of JA in Experiment 1."}
+ms_pja <- d %>% group_by(Condition) %>%
+  multi_boot_standard(col = "pja")
+
+e1pja <- ggplot(ms_pja, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
+  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9))+
+  xlab("Condition") + ylab("Episodes of Passive Joint Attention")  +
+  langcog::scale_colour_solarized() + ggthemes::theme_few() + theme(legend.position="none")
+
+#Episodes of coordinated joint attention
+ms_cja <- d %>% group_by(Condition) %>%
+  multi_boot_standard(col = "cja")
+
+e1cja <- ggplot(ms_cja, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
+  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9))+
+  xlab("Condition") + ylab("Episodes of Coordinated Joint Attention")  +
+  langcog::scale_colour_solarized() + ggthemes::theme_few() + theme(legend.position="none")
+
+multiplot(e1pja, e1cja, cols=2)
+```
+
 ## Discussion
@@
 Demographics and PAQ do not interact with condition, but there is a marginal effect of RR score on lexical diversity (lower diversity for higher RR scores), and marginal effects of parent education on word types and tokens (more types and tokens for higher parent education).
+
+There is a main effect of condition on total bids for joint attention.
+Parents in the experimental condition (i.e., those who saw a video demonstrating an activity) made a greater number of bids for joint attention with their child.
+There was no effect of condition on the number of episodes of either passive or coordinated joint attention, or the duration of these episodes. 
+There is a marginal effect of gender on bids for joint attention, with parents of males producing more bids.
+There is a marginal interaction between RR scores and condition on passive joint attention, such that the experimental condition increased the number of episodes of PJA to a greater extent for people with high RR scores.
+While the electronically-delivered parenting advice increased the number of bids for joint attention by parents, it did not significantly effect the number or duration of episodes of joint attention.
+One possibility is that child variables had a comparatively larger impact on the attainment of joint attention.
 

### 2019-02-09 paper/cogsci2019/cogsci2019.tex
added JA analysis for Exp 1 to the paper

@@
 sustainibility differences of these measure. should I make it more
-clear?) (Susking et al., 2015). The fact that changes did not sustain
-could be due to the intervention itself, or could merely be that
+clear?) (D. L. Suskind et al., 2015). The fact that changes did not
+sustain could be due to the intervention itself, or could merely be that
 home-visiting is not sustainable enough for parents to easily and
@@
 
+\begin{CodeChunk}
+\begin{figure}[H]
+
+{\centering \includegraphics{figs/e1ja-graphs-1}
+
+}
+
+\caption[Mean number of bids and episodes of Joint Attention in Experiment 1]{Mean number of bids and episodes of Joint Attention in Experiment 1.}\label{fig:e1ja-graphs}
+\end{figure}
+\end{CodeChunk}
+
+\begin{CodeChunk}
+\begin{figure}[H]
+
+{\centering \includegraphics{figs/e1ja-graphs-pass-coord-1}
+
+}
+
+\caption[Average number of passive and coordinated episodes of JA in Experiment 1]{Average number of passive and coordinated episodes of JA in Experiment 1.}\label{fig:e1ja-graphs-pass-coord}
+\end{figure}
+\end{CodeChunk}
+
 \subsection{Discussion}\label{discussion}
@@
 tokens for higher parent education).
+
+There is a main effect of condition on total bids for joint attention.
+Parents in the experimental condition (i.e., those who saw a video
+demonstrating an activity) made a greater number of bids for joint
+attention with their child. There was no effect of condition on the
+number of episodes of either passive or coordinated joint attention, or
+the duration of these episodes. There is a marginal effect of gender on
+bids for joint attention, with parents of males producing more bids.
+There is a marginal interaction between RR scores and condition on
+passive joint attention, such that the experimental condition increased
+the number of episodes of PJA to a greater extent for people with high
+RR scores. While the electronically-delivered parenting advice increased
+the number of bids for joint attention by parents, it did not
+significantly effect the number or duration of episodes of joint
+attention. One possibility is that child variables had a comparatively
+larger impact on the attainment of joint attention.
 
@@
 \hypertarget{ref-Suskind2015}{}
-Susking, D. L., Leffel, K. R., Graf, E., Hernandez, M. W., Gunderson, E.
+Suskind, D. L., Leffel, K. R., Graf, E., Hernandez, M. W., Gunderson, E.
 A., Sapolich, S. G., \ldots{} Levine, S. C. (2015). A parent-directed

### 2019-02-09 parenting_obs_e1/joint_attention/parenting_obs_JA.Rmd
added JA analysis for Exp 1 to the paper

@@
 Total number of bids (successful and unsuccessful)
-```{r}
+```{r, width=4, height=4}
+save(d, file="Exp1_joint_attention_data.RData")
 ms_bids <- d %>%
@@
   ggthemes::theme_few() + 
-  theme(legend.title = element_text(size=18), 
-        legend.text = element_text(size=16), 
-        axis.text.x  = element_text(vjust=0.5, size=16),
-        axis.title.x = element_text(size=18), 
-        axis.text.y  = element_text(vjust=0.5, size=16),
-        axis.title.y = element_text(size=18))
+  theme(legend.position="none") 
 ```

### 2019-02-11 paper/cogsci2019/cogsci2019.Rmd
revised citations in intro

@@
 ## Guided Play Scaffolds Learning
-Children's early play behaviors are often assisted by more skilled and knowledgeable play partners such as their caregivers and older siblings (Kaye, 1970). 
-Under such expert guidance, children are encouraged and motivated to engage in more advanced play, undertaking explorations that push the boundaries of what they would be able to do unaided (Vygotsky, 197X).
-These tutorial interactions have been shown to be a "a crucial feature of infancy and childhood" (Wood, 1970).
-Thus, with the knowledge of both play and tutorial interactions, guided play, "where children actively engage in pleasurable and seemingly spontaneous activities under the direction of adults" (Hirsh-Pasek, 2008),
+Children's early play behaviors are often assisted by more skilled and knowledgeable play partners such as their caregivers and older siblings [@Kaye1970]. 
+Under such expert guidance, children are encouraged and motivated to engage in more advanced play, undertaking explorations that push the boundaries of what they would be able to do unaided [@Vygotsky1978].
+These tutorial interactions have been shown to be an important component of child development [@Wood1976].
+Thus, with the knowledge of both play and tutorial interactions, guided play, which consists of both active and enjoyable activities as well as close guidance of adults [@Hirsh2008]
 have drawn researchers' interest. 
 Weisberg showed that, with preschoolers, guided play scaffolds the environment while still allowing children to maintain a large degree of control, 
-and it outperforms direct-instruction approaches in encouraging a variety of positive academic outcomes (Weisberg, Hirsh-Pasek and Golinkoff, 2013).
-Massey specifically showed that guided play could facilitate children's vocabulary and comprehensive language development and subsequent literacy skills (Massey, 2013).
+and it outperforms direct-instruction approaches in encouraging a variety of positive academic outcomes [@Weisberg2013].
+Massey specifically showed that guided play could facilitate children's vocabulary and comprehensive language development and subsequent literacy skills [@Massey2013].
 
 ## Improving Parenting Practices and Language Use
-(early interventions on parenting practices can help children's outcomes)
 Thus, including guided play in parenting practices early on is important and should help with children's later performances.
@@
 should I make it more clear?) [@Suskind2015].
-The fact that changes did not sustain could be due to the intervention itself, 
+That changes did not sustain could be due to the intervention itself,
 or could merely be that home-visiting is not sustainable enough for parents to easily and constantly get parenting advice. 
+Thus, new methods of delivering parenting advice should be considered.
 
 ## Effectiveness of Digital Delivery
-(apps are an easy way to deliver curated, age-appropriate parenting advice — but can we measure an influence on parent's language? and do the interventions lead to children paying more attention?)
-
 Digitally-delivered methods could address some logistic barriers to face-to-face delivery methods. 
-Bretenstein reviewed 11 studies on them and showed good promise for the efficacy of interventions using digitally-delivered methods. 
+Breitenstein reviewed 11 studies on them and showed good promise for the efficacy of interventions using digitally-delivered methods [@Breitenstein2014].
 However, the parent and child outcomes assessed in the review (e.g.infant positive behaviors, satisfaction, emotional symptoms etc.) did not address the nature or quality of parent-infant interactions at a detailed level,
 like if the interventions lead to children paying more attention, or vocabulary changes in parents' language usages. 
+Although digitally-delivered ac-tivities are designed to promote learning and cognitive devel-opment, it is unclear how they might affect these dimensions of parent-child interactions.
 Thus, we want to conduct this experiment to explore if and how digital scaffolding of activities affect the social and linguistic characteristics of parent-child ineractions.
-
-The quality of parent-child interactions can be measured by both the social engagement of parents (e.g., joint attention to objects in the environment) and the quality of language (e.g., vocabulary diversity).
-Although digitally-delivered activities are designed to promote learning and cognitive development, it is unclear how they might affect these dimensions of parent-child interactions. 
-How does digital scaffolding of activities affect the social and linguistic characteristics of parents' speech to their children?
+The quality of parent-child interactions can be measured by both the social engagement of parents (e.g., joint attention to objects in the environment)[@Bigelow2004] and the quality of language (e.g., vocabulary diversity) [@Malvern2004].
 

### 2019-02-11 paper/cogsci2019/cogsci2019.tex
revised citations in intro

@@
 knowledgeable play partners such as their caregivers and older siblings
-(Kaye, 1970). Under such expert guidance, children are encouraged and
-motivated to engage in more advanced play, undertaking explorations that
-push the boundaries of what they would be able to do unaided (Vygotsky,
-197X). These tutorial interactions have been shown to be a ``a crucial
-feature of infancy and childhood'' (Wood, 1970). Thus, with the
-knowledge of both play and tutorial interactions, guided play, ``where
-children actively engage in pleasurable and seemingly spontaneous
-activities under the direction of adults'' (Hirsh-Pasek, 2008), have
-drawn researchers' interest. Weisberg showed that, with preschoolers,
-guided play scaffolds the environment while still allowing children to
-maintain a large degree of control, and it outperforms
+({\textbf{???}})(Kaye, 1970). Under such expert guidance, children are
+encouraged and motivated to engage in more advanced play, undertaking
+explorations that push the boundaries of what they would be able to do
+unaided (Vygotsky, 1978). These tutorial interactions have been shown to
+be an important component of child development (Wood, 1970). Thus, with
+the knowledge of both play and tutorial interactions, guided play, which
+consists of active and enjoyable activities as well as directions of
+adults (Hirsh-Pasek, 2008)
+
+``where children actively engage in pleasurable and seemingly
+spontaneous activities under the direction of adults'' (Hirsh-Pasek,
+2008), have drawn researchers' interest. Weisberg showed that, with
+preschoolers, guided play scaffolds the environment while still allowing
+children to maintain a large degree of control, and it outperforms
 direct-instruction approaches in encouraging a variety of positive

### 2019-02-11 paper/cogsci2019/cogsci2019.Rmd
revised intro and added demo and reliability info

@@
 Children's early play behaviors are often assisted by more skilled and knowledgeable play partners such as their caregivers and older siblings [@Kaye1970]. 
-Under such expert guidance, children are encouraged and motivated to engage in more advanced play, undertaking explorations that push the boundaries of what they would be able to do unaided [@Vygotsky1978].
-These tutorial interactions have been shown to be an important component of child development [@Wood1976].
+Under such expert guidance, children are encouraged and motivated to engage in more advanced play, undertaking explorations that push the boundaries of what they would be able to do unaided [@Vygotsky1980].
+These tutorial interactions have been shown to be important components of child development [@Wood1976].
 Thus, with the knowledge of both play and tutorial interactions, guided play, which consists of both active and enjoyable activities as well as close guidance of adults [@Hirsh2008]
-have drawn researchers' interest. 
-Weisberg showed that, with preschoolers, guided play scaffolds the environment while still allowing children to maintain a large degree of control, 
+has drawn researchers' interest. 
+A study on preschoolers by Weisberg showed that guided play scaffolds the environment while still allowing children to maintain a large degree of control, 
 and it outperforms direct-instruction approaches in encouraging a variety of positive academic outcomes [@Weisberg2013].
-Massey specifically showed that guided play could facilitate children's vocabulary and comprehensive language development and subsequent literacy skills [@Massey2013].
+Another study by Massey specifically found that guided play could facilitate children's vocabulary and comprehensive language development and subsequent literacy skills [@Massey2013].
 
 ## Improving Parenting Practices and Language Use
-Thus, including guided play in parenting practices early on is important and should help with children's later performances.
-Suskind did a parent-directed home-visiting intervention experiment in 2015,
-and found that parents in experimental group have greater knowledge of language development and this effect sustained after the experiment is done. 
-However, more interactive outcomes, like parent word type and token numbers, child word types, conversational turn counts and child vocalization counts, 
-increased during the home-visiting but did not sustain after four months of intervention (there are more detailed sustainibility differences of these measure.
-should I make it more clear?) [@Suskind2015].
+Thus, including guided play in parenting practices early on is crucial and will help with children's later performances in academic and social situations. 
+To intervene in parenting practices, Suskind and others did a parent-directed home-visiting intervention experiment in 2015 for children of low socioeconomic status.
+They showed that parents in experimental group have greater knowledge of language development and this effect sustained four months after the intervention. 
+However, more interactive outcomes, like adult word tokens, conversational turn counts, and child vocalization counts, 
+though increased significantly during the experiment,
+did not sustain after the intervention [@Suskind2015].
 That changes did not sustain could be due to the intervention itself,
-or could merely be that home-visiting is not sustainable enough for parents to easily and constantly get parenting advice. 
+or could merely be that the methods of home-visiting is not sustainable enough for parents to easily and constantly get parenting advice.
 Thus, new methods of delivering parenting advice should be considered.
@@
 ## Effectiveness of Digital Delivery
-Digitally-delivered methods could address some logistic barriers to face-to-face delivery methods. 
-Breitenstein reviewed 11 studies on them and showed good promise for the efficacy of interventions using digitally-delivered methods [@Breitenstein2014].
+With the development of technology, digitally-delivered methods could address some logistic barriers to face-to-face delivery methods. 
+Breitenstein has reviewed 11 studies on them and showed good promise for the efficacy of interventions using digitally-delivered methods [@Breitenstein2014].
 However, the parent and child outcomes assessed in the review (e.g.infant positive behaviors, satisfaction, emotional symptoms etc.) did not address the nature or quality of parent-infant interactions at a detailed level,
@@
          video = as.factor(video))
+
+a <- d$gender == "F"
+length(a[a == TRUE])
+
 ```
@@
 ### Participants. 
-`r nrow(d)` infants aged 6-24 months and their parents participated in a museum in northern California. 
-We included infants who were exposed to English at least 50 percent of the time or who were exposed less but whose participating parent reported that they primarily speak English with their child at home.
-*INCLUDE FULL DEMOGRAPHIC INFO*
+`r nrow(d)` infants  (F=42, M=18) aged 6-24 months (20 6-11.9 month-olds, 20 12-17.9 month-olds, and 20 18-24 month-olds) and their parents participated in a museum in northern California. 
+We included infants who were exposed to English at least 50 percent of the time (n= 58) or who were exposed less but whose participating parent reported that they primarily speak English with their child at home (n = 2).
+Sixty-one% of participants (n=37) had been exposed to 2 or more languages as indicated by their parent.
+Parents identified their children as White (n=25), Asian (n=11), African American/Black (n=2), Biracial (n=12), other (n=5), or declined to state (n=5).
+Fifteen parents reported their child was of Hispanic origin.
+Parents tended to be highly educated, with a highest level of education reported as high school (n = 5), some college (n = 6), four-year college (n = 14), some graduate school (n = 1), completed graduate school (n = 28) or declined to state (n=6).
 
@@
 
-Participants were randomly assigned to either the Activity *Video* condition or the No-Video *Control* condition. 
+Participants were randomly assigned to either the *Video* condition or the *Control* condition. 
 Participants in the Activity Video condition were assigned to one of the two videos available for their child's age group. 
@@
 If either participant looked away for less than 3 seconds and then returned to the same object, it was coded as part of the same period of joint attention. 
-A second coder independently coded a third of the videos (i.e., 20 of the 60 videos, approximately equally distributed across ages) to establish reliability. *REPORT RELIABILITY*
+A second coder independently coded a third of the videos (i.e., 20 of the 60 videos, approximately equally distributed across ages) to establish reliability.
+The two coders achieved reliability with ICC = 0.80 with 95% confident interval = 0.57-0.92 (p<0.05) for number of parent bids; ICC = 0.20 with 95% confident interval = -0.26-0.58 for number of passive joint attention established; ICC = 0.66 with 95% confident interval = 0.32-0.85 (p<0.05) for number of coordinated joint attention established; ICC = 0.24 with 95% confident interval = -0.21-0.61 for length of passive joint attention, and ICC = 0.62 with 95% confident interval = 0.27-0.83 (p<0.05) for length of passive joint attention.
 
@@
 Thus, the content of the videos superficially matched those in the Activity Video condition, but did not suggest any particular activities.
-The videos were trimmed to approximately match the average video length in the Activity Video condition (2 minutes ??).
+The videos were trimmed to approximately match the average video length in the Activity Video condition around 1.5 minutes.
 

### 2019-02-11 paper/cogsci2019/cogsci2019.tex
revised intro and added demo and reliability info

--- 2019-02-09 paper/cogsci2019/cogsci2019.tex
@@
 push the boundaries of what they would be able to do unaided (Vygotsky,
-197X). These tutorial interactions have been shown to be a ``a crucial
-feature of infancy and childhood'' (Wood, 1970). Thus, with the
-knowledge of both play and tutorial interactions, guided play, ``where
-children actively engage in pleasurable and seemingly spontaneous
-activities under the direction of adults'' (Hirsh-Pasek, 2008), have
-drawn researchers' interest. Weisberg showed that, with preschoolers,
+1980). These tutorial interactions have been shown to be important
+components of child development (Wood, Bruner, \& Ross, 1976). Thus,
+with the knowledge of both play and tutorial interactions, guided play,
+which consists of both active and enjoyable activities as well as close
+guidance of adults (Hirsh-Pasek \& Golinkoff, 2008) has drawn
+researchers' interest. A study on preschoolers by Weisberg showed that
 guided play scaffolds the environment while still allowing children to
@@
 direct-instruction approaches in encouraging a variety of positive
-academic outcomes (Weisberg, Hirsh-Pasek and Golinkoff, 2013). Massey
-specifically showed that guided play could facilitate children's
-vocabulary and comprehensive language development and subsequent
-literacy skills (Massey, 2013).
+academic outcomes (Weisberg, Hirsh-Pasek, \& Golinkoff, 2013). Another
+study by Massey specifically found that guided play could facilitate
+children's vocabulary and comprehensive language development and
+subsequent literacy skills (Massey, 2013).
 
@@
 
-(early interventions on parenting practices can help children's
-outcomes) Thus, including guided play in parenting practices early on is
-important and should help with children's later performances. Suskind
-did a parent-directed home-visiting intervention experiment in 2015, and
-found that parents in experimental group have greater knowledge of
-language development and this effect sustained after the experiment is
-done. However, more interactive outcomes, like parent word type and
-token numbers, child word types, conversational turn counts and child
-vocalization counts, increased during the home-visiting but did not
-sustain after four months of intervention (there are more detailed
-sustainibility differences of these measure. should I make it more
-clear?) (D. L. Suskind et al., 2015). The fact that changes did not
-sustain could be due to the intervention itself, or could merely be that
+Thus, including guided play in parenting practices early on is crucial
+and will help with children's later performances in academic and social
+situations. To intervene in parenting practices, Suskind and others did
+a parent-directed home-visiting intervention experiment in 2015 for
+children of low socioeconomic status. They showed that parents in
+experimental group have greater knowledge of language development and
+this effect sustained four months after the intervention. However, more
+interactive outcomes, like adult word tokens, conversational turn
+counts, and child vocalization counts, though increased significantly
+during the experiment, did not sustain after the intervention (D. L.
+Suskind et al., 2015). That changes did not sustain could be due to the
+intervention itself, or could merely be that the methods of
 home-visiting is not sustainable enough for parents to easily and
-constantly get parenting advice.
+constantly get parenting advice. Thus, new methods of delivering
+parenting advice should be considered.
 
@@
 
-(apps are an easy way to deliver curated, age-appropriate parenting
-advice --- but can we measure an influence on parent's language? and do
-the interventions lead to children paying more attention?)
-
-Digitally-delivered methods could address some logistic barriers to
-face-to-face delivery methods. Bretenstein reviewed 11 studies on them
-and showed good promise for the efficacy of interventions using
-digitally-delivered methods. However, the parent and child outcomes
-assessed in the review (e.g.infant positive behaviors, satisfaction,
-emotional symptoms etc.) did not address the nature or quality of
-parent-infant interactions at a detailed level, like if the
+With the development of technology, digitally-delivered methods could
+address some logistic barriers to face-to-face delivery methods.
+Breitenstein has reviewed 11 studies on them and showed good promise for
+the efficacy of interventions using digitally-delivered methods
+(Breitenstein, Gross, \& Christophersen, 2014). However, the parent and
+child outcomes assessed in the review (e.g.infant positive behaviors,
+satisfaction, emotional symptoms etc.) did not address the nature or
+quality of parent-infant interactions at a detailed level, like if the
 interventions lead to children paying more attention, or vocabulary
-changes in parents' language usages. Thus, we want to conduct this
-experiment to explore if and how digital scaffolding of activities
-affect the social and linguistic characteristics of parent-child
-ineractions.
-
-The quality of parent-child interactions can be measured by both the
-social engagement of parents (e.g., joint attention to objects in the
-environment) and the quality of language (e.g., vocabulary diversity).
-Although digitally-delivered activities are designed to promote learning
-and cognitive development, it is unclear how they might affect these
-dimensions of parent-child interactions. How does digital scaffolding of
-activities affect the social and linguistic characteristics of parents'
-speech to their children?
+changes in parents' language usages. Although digitally-delivered
+ac-tivities are designed to promote learning and cognitive devel-opment,
+it is unclear how they might affect these dimensions of parent-child
+interactions. Thus, we want to conduct this experiment to explore if and
+how digital scaffolding of activities affect the social and linguistic
+characteristics of parent-child ineractions. The quality of parent-child
+interactions can be measured by both the social engagement of parents
+(e.g., joint attention to objects in the environment)(Bigelow, MacLean,
+\& Proctor, 2004) and the quality of language (e.g., vocabulary
+diversity) (Malvern, Richards, Chipere, \& Durán, 2004).
 
@@
 
+\begin{CodeChunk}
+\begin{CodeOutput}
+[1] 45
+\end{CodeOutput}
+\end{CodeChunk}
+
 \subsubsection{Participants.}\label{participants.}
 
-59 infants aged 6-24 months and their parents participated in a museum
-in northern California. We included infants who were exposed to English
-at least 50 percent of the time or who were exposed less but whose
-participating parent reported that they primarily speak English with
-their child at home. \emph{INCLUDE FULL DEMOGRAPHIC INFO}
+60 infants (F=42, M=18) aged 6-24 months (20 6-11.9 month-olds, 20
+12-17.9 month-olds, and 20 18-24 month-olds) and their parents
+participated in a museum in northern California. We included infants who
+were exposed to English at least 50 percent of the time (n= 58) or who
+were exposed less but whose participating parent reported that they
+primarily speak English with their child at home (n = 2). Sixty-one\% of
+participants (n=37) had been exposed to 2 or more languages as indicated
+by their parent. Parents identified their children as White (n=25),
+Asian (n=11), African American/Black (n=2), Biracial (n=12), other
+(n=5), or declined to state (n=5). Fifteen parents reported their child
+was of Hispanic origin. Parents tended to be highly educated, with a
+highest level of education reported as high school (n = 5), some college
+(n = 6), four-year college (n = 14), some graduate school (n = 1),
+completed graduate school (n = 28) or declined to state (n=6).
 
@@
 
-Participants were randomly assigned to either the Activity \emph{Video}
-condition or the No-Video \emph{Control} condition. Participants in the
-Activity Video condition were assigned to one of the two videos
-available for their child's age group. The No-Video Control condition
-was yoked to the Activity Video condition such that for every
-participant in the Activity Video condition who saw a particular video
-and received the associated props, a participant in the No-Video Control
-condition received the same props but did not watch the corresponding
-video. Parents also completed the Parenting Attitudes Questionnaire
-(PAQ). The PAQ measures parents' attitudes about parenting and child
-development along three dimensions: rules and respect, early learning,
-and affection and attachment.
+Participants were randomly assigned to either the \emph{Video} condition
+or the \emph{Control} condition. Participants in the Activity Video
+condition were assigned to one of the two videos available for their
+child's age group. The No-Video Control condition was yoked to the
+Activity Video condition such that for every participant in the Activity
+Video condition who saw a particular video and received the associated
+props, a participant in the No-Video Control condition received the same
+props but did not watch the corresponding video. Parents also completed
+the Parenting Attitudes Questionnaire (PAQ). The PAQ measures parents'
+attitudes about parenting and child development along three dimensions:
+rules and respect, early learning, and affection and attachment.
 
@@
 the 60 videos, approximately equally distributed across ages) to
-establish reliability. \emph{REPORT RELIABILITY}
+establish reliability. The two coders achieved reliability with ICC =
+0.80 with 95\% confident interval = 0.57-0.92 (p\textless{}0.05) for
+number of parent bids; ICC = 0.20 with 95\% confident interval =
+-0.26-0.58 for number of passive joint attention established; ICC = 0.66
+with 95\% confident interval = 0.32-0.85 (p\textless{}0.05) for number
+of coordinated joint attention established; ICC = 0.24 with 95\%
+confident interval = -0.21-0.61 for length of passive joint attention,
+and ICC = 0.62 with 95\% confident interval = 0.27-0.83
+(p\textless{}0.05) for length of passive joint attention.
 
@@
 to approximately match the average video length in the Activity Video
-condition (2 minutes ??).
+condition around 1.5 minutes.
 
@@
 \hypertarget{refs}{}
+\hypertarget{ref-Bigelow2004}{}
+Bigelow, A. E., MacLean, K., \& Proctor, J. (2004). The role of joint
+attention in the development of infants' play with objects.
+\emph{Developmental Science}, \emph{7}, 518--526.
+
+\hypertarget{ref-Breitenstein2014}{}
+Breitenstein, S. M., Gross, D., \& Christophersen, R. (2014). Digital
+delivery methods of parenting training interventions: A systematic
+review. \emph{Worldviews on Evidence-Based Nursing}, \emph{11},
+168--176.
+
 \hypertarget{ref-Hart1995}{}
@@
 \url{http://doi.org/10.1126/science.1128898}
+
+\hypertarget{ref-Hirsh2008}{}
+Hirsh-Pasek, K., \& Golinkoff, R. M. (2008). Why play= learning.
+\emph{Encyclopedia on Early Childhood Development}, 1--7.
+
+\hypertarget{ref-Kaye1970}{}
+Kaye, K. (1970). Mother-child instructional interaction.
+\emph{Unpublished Doctoral Thesis, Department of Psychology, Harvard
+University}.
+
+\hypertarget{ref-Malvern2004}{}
+Malvern, D., Richards, B. J., Chipere, N., \& Durán, P. (2004). Lexical
+diversity and language development.
+
+\hypertarget{ref-Massey2013}{}
+Massey, S. L. (2013). From the reading rug to the play center: Enhancing
+vocabulary and comprehensive language skills by connecting storybook
+reading and guided play. \emph{Early Childhood Education Journal},
+\emph{41}, 125--131.
 
@@
 
+\hypertarget{ref-Vygotsky1980}{}
+Vygotsky, L. S. (1980). Mind in society: The development of higher
+psychological processes.
+
+\hypertarget{ref-Weisberg2013}{}
+Weisberg, D. S., Hirsh-Pasek, K., \& Golinkoff, R. M. (2013). Guided
+play: Where curricular goals meet a playful pedagogy. \emph{Mind, Brain,
+and Education}, \emph{7}, 104--112.
+
+\hypertarget{ref-Wood1976}{}
+Wood, D., Bruner, J. S., \& Ross, G. (1976). The role of tutoring in
+problem solving. \emph{Journal of Child Psychology and Psychiatry},
+\emph{17}, 89--100.
+
 \bibliographystyle{apacite}

### 2019-02-11 parenting_obs_e1/parenting_obs_lexdiv.Rmd
revised intro and added demo and reliability info

@@
 conditions <- read.csv("joint_attention/conditions.csv")
-load("paq/paq_demo.RData") # do we use this?? GK: yes, see left_join on line 76
+load("paq/paq_demo.RData")
 
@@
 data$SID <- stringr::str_replace(data$SID, "05116_2", "050116_02")
+data$SID <- stringr::str_replace(data$SID, "98470_111716_02", "111716_02")
 ```

### 2019-02-11 paper/cogsci2019/cogsci2019.Rmd
formatting

@@
 ### Participants. 
-`r nrow(d)` infants  (F=42, M=18) aged 6-24 months (20 6-11.9 month-olds, 20 12-17.9 month-olds, and 20 18-24 month-olds) and their parents participated in a museum in northern California. 
-We included infants who were exposed to English at least 50 percent of the time (n= 58) or who were exposed less but whose participating parent reported that they primarily speak English with their child at home (n = 2).
-Sixty-one% of participants (n=37) had been exposed to 2 or more languages as indicated by their parent.
-Parents identified their children as White (n=25), Asian (n=11), African American/Black (n=2), Biracial (n=12), other (n=5), or declined to state (n=5).
+`r nrow(d)` infants  (F = 42, M = 18) aged 6-24 months (20 6-11.9 month-olds, 20 12-17.9 month-olds, and 20 18-24 month-olds) and their parents participated in a museum in northern California. 
+We included infants who were exposed to English at least 50 percent of the time (n = 58) or who were exposed less but whose participating parent reported that they primarily speak English with their child at home (n = 2).
+Sixty-one% of participants (n = 37) had been exposed to 2 or more languages as indicated by their parent.
+Parents identified their children as White (n = 25), Asian (n = 11), African American/Black (n = 2), Biracial (n = 12), other (n = 5), or declined to state (n = 5).
 Fifteen parents reported their child was of Hispanic origin.
-Parents tended to be highly educated, with a highest level of education reported as high school (n = 5), some college (n = 6), four-year college (n = 14), some graduate school (n = 1), completed graduate school (n = 28) or declined to state (n=6).
+Parents tended to be highly educated, with a highest level of education reported as high school (n = 5), some college (n = 6), four-year college (n = 14), some graduate school (n = 1), completed graduate school (n = 28) or declined to state (n = 6).
 
@@
 A second coder independently coded a third of the videos (i.e., 20 of the 60 videos, approximately equally distributed across ages) to establish reliability.
-The two coders achieved reliability with ICC = 0.80 with 95% confident interval = 0.57-0.92 (p<0.05) for number of parent bids; ICC = 0.20 with 95% confident interval = -0.26-0.58 for number of passive joint attention established; ICC = 0.66 with 95% confident interval = 0.32-0.85 (p<0.05) for number of coordinated joint attention established; ICC = 0.24 with 95% confident interval = -0.21-0.61 for length of passive joint attention, and ICC = 0.62 with 95% confident interval = 0.27-0.83 (p<0.05) for length of passive joint attention.
+The two coders achieved reliability with ICC = 0.80 with 95% confident interval = 0.57-0.92 (p < 0.05) for number of parent bids; ICC = 0.20 with 95% confident interval = -0.26-0.58 for number of passive joint attention established; ICC = 0.66 with 95% confident interval = 0.32-0.85 (p < 0.05) for number of coordinated joint attention established; ICC = 0.24 with 95% confident interval = -0.21-0.61 for length of passive joint attention, and ICC = 0.62 with 95% confident interval = 0.27-0.83 (p < 0.05) for length of passive joint attention.
 

### 2019-02-11 paper/cogsci2019/cogsci2019.tex
formatting

@@
 
-60 infants (F=42, M=18) aged 6-24 months (20 6-11.9 month-olds, 20
+60 infants (F = 42, M = 18) aged 6-24 months (20 6-11.9 month-olds, 20
 12-17.9 month-olds, and 20 18-24 month-olds) and their parents
 participated in a museum in northern California. We included infants who
-were exposed to English at least 50 percent of the time (n= 58) or who
+were exposed to English at least 50 percent of the time (n = 58) or who
 were exposed less but whose participating parent reported that they
 primarily speak English with their child at home (n = 2). Sixty-one\% of
-participants (n=37) had been exposed to 2 or more languages as indicated
-by their parent. Parents identified their children as White (n=25),
-Asian (n=11), African American/Black (n=2), Biracial (n=12), other
-(n=5), or declined to state (n=5). Fifteen parents reported their child
-was of Hispanic origin. Parents tended to be highly educated, with a
-highest level of education reported as high school (n = 5), some college
-(n = 6), four-year college (n = 14), some graduate school (n = 1),
-completed graduate school (n = 28) or declined to state (n=6).
+participants (n = 37) had been exposed to 2 or more languages as
+indicated by their parent. Parents identified their children as White (n
+= 25), Asian (n = 11), African American/Black (n = 2), Biracial (n =
+12), other (n = 5), or declined to state (n = 5). Fifteen parents
+reported their child was of Hispanic origin. Parents tended to be highly
+educated, with a highest level of education reported as high school (n =
+5), some college (n = 6), four-year college (n = 14), some graduate
+school (n = 1), completed graduate school (n = 28) or declined to state
+(n = 6).
 
@@
 establish reliability. The two coders achieved reliability with ICC =
-0.80 with 95\% confident interval = 0.57-0.92 (p\textless{}0.05) for
+0.80 with 95\% confident interval = 0.57-0.92 (p \textless{} 0.05) for
 number of parent bids; ICC = 0.20 with 95\% confident interval =
 -0.26-0.58 for number of passive joint attention established; ICC = 0.66
-with 95\% confident interval = 0.32-0.85 (p\textless{}0.05) for number
+with 95\% confident interval = 0.32-0.85 (p \textless{} 0.05) for number
 of coordinated joint attention established; ICC = 0.24 with 95\%
 confident interval = -0.21-0.61 for length of passive joint attention,
-and ICC = 0.62 with 95\% confident interval = 0.27-0.83
-(p\textless{}0.05) for length of passive joint attention.
+and ICC = 0.62 with 95\% confident interval = 0.27-0.83 (p \textless{}
+0.05) for length of passive joint attention.
 

### 2019-02-27 parenting_obs_e2/joint_attention/parenting_obs_JA.Rmd
add JA data and info data

--- 2019-02-09 parenting_obs_e1/joint_attention/parenting_obs_JA.Rmd
@@
 ---
-title: "Parenting Observational Study"
-author: "Emily"
+title: "Parenting Observational Study E2"
+author: "Emily, Vivian"
 date: "`r Sys.Date()`"
@@
 
-  id <- data.frame(SID = SID,
+  id <- data.frame(sid = SID,
                    line = line,
@@
 
+  # Only count the JA more than 3 seconds
   l_pja <- id%>%
     mutate(phase_length = phase_offset - phase_onset)%>%
-    filter(pja == 1)%>%
-    group_by(SID, pja)%>%
-    summarise(pja_length = sum(phase_length))%>%
+    filter((phase_length >3000)&(pja == 1))%>%
+    group_by(sid, pja)%>%
+    summarise(pja_length = sum(as.numeric(phase_length)))%>%
     select(-pja)
@@
     mutate(phase_length = phase_offset - phase_onset)%>%
-    filter(cja == 1)%>%
-    group_by(SID, cja)%>%
-    summarise(cja_length = sum(phase_length))%>%
+    filter((phase_length >3000)&(cja == 1))%>%
+    group_by(sid, cja)%>%
+    summarise(cja_length = sum(as.numeric(phase_length)))%>%
     select(-cja)
@@
   c_pja <- id%>%
-    group_by(SID)%>%
-    summarise(pja = sum(pja))
+    mutate(phase_length = phase_offset - phase_onset)%>%
+    filter(phase_length >3000)%>%
+    group_by(sid)%>%
+    summarise(pja = sum(as.numeric(pja)))
 
   c_cja <- id%>%
-    group_by(SID)%>%
-    summarise(cja = sum(cja))
+    mutate(phase_length = phase_offset - phase_onset)%>%
+    filter(phase_length >3000)%>%
+    group_by(sid)%>%
+    summarise(cja = sum(as.numeric(cja)))
 
   c_bids <- id%>%
-    group_by(SID)%>%
-    summarise(bids = sum(bid))
+    group_by(sid)%>%
+    summarise(bids = sum(as.numeric(bid)))
 
@@
 
-Read in trial info and demographics.
-
+Read in trial info 
 ```{r}
 conditions <- read.csv("conditions.csv")
-
-load("../paq/paq_demo.RData")
-load("../paq/obs_demo.RData")
-
-ids <- ids%>%
-  mutate(SID = sid)%>%
-  select(-sid)
-
-demo <- demo%>%
-  mutate(SID = sid)%>%
-  select(-sid)%>%
-  mutate(age_months = age * 12)
-
-demo$age_group[demo$age_months < 12] <- "6"
-demo$age_group[demo$age_months >= 12 & demo$age_months < 18 ] <- "12"
-demo$age_group[demo$age_months >= 18] <- "18"
 
@@
 Next time, code all parent bids rather than only unsuccessful ones.
-d <- d.raw %>%
-  left_join(conditions)%>%
-  mutate(bids_tot = bids + cja + pja)%>%
-  left_join(demo)%>%
-  left_join(ids)%>%
-  select(-sid)
-```
 
-#Demographics
-
-```{r}
-demos <- conditions%>%
-  left_join(demo)
-
-demos$parent_ed[demos$parent_ed == 1] <- 8
-demos$parent_ed[demos$parent_ed == 2] <- 12
-demos$parent_ed[demos$parent_ed == 3] <- 14
-demos$parent_ed[demos$parent_ed == 4] <- 18
-demos$parent_ed[demos$parent_ed == 5] <- 20
-demos$parent_ed[demos$parent_ed == 6] <- 22
-
-#child gender
-table(demos$Condition, demos$gender)
-#ethnicity
-table(demos$Condition, demos$ethnicity)
-#years of education
-table(demos$Condition, demos$parent_ed)
+d <- left_join(d.raw, conditions, by = "sid")
+d$condition [d$sid=="111517_3"] = "exp"
+d$video [d$sid=="111517_3"] = "big_small"
+d$age [d$sid=="111517_3"] = "2"
 ```
@@
     mutate(phase_length = phase_offset - phase_onset)%>%
-    filter(pja == 1)%>%
-    group_by(SID, pja)%>%
-    summarise(pja_length = sum(phase_length))%>%
+    filter((phase_length >3000)&(pja == 1))%>%
+    group_by(sid, pja)%>%
+    summarise(pja_length = sum(as.numeric(phase_length)))%>%
     select(-pja)
@@
   c_pja <- id%>%
-    group_by(SID)%>%
-    summarise(pja = sum(pja))
+    mutate(phase_length = phase_offset - phase_onset)%>%
+    filter(phase_length >3000)%>%
+    group_by(sid)%>%
+    summarise(pja = sum(as.numeric(pja)))
 
   c_cja <- id%>%
-    group_by(SID)%>%
-    summarise(cja = sum(cja))
+    mutate(phase_length = phase_offset - phase_onset)%>%
+    filter(phase_length >3000)%>%
+    group_by(sid)%>%
+    summarise(cja = sum(as.numeric(cja)))
 
   c_bids <- id%>%
-    group_by(SID)%>%
+    group_by(sid)%>%
     summarise(bids = sum(bid))
@@
   mutate(bids_rel = bids, pja_rel = pja, cja_rel = cja, l_pja_rel = pja_length, l_cja_rel = cja_length)%>%
-  select(SID, bids_rel, pja_rel, cja_rel, l_cja_rel, l_pja_rel)
+  select(sid, bids_rel, pja_rel, cja_rel, l_cja_rel, l_pja_rel)
 
@@
 ```{r, width=4, height=4}
-save(d, file="Exp1_joint_attention_data.RData")
+save(d, file="Exp2_joint_attention_data.RData")
 ms_bids <- d %>%
-  group_by(Condition) %>%
-  multi_boot_standard(col = "bids_tot")
+  group_by(condition) %>%
+  multi_boot_standard(col = "bids")
 
-ms_bids$Condition <- factor(ms_bids$Condition,
+ms_bids$condition <- factor(ms_bids$condition,
 levels = c("con", "exp"),
@@
 
-ggplot(ms_bids, aes(x = Condition, y = mean, fill = Condition)) + 
+ggplot(ms_bids, aes(x = condition, y = mean, fill = condition)) + 
   geom_bar(stat="identity") + 
@@
 ms_tja <- d %>%
-  group_by(Condition) %>%
+  group_by(condition) %>%
   multi_boot_standard(col = "total_ja")
 
-ms_tja$Condition <- factor(ms_tja$Condition,
+ms_tja$Condition <- factor(ms_tja$condition,
 levels = c("con", "exp"),
@@
 
-ggplot(ms_tja, aes(x = Condition, y = mean, fill = Condition)) + 
+ggplot(ms_tja, aes(x = condition, y = mean, fill = condition)) + 
   geom_bar(stat="identity") + 
@@
 ms_pja <- d %>%
-  group_by(Condition) %>%
+  group_by(condition) %>%
   multi_boot_standard(col = "pja")
 
-ggplot(ms_pja, aes(x = Condition, y = mean, fill = Condition)) + 
+ggplot(ms_pja, aes(x = condition, y = mean, fill = condition)) + 
   geom_bar(stat="identity") + 
@@
 ms_cja <- d %>%
-  group_by(Condition) %>%
+  group_by(condition) %>%
   multi_boot_standard(col = "cja")
 
-ggplot(ms_cja, aes(x = Condition, y = mean, fill = Condition)) + 
+ggplot(ms_cja, aes(x = condition, y = mean, fill = condition)) + 
   geom_bar(stat="identity") + 
@@
 ms_lpja <- d %>%
-  filter(!is.na(Condition))%>%
-  group_by(Condition) %>%
+  filter(!is.na(condition))%>%
+  group_by(condition) %>%
   multi_boot_standard(col = "pja_length")
 
-ggplot(ms_lpja, aes(x = Condition, y = mean, fill = Condition)) + 
+ggplot(ms_lpja, aes(x = condition, y = mean, fill = condition)) + 
   geom_bar(stat="identity") + 
@@
 ms_lcja <- d %>%
-  filter(!is.na(Condition))%>%
-  group_by(Condition) %>%
+  filter(!is.na(condition))%>%
+  group_by(condition) %>%
   multi_boot_standard(col = "cja_length")
 
-ggplot(ms_lcja, aes(x = Condition, y = mean, fill = Condition)) + 
+ggplot(ms_lcja, aes(x = condition, y = mean, fill = condition)) + 
   geom_bar(stat="identity") + 

### 2019-02-28 paper/cogsci2019/cogsci2019.Rmd
working on E1 results and intro

@@
     Department of Psychology, Stanford University \\ 
-    Palo Alto, CA 94301 USA}
+    Stanford, CA 94305 USA}
 
@@
     outcomes of young children [@Hart1995; @Heckman2006]. 
-    In particular, high quality early interactions and early language input appear to 
-    facilitate more effective language learning and higher levels of school performance. 
-    The rise in electronic parenting applications ("apps") holds the promise of delivering 
+    In particular, high-quality early interactions and language input appear to 
+    facilitate language learning and result in higher levels of school performance. 
+    The rise of phone- and tablet-based parenting applications ("apps") holds the promise of delivering 
     low-cost, positive interventions on parenting style to a variety of different populations. 
@@
     Yet little is known about the effects of communicating to parents through app-based interventions.
-    MTLD, types and tokens, joint attention, proportion of nouns/verbs/adjectives, 
-    affect, concreteness, mean length of utterance...
+    In a study of one commercial app offering a collection of age-appropriate activity videos, we find 
+    that the quality of parent-child interactions increases in some ways as a result of using the app. 
+    Specifically, the lexical diversity of parents' child-directed speech increases, and measures of 
+    joint attention show...
 
@@
 
-Children spend a large portion of their waking time at play in their environment.
-Playing with objects may allow them to discover hidden features, as well as to build a causal understanding of how the objects interact. 
-Beyond learning object features, the laws of physics, and causal relationships [e.g., @Schulz2007], during play children practice motor skills that help them effectively navigate their world [@Singer2006].
-Social play can help children learn about human relationships, both through imitation of adult behaviors and by experiencing and learning to process emotional events [@Singer2006].
+Young children spend a large portion of their waking time at play, variously manipulating objects, exploring their environment, and interacting with caregivers and peers.
+Playing with objects allows them to discover hidden object properties and relations, and to build a causal understanding of how objects interact [e.g., @Schulz2007]. 
+Meanwhile, play also gives children an opportunity to set and achieve goals (e.g., build a tower) and to practice a wide range of motor skills (e.g., stacking) that will help them navigate the world [@Singer2006].
+Social play can help children learn about human relationships, both through imitation of adult behaviors and by experiencing and learning to process emotional events such as failures [@Singer2006].
+Of course, young children are rarely playing in isolation: caregivers often provide encouragement and guidance while scaffolding a child's play [@Kaye1970; @Wood1976]. 
+Early parenting practices have been shown to play an important role in shaping the future outcomes of young children [@Hart1995; @Heckman2006]. 
+While many interventions have trouble reaching the parents of very young children, digital delivery of parenting advice by way of
 
@@
 These tutorial interactions have been shown to be important components of child development [@Wood1976].
-Thus, with the knowledge of both play and tutorial interactions, guided play, which consists of both active and enjoyable activities as well as close guidance of adults [@Hirsh2008]
-has drawn researchers' interest. 
-A study on preschoolers by Weisberg showed that guided play scaffolds the environment while still allowing children to maintain a large degree of control, 
+Thus, with the knowledge of both play and tutorial interactions, guided play, which consists of both active and enjoyable activities as well as close guidance of adults [@Hirsh2008] has drawn researchers' interest.
+A study of preschoolers showed that guided play scaffolds the environment while still allowing children to maintain a large degree of control, 
 and it outperforms direct-instruction approaches in encouraging a variety of positive academic outcomes [@Weisberg2013].
-Another study by Massey specifically found that guided play could facilitate children's vocabulary and comprehensive language development and subsequent literacy skills [@Massey2013].
+Another study found that guided play could facilitate children's vocabulary and comprehensive language development and subsequent literacy skills [@Massey2013].
 
@@
 They showed that parents in experimental group have greater knowledge of language development and this effect sustained four months after the intervention. 
-However, more interactive outcomes, like adult word tokens, conversational turn counts, and child vocalization counts, 
-though increased significantly during the experiment,
-did not sustain after the intervention [@Suskind2015].
+However, although a number of interactive measures increased during the experiment, including the number of word tokens, conversational turns, and child vocalizations, these increases did not sustain after the intervention [@Suskind2015].
 That changes did not sustain could be due to the intervention itself,
@@
 ## Effectiveness of Digital Delivery
-With the development of technology, digitally-delivered methods could address some logistic barriers to face-to-face delivery methods. 
-Breitenstein has reviewed 11 studies on them and showed good promise for the efficacy of interventions using digitally-delivered methods [@Breitenstein2014].
+With the widespread use of smartphones and tablets worldwide, digitally-delivered interventions could address many of the logistical barriers that have limited scaling up face-to-face delivery methods.
+A review of 11 studies verified that digital delivery is a promising means of effectively distributing interventions [@Breitenstein2014].
 However, the parent and child outcomes assessed in the review (e.g.infant positive behaviors, satisfaction, emotional symptoms etc.) did not address the nature or quality of parent-infant interactions at a detailed level,
 like if the interventions lead to children paying more attention, or vocabulary changes in parents' language usages. 
-Although digitally-delivered ac-tivities are designed to promote learning and cognitive devel-opment, it is unclear how they might affect these dimensions of parent-child interactions.
+Although digitally-delivered ac-tivities are designed to promote learning and cognitive development, it is unclear how they might affect these dimensions of parent-child interactions.
 Thus, we want to conduct this experiment to explore if and how digital scaffolding of activities affect the social and linguistic characteristics of parent-child ineractions.
@@
 Parents in the control group did not watch a Kinedu video, instead they were given the same props and were told to play with their infants as they would at home.
-We found that compared to the control group, parents who watched a Kinedu video spoke more words overall, but had lower lexical diversity. 
-They also made more bids for joint attention with their infants, although these bids did not result in more episodes of joint attention compared to the control group. 
-In summary, following digitally-scaffolded activities may cause parents to engage with and speak more to children overall, but speak more repetitively.
 
@@
 
-```{r, echo=F}
+```{r, include=F}
 e1path = "../../parenting_obs_e1/"
@@
 We included infants who were exposed to English at least 50 percent of the time (n = 58) or who were exposed less but whose participating parent reported that they primarily speak English with their child at home (n = 2).
-Sixty-one% of participants (n = 37) had been exposed to 2 or more languages as indicated by their parent.
+Sixty-one% of participants (n = 37) had been exposed to two or more languages as indicated by their parent. 
 Parents identified their children as White (n = 25), Asian (n = 11), African American/Black (n = 2), Biracial (n = 12), other (n = 5), or declined to state (n = 5). 
 Fifteen parents reported their child was of Hispanic origin. 
-Parents tended to be highly educated, with a highest level of education reported as high school (n = 5), some college (n = 6), four-year college (n = 14), some graduate school (n = 1), completed graduate school (n = 28) or declined to state (n = 6).
+Parents tended to be highly-educated, with reports of highest level of education ranging from completed high school (n = 5), some college (n = 6), four-year college (n = 14), some graduate school (n = 1), to completed graduate school (n = 28) or declined to state (n = 6).
 
 ### Materials.
-Stimuli included videos from a commercial parenting application, Kinedu Inc. 
-The videos were designed to show activities parents could perform with their child to foster cognitive and physical development, and were targeted to the child's age and development. 
+Stimuli included videos from the Kinedu (Kinedu Inc.) commercial parenting application. 
+The videos were designed to show activities to parents that they could perform with their child in order to foster cognitive and physical development, and were targeted to the child's age and level of development.
 In each video, an adult and child perform the activity while a narrator explains the activity and its purpose. 
@@
 More information about the specific videos is available in the Appendix. 
-Participants were also given a set of props corresponding to those in the video they watched, so that they could complete the activity. 
+Participants were also given a set of props corresponding to those in the video they watched so that they could complete the activity. 
 The props associated with each video are listed in the Appendix.
@@
 Participants were randomly assigned to either the *Video* condition or the *Control* condition. 
-Participants in the Activity Video condition were assigned to one of the two videos available for their child's age group. 
-The No-Video Control condition was yoked to the Activity Video condition such that for every participant in the Activity Video condition who saw a particular video and received the associated props, a participant in the No-Video Control condition received the same props but did not watch the corresponding video.
+Participating parents in the Video condition were assigned to watch one of the two activity videos available for their child's age group. 
+Participating parents in the Control condition watched no activity video, and were merely asked to play with their child as they normally would.
+The Control condition was yoked to the Activity Video condition such that for every participant in the Video condition who saw a particular video and received the associated props, a participant in the Control condition received the same props but did not watch the activity video.
 Parents also completed the Parenting Attitudes Questionnaire (PAQ). 
@@
 ## Procedure.
-After providing informed consent, parents in the Activity Video condition watched the assigned video on a laptop with headphones.
+After providing informed consent, parents in the Video condition watched the assigned activity video on a laptop with headphones.
 To ensure that parents could give the video their full attention, the experimenter played with the infant with a set of toys (different from the experimental props used in the study) while the video was being played.
@@
 The toys were placed on a large foam mat, and parents were instructed to sit on the mat with their child and re-create the activity they had viewed for a period of three minutes.
-In the No-Video control condition, after consenting parents were told to play with their child as they would at home with the provided props for a period of three minutes. 
+In the Control condition, after consenting parents were told to play with their child as they would at home with the provided props for a period of three minutes. 
 They were not given any additional instructions about how to use the props.
 
-In both conditions, two video cameras were used to record the play session from different angles, and parents were fitted with a wireless audio recorder to record their speech to their child. 
+In both conditions, two video cameras were used to record the play session from different angles, and parents were fitted with a wireless audio recorder to record their child-directed speech. 
 After three minutes of play had elapsed, parents were told they could stop playing and cameras and audio were turned off.
@@
 ### Joint Attention Coding Procedure.
-The video of each session was manually coded for episodes of joint attention using the Datavyu software. 
-The video taken at floor level was coded by default, but the other video was referred to if the participants were not visible or if there was a technological error with the first camera. 
-For each participant we coded for episodes of coordinated joint attention, episodes of passive joint attention, and parental bids for joint attention. 
-We defined parental bids for joint attention as any attempt to initiate joint attention (i.e label, point, or otherwise draw attention to an object) that does not result in passive or coordinated joint attention.
+The video of each session was manually coded for episodes of joint attention using the Datavyu software [@datavyu]. 
+The video taken at floor level was coded by default, but the other video was referred to if the participants were not visible or if there was technical difficulty with the first camera. 
+Each session's video was coded for episodes of coordinated joint attention, episodes of passive joint attention, and parental bids for joint attention. 
+Parental bids for joint attention were defined as any attempt to initiate joint attention (i.e labeling, pointing, or otherwise drawing attention to an object) that did not result in passive or coordinated joint attention.
 If more than 3 seconds elapsed between bids, they were coded as separate attempts. 
@@
 A second coder independently coded a third of the videos (i.e., 20 of the 60 videos, approximately equally distributed across ages) to establish reliability. 
-The two coders achieved reliability with ICC = 0.80 with 95% confident interval = 0.57-0.92 (p < 0.05) for number of parent bids; ICC = 0.20 with 95% confident interval = -0.26-0.58 for number of passive joint attention established; ICC = 0.66 with 95% confident interval = 0.32-0.85 (p < 0.05) for number of coordinated joint attention established; ICC = 0.24 with 95% confident interval = -0.21-0.61 for length of passive joint attention, and ICC = 0.62 with 95% confident interval = 0.27-0.83 (p < 0.05) for length of passive joint attention.
+The two coders had a reliability of ICC = 0.80 with 95% confident interval (CI) = [0.57,0.92] (p < 0.05) for number of parent bids for JA; ICC = 0.20 with 95% CI = [-0.26,0.58] for number of passive JA episodes; ICC = 0.66 with 95% CI = [0.32,0.85] (p < 0.05) for number of coordinated JA episodes; ICC = 0.24 with 95% CI = [-0.21,0.61] for total duration of passive JA episodes, and ICC = 0.62 with 95% CI = [0.27,0.83] (p < 0.05) for total duration of passive (coordinated??) JA episodes.
 
@@
 
-The data was analyzed according to our preregistration: [link](https://osf.io/2bpdf/).
+The transcripts and hand-coded behavioral data was analyzed according to our preregistration[^1].
+Below we first describe the lexical diversity results, followed by the joint attention results.
+
+[^1]: Preregistration: [https://osf.io/2bpdf/](https://osf.io/2bpdf/)]
 
@@
 
-We first calculated Type/Token Ratio (TTR) for each transcript. ..
-
-Fig 1 - TTR, maybe also Total Tokens and Total Types (if subfigures fit)
-(otherwise a table with mean and SD of tokens, types, and TTR)
-However, note that TTR is a measure that is correlated with the length of a text. ... 
-MTLD is a better measure of lexical diversity [@McCarthy2010].
+Parents' child-directed speech during the play sessions was transcribed.
+For each transcript, the words were lemmatized using @spacy2, and the word *types* (unique words) and *tokens* (total words) were then tallied and the type-token ratio (TTR) calculated as a measure of lexical diversity.
+Although TTR was our preregistered measure of lexical diversity, TTR is correlated with the length of a text, whereas the measure of textual lexical diversity (MTLD) is not [@McCarthy2010]. 
+Thus, we also measure lexical diversity with MTLD, which is calculated as the mean length of sequential word strings in a text that maintain a given TTR value (here, .720).
 
@@
 # Predicting lexical diversity based on experimental condition, PAQ, demographics. 
-maximal_mod <- lmer(MTLD ~ condition + age + gender + parent_ed + (1| video), data = lmer_data)
-summary(maximal_mod)
+modTTR <- lmer(TTR ~ condition + age + gender + parent_ed + (1|video), data=lmer_data)
+summary(modTTR) #
 
-# predict word tokesn
-tokens_mod <- lmer(tokens ~ condition*EL + condition*AA + condition*RR + age + gender + parent_ed + (1| video), 
-                         data = lmer_data)
-summary(tokens_mod)
+modMTLD <- lmer(MTLD ~ condition + age + gender + parent_ed + (1|video), data=lmer_data)
+summary(modMTLD)
+
+# predict word tokens
+tokens_mod <- lmer(tokens ~ condition*EL + condition*AA + condition*RR + age + gender + parent_ed + (1|video),  data=lmer_data)
+summary(tokens_mod) # condition *
 
 # predict word types
-types_mod <- lmer(types ~ condition*EL + condition*AA + condition*RR  + age + gender + parent_ed + (1| video), 
-                         data = lmer_data)
+types_mod <- lmer(types ~ condition*EL + condition*AA + condition*RR  + age + gender + parent_ed + (1|video), data=lmer_data)
 summary(types_mod)
@@
 
-```{r e1lex_div, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.5, fig.height=3.0, set.cap.width=T, num.cols.cap=1, fig.cap = "Mean lexical diversity scores by condition (left: Type/Token ratio, right: MTLD) in Experiment 1."}
+We fit a mixed-effects linear regression predicting TTR as a function of condition, age (scaled and 0-centered), gender, and parent's education level with a random intercept per video using lme4 [@lme4].
+There was significantly lower TTR in the Video condition (mean: 0.32) than in the Control condition (mean: 0.43, $\beta=-.12$, t(39.9) = 4.25, *p*<.001). 
+There were no significant effects of age, gender, or parent's level of education.
+A similar mixed-effects linear regression instead predicting MTLD also found significantly lower lexical diversity in the Video condition (mean: 15.7) than in the Control condition (mean: 21.9, $\beta=-11.67$, t(43) = 3.08, *p*<.01), with no other significant effects.
+Figure 1 shows the mean of each lexical diversity measure (TTR and MTLD) by condition.
+
+We also conducted similar regressions predicting the number of word tokens and types, finding only a significant effect of condition on the number of word tokens ($\beta=57.23$, t(34.4)=2.19, *p*<.05), with parents using more words in the Video condition (mean: 225, 95% CI: [197,252]) than in the Control condition (mean: 165, 95% CI: [139,193]).
+
+(Table with mean and SD of tokens, types, and TTR)
+
+```{r e1lex_div, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.5, fig.height=3.0, set.cap.width=T, num.cols.cap=1, fig.cap = "Mean lexical diversity scores by condition (left: Type/Token ratio, right: MTLD) in Experiment 1.
+Error bars show bootstrapped 95 percent confidence intervals (CIs)."}
 d$Condition = factor(d$condition, levels = c("con", "exp"), labels = c("Control", "Video"))
@@
 
+Experiment 1 found that compared to parents who did not watch a video, parents who watched a Kinedu video spoke more words overall, but had lower lexical diversity. 
+Parents who watched a video also made more bids for joint attention, although these bids did not result in more episodes of joint attention compared to the control group. 
 In Experiment 2 we attempt to replicate the findings from Experiment 1 with a restricted number of preregistered predictions. 
@@
 
-## Footnotes
-
-Indicate footnotes with a number\footnote{Sample of the first
-footnote.} in the text. You can also use 
-markdown formatting to include footnotes using this syntax [^1].
-
-[^1]: Sample of a markdown footnote.
-
 ## Two-column images

### 2019-02-28 paper/cogsci2019/cogsci2019.tex
working on E1 results and intro

@@
 
-\author{{\large\bf Hanwen Vivian~Zhang} (\texttt{vivian3@stanford.edu}) \\ {\large\bf George~Kachergis} (\texttt{george.kachergis@gmail.com}) \\ {\large\bf Michael C.~Frank} (\texttt{mcfrank@stanford.edu}) \\  Department of Psychology, Stanford University \\  Palo Alto, CA 94301 USA}
+\author{{\large\bf Hanwen Vivian~Zhang} (\texttt{vivian3@stanford.edu}) \\ {\large\bf George~Kachergis} (\texttt{george.kachergis@gmail.com}) \\ {\large\bf Michael C.~Frank} (\texttt{mcfrank@stanford.edu}) \\  Department of Psychology, Stanford University \\  Stanford, CA 94305 USA}
 
@@
 outcomes of young children (Hart \& Risley, 1995; Heckman, 2006). In
-particular, high quality early interactions and early language input
-appear to facilitate more effective language learning and higher levels
-of school performance. The rise in electronic parenting applications
+particular, high-quality early interactions and language input appear to
+facilitate language learning and result in higher levels of school
+performance. The rise of phone- and tablet-based parenting applications
 (``apps'') holds the promise of delivering low-cost, positive
@@
 often difficult to reach in other ways. Yet little is known about the
-effects of communicating to parents through app-based interventions.
-MTLD, types and tokens, joint attention, proportion of
-nouns/verbs/adjectives, affect, concreteness, mean length of
-utterance\ldots{}
+effects of communicating to parents through app-based interventions. In
+a study of one commercial app offering a collection of age-appropriate
+activity videos, we find that the quality of parent-child interactions
+increases in some ways as a result of using the app. Specifically, the
+lexical diversity of parents' child-directed speech increases, and
+measures of joint attention show\ldots{}
 
@@
 
-Children spend a large portion of their waking time at play in their
-environment. Playing with objects may allow them to discover hidden
-features, as well as to build a causal understanding of how the objects
-interact. Beyond learning object features, the laws of physics, and
-causal relationships (e.g., Schulz \& Bonawitz, 2007), during play
-children practice motor skills that help them effectively navigate their
-world (Singer, Golinkoff, \& Hirsh-Pasek, 2006). Social play can help
-children learn about human relationships, both through imitation of
-adult behaviors and by experiencing and learning to process emotional
-events (Singer et al., 2006).
+Young children spend a large portion of their waking time at play,
+variously manipulating objects, exploring their environment, and
+interacting with caregivers and peers. Playing with objects allows them
+to discover hidden object properties and relations, and to build a
+causal understanding of how objects interact (e.g., Schulz \& Bonawitz,
+2007). Meanwhile, play also gives children an opportunity to set and
+achieve goals (e.g., build a tower) and to practice a wide range of
+motor skills (e.g., stacking) that will help them navigate the world
+(Singer, Golinkoff, \& Hirsh-Pasek, 2006). Social play can help children
+learn about human relationships, both through imitation of adult
+behaviors and by experiencing and learning to process emotional events
+such as failures (Singer et al., 2006). Of course, young children are
+rarely playing in isolation: caregivers often provide encouragement and
+guidance while scaffolding a child's play (Kaye, 1970; Wood, Bruner, \&
+Ross, 1976). Early parenting practices have been shown to play an
+important role in shaping the future outcomes of young children (Hart \&
+Risley, 1995; Heckman, 2006). While many interventions have trouble
+reaching the parents of very young children, digital delivery of
+parenting advice by way of
 
@@
 1980). These tutorial interactions have been shown to be important
-components of child development (Wood, Bruner, \& Ross, 1976). Thus,
-with the knowledge of both play and tutorial interactions, guided play,
-which consists of both active and enjoyable activities as well as close
+components of child development (Wood et al., 1976). Thus, with the
+knowledge of both play and tutorial interactions, guided play, which
+consists of both active and enjoyable activities as well as close
 guidance of adults (Hirsh-Pasek \& Golinkoff, 2008) has drawn
-researchers' interest. A study on preschoolers by Weisberg showed that
-guided play scaffolds the environment while still allowing children to
-maintain a large degree of control, and it outperforms
-direct-instruction approaches in encouraging a variety of positive
-academic outcomes (Weisberg, Hirsh-Pasek, \& Golinkoff, 2013). Another
-study by Massey specifically found that guided play could facilitate
-children's vocabulary and comprehensive language development and
-subsequent literacy skills (Massey, 2013).
+researchers' interest. A study of preschoolers showed that guided play
+scaffolds the environment while still allowing children to maintain a
+large degree of control, and it outperforms direct-instruction
+approaches in encouraging a variety of positive academic outcomes
+(Weisberg, Hirsh-Pasek, \& Golinkoff, 2013). Another study found that
+guided play could facilitate children's vocabulary and comprehensive
+language development and subsequent literacy skills (Massey, 2013).
 
@@
 experimental group have greater knowledge of language development and
-this effect sustained four months after the intervention. However, more
-interactive outcomes, like adult word tokens, conversational turn
-counts, and child vocalization counts, though increased significantly
-during the experiment, did not sustain after the intervention (D. L.
-Suskind et al., 2015). That changes did not sustain could be due to the
-intervention itself, or could merely be that the methods of
-home-visiting is not sustainable enough for parents to easily and
-constantly get parenting advice. Thus, new methods of delivering
+this effect sustained four months after the intervention. However,
+although a number of interactive measures increased during the
+experiment, including the number of word tokens, conversational turns,
+and child vocalizations, these increases did not sustain after the
+intervention (D. L. Suskind et al., 2015). That changes did not sustain
+could be due to the intervention itself, or could merely be that the
+methods of home-visiting is not sustainable enough for parents to easily
+and constantly get parenting advice. Thus, new methods of delivering
 parenting advice should be considered.
@@
 
-With the development of technology, digitally-delivered methods could
-address some logistic barriers to face-to-face delivery methods.
-Breitenstein has reviewed 11 studies on them and showed good promise for
-the efficacy of interventions using digitally-delivered methods
-(Breitenstein, Gross, \& Christophersen, 2014). However, the parent and
-child outcomes assessed in the review (e.g.infant positive behaviors,
-satisfaction, emotional symptoms etc.) did not address the nature or
-quality of parent-infant interactions at a detailed level, like if the
-interventions lead to children paying more attention, or vocabulary
-changes in parents' language usages. Although digitally-delivered
-ac-tivities are designed to promote learning and cognitive devel-opment,
-it is unclear how they might affect these dimensions of parent-child
-interactions. Thus, we want to conduct this experiment to explore if and
-how digital scaffolding of activities affect the social and linguistic
+With the widespread use of smartphones and tablets worldwide,
+digitally-delivered interventions could address many of the logistical
+barriers that have limited scaling up face-to-face delivery methods. A
+review of 11 studies verified that digital delivery is a promising means
+of effectively distributing interventions (Breitenstein, Gross, \&
+Christophersen, 2014). However, the parent and child outcomes assessed
+in the review (e.g.infant positive behaviors, satisfaction, emotional
+symptoms etc.) did not address the nature or quality of parent-infant
+interactions at a detailed level, like if the interventions lead to
+children paying more attention, or vocabulary changes in parents'
+language usages. Although digitally-delivered ac-tivities are designed
+to promote learning and cognitive development, it is unclear how they
+might affect these dimensions of parent-child interactions. Thus, we
+want to conduct this experiment to explore if and how digital
+scaffolding of activities affect the social and linguistic
 characteristics of parent-child ineractions. The quality of parent-child
@@
 were given the same props and were told to play with their infants as
-they would at home. We found that compared to the control group, parents
-who watched a Kinedu video spoke more words overall, but had lower
-lexical diversity. They also made more bids for joint attention with
-their infants, although these bids did not result in more episodes of
-joint attention compared to the control group. In summary, following
-digitally-scaffolded activities may cause parents to engage with and
-speak more to children overall, but speak more repetitively.
+they would at home.
 
 \subsection{Method}\label{method}
-
-\begin{CodeChunk}
-\begin{CodeOutput}
-[1] 45
-\end{CodeOutput}
-\end{CodeChunk}
 
@@
 primarily speak English with their child at home (n = 2). Sixty-one\% of
-participants (n = 37) had been exposed to 2 or more languages as
+participants (n = 37) had been exposed to two or more languages as
 indicated by their parent. Parents identified their children as White (n
@@
 12), other (n = 5), or declined to state (n = 5). Fifteen parents
-reported their child was of Hispanic origin. Parents tended to be highly
-educated, with a highest level of education reported as high school (n =
-5), some college (n = 6), four-year college (n = 14), some graduate
-school (n = 1), completed graduate school (n = 28) or declined to state
-(n = 6).
+reported their child was of Hispanic origin. Parents tended to be
+highly-educated, with reports of highest level of education ranging from
+completed high school (n = 5), some college (n = 6), four-year college
+(n = 14), some graduate school (n = 1), to completed graduate school (n
+= 28) or declined to state (n = 6).
 
@@
 
-Stimuli included videos from a commercial parenting application, Kinedu
-Inc. The videos were designed to show activities parents could perform
-with their child to foster cognitive and physical development, and were
-targeted to the child's age and development. In each video, an adult and
-child perform the activity while a narrator explains the activity and
-its purpose. We selected two videos for each of three age groups in our
-sample (6-11.9 months, 12-17.9 months, 18-23.94 months). More
-information about the specific videos is available in the Appendix.
-Participants were also given a set of props corresponding to those in
-the video they watched, so that they could complete the activity. The
-props associated with each video are listed in the Appendix.
+Stimuli included videos from the Kinedu (Kinedu Inc.) commercial
+parenting application. The videos were designed to show activities to
+parents that they could perform with their child in order to foster
+cognitive and physical development, and were targeted to the child's age
+and level of development. In each video, an adult and child perform the
+activity while a narrator explains the activity and its purpose. We
+selected two videos for each of three age groups in our sample (6-11.9
+months, 12-17.9 months, 18-23.94 months). More information about the
+specific videos is available in the Appendix. Participants were also
+given a set of props corresponding to those in the video they watched so
+that they could complete the activity. The props associated with each
+video are listed in the Appendix.
 
 Participants were randomly assigned to either the \emph{Video} condition
-or the \emph{Control} condition. Participants in the Activity Video
-condition were assigned to one of the two videos available for their
-child's age group. The No-Video Control condition was yoked to the
-Activity Video condition such that for every participant in the Activity
-Video condition who saw a particular video and received the associated
-props, a participant in the No-Video Control condition received the same
-props but did not watch the corresponding video. Parents also completed
+or the \emph{Control} condition. Participating parents in the Video
+condition were assigned to watch one of the two activity videos
+available for their child's age group. Participating parents in the
+Control condition watched no activity video, and were merely asked to
+play with their child as they normally would. The Control condition was
+yoked to the Activity Video condition such that for every participant in
+the Video condition who saw a particular video and received the
+associated props, a participant in the Control condition received the
+same props but did not watch the activity video. Parents also completed
 the Parenting Attitudes Questionnaire (PAQ). The PAQ measures parents'
@@
 
-After providing informed consent, parents in the Activity Video
-condition watched the assigned video on a laptop with headphones. To
-ensure that parents could give the video their full attention, the
-experimenter played with the infant with a set of toys (different from
-the experimental props used in the study) while the video was being
-played. Immediately following the video, each parent-child dyad was
-provided with the props to complete the activity they had viewed. The
-toys were placed on a large foam mat, and parents were instructed to sit
-on the mat with their child and re-create the activity they had viewed
-for a period of three minutes. In the No-Video control condition, after
-consenting parents were told to play with their child as they would at
-home with the provided props for a period of three minutes. They were
-not given any additional instructions about how to use the props.
+After providing informed consent, parents in the Video condition watched
+the assigned activity video on a laptop with headphones. To ensure that
+parents could give the video their full attention, the experimenter
+played with the infant with a set of toys (different from the
+experimental props used in the study) while the video was being played.
+Immediately following the video, each parent-child dyad was provided
+with the props to complete the activity they had viewed. The toys were
+placed on a large foam mat, and parents were instructed to sit on the
+mat with their child and re-create the activity they had viewed for a
+period of three minutes. In the Control condition, after consenting
+parents were told to play with their child as they would at home with
+the provided props for a period of three minutes. They were not given
+any additional instructions about how to use the props.
 
@@
 session from different angles, and parents were fitted with a wireless
-audio recorder to record their speech to their child. After three
+audio recorder to record their child-directed speech. After three
 minutes of play had elapsed, parents were told they could stop playing
@@
 The video of each session was manually coded for episodes of joint
-attention using the Datavyu software. The video taken at floor level was
-coded by default, but the other video was referred to if the
-participants were not visible or if there was a technological error with
-the first camera. For each participant we coded for episodes of
+attention using the Datavyu software (Team, 2014). The video taken at
+floor level was coded by default, but the other video was referred to if
+the participants were not visible or if there was technical difficulty
+with the first camera. Each session's video was coded for episodes of
 coordinated joint attention, episodes of passive joint attention, and
-parental bids for joint attention. We defined parental bids for joint
-attention as any attempt to initiate joint attention (i.e label, point,
-or otherwise draw attention to an object) that does not result in
-passive or coordinated joint attention. If more than 3 seconds elapsed
-between bids, they were coded as separate attempts. An episode of joint
-attention was considered passive if both participants visually focused
-on an object for a minimum of 3 seconds but the child did not
+parental bids for joint attention. Parental bids for joint attention
+were defined as any attempt to initiate joint attention (i.e labeling,
+pointing, or otherwise drawing attention to an object) that did not
+result in passive or coordinated joint attention. If more than 3 seconds
+elapsed between bids, they were coded as separate attempts. An episode
+of joint attention was considered passive if both participants visually
+focused on an object for a minimum of 3 seconds but the child did not
 acknowledge the parent. If either participant looked away from the
@@
 the 60 videos, approximately equally distributed across ages) to
-establish reliability. The two coders achieved reliability with ICC =
-0.80 with 95\% confident interval = 0.57-0.92 (p \textless{} 0.05) for
-number of parent bids; ICC = 0.20 with 95\% confident interval =
--0.26-0.58 for number of passive joint attention established; ICC = 0.66
-with 95\% confident interval = 0.32-0.85 (p \textless{} 0.05) for number
-of coordinated joint attention established; ICC = 0.24 with 95\%
-confident interval = -0.21-0.61 for length of passive joint attention,
-and ICC = 0.62 with 95\% confident interval = 0.27-0.83 (p \textless{}
-0.05) for length of passive joint attention.
+establish reliability. The two coders had a reliability of ICC = 0.80
+with 95\% confident interval (CI) = {[}0.57,0.92{]} (p \textless{} 0.05)
+for number of parent bids for JA; ICC = 0.20 with 95\% CI =
+{[}-0.26,0.58{]} for number of passive JA episodes; ICC = 0.66 with 95\%
+CI = {[}0.32,0.85{]} (p \textless{} 0.05) for number of coordinated JA
+episodes; ICC = 0.24 with 95\% CI = {[}-0.21,0.61{]} for total duration
+of passive JA episodes, and ICC = 0.62 with 95\% CI = {[}0.27,0.83{]} (p
+\textless{} 0.05) for total duration of passive (coordinated??) JA
+episodes.
 
@@
 
-The data was analyzed according to our preregistration:
-\href{https://osf.io/2bpdf/}{link}.
+The transcripts and hand-coded behavioral data was analyzed according to
+our preregistration\footnote{Preregistration:
+  \url{https://osf.io/2bpdf/}{]}}. Below we first describe the lexical
+diversity results, followed by the joint attention results.
 
@@
 
-We first calculated Type/Token Ratio (TTR) for each transcript. ..
+Parents' child-directed speech during the play sessions was transcribed.
+For each transcript, the words were lemmatized using Honnibal (2017),
+and the word \emph{types} (unique words) and \emph{tokens} (total words)
+were then tallied and the type-token ratio (TTR) calculated as a measure
+of lexical diversity. Although TTR was our preregistered measure of
+lexical diversity, TTR is correlated with the length of a text, whereas
+the measure of textual lexical diversity (MTLD) is not (McCarthy \&
+Jarvis, 2010). Thus, we also measure lexical diversity with MTLD, which
+is calculated as the mean length of sequential word strings in a text
+that maintain a given TTR value (here, .720).
 
-Fig 1 - TTR, maybe also Total Tokens and Total Types (if subfigures fit)
-(otherwise a table with mean and SD of tokens, types, and TTR) However,
-note that TTR is a measure that is correlated with the length of a text.
-\ldots{} MTLD is a better measure of lexical diversity (McCarthy \&
-Jarvis, 2010).
+We fit a mixed-effects linear regression predicting TTR as a function of
+condition, age (scaled and 0-centered), gender, and parent's education
+level with a random intercept per video using lme4 (Bates, Mächler,
+Bolker, \& Walker, 2015). There was significantly lower TTR in the Video
+condition (mean: 0.32) than in the Control condition (mean: 0.43,
+\(\beta=-.12\), t(39.9) = 4.25, \emph{p}\textless{}.001). There were no
+significant effects of age, gender, or parent's level of education. A
+similar mixed-effects linear regression instead predicting MTLD also
+found significantly lower lexical diversity in the Video condition
+(mean: 15.7) than in the Control condition (mean: 21.9,
+\(\beta=-11.67\), t(43) = 3.08, \emph{p}\textless{}.01), with no other
+significant effects. Figure 1 shows the mean of each lexical diversity
+measure (TTR and MTLD) by condition.
+
+We also conducted similar regressions predicting the number of word
+tokens and types, finding only a significant effect of condition on the
+number of word tokens (\(\beta=57.23\), t(34.4)=2.19,
+\emph{p}\textless{}.05), with parents using more words in the Video
+condition (mean: 225, 95\% CI: {[}197,252{]}) than in the Control
+condition (mean: 165, 95\% CI: {[}139,193{]}).
+
+(Table with mean and SD of tokens, types, and TTR)
 
@@
 
-\caption[Mean lexical diversity scores by condition (left]{Mean lexical diversity scores by condition (left: Type/Token ratio, right: MTLD) in Experiment 1.}\label{fig:e1lex_div}
+\caption[Mean lexical diversity scores by condition (left]{Mean lexical diversity scores by condition (left: Type/Token ratio, right: MTLD) in Experiment 1.
+Error bars show bootstrapped 95 percent confidence intervals (CIs).}\label{fig:e1lex_div}
 \end{figure}
@@
 
-In Experiment 2 we attempt to replicate the findings from Experiment 1
-with a restricted number of preregistered predictions. We will
-additionally include a second control condition, in which the same
-activities are described in written form, rather than being demonstrated
-in video. This manipulation will help determine what the contribution of
-the video demonstration is in producing the observed effects on
-parent-child interactions.
+Experiment 1 found that compared to parents who did not watch a video,
+parents who watched a Kinedu video spoke more words overall, but had
+lower lexical diversity. Parents who watched a video also made more bids
+for joint attention, although these bids did not result in more episodes
+of joint attention compared to the control group. In Experiment 2 we
+attempt to replicate the findings from Experiment 1 with a restricted
+number of preregistered predictions. We will additionally include a
+second control condition, in which the same activities are described in
+written form, rather than being demonstrated in video. This manipulation
+will help determine what the contribution of the video demonstration is
+in producing the observed effects on parent-child interactions.
 
@@
 
-\subsection{Footnotes}\label{footnotes}
-
-Indicate footnotes with a number\footnote{Sample of the first
-footnote.} in the text. You can also use markdown formatting to include
-footnotes using this syntax.\footnote{Sample of a markdown footnote.}
-
 \subsection{Two-column images}\label{two-column-images}
@@
 \hypertarget{refs}{}
+\hypertarget{ref-lme4}{}
+Bates, D., Mächler, M., Bolker, B., \& Walker, S. (2015). Fitting linear
+mixed-effects models using lme4. \emph{Journal of Statistical Software},
+\emph{67}(1), 1--48. \url{http://doi.org/10.18637/jss.v067.i01}
+
 \hypertarget{ref-Bigelow2004}{}
@@
 \emph{Encyclopedia on Early Childhood Development}, 1--7.
+
+\hypertarget{ref-spacy2}{}
+Honnibal, I., Matthew AND Montani. (2017). SpaCy 2: Natural language
+understanding with bloom embeddings, convolutional neural networks and
+incremental parsing. \emph{To Appear}.
 
@@
 
+\hypertarget{ref-datavyu}{}
+Team, D. (2014). Datavyu: A video coding tool. \emph{Databrary Project}.
+Retrieved from \url{http://datavyu.org}
+
 \hypertarget{ref-Vygotsky1980}{}

### 2019-03-01 paper/cogsci2019/cogsci2019.Rmd
writing

@@
 Of course, young children are rarely playing in isolation: caregivers often provide encouragement and guidance while scaffolding a child's play [@Kaye1970; @Wood1976]. 
-Early parenting practices have been shown to play an important role in shaping the future outcomes of young children [@Hart1995; @Heckman2006]. 
-While many interventions have trouble reaching the parents of very young children, digital delivery of parenting advice by way of
+Indeed, parenting practices early in childhood have been shown to play an important role in shaping the future outcomes of young children [@Hart1995; @Heckman2006]. 
+While interventions often have trouble reaching many parents of very young children, the proliferation of mobile devices offers a good avenut for the digital delivery of parenting advice [@Breitenstein2014].
 

### 2019-03-01 parenting_obs_e2/Lexical_Diversity_Analysis.Rmd
integrated lexical diversity graphs for both Exp 1 and Exp 2
writing

@@
 
-```{r echo=FALSE}
+```{r include=FALSE}
 knitr::opts_chunk$set(fig.width=8, fig.height=5, 
@@
 
+# age is "1" or "2", but should be continuous value (in mos)
+d$age = as.numeric(d$age)
+d$Condition <- factor(d$condition, levels=c("con","exp"), labels=c("Control","Video"))
+save(d, file="Exp2_cleaned_data.Rdata")
 ```
@@
 ###Sentence Length by age
-(Maybe do a scatterplot with continuous scatterplot)
+(Maybe do a scatterplot with continuous age)
 

### 2019-03-05 paper/cogsci2019/cogsci2019.Rmd
edits

@@
 
-```{r libraries, echo=F, include=F}
+```{r libraries, include=F}
 suppressPackageStartupMessages(c("dplyr","langcog","tidyr","ggplot2","lme4"))
@@
 While interventions often have trouble reaching many parents of very young children, the proliferation of mobile devices offers a good avenut for the digital delivery of parenting advice [@Breitenstein2014].
+However, the efficacy of digital parenting advice has not been widely proven.
 
@@
 If either participant looked away from the object for less than 3 seconds and then returned to the same object it was considered part of the same period of joint attention. 
-Episodes joint attention were considered coordinated if both participants visually focused on an object for a minimum of 3 seconds and at some point in the interaction the child indicated awareness of interaction with some overt behavior toward the parent.
-This could be looks to the parent's face, gestures, vocalizations, or turn-taking. 
-If either participant looked away for less than 3 seconds and then returned to the same object, it was coded as part of the same period of joint attention. 
+A joint attention episode was considered coordinated if both participants visually focused on an object for a minimum of 3 seconds and at some point in the interaction the child indicated awareness of interaction with some overt behavior toward the parent such as looking at their face, gesturing, vocalizing, or turn-taking.
+
 A second coder independently coded a third of the videos (i.e., 20 of the 60 videos, approximately equally distributed across ages) to establish reliability. 

### 2019-03-09 paper/cogsci2019/cogsci2019.Rmd
update participants info and e2 results

--- 2019-03-01 paper/cogsci2019/cogsci2019.Rmd
@@
 A second coder independently coded a third of the videos (i.e., 20 of the 60 videos, approximately equally distributed across ages) to establish reliability. 
-The two coders had a reliability of ICC = 0.80 with 95% confident interval (CI) = [0.57,0.92] (p < 0.05) for number of parent bids for JA; ICC = 0.20 with 95% CI = [-0.26,0.58] for number of passive JA episodes; ICC = 0.66 with 95% CI = [0.32,0.85] (p < 0.05) for number of coordinated JA episodes; ICC = 0.24 with 95% CI = [-0.21,0.61] for total duration of passive JA episodes, and ICC = 0.62 with 95% CI = [0.27,0.83] (p < 0.05) for total duration of passive (coordinated??) JA episodes.
+The two coders had a reliability of ICC = 0.80 with 95% confident interval (CI) = [0.57,0.92] (p < 0.05) for number of parent bids for JA; ICC = 0.20 with 95% CI = [-0.26,0.58] for number of passive JA episodes; ICC = 0.66 with 95% CI = [0.32,0.85] (p < 0.05) for number of coordinated JA episodes; ICC = 0.24 with 95% CI = [-0.21,0.61] for total duration of passive JA episodes, and ICC = 0.62 with 95% CI = [0.27,0.83] (p < 0.05) for total duration of coordinated JA episodes.
 
@@
 
-There is a main effect of condition on total bids for joint attention.
+There is (was?) a main effect of condition on total bids for joint attention.
 Parents in the experimental condition (i.e., those who saw a video demonstrating an activity) made a greater number of bids for joint attention with their child.
@@
 
+lmer_data <- d %>%
+  mutate(condition = factor(condition), 
+         MTLD = as.numeric(MTLD),
+         TTR = as.numeric(TTR),
+         age = as.numeric(langcog::scale(age, scale=FALSE)),
+         video = as.factor(video))
 ```
@@
 ### Participants. 
-`r nrow(d)` infants aged 12-24 months and their parents participated in the same museum as Experiment 1. 
+`r nrow(d)` infants (F = 37, M = 47) aged 12-24 months (42 12-17.9 month-olds, 42 18-24 month-olds) and their parents participated in the same museum as Experiment 1. 
 We included infants who were exposed to English at least 75 percent of the time or who were exposed less but whose participating parent reported that they primarily speak English with their child at home.
-[specific demo info]
+Forty nine% of participants (n = 41) had been exposed to two or more languages as indicated by their parent. 
+Parents identified their children as White (n = 39), Asian (n = 20), African American/Black (n = 1), Biracial (n = 9), other (n = 7), or declined to state (n = 8).
+Sixteen parents reported their child was of Hispanic origin.
+Parents tended to be highly- educated, with reports of highest level of education ranging from completed high school (n = 0), some college (n = 5), four-year college (n = 28), some graduate school (n = 2), to completed graduate school (n = 35) or declined to state (n = 14).
 
@@
 Consistent with the No-Video control condition in Experiment 1, parents in the Control Video condition were told to play with their child as they would at home, and were not given additional instructions.
+The coding procedure also matched that of Experiment 1.
+A second coder independently coded a third of the videos (i.e., 26 of the 84 videos, approximately equally distributed across ages) to establish reliability.
+The two coders had a reliability of ICC = 0.80 with 95% confident interval (CI) = [0.60,0.90] (p < 0.05) for number of parent bids for JA; ICC = 0.74 with 95% CI = [0.59,0.87] (p < 0.05) for number of passive JA episodes; ICC = 0.78 with 95% CI = [0.58,0.90] (p < 0.05) for number of coordinated JA episodes; ICC = 0.72 with 95% CI = [0.46,0.86] (p < 0.05) for total duration of passive JA episodes, and ICC = 0.88 with 95% CI = [0.75,0.94] (p < 0.05) for total duration of coordinated JA episodes.
 
@@
 
+Parents' child-directed speech was transcribed and processed in the same way as in Experiment 1.
+
 ## Lexical Diversity
+```{r, e2-lexdiv-regressions, echo=F, include=F}
+# Predicting lexical diversity based on experimental condition. 
+modTTR <- lmer(TTR ~ age * condition + (1 | video), data=lmer_data) 
+summary(modTTR)
+
+modMTLD <- lmer(MTLD ~ age * condition + (1 | video), data=lmer_data)
+summary(modMTLD)
+
+# predict word tokens
+tokens_mod <- lmer(tokens ~ age * condition + (1 | video), data=lmer_data)
+summary(tokens_mod)
+
+# predict word types
+types_mod <- lmer(types ~ age * condition + (1 | video), data=lmer_data)
+summary(types_mod)
+```
+
+We fit a mixed-effects linear regression predicting TTR and MTLD as a function of age (scaled and 0-centered) and condition with a random intercept per video using lme4 [@lme4].
+There was significantly lower TTR in the Video condition (mean: 0.38) than in the Control condition (mean: 0.47, $\beta=-.09$, t(8) = 3.16, *p*<.05). 
+There was no significant effect of age.
+A similar mixed-effects linear regression instead predicting MTLD found no significant effects of age or condition.
+Figure 1 shows the mean of each lexical diversity measure (TTR and MTLD) by condition.
+
+We also conducted similar regressions predicting the number of word tokens and types, finding no significant effects of of age or condition.
+
+(Table with mean and SD of tokens, types, and TTR)
 
 ```{r e2lexdiv, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.5, fig.height=3, set.cap.width=T, num.cols.cap=1, fig.cap = "Mean lexical diversity scores by condition (left: Type/Token ratio, right: MTLD) in Experiment 2."}
+
+d$Condition = factor(d$condition, levels = c("con", "exp"), labels = c("Control", "Video"))
+
+# all at once, but there are NAs in SD cols ?
+e2 <- d %>% group_by(Condition) %>%
+  summarise(TTR=mean(TTR), TTRsd=sd(TTR),
+            MTLD=mean(MTLD), MTLDsd=sd(MTLD),
+            types=mean(types), types.sd=sd(types),
+            tokens = mean(tokens), tokens.sd=sd(tokens))
+
 ms_lex <- d %>% group_by(Condition) %>%
@@
   summarise(mean=mean(TTR), sd=sd(TTR))
+
+ttr_means <- d%>%
+  group_by(Condition)%>%
+  summarise(mean = mean(TTR), sd = sd(TTR))
+
+# report table with ttr_means lex_sds
 
@@
 mltd_mean <- d %>% group_by(Condition)%>%
+  summarise(mean = mean(MTLD), sd=sd(MTLD))
+
+mtld_means <- d %>%
+  group_by(Condition)%>%
   summarise(mean = mean(MTLD), sd=sd(MTLD))
@@
 ```
+```{r, e2-effect-size, echo=F}
+cohens_d <- diff(ttr_means$mean) / (sqrt(sum(ttr_means$sd^2)) / 2)
+```
 
 ## Joint Attention
+```{r, e2ja-regressions, echo=F, include=F}
+x<- load(paste(e2path,"joint_attention/Exp2_joint_attention_data.RData",sep=''))
+d$Condition <- factor(d$condition, levels = c("con","exp"), labels = c("Control","Video"))
+
+lmer_data <- d %>%
+  mutate(Condition = factor(Condition), 
+         bids_tot = as.numeric(bids),
+         Video = as.factor(video))
+
+# Total number of bids
+bids_mod <- lmer(bids_tot ~ age * condition + (1 | video), data = lmer_data)
+summary(bids_mod)
+
+# Episodes of coordinated joint attention.
+cja_mod <- lmer(cja ~ age * condition + (1 | video), data = lmer_data)
+summary(cja_mod)
+
+# Episodes of passive joint attention.
+pja_mod <- lmer(pja ~ age * condition + (1 | video), data = lmer_data)
+summary(pja_mod)
+
+# Total duration of passive joint attention.
+pja_time_mod <- lmer(pja_length ~ age * condition + (1 | video), data = lmer_data)
+summary(pja_time_mod)
+
+# Total duration of coordinated joint attention.
+cja_time_mod <- lmer(cja_length ~ age * condition + (1 | video), data = lmer_data)
+summary(cja_time_mod)
+```
+
+```{r e2ja-graphs, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.5, fig.height=3.0, set.cap.width=T, num.cols.cap=1, fig.cap = "Mean number of bids and episodes of Joint Attention in Experiment 2."}
+
+ms_bids <- d %>% group_by(Condition) %>%
+  multi_boot_standard(col="bids")
+
+e2bids <- ggplot(ms_bids, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
+  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
+  xlab("Condition") + ylab("Total Bids for Joint Attention") +
+  langcog::scale_colour_solarized() + ggthemes::theme_few() + 
+  theme(legend.position="none")
+
+# total joint attention episodes
+ms_tja <- d %>% group_by(Condition) %>%
+  multi_boot_standard(col = "total_ja")
+
+e2tja <- ggplot(ms_tja, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
+  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9))+
+  xlab("Condition") + ylab("Total Episodes of Joint Attention") +
+  langcog::scale_colour_solarized() + ggthemes::theme_few() + 
+  theme(legend.position="none")
+
+multiplot(e2bids, e2tja, cols=2)
+```
+
+```{r e2ja-graphs-pass-coord, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.5, fig.height=3.0, set.cap.width=T, num.cols.cap=1, fig.cap = "Average number of passive and coordinated episodes of JA in Experiment 2."}
+ms_pja <- d %>% group_by(Condition) %>%
+  multi_boot_standard(col = "pja")
+
+e2pja <- ggplot(ms_pja, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
+  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9))+
+  xlab("Condition") + ylab("Episodes of Passive Joint Attention")  +
+  langcog::scale_colour_solarized() + ggthemes::theme_few() + theme(legend.position="none")
+
+#Episodes of coordinated joint attention
+ms_cja <- d %>% group_by(Condition) %>%
+  multi_boot_standard(col = "cja")
+
+e2cja <- ggplot(ms_cja, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
+  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9))+
+  xlab("Condition") + ylab("Episodes of Coordinated Joint Attention")  +
+  langcog::scale_colour_solarized() + ggthemes::theme_few() + theme(legend.position="none")
+
+multiplot(e2pja, e2cja, cols=2)
+```
 
 # Discussion
+
+Similar to results in Experiment 1, the number of tokens was higher in the experimental condition, while the number of types and lexical diversity (Type/Token ratio) were higher in the control condition.
+Parents may be relatively more repetetive in the experimental condition since they are attempting to stick to a specific prescribed task, but they talk more overall.
+There was a marginal effect of condition on total bids for joint attention.
+Parents in the experimental condition (i.e., those who saw a video demonstrating an activity) made a greater number of bids for joint attention with their child.
+There was no effect of condition on the number of episodes of coordinated joint attention.
+There was no effect of condition on the number of episodes of either passive or coordinated joint attention, or the duration of these episodes. 
+However, there was a main effect of age on number of episodes of passive joint attention, duration of passive and coordinated joint attention, 
+with the older children having fewer episodes of passive joint attention, shorter duration of passive joint attention, and longer duration of coordinated joint attention. 
+These results suggest that children become more socially engaging in interactions with their caregivers as they develop.
 

### 2019-03-09 paper/cogsci2019/cogsci2019.tex
update participants info and e2 results

@@
 guidance while scaffolding a child's play (Kaye, 1970; Wood, Bruner, \&
-Ross, 1976). Early parenting practices have been shown to play an
-important role in shaping the future outcomes of young children (Hart \&
-Risley, 1995; Heckman, 2006). While many interventions have trouble
-reaching the parents of very young children, digital delivery of
-parenting advice by way of
+Ross, 1976). Indeed, parenting practices early in childhood have been
+shown to play an important role in shaping the future outcomes of young
+children (Hart \& Risley, 1995; Heckman, 2006). While interventions
+often have trouble reaching many parents of very young children, the
+proliferation of mobile devices offers a good avenut for the digital
+delivery of parenting advice (Breitenstein, Gross, \& Christophersen,
+2014).
 
@@
 review of 11 studies verified that digital delivery is a promising means
-of effectively distributing interventions (Breitenstein, Gross, \&
-Christophersen, 2014). However, the parent and child outcomes assessed
-in the review (e.g.infant positive behaviors, satisfaction, emotional
-symptoms etc.) did not address the nature or quality of parent-infant
-interactions at a detailed level, like if the interventions lead to
-children paying more attention, or vocabulary changes in parents'
-language usages. Although digitally-delivered ac-tivities are designed
-to promote learning and cognitive development, it is unclear how they
-might affect these dimensions of parent-child interactions. Thus, we
-want to conduct this experiment to explore if and how digital
-scaffolding of activities affect the social and linguistic
-characteristics of parent-child ineractions. The quality of parent-child
-interactions can be measured by both the social engagement of parents
-(e.g., joint attention to objects in the environment)(Bigelow, MacLean,
-\& Proctor, 2004) and the quality of language (e.g., vocabulary
-diversity) (Malvern, Richards, Chipere, \& Durán, 2004).
+of effectively distributing interventions (Breitenstein et al., 2014).
+However, the parent and child outcomes assessed in the review
+(e.g.infant positive behaviors, satisfaction, emotional symptoms etc.)
+did not address the nature or quality of parent-infant interactions at a
+detailed level, like if the interventions lead to children paying more
+attention, or vocabulary changes in parents' language usages. Although
+digitally-delivered ac-tivities are designed to promote learning and
+cognitive development, it is unclear how they might affect these
+dimensions of parent-child interactions. Thus, we want to conduct this
+experiment to explore if and how digital scaffolding of activities
+affect the social and linguistic characteristics of parent-child
+ineractions. The quality of parent-child interactions can be measured by
+both the social engagement of parents (e.g., joint attention to objects
+in the environment)(Bigelow, MacLean, \& Proctor, 2004) and the quality
+of language (e.g., vocabulary diversity) (Malvern, Richards, Chipere, \&
+Durán, 2004).
 
@@
 of passive JA episodes, and ICC = 0.62 with 95\% CI = {[}0.27,0.83{]} (p
-\textless{} 0.05) for total duration of passive (coordinated??) JA
-episodes.
+\textless{} 0.05) for total duration of coordinated JA episodes.
 
@@
 
-There is a main effect of condition on total bids for joint attention.
-Parents in the experimental condition (i.e., those who saw a video
-demonstrating an activity) made a greater number of bids for joint
+There is (was?) a main effect of condition on total bids for joint
+attention. Parents in the experimental condition (i.e., those who saw a
+video demonstrating an activity) made a greater number of bids for joint
 attention with their child. There was no effect of condition on the
@@
 
-84 infants aged 12-24 months and their parents participated in the same
-museum as Experiment 1. We included infants who were exposed to English
-at least 75 percent of the time or who were exposed less but whose
-participating parent reported that they primarily speak English with
-their child at home. {[}specific demo info{]}
+84 infants (F = 37, M = 47) aged 12-24 months (42 12-17.9 month-olds, 42
+18-24 month-olds) and their parents participated in the same museum as
+Experiment 1. We included infants who were exposed to English at least
+75 percent of the time or who were exposed less but whose participating
+parent reported that they primarily speak English with their child at
+home. Forty nine\% of participants (n = 41) had been exposed to two or
+more languages as indicated by their parent. Parents identified their
+children as White (n = 39), Asian (n = 20), African American/Black (n =
+1), Biracial (n = 9), other (n = 7), or declined to state (n = 8).
+Sixteen parents reported their child was of Hispanic origin. Parents
+tended to be highly- educated, with reports of highest level of
+education ranging from completed high school (n = 0), some college (n =
+5), four-year college (n = 28), some graduate school (n = 2), to
+completed graduate school (n = 35) or declined to state (n = 14).
 
@@
 with their child as they would at home, and were not given additional
-instructions.
+instructions. The coding procedure also matched that of Experiment 1. A
+second coder independently coded a third of the videos (i.e., 26 of the
+84 videos, approximately equally distributed across ages) to establish
+reliability. The two coders had a reliability of ICC = 0.80 with 95\%
+confident interval (CI) = {[}0.60,0.90{]} (p \textless{} 0.05) for
+number of parent bids for JA; ICC = 0.74 with 95\% CI = {[}0.59,0.87{]}
+(p \textless{} 0.05) for number of passive JA episodes; ICC = 0.78 with
+95\% CI = {[}0.58,0.90{]} (p \textless{} 0.05) for number of coordinated
+JA episodes; ICC = 0.72 with 95\% CI = {[}0.46,0.86{]} (p \textless{}
+0.05) for total duration of passive JA episodes, and ICC = 0.88 with
+95\% CI = {[}0.75,0.94{]} (p \textless{} 0.05) for total duration of
+coordinated JA episodes.
 
@@
 
+Parents' child-directed speech was transcribed and processed in the same
+way as in Experiment 1.
+
 \subsection{Lexical Diversity}\label{lexical-diversity-1}
+
+We fit a mixed-effects linear regression predicting TTR and MTLD as a
+function of age (scaled and 0-centered) and condition with a random
+intercept per video using lme4 (Bates et al., 2015). There was
+significantly lower TTR in the Video condition (mean: 0.38) than in the
+Control condition (mean: 0.47, \(\beta=-.09\), t(8) = 3.16,
+\emph{p}\textless{}.05). There was no significant effect of age. A
+similar mixed-effects linear regression instead predicting MTLD found no
+significant effects of age or condition. Figure 1 shows the mean of each
+lexical diversity measure (TTR and MTLD) by condition.
+
+We also conducted similar regressions predicting the number of word
+tokens and types, finding no significant effects of of age or condition.
+
+(Table with mean and SD of tokens, types, and TTR)
 
@@
 
+\begin{CodeChunk}
+\begin{figure}[H]
+
+{\centering \includegraphics{figs/e2ja-graphs-1}
+
+}
+
+\caption[Mean number of bids and episodes of Joint Attention in Experiment 2]{Mean number of bids and episodes of Joint Attention in Experiment 2.}\label{fig:e2ja-graphs}
+\end{figure}
+\end{CodeChunk}
+
+\begin{CodeChunk}
+\begin{figure}[H]
+
+{\centering \includegraphics{figs/e2ja-graphs-pass-coord-1}
+
+}
+
+\caption[Average number of passive and coordinated episodes of JA in Experiment 2]{Average number of passive and coordinated episodes of JA in Experiment 2.}\label{fig:e2ja-graphs-pass-coord}
+\end{figure}
+\end{CodeChunk}
+
 \section{Discussion}\label{discussion-1}
+
+Similar to results in Experiment 1, the number of tokens was higher in
+the experimental condition, while the number of types and lexical
+diversity (Type/Token ratio) were higher in the control condition.
+Parents may be relatively more repetetive in the experimental condition
+since they are attempting to stick to a specific prescribed task, but
+they talk more overall. There was a marginal effect of condition on
+total bids for joint attention. Parents in the experimental condition
+(i.e., those who saw a video demonstrating an activity) made a greater
+number of bids for joint attention with their child. There was no effect
+of condition on the number of episodes of coordinated joint attention.
+There was no effect of condition on the number of episodes of either
+passive or coordinated joint attention, or the duration of these
+episodes. However, there was a main effect of age on number of episodes
+of passive joint attention, duration of passive and coordinated joint
+attention, with the older children having fewer episodes of passive
+joint attention, shorter duration of passive joint attention, and longer
+duration of coordinated joint attention. These results suggest that
+children become more socially engaging in interactions with their
+caregivers as they develop.
 

### 2019-03-09 paper/cogsci2019/cogsci2019.tex

@@
 delivery of parenting advice (Breitenstein, Gross, \& Christophersen,
-2014).
+2014). However, the efficacy of digital parenting advice has not been
+widely proven.
 
@@
 object for less than 3 seconds and then returned to the same object it
-was considered part of the same period of joint attention. Episodes
-joint attention were considered coordinated if both participants
+was considered part of the same period of joint attention. A joint
+attention episode was considered coordinated if both participants
 visually focused on an object for a minimum of 3 seconds and at some
 point in the interaction the child indicated awareness of interaction
-with some overt behavior toward the parent. This could be looks to the
-parent's face, gestures, vocalizations, or turn-taking. If either
-participant looked away for less than 3 seconds and then returned to the
-same object, it was coded as part of the same period of joint attention.
+with some overt behavior toward the parent such as looking at their
+face, gesturing, vocalizing, or turn-taking.
+
 A second coder independently coded a third of the videos (i.e., 20 of

### 2019-03-14 paper/cogsci2019/cogsci2019.Rmd
clean version

@@
 We included infants who were exposed to English at least 50 percent of the time (n = 58) or who were exposed less but whose participating parent reported that they primarily speak English with their child at home (n = 2).
-Sixty-one% of participants (n = 37) had been exposed to two or more languages as indicated by their parent. 
+61% of participants (n = 37) had been exposed to two or more languages as indicated by their parent. 
 Parents identified their children as White (n = 25), Asian (n = 11), African American/Black (n = 2), Biracial (n = 12), other (n = 5), or declined to state (n = 5). 
@@
 modTTR <- lmer(TTR ~ condition + age + gender + parent_ed + (1|video), data=lmer_data)
-summary(modTTR) #
+summary(modTTR) # condition t(39.9) = 4.25 p<.001
 
 modMTLD <- lmer(MTLD ~ condition + age + gender + parent_ed + (1|video), data=lmer_data)
-summary(modMTLD)
+summary(modMTLD) # condition t(43) = 4.69 p<.001
 
@@
 tokens_mod <- lmer(tokens ~ condition*EL + condition*AA + condition*RR + age + gender + parent_ed + (1|video),  data=lmer_data)
-summary(tokens_mod) # condition *
+summary(tokens_mod) # condition t(34.4) = 2.19 p<.05
 
@@
 types_mod <- lmer(types ~ condition*EL + condition*AA + condition*RR  + age + gender + parent_ed + (1|video), data=lmer_data)
-summary(types_mod)
+summary(types_mod) # nothing
 ```
@@
                            (1| Video), data = lmer_data)
-summary(bids_mod)
+summary(bids_mod) # condition beta = 3.51, t(40.3) = 2.95 p<.01
 
@@
                            (1| Video), data = lmer_data)
-summary(cja_mod)
+summary(cja_mod) # NA
 
@@
                            (1| Video), data = lmer_data)
-summary(pja_mod)
+summary(pja_mod) # marginal RR, beta=-1.07 p=.07, condition*RR beta=1.83 p<.05
 
@@
                            (1| Video), data = lmer_data)
-summary(pja_time_mod)
+summary(pja_time_mod) # NA
 
@@
                            (1| Video), data = lmer_data)
-summary(cja_time_mod)
+summary(cja_time_mod) # marginal parent education p=.09
 ```
@@
 
-There is (was?) a main effect of condition on total bids for joint attention.
+There was a main effect of condition on total bids for joint attention.
 Parents in the experimental condition (i.e., those who saw a video demonstrating an activity) made a greater number of bids for joint attention with their child.
@@
 modTTR <- lmer(TTR ~ age * condition + (1 | video), data=lmer_data) 
-summary(modTTR)
+summary(modTTR) # condition beta=-.09  t(8.7) = 3.06 p=.01
 
 modMTLD <- lmer(MTLD ~ age * condition + (1 | video), data=lmer_data)
-summary(modMTLD)
+summary(modMTLD) # NA
 
@@
 tokens_mod <- lmer(tokens ~ age * condition + (1 | video), data=lmer_data)
-summary(tokens_mod)
+summary(tokens_mod) # NA
 
@@
 types_mod <- lmer(types ~ age * condition + (1 | video), data=lmer_data)
-summary(types_mod)
+summary(types_mod) # NA
 ```
@@
 We fit a mixed-effects linear regression predicting TTR and MTLD as a function of age (scaled and 0-centered) and condition with a random intercept per video using lme4 [@lme4].
-There was significantly lower TTR in the Video condition (mean: 0.38) than in the Control condition (mean: 0.47, $\beta=-.09$, t(8) = 3.16, *p*<.05). 
+There was significantly lower TTR in the Video condition (mean: 0.38) than in the Control condition (mean: 0.47, $\beta=-.09$, t(8.7) = 3.06, *p*=.01).
 There was no significant effect of age.
@@
 ```{r, e2ja-regressions, echo=F, include=F}
-x<- load(paste(e2path,"joint_attention/Exp2_joint_attention_data.RData",sep=''))
+load(paste(e2path,"joint_attention/Exp2_joint_attention_data.RData",sep=''))
 d$Condition <- factor(d$condition, levels = c("con","exp"), labels = c("Control","Video"))
+e2ja = d
 
-lmer_data <- d %>%
-  mutate(Condition = factor(Condition), 
-         bids_tot = as.numeric(bids),
-         Video = as.factor(video))
+t.test(subset(e2ja, Condition=="Control")$bids, subset(e2ja, Condition=="Video")$bids)
 
 # Total number of bids
-bids_mod <- lmer(bids_tot ~ age * condition + (1 | video), data = lmer_data)
-summary(bids_mod)
+bids_mod <- lmer(bids ~ age * Condition + (1 | video), data = e2ja)
+summary(bids_mod) # singular fit, covergence code: 0 - no effects
 
 # Episodes of coordinated joint attention.
-cja_mod <- lmer(cja ~ age * condition + (1 | video), data = lmer_data)
-summary(cja_mod)
+cja_mod <- lmer(cja ~ age * condition + (1 | video), data = e2ja)
+summary(cja_mod) # marginal condition: t(79) = 1.88 beta=-5.85 p=.06, age*condition beta=4.92 t(79) = 2.35 p=.02
+# also singular fit, covergence code: 0
 
 # Episodes of passive joint attention.
-pja_mod <- lmer(pja ~ age * condition + (1 | video), data = lmer_data)
-summary(pja_mod)
+pja_mod <- lmer(pja ~ age * condition + (1 | video), data = e2ja)
+summary(pja_mod) # age beta=-2.32 t(26.6) = 2.23 p<.05
 
 # Total duration of passive joint attention.
-pja_time_mod <- lmer(pja_length ~ age * condition + (1 | video), data = lmer_data)
-summary(pja_time_mod)
+pja_time_mod <- lmer(pja_length ~ age * condition + (1 | video), data = e2ja)
+summary(pja_time_mod) # age beta=-15512 t(79) = 2.40 p<.05
 
@@
 cja_time_mod <- lmer(cja_length ~ age * condition + (1 | video), data = lmer_data)
-summary(cja_time_mod)
+summary(cja_time_mod) # marginal age: beta=31757 t(79) = 1.81 p=.07
 ```

### 2019-03-14 paper/cogsci2019/cogsci2019.tex
clean version

@@
 were exposed less but whose participating parent reported that they
-primarily speak English with their child at home (n = 2). Sixty-one\% of
+primarily speak English with their child at home (n = 2). 61\% of
 participants (n = 37) had been exposed to two or more languages as
@@
 
-There is (was?) a main effect of condition on total bids for joint
-attention. Parents in the experimental condition (i.e., those who saw a
-video demonstrating an activity) made a greater number of bids for joint
+There was a main effect of condition on total bids for joint attention.
+Parents in the experimental condition (i.e., those who saw a video
+demonstrating an activity) made a greater number of bids for joint
 attention with their child. There was no effect of condition on the
@@
 
-84 infants (F = 37, M = 47) aged 12-24 months (42 12-17.9 month-olds, 42
+83 infants (F = 37, M = 47) aged 12-24 months (42 12-17.9 month-olds, 42
 18-24 month-olds) and their parents participated in the same museum as
@@
 significantly lower TTR in the Video condition (mean: 0.38) than in the
-Control condition (mean: 0.47, \(\beta=-.09\), t(8) = 3.16,
-\emph{p}\textless{}.05). There was no significant effect of age. A
-similar mixed-effects linear regression instead predicting MTLD found no
+Control condition (mean: 0.47, \(\beta=-.09\), t(8.7) = 3.06,
+\emph{p}=.01). There was no significant effect of age. A similar
+mixed-effects linear regression instead predicting MTLD found no
 significant effects of age or condition. Figure 1 shows the mean of each

### 2019-03-14 parenting_obs_e2/Lexical_Diversity_Analysis.Rmd
clean version

@@
 
-# age is "1" or "2", but should be continuous value (in mos)
-d$age = as.numeric(d$age)
+dem <- read.csv("anonymized_demographics_parenting_obs_e2.csv", header=T)
+dem$age = as.numeric(as.character(dem$age))
+d$age = NULL
+dem$X = NULL
+d <- d %>% left_join(dem, by=c("sid" = "SID")) %>%
+  filter(age <= 2.0)
+
 d$Condition <- factor(d$condition, levels=c("con","exp"), labels=c("Control","Video"))

### 2019-03-14 parenting_obs_e2/joint_attention/parenting_obs_JA.Rmd
clean version

@@
 ```{r, width=4, height=4}
+dem <- read.csv("../anonymized_demographics_parenting_obs_e2.csv", header=T)
+dem$age = as.numeric(as.character(dem$age))
+d$age = NULL
+d$X = NULL
+d$X.1 = NULL
+d$X.2 = NULL
+dem$X = NULL
+d <- d %>% left_join(dem, by=c("sid" = "SID")) %>%
+  filter(age <= 2.0)
+
 save(d, file="Exp2_joint_attention_data.RData")

### 2019-04-19 paper/cogsci2019/cogsci2019.Rmd
writing

@@
 author-information: > 
-    \author{{\large\bf Hanwen Vivian~Zhang} (\texttt{vivian3@stanford.edu}) \\
-    {\large\bf George~Kachergis} (\texttt{george.kachergis@gmail.com}) \\
+    \author{{\large\bf George~Kachergis} (\texttt{kachergis@stanford.edu}) \\
+    {\large\bf Hanwen Vivian~Zhang} (\texttt{vivian3@stanford.edu}) \\
     {\large\bf Michael C.~Frank} (\texttt{mcfrank@stanford.edu}) \\ 
@@
     The rise of phone- and tablet-based parenting applications ("apps") holds the promise of delivering 
-    low-cost, positive interventions on parenting style to a variety of different populations. 
+    low-cost, positive interventions on parenting style to a wide variety of populations. 
     Of special interest are the parents of very young children, who are often difficult to reach in other ways. 
@@
 
+Children of any given age show remarkable variability in their levels of language proficiency [@Fenson1994],
+
 Young children spend a large portion of their waking time at play, variously manipulating objects, exploring their environment, and interacting with caregivers and peers.
@@
 Of course, young children are rarely playing in isolation: caregivers often provide encouragement and guidance while scaffolding a child's play [@Kaye1970; @Wood1976]. 
-Indeed, parenting practices early in childhood have been shown to play an important role in shaping the future outcomes of young children [@Hart1995; @Heckman2006]. 
+The quality of interactions during such guided play has been shown to influence language learning: parents' joint attention to objects that their child was focused on was positively correlated with the child's subsequent vocabulary growth [@Tomasello1986; @Carpenter1998].
+Episodes of joint attention during guided play have also been found to contain more age-appropriate advanced forms of play [@Bigelow2004].
+More generally, parenting practices early in childhood have been shown to play an important role in shaping the future outcomes of young children [@Hart1995; @Heckman2006]. 
 While interventions often have trouble reaching many parents of very young children, the proliferation of mobile devices offers a good avenut for the digital delivery of parenting advice [@Breitenstein2014].
@@
 ## Improving Parenting Practices and Language Use
-Thus, including guided play in parenting practices early on is crucial and will help with children's later performances in academic and social situations. 
-To intervene in parenting practices, Suskind and others did a parent-directed home-visiting intervention experiment in 2015 for children of low socioeconomic status.
-They showed that parents in experimental group have greater knowledge of language development and this effect sustained four months after the intervention. 
-However, although a number of interactive measures increased during the experiment, including the number of word tokens, conversational turns, and child vocalizations, these increases did not sustain after the intervention [@Suskind2015].
+Thus, including guided play in parenting practices from an early age may boost children's language and educational outcomes. 
+A recent home-visit parenting practices intervention targeting children of low socioeconomic status found that parents in the intervention group gained knowledge of language development, and that this effect sustained four months after the intervention [@Suskind2015].
+However, although a number of interactive measures increased during the experiment, including the number of word tokens, conversational turns, and child vocalizations, these increases did not sustain after the intervention.
 That changes did not sustain could be due to the intervention itself,
@@
 Parents identified their children as White (n = 25), Asian (n = 11), African American/Black (n = 2), Biracial (n = 12), other (n = 5), or declined to state (n = 5). 
-Fifteen parents reported their child was of Hispanic origin. 
+Fifteen parents reported that their child was of Hispanic origin. 
 Parents tended to be highly-educated, with reports of highest level of education ranging from completed high school (n = 5), some college (n = 6), four-year college (n = 14), some graduate school (n = 1), to completed graduate school (n = 28) or declined to state (n = 6).
@@
 More information about the specific videos is available in the Appendix. 
-Participants were also given a set of props corresponding to those in the video they watched so that they could complete the activity. 
-The props associated with each video are listed in the Appendix.
+Participants were also given a set of toys corresponding to those in the video that they watched so that they could complete the activity. 
+The toys associated with each video are listed in the Appendix.
 
 Participants were randomly assigned to either the *Video* condition or the *Control* condition. 
-Participating parents in the Video condition were assigned to watch one of the two activity videos available for their child's age group. 
-Participating parents in the Control condition watched no activity video, and were merely asked to play with their child as they normally would.
+Parents participating in the Video condition were assigned to watch one of the two activity videos available for their child's age group, while parents in the Control condition watched no activity video, and were simply asked to play with their child as they normally would.
 The Control condition was yoked to the Activity Video condition such that for every participant in the Video condition who saw a particular video and received the associated props, a participant in the Control condition received the same props but did not watch the activity video.
-Parents also completed the Parenting Attitudes Questionnaire (PAQ). 
-The PAQ measures parents' attitudes about parenting and child development along three dimensions: rules and respect, early learning, and affection and attachment.
+Parents also completed the Early Parenting Attitudes Questionnaire (EPAQ; [@Hembacher2018]). 
+The EPAQ measures parents' attitudes about parenting and child development along three dimensions: rules and respect, early learning, and affection and attachment.
 
@@
 modTTR <- lmer(TTR ~ condition + age + gender + parent_ed + (1|video), data=lmer_data)
-summary(modTTR) # condition t(39.9) = 4.25 p<.001
+summary(modTTR) # condition -0.123 t(39.9) = 4.25 p<.001
 
 modMTLD <- lmer(MTLD ~ condition + age + gender + parent_ed + (1|video), data=lmer_data)
-summary(modMTLD) # condition t(43) = 4.69 p<.001
+summary(modMTLD) # condition -11.67 t(43) = 3.08 p=.004 !! singular fit
+# Bayesian regression (stan_glmer in rstanarm) shows the same
 
@@
 tokens_mod <- lmer(tokens ~ condition*EL + condition*AA + condition*RR + age + gender + parent_ed + (1|video),  data=lmer_data)
-summary(tokens_mod) # condition t(34.4) = 2.19 p<.05
+summary(tokens_mod) # condition 57.23 t(34.4) = 2.19 p<.05
 
 # predict word types
-types_mod <- lmer(types ~ condition*EL + condition*AA + condition*RR  + age + gender + parent_ed + (1|video), data=lmer_data)
+types_mod <- lmer(types ~ condition*EL + condition*AA + condition*RR  + age + gender + parent_ed + (1|video), data=lmer_data) # !! singular fit
 summary(types_mod) # nothing
@@
 
+We fit a mixed-effects linear regression predicting the number of bids for joint attention (JA) as a function of fixed effects of condition, age (scaled and 0-centered), gender, parent's education level, and the subscales of the EPAQ: Early Learning (EL), Affection and Attachment (AA), and Rules and Respect (RR), along with interactions of condition and EL, AA, and RR.
+This lme4 model included random intercepts per video.
+There were significantly more bids for JA in the Video condition (mean: X) than in the Control condition (mean: X, $\beta=3.51$, t(40.3) = 2.95, *p*<.01). 
+There were no other significant effects.
+Mixed-effects regressions with the same structure were performed predicting the number of episodes of coordinated and passive JA, and the total duration of time spent in coordinated and passive JA.
+There were no significant effects on the number or total duration of coordinated JA episodes, nor on the total duration of passive JA episodes. 
+For the regression predicting the number of passive joint attention episodes, the only significant effect was an interaction of condition and RR ($\beta=1.83$, t(41.5) = 2.22, *p*<.05), showing that...
+Figure X shows ... by condition.
+
 ```{r, e1ja-regressions, echo=F, include=F}
@@
 
+model_string =  "~ Condition * EL + Condition * AA + Condition * RR  + age + gender + parent_ed + (1| Video)"
+
 # Total number of bids
-bids_mod <- lmer(bids_tot ~ Condition *  EL  + Condition * AA + Condition * RR + age + gender + parent_ed +
-                           (1| Video), data = lmer_data)
-summary(bids_mod) # condition beta = 3.51, t(40.3) = 2.95 p<.01
+bids_mod <- lmer(paste("bids_tot", model_string), data = lmer_data)
+summary(bids_mod) # condition beta = 3.51, t(40.3) = 2.95 p<.01, gender p=.05 ?
 
 # Episodes of coordinated joint attention.
-cja_mod <- lmer(cja ~ Condition * EL + Condition * AA + Condition * RR  + age + gender + parent_ed +
-                           (1| Video), data = lmer_data)
+cja_mod <- lmer(paste("cja", model_string), data = lmer_data)
 summary(cja_mod) # NA
@@
 # Episodes of passive joint attention.
-pja_mod <- lmer(pja ~ Condition * EL + Condition * AA + Condition * RR  + age + gender + parent_ed +
-                           (1| Video), data = lmer_data)
+pja_mod <- lmer(paste("pja", model_string), data = lmer_data)
 summary(pja_mod) # marginal RR, beta=-1.07 p=.07, condition*RR beta=1.83 p<.05
@@
 # Total duration of passive joint attention.
-pja_time_mod <- lmer(pja_length ~ Condition * EL + Condition * AA + Condition * RR  + age + gender + parent_ed +
-                           (1| Video), data = lmer_data)
+pja_time_mod <- lmer(paste("pja_length", model_string), data = lmer_data)
 summary(pja_time_mod) # NA
@@
 # Total duration of coordinated joint attention.
-cja_time_mod <- lmer(cja_length ~ Condition * EL + Condition * AA + Condition * RR  + age + gender + parent_ed +
-                           (1| Video), data = lmer_data)
+cja_time_mod <- lmer(paste("cja_length", model_string), data = lmer_data)
 summary(cja_time_mod) # marginal parent education p=.09
@@
 
-Both the number of tokens and types are higher in the experimental condition, while lexical diversity (Type/Token ratio) is higher in the control condition. 
+In summary, while the number of tokens and types were higher in the experimental condition, lexical diversity (Type/Token ratio) was higher in the control condition. 
 Parents may be relatively more repetetive in the experimental condition since they are attempting to stick to a specific prescribed task, but they talk more overall.
@@
 There was a main effect of condition on total bids for joint attention. 
-Parents in the experimental condition (i.e., those who saw a video demonstrating an activity) made a greater number of bids for joint attention with their child.
+Parents in the Video condition, after seeing a video demonstrating an activity, made a greater number of bids for joint attention with their child.
 There was no effect of condition on the number of episodes of either passive or coordinated joint attention, or the duration of these episodes. 
-There is a marginal effect of gender on bids for joint attention, with parents of males producing more bids.
-There is a marginal interaction between RR scores and condition on passive joint attention, such that the experimental condition increased the number of episodes of PJA to a greater extent for people with high RR scores.
+There was a marginal effect of gender on bids for joint attention, with parents of males producing more bids. 
+There was a marginal interaction between RR scores and condition on passive joint attention, such that the experimental condition increased the number of episodes of PJA to a greater extent for people with high RR scores.
 While the electronically-delivered parenting advice increased the number of bids for joint attention by parents, it did not significantly effect the number or duration of episodes of joint attention. 
-One possibility is that child variables had a comparatively larger impact on the attainment of joint attention.
+It may be that child variables had a larger relative impact on the attainment of joint attention.
 
@@
 
-Experiment 1 found that compared to parents who did not watch a video, parents who watched a Kinedu video spoke more words overall, but had lower lexical diversity. 
+Experiment 1 found that compared to parents who played with children as they normally would, parents who watched a Kinedu video spoke more words overall, but had lower lexical diversity. 
 Parents who watched a video also made more bids for joint attention, although these bids did not result in more episodes of joint attention compared to the control group. 
-In Experiment 2 we attempt to replicate the findings from Experiment 1 with a restricted number of preregistered predictions. 
+Experiment 2 attempts to replicate the findings from Experiment 1 with a restricted number of preregistered predictions. 
 We will additionally include a second control condition, in which the same activities are described in written form, rather than being demonstrated in video. 
@@
 
-Parents' child-directed speech was transcribed and processed in the same way as in Experiment 1.
+Parents' child-directed speech was transcribed and processed according to the same procedure used in Experiment 1.
 
@@
 
-We fit a mixed-effects linear regression predicting TTR and MTLD as a function of age (scaled and 0-centered) and condition with a random intercept per video using lme4 [@lme4].
+We fit a mixed-effects linear regression predicting TTR and MTLD as a function of age (scaled and 0-centered) and condition with an interaction term, and with random intercepts per video using lme4 [@lme4].
 There was significantly lower TTR in the Video condition (mean: 0.38) than in the Control condition (mean: 0.47, $\beta=-.09$, t(8.7) = 3.06, *p*=.01).
@@
 Figure 1 shows the mean of each lexical diversity measure (TTR and MTLD) by condition.
-
-We also conducted similar regressions predicting the number of word tokens and types, finding no significant effects of of age or condition.
+Regressions with the same structure predicting the number of word tokens and types found no significant effects of age or condition.
 
@@
 # Total duration of coordinated joint attention.
-cja_time_mod <- lmer(cja_length ~ age * condition + (1 | video), data = lmer_data)
+cja_time_mod <- lmer(cja_length ~ age * condition + (1 | video), data = e2ja)
 summary(cja_time_mod) # marginal age: beta=31757 t(79) = 1.81 p=.07

### 2019-04-29 paper/cogsci2019/cogsci2019.Rmd
writing results

@@
 
-## Procedure.
+### Procedure.
 After providing informed consent, parents in the Video condition watched the assigned activity video on a laptop with headphones.
 To ensure that parents could give the video their full attention, the experimenter played with the infant with a set of toys (different from the experimental props used in the study) while the video was being played.
-Immediately following the video, each parent-child dyad was provided with the props to complete the activity they had viewed. 
+Immediately following the video, each parent-child dyad was provided with the props to complete the activity the parent had viewed. 
 The toys were placed on a large foam mat, and parents were instructed to sit on the mat with their child and re-create the activity they had viewed for a period of three minutes.
@@
 
-In both conditions, two video cameras were used to record the play session from different angles, and parents were fitted with a wireless audio recorder to record their child-directed speech. 
-After three minutes of play had elapsed, parents were told they could stop playing and cameras and audio were turned off.
-Parents were then asked to complete the PAQ before being debriefed.
+In both conditions, two video cameras were used to record the play session from different angles, and parents were fitted with a wireless microphone (Shurre lavalier microphone) to record their child-directed speech.
+After three minutes of play had elapsed, parents were told they could stop playing and the cameras and microphone were turned off.
+Parents were then asked to complete the EPAQ before being debriefed.
 
@@
 
-# Results
+## Results
 
@@
 
-## Lexical Diversity
+### Lexical Diversity
 
@@
 
-## Joint Attention
+### Joint Attention
 
@@
 
-In summary, while the number of tokens and types were higher in the experimental condition, lexical diversity (Type/Token ratio) was higher in the control condition. 
+In summary, while parents produced more word types and tokens after viewing the activity video, lexical diversity (Type/Token ratio and MTLD) was higher when parents were just asked to play as they normally would.
 Parents may be relatively more repetetive in the experimental condition since they are attempting to stick to a specific prescribed task, but they talk more overall.
-Demographics and PAQ do not interact with condition, but there is a marginal effect of RR score on lexical diversity (lower diversity for higher RR scores), and marginal effects of parent education on word types and tokens (more types and tokens for higher parent education).
+Demographics and EPAQ do not interact with condition, but there is a marginal effect of RR score on lexical diversity (lower diversity for higher RR scores), and marginal effects of parent education on word types and tokens (more types and tokens for higher parent education).
 
@@
 
-Experiment 1 found that compared to parents who played with children as they normally would, parents who watched a Kinedu video spoke more words overall, but had lower lexical diversity. 
-Parents who watched a video also made more bids for joint attention, although these bids did not result in more episodes of joint attention compared to the control group. 
-Experiment 2 attempts to replicate the findings from Experiment 1 with a restricted number of preregistered predictions. 
+Experiment 1 found that parents who watched a Kinedu video spoke more words overall, but had lower lexical diversity compared to parents who played with their children as they normally would at home. 
+Parents who watched a Kinedu video also made more bids for joint attention, although these bids did not result in more episodes of joint attention compared to the control group. 
+Experiment 2 attempts to replicate the findings from Experiment 1 with a restricted number of preregistered predictions ([link](https://osf.io/2bpdf/)). 
 We will additionally include a second control condition, in which the same activities are described in written form, rather than being demonstrated in video. 
@@
 
-## Lexical Diversity
+### Lexical Diversity
 ```{r, e2-lexdiv-regressions, echo=F, include=F}
@@
 A similar mixed-effects linear regression instead predicting MTLD found no significant effects of age or condition.
-Figure 1 shows the mean of each lexical diversity measure (TTR and MTLD) by condition.
+Figure X shows the mean of each lexical diversity measure (TTR and MTLD) by condition.
 Regressions with the same structure predicting the number of word tokens and types found no significant effects of age or condition.
@@
 
-## Joint Attention
+### Joint Attention
 ```{r, e2ja-regressions, echo=F, include=F}
@@
 
+There was a marginal effect of condition on total bids for joint attention.
+Parents in the experimental condition (i.e., those who saw a video demonstrating an activity) made a greater number of bids for joint attention with their child.
+There was no effect of condition on the number of episodes of passive or coordinated JA, nor on the duration of these episodes. 
+For passive joint attention, there was a main effect of age on both the number and duration of episodes, with older children having fewer episodes of passive JA and episodes of shorter duration.
+Moreover, older children had longer duration episodes of coordinated JA.
+These results suggest that as children age, they become more socially engaged in interactions with their caregivers.
+
 # Discussion
 
-Similar to results in Experiment 1, the number of tokens was higher in the experimental condition, while the number of types and lexical diversity (Type/Token ratio) were higher in the control condition.
+In both experiments, the number of tokens was higher in the experimental condition, while the number of types and lexical diversity (Type/Token ratio) were higher in the control condition. 
 Parents may be relatively more repetetive in the experimental condition since they are attempting to stick to a specific prescribed task, but they talk more overall.
-There was a marginal effect of condition on total bids for joint attention.
-Parents in the experimental condition (i.e., those who saw a video demonstrating an activity) made a greater number of bids for joint attention with their child.
-There was no effect of condition on the number of episodes of coordinated joint attention.
-There was no effect of condition on the number of episodes of either passive or coordinated joint attention, or the duration of these episodes. 
-However, there was a main effect of age on number of episodes of passive joint attention, duration of passive and coordinated joint attention, 
-with the older children having fewer episodes of passive joint attention, shorter duration of passive joint attention, and longer duration of coordinated joint attention. 
-These results suggest that children become more socially engaging in interactions with their caregivers as they develop.
 
-## Two-column images
+# Acknowledgements
 
-You might want to display a wide figure across both columns.
-To do this, you change the `fig.env` chunk option to `figure*`.
-To align the image in the center of the page, set `fig.align` option to `center`.
-To format the width of your caption text, you set the `num.cols.cap` option to `2`.
+This work was supported by a gift from Kinedu, Inc. 
+Thanks to members of the Language and Cognition Lab at Stanford for helpful discussion.
 

### 2019-04-29 paper/cogsci2019/cogsci2019.tex
writing results

@@
 
-\author{{\large\bf Hanwen Vivian~Zhang} (\texttt{vivian3@stanford.edu}) \\ {\large\bf George~Kachergis} (\texttt{george.kachergis@gmail.com}) \\ {\large\bf Michael C.~Frank} (\texttt{mcfrank@stanford.edu}) \\  Department of Psychology, Stanford University \\  Stanford, CA 94305 USA}
+\author{{\large\bf George~Kachergis} (\texttt{kachergis@stanford.edu}) \\ {\large\bf Hanwen Vivian~Zhang} (\texttt{vivian3@stanford.edu}) \\ {\large\bf Michael C.~Frank} (\texttt{mcfrank@stanford.edu}) \\  Department of Psychology, Stanford University \\  Stanford, CA 94305 USA}
 
@@
 (``apps'') holds the promise of delivering low-cost, positive
-interventions on parenting style to a variety of different populations.
-Of special interest are the parents of very young children, who are
-often difficult to reach in other ways. Yet little is known about the
-effects of communicating to parents through app-based interventions. In
-a study of one commercial app offering a collection of age-appropriate
-activity videos, we find that the quality of parent-child interactions
-increases in some ways as a result of using the app. Specifically, the
-lexical diversity of parents' child-directed speech increases, and
-measures of joint attention show\ldots{}
+interventions on parenting style to a wide variety of populations. Of
+special interest are the parents of very young children, who are often
+difficult to reach in other ways. Yet little is known about the effects
+of communicating to parents through app-based interventions. In a study
+of one commercial app offering a collection of age-appropriate activity
+videos, we find that the quality of parent-child interactions increases
+in some ways as a result of using the app. Specifically, the lexical
+diversity of parents' child-directed speech increases, and measures of
+joint attention show\ldots{}
 
@@
 \section{Introduction}\label{introduction}
+
+Children of any given age show remarkable variability in their levels of
+language proficiency (Fenson et al., 1994),
 
@@
 guidance while scaffolding a child's play (Kaye, 1970; Wood, Bruner, \&
-Ross, 1976). Indeed, parenting practices early in childhood have been
-shown to play an important role in shaping the future outcomes of young
-children (Hart \& Risley, 1995; Heckman, 2006). While interventions
-often have trouble reaching many parents of very young children, the
-proliferation of mobile devices offers a good avenut for the digital
-delivery of parenting advice (Breitenstein, Gross, \& Christophersen,
-2014). However, the efficacy of digital parenting advice has not been
-widely proven.
+Ross, 1976). The quality of interactions during such guided play has
+been shown to influence language learning: parents' joint attention to
+objects that their child was focused on was positively correlated with
+the child's subsequent vocabulary growth (M. Carpenter \& Tomasello,
+1998; Tomasello \& Farrar, 1986). Episodes of joint attention during
+guided play have also been found to contain more age-appropriate
+advanced forms of play (Bigelow, MacLean, \& Proctor, 2004). More
+generally, parenting practices early in childhood have been shown to
+play an important role in shaping the future outcomes of young children
+(Hart \& Risley, 1995; Heckman, 2006). While interventions often have
+trouble reaching many parents of very young children, the proliferation
+of mobile devices offers a good avenut for the digital delivery of
+parenting advice (Breitenstein, Gross, \& Christophersen, 2014).
+However, the efficacy of digital parenting advice has not been widely
+proven.
 
@@
 
-Thus, including guided play in parenting practices early on is crucial
-and will help with children's later performances in academic and social
-situations. To intervene in parenting practices, Suskind and others did
-a parent-directed home-visiting intervention experiment in 2015 for
-children of low socioeconomic status. They showed that parents in
-experimental group have greater knowledge of language development and
-this effect sustained four months after the intervention. However,
-although a number of interactive measures increased during the
-experiment, including the number of word tokens, conversational turns,
-and child vocalizations, these increases did not sustain after the
-intervention (D. L. Suskind et al., 2015). That changes did not sustain
-could be due to the intervention itself, or could merely be that the
-methods of home-visiting is not sustainable enough for parents to easily
-and constantly get parenting advice. Thus, new methods of delivering
-parenting advice should be considered.
+Thus, including guided play in parenting practices from an early age may
+boost children's language and educational outcomes. A recent home-visit
+parenting practices intervention targeting children of low socioeconomic
+status found that parents in the intervention group gained knowledge of
+language development, and that this effect sustained four months after
+the intervention (D. L. Suskind et al., 2015). However, although a
+number of interactive measures increased during the experiment,
+including the number of word tokens, conversational turns, and child
+vocalizations, these increases did not sustain after the intervention.
+That changes did not sustain could be due to the intervention itself, or
+could merely be that the methods of home-visiting is not sustainable
+enough for parents to easily and constantly get parenting advice. Thus,
+new methods of delivering parenting advice should be considered.
 
@@
 both the social engagement of parents (e.g., joint attention to objects
-in the environment)(Bigelow, MacLean, \& Proctor, 2004) and the quality
-of language (e.g., vocabulary diversity) (Malvern, Richards, Chipere, \&
-Durán, 2004).
+in the environment)(Bigelow et al., 2004) and the quality of language
+(e.g., vocabulary diversity) (Malvern, Richards, Chipere, \& Durán,
+2004).
 
@@
 12), other (n = 5), or declined to state (n = 5). Fifteen parents
-reported their child was of Hispanic origin. Parents tended to be
+reported that their child was of Hispanic origin. Parents tended to be
 highly-educated, with reports of highest level of education ranging from
@@
 specific videos is available in the Appendix. Participants were also
-given a set of props corresponding to those in the video they watched so
-that they could complete the activity. The props associated with each
-video are listed in the Appendix.
+given a set of toys corresponding to those in the video that they
+watched so that they could complete the activity. The toys associated
+with each video are listed in the Appendix.
 
 Participants were randomly assigned to either the \emph{Video} condition
-or the \emph{Control} condition. Participating parents in the Video
+or the \emph{Control} condition. Parents participating in the Video
 condition were assigned to watch one of the two activity videos
-available for their child's age group. Participating parents in the
-Control condition watched no activity video, and were merely asked to
-play with their child as they normally would. The Control condition was
-yoked to the Activity Video condition such that for every participant in
-the Video condition who saw a particular video and received the
-associated props, a participant in the Control condition received the
-same props but did not watch the activity video. Parents also completed
-the Parenting Attitudes Questionnaire (PAQ). The PAQ measures parents'
-attitudes about parenting and child development along three dimensions:
-rules and respect, early learning, and affection and attachment.
+available for their child's age group, while parents in the Control
+condition watched no activity video, and were simply asked to play with
+their child as they normally would. The Control condition was yoked to
+the Activity Video condition such that for every participant in the
+Video condition who saw a particular video and received the associated
+props, a participant in the Control condition received the same props
+but did not watch the activity video. Parents also completed the Early
+Parenting Attitudes Questionnaire (EPAQ; (Hembacher \& Frank, 2018)).
+The EPAQ measures parents' attitudes about parenting and child
+development along three dimensions: rules and respect, early learning,
+and affection and attachment.
 
@@
 condition, age (scaled and 0-centered), gender, and parent's education
-level with a random intercept per video using lme4 (Bates, Mächler,
+level with a random intercept per video using lme4 (D. Bates, Mächler,
 Bolker, \& Walker, 2015). There was significantly lower TTR in the Video
@@
 
+We fit a mixed-effects linear regression predicting the number of bids
+for joint attention (JA) as a function of fixed effects of condition,
+age (scaled and 0-centered), gender, parent's education level, and the
+subscales of the EPAQ: Early Learning (EL), Affection and Attachment
+(AA), and Rules and Respect (RR), along with interactions of condition
+and EL, AA, and RR. This lme4 model included random intercepts per
+video. There were significantly more bids for JA in the Video condition
+(mean: X) than in the Control condition (mean: X, \(\beta=3.51\),
+t(40.3) = 2.95, \emph{p}\textless{}.01). There were no other significant
+effects. Mixed-effects regressions with the same structure were
+performed predicting the number of episodes of coordinated and passive
+JA, and the total duration of time spent in coordinated and passive JA.
+There were no significant effects on the number or total duration of
+coordinated JA episodes, nor on the total duration of passive JA
+episodes. For the regression predicting the number of passive joint
+attention episodes, the only significant effect was an interaction of
+condition and RR (\(\beta=1.83\), t(41.5) = 2.22,
+\emph{p}\textless{}.05), showing that\ldots{} Figure X shows \ldots{} by
+condition.
+
 \begin{CodeChunk}
@@
 
-Both the number of tokens and types are higher in the experimental
-condition, while lexical diversity (Type/Token ratio) is higher in the
-control condition. Parents may be relatively more repetetive in the
-experimental condition since they are attempting to stick to a specific
-prescribed task, but they talk more overall. Demographics and PAQ do not
-interact with condition, but there is a marginal effect of RR score on
-lexical diversity (lower diversity for higher RR scores), and marginal
-effects of parent education on word types and tokens (more types and
-tokens for higher parent education).
+In summary, while the number of tokens and types were higher in the
+experimental condition, lexical diversity (Type/Token ratio) was higher
+in the control condition. Parents may be relatively more repetetive in
+the experimental condition since they are attempting to stick to a
+specific prescribed task, but they talk more overall. Demographics and
+PAQ do not interact with condition, but there is a marginal effect of RR
+score on lexical diversity (lower diversity for higher RR scores), and
+marginal effects of parent education on word types and tokens (more
+types and tokens for higher parent education).
 
 There was a main effect of condition on total bids for joint attention.
-Parents in the experimental condition (i.e., those who saw a video
-demonstrating an activity) made a greater number of bids for joint
-attention with their child. There was no effect of condition on the
-number of episodes of either passive or coordinated joint attention, or
-the duration of these episodes. There is a marginal effect of gender on
-bids for joint attention, with parents of males producing more bids.
-There is a marginal interaction between RR scores and condition on
-passive joint attention, such that the experimental condition increased
-the number of episodes of PJA to a greater extent for people with high
-RR scores. While the electronically-delivered parenting advice increased
-the number of bids for joint attention by parents, it did not
-significantly effect the number or duration of episodes of joint
-attention. One possibility is that child variables had a comparatively
-larger impact on the attainment of joint attention.
+Parents in the Video condition, after seeing a video demonstrating an
+activity, made a greater number of bids for joint attention with their
+child. There was no effect of condition on the number of episodes of
+either passive or coordinated joint attention, or the duration of these
+episodes. There was a marginal effect of gender on bids for joint
+attention, with parents of males producing more bids. There was a
+marginal interaction between RR scores and condition on passive joint
+attention, such that the experimental condition increased the number of
+episodes of PJA to a greater extent for people with high RR scores.
+While the electronically-delivered parenting advice increased the number
+of bids for joint attention by parents, it did not significantly effect
+the number or duration of episodes of joint attention. It may be that
+child variables had a larger relative impact on the attainment of joint
+attention.
 
@@
 
-Experiment 1 found that compared to parents who did not watch a video,
-parents who watched a Kinedu video spoke more words overall, but had
-lower lexical diversity. Parents who watched a video also made more bids
-for joint attention, although these bids did not result in more episodes
-of joint attention compared to the control group. In Experiment 2 we
-attempt to replicate the findings from Experiment 1 with a restricted
-number of preregistered predictions. We will additionally include a
-second control condition, in which the same activities are described in
-written form, rather than being demonstrated in video. This manipulation
-will help determine what the contribution of the video demonstration is
-in producing the observed effects on parent-child interactions.
+Experiment 1 found that compared to parents who played with children as
+they normally would, parents who watched a Kinedu video spoke more words
+overall, but had lower lexical diversity. Parents who watched a video
+also made more bids for joint attention, although these bids did not
+result in more episodes of joint attention compared to the control
+group. Experiment 2 attempts to replicate the findings from Experiment 1
+with a restricted number of preregistered predictions. We will
+additionally include a second control condition, in which the same
+activities are described in written form, rather than being demonstrated
+in video. This manipulation will help determine what the contribution of
+the video demonstration is in producing the observed effects on
+parent-child interactions.
 
@@
 
-Parents' child-directed speech was transcribed and processed in the same
-way as in Experiment 1.
+Parents' child-directed speech was transcribed and processed according
+to the same procedure used in Experiment 1.
 
@@
 We fit a mixed-effects linear regression predicting TTR and MTLD as a
-function of age (scaled and 0-centered) and condition with a random
-intercept per video using lme4 (Bates et al., 2015). There was
-significantly lower TTR in the Video condition (mean: 0.38) than in the
-Control condition (mean: 0.47, \(\beta=-.09\), t(8.7) = 3.06,
-\emph{p}=.01). There was no significant effect of age. A similar
-mixed-effects linear regression instead predicting MTLD found no
-significant effects of age or condition. Figure 1 shows the mean of each
-lexical diversity measure (TTR and MTLD) by condition.
-
-We also conducted similar regressions predicting the number of word
-tokens and types, finding no significant effects of of age or condition.
+function of age (scaled and 0-centered) and condition with an
+interaction term, and with random intercepts per video using lme4 (D.
+Bates et al., 2015). There was significantly lower TTR in the Video
+condition (mean: 0.38) than in the Control condition (mean: 0.47,
+\(\beta=-.09\), t(8.7) = 3.06, \emph{p}=.01). There was no significant
+effect of age. A similar mixed-effects linear regression instead
+predicting MTLD found no significant effects of age or condition. Figure
+1 shows the mean of each lexical diversity measure (TTR and MTLD) by
+condition. Regressions with the same structure predicting the number of
+word tokens and types found no significant effects of age or condition.
 
@@
 
+\hypertarget{ref-Fenson1994}{}
+Fenson, L., Dale, P. S., Reznick, J. S., Bates, E., Thal, D. J.,
+Pethick, S. J., \ldots{} Stiles, J. (1994). Variability in early
+communicative development. \emph{Monographs of the Society for Research
+in Child Development}, i--185.
+
 \hypertarget{ref-Hart1995}{}
@@
 \url{http://doi.org/10.1126/science.1128898}
+
+\hypertarget{ref-Hembacher2018}{}
+Hembacher, E., \& Frank, M. C. (2018). The early parenting attitudes
+questionnaire: Measuring intuitive theories of parenting and child
+development. \emph{PsyArXiv}. \url{http://doi.org/10.31234/osf.io/hxk3d}
 
@@
 University}.
+
+\hypertarget{ref-Carpenter1998}{}
+M. Carpenter, K. Nagell, \& Tomasello, M. (1998). Social cognition,
+joint attention, and communicative competence from 9 to 15 months of
+age. \emph{Monographs of the Society for Research in Child Development},
+\emph{63}(4), i--vi, 1--143.
 
@@
 
+\hypertarget{ref-Tomasello1986}{}
+Tomasello, M., \& Farrar, M. J. (1986). Joint attention and early
+language. \emph{Child Development}, \emph{57}(6), 1454--1463.
+
 \hypertarget{ref-Vygotsky1980}{}

### 2019-05-15 paper/cogsci2019/cogsci2019.Rmd
minor edits

@@
 author-information: > 
-    \author{{\large\bf George~Kachergis} (\texttt{kachergis@stanford.edu}) \\
-    {\large\bf Hanwen Vivian~Zhang} (\texttt{vivian3@stanford.edu}) \\
-    {\large\bf Michael C.~Frank} (\texttt{mcfrank@stanford.edu}) \\ 
-    Department of Psychology, Stanford University \\ 
-    Stanford, CA 94305 USA}
+    \author{ 
+      {\large\bf George~Kachergis}^1 (\texttt{kachergis@stanford.edu}) \\
+      {\large\bf Emily~Hembacher}^2 (\texttt{emily.hembacher@gmail.com}) \\
+      {\large\bf Veronica~Cristiano}^2 (\texttt{CRISTIANO @gallaudet.edu}) \\
+      {\large\bf Hanwen Vivian~Zhang}^1 (\texttt{vivian3@stanford.edu}) \\
+      {\large\bf Michael C.~Frank}^1 (\texttt{mcfrank@stanford.edu}) \\ 
+    ^{1}Department of Psychology, Stanford University \\ 
+    Stanford, CA 94305 USA \\
+    ^{2} Nextdoor, Inc., Burlingame, CA \\
+    ^{3} Gallaudet University 
+    }
 
@@
 Parents who watched a Kinedu video also made more bids for joint attention, although these bids did not result in more episodes of joint attention compared to the control group. 
-Experiment 2 attempts to replicate the findings from Experiment 1 with a restricted number of preregistered predictions ([link](https://osf.io/2bpdf/)). 
-We will additionally include a second control condition, in which the same activities are described in written form, rather than being demonstrated in video. 
-This manipulation will help determine what the contribution of the video demonstration is in producing the observed effects on parent-child interactions.
+Experiment 2 attempts to replicate these findings from with a restricted number of preregistered predictions ([link](https://osf.io/2bpdf/)).
 
@@
 
-(Table with mean and SD of tokens, types, and TTR)
+(Table with mean and SD of tokens, types, TTR, MTLD)
 

### 2019-05-15 paper/cogsci2019/cogsci2019.Rmd
added Appendix skeleton

@@
 ### Materials.
+
 The design of Experiment 2 was similar to that of Experiment 1, except that instead of a No-Video control condition, parents instead watched a video that was generally related to child development research, but did not give any specific instructions about how to interact with infants or children.
@@
 Thus, the content of the videos superficially matched those in the Activity Video condition, but did not suggest any particular activities.
-The videos were trimmed to approximately match the average video length in the Activity Video condition around 1.5 minutes.
+The videos were trimmed to approximately match the average video length in the Activity Video condition (close to 90 s).
 
@@
 \noindent
+
+# Appendix
+
+## Experiment 1
+
+### Video A (6-11.9 months) "Pick it up"
+
+Parents are told to encourage their child to pick up and drop individual objects.
+They are also encouraged to place toys on a small cloth and show the child that they can drag the cloth towards them to reach the toys.
+
+Props: cloth, small plastic horse, small plastic sheep, small plastic elephant, small toy car
+
+### Video B (6-11.9 months) “Animal sounds”
+
+### Video C (12-17.9 months)
+
+### Video D (12-17.9 months)
+
+### Video E (18-23.9 months)
+
+### Video F (18-23.9 months)
+
+## Experiment 2
+
+### Video A (12-17.9 months)
+
+### Video B (12-17.9 months)
+
+### Video C (12-17.9 months)
+
+### Video D (18-23.9 months)
+
+### Video E (18-23.9 months)
+
+### Video F (18-23.9 months)

### 2019-05-20 paper/cogsci2019/cogsci2019.Rmd
writing

@@
     ^{2} Nextdoor, Inc., Burlingame, CA \\
-    ^{3} Gallaudet University 
+    ^{3} Gallaudet University, Washington, D.C.
     }
@@
 ### Joint Attention Coding Procedure.
-The video of each session was manually coded for episodes of joint attention using the Datavyu software [@datavyu]. 
+The video of each session was manually coded for episodes of joint attention (JA) using the Datavyu software [@datavyu]. 
 The video taken at floor level was coded by default, but the other video was referred to if the participants were not visible or if there was technical difficulty with the first camera. 
-Each session's video was coded for episodes of coordinated joint attention, episodes of passive joint attention, and parental bids for joint attention. 
-Parental bids for joint attention were defined as any attempt to initiate joint attention (i.e labeling, pointing, or otherwise drawing attention to an object) that did not result in passive or coordinated joint attention.
+Each session's video was coded for episodes of coordinated JA, episodes of passive JA, and parental bids for JA. 
+Parental bids for JA were defined as any attempt to initiate joint attention (i.e labeling, pointing, or otherwise drawing attention to an object) that did not result in passive or coordinated JA. 
 If more than 3 seconds elapsed between bids, they were coded as separate attempts. 
@@
 
-We fit a mixed-effects linear regression predicting the number of bids for joint attention (JA) as a function of fixed effects of condition, age (scaled and 0-centered), gender, parent's education level, and the subscales of the EPAQ: Early Learning (EL), Affection and Attachment (AA), and Rules and Respect (RR), along with interactions of condition and EL, AA, and RR.
-This lme4 model included random intercepts per video.
-There were significantly more bids for JA in the Video condition (mean: X) than in the Control condition (mean: X, $\beta=3.51$, t(40.3) = 2.95, *p*<.01). 
-There were no other significant effects.
-Mixed-effects regressions with the same structure were performed predicting the number of episodes of coordinated and passive JA, and the total duration of time spent in coordinated and passive JA.
-There were no significant effects on the number or total duration of coordinated JA episodes, nor on the total duration of passive JA episodes. 
-For the regression predicting the number of passive joint attention episodes, the only significant effect was an interaction of condition and RR ($\beta=1.83$, t(41.5) = 2.22, *p*<.05), showing that...
-Figure X shows ... by condition.
-
 ```{r, e1ja-regressions, echo=F, include=F}
@@
 
+bid_cond <- lmer_data %>% group_by(Condition) %>% 
+  summarise(mean = mean(bids), sd = sd(bids)) 
+print(bid_cond)
+
 # Episodes of coordinated joint attention.
@@
 ```
+
+We fit a mixed-effects linear regression predicting the number of bids for joint attention (JA) as a function of fixed effects of condition, age (scaled and 0-centered), gender, parent's education level, and the subscales of the EPAQ: Early Learning (EL), Affection and Attachment (AA), and Rules and Respect (RR), along with interactions of condition and EL, AA, and RR.
+This lme4 model included random intercepts per video.
+There were significantly more bids for JA in the Video condition (mean: 6.24, sd: 2.79) than in the Control condition (mean: 3.56, sd: 2.50, $\beta=3.51$, t(40.3) = 2.95, *p*<.01). 
+There were no other significant effects.
+Mixed-effects regressions with the same structure were performed predicting the number of episodes of coordinated and passive JA, and the total duration of time spent in coordinated and passive JA.
+There were no significant effects on the number or total duration of coordinated JA episodes, nor on the total duration of passive JA episodes. 
+For the regression predicting the number of passive JA episodes, the only significant effect was an interaction of condition and RR ($\beta=1.83$, t(41.5) = 2.22, *p*<.05), showing that for parents in the Video condition, those with higher Rules and Respect subscores engaged in more passive JA episodes.
+Figure X shows ... by condition.
 
@@
 In summary, while parents produced more word types and tokens after viewing the activity video, lexical diversity (Type/Token ratio and MTLD) was higher when parents were just asked to play as they normally would.
-Parents may be relatively more repetetive in the experimental condition since they are attempting to stick to a specific prescribed task, but they talk more overall.
+This may suggest that parents in the Video condition are being more repetitive in their attempt to stick to the task prescribed in the video.
 Demographics and EPAQ do not interact with condition, but there is a marginal effect of RR score on lexical diversity (lower diversity for higher RR scores), and marginal effects of parent education on word types and tokens (more types and tokens for higher parent education).

### 2019-05-22 paper/cogsci2019/cogsci2019.Rmd
editing intro

@@
 ---
-title: "Understanding the impact of electronically-delivered parenting advice"
+title: "Understanding the impacts of video activity guides on parent-child interaction"
 bibliography: library.bib
@@
 
-Children of any given age show remarkable variability in their levels of language proficiency [@Fenson1994],
+The quantity and quality of early language input has been found to be strongly associated with later language and academic outcomes [@Hart1995; @Marchman2008; @cartmill2012; @HirshPasek2015].
+Thus, because of the potential for large downstream effects [@Heckman2006], there is tremendous interest in interventions that change children's language environment.
+And because parents define a large portion of that environment, especially before the onset of formal schooling, parent behavior is a critical locus for such interventions. 
+Many effective parenting interventions require large resource investments and require many hours of in-person contact [@Jamaica2014; @PerryPreschool2004], making implementation at scale a daunting proposition.
+For this reason, many researchers targeting early language are interested in delivering parenting interventions remotely -- through texts, apps, and videos. 
+But what do parents take away from these short messages about what to do or how to talk?
+
+The content provided by digital parenting interventions runs the gamut from general parenting messages and facts from child development research to specific advice and suggested activities. 
+A growing body of evidence suggests that these digital interventions can be effective in a range of contexts [@Breitenstein2014]. AGE RANGE
+For example, HIGHLIGHT ONE INTERVENTION.
+Often, however, the theory of change presupposed by such interventions is relatively vague.
+Both within and outside the realm of academic interventions, mesages to parents of young children often seek to provide knowledge about some aspect of developent (e.g., early language), often in tandem with a suggestion regarding activities.
+Such messages are assumed to inform parents' behavior choice and spur them to engage in the target activity, which is assumed to be more stimulating than what parents would have done otherwise.
+
+This theory of change is grounded in ideas about guided play and early language stimulation. 
+TOKEN DIVERSITY [@Malvern2004]
+Further, language learning -- especially the acquisition of early vocabulary in the first years -- appears to be supported preferentially by joint attention, DEF. [@Bigelow2004]
+Guided PLAY link here? 
+Thus, the current literature supports interventions that encourage parents to provide high quality language and interaction through something like guided play -- whether via reading books or playing with a shape-sorter at home, or via a conversation about categories in the supermarket.
+
+But is this theory of change correct? That is, does the provision of knowledge and activities lead to higher-quality play? 
+An alternative hypothesis is that this theory could be wrong in a number of ways. 
+By focusing parents on a specific activity, they could over-focus on achieving the superficial goals of the activity. 
+This problem might be especially likely with video messages, which could encourage parents to try to mimic a model. 
+And these misinterpretation in turn could result in less high quality talk, with less joint attention. 
+Or, these messages could produce the desired effect, but only for those parents who already have a general orientation towards children's early learning.
+
+Our current experiments were designed to make a direct test of this question: how do parents change their interactions with young children on the basis of short video parenting messages? 
+In both studies, we collected data from parent-child dyads in a local children's museum. 
+We showed parents in the experimental group a single short video modeling an interactive toy-based activity along with a scientific justification. 
+Parents in the control group received either no video (Experiment 1) or a video of a recent finding in developmental psychology (Experiment 2). 
+We then gave the toys from the video to all dyads and videotaped their interactions, coding for language quantity and quality as well as joint attention.
+
+partners such as their caregivers and older siblings [@Kaye1970]. 
+Under such expert guidance, children are encouraged and motivated to engage in more advanced play, undertaking explorations that push the boundaries of what they would be able to do unaided [@Vygotsky1980].
+These tutorial interactions have been shown to be important components of child development [@Wood1976].
+Thus, with the knowledge of both play and tutorial interactions, guided play, which consists of both active and enjoyable activities as well as close guidance of adults [@Hirsh2008] has drawn researchers' interest.
+A study of preschoolers showed that guided play scaffolds the environment while still allowing children to maintain a large degree of control, 
+and it outperforms direct-instruction approaches in encouraging a variety of positive academic outcomes [@Weisberg2013].
+
+But does providing such information change parents' behavior towards young children?
+And are those changes effective in producing change along the desired dimension?
+An alternative might be that asking parents to focus on a specific activity could result in decreases in
+
+What are digital interventions
+With the widespread use of smartphones and tablets worldwide, digitally-delivered interventions could address many of the logistical barriers that have limited scaling up face-to-face delivery methods.
+A review of 11 studies verified that 
+However, the parent and child outcomes assessed in the review (e.g.infant positive behaviors, satisfaction, emotional symptoms etc.) did not address the nature or quality of parent-infant interactions at a detailed level, for example whether the interventions lead to children paying more attention, or vocabulary changes in parents' language usages.
+Although digitally-delivered ac-tivities are designed to promote learning and cognitive development, it is unclear how they might affect these dimensions of parent-child interactions.
+Thus, we want to conduct this experiment to explore if and how digital scaffolding of activities affect the social and linguistic characteristics of parent-child ineractions.
+The quality of parent-child interactions can be measured by both the social engagement of parents (e.g., joint attention to objects in the environment)[@Bigelow2004] and the quality of language (e.g., vocabulary diversity) [@Malvern2004].
+
+Communication and message conntet
+
+In our study, we focus on videos that provide suggested play activities to parents. 
+These videos constitute a short-term "guided play" intervention.
 
@@
 ## Effectiveness of Digital Delivery
-With the widespread use of smartphones and tablets worldwide, digitally-delivered interventions could address many of the logistical barriers that have limited scaling up face-to-face delivery methods.
-A review of 11 studies verified that digital delivery is a promising means of effectively distributing interventions [@Breitenstein2014].
-However, the parent and child outcomes assessed in the review (e.g.infant positive behaviors, satisfaction, emotional symptoms etc.) did not address the nature or quality of parent-infant interactions at a detailed level,
-like if the interventions lead to children paying more attention, or vocabulary changes in parents' language usages. 
-Although digitally-delivered ac-tivities are designed to promote learning and cognitive development, it is unclear how they might affect these dimensions of parent-child interactions.
-Thus, we want to conduct this experiment to explore if and how digital scaffolding of activities affect the social and linguistic characteristics of parent-child ineractions.
-The quality of parent-child interactions can be measured by both the social engagement of parents (e.g., joint attention to objects in the environment)[@Bigelow2004] and the quality of language (e.g., vocabulary diversity) [@Malvern2004].
 

### 2019-05-22 paper/cogsci2019/cogsci2019.Rmd
update Appendix

--- 2019-05-20 paper/cogsci2019/cogsci2019.Rmd
@@
 
-### Video A (12-17.9 months)
+### Video A (12-17.9 months) "Give me the toy"
 
-### Video B (12-17.9 months)
+Parents are told to ask their child to hand over individual toys.
+They are also encouraged to praise the child after they give them the toys, and repeat the process until the child could follow the verbal instructions.
 
-### Video C (12-17.9 months)
+Props: plastic pig, plastic horse, plastic dog, plastic cat, plastic cow
 
-### Video D (18-23.9 months)
+### Video B (12-17.9 months) "Classifying my toys"
 
-### Video E (18-23.9 months)
+Parents are told to place toys of different sizes (big or small) in two hoops. They are also encouraged to ask their child to distinguish between two objects and identify which one is larger.
 
-### Video F (18-23.9 months)
+Props: two yellow and green rings, big car, small car, big horse, small horse
+
+### Video C (12-17.9 months) "Geometric shapes jigzsaw puzzle"
+
+Parents are told to encourage their child to name different shapes on a jigzsaw puzzle. Then they are told to undo the puzzle and invite the child to complete the puzzle.
+
+Props: A jigzsaw puzzle of geometric shapes
+
+### Video D (18-23.9 months) "My toys II"
+
+Parents are told to show the child toys of the same shape but different sizes, to place one of the objects in a basket and to ask the child to take out the object.
+They are also encoureaged to ask their child if the object is bigger or smaller compared to its pair.
+
+Props: two buckets, big car, small car, big horse, small horse
+
+### Video E (18-23.9 months) "The Orchestra"
+
+Parents are told to give their child a musical instrument to play. They are also encouraged to play a song and see if the child follows the rhythm.
+
+Props: maracas, drum, tambourine, clapper
+
+### Video F (18-23.9 months) "My Yellow Toys"
+
+Parents are told to show their child yellow toys and to ask "what color are they".
+They are also told to give the child toys of different colors, ask them to only play with the yellow ones and praise the child after they do so.
+
+Props: blue car, yellow car, yellow block, red block, blue block, green block

### 2019-06-15 paper/cogsci2019/cogsci2019.Rmd
cleaning up intro

@@
 
-output: cogsci2016::cogsci_paper
+output: pdf_document
 final-submission: \cogscifinalcopy
@@
 
-The quantity and quality of early language input has been found to be strongly associated with later language and academic outcomes [@Hart1995; @Marchman2008; @cartmill2012; @HirshPasek2015].
+The quantity and quality of early language input has been found to be strongly associated with later language and academic outcomes [@Hart1995; @Marchman2008; @Cartmill2013; @HirshPasek2015].
 Thus, because of the potential for large downstream effects [@Heckman2006], there is tremendous interest in interventions that change children's language environment.
@@
 Many effective parenting interventions require large resource investments and require many hours of in-person contact [@Jamaica2014; @PerryPreschool2004], making implementation at scale a daunting proposition.
-For this reason, many researchers targeting early language are interested in delivering parenting interventions remotely -- through texts, apps, and videos. 
-But what do parents take away from these short messages about what to do or how to talk?
+For this reason, many researchers targeting early language are interested in delivering parenting interventions remotely -- through texts, apps, and videos delivered on digital devices. 
+But what do parents take away from these short messages about what to do or how to talk with their children?
 
 The content provided by digital parenting interventions runs the gamut from general parenting messages and facts from child development research to specific advice and suggested activities. 
-A growing body of evidence suggests that these digital interventions can be effective in a range of contexts [@Breitenstein2014]. AGE RANGE
-For example, HIGHLIGHT ONE INTERVENTION.
+A growing body of evidence suggests that these digital interventions can be effective across a range of cultures, income levels, and children's ages (for a review, see )[@Breitenstein2014].
+For example, in contrast to a face-to-face parent training intervention, a tablet-based version saw significantly higher session completion rates (51% attendance vs.
+85% module completion) and comparable or larger effect sizes on parents' and children's (aged 2 to 5 years) behavior [@Breitenstein2016].
 Often, however, the theory of change presupposed by such interventions is relatively vague.
-Both within and outside the realm of academic interventions, mesages to parents of young children often seek to provide knowledge about some aspect of developent (e.g., early language), often in tandem with a suggestion regarding activities.
-Such messages are assumed to inform parents' behavior choice and spur them to engage in the target activity, which is assumed to be more stimulating than what parents would have done otherwise.
+Both within and outside the realm of academic interventions, messages to parents of young children often seek to provide knowledge about some aspect of development (e.g., early language), often in tandem with a suggestion regarding activities.
+Such messages are assumed to inform parents' choice of behaviors, spurring them to engage in the target activity, which is assumed to be more stimulating than what parents would have done otherwise.
 
 This theory of change is grounded in ideas about guided play and early language stimulation. 
-TOKEN DIVERSITY [@Malvern2004]
-Further, language learning -- especially the acquisition of early vocabulary in the first years -- appears to be supported preferentially by joint attention, DEF. [@Bigelow2004]
-Guided PLAY link here? 
-Thus, the current literature supports interventions that encourage parents to provide high quality language and interaction through something like guided play -- whether via reading books or playing with a shape-sorter at home, or via a conversation about categories in the supermarket.
+Language input varies not only in quantity (i.e., the number of total tokens), but also in quality (i.e., the diversity of the tokens) [@Malvern2004].
+Further, language learning -- especially the acquisition of early vocabulary in the first years -- appears to be supported preferentially by parents and children _jointly attending_ to some object or activity [@Bigelow2004].
+Episodes of joint attention are frequent during guided play, when parents set goals and scaffold their child's activities [@Wood1976; @Weisberg2013].
+Thus, the current literature supports interventions that encourage parents to provide high-quality language and interaction through something like guided play -- whether via reading books or playing with a shape-sorter at home, or via a conversation about categories in the supermarket.
 
@@
 This problem might be especially likely with video messages, which could encourage parents to try to mimic a model. 
-And these misinterpretation in turn could result in less high quality talk, with less joint attention. 
+And these misinterpretations in turn could result in less high-quality talk, with less joint attention. 
 Or, these messages could produce the desired effect, but only for those parents who already have a general orientation towards children's early learning.
 
-Our current experiments were designed to make a direct test of this question: how do parents change their interactions with young children on the basis of short video parenting messages? 
+Our current experiments were designed to make a direct test of this question: How do parents change their interactions with young children on the basis of short video parenting messages? 
 In both studies, we collected data from parent-child dyads in a local children's museum. 
@@
 
-partners such as their caregivers and older siblings [@Kaye1970]. 
 Under such expert guidance, children are encouraged and motivated to engage in more advanced play, undertaking explorations that push the boundaries of what they would be able to do unaided [@Vygotsky1980].
-These tutorial interactions have been shown to be important components of child development [@Wood1976].
-Thus, with the knowledge of both play and tutorial interactions, guided play, which consists of both active and enjoyable activities as well as close guidance of adults [@Hirsh2008] has drawn researchers' interest.
-A study of preschoolers showed that guided play scaffolds the environment while still allowing children to maintain a large degree of control, 
-and it outperforms direct-instruction approaches in encouraging a variety of positive academic outcomes [@Weisberg2013].
 
 But does providing such information change parents' behavior towards young children? 
-And are those changes effective in producing change along the desired dimension?
-An alternative might be that asking parents to focus on a specific activity could result in decreases in
+And is this advice effective in producing change along the desired dimension? 
+An alternative might be that asking parents to focus on a specific activity that may be novel to them may tax their cognitive resources, resulting in decreases in the quality of their child-directed speech, or in less flexible, lower-quality social interactions.
 
@@
 With the widespread use of smartphones and tablets worldwide, digitally-delivered interventions could address many of the logistical barriers that have limited scaling up face-to-face delivery methods.
-A review of 11 studies verified that 
 However, the parent and child outcomes assessed in the review (e.g.infant positive behaviors, satisfaction, emotional symptoms etc.) did not address the nature or quality of parent-infant interactions at a detailed level, for example whether the interventions lead to children paying more attention, or vocabulary changes in parents' language usages.
-Although digitally-delivered ac-tivities are designed to promote learning and cognitive development, it is unclear how they might affect these dimensions of parent-child interactions.
+Although digitally-delivered activities are designed to promote learning and cognitive development, it is unclear how they might affect these dimensions of parent-child interactions.
 Thus, we want to conduct this experiment to explore if and how digital scaffolding of activities affect the social and linguistic characteristics of parent-child ineractions.
@@
 
-Communication and message conntet
+Communication and message content
 
@@
 
-Props: cloth, small plastic horse, small plastic sheep, small plastic elephant, small toy car
+Props: cloth, plastic horse, plastic sheep, plastic elephant, toy car
 
@@
 
-### Video C (12-17.9 months)
+Parents are told to call different animals and imitate different sounds the animals make. They are also encourgaed to observe which animal the child prefers.
 
-### Video D (12-17.9 months)
+Props: plastic sheep, plastic horse, plastic frog, plastic cow, bowls
 
-### Video E (18-23.9 months)
+### Video C (12-17.9 months) "Give me the toy"
 
-### Video F (18-23.9 months)
+Parents are told to ask their child to hand over individual toys.
+They are also encouraged to praise the child after they give them the toys, and repeat the process until the child could follow the verbal instructions.
+
+Props: toy boat, plastic frog, plastic elephant, toy bus
+
+### Video D (12-17.9 months) "Classifying my toys"
+
+Parents are told to place toys of different sizes (big or small) in two hoops. They are also encouraged to ask their child to distinguish between two objects and identify which one is larger.
+
+Props: two yellow and green rings, big car, small car, big horse, small horse
+
+### Video E (18-23.9 months) "My toys"
+
+Parents are told to show the child toys of the same shape but different sizes, to place one of the objects in a basket and to ask the child to take out the object.
+They are also encouraged to ask their child if the object is bigger or smaller compared to its pair.
+
+Props: two buckets, big car, small car, big horse, small horse
+
+### Video F (18-23.9 months) "The Orchestra"
+
+Parents are told to give their child a musical instrument to play. They are also encouraged to play a song and see if the child follows the rhythm.
+
+Props: maracas, drum, tambourine, clapper
 
@@
 
-### Video D (18-23.9 months) "My toys II"
+### Video D (18-23.9 months) "My toys"
 
 Parents are told to show the child toys of the same shape but different sizes, to place one of the objects in a basket and to ask the child to take out the object.
-They are also encoureaged to ask their child if the object is bigger or smaller compared to its pair.
+They are also encouraged to ask their child if the object is bigger or smaller compared to its pair.
 

### 2019-06-15 paper/cogsci2019/cogsci2019.tex
cleaning up intro

@@
-% Template for Cogsci submission with R Markdown
+\documentclass[]{article}
+\usepackage{lmodern}
+\usepackage{amssymb,amsmath}
+\usepackage{ifxetex,ifluatex}
+\usepackage{fixltx2e} % provides \textsubscript
+\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
+  \usepackage[T1]{fontenc}
+  \usepackage[utf8]{inputenc}
+\else % if luatex or xelatex
+  \ifxetex
+    \usepackage{mathspec}
+  \else
+    \usepackage{fontspec}
+  \fi
+  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
+\fi
+% use upquote if available, for straight quotes in verbatim environments
+\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
+% use microtype if available
+\IfFileExists{microtype.sty}{%
+\usepackage{microtype}
+\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
+}{}
+\usepackage[margin=1in]{geometry}
+\usepackage{hyperref}
+\hypersetup{unicode=true,
+            pdftitle={Understanding the impacts of video activity guides on parent-child interaction},
+            pdfkeywords={digital parenting advice; joint attention; lexical diversity; guided
+play;},
+            pdfborder={0 0 0},
+            breaklinks=true}
+\urlstyle{same}  % don't use monospace font for urls
+\usepackage{graphicx,grffile}
+\makeatletter
+\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
+\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
+\makeatother
+% Scale images if necessary, so that they will not overflow the page
+% margins by default, and it is still possible to overwrite the defaults
+% using explicit options in \includegraphics[width, height, ...]{}
+\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
+\IfFileExists{parskip.sty}{%
+\usepackage{parskip}
+}{% else
+\setlength{\parindent}{0pt}
+\setlength{\parskip}{6pt plus 2pt minus 1pt}
+}
+\setlength{\emergencystretch}{3em}  % prevent overfull lines
+\providecommand{\tightlist}{%
+  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
+\setcounter{secnumdepth}{0}
+% Redefines (sub)paragraphs to behave more like sections
+\ifx\paragraph\undefined\else
+\let\oldparagraph\paragraph
+\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
+\fi
+\ifx\subparagraph\undefined\else
+\let\oldsubparagraph\subparagraph
+\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
+\fi
 
-% Stuff changed from original Markdown PLOS Template
-\documentclass[10pt, letterpaper]{article}
+%%% Use protect on footnotes to avoid problems with footnotes in titles
+\let\rmarkdownfootnote\footnote%
+\def\footnote{\protect\rmarkdownfootnote}
 
-\usepackage{cogsci}
-\usepackage{pslatex}
-\usepackage{float}
-\usepackage{caption}
+%%% Change title format to be more compact
+\usepackage{titling}
 
-% amsmath package, useful for mathematical formulas
-\usepackage{amsmath}
+% Create subtitle command for use in maketitle
+\providecommand{\subtitle}[1]{
+  \posttitle{
+    \begin{center}\large#1\end{center}
+    }
+}
 
-% amssymb package, useful for mathematical symbols
-\usepackage{amssymb}
+\setlength{\droptitle}{-2em}
 
-% hyperref package, useful for hyperlinks
-\usepackage{hyperref}
-
-% graphicx package, useful for including eps and pdf graphics
-% include graphics with the command \includegraphics
-\usepackage{graphicx}
-
-% Sweave(-like)
-\usepackage{fancyvrb}
-\DefineVerbatimEnvironment{Sinput}{Verbatim}{fontshape=sl}
-\DefineVerbatimEnvironment{Soutput}{Verbatim}{}
-\DefineVerbatimEnvironment{Scode}{Verbatim}{fontshape=sl}
-\newenvironment{Schunk}{}{}
-\DefineVerbatimEnvironment{Code}{Verbatim}{}
-\DefineVerbatimEnvironment{CodeInput}{Verbatim}{fontshape=sl}
-\DefineVerbatimEnvironment{CodeOutput}{Verbatim}{}
-\newenvironment{CodeChunk}{}{}
-
-% cite package, to clean up citations in the main text. Do not remove.
-\usepackage{apacite}
-
-% KM added 1/4/18 to allow control of blind submission
-\cogscifinalcopy
-
-\usepackage{color}
-
-% Use doublespacing - comment out for single spacing
-%\usepackage{setspace}
-%\doublespacing
-
-% % Text layout
-% \topmargin 0.0cm
-% \oddsidemargin 0.5cm
-% \evensidemargin 0.5cm
-% \textwidth 16cm
-% \textheight 21cm
-
-\title{Understanding the impact of electronically-delivered parenting advice}
-
-\author{{\large\bf George~Kachergis} (\texttt{kachergis@stanford.edu}) \\ {\large\bf Hanwen Vivian~Zhang} (\texttt{vivian3@stanford.edu}) \\ {\large\bf Michael C.~Frank} (\texttt{mcfrank@stanford.edu}) \\  Department of Psychology, Stanford University \\  Stanford, CA 94305 USA}
+  \title{Understanding the impacts of video activity guides on parent-child
+interaction}
+    \pretitle{\vspace{\droptitle}\centering\huge}
+  \posttitle{\par}
+    \author{}
+    \preauthor{}\postauthor{}
+    \date{}
+    \predate{}\postdate{}
 
 \begin{document}
-
 \maketitle
-
 \begin{abstract}
@@
 joint attention show\ldots{}
-
-\textbf{Keywords:}
-digital parenting advice; joint attention; lexical diversity; guided
-play;
 \end{abstract}
 
-\section{Introduction}\label{introduction}
+\hypertarget{introduction}{%
+\section{Introduction}\label{introduction}}
 
-Children of any given age show remarkable variability in their levels of
-language proficiency (Fenson et al., 1994),
+The quantity and quality of early language input has been found to be
+strongly associated with later language and academic outcomes (Cartmill
+et al., 2013; Hart \& Risley, 1995; Hirsh-Pasek et al., 2015; Marchman
+\& Fernald, 2008). Thus, because of the potential for large downstream
+effects (Heckman, 2006), there is tremendous interest in interventions
+that change children's language environment. And because parents define
+a large portion of that environment, especially before the onset of
+formal schooling, parent behavior is a critical locus for such
+interventions. Many effective parenting interventions require large
+resource investments and require many hours of in-person contact
+(Gertler et al., 2014; Schweinhart et al., 2004), making implementation
+at scale a daunting proposition. For this reason, many researchers
+targeting early language are interested in delivering parenting
+interventions remotely -- through texts, apps, and videos delivered on
+digital devices. But what do parents take away from these short messages
+about what to do or how to talk with their children?
+
+The content provided by digital parenting interventions runs the gamut
+from general parenting messages and facts from child development
+research to specific advice and suggested activities. A growing body of
+evidence suggests that these digital interventions can be effective
+across a range of cultures, income levels, and children's ages (for a
+review, see )(Breitenstein, Gross, \& Christophersen, 2014). For
+example, in contrast to a face-to-face parent training intervention, a
+tablet-based version saw significantly higher session completion rates
+(51\% attendance vs.~85\% module completion) and comparable or larger
+effect sizes on parents' and children's (aged 2 to 5 years) behavior
+(Breitenstein, Fogg, Ocampo, Acosta, \& Gross, 2016). Often, however,
+the theory of change presupposed by such interventions is relatively
+vague. Both within and outside the realm of academic interventions,
+messages to parents of young children often seek to provide knowledge
+about some aspect of development (e.g., early language), often in tandem
+with a suggestion regarding activities. Such messages are assumed to
+inform parents' choice of behaviors, spurring them to engage in the
+target activity, which is assumed to be more stimulating than what
+parents would have done otherwise.
+
+This theory of change is grounded in ideas about guided play and early
+language stimulation. Language input varies not only in quantity (i.e.,
+the number of total tokens), but also in quality (i.e., the diversity of
+the tokens) (Malvern, Richards, Chipere, \& Durán, 2004). Further,
+language learning -- especially the acquisition of early vocabulary in
+the first years -- appears to be supported preferentially by parents and
+children \emph{jointly attending} to some object or activity (Bigelow,
+MacLean, \& Proctor, 2004). Episodes of joint attention are frequent
+during guided play, when parents set goals and scaffold their child's
+activities (Weisberg, Hirsh-Pasek, \& Golinkoff, 2013; Wood, Bruner, \&
+Ross, 1976). Thus, the current literature supports interventions that
+encourage parents to provide high-quality language and interaction
+through something like guided play -- whether via reading books or
+playing with a shape-sorter at home, or via a conversation about
+categories in the supermarket.
+
+But is this theory of change correct? That is, does the provision of
+knowledge and activities lead to higher-quality play? An alternative
+hypothesis is that this theory could be wrong in a number of ways. By
+focusing parents on a specific activity, they could over-focus on
+achieving the superficial goals of the activity. This problem might be
+especially likely with video messages, which could encourage parents to
+try to mimic a model. And these misinterpretations in turn could result
+in less high-quality talk, with less joint attention. Or, these messages
+could produce the desired effect, but only for those parents who already
+have a general orientation towards children's early learning.
+
+Our current experiments were designed to make a direct test of this
+question: How do parents change their interactions with young children
+on the basis of short video parenting messages? In both studies, we
+collected data from parent-child dyads in a local children's museum. We
+showed parents in the experimental group a single short video modeling
+an interactive toy-based activity along with a scientific justification.
+Parents in the control group received either no video (Experiment 1) or
+a video of a recent finding in developmental psychology (Experiment 2).
+We then gave the toys from the video to all dyads and videotaped their
+interactions, coding for language quantity and quality as well as joint
+attention.
+
+Under such expert guidance, children are encouraged and motivated to
+engage in more advanced play, undertaking explorations that push the
+boundaries of what they would be able to do unaided (Vygotsky, 1980).
+
+But does providing such information change parents' behavior towards
+young children? And is this advice effective in producing change along
+the desired dimension? An alternative might be that asking parents to
+focus on a specific activity that may be novel to them may tax their
+cognitive resources, resulting in decreases in the quality of their
+child-directed speech, or in less flexible, lower-quality social
+interactions.
+
+What are digital interventions With the widespread use of smartphones
+and tablets worldwide, digitally-delivered interventions could address
+many of the logistical barriers that have limited scaling up
+face-to-face delivery methods. However, the parent and child outcomes
+assessed in the review (e.g.infant positive behaviors, satisfaction,
+emotional symptoms etc.) did not address the nature or quality of
+parent-infant interactions at a detailed level, for example whether the
+interventions lead to children paying more attention, or vocabulary
+changes in parents' language usages. Although digitally-delivered
+activities are designed to promote learning and cognitive development,
+it is unclear how they might affect these dimensions of parent-child
+interactions. Thus, we want to conduct this experiment to explore if and
+how digital scaffolding of activities affect the social and linguistic
+characteristics of parent-child ineractions. The quality of parent-child
+interactions can be measured by both the social engagement of parents
+(e.g., joint attention to objects in the environment)(Bigelow et al.,
+2004) and the quality of language (e.g., vocabulary diversity) (Malvern
+et al., 2004).
+
+Communication and message content
+
+In our study, we focus on videos that provide suggested play activities
+to parents. These videos constitute a short-term ``guided play''
+intervention.
 
@@
 rarely playing in isolation: caregivers often provide encouragement and
-guidance while scaffolding a child's play (Kaye, 1970; Wood, Bruner, \&
-Ross, 1976). The quality of interactions during such guided play has
-been shown to influence language learning: parents' joint attention to
+guidance while scaffolding a child's play (Kaye, 1970; Wood et al.,
+1976). The quality of interactions during such guided play has been
+shown to influence language learning: parents' joint attention to
 objects that their child was focused on was positively correlated with
@@
 guided play have also been found to contain more age-appropriate
-advanced forms of play (Bigelow, MacLean, \& Proctor, 2004). More
-generally, parenting practices early in childhood have been shown to
-play an important role in shaping the future outcomes of young children
-(Hart \& Risley, 1995; Heckman, 2006). While interventions often have
-trouble reaching many parents of very young children, the proliferation
-of mobile devices offers a good avenut for the digital delivery of
-parenting advice (Breitenstein, Gross, \& Christophersen, 2014).
-However, the efficacy of digital parenting advice has not been widely
-proven.
+advanced forms of play (Bigelow et al., 2004). More generally, parenting
+practices early in childhood have been shown to play an important role
+in shaping the future outcomes of young children (Hart \& Risley, 1995;
+Heckman, 2006). While interventions often have trouble reaching many
+parents of very young children, the proliferation of mobile devices
+offers a good avenut for the digital delivery of parenting advice
+(Breitenstein et al., 2014). However, the efficacy of digital parenting
+advice has not been widely proven.
 
+\hypertarget{guided-play-scaffolds-learning}{%
 \subsection{Guided Play Scaffolds
-Learning}\label{guided-play-scaffolds-learning}
+Learning}\label{guided-play-scaffolds-learning}}
 
@@
 approaches in encouraging a variety of positive academic outcomes
-(Weisberg, Hirsh-Pasek, \& Golinkoff, 2013). Another study found that
-guided play could facilitate children's vocabulary and comprehensive
-language development and subsequent literacy skills (Massey, 2013).
+(Weisberg et al., 2013). Another study found that guided play could
+facilitate children's vocabulary and comprehensive language development
+and subsequent literacy skills (Massey, 2013).
 
+\hypertarget{improving-parenting-practices-and-language-use}{%
 \subsection{Improving Parenting Practices and Language
-Use}\label{improving-parenting-practices-and-language-use}
+Use}\label{improving-parenting-practices-and-language-use}}
 
@@
 language development, and that this effect sustained four months after
-the intervention (D. L. Suskind et al., 2015). However, although a
-number of interactive measures increased during the experiment,
-including the number of word tokens, conversational turns, and child
-vocalizations, these increases did not sustain after the intervention.
-That changes did not sustain could be due to the intervention itself, or
-could merely be that the methods of home-visiting is not sustainable
-enough for parents to easily and constantly get parenting advice. Thus,
-new methods of delivering parenting advice should be considered.
+the intervention (Suskind et al., 2015). However, although a number of
+interactive measures increased during the experiment, including the
+number of word tokens, conversational turns, and child vocalizations,
+these increases did not sustain after the intervention. That changes did
+not sustain could be due to the intervention itself, or could merely be
+that the methods of home-visiting is not sustainable enough for parents
+to easily and constantly get parenting advice. Thus, new methods of
+delivering parenting advice should be considered.
 
+\hypertarget{effectiveness-of-digital-delivery}{%
 \subsection{Effectiveness of Digital
-Delivery}\label{effectiveness-of-digital-delivery}
+Delivery}\label{effectiveness-of-digital-delivery}}
 
-With the widespread use of smartphones and tablets worldwide,
-digitally-delivered interventions could address many of the logistical
-barriers that have limited scaling up face-to-face delivery methods. A
-review of 11 studies verified that digital delivery is a promising means
-of effectively distributing interventions (Breitenstein et al., 2014).
-However, the parent and child outcomes assessed in the review
-(e.g.infant positive behaviors, satisfaction, emotional symptoms etc.)
-did not address the nature or quality of parent-infant interactions at a
-detailed level, like if the interventions lead to children paying more
-attention, or vocabulary changes in parents' language usages. Although
-digitally-delivered ac-tivities are designed to promote learning and
-cognitive development, it is unclear how they might affect these
-dimensions of parent-child interactions. Thus, we want to conduct this
-experiment to explore if and how digital scaffolding of activities
-affect the social and linguistic characteristics of parent-child
-ineractions. The quality of parent-child interactions can be measured by
-both the social engagement of parents (e.g., joint attention to objects
-in the environment)(Bigelow et al., 2004) and the quality of language
-(e.g., vocabulary diversity) (Malvern, Richards, Chipere, \& Durán,
-2004).
-
-\section{Experiment 1}\label{experiment-1}
+\hypertarget{experiment-1}{%
+\section{Experiment 1}\label{experiment-1}}
 
@@
 
-\subsection{Method}\label{method}
+\hypertarget{method}{%
+\subsection{Method}\label{method}}
 
-\subsubsection{Participants.}\label{participants.}
+\hypertarget{participants.}{%
+\subsubsection{Participants.}\label{participants.}}
 
@@
 
-\subsubsection{Materials.}\label{materials.}
+\hypertarget{materials.}{%
+\subsubsection{Materials.}\label{materials.}}
 
@@
 
-\subsection{Procedure.}\label{procedure.}
+\hypertarget{procedure.}{%
+\subsubsection{Procedure.}\label{procedure.}}
 
@@
 Immediately following the video, each parent-child dyad was provided
-with the props to complete the activity they had viewed. The toys were
-placed on a large foam mat, and parents were instructed to sit on the
-mat with their child and re-create the activity they had viewed for a
-period of three minutes. In the Control condition, after consenting
+with the props to complete the activity the parent had viewed. The toys
+were placed on a large foam mat, and parents were instructed to sit on
+the mat with their child and re-create the activity they had viewed for
+a period of three minutes. In the Control condition, after consenting
 parents were told to play with their child as they would at home with
@@
 session from different angles, and parents were fitted with a wireless
-audio recorder to record their child-directed speech. After three
-minutes of play had elapsed, parents were told they could stop playing
-and cameras and audio were turned off. Parents were then asked to
-complete the PAQ before being debriefed.
+microphone (Shurre lavalier microphone) to record their child-directed
+speech. After three minutes of play had elapsed, parents were told they
+could stop playing and the cameras and microphone were turned off.
+Parents were then asked to complete the EPAQ before being debriefed.
 
+\hypertarget{joint-attention-coding-procedure.}{%
 \subsubsection{Joint Attention Coding
-Procedure.}\label{joint-attention-coding-procedure.}
+Procedure.}\label{joint-attention-coding-procedure.}}
 
 The video of each session was manually coded for episodes of joint
-attention using the Datavyu software (Team, 2014). The video taken at
-floor level was coded by default, but the other video was referred to if
-the participants were not visible or if there was technical difficulty
-with the first camera. Each session's video was coded for episodes of
-coordinated joint attention, episodes of passive joint attention, and
-parental bids for joint attention. Parental bids for joint attention
-were defined as any attempt to initiate joint attention (i.e labeling,
-pointing, or otherwise drawing attention to an object) that did not
-result in passive or coordinated joint attention. If more than 3 seconds
-elapsed between bids, they were coded as separate attempts. An episode
-of joint attention was considered passive if both participants visually
-focused on an object for a minimum of 3 seconds but the child did not
-acknowledge the parent. If either participant looked away from the
-object for less than 3 seconds and then returned to the same object it
-was considered part of the same period of joint attention. A joint
-attention episode was considered coordinated if both participants
-visually focused on an object for a minimum of 3 seconds and at some
-point in the interaction the child indicated awareness of interaction
-with some overt behavior toward the parent such as looking at their
-face, gesturing, vocalizing, or turn-taking.
+attention (JA) using the Datavyu software (Team, 2014). The video taken
+at floor level was coded by default, but the other video was referred to
+if the participants were not visible or if there was technical
+difficulty with the first camera. Each session's video was coded for
+episodes of coordinated JA, episodes of passive JA, and parental bids
+for JA. Parental bids for JA were defined as any attempt to initiate
+joint attention (i.e labeling, pointing, or otherwise drawing attention
+to an object) that did not result in passive or coordinated JA. If more
+than 3 seconds elapsed between bids, they were coded as separate
+attempts. An episode of joint attention was considered passive if both
+participants visually focused on an object for a minimum of 3 seconds
+but the child did not acknowledge the parent. If either participant
+looked away from the object for less than 3 seconds and then returned to
+the same object it was considered part of the same period of joint
+attention. A joint attention episode was considered coordinated if both
+participants visually focused on an object for a minimum of 3 seconds
+and at some point in the interaction the child indicated awareness of
+interaction with some overt behavior toward the parent such as looking
+at their face, gesturing, vocalizing, or turn-taking.
 
@@
 
-\section{Results}\label{results}
+\hypertarget{results}{%
+\subsection{Results}\label{results}}
 
@@
 
-\subsection{Lexical Diversity}\label{lexical-diversity}
+\hypertarget{lexical-diversity}{%
+\subsubsection{Lexical Diversity}\label{lexical-diversity}}
 
@@
 condition, age (scaled and 0-centered), gender, and parent's education
-level with a random intercept per video using lme4 (D. Bates, Mächler,
+level with a random intercept per video using lme4 (Bates, Mächler,
 Bolker, \& Walker, 2015). There was significantly lower TTR in the Video
@@
 
-\begin{CodeChunk}
 \begin{figure}[H]
@@
 
-\caption[Mean lexical diversity scores by condition (left]{Mean lexical diversity scores by condition (left: Type/Token ratio, right: MTLD) in Experiment 1.
-Error bars show bootstrapped 95 percent confidence intervals (CIs).}\label{fig:e1lex_div}
+\caption{Mean lexical diversity scores by condition (left: Type/Token ratio, right: MTLD) in Experiment 1. Error bars show bootstrapped 95 percent confidence intervals (CIs).}\label{fig:e1lex_div}
 \end{figure}
-\end{CodeChunk}
 
@@
 
-\caption[Mean number of word types and word tokens by condition in Experiment 1]{Mean number of word types and word tokens by condition in Experiment 1.}\label{fig:e1token_type}
+\caption{Mean number of word types and word tokens by condition in Experiment 1.}\label{fig:e1token_type}
 \end{figure}
-\end{CodeChunk}
 
-\subsection{Joint Attention}\label{joint-attention}
+\hypertarget{joint-attention}{%
+\subsubsection{Joint Attention}\label{joint-attention}}
 
@@
 video. There were significantly more bids for JA in the Video condition
-(mean: X) than in the Control condition (mean: X, \(\beta=3.51\),
-t(40.3) = 2.95, \emph{p}\textless{}.01). There were no other significant
-effects. Mixed-effects regressions with the same structure were
-performed predicting the number of episodes of coordinated and passive
-JA, and the total duration of time spent in coordinated and passive JA.
-There were no significant effects on the number or total duration of
-coordinated JA episodes, nor on the total duration of passive JA
-episodes. For the regression predicting the number of passive joint
-attention episodes, the only significant effect was an interaction of
-condition and RR (\(\beta=1.83\), t(41.5) = 2.22,
-\emph{p}\textless{}.05), showing that\ldots{} Figure X shows \ldots{} by
-condition.
+(mean: 6.24, sd: 2.79) than in the Control condition (mean: 3.56, sd:
+2.50, \(\beta=3.51\), t(40.3) = 2.95, \emph{p}\textless{}.01). There
+were no other significant effects. Mixed-effects regressions with the
+same structure were performed predicting the number of episodes of
+coordinated and passive JA, and the total duration of time spent in
+coordinated and passive JA. There were no significant effects on the
+number or total duration of coordinated JA episodes, nor on the total
+duration of passive JA episodes. For the regression predicting the
+number of passive JA episodes, the only significant effect was an
+interaction of condition and RR (\(\beta=1.83\), t(41.5) = 2.22,
+\emph{p}\textless{}.05), showing that for parents in the Video
+condition, those with higher Rules and Respect subscores engaged in more
+passive JA episodes. Figure X shows \ldots{} by condition.
 
-\begin{CodeChunk}
 \begin{figure}[H]
@@
 
-\caption[Mean number of bids and episodes of Joint Attention in Experiment 1]{Mean number of bids and episodes of Joint Attention in Experiment 1.}\label{fig:e1ja-graphs}
+\caption{Mean number of bids and episodes of Joint Attention in Experiment 1.}\label{fig:e1ja-graphs}
 \end{figure}
-\end{CodeChunk}
 
-\begin{CodeChunk}
 \begin{figure}[H]
@@
 
-\caption[Average number of passive and coordinated episodes of JA in Experiment 1]{Average number of passive and coordinated episodes of JA in Experiment 1.}\label{fig:e1ja-graphs-pass-coord}
+\caption{Average number of passive and coordinated episodes of JA in Experiment 1.}\label{fig:e1ja-graphs-pass-coord}
 \end{figure}
-\end{CodeChunk}
 
-\subsection{Discussion}\label{discussion}
+\hypertarget{discussion}{%
+\subsection{Discussion}\label{discussion}}
 
-In summary, while the number of tokens and types were higher in the
-experimental condition, lexical diversity (Type/Token ratio) was higher
-in the control condition. Parents may be relatively more repetetive in
-the experimental condition since they are attempting to stick to a
-specific prescribed task, but they talk more overall. Demographics and
-PAQ do not interact with condition, but there is a marginal effect of RR
-score on lexical diversity (lower diversity for higher RR scores), and
-marginal effects of parent education on word types and tokens (more
-types and tokens for higher parent education).
+In summary, while parents produced more word types and tokens after
+viewing the activity video, lexical diversity (Type/Token ratio and
+MTLD) was higher when parents were just asked to play as they normally
+would. This may suggest that parents in the Video condition are being
+more repetitive in their attempt to stick to the task prescribed in the
+video. Demographics and EPAQ do not interact with condition, but there
+is a marginal effect of RR score on lexical diversity (lower diversity
+for higher RR scores), and marginal effects of parent education on word
+types and tokens (more types and tokens for higher parent education).
 
@@
 
-\section{Experiment 2}\label{experiment-2}
+\hypertarget{experiment-2}{%
+\section{Experiment 2}\label{experiment-2}}
 
-Experiment 1 found that compared to parents who played with children as
-they normally would, parents who watched a Kinedu video spoke more words
-overall, but had lower lexical diversity. Parents who watched a video
-also made more bids for joint attention, although these bids did not
-result in more episodes of joint attention compared to the control
-group. Experiment 2 attempts to replicate the findings from Experiment 1
-with a restricted number of preregistered predictions. We will
-additionally include a second control condition, in which the same
-activities are described in written form, rather than being demonstrated
-in video. This manipulation will help determine what the contribution of
-the video demonstration is in producing the observed effects on
-parent-child interactions.
+Experiment 1 found that parents who watched a Kinedu video spoke more
+words overall, but had lower lexical diversity compared to parents who
+played with their children as they normally would at home. Parents who
+watched a Kinedu video also made more bids for joint attention, although
+these bids did not result in more episodes of joint attention compared
+to the control group. Experiment 2 attempts to replicate these findings
+from with a restricted number of preregistered predictions
+(\href{https://osf.io/2bpdf/}{link}).
 
-\subsection{Method}\label{method-1}
+\hypertarget{method-1}{%
+\subsection{Method}\label{method-1}}
 
-\subsubsection{Participants.}\label{participants.-1}
+\hypertarget{participants.-1}{%
+\subsubsection{Participants.}\label{participants.-1}}
 
@@
 
-\subsubsection{Materials.}\label{materials.-1}
+\hypertarget{materials.-1}{%
+\subsubsection{Materials.}\label{materials.-1}}
 
@@
 to approximately match the average video length in the Activity Video
-condition around 1.5 minutes.
+condition (close to 90 s).
 
-\subsubsection{Procedure.}\label{procedure.-1}
+\hypertarget{procedure.-1}{%
+\subsubsection{Procedure.}\label{procedure.-1}}
 
@@
 
-\section{Results}\label{results-1}
+\hypertarget{results-1}{%
+\subsection{Results}\label{results-1}}
 
@@
 
-\subsection{Lexical Diversity}\label{lexical-diversity-1}
+\hypertarget{lexical-diversity-1}{%
+\subsubsection{Lexical Diversity}\label{lexical-diversity-1}}
 
@@
 function of age (scaled and 0-centered) and condition with an
-interaction term, and with random intercepts per video using lme4 (D.
-Bates et al., 2015). There was significantly lower TTR in the Video
-condition (mean: 0.38) than in the Control condition (mean: 0.47,
-\(\beta=-.09\), t(8.7) = 3.06, \emph{p}=.01). There was no significant
-effect of age. A similar mixed-effects linear regression instead
-predicting MTLD found no significant effects of age or condition. Figure
-1 shows the mean of each lexical diversity measure (TTR and MTLD) by
-condition. Regressions with the same structure predicting the number of
-word tokens and types found no significant effects of age or condition.
+interaction term, and with random intercepts per video using lme4 (Bates
+et al., 2015). There was significantly lower TTR in the Video condition
+(mean: 0.38) than in the Control condition (mean: 0.47, \(\beta=-.09\),
+t(8.7) = 3.06, \emph{p}=.01). There was no significant effect of age. A
+similar mixed-effects linear regression instead predicting MTLD found no
+significant effects of age or condition. Figure X shows the mean of each
+lexical diversity measure (TTR and MTLD) by condition. Regressions with
+the same structure predicting the number of word tokens and types found
+no significant effects of age or condition.
 
-(Table with mean and SD of tokens, types, and TTR)
+(Table with mean and SD of tokens, types, TTR, MTLD)
 
-\begin{CodeChunk}
 \begin{figure}[H]
@@
 
-\caption[Mean lexical diversity scores by condition (left]{Mean lexical diversity scores by condition (left: Type/Token ratio, right: MTLD) in Experiment 2.}\label{fig:e2lexdiv}
+\caption{Mean lexical diversity scores by condition (left: Type/Token ratio, right: MTLD) in Experiment 2.}\label{fig:e2lexdiv}
 \end{figure}
-\end{CodeChunk}
 
-\begin{CodeChunk}
 \begin{figure}[H]
@@
 
-\caption[Mean number of word types and word tokens by condition in Experiment 2]{Mean number of word types and word tokens by condition in Experiment 2.}\label{fig:e2token-type}
+\caption{Mean number of word types and word tokens by condition in Experiment 2.}\label{fig:e2token-type}
 \end{figure}
-\end{CodeChunk}
 
-\subsection{Joint Attention}\label{joint-attention-1}
+\hypertarget{joint-attention-1}{%
+\subsubsection{Joint Attention}\label{joint-attention-1}}
 
-\begin{CodeChunk}
 \begin{figure}[H]
@@
 
-\caption[Mean number of bids and episodes of Joint Attention in Experiment 2]{Mean number of bids and episodes of Joint Attention in Experiment 2.}\label{fig:e2ja-graphs}
+\caption{Mean number of bids and episodes of Joint Attention in Experiment 2.}\label{fig:e2ja-graphs}
 \end{figure}
-\end{CodeChunk}
 
-\begin{CodeChunk}
 \begin{figure}[H]
@@
 
-\caption[Average number of passive and coordinated episodes of JA in Experiment 2]{Average number of passive and coordinated episodes of JA in Experiment 2.}\label{fig:e2ja-graphs-pass-coord}
+\caption{Average number of passive and coordinated episodes of JA in Experiment 2.}\label{fig:e2ja-graphs-pass-coord}
 \end{figure}
-\end{CodeChunk}
 
-\section{Discussion}\label{discussion-1}
+There was a marginal effect of condition on total bids for joint
+attention. Parents in the experimental condition (i.e., those who saw a
+video demonstrating an activity) made a greater number of bids for joint
+attention with their child. There was no effect of condition on the
+number of episodes of passive or coordinated JA, nor on the duration of
+these episodes. For passive joint attention, there was a main effect of
+age on both the number and duration of episodes, with older children
+having fewer episodes of passive JA and episodes of shorter duration.
+Moreover, older children had longer duration episodes of coordinated JA.
+These results suggest that as children age, they become more socially
+engaged in interactions with their caregivers.
 
-Similar to results in Experiment 1, the number of tokens was higher in
-the experimental condition, while the number of types and lexical
-diversity (Type/Token ratio) were higher in the control condition.
-Parents may be relatively more repetetive in the experimental condition
-since they are attempting to stick to a specific prescribed task, but
-they talk more overall. There was a marginal effect of condition on
-total bids for joint attention. Parents in the experimental condition
-(i.e., those who saw a video demonstrating an activity) made a greater
-number of bids for joint attention with their child. There was no effect
-of condition on the number of episodes of coordinated joint attention.
-There was no effect of condition on the number of episodes of either
-passive or coordinated joint attention, or the duration of these
-episodes. However, there was a main effect of age on number of episodes
-of passive joint attention, duration of passive and coordinated joint
-attention, with the older children having fewer episodes of passive
-joint attention, shorter duration of passive joint attention, and longer
-duration of coordinated joint attention. These results suggest that
-children become more socially engaging in interactions with their
-caregivers as they develop.
+\hypertarget{discussion-1}{%
+\section{Discussion}\label{discussion-1}}
 
-\subsection{Two-column images}\label{two-column-images}
+In both experiments, the number of tokens was higher in the experimental
+condition, while the number of types and lexical diversity (Type/Token
+ratio) were higher in the control condition. Parents may be relatively
+more repetetive in the experimental condition since they are attempting
+to stick to a specific prescribed task, but they talk more overall.
 
-You might want to display a wide figure across both columns. To do this,
-you change the \texttt{fig.env} chunk option to \texttt{figure*}. To
-align the image in the center of the page, set \texttt{fig.align} option
-to \texttt{center}. To format the width of your caption text, you set
-the \texttt{num.cols.cap} option to \texttt{2}.
+\hypertarget{acknowledgements}{%
+\section{Acknowledgements}\label{acknowledgements}}
 
-\section{References}\label{references}
+This work was supported by a gift from Kinedu, Inc. Thanks to members of
+the Language and Cognition Lab at Stanford for helpful discussion.
 
-\setlength{\parindent}{-0.1in} \setlength{\leftskip}{0.125in} \noindent
+\hypertarget{references}{%
+\section{References}\label{references}}
+
+\setlength{\parindent}{-0.1in} 
+\setlength{\leftskip}{0.125in}
+
+\noindent
+
+\hypertarget{appendix}{%
+\section{Appendix}\label{appendix}}
+
+\hypertarget{experiment-1-1}{%
+\subsection{Experiment 1}\label{experiment-1-1}}
+
+\hypertarget{video-a-6-11.9-months-pick-it-up}{%
+\subsubsection{Video A (6-11.9 months) ``Pick it
+up''}\label{video-a-6-11.9-months-pick-it-up}}
+
+Parents are told to encourage their child to pick up and drop individual
+objects. They are also encouraged to place toys on a small cloth and
+show the child that they can drag the cloth towards them to reach the
+toys.
+
+Props: cloth, plastic horse, plastic sheep, plastic elephant, toy car
+
+\hypertarget{video-b-6-11.9-months-animal-sounds}{%
+\subsubsection{Video B (6-11.9 months) ``Animal
+sounds''}\label{video-b-6-11.9-months-animal-sounds}}
+
+Parents are told to call different animals and imitate different sounds
+the animals make. They are also encourgaed to observe which animal the
+child prefers.
+
+Props: plastic sheep, plastic horse, plastic frog, plastic cow, bowls
+
+\hypertarget{video-c-12-17.9-months-give-me-the-toy}{%
+\subsubsection{Video C (12-17.9 months) ``Give me the
+toy''}\label{video-c-12-17.9-months-give-me-the-toy}}
+
+Parents are told to ask their child to hand over individual toys. They
+are also encouraged to praise the child after they give them the toys,
+and repeat the process until the child could follow the verbal
+instructions.
+
+Props: toy boat, plastic frog, plastic elephant, toy bus
+
+\hypertarget{video-d-12-17.9-months-classifying-my-toys}{%
+\subsubsection{Video D (12-17.9 months) ``Classifying my
+toys''}\label{video-d-12-17.9-months-classifying-my-toys}}
+
+Parents are told to place toys of different sizes (big or small) in two
+hoops. They are also encouraged to ask their child to distinguish
+between two objects and identify which one is larger.
+
+Props: two yellow and green rings, big car, small car, big horse, small
+horse
+
+\hypertarget{video-e-18-23.9-months-my-toys}{%
+\subsubsection{Video E (18-23.9 months) ``My
+toys''}\label{video-e-18-23.9-months-my-toys}}
+
+Parents are told to show the child toys of the same shape but different
+sizes, to place one of the objects in a basket and to ask the child to
+take out the object. They are also encouraged to ask their child if the
+object is bigger or smaller compared to its pair.
+
+Props: two buckets, big car, small car, big horse, small horse
+
+\hypertarget{video-f-18-23.9-months-the-orchestra}{%
+\subsubsection{Video F (18-23.9 months) ``The
+Orchestra''}\label{video-f-18-23.9-months-the-orchestra}}
+
+Parents are told to give their child a musical instrument to play. They
+are also encouraged to play a song and see if the child follows the
+rhythm.
+
+Props: maracas, drum, tambourine, clapper
+
+\hypertarget{experiment-2-1}{%
+\subsection{Experiment 2}\label{experiment-2-1}}
+
+\hypertarget{video-a-12-17.9-months-give-me-the-toy}{%
+\subsubsection{Video A (12-17.9 months) ``Give me the
+toy''}\label{video-a-12-17.9-months-give-me-the-toy}}
+
+Parents are told to ask their child to hand over individual toys. They
+are also encouraged to praise the child after they give them the toys,
+and repeat the process until the child could follow the verbal
+instructions.
+
+Props: plastic pig, plastic horse, plastic dog, plastic cat, plastic cow
+
+\hypertarget{video-b-12-17.9-months-classifying-my-toys}{%
+\subsubsection{Video B (12-17.9 months) ``Classifying my
+toys''}\label{video-b-12-17.9-months-classifying-my-toys}}
+
+Parents are told to place toys of different sizes (big or small) in two
+hoops. They are also encouraged to ask their child to distinguish
+between two objects and identify which one is larger.
+
+Props: two yellow and green rings, big car, small car, big horse, small
+horse
+
+\hypertarget{video-c-12-17.9-months-geometric-shapes-jigzsaw-puzzle}{%
+\subsubsection{Video C (12-17.9 months) ``Geometric shapes jigzsaw
+puzzle''}\label{video-c-12-17.9-months-geometric-shapes-jigzsaw-puzzle}}
+
+Parents are told to encourage their child to name different shapes on a
+jigzsaw puzzle. Then they are told to undo the puzzle and invite the
+child to complete the puzzle.
+
+Props: A jigzsaw puzzle of geometric shapes
+
+\hypertarget{video-d-18-23.9-months-my-toys}{%
+\subsubsection{Video D (18-23.9 months) ``My
+toys''}\label{video-d-18-23.9-months-my-toys}}
+
+Parents are told to show the child toys of the same shape but different
+sizes, to place one of the objects in a basket and to ask the child to
+take out the object. They are also encouraged to ask their child if the
+object is bigger or smaller compared to its pair.
+
+Props: two buckets, big car, small car, big horse, small horse
+
+\hypertarget{video-e-18-23.9-months-the-orchestra}{%
+\subsubsection{Video E (18-23.9 months) ``The
+Orchestra''}\label{video-e-18-23.9-months-the-orchestra}}
+
+Parents are told to give their child a musical instrument to play. They
+are also encouraged to play a song and see if the child follows the
+rhythm.
+
+Props: maracas, drum, tambourine, clapper
+
+\hypertarget{video-f-18-23.9-months-my-yellow-toys}{%
+\subsubsection{Video F (18-23.9 months) ``My Yellow
+Toys''}\label{video-f-18-23.9-months-my-yellow-toys}}
+
+Parents are told to show their child yellow toys and to ask ``what color
+are they''. They are also told to give the child toys of different
+colors, ask them to only play with the yellow ones and praise the child
+after they do so.
+
+Props: blue car, yellow car, yellow block, red block, blue block, green
+block
 
 \hypertarget{refs}{}
-\hypertarget{ref-lme4}{}
+\leavevmode\hypertarget{ref-lme4}{}%
 Bates, D., Mächler, M., Bolker, B., \& Walker, S. (2015). Fitting linear
@@
 
-\hypertarget{ref-Bigelow2004}{}
+\leavevmode\hypertarget{ref-Bigelow2004}{}%
 Bigelow, A. E., MacLean, K., \& Proctor, J. (2004). The role of joint
@@
 
-\hypertarget{ref-Breitenstein2014}{}
+\leavevmode\hypertarget{ref-Breitenstein2016}{}%
+Breitenstein, S. M., Fogg, L., Ocampo, E. V., Acosta, D. I., \& Gross,
+D. (2016). Parent use and efficacy of a self-administered, tablet-based
+parent training intervention: A randomized controlled trial. \emph{JMIR
+mHealth and uHealth}, \emph{4}(2), e36.
+\url{http://doi.org/10.2196/mhealth.5202}
+
+\leavevmode\hypertarget{ref-Breitenstein2014}{}%
 Breitenstein, S. M., Gross, D., \& Christophersen, R. (2014). Digital
@@
 
-\hypertarget{ref-Fenson1994}{}
-Fenson, L., Dale, P. S., Reznick, J. S., Bates, E., Thal, D. J.,
-Pethick, S. J., \ldots{} Stiles, J. (1994). Variability in early
-communicative development. \emph{Monographs of the Society for Research
-in Child Development}, i--185.
+\leavevmode\hypertarget{ref-Cartmill2013}{}%
+Cartmill, E. A., Armstrong, B. F., Gleitman, L. R., Goldin-Meadow, S.,
+Medina, T. N., \& Trueswell, J. C. (2013). Quality of early parent input
+predicts child vocabulary 3 years later. \emph{Proceedings of the
+National Academy of Sciences}, \emph{110}(28), 11278--11283.
+\url{http://doi.org/10.1073/pnas.1309518110}
 
-\hypertarget{ref-Hart1995}{}
+\leavevmode\hypertarget{ref-Jamaica2014}{}%
+Gertler, P., Heckman, J., Pinto, R., Zanolini, A., Vermeersch, C.,
+Walker, S., \ldots{} Grantham-McGregor, S. (2014). Labor market returns
+to an early childhood stimulation intervention in jamaica.
+\emph{Science}, \emph{344}(6187), 998--1001.
+\url{http://doi.org/10.1126/science.1251178}
+
+\leavevmode\hypertarget{ref-Hart1995}{}%
 Hart, B., \& Risley, T. R. (1995). \emph{Meaningful differences in the
@@
 
-\hypertarget{ref-Heckman2006}{}
+\leavevmode\hypertarget{ref-Heckman2006}{}%
 Heckman, J. J. (2006). Skill formation and the economics of investing in
@@
 
-\hypertarget{ref-Hembacher2018}{}
+\leavevmode\hypertarget{ref-Hembacher2018}{}%
 Hembacher, E., \& Frank, M. C. (2018). The early parenting attitudes
@@
 
-\hypertarget{ref-Hirsh2008}{}
+\leavevmode\hypertarget{ref-HirshPasek2015}{}%
+Hirsh-Pasek, K., Adamson, L. B., Bakeman, R., Owen, M. T., Golinkoff, R.
+M., Pace, A., \ldots{} Suma, K. (2015). The contribution of early
+communication quality to low-income children's language success.
+\emph{Psychological Science}, \emph{26}(7), 1071--1083.
+\url{http://doi.org/10.1177/0956797615581493}
+
+\leavevmode\hypertarget{ref-Hirsh2008}{}%
 Hirsh-Pasek, K., \& Golinkoff, R. M. (2008). Why play= learning.
@@
 
-\hypertarget{ref-spacy2}{}
+\leavevmode\hypertarget{ref-spacy2}{}%
 Honnibal, I., Matthew AND Montani. (2017). SpaCy 2: Natural language
@@
 
-\hypertarget{ref-Kaye1970}{}
+\leavevmode\hypertarget{ref-Kaye1970}{}%
 Kaye, K. (1970). Mother-child instructional interaction.
@@
 
-\hypertarget{ref-Carpenter1998}{}
+\leavevmode\hypertarget{ref-Malvern2004}{}%
+Malvern, D., Richards, B. J., Chipere, N., \& Durán, P. (2004).
+\emph{Lexical diversity and language development}. Palgrave Macmillan.
+
+\leavevmode\hypertarget{ref-Marchman2008}{}%
+Marchman, V. A., \& Fernald, A. (2008). Speed of word recognition and
+vocabulary knowledge in infancy predict cognitive and language outcomes
+in later childhood. \emph{Developmental Science}, \emph{11}, F9--F16.
+
+\leavevmode\hypertarget{ref-Massey2013}{}%
+Massey, S. L. (2013). From the reading rug to the play center: Enhancing
+vocabulary and comprehensive language skills by connecting storybook
+reading and guided play. \emph{Early Childhood Education Journal},
+\emph{41}, 125--131.
+
+\leavevmode\hypertarget{ref-Carpenter1998}{}%
 M. Carpenter, K. Nagell, \& Tomasello, M. (1998). Social cognition,
@@
 
-\hypertarget{ref-Malvern2004}{}
-Malvern, D., Richards, B. J., Chipere, N., \& Durán, P. (2004). Lexical
-diversity and language development.
-
-\hypertarget{ref-Massey2013}{}
-Massey, S. L. (2013). From the reading rug to the play center: Enhancing
-vocabulary and comprehensive language skills by connecting storybook
-reading and guided play. \emph{Early Childhood Education Journal},
-\emph{41}, 125--131.
-
-\hypertarget{ref-McCarthy2010}{}
+\leavevmode\hypertarget{ref-McCarthy2010}{}%
 McCarthy, P. M., \& Jarvis, S. (2010). MTLD, vocd-d, and hd-d: A
@@
 
-\hypertarget{ref-Schulz2007}{}
+\leavevmode\hypertarget{ref-Schulz2007}{}%
 Schulz, L., \& Bonawitz, E. (2007). Serious fun: Preschoolers engage in
@@
 
-\hypertarget{ref-Singer2006}{}
+\leavevmode\hypertarget{ref-PerryPreschool2004}{}%
+Schweinhart, L. J., Montie, J., Xiang, Z., Barnett, W. S., Belfield, C.
+R., \& Nores, M. (2004). \emph{Lifetime effects: The highscope perry
+preschool study through age 40}. Ypsilanti, MI: HighScope Press.
+
+\leavevmode\hypertarget{ref-Singer2006}{}%
 Singer, D. G., Golinkoff, R. M., \& Hirsh-Pasek, K. (Eds.). (2006).
@@
 
-\hypertarget{ref-Suskind2015}{}
+\leavevmode\hypertarget{ref-Suskind2015}{}%
 Suskind, D. L., Leffel, K. R., Graf, E., Hernandez, M. W., Gunderson, E.
@@
 
-\hypertarget{ref-datavyu}{}
+\leavevmode\hypertarget{ref-datavyu}{}%
 Team, D. (2014). Datavyu: A video coding tool. \emph{Databrary Project}.
@@
 
-\hypertarget{ref-Tomasello1986}{}
+\leavevmode\hypertarget{ref-Tomasello1986}{}%
 Tomasello, M., \& Farrar, M. J. (1986). Joint attention and early
@@
 
-\hypertarget{ref-Vygotsky1980}{}
+\leavevmode\hypertarget{ref-Vygotsky1980}{}%
 Vygotsky, L. S. (1980). Mind in society: The development of higher
@@
 
-\hypertarget{ref-Weisberg2013}{}
+\leavevmode\hypertarget{ref-Weisberg2013}{}%
 Weisberg, D. S., Hirsh-Pasek, K., \& Golinkoff, R. M. (2013). Guided
@@
 
-\hypertarget{ref-Wood1976}{}
+\leavevmode\hypertarget{ref-Wood1976}{}%
 Wood, D., Bruner, J. S., \& Ross, G. (1976). The role of tutoring in
@@
 
-\bibliographystyle{apacite}
-
 \end{document}

### 2019-06-20 paper/cogsci2019/cogsci2019.Rmd
intro edits

@@
 title: "Understanding the impacts of video activity guides on parent-child interaction"
+author-information: "\\author{ \n  {\\large\\bf George~Kachergis}^1 (\\texttt{kachergis@stanford.edu})
+  \\\\\n  {\\large\\bf Emily~Hembacher}^2 (\\texttt{emily.hembacher@gmail.com}) \\\\\n
+  \ {\\large\\bf Veronica~Cristiano}^2 (\\texttt{CRISTIANO @gallaudet.edu}) \\\\\n
+  \ {\\large\\bf Hanwen Vivian~Zhang}^1 (\\texttt{vivian3@stanford.edu}) \\\\\n  {\\large\\bf
+  Michael C.~Frank}^1 (\\texttt{mcfrank@stanford.edu}) \\\\ \n^{1}Department of Psychology,
+  Stanford University \\\\  Stanford, CA 94305 USA \\\\ ^{2} Nextdoor, Inc., Burlingame,
+  CA \\\\ ^{3} Gallaudet University, Washington, D.C. }\n"
+header-includes:
+   - \usepackage{float}
 bibliography: library.bib
+output:
+  pdf_document: default
+  html_document:
+    df_print: paged
+document-params: 10pt, letterpaper
+final-submission: \cogscifinalcopy
+keywords: "digital parenting advice; joint attention; lexical diversity; guided play;
+  \n"
 csl: apa6.csl
-document-params: "10pt, letterpaper"
-
-author-information: > 
-    \author{ 
-      {\large\bf George~Kachergis}^1 (\texttt{kachergis@stanford.edu}) \\
-      {\large\bf Emily~Hembacher}^2 (\texttt{emily.hembacher@gmail.com}) \\
-      {\large\bf Veronica~Cristiano}^2 (\texttt{CRISTIANO @gallaudet.edu}) \\
-      {\large\bf Hanwen Vivian~Zhang}^1 (\texttt{vivian3@stanford.edu}) \\
-      {\large\bf Michael C.~Frank}^1 (\texttt{mcfrank@stanford.edu}) \\ 
-    ^{1}Department of Psychology, Stanford University \\ 
-    Stanford, CA 94305 USA \\
-    ^{2} Nextdoor, Inc., Burlingame, CA \\
-    ^{3} Gallaudet University, Washington, D.C.
-    }
-
-abstract: >
-    Early parenting practices play an important role in shaping the future 
-    outcomes of young children [@Hart1995; @Heckman2006]. 
-    In particular, high-quality early interactions and language input appear to 
-    facilitate language learning and result in higher levels of school performance. 
-    The rise of phone- and tablet-based parenting applications ("apps") holds the promise of delivering 
-    low-cost, positive interventions on parenting style to a wide variety of populations. 
+abstract: |
+  Early parenting practices play an important role in shaping the future  outcomes of young children [@Hart1995; @Heckman2006].
+In particular, high-quality early interactions and language input appear to  facilitate language learning and result in higher levels of school performance.
+The rise of phone- and tablet-based parenting applications ("apps") holds the promise of delivering  low-cost, positive interventions on parenting style to a wide variety of populations.
 Of special interest are the parents of very young children, who are often difficult to reach in other ways.
 Yet little is known about the effects of communicating to parents through app-based interventions.
-    In a study of one commercial app offering a collection of age-appropriate activity videos, we find 
-    that the quality of parent-child interactions increases in some ways as a result of using the app. 
-    Specifically, the lexical diversity of parents' child-directed speech increases, and measures of 
-    joint attention show...
-
-keywords: >
-    digital parenting advice; joint attention; lexical diversity; guided play;
-
-output: pdf_document
-final-submission: \cogscifinalcopy
+In a study of one commercial app offering a collection of age-appropriate activity videos, we find  that the quality of parent-child interactions increases in some ways as a result of using the app.
+Specifically, the lexical diversity of parents' child-directed speech increases, and measures of  joint attention show...
 ---
@@
 The content provided by digital parenting interventions runs the gamut from general parenting messages and facts from child development research to specific advice and suggested activities. 
-A growing body of evidence suggests that these digital interventions can be effective across a range of cultures, income levels, and children's ages (for a review, see )[@Breitenstein2014].
+A growing body of evidence suggests that these digital interventions can be effective across a range of cultures, income levels, and children's ages [for a review, see @Breitenstein2014].
 For example, in contrast to a face-to-face parent training intervention, a tablet-based version saw significantly higher session completion rates (51% attendance vs.
@@
 Both within and outside the realm of academic interventions, messages to parents of young children often seek to provide knowledge about some aspect of development (e.g., early language), often in tandem with a suggestion regarding activities.
-Such messages are assumed to inform parents' choice of behaviors, spurring them to engage in the target activity, which is assumed to be more stimulating than what parents would have done otherwise.
+Such messages are assumed to inform parents' choice of behaviors, spurring them to engage in some target activity, which is assumed to be more stimulating than what parents would have done otherwise.
 
-This theory of change is grounded in ideas about guided play and early language stimulation. 
-Language input varies not only in quantity (i.e., the number of total tokens), but also in quality (i.e., the diversity of the tokens) [@Malvern2004].
-Further, language learning -- especially the acquisition of early vocabulary in the first years -- appears to be supported preferentially by parents and children _jointly attending_ to some object or activity [@Bigelow2004].
+This theory of change is typically grounded in ideas about guided play and early language stimulation. 
+Child-directed speech varies not only in quantity (i.e., the number of total tokens), but also in quality in terms of the diversity of the tokens [@Malvern2004] or the context-appropriateness of the speech [@Cartmill2013], both of which have been linked to children's subsequent language development.
+Further, language learning -- especially the acquisition of early vocabulary in the first years -- appears to be supported preferentially by parents and children _jointly attending_ to some object or activity [@Baldwin1991; @Bigelow2004].
 Episodes of joint attention are frequent during guided play, when parents set goals and scaffold their child's activities [@Wood1976; @Weisberg2013].
@@
 We then gave the toys from the video to all dyads and videotaped their interactions, coding for language quantity and quality as well as joint attention.
-
-Under such expert guidance, children are encouraged and motivated to engage in more advanced play, undertaking explorations that push the boundaries of what they would be able to do unaided [@Vygotsky1980].
 

### 2019-06-20 paper/cogsci2019/extra_text.Rmd.R

@@ -1,0 +1,50 @@
+unused text
+
+Under such expert guidance, children are encouraged and motivated to engage in more advanced play, undertaking explorations that push the boundaries of what they would be able to do unaided [@Vygotsky1980].
+
+
+What are digital interventions
+With the widespread use of smartphones and tablets worldwide, digitally-delivered interventions could address many of the logistical barriers that have limited scaling up face-to-face delivery methods.
+However, the parent and child outcomes assessed in the review (e.g.infant positive behaviors, satisfaction, emotional symptoms etc.) did not address the nature or quality of parent-infant interactions at a detailed level, for example whether the interventions lead to children paying more attention, or vocabulary changes in parents' language usages. 
+Although digitally-delivered activities are designed to promote learning and cognitive development, it is unclear how they might affect these dimensions of parent-child interactions.
+Thus, we want to conduct this experiment to explore if and how digital scaffolding of activities affect the social and linguistic characteristics of parent-child ineractions.
+The quality of parent-child interactions can be measured by both the social engagement of parents (e.g., joint attention to objects in the environment)[@Bigelow2004] and the quality of language (e.g., vocabulary diversity) [@Malvern2004]. 
+
+
+Communication and message content
+
+
+In our study, we focus on videos that provide suggested play activities to parents. 
+These videos constitute a short-term "guided play" intervention. 
+
+
+Young children spend a large portion of their waking time at play, variously manipulating objects, exploring their environment, and interacting with caregivers and peers.
+Playing with objects allows them to discover hidden object properties and relations, and to build a causal understanding of how objects interact [e.g., @Schulz2007]. 
+Meanwhile, play also gives children an opportunity to set and achieve goals (e.g., build a tower) and to practice a wide range of motor skills (e.g., stacking) that will help them navigate the world [@Singer2006].
+Social play can help children learn about human relationships, both through imitation of adult behaviors and by experiencing and learning to process emotional events such as failures [@Singer2006].
+Of course, young children are rarely playing in isolation: caregivers often provide encouragement and guidance while scaffolding a child's play [@Kaye1970; @Wood1976]. 
+The quality of interactions during such guided play has been shown to influence language learning: parents' joint attention to objects that their child was focused on was positively correlated with the child's subsequent vocabulary growth [@Tomasello1986; @Carpenter1998].
+Episodes of joint attention during guided play have also been found to contain more age-appropriate advanced forms of play [@Bigelow2004].
[…]

### 2019-06-21 paper/cogsci2019/cogsci2019.Rmd
methods revised

@@
 ---
-title: "Understanding the impacts of video activity guides on parent-child interaction"
+title: "Understanding the impacts of video-guided activities on parent-child interaction"
 author-information: "\\author{ \n  {\\large\\bf George~Kachergis}^1 (\\texttt{kachergis@stanford.edu})
@@
 But is this theory of change correct? That is, does the provision of knowledge and activities lead to higher-quality play? 
-An alternative hypothesis is that this theory could be wrong in a number of ways. 
-By focusing parents on a specific activity, they could over-focus on achieving the superficial goals of the activity. 
-This problem might be especially likely with video messages, which could encourage parents to try to mimic a model. 
-And these misinterpretations in turn could result in less high-quality talk, with less joint attention. 
-Or, these messages could produce the desired effect, but only for those parents who already have a general orientation towards children's early learning.
+Alternatively, this theory could be wrong in a number of ways. 
+By focusing parents on a specific activity, parents may over-focus on achieving the superficial goals of the activity. 
+This problem might be especially likely with video messages, which could encourage parents to try to mimic a model's specific speech and/or actions.
+Attempting to reproduce such surface details of a video-guided activity could in turn result in less high-quality talk, with less responsiveness to their child's play.
+Another possibility is that these messages do produce the desired effect, but only for those parents who already have a general orientation towards children's early learning.
 
 Our current experiments were designed to make a direct test of this question: How do parents change their interactions with young children on the basis of short video parenting messages? 
-In both studies, we collected data from parent-child dyads in a local children's museum. 
+In two experiments, we collected data from parent-child dyads in a local children's museum. 
 We showed parents in the experimental group a single short video modeling an interactive toy-based activity along with a scientific justification. 
@@
 
-But does providing such information change parents' behavior towards young children? 
-And is this advice effective in producing change along the desired dimension? 
-An alternative might be that asking parents to focus on a specific activity that may be novel to them may tax their cognitive resources, resulting in decreases in the quality of their child-directed speech, or in less flexible, lower-quality social interactions.
-
-What are digital interventions
-With the widespread use of smartphones and tablets worldwide, digitally-delivered interventions could address many of the logistical barriers that have limited scaling up face-to-face delivery methods.
-However, the parent and child outcomes assessed in the review (e.g.infant positive behaviors, satisfaction, emotional symptoms etc.) did not address the nature or quality of parent-infant interactions at a detailed level, for example whether the interventions lead to children paying more attention, or vocabulary changes in parents' language usages.
-Although digitally-delivered activities are designed to promote learning and cognitive development, it is unclear how they might affect these dimensions of parent-child interactions.
-Thus, we want to conduct this experiment to explore if and how digital scaffolding of activities affect the social and linguistic characteristics of parent-child ineractions.
-The quality of parent-child interactions can be measured by both the social engagement of parents (e.g., joint attention to objects in the environment)[@Bigelow2004] and the quality of language (e.g., vocabulary diversity) [@Malvern2004].
-
-Communication and message content
-
-In our study, we focus on videos that provide suggested play activities to parents. 
-These videos constitute a short-term "guided play" intervention.
-
-Young children spend a large portion of their waking time at play, variously manipulating objects, exploring their environment, and interacting with caregivers and peers.
-Playing with objects allows them to discover hidden object properties and relations, and to build a causal understanding of how objects interact [e.g., @Schulz2007]. 
-Meanwhile, play also gives children an opportunity to set and achieve goals (e.g., build a tower) and to practice a wide range of motor skills (e.g., stacking) that will help them navigate the world [@Singer2006].
-Social play can help children learn about human relationships, both through imitation of adult behaviors and by experiencing and learning to process emotional events such as failures [@Singer2006].
-Of course, young children are rarely playing in isolation: caregivers often provide encouragement and guidance while scaffolding a child's play [@Kaye1970; @Wood1976]. 
-The quality of interactions during such guided play has been shown to influence language learning: parents' joint attention to objects that their child was focused on was positively correlated with the child's subsequent vocabulary growth [@Tomasello1986; @Carpenter1998].
-Episodes of joint attention during guided play have also been found to contain more age-appropriate advanced forms of play [@Bigelow2004].
-More generally, parenting practices early in childhood have been shown to play an important role in shaping the future outcomes of young children [@Hart1995; @Heckman2006]. 
-While interventions often have trouble reaching many parents of very young children, the proliferation of mobile devices offers a good avenut for the digital delivery of parenting advice [@Breitenstein2014].
-However, the efficacy of digital parenting advice has not been widely proven.
-
-## Guided Play Scaffolds Learning
-Children's early play behaviors are often assisted by more skilled and knowledgeable play partners such as their caregivers and older siblings [@Kaye1970]. 
-Under such expert guidance, children are encouraged and motivated to engage in more advanced play, undertaking explorations that push the boundaries of what they would be able to do unaided [@Vygotsky1980].
-These tutorial interactions have been shown to be important components of child development [@Wood1976].
-Thus, with the knowledge of both play and tutorial interactions, guided play, which consists of both active and enjoyable activities as well as close guidance of adults [@Hirsh2008] has drawn researchers' interest.
-A study of preschoolers showed that guided play scaffolds the environment while still allowing children to maintain a large degree of control, 
-and it outperforms direct-instruction approaches in encouraging a variety of positive academic outcomes [@Weisberg2013].
-Another study found that guided play could facilitate children's vocabulary and comprehensive language development and subsequent literacy skills [@Massey2013].
-
-## Improving Parenting Practices and Language Use
-Thus, including guided play in parenting practices from an early age may boost children's language and educational outcomes. 
-A recent home-visit parenting practices intervention targeting children of low socioeconomic status found that parents in the intervention group gained knowledge of language development, and that this effect sustained four months after the intervention [@Suskind2015].
-However, although a number of interactive measures increased during the experiment, including the number of word tokens, conversational turns, and child vocalizations, these increases did not sustain after the intervention.
-That changes did not sustain could be due to the intervention itself,
-or could merely be that the methods of home-visiting is not sustainable enough for parents to easily and constantly get parenting advice.
-Thus, new methods of delivering parenting advice should be considered.
-
-## Effectiveness of Digital Delivery
-
 # Experiment 1
 
-In Experiment 1, we invited parents of 6- to 24-month-old infants visiting the Children's Discovery Museum in San Jose to complete activities from the Kinedu app. 
+In Experiment 1, we invited parents of 6- to 24-month-old infants visiting the Children's Discovery Museum in San Jose to complete video-guided activities from Kinedu (Kinedu Inc.), a parenting app that delivers digital parenting advice in the form of short videos.
 Parents were randomly assigned to the video group or the control group; parents in the video group watched a video from the Kinedu app (matched to their child's age), and then performed the activity with their child using the props from the video.
-Parents in the control group did not watch a Kinedu video, instead they were given the same props and were told to play with their infants as they would at home.
+Parents in the control group did not watch a Kinedu video, but were given a set of the same age-appropriate props and asked to play with their infants as they would at home.
 
@@
 ### Materials.
-Stimuli included videos from the Kinedu (Kinedu Inc.) commercial parenting application. 
+Stimuli included videos from the Kinedu commercial parenting application. 
 The videos were designed to show activities to parents that they could perform with their child in order to foster cognitive and physical development, and were targeted to the child's age and level of development.
@@
 We selected two videos for each of three age groups in our sample (6-11.9 months, 12-17.9 months, 18-23.94 months). 
-More information about the specific videos is available in the Appendix. 
-Participants were also given a set of toys corresponding to those in the video that they watched so that they could complete the activity. 
-The toys associated with each video are listed in the Appendix.
+Participants were also given a set of toys corresponding to those in the video that they watched so that they could complete the activity.[^1]
+
+[^1]: Details of the specific videos used and the toys associated with each video are in the Appendix.
 
@@
 The Control condition was yoked to the Activity Video condition such that for every participant in the Video condition who saw a particular video and received the associated props, a participant in the Control condition received the same props but did not watch the activity video.
-Parents also completed the Early Parenting Attitudes Questionnaire (EPAQ; [@Hembacher2018]). 
+Parents also completed the Early Parenting Attitudes Questionnaire [EPAQ; @Hembacher2018]. 
 The EPAQ measures parents' attitudes about parenting and child development along three dimensions: rules and respect, early learning, and affection and attachment.
@@
 To ensure that parents could give the video their full attention, the experimenter played with the infant with a set of toys (different from the experimental props used in the study) while the video was being played.
-Immediately following the video, each parent-child dyad was provided with the props to complete the activity the parent had viewed. 
-The toys were placed on a large foam mat, and parents were instructed to sit on the mat with their child and re-create the activity they had viewed for a period of three minutes.
-In the Control condition, after consenting parents were told to play with their child as they would at home with the provided props for a period of three minutes. 
+Immediately following the video, each parent-child dyad was provided with the props to complete the video-guided activity that the parent had viewed. 
+The toys were placed on a large foam play mat, and parents were instructed to sit on the mat with their child and re-create the activity they had viewed for a period of three minutes.
+In the Control condition, after informed consent parents were told to play with their child as they would at home with the provided props for a period of three minutes. 
 They were not given any additional instructions about how to use the props.
 
-In both conditions, two video cameras were used to record the play session from different angles, and parents were fitted with a wireless microphone (Shurre lavalier microphone) to record their child-directed speech.
+In both conditions, two video cameras were used to record the play session from different angles, and parents were fitted with a wireless Shurre lavalier microphone to record their child-directed speech.
 After three minutes of play had elapsed, parents were told they could stop playing and the cameras and microphone were turned off.
@@
 If more than 3 seconds elapsed between bids, they were coded as separate attempts. 
-An episode of joint attention was considered passive if both participants visually focused on an object for a minimum of 3 seconds but the child did not acknowledge the parent. 
-If either participant looked away from the object for less than 3 seconds and then returned to the same object it was considered part of the same period of joint attention. 
-A joint attention episode was considered coordinated if both participants visually focused on an object for a minimum of 3 seconds and at some point in the interaction the child indicated awareness of interaction with some overt behavior toward the parent such as looking at their face, gesturing, vocalizing, or turn-taking.
+An episode of joint attention was considered _passive_ if both participants visually focused on an object for 3 or more seconds but the child did not acknowledge the parent. 
+If either participant looked away from the object for less than 3 seconds and then returned to the same object it was considered part of the same episode of joint attention. 
+A joint attention episode was considered _coordinated_ if both participants visually focused on an object for 3 or more seconds and at some point in the interaction the child indicated awareness of interaction with some overt behavior toward the parent such as looking at their face, gesturing, vocalizing, or turn-taking.
+Full details of our guidelines for coding joint attention are available [here](https://docs.google.com/document/d/1cZrT_Gjt6p0om19lXO-XcFnT09pb0giyhRQ-Pm1yoBU/edit?usp=sharing).
 
 A second coder independently coded a third of the videos (i.e., 20 of the 60 videos, approximately equally distributed across ages) to establish reliability. 
-The two coders had a reliability of ICC = 0.80 with 95% confident interval (CI) = [0.57,0.92] (p < 0.05) for number of parent bids for JA; ICC = 0.20 with 95% CI = [-0.26,0.58] for number of passive JA episodes; ICC = 0.66 with 95% CI = [0.32,0.85] (p < 0.05) for number of coordinated JA episodes; ICC = 0.24 with 95% CI = [-0.21,0.61] for total duration of passive JA episodes, and ICC = 0.62 with 95% CI = [0.27,0.83] (p < 0.05) for total duration of coordinated JA episodes.
+The two coders had a reliability of ICC = 0.80 with 95% confident interval (CI) = [0.57,0.92] for number of parent bids for JA; ICC = 0.20 with 95% CI = [-0.26,0.58] for number of passive JA episodes; ICC = 0.66 with 95% CI = [0.32,0.85] for number of coordinated JA episodes; ICC = 0.24 with 95% CI = [-0.21,0.61] for total duration of passive JA episodes, and ICC = 0.62 with 95% CI = [0.27,0.83] for total duration of coordinated JA episodes.
 
@@
 
-The transcripts and hand-coded behavioral data was analyzed according to our preregistration[^1].
-Below we first describe the lexical diversity results, followed by the joint attention results.
+Parents' child-directed speech during the play sessions was transcribed.
+The transcripts and hand-coded joint attention data were analyzed according to our preregistration[^2], with any deviations or extensions noted.
+Below we first report the lexical diversity results, followed by the joint attention results.
 
-[^1]: Preregistration: [https://osf.io/2bpdf/](https://osf.io/2bpdf/)]
+[^2]: Preregistration: [https://osf.io/2bpdf/](https://osf.io/2bpdf/)]
 
@@
 
-Parents' child-directed speech during the play sessions was transcribed.
-For each transcript, the words were lemmatized using @spacy2, and the word *types* (unique words) and *tokens* (total words) were then tallied and the type-token ratio (TTR) calculated as a measure of lexical diversity.
-Although TTR was our preregistered measure of lexical diversity, TTR is correlated with the length of a text, whereas the measure of textual lexical diversity (MTLD) is not [@McCarthy2010]. 
-Thus, we also measure lexical diversity with MTLD, which is calculated as the mean length of sequential word strings in a text that maintain a given TTR value (here, .720).
+For each transcript, the words were lemmatized using ``spacy2`` [@spacy2], and the word *types* (unique words) and *tokens* (total words) were then tallied and the type-token ratio (TTR) calculated as a measure of lexical diversity.
+Although TTR was our preregistered measure of lexical diversity as it has commonly been used, it has been noted that TTR is correlated with the length of a text, which has led to the development of new measures such as the measure of textual lexical diversity [MTLD; @McCarthy2010].
+Thus, we also measure lexical diversity with MTLD, which is calculated as the mean length of sequential word strings in a text that maintain a given TTR value (here we use the value proposed by @McCarthy2010: 0.720).
 

### 2019-06-21 paper/cogsci2019/extra_text.Rmd.R

@@ -48,3 +48,8 @@ or could merely be that the methods of home-visiting is not sustainable enough f
 Thus, new methods of delivering parenting advice should be considered.
 
 ## Effectiveness of Digital Delivery
+
+
+But does providing such information change parents' behavior towards young children? 
+And is this advice effective in producing change along the desired dimension? 
+An alternative might be that asking parents to focus on a specific activity that may be novel to them may tax their cognitive resources, resulting in decreases in the quality of their child-directed speech, or in less flexible, lower-quality social interactions.

### 2019-07-04 paper/cogsci2019/cogsci2019.Rmd
graph improvements, updated results

@@
 library(lmerTest)
+library(tidyboot)
+library(knitr)
 source("multiplot.R")
@@
 In Experiment 1, we invited parents of 6- to 24-month-old infants visiting the Children's Discovery Museum in San Jose to complete video-guided activities from Kinedu (Kinedu Inc.), a parenting app that delivers digital parenting advice in the form of short videos.
-Parents were randomly assigned to the video group or the control group; parents in the video group watched a video from the Kinedu app (matched to their child's age), and then performed the activity with their child using the props from the video.
-Parents in the control group did not watch a Kinedu video, but were given a set of the same age-appropriate props and asked to play with their infants as they would at home.
+Parents were randomly assigned to the video condition or the control condition; parents in the _video_ condition watched a video from the Kinedu app (matched to their child's age), and then performed the activity with their child using the props from the video.
+Parents in the _control_ condition did not watch a Kinedu video, but were given a set of the same age-appropriate props and asked to play with their infants as they normally would at home.
 
@@
 lmer_data <- d %>%
-  filter(!is.na(AA), !is.na(EL), !is.na(RR))%>%
+  #filter(!is.na(AA), !is.na(EL), !is.na(RR))%>%
   mutate(condition = factor(condition), 
@@
 
-a <- d$gender == "F"
-length(a[a == TRUE])
-
+e1_gender = table(d$gender)
+#table(cut_interval(d$age, n=2, breaks=c(.5,1.5,2.1), labels=F))
+#table(cut_number(d$age, n=3, breaks=c(.5,1.5,2.1)))
+e1_parent_ed = table(d$parent_ed)
 ```
@@
 ### Participants. 
-`r nrow(d)` infants (F = 42, M = 18) aged 6-24 months (20 6-11.9 month-olds, 20 12-17.9 month-olds, and 20 18-24 month-olds) and their parents participated in a museum in northern California. 
+`r nrow(d)` infants (F = `r e1_gender['F']`, M = `r e1_gender['M']`) aged 6-24 months (20 6-11.9 month-olds, 20 12-17.9 month-olds, and 20 18-24 month-olds) and their parents participated in a museum in northern California.
 We included infants who were exposed to English at least 50 percent of the time (n = 58) or who were exposed less but whose participating parent reported that they primarily speak English with their child at home (n = 2).
-61% of participants (n = 37) had been exposed to two or more languages as indicated by their parent. 
+62% of participants (n = 37) had been exposed to two or more languages, as indicated by their parent. 
 Parents identified their children as White (n = 25), Asian (n = 11), African American/Black (n = 2), Biracial (n = 12), other (n = 5), or declined to state (n = 5). 
 Fifteen parents reported that their child was of Hispanic origin. 
-Parents tended to be highly-educated, with reports of highest level of education ranging from completed high school (n = 5), some college (n = 6), four-year college (n = 14), some graduate school (n = 1), to completed graduate school (n = 28) or declined to state (n = 6).
+Parents tended to be highly-educated, with reports of highest level of education ranging from completed high school (n = `r e1_parent_ed[1]`), some college (n = `r e1_parent_ed[2]`), four-year college (n = `r e1_parent_ed[3]`), some graduate school (n = `r e1_parent_ed[4]`), to completed graduate school (n = `r e1_parent_ed[5]`).
 
@@
 Parents participating in the Video condition were assigned to watch one of the two activity videos available for their child's age group, while parents in the Control condition watched no activity video, and were simply asked to play with their child as they normally would.
-The Control condition was yoked to the Activity Video condition such that for every participant in the Video condition who saw a particular video and received the associated props, a participant in the Control condition received the same props but did not watch the activity video.
+The Control condition was yoked to the Video condition such that for every participant in the Video condition who saw a particular video and received the associated props, a participant in the Control condition received the same props but did not watch the activity video.
 Parents also completed the Early Parenting Attitudes Questionnaire [EPAQ; @Hembacher2018]. 
@@
 ```{r, e1-lexdiv-regressions, echo=F, include=F}
+get_lmer_reporting_values <- function(lmer.fit, digits=2) {
+  Vcov <- vcov(lmer.fit, useScale = FALSE)
+  beta <- round(fixef(lmer.fit), digits)
+  se <- round(sqrt(diag(Vcov)), digits)
+  zval <- round(beta / se, digits)
+  pval <- round(2 * pnorm(abs(zval), lower.tail = FALSE), 4)
+  # not sure how to pull estimated degrees of freedom...
+  return(cbind(beta, se, zval, pval))
+}
+require("lmerTest")
 # Predicting lexical diversity based on experimental condition, PAQ, demographics. 
 modTTR <- lmer(TTR ~ condition + age + gender + parent_ed + (1|video), data=lmer_data)
-summary(modTTR) # condition -0.123 t(39.9) = 4.25 p<.001
+summary(modTTR) # condition:Exp -0.113 t(52.4) = 4.22 p<.001
+e1TTR = get_lmer_reporting_values(modTTR)
 
 modMTLD <- lmer(MTLD ~ condition + age + gender + parent_ed + (1|video), data=lmer_data)
-summary(modMTLD) # condition -11.67 t(43) = 3.08 p=.004 !! singular fit
-# Bayesian regression (stan_glmer in rstanarm) shows the same
+summary(modMTLD) # condition -8.73 t(55) = 2.67 p=.001 !! singular fit
+e1MTLD = get_lmer_reporting_values(modMTLD)
+# Bayesian regression (stan_glmer in rstanarm) shows the same:
+require("rstanarm")
+bmodMTLD <- stan_glmer(MTLD ~ condition + age + gender + parent_ed + (1|video), data=lmer_data)
+summary(bmodMTLD) # condition mean=-8.7 sd=3.3 2.5%=-15.1 97.5%=-20
 
 # predict word tokens
-tokens_mod <- lmer(tokens ~ condition*EL + condition*AA + condition*RR + age + gender + parent_ed + (1|video),  data=lmer_data)
-summary(tokens_mod) # condition 57.23 t(34.4) = 2.19 p<.05
+tokens_mod <- lmer(tokens ~ condition*EL + condition*AA + condition*RR + age + gender + parent_ed + (1|video),  data=lmer_data) # only 54 parents completed the EPAQ
+summary(tokens_mod) # condition 56.02 t(40.4) = 2.30 p<.05
+e1tokens = get_lmer_reporting_values(tokens_mod)
 
@@
 types_mod <- lmer(types ~ condition*EL + condition*AA + condition*RR  + age + gender + parent_ed + (1|video), data=lmer_data) # !! singular fit
-summary(types_mod) # nothing
+summary(types_mod) # nothing (hint: conditionexp:AA beta=19.04 p=.11)
+e1types = get_lmer_reporting_values(types_mod) 
+# verify with Bayesian regression:
+bmod_types <- stan_glmer(types ~ condition*EL + condition*AA + condition*RR  + age + gender + parent_ed + (1|video), data=lmer_data)
+summary(bmod_types)
+
+e1_lexdiv <- lmer_data %>% group_by(condition) %>%
+  summarise(TTR=mean(TTR), MTLD=mean(MTLD), tokens=mean(tokens)) 
 ```
@@
 We fit a mixed-effects linear regression predicting TTR as a function of condition, age (scaled and 0-centered), gender, and parent's education level with a random intercept per video using lme4 [@lme4].
-There was significantly lower TTR in the Video condition (mean: 0.32) than in the Control condition (mean: 0.43, $\beta=-.12$, t(39.9) = 4.25, *p*<.001). 
+There was significantly lower TTR in the Video condition (mean: `r round(subset(e1_lexdiv, condition=='exp')$TTR, 2)`) than in the Control condition (mean: `r round(subset(e1_lexdiv, condition=='con')$TTR, 2)`, $\beta=$`r e1TTR["conditionexp","beta"]`, t(52.4) = `r e1TTR["conditionexp","zval"]`, *p*<.001).
 There were no significant effects of age, gender, or parent's level of education.
-A similar mixed-effects linear regression instead predicting MTLD also found significantly lower lexical diversity in the Video condition (mean: 15.7) than in the Control condition (mean: 21.9, $\beta=-11.67$, t(43) = 3.08, *p*<.01), with no other significant effects.
-Figure 1 shows the mean of each lexical diversity measure (TTR and MTLD) by condition.
+A similar mixed-effects linear regression instead predicting MTLD also found significantly lower lexical diversity in the Video condition (mean MTLD: `r round(subset(e1_lexdiv, condition=='exp')$MTLD, 2)`) than in the Control condition (mean: `r round(subset(e1_lexdiv, condition=='exp')$TTR, 2)`, $\beta=$`r e1MTLD["conditionexp","beta"]`, t(55) = `r e1MTLD["conditionexp","zval"]`, *p*=.001), with no other significant effects.
+Figure \ref{fig:e1lex_div} shows the mean of each lexical diversity measure (TTR and MTLD) by condition.
 
-We also conducted similar regressions predicting the number of word tokens and types, finding only a significant effect of condition on the number of word tokens ($\beta=57.23$, t(34.4)=2.19, *p*<.05), with parents using more words in the Video condition (mean: 225, 95% CI: [197,252]) than in the Control condition (mean: 165, 95% CI: [139,193]).
-
-(Table with mean and SD of tokens, types, and TTR)
-
-```{r e1lex_div, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.5, fig.height=3.0, set.cap.width=T, num.cols.cap=1, fig.cap = "Mean lexical diversity scores by condition (left: Type/Token ratio, right: MTLD) in Experiment 1.
-Error bars show bootstrapped 95 percent confidence intervals (CIs)."}
+```{r e1tokens, echo=F, include=F}
 d$Condition = factor(d$condition, levels = c("con", "exp"), labels = c("Control", "Video"))
 
-# all at once, but there are NAs in SD cols ?
+ms_lex_mtld <- d %>% group_by(Condition) %>%
+  tidyboot_mean(MTLD) 
+ms_lex <- d %>% group_by(Condition) %>%
+  tidyboot_mean(TTR) # Type/Token Ratio
+ms_tok <- d %>% group_by(Condition) %>%
+  tidyboot_mean(tokens) 
+ms_type <- d %>% group_by(Condition) %>%
+  tidyboot_mean(types)
+```
+
+We also conducted similar regressions predicting the number of word tokens and types, finding only a significant effect of condition on the number of word tokens ($\beta= `r e1tokens["conditionexp","beta"]`$, t(40.4)=`r e1tokens["conditionexp","zval"]`, *p*<.05), with parents using more words in the Video condition (mean: `r round(subset(e1_lexdiv, condition=='exp')$tokens, 0)`, bootstrapped 95% confidence intervals (CI): [`r round(subset(ms_tok, Condition=="Video")$ci_lower, 0)`,`r round(subset(ms_tok, Condition=="Video")$ci_upper, 0)`]) than in the Control condition (mean: `r round(subset(e1_lexdiv, condition=='con')$tokens, 0)`, bootstrapped 95% CI: [`r round(subset(ms_tok, Condition=="Control")$ci_lower, 0)`,`r round(subset(ms_tok, Condition=="Control")$ci_upper, 0)`]).
+
+```{r tab1, echo=FALSE}
 e1 <- d %>% group_by(Condition) %>%
-  summarise(TTR=mean(TTR), TTRsd=sd(TTR),
-            MTLD=mean(MTLD), MTLDsd=sd(MTLD),
-            types=mean(types), types.sd=sd(types),
-            tokens = mean(tokens), tokens.sd=sd(tokens))
+  summarise("Mean TTR"=mean(TTR), TTRsd=sd(TTR),
+            "Mean MTLD"=mean(MTLD), MTLDsd=sd(MTLD),
+            "Mean types"=mean(types), types.sd=sd(types),
+            "Mean tokens"= mean(tokens), tokens.sd=sd(tokens))
+names(e1) = c("Condition","TTR (M)", "(sd)", "MTLD (M)", "(sd)", "Types (M)", "(sd)", "Tokens (M)", "(sd)")
+kable(e1, digits=2, caption="Lexical diversity measures in Experiment 1.")
+```
 
-ms_lex <- d %>%
-  group_by(Condition) %>%
-  multi_boot_standard(col="TTR") # Type/Token Ratio
-
-ttr_means <- d%>%
-  group_by(Condition)%>%
-  summarise(mean = mean(TTR), sd = sd(TTR))
-
-# report table with ttr_means lex_sds
+```{r fig:e1lex_div, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.5, fig.height=3.0, set.cap.width=T, num.cols.cap=1, fig.cap = "\\label{fig:e1lex_div} Mean lexical diversity scores by condition (left: Type/Token ratio, right: MTLD) in Experiment 1.
+Error bars show bootstrapped 95 percent confidence intervals (CIs)."}
 
 e1ttr <- ggplot(ms_lex, aes(x=Condition, y=mean, fill=Condition)) + geom_bar(stat="identity") + 
-  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
+  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .7)) +
+  geom_point(data=d, aes(x=Condition, y=TTR), alpha=.3, position = position_jitterdodge()) +
   xlab("Condition") + ylab("Type/Token Ratio (TTR)") +
@@
 
-ms_lex_mtld <- d %>%
-  group_by(Condition) %>%
-  multi_boot_standard(col="MTLD")
-
-mtld_means <- d %>%
-  group_by(Condition)%>%
-  summarise(mean = mean(MTLD), sd=sd(MTLD))
-
-# report table with mtld_means
-
 e1mtld <- ggplot(ms_lex_mtld, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
-  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9))+
+  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
+  geom_point(data=d, aes(x=Condition, y=MTLD), alpha=.3, position = position_jitterdodge()) +
   xlab("Condition") + ylab("MTLD") +
@@
 ```{r e1token_type, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.5, fig.height=3.0, set.cap.width=T, num.cols.cap=1, fig.cap = "Mean number of word types and word tokens by condition in Experiment 1."}
-ms_tok <- d %>% group_by(Condition) %>%
-  multi_boot_standard(col = "tokens")
 
-e1tokens <- ggplot(ms_tok, aes(x=Condition, y = mean, fill = Condition)) +geom_bar(stat="identity") + 
-  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9))+
+e1tokens <- ggplot(ms_tok, aes(x=Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
+  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
+  geom_point(data=d, aes(x=Condition, y=tokens), alpha=.3, position = position_jitterdodge()) +
   xlab("Condition") + ylab("Total Number of Word Tokens") +
@@
 
-ms_type <- d %>% group_by(Condition) %>%
-  multi_boot_standard(col = "types")
-
 e1types <- ggplot(ms_type, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
-  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
-             position = position_dodge(width = .9))+
+  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
+  geom_point(data=d, aes(x=Condition, y=types), alpha=.3, position = position_jitterdodge()) +
   xlab("Condition") + ylab("Total Number of Word Types") +
@@
 
-```{r, e1-effect-size, echo=F}
-cohens_d <- diff(ttr_means$mean) / (sqrt(sum(ttr_means$sd^2)) / 2)
+```{r, e1-effect-size, echo=F, include=F}
+cohens_d <- function(dat) {
+  return( diff(dat$mean) / (sqrt(sum(dat$sd^2)) / 2) )
+}
+
+ttr_means <- d %>% group_by(Condition) %>%
+  summarise(mean = mean(TTR), sd = sd(TTR))
+cohens_d(ttr_means) # -1.68
 ```
@@
 lmer_data <- d %>%
-  filter(!is.na(AA), !is.na(EL), !is.na(RR))%>%
+  filter(!is.na(AA), !is.na(EL), !is.na(RR)) %>%
   mutate(Condition = factor(Condition), 
@@
 summary(bids_mod) # condition beta = 3.51, t(40.3) = 2.95 p<.01, gender p=.05 ?
+e1bids = get_lmer_reporting_values(bids_mod)
 
-bid_cond <- lmer_data %>% group_by(Condition) %>% 
+e1bids_M <- lmer_data %>% group_by(Condition) %>% 
   summarise(mean = mean(bids), sd = sd(bids))
-print(bid_cond)
 
@@
 summary(pja_mod) # marginal RR, beta=-1.07 p=.07, condition*RR beta=1.83 p<.05
+e1pja = get_lmer_reporting_values(pja_mod)
 
@@
 This lme4 model included random intercepts per video. 
-There were significantly more bids for JA in the Video condition (mean: 6.24, sd: 2.79) than in the Control condition (mean: 3.56, sd: 2.50, $\beta=3.51$, t(40.3) = 2.95, *p*<.01). 
+There were significantly more bids for JA in the Video condition (mean: `r round(subset(e1bids_M, Condition=="Video")$mean,2)`, sd: `r round(subset(e1bids_M, Condition=="Video")$sd,2)`) than in the Control condition (mean: `r round(subset(e1bids_M, Condition=="Control")$mean,2)`, sd: `r round(subset(e1bids_M, Condition=="Control")$sd,2)`, $\beta=`r e1bids["ConditionVideo","beta"]`$, t(40.3) = `r e1bids["ConditionVideo","zval"]`, *p*<.01).
 There were no other significant effects.
@@
 
-```{r e1ja-graphs, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.5, fig.height=3.0, set.cap.width=T, num.cols.cap=1, fig.cap = "Mean number of bids and episodes of Joint Attention in Experiment 1."}
+```{r fig:e1ja, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.5, fig.height=3.0, set.cap.width=T, num.cols.cap=1, fig.cap = "\\label{fig:e1ja} Mean number of bids (left) and episodes (right) of joint attention by condition in Experiment 1."}
 
 ms_bids <- d %>% group_by(Condition) %>%
-  multi_boot_standard(col="bids_tot")
+  tidyboot_mean(bids_tot)
 
@@
   geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
+  geom_point(data=d, aes(x=Condition, y=bids_tot), alpha=.3, position = position_jitterdodge()) +
   xlab("Condition") + ylab("Total Bids for Joint Attention") +
@@
 ms_tja <- d %>% group_by(Condition) %>%
-  multi_boot_standard(col = "total_ja")
+  tidyboot_mean(total_ja)
 
 e1tja <- ggplot(ms_tja, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
-  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9))+
+  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
+  geom_point(data=d, aes(x=Condition, y=total_ja), alpha=.3, position = position_jitterdodge()) +
   xlab("Condition") + ylab("Total Episodes of Joint Attention") +
@@
 
-```{r e1ja-graphs-pass-coord, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.5, fig.height=3.0, set.cap.width=T, num.cols.cap=1, fig.cap = "Average number of passive and coordinated episodes of JA in Experiment 1."}
+```{r fig:e1ja-pass-coord, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.5, fig.height=3.5, set.cap.width=T, num.cols.cap=1, fig.cap = "\\label{fig:e1ja-pass-coord} Average number of passive and coordinated episodes of JA in Experiment 1."}
 ms_pja <- d %>% group_by(Condition) %>%
-  multi_boot_standard(col = "pja")
+  tidyboot_mean(pja)
 
 e1pja <- ggplot(ms_pja, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
-  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9))+
+  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
+  geom_point(data=d, aes(x=Condition, y=pja), alpha=.3, position = position_jitterdodge()) +
   xlab("Condition") + ylab("Episodes of Passive Joint Attention") +
@@
 ms_cja <- d %>% group_by(Condition) %>%
-  multi_boot_standard(col = "cja")
+  tidyboot_mean(cja)
 
 e1cja <- ggplot(ms_cja, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
-  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9))+
+  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
+  geom_point(data=d, aes(x=Condition, y=cja), alpha=.3, position = position_jitterdodge()) +
   xlab("Condition") + ylab("Episodes of Coordinated Joint Attention")  +
@@
 In summary, while parents produced more word types and tokens after viewing the activity video, lexical diversity (Type/Token ratio and MTLD) was higher when parents were just asked to play as they normally would.
-This may suggest that parents in the Video condition are being more repetitive in their attempt to stick to the task prescribed in the video.
-Demographics and EPAQ do not interact with condition, but there is a marginal effect of RR score on lexical diversity (lower diversity for higher RR scores), and marginal effects of parent education on word types and tokens (more types and tokens for higher parent education).
+This may suggest that parents in the Video condition end up being more repetitive in their attempt to stick to the task prescribed in the video.
+Demographics and EPAQ do not interact with condition, although there was a marginal effect of RR score on lexical diversity (lower diversity for higher RR scores), and marginal effects of parent education on word types and tokens (more types and tokens for higher parent education).
 
 There was a main effect of condition on total bids for joint attention. 
-Parents in the Video condition, after seeing a video demonstrating an activity, made a greater number of bids for joint attention with their child.
+Parents in the Video condition, after seeing a video demonstrating an activity, made a greater number of bids for JA with their child.
 There was no effect of condition on the number of episodes of either passive or coordinated joint attention, or the duration of these episodes. 
-There was a marginal effect of gender on bids for joint attention, with parents of males producing more bids. 
-There was a marginal interaction between RR scores and condition on passive joint attention, such that the experimental condition increased the number of episodes of PJA to a greater extent for people with high RR scores.
+There was a marginal effect of gender on bids for JA, with parents of males producing more bids. 
+There was a marginal interaction between RR scores and condition on passive joint attention, such that the experimental condition increased the number of episodes of passive JA to a greater extent for people with high RR scores.
 While the electronically-delivered parenting advice increased the number of bids for joint attention by parents, it did not significantly effect the number or duration of episodes of joint attention. 
@@
 Parents who watched a Kinedu video also made more bids for joint attention, although these bids did not result in more episodes of joint attention compared to the control group. 
-Experiment 2 attempts to replicate these findings from with a restricted number of preregistered predictions ([link](https://osf.io/2bpdf/)).
+Experiment 2 attempts to replicate these findings from with a restricted number of preregistered predictions.[^3]
+
+[^3]: Preregistration: [https://osf.io/2bpdf/](https://osf.io/2bpdf/).
 
@@
          video = as.factor(video))
+
+e2_gender = table(d$gender)
+e2_ethnicity = table(d$ethnicity)
+e2_parent_ed = table(d$parent_ed)
 ```
@@
 ### Participants. 
-`r nrow(d)` infants (F = 37, M = 47) aged 12-24 months (42 12-17.9 month-olds, 42 18-24 month-olds) and their parents participated in the same museum as Experiment 1. 
+`r nrow(d)` infants (F = `r e2_gender['F']`, M = `r e2_gender['M']`) aged 12-24 months (42 12-17.9 month-olds, 42 18-24 month-olds) and their parents participated in the same museum as Experiment 1. 
 We included infants who were exposed to English at least 75 percent of the time or who were exposed less but whose participating parent reported that they primarily speak English with their child at home.
-Forty nine% of participants (n = 41) had been exposed to two or more languages as indicated by their parent. 
+Forty-nine percent of participants (n = 41) had been exposed to two or more languages as indicated by their parent. 
 Parents identified their children as White (n = 39), Asian (n = 20), African American/Black (n = 1), Biracial (n = 9), other (n = 7), or declined to state (n = 8).
 Sixteen parents reported their child was of Hispanic origin.
-Parents tended to be highly- educated, with reports of highest level of education ranging from completed high school (n = 0), some college (n = 5), four-year college (n = 28), some graduate school (n = 2), to completed graduate school (n = 35) or declined to state (n = 14).
+Parents tended to be highly-educated, with reports of highest level of education ranging from some college (n = `r e2_parent_ed[3]`), four-year college (n = `r e2_parent_ed[4]`), some graduate school (n = `r e2_parent_ed[5]`), to completed graduate school (n = `r e2_parent_ed[6]`) or declined to state (n = 13).
 
@@
 A second coder independently coded a third of the videos (i.e., 26 of the 84 videos, approximately equally distributed across ages) to establish reliability. 
-The two coders had a reliability of ICC = 0.80 with 95% confident interval (CI) = [0.60,0.90] (p < 0.05) for number of parent bids for JA; ICC = 0.74 with 95% CI = [0.59,0.87] (p < 0.05) for number of passive JA episodes; ICC = 0.78 with 95% CI = [0.58,0.90] (p < 0.05) for number of coordinated JA episodes; ICC = 0.72 with 95% CI = [0.46,0.86] (p < 0.05) for total duration of passive JA episodes, and ICC = 0.88 with 95% CI = [0.75,0.94] (p < 0.05) for total duration of coordinated JA episodes.
+The two coders had a reliability of ICC = 0.80 with 95% confidence interval (CI) = [0.60,0.90] for number of parent bids for JA; ICC = 0.74 with 95% CI = [0.59,0.87] for number of passive JA episodes; ICC = 0.78 with 95% CI = [0.58,0.90] for number of coordinated JA episodes; ICC = 0.72 with 95% CI = [0.46,0.86] for total duration of passive JA episodes, and ICC = 0.88 with 95% CI = [0.75,0.94] for total duration of coordinated JA episodes.
 
@@
 A similar mixed-effects linear regression instead predicting MTLD found no significant effects of age or condition.
-Figure X shows the mean of each lexical diversity measure (TTR and MTLD) by condition.
+Figure \ref{fig:e2lexdiv} shows the mean of each lexical diversity measure (TTR and MTLD) by condition.
 Regressions with the same structure predicting the number of word tokens and types found no significant effects of age or condition.
 
-(Table with mean and SD of tokens, types, TTR, MTLD)
+```{r e2tab, echo=F}
+d$Condition = factor(d$condition, levels = c("con", "exp"), labels = c("Control", "Video"))
+e2 <- d %>% group_by(Condition) %>%
+  summarise("Mean TTR"=mean(TTR), TTRsd=sd(TTR),
+            "Mean MTLD"=mean(MTLD), MTLDsd=sd(MTLD),
+            "Mean types"=mean(types), types.sd=sd(types),
+            "Mean tokens"= mean(tokens), tokens.sd=sd(tokens))
+names(e2) = c("Condition","TTR (M)", "(sd)", "MTLD (M)", "(sd)", "Types (M)", "(sd)", "Tokens (M)", "(sd)")
+kable(e2, digits=2, caption="Lexical diversity measures in Experiment 2.")
+```
 
-```{r e2lexdiv, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.5, fig.height=3, set.cap.width=T, num.cols.cap=1, fig.cap = "Mean lexical diversity scores by condition (left: Type/Token ratio, right: MTLD) in Experiment 2."}
-
-d$Condition = factor(d$condition, levels = c("con", "exp"), labels = c("Control", "Video"))
-
-# all at once, but there are NAs in SD cols ?
-e2 <- d %>% group_by(Condition) %>%
-  summarise(TTR=mean(TTR), TTRsd=sd(TTR),
-            MTLD=mean(MTLD), MTLDsd=sd(MTLD),
-            types=mean(types), types.sd=sd(types),
-            tokens = mean(tokens), tokens.sd=sd(tokens))
+```{r fig:e2lexdiv, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.5, fig.height=3, set.cap.width=T, num.cols.cap=1, fig.cap = "\\label{fig:e2lexdiv} Mean lexical diversity scores by condition (left: Type/Token ratio, right: MTLD) in Experiment 2."}
 
 ms_lex <- d %>% group_by(Condition) %>%
-  multi_boot_standard(col="TTR") 
-ttr_mean <- d%>% group_by(Condition)%>%
-  summarise(mean=mean(TTR), sd=sd(TTR))
+  tidyboot_mean(TTR)
 
-ttr_means <- d%>%
-  group_by(Condition)%>%
+ttr_means <- d %>% group_by(Condition) %>%
   summarise(mean = mean(TTR), sd = sd(TTR))
@@
   geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
+  geom_point(data=d, aes(x=Condition, y=TTR), alpha=.3, position = position_jitterdodge()) +
   xlab("Condition") + ylab("TTR") +
@@
 ms_lex <- d %>% group_by(Condition) %>%
-  multi_boot_standard(col="MTLD") 
+  tidyboot_mean(MTLD) 
 mltd_mean <- d %>% group_by(Condition)%>%
-  summarise(mean = mean(MTLD), sd=sd(MTLD))
-
-mtld_means <- d %>%
-  group_by(Condition)%>%
   summarise(mean = mean(MTLD), sd=sd(MTLD))
@@
   geom_bar(stat="identity") + 
-  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9))+
+  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
+  geom_point(data=d, aes(x=Condition, y=MTLD), alpha=.3, position = position_jitterdodge()) +
   xlab("Condition") + ylab("MTLD") +
@@
 ms_tok <- d %>% group_by(Condition) %>%
-  multi_boot_standard(col = "tokens")
+  tidyboot_mean(tokens)
 
 e2tokens <- ggplot(ms_tok, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
-  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9))+
+  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
+  geom_point(data=d, aes(x=Condition, y=tokens), alpha=.3, position = position_jitterdodge()) +
   xlab("Condition") + ylab("Total Number of Word Tokens") +
@@
 ms_typ <- d %>% group_by(Condition) %>%
-  multi_boot_standard(col = "types")
+  tidyboot_mean(types)
 
 e2types <- ggplot(ms_typ, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
-  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9))+
+  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
+  geom_point(data=d, aes(x=Condition, y=types), alpha=.3, position = position_jitterdodge()) +
   xlab("Condition") + ylab("Total Number of Word Types") +
@@
 
-```{r e2ja-graphs, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.5, fig.height=3.0, set.cap.width=T, num.cols.cap=1, fig.cap = "Mean number of bids and episodes of Joint Attention in Experiment 2."}
+```{r fig:e2ja, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.5, fig.height=3.0, set.cap.width=T, num.cols.cap=1, fig.cap = "\\label{fig:e2ja} Mean number of bids and episodes of Joint Attention in Experiment 2."}
 
 ms_bids <- d %>% group_by(Condition) %>%
-  multi_boot_standard(col="bids")
+  tidyboot_mean(bids)
 
@@
   geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
+  geom_point(data=d, aes(x=Condition, y=bids), alpha=.3, position = position_jitterdodge()) +
   xlab("Condition") + ylab("Total Bids for Joint Attention") +
@@
 ms_tja <- d %>% group_by(Condition) %>%
-  multi_boot_standard(col = "total_ja")
+  tidyboot_mean(total_ja)
 
 e2tja <- ggplot(ms_tja, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
-  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9))+
+  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
+  geom_point(data=d, aes(x=Condition, y=total_ja), alpha=.3, position = position_jitterdodge()) +
   xlab("Condition") + ylab("Total Episodes of Joint Attention") +
@@
 ms_pja <- d %>% group_by(Condition) %>%
-  multi_boot_standard(col = "pja")
+  tidyboot_mean(pja)
 
 e2pja <- ggplot(ms_pja, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
-  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9))+
+  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
+  geom_point(data=d, aes(x=Condition, y=pja), alpha=.3, position = position_jitterdodge()) +
   xlab("Condition") + ylab("Episodes of Passive Joint Attention") +
@@
 ms_cja <- d %>% group_by(Condition) %>%
-  multi_boot_standard(col = "cja")
+  tidyboot_mean(cja)
 
 e2cja <- ggplot(ms_cja, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
-  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9))+
+  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
+  geom_point(data=d, aes(x=Condition, y=cja), alpha=.3, position = position_jitterdodge()) +
   xlab("Condition") + ylab("Episodes of Coordinated Joint Attention") +

### 2019-07-06 paper/cogsci2019/cogsci2019.Rmd
Update cogsci2019.Rmd

@@
 
-```{r fig:e1ja-pass-coord, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.5, fig.height=3.5, set.cap.width=T, num.cols.cap=1, fig.cap = "\\label{fig:e1ja-pass-coord} Average number of passive and coordinated episodes of JA in Experiment 1."}
+```{r fig:e1ja-pass-coord, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.5, fig.height=3.5, set.cap.width=T, num.cols.cap=1, fig.cap = "\\label{fig:e1ja-pass-coord} Mean number of passive (left) and coordinated episodes (right) of JA by condition in Experiment 1."}
 ms_pja <- d %>% group_by(Condition) %>%
@@
 
-In summary, while parents produced more word types and tokens after viewing the activity video, lexical diversity (Type/Token ratio and MTLD) was higher when parents were just asked to play as they normally would.
-This may suggest that parents in the Video condition end up being more repetitive in their attempt to stick to the task prescribed in the video.
+In summary, while parents produced more word types and tokens after viewing the activity video, lexical diversity (both TTR and MTLD) was higher when parents were just asked to play as they normally would.
+It may be that parents in the Video condition, in their attempt to stick to the prescribed task, end up repeating themselves more.
 Demographics and EPAQ do not interact with condition, although there was a marginal effect of RR score on lexical diversity (lower diversity for higher RR scores), and marginal effects of parent education on word types and tokens (more types and tokens for higher parent education).
 
-There was a main effect of condition on total bids for joint attention. 
+There was a main effect of condition on total bids for joint attention (JA). 
 Parents in the Video condition, after seeing a video demonstrating an activity, made a greater number of bids for JA with their child.
-There was no effect of condition on the number of episodes of either passive or coordinated joint attention, or the duration of these episodes. 
+There was no effect of condition on the number of episodes of either passive or coordinated JA, or the duration of these episodes. 
 There was a marginal effect of gender on bids for JA, with parents of males producing more bids. 
-There was a marginal interaction between RR scores and condition on passive joint attention, such that the experimental condition increased the number of episodes of passive JA to a greater extent for people with high RR scores.
-While the electronically-delivered parenting advice increased the number of bids for joint attention by parents, it did not significantly effect the number or duration of episodes of joint attention. 
-It may be that child variables had a larger relative impact on the attainment of joint attention.
+There was a marginal interaction between RR scores and condition on passive JA, such that the experimental condition increased the number of episodes of passive JA to a greater extent for people with high RR scores.
+While the electronically-delivered parenting advice increased the number of bids for JA by parents, it did not significantly affect the number or duration of episodes of JA. 
+It may be that children had a larger relative impact on the attainment of joint attention.
 
@@
 The design of Experiment 2 was similar to that of Experiment 1, except that instead of a No-Video control condition, parents instead watched a video that was generally related to child development research, but did not give any specific instructions about how to interact with infants or children.
-This was to control for the possibility that differences in language output and joint attention in Experiment 1 could be due to simply cuing parents to think about infants' learning and cognitive development.
+This condition was included to control for the possibility that differences in language output and joint attention in Experiment 1 could be due to simply cueing parents to think about infants' learning and cognitive development.
 The videos presented in the Control Video condition were media clips (available on YouTube) of developmental psychologists explaining their research interleaved with footage of infants or toddlers engaged in developmental research studies.
@@
 The videos were trimmed to approximately match the average video length in the Activity Video condition (close to 90 s).
+Details of the Kinedu videos used in the Activity Video conditions are in the Appendix.
 
@@
 summary(modTTR) # condition beta=-.09  t(8.7) = 3.06 p=.01
+e2TTR <- get_lmer_reporting_values(modTTR)
 
@@
 We fit a mixed-effects linear regression predicting TTR and MTLD as a function of age (scaled and 0-centered) and condition with an interaction term, and with random intercepts per video using lme4 [@lme4].
-There was significantly lower TTR in the Video condition (mean: 0.38) than in the Control condition (mean: 0.47, $\beta=-.09$, t(8.7) = 3.06, *p*=.01).
-There was no significant effect of age.
+There was significantly lower TTR in the Video condition (mean: 0.38) than in the Control condition (mean: 0.47, $\beta=`r e2TTR["conditionexp","beta"]`$, t(8.7) = `r e2TTR["conditionexp","zval"]`, *p*=.01).
+There was no significant effect of age, nor a significant interaction.
 A similar mixed-effects linear regression instead predicting MTLD found no significant effects of age or condition.
@@
 Regressions with the same structure predicting the number of word tokens and types found no significant effects of age or condition.
+The means of the lexical measures are shown in Table \ref{e2tab}.
 
@@
 
-ttr_means <- d %>% group_by(Condition) %>%
-  summarise(mean = mean(TTR), sd = sd(TTR))
-
-# report table with ttr_means lex_sds
-
-e2ttr <- ggplot(ms_lex, aes(x=Condition, y=mean, fill=Condition)) + ylim(0.0, 0.6) + geom_bar(stat="identity") + 
+e2ttr <- ggplot(ms_lex, aes(x=Condition, y=mean, fill=Condition)) + geom_bar(stat="identity") + 
   geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
@@
 ```{r, e2-effect-size, echo=F}
-cohens_d <- diff(ttr_means$mean) / (sqrt(sum(ttr_means$sd^2)) / 2)
+ttr_means <- d %>% group_by(Condition) %>%
+  summarise(mean = mean(TTR), sd = sd(TTR))
+cohens_d(ttr_means)
 ```
@@
 load(paste(e2path,"joint_attention/Exp2_joint_attention_data.RData",sep=''))
+summary(d)
+# triplicate variables: gender.x/y, ethnicity, english, num_lang, parent_ed, Exclude
 d$Condition <- factor(d$condition, levels = c("con","exp"), labels = c("Control","Video"))
 e2ja = d
+e2ja$age = scale(e2ja$age)
 
+# did preregistration include this?
 t.test(subset(e2ja, Condition=="Control")$bids, subset(e2ja, Condition=="Video")$bids)
@@
 summary(bids_mod) # singular fit, covergence code: 0 - no effects
+bmodMTLD <- stan_glmer(bids ~ age * Condition + (1|video), data=e2ja)
+summary(bmodMTLD) # significant effect of condition! mean=3.2, 95%CI = [1.2, 5.2]
 
-# Episodes of coordinated joint attention.
+# Episodes of coordinated joint attention
 cja_mod <- lmer(cja ~ age * condition + (1 | video), data = e2ja)
@@
 
-```{r fig:e2ja, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.5, fig.height=3.0, set.cap.width=T, num.cols.cap=1, fig.cap = "\\label{fig:e2ja} Mean number of bids and episodes of Joint Attention in Experiment 2."}
+As specified in our preregistration, we fit five mixed-effects linear regressions predicting the following JA variables: parental bids, the number of episodes of coordinated JA and passive JA, and the total duration of coordinated and passive JA.
+These JA variables were predicted as a function of fixed effects of condition, age (scaled and 0-centered), and gender, with random intercepts per video.
+There were significantly more bids for JA in the Video condition (mean: `r round(subset(e1bids_M, Condition=="Video")$mean,2)`, sd: `r round(subset(e1bids_M, Condition=="Video")$sd,2)`) than in the Control condition (mean: `r round(subset(e1bids_M, Condition=="Control")$mean,2)`, sd: `r round(subset(e1bids_M, Condition=="Control")$sd,2)`, $\beta=`r e1bids["ConditionVideo","beta"]`$, t(40.3) = `r e1bids["ConditionVideo","zval"]`, *p*<.01).
+There were no other significant effects.
+There were no significant effects on the number or total duration of coordinated JA episodes, nor on the total duration of passive JA episodes. 
+For the regression predicting the number of passive JA episodes, the only significant effect was an interaction of condition and RR ($\beta=1.83$, t(41.5) = 2.22, *p*<.05), showing that for parents in the Video condition, those with higher Rules and Respect subscores engaged in more passive JA episodes.
+Figure X shows ... by condition.
+
+```{r fig:e2ja, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.5, fig.height=3.0, set.cap.width=T, num.cols.cap=1, fig.cap = "\\label{fig:e2ja} Mean number of bids and episodes of JA by condition in Experiment 2."}
 
@@
 
-```{r e2ja-graphs-pass-coord, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.5, fig.height=3.0, set.cap.width=T, num.cols.cap=1, fig.cap = "Average number of passive and coordinated episodes of JA in Experiment 2."}
+```{r e2ja-pass-coord, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.5, fig.height=3.0, set.cap.width=T, num.cols.cap=1, fig.cap = "\\label{fig:e2ja-pass-coord} Mean number of passive (left) and coordinated (right) episodes of JA by condition in Experiment 2."}
 ms_pja <- d %>% group_by(Condition) %>%

### 2019-07-07 paper/cogsci2019/cogsci2019.Rmd
updated Exp2 analyses

@@
 
-Parents' child-directed speech was transcribed and processed according to the same procedure used in Experiment 1.
+Parents' child-directed speech was transcribed and processed according to the same procedure used in Experiment 1, and the preregistered regressions predicting TTR and number of tokens were carried out.
 
@@
 
-# predict word types
-types_mod <- lmer(types ~ age * condition + (1 | video), data=lmer_data)
-summary(types_mod) # NA
+# predict word types (NOT A PREREGISTERED REGRESSION)
+#types_mod <- lmer(types ~ age * condition + (1 | video), data=lmer_data)
+#summary(types_mod) # NA
 ```
 
-We fit a mixed-effects linear regression predicting TTR and MTLD as a function of age (scaled and 0-centered) and condition with an interaction term, and with random intercepts per video using lme4 [@lme4].
+We fit a mixed-effects linear regression predicting TTR as a function of age (scaled and 0-centered) and condition with an interaction term, and with random intercepts per video using lme4 [@lme4].
 There was significantly lower TTR in the Video condition (mean: 0.38) than in the Control condition (mean: 0.47, $\beta=`r e2TTR["conditionexp","beta"]`$, t(8.7) = `r e2TTR["conditionexp","zval"]`, *p*=.01).
 There was no significant effect of age, nor a significant interaction.
-A similar mixed-effects linear regression instead predicting MTLD found no significant effects of age or condition.
+The preregistered regression of 
+An exploratory similar mixed-effects linear regression instead predicting MTLD found no significant effects of age or condition.
 Figure \ref{fig:e2lexdiv} shows the mean of each lexical diversity measure (TTR and MTLD) by condition.
-Regressions with the same structure predicting the number of word tokens and types found no significant effects of age or condition.
+Regressions with the same structure predicting the number of words tokens found no significant effects of age or condition.
 The means of the lexical measures are shown in Table \ref{e2tab}.
@@
 
-```{r fig:e2lexdiv, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.5, fig.height=3, set.cap.width=T, num.cols.cap=1, fig.cap = "\\label{fig:e2lexdiv} Mean lexical diversity scores by condition (left: Type/Token ratio, right: MTLD) in Experiment 2."}
+```{r fig:e2lexdiv, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=5.5, fig.height=3, set.cap.width=T, num.cols.cap=1, fig.cap = "\\label{fig:e2lexdiv} Mean lexical diversity scores by condition (left: Type/Token ratio, middle: MTLD, right: word tokens) in Experiment 2."}
 
@@
   tidyboot_mean(MTLD)
-mltd_mean <- d %>% group_by(Condition)%>%
-  summarise(mean = mean(MTLD), sd=sd(MTLD))
 
@@
 
-multiplot(e2ttr, e2mtld, cols=2)
-```
-
-```{r e2token-type, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.5, fig.height=3, set.cap.width=T, num.cols.cap=1, fig.cap = "Mean number of word types and word tokens by condition in Experiment 2."}
 ms_tok <- d %>% group_by(Condition) %>%
@@
   theme(legend.position="none")
+
+multiplot(e2ttr, e2mtld, e2tokens, cols=3)
+```
+
+```{r e2token-type, include=F, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.5, fig.height=3, set.cap.width=T, num.cols.cap=1, fig.cap = "Mean number of word types and word tokens by condition in Experiment 2."}
 
@@
 
-multiplot(e2tokens, e2types, cols=2)
+#multiplot(e2tokens, e2types, cols=2)
 ```
@@
 e2ja = d
-e2ja$age = scale(e2ja$age)
-
-# did preregistration include this?
-t.test(subset(e2ja, Condition=="Control")$bids, subset(e2ja, Condition=="Video")$bids)
+e2ja$age = as.numeric(langcog::scale(e2ja$age, scale=FALSE)) # 0-centered but NOT scaled -- change text
 
@@
 bids_mod <- lmer(bids ~ age * Condition + (1 | video), data = e2ja)
-summary(bids_mod) # singular fit, covergence code: 0 - no effects
-bmodMTLD <- stan_glmer(bids ~ age * Condition + (1|video), data=e2ja)
-summary(bmodMTLD) # significant effect of condition! mean=3.2, 95%CI = [1.2, 5.2]
+summary(bids_mod) # singular fit, convergence code: 0
+e2bids <- get_lmer_reporting_values(bids_mod)
+# Condition est = 3.25 t(79) = 3.65 p<.001
+bids_bmod <- stan_glmer(bids ~ age * Condition + (1|video), data=e2ja)
+summary(bids_bmod) # significant effect of condition! mean=3.2, 95%CI = [1.2, 5.2]
+
+tja_mod <- lmer(total_ja ~ age * Condition + (1 | video), data = e2ja)
+summary(tja_mod) # singular fit, convergence code: 0
+#                    Estimate Std. Error      df t value  Pr(>|t|) 
+# age                 -4.6051     1.3927 79.0000  -3.306  0.00142 ** 
+# ConditionVideo       1.5253     0.5626 79.0000   2.711  0.00822 ** 
+# age:ConditionVideo   5.5193     2.1893 79.0000   2.521  0.01371 *
+
+tja_bmod <- stan_glmer(total_ja ~ age * Condition + (1|video), data=e2ja)
+summary(tja_bmod) # age n.s., sig effect of condition: mean=3.2 95%CI = [1.1, 5.2]
+#                                        mean    sd     2.5%   25%    50%    75%    97.5%
+# (Intercept)                             7.3    0.5    6.3    6.9    7.2    7.6    8.2 
+# age                                    -4.3    1.5   -7.2   -5.3   -4.3   -3.3   -1.3 
+# ConditionVideo                          1.5    0.7    0.2    1.1    1.5    1.9    2.9
+
+# EXPLORATORY ANALYSES (NOT PREREGISTERED)
 
 # Episodes of coordinated joint attention
-cja_mod <- lmer(cja ~ age * condition + (1 | video), data = e2ja)
-summary(cja_mod) # marginal condition: t(79) = 1.88 beta=-5.85 p=.06, age*condition beta=4.92 t(79) = 2.35 p=.02
-# also singular fit, covergence code: 0
+cja_mod <- lmer(cja ~ age * Condition + (1 | video), data = e2ja)
+summary(cja_mod) #  Condition: t(79) = 2.47 beta=1.33 p=.02; age*Condition beta=4.92 t(79) = 2.35 p=.02
+# also singular fit, convergence code: 0 - check Bayesian regression
+cja_bmod <- stan_glmer(cja ~ age * Condition + (1|video), data=e2ja)
+summary(cja_bmod) # age n.s., sig effect of condition: mean=1.3 95% CI=[.1,2.6]; age*condition mean=5.1 CI=[.5,9.6]
+#                                        mean    sd     2.5%   25%    50%    75%    97.5%
+# (Intercept)                             5.3    0.4    4.5    5.0    5.3    5.6    6.2 
+# age                                    -2.0    1.4   -4.8   -2.9   -2.0   -1.1    0.9 
+# ConditionVideo                          1.3    0.6    0.1    0.9    1.3    1.7    2.6 
+# age:ConditionVideo                      5.1    2.3    0.5    3.5    5.1    6.5    9.6
 
 # Episodes of passive joint attention.
-pja_mod <- lmer(pja ~ age * condition + (1 | video), data = e2ja)
+pja_mod <- lmer(pja ~ age * Condition + (1 | video), data = e2ja)
 summary(pja_mod) # age beta=-2.32 t(26.6) = 2.23 p<.05
@@
 # Total duration of passive joint attention.
-pja_time_mod <- lmer(pja_length ~ age * condition + (1 | video), data = e2ja)
-summary(pja_time_mod) # age beta=-15512 t(79) = 2.40 p<.05
+pja_time_mod <- lmer(pja_length ~ age * Condition + (1 | video), data = e2ja)
+summary(pja_time_mod) # singular - convergence code: 0, age beta=-15512 t(79) = 2.40 p<.05
+pjat_bmod <- stan_glmer(pja_length ~ age * Condition + (1|video), data=e2ja)
+summary(pjat_bmod)
+#                                        mean       sd         2.5%       25%        50%        75%        97.5%   
+#(Intercept)                             11247.4     2193.1     6977.7     9822.1    11239.1    12655.2    15736.7
+#age                                    -13924.2     7097.9   -27467.6   -18661.5   -14163.6    -9341.5      722.4
+#ConditionVideo                            824.8     3098.5    -5399.6    -1190.0      846.8     2877.5     6867.3
+#age:ConditionVideo                        108.3    11738.0   -23881.5    -7171.3      411.3     7778.3    22058.5
 
@@
 cja_time_mod <- lmer(cja_length ~ age * condition + (1 | video), data = e2ja)
-summary(cja_time_mod) # marginal age: beta=31757 t(79) = 1.81 p=.07
+summary(cja_time_mod) # singular - convergence code: 0, marginal age: beta=31757 t(79) = 1.81 p=.07
+cjat_bmod <- stan_glmer(cja_length ~ age * Condition + (1|video), data=e2ja)
+summary(cjat_bmod)
+#                                           mean        sd          2.5%        25%         50%         75%      
+#(Intercept)                              73053.4      5611.1     62252.3     69338.3     73049.6     76773.7
+#age                                      28879.1     19079.4     -8533.5     16385.2     29112.3     41487.9
+#ConditionVideo                            5745.4      7874.5     -9994.6       535.3      5725.3     11163.4
+#age:ConditionVideo                       45792.3     30918.9    -14154.8     25281.7     45101.1     66074.2
+
+e2_bids <- e2ja %>% group_by(Condition) %>%
+  tidyboot_mean(bids)
+e2_tja <- e2ja %>% group_by(Condition) %>%
+  tidyboot_mean(total_ja) 
 ```
@@
 As specified in our preregistration, we fit five mixed-effects linear regressions predicting the following JA variables: parental bids, the number of episodes of coordinated JA and passive JA, and the total duration of coordinated and passive JA.
-These JA variables were predicted as a function of fixed effects of condition, age (scaled and 0-centered), and gender, with random intercepts per video.
-There were significantly more bids for JA in the Video condition (mean: `r round(subset(e1bids_M, Condition=="Video")$mean,2)`, sd: `r round(subset(e1bids_M, Condition=="Video")$sd,2)`) than in the Control condition (mean: `r round(subset(e1bids_M, Condition=="Control")$mean,2)`, sd: `r round(subset(e1bids_M, Condition=="Control")$sd,2)`, $\beta=`r e1bids["ConditionVideo","beta"]`$, t(40.3) = `r e1bids["ConditionVideo","zval"]`, *p*<.01).
+These JA variables were predicted as a function of fixed effects of condition, age (0-centered), with random intercepts per video.
+There were significantly more bids for JA in the Video condition (mean: `r round(subset(e2_bids, Condition=="Video")$mean,2)`, bootstrapped 95% CI: `r round(subset(e2_bids, Condition=="Video")$ci_lower,2)`, `r round(subset(e2_bids, Condition=="Video")$ci_upper,2)`) than in the Control condition (mean: `r round(subset(e2_bids, Condition=="Control")$mean,2)`, 95% CI: `r round(subset(e2_bids, Condition=="Control")$ci_lower,2)`, `r round(subset(e2_bids, Condition=="Control")$ci_upper,2)`, $\beta=`r e2bids["ConditionVideo","beta"]`$, t(79) = `r e2bids["ConditionVideo","zval"]`, *p*<.001).
 There were no other significant effects.
 There were no significant effects on the number or total duration of coordinated JA episodes, nor on the total duration of passive JA episodes.
-For the regression predicting the number of passive JA episodes, the only significant effect was an interaction of condition and RR ($\beta=1.83$, t(41.5) = 2.22, *p*<.05), showing that for parents in the Video condition, those with higher Rules and Respect subscores engaged in more passive JA episodes.
-Figure X shows ... by condition.
+
+Figure \ref{fig:e2ja} shows the mean number of bids and episodes of JA by condition.
 
@@
 
-ms_bids <- d %>% group_by(Condition) %>%
-  tidyboot_mean(bids)
-
-e2bids <- ggplot(ms_bids, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
+e2bids <- ggplot(e2_bids, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
   geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
@@
 
-# total joint attention episodes
-ms_tja <- d %>% group_by(Condition) %>%
-  tidyboot_mean(total_ja)
-
-e2tja <- ggplot(ms_tja, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
+# total JA episodes
+e2tja <- ggplot(e2_tja, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
   geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +

### 2019-07-08 paper/cogsci2019/cogsci2019.Rmd
fixed rounded ages in Exp 2

@@
   geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .7)) +
-  geom_point(data=d, aes(x=Condition, y=TTR), alpha=.3, position = position_jitterdodge()) +
+  geom_point(data=d, aes(x=Condition, y=TTR), alpha=.2, position = position_jitterdodge()) +
   xlab("Condition") + ylab("Type/Token Ratio (TTR)") +
@@
   geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
-  geom_point(data=d, aes(x=Condition, y=MTLD), alpha=.3, position = position_jitterdodge()) +
+  geom_point(data=d, aes(x=Condition, y=MTLD), alpha=.2, position = position_jitterdodge()) +
   xlab("Condition") + ylab("MTLD") +
@@
   geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
-  geom_point(data=d, aes(x=Condition, y=tokens), alpha=.3, position = position_jitterdodge()) +
+  geom_point(data=d, aes(x=Condition, y=tokens), alpha=.2, position = position_jitterdodge()) +
   xlab("Condition") + ylab("Total Number of Word Tokens") +
@@
   geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
-  geom_point(data=d, aes(x=Condition, y=types), alpha=.3, position = position_jitterdodge()) +
+  geom_point(data=d, aes(x=Condition, y=types), alpha=.2, position = position_jitterdodge()) +
   xlab("Condition") + ylab("Total Number of Word Types") +
@@
   geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
-  geom_point(data=d, aes(x=Condition, y=bids_tot), alpha=.3, position = position_jitterdodge()) +
+  geom_point(data=d, aes(x=Condition, y=bids_tot), alpha=.2, position = position_jitterdodge()) +
   xlab("Condition") + ylab("Total Bids for Joint Attention") +
@@
   geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
-  geom_point(data=d, aes(x=Condition, y=total_ja), alpha=.3, position = position_jitterdodge()) +
+  geom_point(data=d, aes(x=Condition, y=total_ja), alpha=.2, position = position_jitterdodge()) +
   xlab("Condition") + ylab("Total Episodes of Joint Attention") +
@@
   geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
-  geom_point(data=d, aes(x=Condition, y=pja), alpha=.3, position = position_jitterdodge()) +
+  geom_point(data=d, aes(x=Condition, y=pja), alpha=.2, position = position_jitterdodge()) +
   xlab("Condition") + ylab("Episodes of Passive Joint Attention") +
@@
   geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
-  geom_point(data=d, aes(x=Condition, y=cja), alpha=.3, position = position_jitterdodge()) +
+  geom_point(data=d, aes(x=Condition, y=cja), alpha=.2, position = position_jitterdodge()) +
   xlab("Condition") + ylab("Episodes of Coordinated Joint Attention")  +
@@
 ```{r, e2-lexdiv-regressions, echo=F, include=F}
+# preregistered analyses:
+# The number of parent bids for joint attention, the number of episodes of joint attention, the number of word tokens produced by parents, and the lexical diversity of parent language output (word types/word tokens).
+# Mixed-effects linear regressions predicting the dependent variables with condition (video scaffolding vs.
+control) and age in months as fixed effects and participant and specific video as random effects.
+# DV ~ age * condition + (1 | participant) + (1 | video)
+# Lab standard operating procedures will be used for random effects pruning in case of non-convergence.
+# We will interpret condition main effects as well as age * condition interactions (positive or negative) as evidence for behavior changes caused by video scaffolding. 
+# Because of the larger number of coefficients of interest (4 models x 2 coefficients), we will adopt an alpha level of .005 for statistical significance and will report alpha between .05 and .005 as suggestive.
+# “secondary analyses"
+# We will analyze the proportion of coordinated vs. passive joint attention separately using the same model specification.
+
+# Notes: 
+# - including (1|sid) never works: "Error: number of levels of each grouping factor must be < number of observations", so we back off to (1|video)
 # Predicting lexical diversity based on experimental condition. 
 modTTR <- lmer(TTR ~ age * condition + (1 | video), data=lmer_data) 
-summary(modTTR) # condition beta=-.09  t(8.7) = 3.06 p=.01
-e2TTR <- get_lmer_reporting_values(modTTR)
+summary(modTTR) # condition beta=-.09  t(8.7) = 3.06 p=.0141
+e2TTR <- get_lmer_reporting_values(modTTR) # here, the extracted pval = .003
 
@@
 
-We fit a mixed-effects linear regression predicting TTR as a function of age (scaled and 0-centered) and condition with an interaction term, and with random intercepts per video using lme4 [@lme4].
-There was significantly lower TTR in the Video condition (mean: 0.38) than in the Control condition (mean: 0.47, $\beta=`r e2TTR["conditionexp","beta"]`$, t(8.7) = `r e2TTR["conditionexp","zval"]`, *p*=.01).
+We fit a mixed-effects linear regression predicting TTR as a function of age (0-centered) and condition with an interaction term, and with random intercepts per video using lme4 [@lme4].
+There was suggestively lower TTR in the Video condition (mean: 0.38) than in the Control condition (mean: 0.47, $\beta=`r e2TTR["conditionexp","beta"]`$, t(8.7) = `r e2TTR["conditionexp","zval"]`, *p*=.01).
 There was no significant effect of age, nor a significant interaction.
 The preregistered regression of 
-An exploratory similar mixed-effects linear regression instead predicting MTLD found no significant effects of age or condition.
+A similar but exploratory mixed-effects linear regression predicting MTLD found no significant effects of age or condition.
 Figure \ref{fig:e2lexdiv} shows the mean of each lexical diversity measure (TTR and MTLD) by condition.
@@
   geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
-  geom_point(data=d, aes(x=Condition, y=TTR), alpha=.3, position = position_jitterdodge()) +
+  geom_point(data=d, aes(x=Condition, y=TTR), alpha=.2, position = position_jitterdodge()) +
   xlab("Condition") + ylab("TTR") +
@@
 ```
-```{r, e2-effect-size, echo=F}
+
+```{r, e2-effect-size, echo=F, include=F}
 ttr_means <- d %>% group_by(Condition) %>%
@@
 d$Condition <- factor(d$condition, levels = c("con","exp"), labels = c("Control","Video"))
-e2ja = d
-e2ja$age = as.numeric(langcog::scale(e2ja$age, scale=FALSE)) # 0-centered but NOT scaled -- change text
+
+e2ja <- d %>% mutate(bids = bids_tot,
+                     age = as.numeric(langcog::scale(age, scale=FALSE)),
+                     pja_length = pja_length/1000,
+                     cja_length = cja_length/1000,
+                     total_lja = total_lja/1000)
 
@@
   geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
-  geom_point(data=d, aes(x=Condition, y=bids), alpha=.3, position = position_jitterdodge()) +
+  geom_point(data=e2ja, aes(x=Condition, y=bids), alpha=.2, position = position_jitterdodge()) +
   xlab("Condition") + ylab("Total Bids for Joint Attention") +
@@
   geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
-  geom_point(data=d, aes(x=Condition, y=total_ja), alpha=.3, position = position_jitterdodge()) +
+  geom_point(data=e2ja, aes(x=Condition, y=total_ja), alpha=.2, position = position_jitterdodge()) +
   xlab("Condition") + ylab("Total Episodes of Joint Attention") +
@@
   geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
-  geom_point(data=d, aes(x=Condition, y=cja), alpha=.3, position = position_jitterdodge()) +
+  geom_point(data=d, aes(x=Condition, y=cja), alpha=.2, position = position_jitterdodge()) +
   xlab("Condition") + ylab("Episodes of Coordinated Joint Attention") +

### 2019-07-08 parenting_obs_e2/joint_attention/parenting_obs_JA.Rmd
fixed rounded ages in Exp 2

--- 2019-02-27 parenting_obs_e2/joint_attention/parenting_obs_JA.Rmd
@@
 title: "Parenting Observational Study E2"
-author: "Emily, Vivian"
+author: "Emily, Vivian, George"
 date: "`r Sys.Date()`"
@@
 
-```{r}
+```{r echo=F}
 d.raw <- data.frame() 
@@
     group_by(sid)%>%
-    summarise(bids = sum(as.numeric(bid)))
+    summarise(bids_tot = sum(as.numeric(bid)))
 
@@
     group_by(sid)%>%
-    summarise(bids = sum(bid))
+    summarise(bids_tot = sum(bid))
 
@@
 d.raw_rel <- d.raw_rel%>%
-  mutate(bids_rel = bids, pja_rel = pja, cja_rel = cja, l_pja_rel = pja_length, l_cja_rel = cja_length)%>%
+  mutate(bids_rel = bids_tot, pja_rel = pja, cja_rel = cja, l_pja_rel = pja_length, l_cja_rel = cja_length)%>%
   select(sid, bids_rel, pja_rel, cja_rel, l_cja_rel, l_pja_rel)
@@
   left_join(d.raw)%>%
-  select(bids, bids_rel)
+  select(bids_tot, bids_rel)
 
@@
 ```{r, width=4, height=4}
+dem <- read.csv("../anonymized_demographics_parenting_obs_e2.csv", header=T)
+dem$age = as.numeric(as.character(dem$age))
+d$age = NULL
+d <- d %>% left_join(dem, by=c("sid" = "SID")) %>%
+  filter(age <= 2.0) # 1 kid exactly 2...
+
 save(d, file="Exp2_joint_attention_data.RData")
+
+d$condition <- factor(d$condition, levels = c("con", "exp"), labels = c("control", "video"))
+
 ms_bids <- d %>%
   group_by(condition) %>%
-  multi_boot_standard(col = "bids")
-
-ms_bids$condition <- factor(ms_bids$condition,
-levels = c("con", "exp"),
-labels = c("control", "video"))
+  multi_boot_standard(col = "bids_tot")
 
@@
              position = position_dodge(width = .9))+
-  xlab("Condition") + 
-  ylab("Total bids for Joint Attention") +
-  langcog::scale_colour_solarized()  +
-  ggthemes::theme_few() + 
-  theme(legend.position="none") 
+  xlab("Condition") + ylab("Total bids for Joint Attention") +
+  langcog::scale_colour_solarized() + ggthemes::theme_few() + theme(legend.position="none") 
 ```
@@
 
-ms_tja$Condition <- factor(ms_tja$condition,
-levels = c("con", "exp"),
-labels = c("control", "video"))
-
 ggplot(ms_tja, aes(x = condition, y = mean, fill = condition)) + 
@@
   ylab("Total episodes of Joint Attention") +
-  langcog::scale_colour_solarized()  +
-  ggthemes::theme_few() + 
+  langcog::scale_colour_solarized()  + ggthemes::theme_few() + 
   theme(legend.title = element_text(size=18), 
@@
 ms_bids <- d %>%
-  group_by(Condition, gender) %>%
+  group_by(condition, gender) %>%
   multi_boot_standard(col = "bids_tot")
 
-ggplot(ms_bids, aes(x = Condition, y = mean, fill=gender)) + 
+ggplot(ms_bids, aes(x = condition, y = mean, fill=gender)) + 
   geom_bar(stat="identity", position = "dodge") + 
@@
 ms_lpja <- d %>%
-  filter(!is.na(Condition))%>%
-  group_by(Condition, gender) %>%
+  filter(!is.na(condition))%>%
+  group_by(condition, gender) %>%
   multi_boot_standard(col = "pja_length")
 
-ggplot(ms_lpja, aes(x = Condition, y = mean, fill=gender)) + 
+ggplot(ms_lpja, aes(x = condition, y = mean, fill=gender)) + 
   geom_bar(stat="identity", position = "dodge") + 
@@
 ms_lcja <- d %>%
-  filter(!is.na(Condition))%>%
-  group_by(Condition, gender) %>%
+  filter(!is.na(condition))%>%
+  group_by(condition, gender) %>%
   multi_boot_standard(col = "cja_length")
 
-ggplot(ms_lcja, aes(x = Condition, y = mean, fill=gender)) + 
+ggplot(ms_lcja, aes(x = condition, y = mean, fill=gender)) + 
   geom_bar(stat="identity", position = "dodge") + 
@@
 # total bids
+d$age_group = ifelse(d$age<1, "6-12", ifelse(d$age<1.5, "12-18", "18-24"))
+d$age_group <- factor(d$age_group , levels = c("6-12","12-18", "18-24"))
+
 ms_bids <- d %>%
-  group_by(Condition, age_group) %>%
+  group_by(condition, age_group) %>%
   multi_boot_standard(col = "bids_tot")
 
-ms_bids$age_group <- factor(ms_bids$age_group , levels = c("6","12", "18"))
-
-ggplot(ms_bids, aes(x = Condition, y = mean, fill=age_group)) + 
+ggplot(ms_bids, aes(x = condition, y = mean, fill=age_group)) + 
   geom_bar(stat="identity", position= "dodge") + 
@@
 ms_lpja <- d %>%
-  filter(!is.na(Condition))%>%
-  group_by(Condition, age_group) %>%
+  filter(!is.na(condition))%>%
+  group_by(condition, age_group) %>%
   multi_boot_standard(col = "pja_length")
 
-ms_lpja$age_group <- factor(ms_lpja$age_group , levels = c("6","12", "18"))
-
-ggplot(ms_lpja, aes(x = Condition, y = mean, fill = age_group)) + 
+ggplot(ms_lpja, aes(x = condition, y = mean, fill = age_group)) + 
   geom_bar(stat="identity", position = "dodge") + 
@@
 ms_lcja <- d %>%
-  filter(!is.na(Condition))%>%
-  group_by(Condition, age_group) %>%
+  filter(!is.na(condition))%>%
+  group_by(condition, age_group) %>%
   multi_boot_standard(col = "cja_length")
 
-ms_lcja$age_group <- factor(ms_lcja$age_group , levels = c("6","12", "18"))
-
-ggplot(ms_lcja, aes(x = Condition, y = mean, fill = age_group)) + 
+ggplot(ms_lcja, aes(x = condition, y = mean, fill = age_group)) + 
   geom_bar(stat="identity", position = "dodge") + 
@@
 
-###Parenting attitudes and education
+# Analysis
 
-Do PAQ scores predict the number of bids for joint attention by parents?
-```{r}
-d_plot <- d %>%
-  gather("subscale","score", AA:RR)
-
-ggplot(d_plot, aes(x = score, y = bids_tot, col = subscale)) +
-  geom_jitter() + 
-  xlim(0,6) +
-  geom_smooth(method="lm", se=FALSE)  + 
-  facet_wrap(~Condition)+
-  ggthemes::theme_few() +
-  langcog::scale_colour_solarized() 
-```
-
-Does parent education predict the number of bids for joint attention by parents?
-```{r}
-d_plot <- d %>%
-  gather("subscale","score", AA:RR)
-
-ggplot(d_plot, aes(x = parent_ed, y = bids_tot)) +
-  geom_jitter() + 
-  xlim(0,6) +
-  geom_smooth(method="lm", se=FALSE)  + 
-  facet_wrap(~Condition)+
-  ggthemes::theme_few() +
-  langcog::scale_colour_solarized() 
-```
-
-#Analysis
-
-Is the duration of joint attention correlated with age in months?
+Is the duration of joint attention correlated with age?
 
@@
 cormat <- d %>%
-  select(age_months, pja_length, cja_length, total_lja)
+  select(age, pja_length, cja_length, total_lja)
 rcorr(as.matrix(cormat))
-
 ```
@@
 lmer_data <- d %>% 
-  filter(!is.na(AA), !is.na(EL), !is.na(RR))%>%
-  mutate(Condition = factor(Condition), 
+  mutate(Condition = factor(condition), 
          bids_tot = as.numeric(bids_tot),
-         EL = as.numeric(langcog::scale(EL, scale=FALSE)),
-         AA = as.numeric(langcog::scale(AA, scale=FALSE)),
-         RR = as.numeric(langcog::scale(RR, scale=FALSE)),
          age = as.numeric(langcog::scale(age, scale=FALSE)),
          gender = as.factor(gender),
-         Video = as.factor(Video))
+         Video = as.factor(video))
 ```
@@
 ```{r}
-maximal_mod <- lmer(bids_tot ~ Condition *  EL  + Condition * AA + Condition * RR + age + gender + parent_ed +
-                           (1| Video), 
-                         data = lmer_data)
+lmer_data$parent_ed = as.numeric(as.character(lmer_data$parent_ed))
+maximal_mod <- lmer(bids_tot ~ Condition * age + (1| Video), data = lmer_data)
 summary(maximal_mod)
@@
 ```{r}
-maximal_mod <- lmer(cja ~ Condition *  EL  + Condition * AA + Condition * RR  + age + gender + parent_ed +
-                           (1| Video), 
-                         data = lmer_data)
+maximal_mod <- lmer(cja ~ Condition * age + (1| Video), data = lmer_data)
 summary(maximal_mod)
@@
 ```{r}
-maximal_mod <- lmer(pja ~ Condition *  EL  + Condition * AA + Condition * RR  + age + gender + parent_ed +
-                           (1| Video), 
-                         data = lmer_data)
+maximal_mod <- lmer(pja ~ Condition * age + (1| Video), data = lmer_data)
 summary(maximal_mod)
@@
 ```{r}
-maximal_mod <- lmer(pja_length ~ Condition *  EL  + Condition * AA + Condition * RR  + age + gender + parent_ed +
-                           (1| Video), 
-                         data = lmer_data)
+maximal_mod <- lmer(pja_length ~ Condition * age + (1| Video), data = lmer_data)
 summary(maximal_mod)
@@
 ```{r}
-maximal_mod <- lmer(cja_length ~ Condition *  EL  + Condition * AA + Condition * RR  + age + gender + parent_ed +
-                           (1| Video), 
-                         data = lmer_data)
+maximal_mod <- lmer(cja_length ~ Condition * age + (1| Video), data = lmer_data)
 summary(maximal_mod)
@@
 
-#Conclusions
+# Conclusions
 

### 2019-07-08 paper/cogsci2019/cogsci2019.Rmd
updated LD Exp 2 analysis

@@
 
-We fit a mixed-effects linear regression predicting TTR as a function of condition, age (scaled and 0-centered), gender, and parent's education level with a random intercept per video using lme4 [@lme4].
+We fit a mixed-effects linear regression predicting TTR as a function of condition, age (0-centered), gender, and parent's education level with a random intercept per video using lme4 [@lme4]. 
 There was significantly lower TTR in the Video condition (mean: `r round(subset(e1_lexdiv, condition=='exp')$TTR, 2)`) than in the Control condition (mean: `r round(subset(e1_lexdiv, condition=='con')$TTR, 2)`, $\beta=$`r e1TTR["conditionexp","beta"]`, t(52.4) = `r e1TTR["conditionexp","zval"]`, *p*<.001).

### 2019-07-08 parenting_obs_e2/Lexical_Diversity_Analysis.Rmd
updated LD Exp 2 analysis

@@
 d <- d %>% left_join(dem, by=c("sid" = "SID")) %>%
-  filter(age <= 2.0)
+  filter(age <= 2.0 & age>=1.0)
 
@@
 
-#Plots
+# Plots
 
-##TTR
+## TTR
+
 ```{r echo=FALSE}
@@
 ```
+
 ## MTLD
+
 ```{r echo=FALSE}
@@
 ```
-## HD-D
-```{r echo=FALSE}
-ms_lex <- d %>%
-  group_by(condition) %>%
-  multi_boot_standard(col = "HDD")
 
-lex_means <- d%>%
-  group_by(condition)%>%
-  summarise(mean = mean(HDD))
+## Word Tokens
 
-lex_sds <- d%>%
-  group_by(condition)%>%
-  summarise(sd = sd(HDD))
-
-ms_lex$condition <- factor(ms_lex$condition,
-levels = c("con", "exp"),
-labels = c("Control", "Video"))
-
-ggplot(ms_lex, aes(x = condition, y = mean, fill = condition)) + 
-  geom_bar(stat="identity") + 
-  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
-             position = position_dodge(width = .9))+
-  xlab("Condition") + 
-  ylab("HD-D") +
-  langcog::scale_colour_solarized()  +
-  ggthemes::theme_few()
-ggsave(file="figs/e2_HDD.pdf", width=3, height=3)
-```
-##Word Tokens
 ```{r echo=FALSE}
@@
 
-##Word Types
+## Word Types
+
 ```{r echo=FALSE}
@@
 
-##Sentence Length
+## Sentence Length
+
 ```{r echo=FALSE}
@@
 
-###Sentence Length by videos
+### Sentence Length by Video
 
@@
 
-###Sentence Length by age
+### Sentence Length by age
 (Maybe do a scatterplot with continuous age)
@@
 ```{r echo=FALSE}
-ms_length <- d %>%
-  group_by(age) %>%
-  multi_boot_standard(col = "len_sentence")
-
-ms_length$age <- factor(ms_length$age,
-levels = c("1", "2"),
-labels = c("12-18", "18-24"))
-
-ggplot(ms_length, aes(x = age, y = mean, fill = age)) +
-  geom_bar(stat="identity") + 
-  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
-             position = position_dodge(width = .9))+
-  xlab("Age (months)") + 
-  ylab("Average Sentence Length") +
+ac <- d %>% filter(!is.na(age) & !is.na(condition))
+ggplot(ac, aes(x = age, y = len_sentence, group=condition, colour = condition)) +
+  geom_point(alpha=.7) + geom_smooth(method='lm') + 
+  xlab("Age (years)") + ylab("Mean Sentence Length") +
   langcog::scale_colour_solarized() +
-  ggthemes::theme_few() + 
-  theme(legend.title = element_text(size=18), 
-        legend.text = element_text(size=16), 
-        axis.text.x  = element_text(vjust=0.5, size=16),
-        axis.title.x = element_text(size=18), 
-        axis.text.y  = element_text(vjust=0.5, size=16),
-        axis.title.y = element_text(size=18))
+  ggthemes::theme_few() 
 ```
@@
 
-#Conclusions
-In McCarthy-Jarvis2010 paper, MTLD and HD-D has a correlation of r = .800; 
-MTLD and TTR r =.322;
-HD-D and TTR r = -.051 (N = 1584). 
-In our results, MTLD and HD-D have the highest correlation (r = .714). Meanwhile, MTLD and TTR has r = .270, a bit lower than what M-J2010 reported. TTR and HDD are also modestly correlated (r = .426)
+# Conclusions
+
+In McCarthy-Jarvis2010 paper, MTLD and HD-D has a correlation of r = .800; MTLD and TTR r =.322; HD-D and TTR r = -.051 (N = 1584). 
+In our results, MTLD and HD-D have the highest correlation (r = .710).
+Meanwhile, MTLD and TTR has r = .287, a bit lower than what M-J2010 reported.
+TTR and HDD are also modestly correlated (r = .444).
 

### 2019-07-17 paper/cogsci2019/cogsci2019.Rmd
wrapping up results

@@
   CA \\\\ ^{3} Gallaudet University, Washington, D.C. }\n"
-header-includes:
-   - \usepackage{float}
 bibliography: library.bib
@@
   pdf_document: default
+  word_document: default
   html_document:
@@
 final-submission: \cogscifinalcopy
+header-includes: \usepackage{float}
 keywords: "digital parenting advice; joint attention; lexical diversity; guided play;
@@
 The videos were designed to show activities to parents that they could perform with their child in order to foster cognitive and physical development, and were targeted to the child's age and level of development.
-In each video, an adult and child perform the activity while a narrator explains the activity and its purpose. 
+In each video, an adult and child perform the activity (e.g., sorting toys according to size) while a narrator explains the activity and its purpose. 
 We selected two videos for each of three age groups in our sample (6-11.9 months, 12-17.9 months, 18-23.94 months). 
@@
 bmodMTLD <- stan_glmer(MTLD ~ condition + age + gender + parent_ed + (1|video), data=lmer_data)
-summary(bmodMTLD) # condition mean=-8.7 sd=3.3 2.5%=-15.1 97.5%=-20
+summary(bmodMTLD) # condition mean=-8.6 sd=3.2 95% CI = [-14.9,-2.3]
 
@@
 bmod_types <- stan_glmer(types ~ condition*EL + condition*AA + condition*RR  + age + gender + parent_ed + (1|video), data=lmer_data)
-summary(bmod_types)
+summary(bmod_types) # nothing
 
@@
 We also conducted similar regressions predicting the number of word tokens and types, finding only a significant effect of condition on the number of word tokens ($\beta= `r e1tokens["conditionexp","beta"]`$, t(40.4)=`r e1tokens["conditionexp","zval"]`, *p*<.05), with parents using more words in the Video condition (mean: `r round(subset(e1_lexdiv, condition=='exp')$tokens, 0)`, bootstrapped 95% confidence intervals (CI): [`r round(subset(ms_tok, Condition=="Video")$ci_lower, 0)`,`r round(subset(ms_tok, Condition=="Video")$ci_upper, 0)`]) than in the Control condition (mean: `r round(subset(e1_lexdiv, condition=='con')$tokens, 0)`, bootstrapped 95% CI: [`r round(subset(ms_tok, Condition=="Control")$ci_lower, 0)`,`r round(subset(ms_tok, Condition=="Control")$ci_upper, 0)`]).
+The means of the lexical diversity measures are reported in Table \ref{e1tab}.
 
-```{r tab1, echo=FALSE}
+```{r e1tab, echo=FALSE}
 e1 <- d %>% group_by(Condition) %>%
@@
 names(e1) = c("Condition","TTR (M)", "(sd)", "MTLD (M)", "(sd)", "Types (M)", "(sd)", "Tokens (M)", "(sd)")
-kable(e1, digits=2, caption="Lexical diversity measures in Experiment 1.")
+kable(e1, digits=2, caption="Lexical diversity measures in Experiment 1.", label="e1tab")
 ```
@@
   xlab("Condition") + ylab("Type/Token Ratio (TTR)") +
-  langcog::scale_colour_solarized() + ggthemes::theme_few() +
+  langcog::scale_fill_solarized() + ggthemes::theme_few() +
   theme(legend.position="none")
@@
   xlab("Condition") + ylab("MTLD") +
-  langcog::scale_colour_solarized() + ggthemes::theme_few() + 
+  langcog::scale_fill_solarized() + ggthemes::theme_few() + 
   theme(legend.position="none")
@@
   xlab("Condition") + ylab("Total Number of Word Tokens") +
-  langcog::scale_colour_solarized() + ggthemes::theme_few() +
+  langcog::scale_fill_solarized() + ggthemes::theme_few() +
   theme(legend.position="none")
@@
   xlab("Condition") + ylab("Total Number of Word Types") +
-  langcog::scale_colour_solarized() + ggthemes::theme_few() +
+  langcog::scale_fill_solarized() + ggthemes::theme_few() +
   theme(legend.position="none")
@@
 pja_mod <- lmer(paste("pja", model_string), data = lmer_data)
-summary(pja_mod) # marginal RR, beta=-1.07 p=.07, condition*RR beta=1.83 p<.05
+summary(pja_mod) # marginal RR, beta=-1.07 p=.07, condition*RR beta=1.83 p<.05 t(41.5)=2.22
 e1pja = get_lmer_reporting_values(pja_mod)
@@
   xlab("Condition") + ylab("Total Bids for Joint Attention") +
-  langcog::scale_colour_solarized() + ggthemes::theme_few() + 
+  langcog::scale_fill_solarized() + ggthemes::theme_few() + 
   theme(legend.position="none")
@@
   xlab("Condition") + ylab("Total Episodes of Joint Attention") +
-  langcog::scale_colour_solarized() + ggthemes::theme_few() + 
+  langcog::scale_fill_solarized() + ggthemes::theme_few() + 
   theme(legend.position="none")
@@
   xlab("Condition") + ylab("Episodes of Passive Joint Attention") +
-  langcog::scale_colour_solarized() + ggthemes::theme_few() + theme(legend.position="none")
+  langcog::scale_fill_solarized() + ggthemes::theme_few() + theme(legend.position="none")
 
@@
   xlab("Condition") + ylab("Episodes of Coordinated Joint Attention")  +
-  langcog::scale_colour_solarized() + ggthemes::theme_few() + theme(legend.position="none")
+  langcog::scale_fill_solarized() + ggthemes::theme_few() + theme(legend.position="none")
 
@@
 e2_parent_ed = table(d$parent_ed)
+e2_12to18 = nrow(subset(d, age<1.5))
+e2_18to24 = nrow(subset(d, age>=1.5))
 ```
@@
 ### Participants. 
-`r nrow(d)` infants (F = `r e2_gender['F']`, M = `r e2_gender['M']`) aged 12-24 months (42 12-17.9 month-olds, 42 18-24 month-olds) and their parents participated in the same museum as Experiment 1. 
+`r nrow(d)` infants (F = `r e2_gender['F']`, M = `r e2_gender['M']`) aged 12-24 months (`r e2_12to18` 12-17.9 month-olds, `r e2_18to24` 18-24 month-olds) and their parents participated in the same museum as Experiment 1.
 We included infants who were exposed to English at least 75 percent of the time or who were exposed less but whose participating parent reported that they primarily speak English with their child at home.
@@
 
-Parents' child-directed speech was transcribed and processed according to the same procedure used in Experiment 1, and the preregistered regressions predicting TTR and number of tokens were carried out.
+Parents' child-directed speech was transcribed and processed, and bids and episodes of joint attention were coded according to the same procedure used in Experiment 1.
+We first report reregistered regressions predicting TTR and number of tokens, as well as an exploratory regression predicting MTLD.
+We then turn to preregistered regressions of parental bids for joint attention and the total number of JA episodes.
+As noted in the preregistration, we adopt an alpha level of .005 for statistical significance and will report alphas between .05 and .005 as suggestive.
 
@@
 # The number of parent bids for joint attention, the number of episodes of joint attention, the number of word tokens produced by parents, and the lexical diversity of parent language output (word types/word tokens).
+# 1) bids, 2) total JA eps, 3) # tokens 4) TTR -- alpha level = .005
 # Mixed-effects linear regressions predicting the dependent variables with condition (video scaffolding vs.
@@
 modTTR <- lmer(TTR ~ age * condition + (1 | video), data=lmer_data) 
-summary(modTTR) # condition beta=-.09  t(8.7) = 3.06 p=.0141
+summary(modTTR) # condition beta=-.09  t(8.6) = 3.33 p=.009 (suggestive)
 e2TTR <- get_lmer_reporting_values(modTTR) # here, the extracted pval = .003
-
-modMTLD <- lmer(MTLD ~ age * condition + (1 | video), data=lmer_data)
-summary(modMTLD) # NA
 
@@
 summary(tokens_mod) # NA
+
+modMTLD <- lmer(MTLD ~ age * condition + (1 | video), data=lmer_data)
+summary(modMTLD) # NA
 
@@
 We fit a mixed-effects linear regression predicting TTR as a function of age (0-centered) and condition with an interaction term, and with random intercepts per video using lme4 [@lme4].
-There was suggestively lower TTR in the Video condition (mean: 0.38) than in the Control condition (mean: 0.47, $\beta=`r e2TTR["conditionexp","beta"]`$, t(8.7) = `r e2TTR["conditionexp","zval"]`, *p*=.01).
+There was suggestively lower TTR in the Video condition (mean: 0.38) than in the Control condition (mean: 0.47, $\beta=`r e2TTR["conditionexp","beta"]`$, t(8.6) = `r e2TTR["conditionexp","zval"]`, *p*=.009).
 There was no significant effect of age, nor a significant interaction.
-The preregistered regression of 
-A similar but exploratory mixed-effects linear regression predicting MTLD found no significant effects of age or condition.
+The preregistered regression predicting the number of tokens used by parents found no significant effects. 
+An exploratory mixed-effects linear regression predicting MTLD found no significant effects of age or condition.
 Figure \ref{fig:e2lexdiv} shows the mean of each lexical diversity measure (TTR and MTLD) by condition.
@@
 names(e2) = c("Condition","TTR (M)", "(sd)", "MTLD (M)", "(sd)", "Types (M)", "(sd)", "Tokens (M)", "(sd)")
-kable(e2, digits=2, caption="Lexical diversity measures in Experiment 2.")
+kable(e2, digits=2, caption="Lexical diversity measures in Experiment 2.", label="e2tab")
 ```
@@
   xlab("Condition") + ylab("TTR") +
-  langcog::scale_colour_solarized() + ggthemes::theme_few() +
+  langcog::scale_fill_solarized() + ggthemes::theme_few() +
   theme(legend.position="none")
@@
   xlab("Condition") + ylab("MTLD") +
-  langcog::scale_colour_solarized() + ggthemes::theme_few() +
+  langcog::scale_fill_solarized() + ggthemes::theme_few() +
   theme(legend.position="none")
@@
 bids_mod <- lmer(bids ~ age * Condition + (1 | video), data = e2ja)
-summary(bids_mod) # singular fit, convergence code: 0
+summary(bids_mod) # singular fit, convergence code: 0 condition beta=3.11, t(80) = 3.52 p<.001
 e2bids <- get_lmer_reporting_values(bids_mod)
-# Condition est = 3.25 t(79) = 3.65 p<.001
 bids_bmod <- stan_glmer(bids ~ age * Condition + (1|video), data=e2ja)
-summary(bids_bmod) # significant effect of condition! mean=3.2, 95%CI = [1.2, 5.2]
+summary(bids_bmod) # significant effect of condition! mean=3.1, 95%CI = [1.1, 5.0]
 
@@
 #                    Estimate Std. Error      df t value  Pr(>|t|) 
-# age                 -4.6051     1.3927 79.0000  -3.306  0.00142 ** 
-# ConditionVideo       1.5253     0.5626 79.0000   2.711  0.00822 ** 
-# age:ConditionVideo   5.5193     2.1893 79.0000   2.521  0.01371 *
+# (Intercept)          7.2912     0.3898 80.0000  18.704  < 2e-16 ***
+# age                 -5.2687     1.5122 80.0000  -3.484 0.000804 ***
+# ConditionVideo       1.4893     0.5513 80.0000   2.701 0.008428 ** 
+# age:ConditionVideo   5.9189     2.2721 80.0000   2.605 0.010950 *
 
 tja_bmod <- stan_glmer(total_ja ~ age * Condition + (1|video), data=e2ja)
-summary(tja_bmod) # age n.s., sig effect of condition: mean=3.2 95%CI = [1.1, 5.2]
+summary(tja_bmod) # total episodes of joint attention -- age, age*condition, condition
 #                                        mean    sd     2.5%   25%    50%    75%    97.5%
-# (Intercept)                             7.3    0.5    6.3    6.9    7.2    7.6    8.2 
-# age                                    -4.3    1.5   -7.2   -5.3   -4.3   -3.3   -1.3 
-# ConditionVideo                          1.5    0.7    0.2    1.1    1.5    1.9    2.9
+# (Intercept)                             7.3    0.4    6.4    7.0    7.3    7.6    8.2 
+# age                                    -5.0    1.7   -8.2   -6.1   -5.0   -3.9   -1.6 
+# ConditionVideo                          1.5    0.6    0.3    1.1    1.5    1.9    2.8 
+# age:ConditionVideo                      5.6    2.5    0.7    3.9    5.7    7.4   10.5
 
@@
 cja_mod <- lmer(cja ~ age * Condition + (1 | video), data = e2ja)
-summary(cja_mod) #  Condition: t(79) = 2.47 beta=1.33 p=.02; age*Condition beta=4.92 t(79) = 2.35 p=.02
+summary(cja_mod) #  Condition: t(80) = 2.47 beta=1.37 p=.01; age*Condition beta=5.24 t(80) = 2.19 p=.02
 # also singular fit, convergence code: 0 - check Bayesian regression
@@
 pja_mod <- lmer(pja ~ age * Condition + (1 | video), data = e2ja)
-summary(pja_mod) # age beta=-2.32 t(26.6) = 2.23 p<.05
+summary(pja_mod) # age beta=-2.88 t(13.4) = 2.53 p=.02
 
@@
 pja_time_mod <- lmer(pja_length ~ age * Condition + (1 | video), data = e2ja)
-summary(pja_time_mod) # singular - convergence code: 0, age beta=-15512 t(79) = 2.40 p<.05
+summary(pja_time_mod) # singular - convergence code: 0, age beta=-18.89 t(80) = 2.72 p=.008
 pjat_bmod <- stan_glmer(pja_length ~ age * Condition + (1|video), data=e2ja)
-summary(pjat_bmod)
-#                                        mean       sd         2.5%       25%        50%        75%        97.5%   
-#(Intercept)                             11247.4     2193.1     6977.7     9822.1    11239.1    12655.2    15736.7
-#age                                    -13924.2     7097.9   -27467.6   -18661.5   -14163.6    -9341.5      722.4
-#ConditionVideo                            824.8     3098.5    -5399.6    -1190.0      846.8     2877.5     6867.3
-#age:ConditionVideo                        108.3    11738.0   -23881.5    -7171.3      411.3     7778.3    22058.5
+summary(pjat_bmod) # age: est: -17.9 95% CI = [-33.1,-2.2]
 
@@
 cja_time_mod <- lmer(cja_length ~ age * condition + (1 | video), data = e2ja)
-summary(cja_time_mod) # singular - convergence code: 0, marginal age: beta=31757 t(79) = 1.81 p=.07
+summary(cja_time_mod) # singular - convergence code: 0, marginal age: beta=37.35 t(80) = 1.95 p=.05
 cjat_bmod <- stan_glmer(cja_length ~ age * Condition + (1|video), data=e2ja)
-summary(cjat_bmod)
-#                                           mean        sd          2.5%        25%         50%         75%      
-#(Intercept)                              73053.4      5611.1     62252.3     69338.3     73049.6     76773.7
-#age                                      28879.1     19079.4     -8533.5     16385.2     29112.3     41487.9
-#ConditionVideo                            5745.4      7874.5     -9994.6       535.3      5725.3     11163.4
-#age:ConditionVideo                       45792.3     30918.9    -14154.8     25281.7     45101.1     66074.2
+summary(cjat_bmod) # age: est: 35.3 95% CI = [-6.1,77.4] NOT SIGNIFICANT
 
@@
 
-As specified in our preregistration, we fit five mixed-effects linear regressions predicting the following JA variables: parental bids, the number of episodes of coordinated JA and passive JA, and the total duration of coordinated and passive JA.
-These JA variables were predicted as a function of fixed effects of condition, age (0-centered), with random intercepts per video.
-There were significantly more bids for JA in the Video condition (mean: `r round(subset(e2_bids, Condition=="Video")$mean,2)`, bootstrapped 95% CI: `r round(subset(e2_bids, Condition=="Video")$ci_lower,2)`, `r round(subset(e2_bids, Condition=="Video")$ci_upper,2)`) than in the Control condition (mean: `r round(subset(e2_bids, Condition=="Control")$mean,2)`, 95% CI: `r round(subset(e2_bids, Condition=="Control")$ci_lower,2)`, `r round(subset(e2_bids, Condition=="Control")$ci_upper,2)`, $\beta=`r e2bids["ConditionVideo","beta"]`$, t(79) = `r e2bids["ConditionVideo","zval"]`, *p*<.001).
-There were no other significant effects.
-There were no significant effects on the number or total duration of coordinated JA episodes, nor on the total duration of passive JA episodes.
+For the preregistered analyses, we fit mixed-effects linear regressions predicting the number of parental bids for joint attention and the total number of episodes of JA. 
+These JA variables were predicted as a function of fixed effects of condition, age (0-centered), and their interaction, with random intercepts per video.
+Parents made significantly more bids for JA in the Video condition (mean: `r round(subset(e2_bids, Condition=="Video")$mean,2)`, bootstrapped 95% CI: `r round(subset(e2_bids, Condition=="Video")$ci_lower,2)`, `r round(subset(e2_bids, Condition=="Video")$ci_upper,2)`) than in the Control condition (mean: `r round(subset(e2_bids, Condition=="Control")$mean,2)`, 95% CI: `r round(subset(e2_bids, Condition=="Control")$ci_lower,2)`, `r round(subset(e2_bids, Condition=="Control")$ci_upper,2)`, $\beta=`r e2bids["ConditionVideo","beta"]`$, t(79) = `r e2bids["ConditionVideo","zval"]`, *p*<.001).
+There were no other significant effects on parental bids for JA.
 
-Figure \ref{fig:e2ja} shows the mean number of bids and episodes of JA by condition.
+There were significant effects of condition, age, and
 
-```{r fig:e2ja, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.5, fig.height=3.0, set.cap.width=T, num.cols.cap=1, fig.cap = "\\label{fig:e2ja} Mean number of bids and episodes of JA by condition in Experiment 2."}
+Figure \ref{fig:e2ja} shows the mean number of parental bids for JA by condition (left), along with total episodes of JA by age and condition (right).
+
+Additional exploratory regressions with a similar structure were carried out on number and duration of coordinated and passive JA episodes.
+
+```{r fig:e2ja, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=6, fig.height=3.0, set.cap.width=T, num.cols.cap=1, fig.cap = "\\label{fig:e2ja} Mean number of bids for JA by condition (left) and total episodes of JA by age and condition (right) in Experiment 2."}
 
@@
   xlab("Condition") + ylab("Total Episodes of Joint Attention") +
-  langcog::scale_colour_solarized() + ggthemes::theme_few() + 
+  langcog::scale_fill_solarized() + ggthemes::theme_few() + 
   theme(legend.position="none")
 
-multiplot(e2bids, e2tja, cols=2)
+e2tja_age = ggplot(d, aes(x = age, y = total_ja, group=Condition, colour = Condition)) +
+  geom_point(alpha=.7) + geom_smooth(method='lm') + 
+  xlab("Age (years)") + ylab("Total Episodes of Joint Attention") +
+  langcog::scale_colour_solarized() +
+  ggthemes::theme_few()
+
+multiplot(e2bids, e2tja_age, cols=4, layout=matrix(c(1,2,2,2), nrow=1))
 ```
@@
   geom_point(data=d, aes(x=Condition, y=cja), alpha=.2, position = position_jitterdodge()) +
-  xlab("Condition") + ylab("Episodes of Coordinated Joint Attention") +
-  langcog::scale_colour_solarized() + ggthemes::theme_few() + theme(legend.position="none")
+  xlab("Condition") + ylab("Episodes of Coordinated JA") +
+  langcog::scale_fill_solarized() + ggthemes::theme_few() + theme(legend.position="none")
 
@@
 
-There was a marginal effect of condition on total bids for joint attention. 
+There was an effect on total bids for joint attention. 
 Parents in the experimental condition (i.e., those who saw a video demonstrating an activity) made a greater number of bids for joint attention with their child.

### 2019-07-21 paper/cogsci2019/cogsci2019.Rmd
done with Exp 2 results

@@
 get_lmer_reporting_values <- function(lmer.fit, digits=2) {
+  sm <- summary(lmer.fit)
   Vcov <- vcov(lmer.fit, useScale = FALSE)
@@
   zval <- round(beta / se, digits)
-  pval <- round(2 * pnorm(abs(zval), lower.tail = FALSE), 4)
-  # not sure how to pull estimated degrees of freedom...
-  return(cbind(beta, se, zval, pval))
+  pvalEst <- round(2 * pnorm(abs(zval), lower.tail = FALSE), 3)
+  pval <- round(sm$coefficients[,"Pr(>|t|)"], 3)
+  tval <- abs(round(sm$coefficients[,"t value"], digits))
+  df <- round(sm$coefficients[,"df"], 1)
+  return(cbind(beta, se, zval, tval, pval, pvalEst, df))
 }
+
 require("lmerTest")
@@
 We fit a mixed-effects linear regression predicting TTR as a function of condition, age (0-centered), gender, and parent's education level with a random intercept per video using lme4 [@lme4]. 
-There was significantly lower TTR in the Video condition (mean: `r round(subset(e1_lexdiv, condition=='exp')$TTR, 2)`) than in the Control condition (mean: `r round(subset(e1_lexdiv, condition=='con')$TTR, 2)`, $\beta=$`r e1TTR["conditionexp","beta"]`, t(52.4) = `r e1TTR["conditionexp","zval"]`, *p*<.001).
+There was significantly lower TTR in the Video condition (mean: `r round(subset(e1_lexdiv, condition=='exp')$TTR, 2)`) than in the Control condition (mean: `r round(subset(e1_lexdiv, condition=='con')$TTR, 2)`, $\beta=$`r e1TTR["conditionexp","beta"]`, t(52.4) = `r e1TTR["conditionexp","tval"]`, *p*<.001).
 There were no significant effects of age, gender, or parent's level of education.
-A similar mixed-effects linear regression instead predicting MTLD also found significantly lower lexical diversity in the Video condition (mean MTLD: `r round(subset(e1_lexdiv, condition=='exp')$MTLD, 2)`) than in the Control condition (mean: `r round(subset(e1_lexdiv, condition=='exp')$TTR, 2)`, $\beta=$`r e1MTLD["conditionexp","beta"]`, t(55) = `r e1MTLD["conditionexp","zval"]`, *p*=.001), with no other significant effects.
+A similar mixed-effects linear regression instead predicting MTLD also found significantly lower lexical diversity in the Video condition (mean MTLD: `r round(subset(e1_lexdiv, condition=='exp')$MTLD, 2)`) than in the Control condition (mean: `r round(subset(e1_lexdiv, condition=='exp')$TTR, 2)`, $\beta=$`r e1MTLD["conditionexp","beta"]`, t(55) = `r e1MTLD["conditionexp","tval"]`, *p*=.001), with no other significant effects.
 Figure \ref{fig:e1lex_div} shows the mean of each lexical diversity measure (TTR and MTLD) by condition.
@@
 
-We also conducted similar regressions predicting the number of word tokens and types, finding only a significant effect of condition on the number of word tokens ($\beta= `r e1tokens["conditionexp","beta"]`$, t(40.4)=`r e1tokens["conditionexp","zval"]`, *p*<.05), with parents using more words in the Video condition (mean: `r round(subset(e1_lexdiv, condition=='exp')$tokens, 0)`, bootstrapped 95% confidence intervals (CI): [`r round(subset(ms_tok, Condition=="Video")$ci_lower, 0)`,`r round(subset(ms_tok, Condition=="Video")$ci_upper, 0)`]) than in the Control condition (mean: `r round(subset(e1_lexdiv, condition=='con')$tokens, 0)`, bootstrapped 95% CI: [`r round(subset(ms_tok, Condition=="Control")$ci_lower, 0)`,`r round(subset(ms_tok, Condition=="Control")$ci_upper, 0)`]).
+We also conducted similar regressions predicting the number of word tokens and types, finding only a significant effect of condition on the number of word tokens ($\beta= `r e1tokens["conditionexp","beta"]`$, t(40.4)=`r e1tokens["conditionexp","tval"]`, *p*<.05), with parents using more words in the Video condition (mean: `r round(subset(e1_lexdiv, condition=='exp')$tokens, 0)`, bootstrapped 95% confidence intervals (CI): [`r round(subset(ms_tok, Condition=="Video")$ci_lower, 0)`,`r round(subset(ms_tok, Condition=="Video")$ci_upper, 0)`]) than in the Control condition (mean: `r round(subset(e1_lexdiv, condition=='con')$tokens, 0)`, bootstrapped 95% CI: [`r round(subset(ms_tok, Condition=="Control")$ci_lower, 0)`,`r round(subset(ms_tok, Condition=="Control")$ci_upper, 0)`]).
 The means of the lexical diversity measures are reported in Table \ref{e1tab}.
@@
 names(e1) = c("Condition","TTR (M)", "(sd)", "MTLD (M)", "(sd)", "Types (M)", "(sd)", "Tokens (M)", "(sd)")
-kable(e1, digits=2, caption="Lexical diversity measures in Experiment 1.", label="e1tab")
+kable(e1, digits=2, caption="\\label{e1tab} Lexical diversity measures in Experiment 1.")
 ```
@@
 ```{r fig:e1lex_div, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.5, fig.height=3.0, set.cap.width=T, num.cols.cap=1, fig.cap = "\\label{fig:e1lex_div} Mean lexical diversity scores by condition (left: Type/Token ratio, right: MTLD) in Experiment 1.
-Error bars show bootstrapped 95 percent confidence intervals (CIs)."}
+Both measures of lexical diversity were significantly lower after watching an activity video.
+Error bars show bootstrapped 95\\% confidence intervals (CIs), and gray dots indicate values for each participant."}
 
@@
 
-```{r e1token_type, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.5, fig.height=3.0, set.cap.width=T, num.cols.cap=1, fig.cap = "Mean number of word types and word tokens by condition in Experiment 1."}
+```{r e1token_type, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.5, fig.height=3.0, set.cap.width=T, num.cols.cap=1, fig.cap = "Mean number of word tokens (left) and word types (right) by condition in Experiment 1.
+Parents used significantly more word tokens after watching an activity video.
+Error bars show bootstrapped 95\\% CIs."}
 
@@
   summarise(mean = mean(TTR), sd = sd(TTR))
-cohens_d(ttr_means) # -1.68
+cohens_d(ttr_means) # -1.68 - should we report this?
 ```
@@
 cja_time_mod <- lmer(paste("cja_length", model_string), data = lmer_data)
-summary(cja_time_mod) # marginal parent education p=.09
+summary(cja_time_mod) # marginal parent education p=.09 - SINGULAR (do stan_glmer)
 ```
@@
 This lme4 model included random intercepts per video. 
-There were significantly more bids for JA in the Video condition (mean: `r round(subset(e1bids_M, Condition=="Video")$mean,2)`, sd: `r round(subset(e1bids_M, Condition=="Video")$sd,2)`) than in the Control condition (mean: `r round(subset(e1bids_M, Condition=="Control")$mean,2)`, sd: `r round(subset(e1bids_M, Condition=="Control")$sd,2)`, $\beta=`r e1bids["ConditionVideo","beta"]`$, t(40.3) = `r e1bids["ConditionVideo","zval"]`, *p*<.01).
+There were significantly more bids for JA in the Video condition (mean: `r round(subset(e1bids_M, Condition=="Video")$mean,2)`, sd: `r round(subset(e1bids_M, Condition=="Video")$sd,2)`) than in the Control condition (mean: `r round(subset(e1bids_M, Condition=="Control")$mean,2)`, sd: `r round(subset(e1bids_M, Condition=="Control")$sd,2)`, $\beta=`r e1bids["ConditionVideo","beta"]`$, t(`r e1bids["ConditionVideo","df"]`) = `r e1bids["ConditionVideo","tval"]`, *p*<.01).
 There were no other significant effects.
+
 Mixed-effects regressions with the same structure were performed predicting the number of episodes of coordinated and passive JA, and the total duration of time spent in coordinated and passive JA.
 There were no significant effects on the number or total duration of coordinated JA episodes, nor on the total duration of passive JA episodes. 
-For the regression predicting the number of passive JA episodes, the only significant effect was an interaction of condition and RR ($\beta=1.83$, t(41.5) = 2.22, *p*<.05), showing that for parents in the Video condition, those with higher Rules and Respect subscores engaged in more passive JA episodes.
-Figure X shows ... by condition.
+For the regression predicting the number of passive JA episodes, the only significant effect was an interaction of condition and RR ($\beta=`r e1pja["ConditionVideo:RR","beta"]`$, t(`r e1pja["ConditionVideo:RR","df"]`) = `r e1pja["ConditionVideo:RR","tval"]`, *p*<.05), showing that for parents in the Video condition, those with higher Rules and Respect subscores engaged in more passive JA episodes.
+Figure \ref{fig:e1ja} shows the mean number bids for JA and episodes of JA by condition in Experiment 1.
 
-```{r fig:e1ja, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.5, fig.height=3.0, set.cap.width=T, num.cols.cap=1, fig.cap = "\\label{fig:e1ja} Mean number of bids (left) and episodes (right) of joint attention by condition in Experiment 1."}
+```{r fig:e1ja, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.5, fig.height=3.0, set.cap.width=T, num.cols.cap=1, fig.cap = "\\label{fig:e1ja} Mean number of bids (left) and episodes (right) of joint attention (JA) by condition in Experiment 1.
+Parents made significantly more bids for JA after watching an activity video, but this did not result in a greater number of episodes of JA."}
 
@@
   geom_point(data=d, aes(x=Condition, y=bids_tot), alpha=.2, position = position_jitterdodge()) +
-  xlab("Condition") + ylab("Total Bids for Joint Attention") +
+  xlab("Condition") + ylab("Mean Bids for Joint Attention") +
   langcog::scale_fill_solarized() + ggthemes::theme_few() + 
@@
   geom_point(data=d, aes(x=Condition, y=total_ja), alpha=.2, position = position_jitterdodge()) +
-  xlab("Condition") + ylab("Total Episodes of Joint Attention") +
+  xlab("Condition") + ylab("Mean Episodes of Joint Attention") +
   langcog::scale_fill_solarized() + ggthemes::theme_few() + 
@@
 
-There was a main effect of condition on total bids for joint attention (JA). 
-Parents in the Video condition, after seeing a video demonstrating an activity, made a greater number of bids for JA with their child.
-There was no effect of condition on the number of episodes of either passive or coordinated JA, or the duration of these episodes. 
+Compared to parents in the Control condition, parents who watched an activity video made significantly more bids for JA with their child, although this did not result in a greater number of successful episodes of JA than dyads in the Control condition.
+No differences in the duration or number of episodes of passive or coordinated JA between conditions were found.
+
 There was a marginal effect of gender on bids for JA, with parents of males producing more bids. 
-There was a marginal interaction between RR scores and condition on passive JA, such that the experimental condition increased the number of episodes of passive JA to a greater extent for people with high RR scores.
+There was an interaction between RR scores and condition on passive JA, such that Video condition increased the number of episodes of passive JA to a greater extent for people with high RR scores.
 While the electronically-delivered parenting advice increased the number of bids for JA by parents, it did not significantly affect the number or duration of episodes of JA. 
@@
 
-The design of Experiment 2 was similar to that of Experiment 1, except that instead of a No-Video control condition, parents instead watched a video that was generally related to child development research, but did not give any specific instructions about how to interact with infants or children.
+The design of Experiment 2 was similar to that of Experiment 1, except that instead of No Video control condition, parents instead watched a video that was generally related to child development research, but did not give any specific instructions about how to interact with infants or children.
 This condition was included to control for the possibility that differences in language output and joint attention in Experiment 1 could be due to simply cueing parents to think about infants' learning and cognitive development.
@@
 summary(modTTR) # condition beta=-.09  t(8.6) = 3.33 p=.009 (suggestive)
-e2TTR <- get_lmer_reporting_values(modTTR) # here, the extracted pval = .003
+e2TTR <- get_lmer_reporting_values(modTTR)
 
@@
 
+e2_lexdiv <- lmer_data %>% group_by(condition) %>%
+  summarise(TTR=mean(TTR), MTLD=mean(MTLD), tokens=mean(tokens)) 
 # predict word types (NOT A PREREGISTERED REGRESSION)
@@
 We fit a mixed-effects linear regression predicting TTR as a function of age (0-centered) and condition with an interaction term, and with random intercepts per video using lme4 [@lme4].
-There was suggestively lower TTR in the Video condition (mean: 0.38) than in the Control condition (mean: 0.47, $\beta=`r e2TTR["conditionexp","beta"]`$, t(8.6) = `r e2TTR["conditionexp","zval"]`, *p*=.009).
+There was suggestively lower TTR in the Video condition (mean: `r round(e2_lexdiv[2,]$TTR, 2)`) than in the Control condition (mean: `r round(e2_lexdiv[1,]$TTR, 2)`, $\beta=`r e2TTR["conditionexp","beta"]`$, t(`r e2TTR["conditionexp","df"]`) = `r e2TTR["conditionexp","tval"]`, *p*=`r e2TTR["conditionexp","pval"]`).
 There was no significant effect of age, nor a significant interaction.
-The preregistered regression predicting the number of tokens used by parents found no significant effects. 
+The preregistered regression predicting the number of tokens used by parents revealed no significant effects. 
 An exploratory mixed-effects linear regression predicting MTLD found no significant effects of age or condition.
@@
 names(e2) = c("Condition","TTR (M)", "(sd)", "MTLD (M)", "(sd)", "Types (M)", "(sd)", "Tokens (M)", "(sd)")
-kable(e2, digits=2, caption="Lexical diversity measures in Experiment 2.", label="e2tab")
+kable(e2, digits=2, caption="\\label{e2tab} Lexical diversity measures in Experiment 2.")
 ```
@@
 tja_mod <- lmer(total_ja ~ age * Condition + (1 | video), data = e2ja)
+e2tja <- get_lmer_reporting_values(tja_mod)
 summary(tja_mod) # singular fit, convergence code: 0
@@
 
-# EXPLORATORY ANALYSES (NOT PREREGISTERED)
-
-# Episodes of coordinated joint attention
-cja_mod <- lmer(cja ~ age * Condition + (1 | video), data = e2ja)
-summary(cja_mod) #  Condition: t(80) = 2.47 beta=1.37 p=.01; age*Condition beta=5.24 t(80) = 2.19 p=.02
-# also singular fit, convergence code: 0 - check Bayesian regression
-cja_bmod <- stan_glmer(cja ~ age * Condition + (1|video), data=e2ja)
-summary(cja_bmod) # age n.s., sig effect of condition: mean=1.3 95% CI=[.1,2.6]; age*condition mean=5.1 CI=[.5,9.6]
-#                                        mean    sd     2.5%   25%    50%    75%    97.5%
-# (Intercept)                             5.3    0.4    4.5    5.0    5.3    5.6    6.2 
-# age                                    -2.0    1.4   -4.8   -2.9   -2.0   -1.1    0.9 
-# ConditionVideo                          1.3    0.6    0.1    0.9    1.3    1.7    2.6 
-# age:ConditionVideo                      5.1    2.3    0.5    3.5    5.1    6.5    9.6
-
-# Episodes of passive joint attention.
-pja_mod <- lmer(pja ~ age * Condition + (1 | video), data = e2ja)
-summary(pja_mod) # age beta=-2.88 t(13.4) = 2.53 p=.02
-
-# Total duration of passive joint attention.
-pja_time_mod <- lmer(pja_length ~ age * Condition + (1 | video), data = e2ja)
-summary(pja_time_mod) # singular - convergence code: 0, age beta=-18.89 t(80) = 2.72 p=.008
-pjat_bmod <- stan_glmer(pja_length ~ age * Condition + (1|video), data=e2ja)
-summary(pjat_bmod) # age: est: -17.9 95% CI = [-33.1,-2.2]
-
-# Total duration of coordinated joint attention.
-cja_time_mod <- lmer(cja_length ~ age * condition + (1 | video), data = e2ja)
-summary(cja_time_mod) # singular - convergence code: 0, marginal age: beta=37.35 t(80) = 1.95 p=.05
-cjat_bmod <- stan_glmer(cja_length ~ age * Condition + (1|video), data=e2ja)
-summary(cjat_bmod) # age: est: 35.3 95% CI = [-6.1,77.4] NOT SIGNIFICANT
-
 e2_bids <- e2ja %>% group_by(Condition) %>%
@@
   tidyboot_mean(total_ja)
+
 ```
 
-For the preregistered analyses, we fit mixed-effects linear regressions predicting the number of parental bids for joint attention and the total number of episodes of JA. 
-These JA variables were predicted as a function of fixed effects of condition, age (0-centered), and their interaction, with random intercepts per video.
-Parents made significantly more bids for JA in the Video condition (mean: `r round(subset(e2_bids, Condition=="Video")$mean,2)`, bootstrapped 95% CI: `r round(subset(e2_bids, Condition=="Video")$ci_lower,2)`, `r round(subset(e2_bids, Condition=="Video")$ci_upper,2)`) than in the Control condition (mean: `r round(subset(e2_bids, Condition=="Control")$mean,2)`, 95% CI: `r round(subset(e2_bids, Condition=="Control")$ci_lower,2)`, `r round(subset(e2_bids, Condition=="Control")$ci_upper,2)`, $\beta=`r e2bids["ConditionVideo","beta"]`$, t(79) = `r e2bids["ConditionVideo","zval"]`, *p*<.001).
+As preregistered, we fit mixed-effects linear regressions predicting the number of parental bids for joint attention and the total number of episodes of JA as a function of fixed effects of condition, age (0-centered), and their interaction, with random intercepts per video.
+Shown in Figure \ref{fig:e2ja} (left panel), parents made significantly more bids for JA after watching the Activity Video (mean: `r round(subset(e2_bids, Condition=="Video")$mean,2)`, bootstrapped 95% CI: `r round(subset(e2_bids, Condition=="Video")$ci_lower,2)`, `r round(subset(e2_bids, Condition=="Video")$ci_upper,2)`; $\beta=`r e2bids["ConditionVideo","beta"]`$, t(`r e2bids["ConditionVideo","df"]`) = `r e2bids["ConditionVideo","tval"]`, *p*=`r e2bids["ConditionVideo","pval"]`)) than after the Control Video (mean: `r round(subset(e2_bids, Condition=="Control")$mean,2)`, 95% CI: `r round(subset(e2_bids, Condition=="Control")$ci_lower,2)`, `r round(subset(e2_bids, Condition=="Control")$ci_upper,2)`, $\beta=`r e2bids["ConditionVideo","beta"]`$, t(`r e2bids["ConditionVideo","df"]`) = `r e2bids["ConditionVideo","tval"]`, *p*<.001).
 There were no other significant effects on parental bids for JA.
 
-There were significant effects of condition, age, and
+In the regression predicting the number of episodes of JA, there was a significant main effect of condition ($\beta=`r e2tja["ConditionVideo","beta"]`$, t(`r e2tja["ConditionVideo","df"]`) = `r e2tja["ConditionVideo","tval"]`, *p*=`r e2tja["ConditionVideo","pval"]`), with more episodes of JA occurring after the Activity Video (mean: `r round(subset(e2_tja, Condition=="Video")$mean,2)`, 95% CI: `r round(subset(e2_tja, Condition=="Video")$ci_lower,2)`, `r round(subset(e2_tja, Condition=="Video")$ci_upper,2)`) than after the Control Video (mean: `r round(subset(e2_tja, Condition=="Control")$mean,2)`, 95% CI: `r round(subset(e2_tja, Condition=="Control")$ci_lower,2)`, `r round(subset(e2_tja, Condition=="Control")$ci_upper,2)`).
+There was also a significant main effect of age ($\beta=`r e2tja["age","beta"]`$, t(`r e2tja["age","df"]`) = `r e2tja["age","tval"]`, *p*=`r e2tja["age","pval"]`), showing that the number of episodes of JA decreased with the child's age.
+However, a significant interaction of age and condition ($\beta=`r e2tja["age:ConditionVideo","beta"]`$, t(`r e2tja["age:ConditionVideo","df"]`) = `r e2tja["age:ConditionVideo","tval"]`, *p*=`r e2tja["age:ConditionVideo","pval"]`), shown in the right panel of Figure \ref{fig:e2ja}, demonstrates that older children in the Activity Video condition did not see a decrease in the number of episodes of JA.
 
-Figure \ref{fig:e2ja} shows the mean number of parental bids for JA by condition (left), along with total episodes of JA by age and condition (right).
-
-Additional exploratory regressions with a similar structure were carried out on number and duration of coordinated and passive JA episodes.
-
-```{r fig:e2ja, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=6, fig.height=3.0, set.cap.width=T, num.cols.cap=1, fig.cap = "\\label{fig:e2ja} Mean number of bids for JA by condition (left) and total episodes of JA by age and condition (right) in Experiment 2."}
+```{r fig:e2ja, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=6, fig.height=3.0, set.cap.width=T, num.cols.cap=1, fig.cap = "\\label{fig:e2ja} Mean number of bids for JA by condition (left) and the number of episodes of JA by age and condition (right) in Experiment 2.
+After watching an activity video, parents made more bids for JA.
+Older children in the Activity Video condition showed no decrease in the number of episodes of JA, unlike children in the Control Video condition."}
 
@@
 
-```{r e2ja-pass-coord, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.5, fig.height=3.0, set.cap.width=T, num.cols.cap=1, fig.cap = "\\label{fig:e2ja-pass-coord} Mean number of passive (left) and coordinated (right) episodes of JA by condition in Experiment 2."}
-ms_pja <- d %>% group_by(Condition) %>%
-  tidyboot_mean(pja)
+```{r e2ja-exploratory, echo=F, include=F}
+# EXPLORATORY ANALYSES (NOT PREREGISTERED)
 
-e2pja <- ggplot(ms_pja, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
-  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
-  geom_point(data=d, aes(x=Condition, y=pja), alpha=.2, position = position_jitterdodge()) +
-  xlab("Condition") + ylab("Episodes of Passive Joint Attention") +
-  langcog::scale_fill_solarized() + ggthemes::theme_few() + theme(legend.position="none")
+# Episodes of coordinated joint attention
+cja_mod <- lmer(cja ~ age * Condition + (1 | video), data = e2ja)
+summary(cja_mod) #  Condition: t(80) = 2.47 beta=1.37 p=.01; age*Condition beta=5.24 t(80) = 2.19 p=.02
+e2cja <- get_lmer_reporting_values(cja_mod)
+# also singular fit, convergence code: 0 - Bayesian regression confirms:
+cja_bmod <- stan_glmer(cja ~ age * Condition + (1|video), data=e2ja)
+summary(cja_bmod) # age n.s., sig effect of condition: mean=1.3 95% CI=[.1,2.6]; age*condition mean=5.1 CI=[.5,9.6]
+#                                        mean    sd     2.5%   25%    50%    75%    97.5%
+# (Intercept)                             5.3    0.4    4.5    5.0    5.3    5.6    6.2 
+# age                                    -2.0    1.4   -4.8   -2.9   -2.0   -1.1    0.9 
+# ConditionVideo                          1.3    0.6    0.1    0.9    1.3    1.7    2.6 
+# age:ConditionVideo                      5.1    2.3    0.5    3.5    5.1    6.5    9.6
+
+# Episodes of passive joint attention.
+pja_mod <- lmer(pja ~ age * Condition + (1 | video), data = e2ja)
+summary(pja_mod) # age beta=-2.88 t(13.4) = 2.53 p=.02
+e2pja <- get_lmer_reporting_values(pja_mod)
+
+# Total duration of passive joint attention.
+pja_time_mod <- lmer(pja_length ~ age * Condition + (1 | video), data = e2ja)
+summary(pja_time_mod) # singular - convergence code: 0, age beta=-18.89 t(80) = 2.72 p=.008
+e2pja_time <- get_lmer_reporting_values(pja_time_mod)
+pjat_bmod <- stan_glmer(pja_length ~ age * Condition + (1|video), data=e2ja)
+summary(pjat_bmod) # age: est: -17.9 95% CI = [-33.1,-2.2]
+
+# Total duration of coordinated joint attention.
+cja_time_mod <- lmer(cja_length ~ age * condition + (1 | video), data = e2ja)
+summary(cja_time_mod) # singular - convergence code: 0, marginal age: beta=37.35 t(80) = 1.95 p=.05
+cjat_bmod <- stan_glmer(cja_length ~ age * Condition + (1|video), data=e2ja)
+summary(cjat_bmod) # age: est: 35.3 95% CI = [-6.1,77.4] NOT SIGNIFICANT
+
+e2_cja <- e2ja %>% group_by(Condition) %>%
+  tidyboot_mean(cja)
+```
+
+### Exploratory Analyses
+
+Four additional exploratory regressions with a similar structure were carried out to predict the number and duration of coordinated and passive JA episodes.
+The regression predicting the number of episodes of coordinated JA found a significant main effect of condition ($\beta=`r e2cja["ConditionVideo","beta"]`$, t(`r e2cja["ConditionVideo","df"]`) = `r e2cja["ConditionVideo","tval"]`, *p*=`r e2cja["ConditionVideo","pval"]`), with more episodes of coordinated JA occurring after the Activity Video (mean: `r round(subset(e2_cja, Condition=="Video")$mean,2)`, 95% CI: `r round(subset(e2_cja, Condition=="Video")$ci_lower,2)`, `r round(subset(e2_cja, Condition=="Video")$ci_upper,2)`) than after the Control Video (mean: `r round(subset(e2_cja, Condition=="Control")$mean,2)`, 95% CI: `r round(subset(e2_cja, Condition=="Control")$ci_lower,2)`, `r round(subset(e2_cja, Condition=="Control")$ci_upper,2)`).
+There was no significant effect of age, but there was a significant interaction of age and condition ($\beta=`r e2cja["age:ConditionVideo","beta"]`$, t(`r e2cja["age:ConditionVideo","df"]`) = `r e2cja["age:ConditionVideo","tval"]`, *p*=`r e2cja["age:ConditionVideo","pval"]`), shown in Figure \ref{e2ja-coord}, revealing that older children in the Activity Video condition had more episodes of coordinated JA than children in the Control Video condition.
+The regression predicting the total duration of coordinated JA episodes revealed no significant effects.
+
+In the regression predicting the number of episodes of passive JA, there was a main effect of age ($\beta=`r e2pja["ConditionVideo","beta"]`$, t(`r e2pja["ConditionVideo","df"]`) = `r e2pja["ConditionVideo","tval"]`, *p*=`r e2pja["ConditionVideo","pval"]`), showing that older children had more episodes of passive JA with their caregiver.
+The regression predicting the total duration of passive JA revealed a main effect of age ($\beta=`r e2pja_time["ConditionVideo","beta"]`$, t(`r e2pja_time["ConditionVideo","df"]`) = `r e2pja_time["ConditionVideo","tval"]`, *p*=`r e2pja_time["ConditionVideo","pval"]`), revealing that older children spent more time in passive JA with their caregiver.
+Overall, these results show that the older children in our sample engage in more and longer episodes of joint attention with their caregivers, and suggest that the Activity Video strengthened this trend in the number of episodes of coordinated JA.
+
+```{r e2ja-coord, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=4.5, fig.height=3.5, set.cap.width=T, num.cols.cap=1, fig.cap = "\\label{fig:e2ja-coord} The number of episodes of coordinated JA by condition and age in Experiment 2.
+Older children in the Activity Video condition engaged in more episodes of coordinated JA with their caregiver than dyads in the Control Video condition."}
 
@@
 
-multiplot(e2pja, e2cja, cols=2)
+e2cja_age = ggplot(d, aes(x = age, y = cja, group=Condition, colour = Condition)) +
+  geom_point(alpha=.7) + geom_smooth(method='lm') + 
+  xlab("Age (years)") + ylab("Episodes of Coordinated JA") +
+  langcog::scale_colour_solarized() + ggthemes::theme_few()
+
+print(e2cja_age)
+#multiplot(e2cja, e2tja_age, cols=4, layout=matrix(c(1,2,2,2), nrow=1))
 ```
-
-There was an effect on total bids for joint attention. 
-Parents in the experimental condition (i.e., those who saw a video demonstrating an activity) made a greater number of bids for joint attention with their child.
-There was no effect of condition on the number of episodes of passive or coordinated JA, nor on the duration of these episodes. 
-For passive joint attention, there was a main effect of age on both the number and duration of episodes, with older children having fewer episodes of passive JA and episodes of shorter duration.
-Moreover, older children had longer duration episodes of coordinated JA.
-These results suggest that as children age, they become more socially engaged in interactions with their caregivers.
 
@@
 
-Parents are told to show their child yellow toys and to ask "what color are they".
-They are also told to give the child toys of different colors, ask them to only play with the yellow ones and praise the child after they do so.
+Parents are told to show their child yellow toys and to ask, "What color are they?" They are also told to give the child toys of different colors, to ask them to only play with the yellow ones, and to praise the child after they do so.
 

### 2019-07-21 paper/cogsci2019/cogsci2019.Rmd
sketched discussion

@@
 But is this theory of change correct? That is, does the provision of knowledge and activities lead to higher-quality play? 
-Alternatively, this theory could be wrong in a number of ways. 
+Alternatively, this theory could be flawed in a number of ways. 
 By focusing parents on a specific activity, parents may over-focus on achieving the superficial goals of the activity. 
@@
 
-```{r fig:e1ja-pass-coord, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.5, fig.height=3.5, set.cap.width=T, num.cols.cap=1, fig.cap = "\\label{fig:e1ja-pass-coord} Mean number of passive (left) and coordinated episodes (right) of JA by condition in Experiment 1."}
+```{r fig:e1ja-pass-coord, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.5, fig.height=3.5, set.cap.width=T, num.cols.cap=1, fig.cap = "\\label{fig:e1ja-pass-coord} The mean number of passive (left) and coordinated episodes (right) of JA  in Experiment 1 were similar in both conditions."}
 ms_pja <- d %>% group_by(Condition) %>%
@@
 It may be that parents in the Video condition, in their attempt to stick to the prescribed task, end up repeating themselves more.
-Demographics and EPAQ do not interact with condition, although there was a marginal effect of RR score on lexical diversity (lower diversity for higher RR scores), and marginal effects of parent education on word types and tokens (more types and tokens for higher parent education).
+Demographics and EPAQ do not interact with condition, although there was a marginal effect of RR score on lexical diversity (lower diversity for higher RR scores), and marginal effects of parent education on word types and tokens (higher education yielding more types and tokens).
 
-Compared to parents in the Control condition, parents who watched an activity video made significantly more bids for JA with their child, although this did not result in a greater number of successful episodes of JA than dyads in the Control condition.
+Parents who watched an activity video made significantly more bids for JA with their child, although this did not result in a greater number of successful episodes of JA than dyads in the no video condition.
 No differences in the duration or number of episodes of passive or coordinated JA between conditions were found.
 
-There was a marginal effect of gender on bids for JA, with parents of males producing more bids. 
-There was an interaction between RR scores and condition on passive JA, such that Video condition increased the number of episodes of passive JA to a greater extent for people with high RR scores.
+There was an interactive effect of RR scores and condition on passive JA, such that for parents with high RR scores, the activity video increased the number of episodes of passive JA to a greater extent than for parents in the no video condition.
 While the electronically-delivered parenting advice increased the number of bids for JA by parents, it did not significantly affect the number or duration of episodes of JA.
-It may be that children had a larger relative impact on the attainment of joint attention.
 
@@
 As preregistered, we fit mixed-effects linear regressions predicting the number of parental bids for joint attention and the total number of episodes of JA as a function of fixed effects of condition, age (0-centered), and their interaction, with random intercepts per video.
-Shown in Figure \ref{fig:e2ja} (left panel), parents made significantly more bids for JA after watching the Activity Video (mean: `r round(subset(e2_bids, Condition=="Video")$mean,2)`, bootstrapped 95% CI: `r round(subset(e2_bids, Condition=="Video")$ci_lower,2)`, `r round(subset(e2_bids, Condition=="Video")$ci_upper,2)`; $\beta=`r e2bids["ConditionVideo","beta"]`$, t(`r e2bids["ConditionVideo","df"]`) = `r e2bids["ConditionVideo","tval"]`, *p*=`r e2bids["ConditionVideo","pval"]`)) than after the Control Video (mean: `r round(subset(e2_bids, Condition=="Control")$mean,2)`, 95% CI: `r round(subset(e2_bids, Condition=="Control")$ci_lower,2)`, `r round(subset(e2_bids, Condition=="Control")$ci_upper,2)`, $\beta=`r e2bids["ConditionVideo","beta"]`$, t(`r e2bids["ConditionVideo","df"]`) = `r e2bids["ConditionVideo","tval"]`, *p*<.001).
+Shown in Figure \ref{fig:e2ja} (left panel), parents made significantly more bids for JA after watching the Activity Video (mean: `r round(subset(e2_bids, Condition=="Video")$mean,2)`, bootstrapped 95% CI: `r round(subset(e2_bids, Condition=="Video")$ci_lower,2)`, `r round(subset(e2_bids, Condition=="Video")$ci_upper,2)`; $\beta=`r e2bids["ConditionVideo","beta"]`$, t(`r e2bids["ConditionVideo","df"]`) = `r e2bids["ConditionVideo","tval"]`, *p*=`r e2bids["ConditionVideo","pval"]`)) than after the Control Video (mean: `r round(subset(e2_bids, Condition=="Control")$mean,2)`, 95% CI: [`r round(subset(e2_bids, Condition=="Control")$ci_lower,2)`, `r round(subset(e2_bids, Condition=="Control")$ci_upper,2)`], $\beta=`r e2bids["ConditionVideo","beta"]`$, t(`r e2bids["ConditionVideo","df"]`) = `r e2bids["ConditionVideo","tval"]`, *p*<.001).
 There were no other significant effects on parental bids for JA.
 
-In the regression predicting the number of episodes of JA, there was a significant main effect of condition ($\beta=`r e2tja["ConditionVideo","beta"]`$, t(`r e2tja["ConditionVideo","df"]`) = `r e2tja["ConditionVideo","tval"]`, *p*=`r e2tja["ConditionVideo","pval"]`), with more episodes of JA occurring after the Activity Video (mean: `r round(subset(e2_tja, Condition=="Video")$mean,2)`, 95% CI: `r round(subset(e2_tja, Condition=="Video")$ci_lower,2)`, `r round(subset(e2_tja, Condition=="Video")$ci_upper,2)`) than after the Control Video (mean: `r round(subset(e2_tja, Condition=="Control")$mean,2)`, 95% CI: `r round(subset(e2_tja, Condition=="Control")$ci_lower,2)`, `r round(subset(e2_tja, Condition=="Control")$ci_upper,2)`).
+In the regression predicting the number of episodes of JA, there was a significant main effect of condition ($\beta=`r e2tja["ConditionVideo","beta"]`$, t(`r e2tja["ConditionVideo","df"]`) = `r e2tja["ConditionVideo","tval"]`, *p*=`r e2tja["ConditionVideo","pval"]`), with more episodes of JA occurring after the Activity Video (mean: `r round(subset(e2_tja, Condition=="Video")$mean,2)`, 95% CI: [`r round(subset(e2_tja, Condition=="Video")$ci_lower,2)`, `r round(subset(e2_tja, Condition=="Video")$ci_upper,2)`]) than after the Control Video (mean: `r round(subset(e2_tja, Condition=="Control")$mean,2)`, 95% CI: [`r round(subset(e2_tja, Condition=="Control")$ci_lower,2)`, `r round(subset(e2_tja, Condition=="Control")$ci_upper,2)`]).
 There was also a significant main effect of age ($\beta=`r e2tja["age","beta"]`$, t(`r e2tja["age","df"]`) = `r e2tja["age","tval"]`, *p*=`r e2tja["age","pval"]`), showing that the number of episodes of JA decreased with the child's age.
@@
 Four additional exploratory regressions with a similar structure were carried out to predict the number and duration of coordinated and passive JA episodes.
-The regression predicting the number of episodes of coordinated JA found a significant main effect of condition ($\beta=`r e2cja["ConditionVideo","beta"]`$, t(`r e2cja["ConditionVideo","df"]`) = `r e2cja["ConditionVideo","tval"]`, *p*=`r e2cja["ConditionVideo","pval"]`), with more episodes of coordinated JA occurring after the Activity Video (mean: `r round(subset(e2_cja, Condition=="Video")$mean,2)`, 95% CI: `r round(subset(e2_cja, Condition=="Video")$ci_lower,2)`, `r round(subset(e2_cja, Condition=="Video")$ci_upper,2)`) than after the Control Video (mean: `r round(subset(e2_cja, Condition=="Control")$mean,2)`, 95% CI: `r round(subset(e2_cja, Condition=="Control")$ci_lower,2)`, `r round(subset(e2_cja, Condition=="Control")$ci_upper,2)`).
+The regression predicting the number of episodes of coordinated JA found a significant main effect of condition ($\beta=`r e2cja["ConditionVideo","beta"]`$, t(`r e2cja["ConditionVideo","df"]`) = `r e2cja["ConditionVideo","tval"]`, *p*=`r e2cja["ConditionVideo","pval"]`), with more episodes of coordinated JA occurring after the Activity Video (mean: `r round(subset(e2_cja, Condition=="Video")$mean,2)`, 95% CI: [`r round(subset(e2_cja, Condition=="Video")$ci_lower,2)`, `r round(subset(e2_cja, Condition=="Video")$ci_upper,2)`]) than after the Control Video (mean: `r round(subset(e2_cja, Condition=="Control")$mean,2)`, 95% CI: [`r round(subset(e2_cja, Condition=="Control")$ci_lower,2)`, `r round(subset(e2_cja, Condition=="Control")$ci_upper,2)`]).
 There was no significant effect of age, but there was a significant interaction of age and condition ($\beta=`r e2cja["age:ConditionVideo","beta"]`$, t(`r e2cja["age:ConditionVideo","df"]`) = `r e2cja["age:ConditionVideo","tval"]`, *p*=`r e2cja["age:ConditionVideo","pval"]`), shown in Figure \ref{e2ja-coord}, revealing that older children in the Activity Video condition had more episodes of coordinated JA than children in the Control Video condition.
@@
 
-In both experiments, the number of tokens was higher in the experimental condition, while the number of types and lexical diversity (Type/Token ratio) were higher in the control condition. 
-Parents may be relatively more repetetive in the experimental condition since they are attempting to stick to a specific prescribed task, but they talk more overall.
+This study investigated how parents change their interactions with their young children on the basis of one of several short video parenting messages from the Kinedu commercial parenting app, which suggest interactive toy-based activities (e.g., learning animal sounds), along with a scientific justification.
+Parents in the control conditions received either no video (Experiment 1) or a video of a recent finding in developmental psychology (Experiment 2), but played with the same sets of toys given to those in the experimental conditions.
+After completing the videos, parents were videotaped playing with their children for two minutes. 
+The quality of parents' interactions with their children were measured by the lexical diversity of their child-directed speech, and through behavioral coding of bids for and episodes of joint attention (JA).
+
+Experiment 1 investigated 6--24-month-olds, and found a greater number of bids for JA from parents after watching the activity video, but no difference in the number of JA episodes. 
+Experiment 2 (12--24-month-olds) replicated this greater number of bids for JA after the activity video, and moreover found that while the number of JA episodes dwindled for older infants in the control condition, dyads in the activity video condition achieved an overall higher and constant number of JA episodes.
+In combination, these results suggest that short parenting messages suggesting activities can encourage parents to make more attempts to engage their child in joint attention, and that in some cases--especially in older children--these bids are successful in increasing engagement.
+
+Experiment 1 found lower lexical diversity in parents' speech after watching the activity video, but the average number of word tokens used was higher after the activity video, and the number of word types was the same in both conditions.
+Experiment 2 had similar lexical diversity results, finding suggestively lower Type-Token Ratio after the activity video, although the length-corrected lexical diversity measure (MTLD) did not differ significantly.
+However, the number of tokens did not significantly differ betwen condition in Experiment 2. [nor types -- exploratory regression]
+Overall, although it may seem worrisome that the activity videos lead to somewhat lower lexical diversity, this worry is  mitigated by the fact that this difference is explained not by fewer word types but by a greater number of word tokens used by parents after the activity video (significantly in Experiment 1, and numerically in Experiment 2).
+It may be that parents are relatively more repetitive after watching the activity video in their attempt to stick to the prescribed task, but overall they talk more.
+
+Taken together, the results of this study show that digital parenting interventions recommending particular play activities to parents of young children can influence both the quality and quantity of child-directed speech, as well as parents attempts to engage their children in joint attention---at least in the short term.
+[more limitations / recommendations for extensions]
+What do these results imply for a theory of change?
 
@@
 
-### Video B (6-11.9 months) “Animal sounds”
+### Video B (6-11.9 months) "Animal sounds"
 

### 2019-08-06 paper/cogsci2019/cogsci2019.Rmd
edits

@@
 Yet little is known about the effects of communicating to parents through app-based interventions.
-In a study of one commercial app offering a collection of age-appropriate activity videos, we find  that the quality of parent-child interactions increases in some ways as a result of using the app.
-Specifically, the lexical diversity of parents' child-directed speech increases, and measures of  joint attention show...
+We showed parents a short video depicting an age-appropriate parent-child activity from a commercial parenting app, and found that the quality of parent-child interactions increases in some ways as a result of the intervention.
+Specifically, after watching the activity video, parents spoke more and made more bids for joint attention with the child.
 ---
@@
 ```{r global_options, include=FALSE}
-knitr::opts_chunk$set(fig.width=3, fig.height=3, fig.crop = F, 
+knitr::opts_chunk$set(fig.width=4, fig.height=3, fig.crop = F, 
                       fig.pos = "tb", fig.path='figs/',
@@
 theme_set(theme_few())
+
+# labels=addline_format(c("Activity Video", "Science Video"))
+addline_format <- function(x,...){
+    gsub('\\s','\n',x)
+}
 ```
@@
 For this reason, many researchers targeting early language are interested in delivering parenting interventions remotely -- through texts, apps, and videos delivered on digital devices. 
-But what do parents take away from these short messages about what to do or how to talk with their children?
+But what do parents take away from these short messages about what to do with or how to talk with their children?
 
@@
 But is this theory of change correct? That is, does the provision of knowledge and activities lead to higher-quality play? 
-Alternatively, this theory could be flawed in a number of ways. 
-By focusing parents on a specific activity, parents may over-focus on achieving the superficial goals of the activity. 
+Alternatively, by focusing parents on a specific activity, this theory could be flawed, causing parents to over-focus on achieving the superficial goals of the activity. 
 This problem might be especially likely with video messages, which could encourage parents to try to mimic a model's specific speech and/or actions.
 Attempting to reproduce such surface details of a video-guided activity could in turn result in less high-quality talk, with less responsiveness to their child's play.
-Another possibility is that these messages do produce the desired effect, but only for those parents who already have a general orientation towards children's early learning.
+Another possibility is that these messages might produce the desired effect, but only for those parents who already have a general orientation towards children's early learning.
 
@@
 
-In Experiment 1, we invited parents of 6- to 24-month-old infants visiting the Children's Discovery Museum in San Jose to complete video-guided activities from Kinedu (Kinedu Inc.), a parenting app that delivers digital parenting advice in the form of short videos.
-Parents were randomly assigned to the video condition or the control condition; parents in the _video_ condition watched a video from the Kinedu app (matched to their child's age), and then performed the activity with their child using the props from the video.
-Parents in the _control_ condition did not watch a Kinedu video, but were given a set of the same age-appropriate props and asked to play with their infants as they normally would at home.
+In Experiment 1, we invited parents of 6- to 24-month-old infants visiting the Children's Discovery Museum in San Jose to complete video-guided activities from a commerical parenting app that delivers digital parenting advice in the form of short videos.
+Parents were randomly assigned to the video condition or the control condition; parents in the _activity video_ condition watched a video from the app (matched to their child's age), and then performed the activity with their child using the props from the video.
+Parents in the _control_ condition did not watch an activity video, but were given a set of the same age-appropriate props and asked to play with their infants as they normally would at home.
 
@@
          age = as.numeric(langcog::scale(age, scale=FALSE)),
+         parent_ed = as.numeric(langcog::scale(parent_ed, scale=T)),
          gender = as.factor(gender),
@@
 ### Materials.
-Stimuli included videos from the Kinedu commercial parenting application. 
+Stimuli included activity videos from a commercial parenting application. 
 The videos were designed to show activities to parents that they could perform with their child in order to foster cognitive and physical development, and were targeted to the child's age and level of development.
@@
 
-Participants were randomly assigned to either the *Video* condition or the *Control* condition. 
-Parents participating in the Video condition were assigned to watch one of the two activity videos available for their child's age group, while parents in the Control condition watched no activity video, and were simply asked to play with their child as they normally would.
-The Control condition was yoked to the Video condition such that for every participant in the Video condition who saw a particular video and received the associated props, a participant in the Control condition received the same props but did not watch the activity video.
+Participants were randomly assigned to either the *Activity Video* condition or the *No Video* condition. 
+Parents participating in the Activity Video condition were assigned to watch one of the two activity videos available for their child's age group, while parents in the No Video condition watched no video, and were simply asked to play with their child as they normally would.
+The No Video condition was yoked to the Activity Video condition such that for every participant in the Video condition who saw a particular video and received the associated props, a participant in the No Video condition received the same props but did not watch the activity video.
 Parents also completed the Early Parenting Attitudes Questionnaire [EPAQ; @Hembacher2018]. 
-The EPAQ measures parents' attitudes about parenting and child development along three dimensions: rules and respect, early learning, and affection and attachment.
+The EPAQ measures parents of young children's attitudes about parenting and child development along three dimensions: rules and respect, early learning, and affection and attachment.
 
 ### Procedure.
-After providing informed consent, parents in the Video condition watched the assigned activity video on a laptop with headphones.
+After providing informed consent, parents in the Activity Video condition watched the assigned activity video on a laptop with headphones.
 To ensure that parents could give the video their full attention, the experimenter played with the infant with a set of toys (different from the experimental props used in the study) while the video was being played.
 Immediately following the video, each parent-child dyad was provided with the props to complete the video-guided activity that the parent had viewed. 
-The toys were placed on a large foam play mat, and parents were instructed to sit on the mat with their child and re-create the activity they had viewed for a period of three minutes.
+The toys were placed on a large foam play mat, and parents were instructed to sit on the mat with their child and re-create the activity they had viewed for a period of three minutes.[^2]
 In the Control condition, after informed consent parents were told to play with their child as they would at home with the provided props for a period of three minutes. 
@@
 
-In both conditions, two video cameras were used to record the play session from different angles, and parents were fitted with a wireless Shurre lavalier microphone to record their child-directed speech.
+[^2]: Based on piloting, we estimated these activities would would only require three minutes to complete.
+
+In both conditions, two video cameras were used to record the play session from different angles, and parents were fitted with a wireless Shure lavalier microphone to record their child-directed speech.
 After three minutes of play had elapsed, parents were told they could stop playing and the cameras and microphone were turned off.
@@
 The video of each session was manually coded for episodes of joint attention (JA) using the Datavyu software [@datavyu]. 
-The video taken at floor level was coded by default, but the other video was referred to if the participants were not visible or if there was technical difficulty with the first camera. 
+The video taken at floor level was coded by default, but the other video was referred to if the participants were occluded or if there was technical difficulty with the first camera. 
 Each session's video was coded for episodes of coordinated JA, episodes of passive JA, and parental bids for JA. 
@@
 A joint attention episode was considered _coordinated_ if both participants visually focused on an object for 3 or more seconds and at some point in the interaction the child indicated awareness of interaction with some overt behavior toward the parent such as looking at their face, gesturing, vocalizing, or turn-taking.
-Full details of our guidelines for coding joint attention are available [here](https://docs.google.com/document/d/1cZrT_Gjt6p0om19lXO-XcFnT09pb0giyhRQ-Pm1yoBU/edit?usp=sharing).
+Full details of our guidelines for coding joint attention are available in [SI](https://docs.google.com/document/d/1cZrT_Gjt6p0om19lXO-XcFnT09pb0giyhRQ-Pm1yoBU/edit?usp=sharing).
 
@@
 Parents' child-directed speech during the play sessions was transcribed.
-The transcripts and hand-coded joint attention data were analyzed according to our preregistration[^2], with any deviations or extensions noted.
+The transcripts and hand-coded joint attention data were analyzed according to our preregistration[^3], with any deviations or extensions noted.
 Below we first report the lexical diversity results, followed by the joint attention results.
 
-[^2]: Preregistration: [https://osf.io/2bpdf/](https://osf.io/2bpdf/)]
+[^3]: Preregistration: [https://osf.io/2bpdf/](https://osf.io/2bpdf/)]
 
@@
 require("lmerTest")
+
 # Predicting lexical diversity based on experimental condition, PAQ, demographics. 
@@
 modMTLD <- lmer(MTLD ~ condition + age + gender + parent_ed + (1|video), data=lmer_data)
+ # , control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5)))
 summary(modMTLD) # condition -8.73 t(55) = 2.67 p=.001 !! singular fit
 e1MTLD = get_lmer_reporting_values(modMTLD)
+
+tt <- getME(modMTLD,"theta")
+ll <- getME(modMTLD,"lower")
+min(tt[ll==0]) # 0
+
 # Bayesian regression (stan_glmer in rstanarm) shows the same:
@@
 # predict word types
-types_mod <- lmer(types ~ condition*EL + condition*AA + condition*RR  + age + gender + parent_ed + (1|video), data=lmer_data) # !! singular fit
+types_mod <- lmer(types ~ condition*EL + condition*AA + condition*RR  + age + gender + parent_ed + (1|video), data=lmer_data,
+                  control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) # !! singular fit
 summary(types_mod) # nothing (hint: conditionexp:AA beta=19.04 p=.11)
@@
 
-We fit a mixed-effects linear regression predicting TTR as a function of condition, age (0-centered), gender, and parent's education level with a random intercept per video using lme4 [@lme4]. 
+We fit a mixed-effects linear regression predicting TTR as a function of condition, age (centered), gender, and parent's education level with a random intercept per video using lme4 [@lme4]. 
 There was significantly lower TTR in the Video condition (mean: `r round(subset(e1_lexdiv, condition=='exp')$TTR, 2)`) than in the Control condition (mean: `r round(subset(e1_lexdiv, condition=='con')$TTR, 2)`, $\beta=$`r e1TTR["conditionexp","beta"]`, t(52.4) = `r e1TTR["conditionexp","tval"]`, *p*<.001).
@@
 ```{r e1tokens, echo=F, include=F}
-d$Condition = factor(d$condition, levels = c("con", "exp"), labels = c("Control", "Video"))
+d$Condition = factor(d$condition, levels = c("con", "exp"), labels = c("No Video", "Activity Video"))
 
@@
 
-We also conducted similar regressions predicting the number of word tokens and types, finding only a significant effect of condition on the number of word tokens ($\beta= `r e1tokens["conditionexp","beta"]`$, t(40.4)=`r e1tokens["conditionexp","tval"]`, *p*<.05), with parents using more words in the Video condition (mean: `r round(subset(e1_lexdiv, condition=='exp')$tokens, 0)`, bootstrapped 95% confidence intervals (CI): [`r round(subset(ms_tok, Condition=="Video")$ci_lower, 0)`,`r round(subset(ms_tok, Condition=="Video")$ci_upper, 0)`]) than in the Control condition (mean: `r round(subset(e1_lexdiv, condition=='con')$tokens, 0)`, bootstrapped 95% CI: [`r round(subset(ms_tok, Condition=="Control")$ci_lower, 0)`,`r round(subset(ms_tok, Condition=="Control")$ci_upper, 0)`]).
+We also conducted similar regressions predicting the number of word tokens and types, finding only a significant effect of condition on the number of word tokens ($\beta= `r e1tokens["conditionexp","beta"]`$, t(40.4)=`r e1tokens["conditionexp","tval"]`, *p*<.05), with parents using more words in the Video condition (mean: `r round(subset(e1_lexdiv, condition=='exp')$tokens, 0)`, bootstrapped 95% confidence intervals (CI): [`r round(subset(ms_tok, Condition=="Activity Video")$ci_lower, 0)`,`r round(subset(ms_tok, Condition=="Activity Video")$ci_upper, 0)`]) than in the Control condition (mean: `r round(subset(e1_lexdiv, condition=='con')$tokens, 0)`, bootstrapped 95% CI: [`r round(subset(ms_tok, Condition=="No Video")$ci_lower, 0)`,`r round(subset(ms_tok, Condition=="No Video")$ci_upper, 0)`]).
 The means of the lexical diversity measures are reported in Table \ref{e1tab}.
@@
 
-```{r fig:e1lex_div, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.5, fig.height=3.0, set.cap.width=T, num.cols.cap=1, fig.cap = "\\label{fig:e1lex_div} Mean lexical diversity scores by condition (left: Type/Token ratio, right: MTLD) in Experiment 1.
+```{r fig:e1lex_div, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=7, fig.height=3.0, set.cap.width=T, num.cols.cap=1, fig.cap = "\\label{fig:e1lex_div} Mean lexical diversity scores by condition (left: Type/Token ratio, right: MTLD) in Experiment 1.
 Both measures of lexical diversity were significantly lower after watching an activity video.
@@
 
-multiplot(e1ttr, e1mtld, cols=2)
-```
-
-Word tokens and word types
-
-```{r e1token_type, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.5, fig.height=3.0, set.cap.width=T, num.cols.cap=1, fig.cap = "Mean number of word tokens (left) and word types (right) by condition in Experiment 1.
-Parents used significantly more word tokens after watching an activity video.
-Error bars show bootstrapped 95\\% CIs."}
-
 e1tokens <- ggplot(ms_tok, aes(x=Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
@@
 
-e1types <- ggplot(ms_type, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
-  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
-  geom_point(data=d, aes(x=Condition, y=types), alpha=.2, position = position_jitterdodge()) +
-  xlab("Condition") + ylab("Total Number of Word Types") +
-  langcog::scale_fill_solarized() + ggthemes::theme_few() +
-  theme(legend.position="none")
-
-multiplot(e1tokens, e1types, cols=2)
+multiplot(e1ttr, e1mtld, e1tokens, cols=3)
 ```
@@
 load(paste(e1path,"joint_attention/Exp1_joint_attention_data.RData",sep=''))
-d$Condition <- factor(d$Condition, levels = c("con","exp"), labels = c("Control","Video"))
+d$Condition <- factor(d$Condition, levels = c("con","exp"), labels = c("No Video","Activity Video"))
 
@@
 # Total duration of coordinated joint attention.
-cja_time_mod <- lmer(paste("cja_length", model_string), data = lmer_data)
+cja_time_mod <- lmer(paste("cja_length", model_string), data = lmer_data,
+                     control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5)))
 summary(cja_time_mod) # marginal parent education p=.09 - SINGULAR (do stan_glmer)
@@
 
-We fit a mixed-effects linear regression predicting the number of bids for joint attention (JA) as a function of fixed effects of condition, age (scaled and 0-centered), gender, parent's education level, and the subscales of the EPAQ: Early Learning (EL), Affection and Attachment (AA), and Rules and Respect (RR), along with interactions of condition and EL, AA, and RR.
+We fit a mixed-effects linear regression predicting the number of bids for joint attention (JA) as a function of fixed effects of condition, age (centered), gender, parent's education level, and the subscales of the EPAQ: Early Learning (EL), Affection and Attachment (AA), and Rules and Respect (RR), along with interactions of condition and EL, AA, and RR.
 This lme4 model included random intercepts per video. 
-There were significantly more bids for JA in the Video condition (mean: `r round(subset(e1bids_M, Condition=="Video")$mean,2)`, sd: `r round(subset(e1bids_M, Condition=="Video")$sd,2)`) than in the Control condition (mean: `r round(subset(e1bids_M, Condition=="Control")$mean,2)`, sd: `r round(subset(e1bids_M, Condition=="Control")$sd,2)`, $\beta=`r e1bids["ConditionVideo","beta"]`$, t(`r e1bids["ConditionVideo","df"]`) = `r e1bids["ConditionVideo","tval"]`, *p*<.01).
+There were significantly more bids for JA in the Video condition (mean: `r round(subset(e1bids_M, Condition=="Activity Video")$mean,2)`, sd: `r round(subset(e1bids_M, Condition=="Activity Video")$sd,2)`) than in the Control condition (mean: `r round(subset(e1bids_M, Condition=="No Video")$mean,2)`, sd: `r round(subset(e1bids_M, Condition=="No Video")$sd,2)`, $\beta=`r e1bids["ConditionActivity Video","beta"]`$, t(`r e1bids["ConditionActivity Video","df"]`) = `r e1bids["ConditionActivity Video","tval"]`, *p*<.01).
 There were no other significant effects.
@@
 There were no significant effects on the number or total duration of coordinated JA episodes, nor on the total duration of passive JA episodes. 
-For the regression predicting the number of passive JA episodes, the only significant effect was an interaction of condition and RR ($\beta=`r e1pja["ConditionVideo:RR","beta"]`$, t(`r e1pja["ConditionVideo:RR","df"]`) = `r e1pja["ConditionVideo:RR","tval"]`, *p*<.05), showing that for parents in the Video condition, those with higher Rules and Respect subscores engaged in more passive JA episodes.
+For the regression predicting the number of passive JA episodes, the only significant effect was an interaction of condition and RR ($\beta=`r e1pja["ConditionActivity Video:RR","beta"]`$, t(`r e1pja["ConditionActivity Video:RR","df"]`) = `r e1pja["ConditionActivity Video:RR","tval"]`, *p*<.05), showing that for parents in the Video condition, those with higher Rules and Respect subscores engaged in more passive JA episodes.
 Figure \ref{fig:e1ja} shows the mean number bids for JA and episodes of JA by condition in Experiment 1.
 
-```{r fig:e1ja, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.5, fig.height=3.0, set.cap.width=T, num.cols.cap=1, fig.cap = "\\label{fig:e1ja} Mean number of bids (left) and episodes (right) of joint attention (JA) by condition in Experiment 1.
+```{r fig:e1ja, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=5.5, fig.height=3.0, set.cap.width=T, num.cols.cap=1, fig.cap = "\\label{fig:e1ja} Mean number of bids (left) and episodes (right) of joint attention (JA) by condition in Experiment 1.
 Parents made significantly more bids for JA after watching an activity video, but this did not result in a greater number of episodes of JA."}
 
-ms_bids <- d %>% group_by(Condition) %>%
+ms_bids1 <- d %>% group_by(Condition) %>%
   tidyboot_mean(bids_tot)
 
-e1bids <- ggplot(ms_bids, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
+e1bids <- ggplot(ms_bids1, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
   geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
@@
 # total joint attention episodes
-ms_tja <- d %>% group_by(Condition) %>%
+ms_tja1 <- d %>% group_by(Condition) %>%
   tidyboot_mean(total_ja)
 
-e1tja <- ggplot(ms_tja, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
+e1tja <- ggplot(ms_tja1, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
   geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
@@
 multiplot(e1bids, e1tja, cols=2)
-```
-
-```{r fig:e1ja-pass-coord, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.5, fig.height=3.5, set.cap.width=T, num.cols.cap=1, fig.cap = "\\label{fig:e1ja-pass-coord} The mean number of passive (left) and coordinated episodes (right) of JA  in Experiment 1 were similar in both conditions."}
-ms_pja <- d %>% group_by(Condition) %>%
-  tidyboot_mean(pja)
-
-e1pja <- ggplot(ms_pja, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
-  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
-  geom_point(data=d, aes(x=Condition, y=pja), alpha=.2, position = position_jitterdodge()) +
-  xlab("Condition") + ylab("Episodes of Passive Joint Attention") +
-  langcog::scale_fill_solarized() + ggthemes::theme_few() + theme(legend.position="none")
-
-#Episodes of coordinated joint attention
-ms_cja <- d %>% group_by(Condition) %>%
-  tidyboot_mean(cja)
-
-e1cja <- ggplot(ms_cja, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
-  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
-  geom_point(data=d, aes(x=Condition, y=cja), alpha=.2, position = position_jitterdodge()) +
-  xlab("Condition") + ylab("Episodes of Coordinated Joint Attention")  +
-  langcog::scale_fill_solarized() + ggthemes::theme_few() + theme(legend.position="none")
-
-multiplot(e1pja, e1cja, cols=2)
 ```
@@
 
-Experiment 1 found that parents who watched a Kinedu video spoke more words overall, but had lower lexical diversity compared to parents who played with their children as they normally would at home. 
-Parents who watched a Kinedu video also made more bids for joint attention, although these bids did not result in more episodes of joint attention compared to the control group. 
-Experiment 2 attempts to replicate these findings from with a restricted number of preregistered predictions.[^3]
+Experiment 1 found that parents who watched an activity video spoke more words overall, but had lower lexical diversity compared to parents who played with their children as they normally would at home.
+Parents who watched an activity video also made more bids for joint attention, although these bids did not result in more episodes of joint attention compared to the control group. 
+Experiment 2 attempts to replicate these findings from with a restricted number of preregistered predictions.[^4]
 
-[^3]: Preregistration: [https://osf.io/2bpdf/](https://osf.io/2bpdf/).
+[^4]: Preregistration: [https://osf.io/2bpdf/](https://osf.io/2bpdf/).
 
@@
 The videos were trimmed to approximately match the average video length in the Activity Video condition (close to 90 s).
-Details of the Kinedu videos used in the Activity Video conditions are in the Appendix.
+Details of the videos used in the Activity Video conditions are in the Appendix.
 
@@
 
-We fit a mixed-effects linear regression predicting TTR as a function of age (0-centered) and condition with an interaction term, and with random intercepts per video using lme4 [@lme4].
+We fit a mixed-effects linear regression predicting TTR as a function of age (centered) and condition with an interaction term, and with random intercepts per video using lme4 [@lme4].
 There was suggestively lower TTR in the Video condition (mean: `r round(e2_lexdiv[2,]$TTR, 2)`) than in the Control condition (mean: `r round(e2_lexdiv[1,]$TTR, 2)`, $\beta=`r e2TTR["conditionexp","beta"]`$, t(`r e2TTR["conditionexp","df"]`) = `r e2TTR["conditionexp","tval"]`, *p*=`r e2TTR["conditionexp","pval"]`).
@@
 ```{r e2tab, echo=F}
-d$Condition = factor(d$condition, levels = c("con", "exp"), labels = c("Control", "Video"))
+d$Condition = factor(d$condition, levels = c("con", "exp"), labels = c("Science Video", "Activity Video"))
 e2 <- d %>% group_by(Condition) %>%
@@
 
-ms_lex <- d %>% group_by(Condition) %>%
+ttr2 <- d %>% group_by(Condition) %>%
   tidyboot_mean(TTR)
 
-e2ttr <- ggplot(ms_lex, aes(x=Condition, y=mean, fill=Condition)) + geom_bar(stat="identity") + 
+e2ttr <- ggplot(ttr2, aes(x=Condition, y=mean, fill=Condition)) + geom_bar(stat="identity") + 
   geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
@@
 
-ms_lex <- d %>% group_by(Condition) %>%
+mtld2 <- d %>% group_by(Condition) %>%
   tidyboot_mean(MTLD)
 
-e2mtld <- ggplot(ms_lex, aes(x = Condition, y = mean, fill = Condition)) + 
+e2mtld <- ggplot(mtld2, aes(x = Condition, y = mean, fill = Condition)) + 
   geom_bar(stat="identity") + 
@@
 
-ms_tok <- d %>% group_by(Condition) %>%
+ms_tok2 <- d %>% group_by(Condition) %>%
   tidyboot_mean(tokens)
 
-e2tokens <- ggplot(ms_tok, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
+e2tokens <- ggplot(ms_tok2, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
   geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
@@
 
-```{r e2token-type, include=F, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.5, fig.height=3, set.cap.width=T, num.cols.cap=1, fig.cap = "Mean number of word types and word tokens by condition in Experiment 2."}
+```{r e2token-type, include=F, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=5.5, fig.height=3, set.cap.width=T, num.cols.cap=1, fig.cap = "Mean number of word types and word tokens by condition in Experiment 2."}
 
@@
 # triplicate variables: gender.x/y, ethnicity, english, num_lang, parent_ed, Exclude
-d$Condition <- factor(d$condition, levels = c("con","exp"), labels = c("Control","Video"))
+d$Condition <- factor(d$condition, levels = c("con","exp"), labels = c("Science Video","Activity Video"))
 
@@
 # Total number of bids
-bids_mod <- lmer(bids ~ age * Condition + (1 | video), data = e2ja)
+bids_mod <- lmer(bids ~ age * Condition + (1 | video), data = e2ja, 
+                 control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5)))
 summary(bids_mod) # singular fit, convergence code: 0 condition beta=3.11, t(80) = 3.52 p<.001
@@
 
-tja_mod <- lmer(total_ja ~ age * Condition + (1 | video), data = e2ja)
+tja_mod <- lmer(total_ja ~ age * Condition + (1 | video), data = e2ja,
+                control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5)))
 e2tja <- get_lmer_reporting_values(tja_mod)
@@
 
-As preregistered, we fit mixed-effects linear regressions predicting the number of parental bids for joint attention and the total number of episodes of JA as a function of fixed effects of condition, age (0-centered), and their interaction, with random intercepts per video.
-Shown in Figure \ref{fig:e2ja} (left panel), parents made significantly more bids for JA after watching the Activity Video (mean: `r round(subset(e2_bids, Condition=="Video")$mean,2)`, bootstrapped 95% CI: `r round(subset(e2_bids, Condition=="Video")$ci_lower,2)`, `r round(subset(e2_bids, Condition=="Video")$ci_upper,2)`; $\beta=`r e2bids["ConditionVideo","beta"]`$, t(`r e2bids["ConditionVideo","df"]`) = `r e2bids["ConditionVideo","tval"]`, *p*=`r e2bids["ConditionVideo","pval"]`)) than after the Control Video (mean: `r round(subset(e2_bids, Condition=="Control")$mean,2)`, 95% CI: [`r round(subset(e2_bids, Condition=="Control")$ci_lower,2)`, `r round(subset(e2_bids, Condition=="Control")$ci_upper,2)`], $\beta=`r e2bids["ConditionVideo","beta"]`$, t(`r e2bids["ConditionVideo","df"]`) = `r e2bids["ConditionVideo","tval"]`, *p*<.001).
+As preregistered, we fit mixed-effects linear regressions predicting the number of parental bids for joint attention and the total number of episodes of JA as a function of fixed effects of condition, age (centered), and their interaction, with random intercepts per video.
+Shown in Figure \ref{fig:e2ja} (left panel), parents made significantly more bids for JA after watching the Activity Video (mean: `r round(subset(e2_bids, Condition=="Activity Video")$mean,2)`, bootstrapped 95% CI: `r round(subset(e2_bids, Condition=="Activity Video")$ci_lower,2)`, `r round(subset(e2_bids, Condition=="Activity Video")$ci_upper,2)`; $\beta=`r e2bids["ConditionActivity Video","beta"]`$, t(`r e2bids["ConditionActivity Video","df"]`) = `r e2bids["ConditionActivity Video","tval"]`, *p*=`r e2bids["ConditionActivity Video","pval"]`)) than after the Science Video (mean: `r round(subset(e2_bids, Condition=="Science Video")$mean,2)`, 95% CI: [`r round(subset(e2_bids, Condition=="Science Video")$ci_lower,2)`, `r round(subset(e2_bids, Condition=="Science Video")$ci_upper,2)`], $\beta=`r e2bids["ConditionActivity Video","beta"]`$, t(`r e2bids["ConditionActivity Video","df"]`) = `r e2bids["ConditionActivity Video","tval"]`, *p*<.001).
 There were no other significant effects on parental bids for JA.
 
-In the regression predicting the number of episodes of JA, there was a significant main effect of condition ($\beta=`r e2tja["ConditionVideo","beta"]`$, t(`r e2tja["ConditionVideo","df"]`) = `r e2tja["ConditionVideo","tval"]`, *p*=`r e2tja["ConditionVideo","pval"]`), with more episodes of JA occurring after the Activity Video (mean: `r round(subset(e2_tja, Condition=="Video")$mean,2)`, 95% CI: [`r round(subset(e2_tja, Condition=="Video")$ci_lower,2)`, `r round(subset(e2_tja, Condition=="Video")$ci_upper,2)`]) than after the Control Video (mean: `r round(subset(e2_tja, Condition=="Control")$mean,2)`, 95% CI: [`r round(subset(e2_tja, Condition=="Control")$ci_lower,2)`, `r round(subset(e2_tja, Condition=="Control")$ci_upper,2)`]).
+In the regression predicting the number of episodes of JA, there was a significant main effect of condition ($\beta=`r e2tja["ConditionActivity Video","beta"]`$, t(`r e2tja["ConditionActivity Video","df"]`) = `r e2tja["ConditionActivity Video","tval"]`, *p*=`r e2tja["ConditionActivity Video","pval"]`), with more episodes of JA occurring after the Activity Video (mean: `r round(subset(e2_tja, Condition=="Activity Video")$mean,2)`, 95% CI: [`r round(subset(e2_tja, Condition=="Activity Video")$ci_lower,2)`, `r round(subset(e2_tja, Condition=="Activity Video")$ci_upper,2)`]) than after the Control Video (mean: `r round(subset(e2_tja, Condition=="Science Video")$mean,2)`, 95% CI: [`r round(subset(e2_tja, Condition=="Science Video")$ci_lower,2)`, `r round(subset(e2_tja, Condition=="Science Video")$ci_upper,2)`]).
 There was also a significant main effect of age ($\beta=`r e2tja["age","beta"]`$, t(`r e2tja["age","df"]`) = `r e2tja["age","tval"]`, *p*=`r e2tja["age","pval"]`), showing that the number of episodes of JA decreased with the child's age.
-However, a significant interaction of age and condition ($\beta=`r e2tja["age:ConditionVideo","beta"]`$, t(`r e2tja["age:ConditionVideo","df"]`) = `r e2tja["age:ConditionVideo","tval"]`, *p*=`r e2tja["age:ConditionVideo","pval"]`), shown in the right panel of Figure \ref{fig:e2ja}, demonstrates that older children in the Activity Video condition did not see a decrease in the number of episodes of JA.
+However, a significant interaction of age and condition ($\beta=`r e2tja["age:ConditionActivity Video","beta"]`$, t(`r e2tja["age:ConditionActivity Video","df"]`) = `r e2tja["age:ConditionActivity Video","tval"]`, *p*=`r e2tja["age:ConditionActivity Video","pval"]`), shown in the right panel of Figure \ref{fig:e2ja}, demonstrates that older children in the Activity Video condition did not see a decrease in the number of episodes of JA.
 
-```{r fig:e2ja, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=6, fig.height=3.0, set.cap.width=T, num.cols.cap=1, fig.cap = "\\label{fig:e2ja} Mean number of bids for JA by condition (left) and the number of episodes of JA by age and condition (right) in Experiment 2.
+```{r fig:e2ja, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=6.5, fig.height=3.0, set.cap.width=T, num.cols.cap=1, fig.cap = "\\label{fig:e2ja} Mean number of bids for JA by condition (left) and the number of episodes of JA by age and condition (right) in Experiment 2.
 After watching an activity video, parents made more bids for JA.
@@
 # Episodes of coordinated joint attention
-cja_mod <- lmer(cja ~ age * Condition + (1 | video), data = e2ja)
+cja_mod <- lmer(cja ~ age * Condition + (1 | video), data = e2ja,
+                control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5)))
 summary(cja_mod) #  Condition: t(80) = 2.47 beta=1.37 p=.01; age*Condition beta=5.24 t(80) = 2.19 p=.02
@@
 # Total duration of passive joint attention.
-pja_time_mod <- lmer(pja_length ~ age * Condition + (1 | video), data = e2ja)
+pja_time_mod <- lmer(pja_length ~ age * Condition + (1 | video), data = e2ja,
+                     control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5)))
 summary(pja_time_mod) # singular - convergence code: 0, age beta=-18.89 t(80) = 2.72 p=.008
@@
 # Total duration of coordinated joint attention.
-cja_time_mod <- lmer(cja_length ~ age * condition + (1 | video), data = e2ja)
+cja_time_mod <- lmer(cja_length ~ age * condition + (1 | video), data = e2ja,
+                     control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5)))
 summary(cja_time_mod) # singular - convergence code: 0, marginal age: beta=37.35 t(80) = 1.95 p=.05
@@
 Four additional exploratory regressions with a similar structure were carried out to predict the number and duration of coordinated and passive JA episodes.
-The regression predicting the number of episodes of coordinated JA found a significant main effect of condition ($\beta=`r e2cja["ConditionVideo","beta"]`$, t(`r e2cja["ConditionVideo","df"]`) = `r e2cja["ConditionVideo","tval"]`, *p*=`r e2cja["ConditionVideo","pval"]`), with more episodes of coordinated JA occurring after the Activity Video (mean: `r round(subset(e2_cja, Condition=="Video")$mean,2)`, 95% CI: [`r round(subset(e2_cja, Condition=="Video")$ci_lower,2)`, `r round(subset(e2_cja, Condition=="Video")$ci_upper,2)`]) than after the Control Video (mean: `r round(subset(e2_cja, Condition=="Control")$mean,2)`, 95% CI: [`r round(subset(e2_cja, Condition=="Control")$ci_lower,2)`, `r round(subset(e2_cja, Condition=="Control")$ci_upper,2)`]).
-There was no significant effect of age, but there was a significant interaction of age and condition ($\beta=`r e2cja["age:ConditionVideo","beta"]`$, t(`r e2cja["age:ConditionVideo","df"]`) = `r e2cja["age:ConditionVideo","tval"]`, *p*=`r e2cja["age:ConditionVideo","pval"]`), shown in Figure \ref{e2ja-coord}, revealing that older children in the Activity Video condition had more episodes of coordinated JA than children in the Control Video condition.
+The regression predicting the number of episodes of coordinated JA found a significant main effect of condition ($\beta=`r e2cja["ConditionActivity Video","beta"]`$, t(`r e2cja["ConditionActivity Video","df"]`) = `r e2cja["ConditionActivity Video","tval"]`, *p*=`r e2cja["ConditionActivity Video","pval"]`), with more episodes of coordinated JA occurring after the Activity Video (mean: `r round(subset(e2_cja, Condition=="Activity Video")$mean,2)`, 95% CI: [`r round(subset(e2_cja, Condition=="Activity Video")$ci_lower,2)`, `r round(subset(e2_cja, Condition=="Activity Video")$ci_upper,2)`]) than after the Control Video (mean: `r round(subset(e2_cja, Condition=="Science Video")$mean,2)`, 95% CI: [`r round(subset(e2_cja, Condition=="Science Video")$ci_lower,2)`, `r round(subset(e2_cja, Condition=="Science Video")$ci_upper,2)`]).
+There was no significant effect of age, but there was a significant interaction of age and condition ($\beta=`r e2cja["age:ConditionActivity Video","beta"]`$, t(`r e2cja["age:ConditionActivity Video","df"]`) = `r e2cja["age:ConditionActivity Video","tval"]`, *p*=`r e2cja["age:ConditionActivity Video","pval"]`), shown in Figure \ref{fig:e2ja-coord}, revealing that older children in the Activity Video condition had more episodes of coordinated JA than children in the Control Video condition.
 The regression predicting the total duration of coordinated JA episodes revealed no significant effects.
 
-In the regression predicting the number of episodes of passive JA, there was a main effect of age ($\beta=`r e2pja["ConditionVideo","beta"]`$, t(`r e2pja["ConditionVideo","df"]`) = `r e2pja["ConditionVideo","tval"]`, *p*=`r e2pja["ConditionVideo","pval"]`), showing that older children had more episodes of passive JA with their caregiver.
-The regression predicting the total duration of passive JA revealed a main effect of age ($\beta=`r e2pja_time["ConditionVideo","beta"]`$, t(`r e2pja_time["ConditionVideo","df"]`) = `r e2pja_time["ConditionVideo","tval"]`, *p*=`r e2pja_time["ConditionVideo","pval"]`), revealing that older children spent more time in passive JA with their caregiver.
+In the regression predicting the number of episodes of passive JA, there was a main effect of age ($\beta=`r e2pja["ConditionActivity Video","beta"]`$, t(`r e2pja["ConditionActivity Video","df"]`) = `r e2pja["ConditionActivity Video","tval"]`, *p*=`r e2pja["ConditionActivity Video","pval"]`), showing that older children had more episodes of passive JA with their caregiver.
+The regression predicting the total duration of passive JA revealed a main effect of age ($\beta=`r e2pja_time["ConditionActivity Video","beta"]`$, t(`r e2pja_time["ConditionActivity Video","df"]`) = `r e2pja_time["ConditionActivity Video","tval"]`, *p*=`r e2pja_time["ConditionActivity Video","pval"]`), revealing that older children spent more time in passive JA with their caregiver.
 Overall, these results show that the older children in our sample engage in more and longer episodes of joint attention with their caregivers, and suggest that the Activity Video strengthened this trend in the number of episodes of coordinated JA.
 
-```{r e2ja-coord, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=4.5, fig.height=3.5, set.cap.width=T, num.cols.cap=1, fig.cap = "\\label{fig:e2ja-coord} The number of episodes of coordinated JA by condition and age in Experiment 2.
+```{r e2ja-coord, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=5.5, fig.height=3.5, set.cap.width=T, num.cols.cap=1, fig.cap = "\\label{fig:e2ja-coord} The number of episodes of coordinated JA by condition and age in Experiment 2.
 Older children in the Activity Video condition engaged in more episodes of coordinated JA with their caregiver than dyads in the Control Video condition."}
@@
 
-This study investigated how parents change their interactions with their young children on the basis of one of several short video parenting messages from the Kinedu commercial parenting app, which suggest interactive toy-based activities (e.g., learning animal sounds), along with a scientific justification.
+This study investigated how parents change their interactions with their young children on the basis of one of several short video parenting messages from a commercial parenting app, which suggest interactive toy-based activities (e.g., learning animal sounds), along with a scientific justification.
 Parents in the control conditions received either no video (Experiment 1) or a video of a recent finding in developmental psychology (Experiment 2), but played with the same sets of toys given to those in the experimental conditions.

### 2019-08-06 parenting_obs_e2/Lexical_Diversity_Analysis.Rmd
wrapping up results
edits

@@
 d$Condition <- factor(d$condition, levels=c("con","exp"), labels=c("Control","Video"))
-save(d, file="Exp2_cleaned_data.Rdata")
+#save(d, file="Exp2_cleaned_data.Rdata")
 ```
@@
   multi_boot_standard(col = "TTR")
-
-lex_mean_TTR <- d%>%
-  group_by(condition)%>%
-  summarise(mean = mean(TTR), sd = sd(TTR))
 
@@
   multi_boot_standard(col = "MTLD")
-
-lex_mean_MTLD <- d%>%
-  group_by(condition)%>%
-  summarise(mean = mean(MTLD), sd=sd(MTLD))
 

### 2019-08-12 paper/cogsci2019/appendix.Rmd
fighting papaja

--- 2019-07-21 paper/cogsci2019/cogsci2019.Rmd
@@
 ---
-title: "Understanding the impacts of video-guided activities on parent-child interaction"
-author-information: "\\author{ \n  {\\large\\bf George~Kachergis}^1 (\\texttt{kachergis@stanford.edu})
-  \\\\\n  {\\large\\bf Emily~Hembacher}^2 (\\texttt{emily.hembacher@gmail.com}) \\\\\n
-  \ {\\large\\bf Veronica~Cristiano}^2 (\\texttt{CRISTIANO @gallaudet.edu}) \\\\\n
-  \ {\\large\\bf Hanwen Vivian~Zhang}^1 (\\texttt{vivian3@stanford.edu}) \\\\\n  {\\large\\bf
-  Michael C.~Frank}^1 (\\texttt{mcfrank@stanford.edu}) \\\\ \n^{1}Department of Psychology,
-  Stanford University \\\\  Stanford, CA 94305 USA \\\\ ^{2} Nextdoor, Inc., Burlingame,
-  CA \\\\ ^{3} Gallaudet University, Washington, D.C. }\n"
-bibliography: library.bib
-output:
-  pdf_document: default
-  word_document: default
-  html_document:
-    df_print: paged
-document-params: 10pt, letterpaper
-final-submission: \cogscifinalcopy
-header-includes: \usepackage{float}
-keywords: "digital parenting advice; joint attention; lexical diversity; guided play;
-  \n"
-csl: apa6.csl
-abstract: |
-  Early parenting practices play an important role in shaping the future  outcomes of young children [@Hart1995; @Heckman2006].
-In particular, high-quality early interactions and language input appear to  facilitate language learning and result in higher levels of school performance.
-The rise of phone- and tablet-based parenting applications ("apps") holds the promise of delivering  low-cost, positive interventions on parenting style to a wide variety of populations.
-Of special interest are the parents of very young children, who are often difficult to reach in other ways.
-Yet little is known about the effects of communicating to parents through app-based interventions.
-In a study of one commercial app offering a collection of age-appropriate activity videos, we find  that the quality of parent-child interactions increases in some ways as a result of using the app.
-Specifically, the lexical diversity of parents' child-directed speech increases, and measures of  joint attention show...
+title: "Appendix"
+output: pdf_document
 ---
-
-```{r global_options, include=FALSE}
-knitr::opts_chunk$set(fig.width=3, fig.height=3, fig.crop = F, 
-                      fig.pos = "tb", fig.path='figs/',
-                      echo=F, warning=F, cache=F, 
-                      message=F, sanitize = T)
-```
-
-```{r libraries, include=F}
-suppressPackageStartupMessages(c("dplyr","langcog","tidyr","ggplot2","lme4"))
-library(png)
-library(grid)
-library(ggplot2)
-library(xtable)
-library(psych)
-library(langcog)
-library(tidyverse)
-library(ggthemes)
-library(lme4)
-library(lmerTest)
-library(tidyboot)
-library(knitr)
-source("multiplot.R")
-
-select <- dplyr::select # masked by MASS
-theme_set(theme_few())
-```
-
-# Introduction
-
-The quantity and quality of early language input has been found to be strongly associated with later language and academic outcomes [@Hart1995; @Marchman2008; @Cartmill2013; @HirshPasek2015].
-Thus, because of the potential for large downstream effects [@Heckman2006], there is tremendous interest in interventions that change children's language environment.
-And because parents define a large portion of that environment, especially before the onset of formal schooling, parent behavior is a critical locus for such interventions. 
-Many effective parenting interventions require large resource investments and require many hours of in-person contact [@Jamaica2014; @PerryPreschool2004], making implementation at scale a daunting proposition.
-For this reason, many researchers targeting early language are interested in delivering parenting interventions remotely -- through texts, apps, and videos delivered on digital devices. 
-But what do parents take away from these short messages about what to do or how to talk with their children?
-
-The content provided by digital parenting interventions runs the gamut from general parenting messages and facts from child development research to specific advice and suggested activities. 
-A growing body of evidence suggests that these digital interventions can be effective across a range of cultures, income levels, and children's ages [for a review, see @Breitenstein2014].
-For example, in contrast to a face-to-face parent training intervention, a tablet-based version saw significantly higher session completion rates (51% attendance vs.
-85% module completion) and comparable or larger effect sizes on parents' and children's (aged 2 to 5 years) behavior [@Breitenstein2016].
-Often, however, the theory of change presupposed by such interventions is relatively vague.
-Both within and outside the realm of academic interventions, messages to parents of young children often seek to provide knowledge about some aspect of development (e.g., early language), often in tandem with a suggestion regarding activities.
-Such messages are assumed to inform parents' choice of behaviors, spurring them to engage in some target activity, which is assumed to be more stimulating than what parents would have done otherwise.
-
-This theory of change is typically grounded in ideas about guided play and early language stimulation. 
-Child-directed speech varies not only in quantity (i.e., the number of total tokens), but also in quality in terms of the diversity of the tokens [@Malvern2004] or the context-appropriateness of the speech [@Cartmill2013], both of which have been linked to children's subsequent language development.
-Further, language learning -- especially the acquisition of early vocabulary in the first years -- appears to be supported preferentially by parents and children _jointly attending_ to some object or activity [@Baldwin1991; @Bigelow2004].
-Episodes of joint attention are frequent during guided play, when parents set goals and scaffold their child's activities [@Wood1976; @Weisberg2013].
-Thus, the current literature supports interventions that encourage parents to provide high-quality language and interaction through something like guided play -- whether via reading books or playing with a shape-sorter at home, or via a conversation about categories in the supermarket.
-
-But is this theory of change correct? That is, does the provision of knowledge and activities lead to higher-quality play? 
-Alternatively, this theory could be wrong in a number of ways. 
-By focusing parents on a specific activity, parents may over-focus on achieving the superficial goals of the activity. 
-This problem might be especially likely with video messages, which could encourage parents to try to mimic a model's specific speech and/or actions.
-Attempting to reproduce such surface details of a video-guided activity could in turn result in less high-quality talk, with less responsiveness to their child's play.
-Another possibility is that these messages do produce the desired effect, but only for those parents who already have a general orientation towards children's early learning.
-
-Our current experiments were designed to make a direct test of this question: How do parents change their interactions with young children on the basis of short video parenting messages? 
-In two experiments, we collected data from parent-child dyads in a local children's museum. 
-We showed parents in the experimental group a single short video modeling an interactive toy-based activity along with a scientific justification. 
-Parents in the control group received either no video (Experiment 1) or a video of a recent finding in developmental psychology (Experiment 2). 
-We then gave the toys from the video to all dyads and videotaped their interactions, coding for language quantity and quality as well as joint attention.
-
-# Experiment 1
-
-In Experiment 1, we invited parents of 6- to 24-month-old infants visiting the Children's Discovery Museum in San Jose to complete video-guided activities from Kinedu (Kinedu Inc.), a parenting app that delivers digital parenting advice in the form of short videos.
-Parents were randomly assigned to the video condition or the control condition; parents in the _video_ condition watched a video from the Kinedu app (matched to their child's age), and then performed the activity with their child using the props from the video.
-Parents in the _control_ condition did not watch a Kinedu video, but were given a set of the same age-appropriate props and asked to play with their infants as they normally would at home.
-
-## Method
-
-```{r, include=F}
-e1path = "../../parenting_obs_e1/"
-load(paste(e1path,"Exp1_cleaned_data.RData",sep='')) # merged dataframe ready for plotting
-
-lmer_data <- d %>%
-  #filter(!is.na(AA), !is.na(EL), !is.na(RR))%>%
-  mutate(condition = factor(condition), 
-         MTLD = as.numeric(MTLD),
-         EL = as.numeric(langcog::scale(EL, scale=FALSE)),
-         AA = as.numeric(langcog::scale(AA, scale=FALSE)),
-         RR = as.numeric(langcog::scale(RR, scale=FALSE)),
-         age = as.numeric(langcog::scale(age, scale=FALSE)),
-         gender = as.factor(gender),
-         video = as.factor(video))
-
-e1_gender = table(d$gender)
-#table(cut_interval(d$age, n=2, breaks=c(.5,1.5,2.1), labels=F))
-#table(cut_number(d$age, n=3, breaks=c(.5,1.5,2.1)))
-e1_parent_ed = table(d$parent_ed)
-```
-
-### Participants. 
-`r nrow(d)` infants (F = `r e1_gender['F']`, M = `r e1_gender['M']`) aged 6-24 months (20 6-11.9 month-olds, 20 12-17.9 month-olds, and 20 18-24 month-olds) and their parents participated in a museum in northern California.
-We included infants who were exposed to English at least 50 percent of the time (n = 58) or who were exposed less but whose participating parent reported that they primarily speak English with their child at home (n = 2).
-62% of participants (n = 37) had been exposed to two or more languages, as indicated by their parent. 
-Parents identified their children as White (n = 25), Asian (n = 11), African American/Black (n = 2), Biracial (n = 12), other (n = 5), or declined to state (n = 5). 
-Fifteen parents reported that their child was of Hispanic origin. 
-Parents tended to be highly-educated, with reports of highest level of education ranging from completed high school (n = `r e1_parent_ed[1]`), some college (n = `r e1_parent_ed[2]`), four-year college (n = `r e1_parent_ed[3]`), some graduate school (n = `r e1_parent_ed[4]`), to completed graduate school (n = `r e1_parent_ed[5]`).
-
-### Materials.
-Stimuli included videos from the Kinedu commercial parenting application. 
-The videos were designed to show activities to parents that they could perform with their child in order to foster cognitive and physical development, and were targeted to the child's age and level of development.
-In each video, an adult and child perform the activity (e.g., sorting toys according to size) while a narrator explains the activity and its purpose. 
-We selected two videos for each of three age groups in our sample (6-11.9 months, 12-17.9 months, 18-23.94 months). 
-Participants were also given a set of toys corresponding to those in the video that they watched so that they could complete the activity.[^1]
-
-[^1]: Details of the specific videos used and the toys associated with each video are in the Appendix.
-
-Participants were randomly assigned to either the *Video* condition or the *Control* condition. 
-Parents participating in the Video condition were assigned to watch one of the two activity videos available for their child's age group, while parents in the Control condition watched no activity video, and were simply asked to play with their child as they normally would.
-The Control condition was yoked to the Video condition such that for every participant in the Video condition who saw a particular video and received the associated props, a participant in the Control condition received the same props but did not watch the activity video.
-Parents also completed the Early Parenting Attitudes Questionnaire [EPAQ; @Hembacher2018]. 
-The EPAQ measures parents' attitudes about parenting and child development along three dimensions: rules and respect, early learning, and affection and attachment.
-
-### Procedure.
-After providing informed consent, parents in the Video condition watched the assigned activity video on a laptop with headphones.
-To ensure that parents could give the video their full attention, the experimenter played with the infant with a set of toys (different from the experimental props used in the study) while the video was being played.
-Immediately following the video, each parent-child dyad was provided with the props to complete the video-guided activity that the parent had viewed. 
-The toys were placed on a large foam play mat, and parents were instructed to sit on the mat with their child and re-create the activity they had viewed for a period of three minutes.
-In the Control condition, after informed consent parents were told to play with their child as they would at home with the provided props for a period of three minutes. 
-They were not given any additional instructions about how to use the props.
-
-In both conditions, two video cameras were used to record the play session from different angles, and parents were fitted with a wireless Shurre lavalier microphone to record their child-directed speech.
-After three minutes of play had elapsed, parents were told they could stop playing and the cameras and microphone were turned off.
-Parents were then asked to complete the EPAQ before being debriefed.
-
-### Joint Attention Coding Procedure.
-The video of each session was manually coded for episodes of joint attention (JA) using the Datavyu software [@datavyu]. 
-The video taken at floor level was coded by default, but the other video was referred to if the participants were not visible or if there was technical difficulty with the first camera. 
-Each session's video was coded for episodes of coordinated JA, episodes of passive JA, and parental bids for JA. 
-Parental bids for JA were defined as any attempt to initiate joint attention (i.e labeling, pointing, or otherwise drawing attention to an object) that did not result in passive or coordinated JA. 
-If more than 3 seconds elapsed between bids, they were coded as separate attempts. 
-An episode of joint attention was considered _passive_ if both participants visually focused on an object for 3 or more seconds but the child did not acknowledge the parent. 
-If either participant looked away from the object for less than 3 seconds and then returned to the same object it was considered part of the same episode of joint attention. 
-A joint attention episode was considered _coordinated_ if both participants visually focused on an object for 3 or more seconds and at some point in the interaction the child indicated awareness of interaction with some overt behavior toward the parent such as looking at their face, gesturing, vocalizing, or turn-taking.
-Full details of our guidelines for coding joint attention are available [here](https://docs.google.com/document/d/1cZrT_Gjt6p0om19lXO-XcFnT09pb0giyhRQ-Pm1yoBU/edit?usp=sharing).
-
-A second coder independently coded a third of the videos (i.e., 20 of the 60 videos, approximately equally distributed across ages) to establish reliability. 
-The two coders had a reliability of ICC = 0.80 with 95% confident interval (CI) = [0.57,0.92] for number of parent bids for JA; ICC = 0.20 with 95% CI = [-0.26,0.58] for number of passive JA episodes; ICC = 0.66 with 95% CI = [0.32,0.85] for number of coordinated JA episodes; ICC = 0.24 with 95% CI = [-0.21,0.61] for total duration of passive JA episodes, and ICC = 0.62 with 95% CI = [0.27,0.83] for total duration of coordinated JA episodes.
-
-## Results
-
-Parents' child-directed speech during the play sessions was transcribed.
-The transcripts and hand-coded joint attention data were analyzed according to our preregistration[^2], with any deviations or extensions noted.
-Below we first report the lexical diversity results, followed by the joint attention results.
-
-[^2]: Preregistration: [https://osf.io/2bpdf/](https://osf.io/2bpdf/)]
-
-### Lexical Diversity
-
-For each transcript, the words were lemmatized using ``spacy2`` [@spacy2], and the word *types* (unique words) and *tokens* (total words) were then tallied and the type-token ratio (TTR) calculated as a measure of lexical diversity.
-Although TTR was our preregistered measure of lexical diversity as it has commonly been used, it has been noted that TTR is correlated with the length of a text, which has led to the development of new measures such as the measure of textual lexical diversity [MTLD; @McCarthy2010].
-Thus, we also measure lexical diversity with MTLD, which is calculated as the mean length of sequential word strings in a text that maintain a given TTR value (here we use the value proposed by @McCarthy2010: 0.720).
-
-```{r, e1-lexdiv-regressions, echo=F, include=F}
-get_lmer_reporting_values <- function(lmer.fit, digits=2) {
-  sm <- summary(lmer.fit)
-  Vcov <- vcov(lmer.fit, useScale = FALSE)
-  beta <- round(fixef(lmer.fit), digits)
-  se <- round(sqrt(diag(Vcov)), digits)
-  zval <- round(beta / se, digits)
-  pvalEst <- round(2 * pnorm(abs(zval), lower.tail = FALSE), 3)
-  pval <- round(sm$coefficients[,"Pr(>|t|)"], 3)
-  tval <- abs(round(sm$coefficients[,"t value"], digits))
-  df <- round(sm$coefficients[,"df"], 1)
-  return(cbind(beta, se, zval, tval, pval, pvalEst, df))
-}
-
-require("lmerTest")
-# Predicting lexical diversity based on experimental condition, PAQ, demographics. 
-modTTR <- lmer(TTR ~ condition + age + gender + parent_ed + (1|video), data=lmer_data)
-summary(modTTR) # condition:Exp -0.113 t(52.4) = 4.22 p<.001
-e1TTR = get_lmer_reporting_values(modTTR)
-
-modMTLD <- lmer(MTLD ~ condition + age + gender + parent_ed + (1|video), data=lmer_data)
-summary(modMTLD) # condition -8.73 t(55) = 2.67 p=.001 !! singular fit
-e1MTLD = get_lmer_reporting_values(modMTLD)
-# Bayesian regression (stan_glmer in rstanarm) shows the same:
-require("rstanarm")
-bmodMTLD <- stan_glmer(MTLD ~ condition + age + gender + parent_ed + (1|video), data=lmer_data)
-summary(bmodMTLD) # condition mean=-8.6 sd=3.2 95% CI = [-14.9,-2.3]
-
-# predict word tokens
-tokens_mod <- lmer(tokens ~ condition*EL + condition*AA + condition*RR + age + gender + parent_ed + (1|video),  data=lmer_data) # only 54 parents completed the EPAQ
-summary(tokens_mod) # condition 56.02 t(40.4) = 2.30 p<.05
-e1tokens = get_lmer_reporting_values(tokens_mod)
-
-# predict word types
-types_mod <- lmer(types ~ condition*EL + condition*AA + condition*RR  + age + gender + parent_ed + (1|video), data=lmer_data) # !! singular fit
-summary(types_mod) # nothing (hint: conditionexp:AA beta=19.04 p=.11)
-e1types = get_lmer_reporting_values(types_mod) 
-# verify with Bayesian regression:
-bmod_types <- stan_glmer(types ~ condition*EL + condition*AA + condition*RR  + age + gender + parent_ed + (1|video), data=lmer_data)
-summary(bmod_types) # nothing
-
-e1_lexdiv <- lmer_data %>% group_by(condition) %>%
-  summarise(TTR=mean(TTR), MTLD=mean(MTLD), tokens=mean(tokens)) 
-```
-
-We fit a mixed-effects linear regression predicting TTR as a function of condition, age (0-centered), gender, and parent's education level with a random intercept per video using lme4 [@lme4]. 
-There was significantly lower TTR in the Video condition (mean: `r round(subset(e1_lexdiv, condition=='exp')$TTR, 2)`) than in the Control condition (mean: `r round(subset(e1_lexdiv, condition=='con')$TTR, 2)`, $\beta=$`r e1TTR["conditionexp","beta"]`, t(52.4) = `r e1TTR["conditionexp","tval"]`, *p*<.001).
-There were no significant effects of age, gender, or parent's level of education.
-A similar mixed-effects linear regression instead predicting MTLD also found significantly lower lexical diversity in the Video condition (mean MTLD: `r round(subset(e1_lexdiv, condition=='exp')$MTLD, 2)`) than in the Control condition (mean: `r round(subset(e1_lexdiv, condition=='exp')$TTR, 2)`, $\beta=$`r e1MTLD["conditionexp","beta"]`, t(55) = `r e1MTLD["conditionexp","tval"]`, *p*=.001), with no other significant effects.
-Figure \ref{fig:e1lex_div} shows the mean of each lexical diversity measure (TTR and MTLD) by condition.
-
-```{r e1tokens, echo=F, include=F}
-d$Condition = factor(d$condition, levels = c("con", "exp"), labels = c("Control", "Video"))
-
-ms_lex_mtld <- d %>% group_by(Condition) %>%
-  tidyboot_mean(MTLD) 
-ms_lex <- d %>% group_by(Condition) %>%
-  tidyboot_mean(TTR) # Type/Token Ratio
-ms_tok <- d %>% group_by(Condition) %>%
-  tidyboot_mean(tokens) 
-ms_type <- d %>% group_by(Condition) %>%
-  tidyboot_mean(types)
-```
-
-We also conducted similar regressions predicting the number of word tokens and types, finding only a significant effect of condition on the number of word tokens ($\beta= `r e1tokens["conditionexp","beta"]`$, t(40.4)=`r e1tokens["conditionexp","tval"]`, *p*<.05), with parents using more words in the Video condition (mean: `r round(subset(e1_lexdiv, condition=='exp')$tokens, 0)`, bootstrapped 95% confidence intervals (CI): [`r round(subset(ms_tok, Condition=="Video")$ci_lower, 0)`,`r round(subset(ms_tok, Condition=="Video")$ci_upper, 0)`]) than in the Control condition (mean: `r round(subset(e1_lexdiv, condition=='con')$tokens, 0)`, bootstrapped 95% CI: [`r round(subset(ms_tok, Condition=="Control")$ci_lower, 0)`,`r round(subset(ms_tok, Condition=="Control")$ci_upper, 0)`]).
-The means of the lexical diversity measures are reported in Table \ref{e1tab}.
-
-```{r e1tab, echo=FALSE}
-e1 <- d %>% group_by(Condition) %>%
-  summarise("Mean TTR"=mean(TTR), TTRsd=sd(TTR),
-            "Mean MTLD"=mean(MTLD), MTLDsd=sd(MTLD),
-            "Mean types"=mean(types), types.sd=sd(types),
-            "Mean tokens"= mean(tokens), tokens.sd=sd(tokens))
-names(e1) = c("Condition","TTR (M)", "(sd)", "MTLD (M)", "(sd)", "Types (M)", "(sd)", "Tokens (M)", "(sd)")
-kable(e1, digits=2, caption="\\label{e1tab} Lexical diversity measures in Experiment 1.")
-```
-
-```{r fig:e1lex_div, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.5, fig.height=3.0, set.cap.width=T, num.cols.cap=1, fig.cap = "\\label{fig:e1lex_div} Mean lexical diversity scores by condition (left: Type/Token ratio, right: MTLD) in Experiment 1.
-Both measures of lexical diversity were significantly lower after watching an activity video.
-Error bars show bootstrapped 95\\% confidence intervals (CIs), and gray dots indicate values for each participant."}
-
-e1ttr <- ggplot(ms_lex, aes(x=Condition, y=mean, fill=Condition)) + geom_bar(stat="identity") + 
-  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .7)) +
-  geom_point(data=d, aes(x=Condition, y=TTR), alpha=.2, position = position_jitterdodge()) +
-  xlab("Condition") + ylab("Type/Token Ratio (TTR)") +
-  langcog::scale_fill_solarized() + ggthemes::theme_few() +
-  theme(legend.position="none")
-
-e1mtld <- ggplot(ms_lex_mtld, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
-  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
-  geom_point(data=d, aes(x=Condition, y=MTLD), alpha=.2, position = position_jitterdodge()) +
-  xlab("Condition") + ylab("MTLD") +
-  langcog::scale_fill_solarized() + ggthemes::theme_few() + 
-  theme(legend.position="none")
-
-multiplot(e1ttr, e1mtld, cols=2)
-```
-
-Word tokens and word types
-
-```{r e1token_type, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.5, fig.height=3.0, set.cap.width=T, num.cols.cap=1, fig.cap = "Mean number of word tokens (left) and word types (right) by condition in Experiment 1.
-Parents used significantly more word tokens after watching an activity video.
-Error bars show bootstrapped 95\\% CIs."}
-
-e1tokens <- ggplot(ms_tok, aes(x=Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
-  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
-  geom_point(data=d, aes(x=Condition, y=tokens), alpha=.2, position = position_jitterdodge()) +
-  xlab("Condition") + ylab("Total Number of Word Tokens") +
-  langcog::scale_fill_solarized() + ggthemes::theme_few() +
-  theme(legend.position="none")
-
-e1types <- ggplot(ms_type, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
-  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
-  geom_point(data=d, aes(x=Condition, y=types), alpha=.2, position = position_jitterdodge()) +
-  xlab("Condition") + ylab("Total Number of Word Types") +
-  langcog::scale_fill_solarized() + ggthemes::theme_few() +
-  theme(legend.position="none")
-
-multiplot(e1tokens, e1types, cols=2)
-```
-
-```{r, e1-effect-size, echo=F, include=F}
-cohens_d <- function(dat) {
-  return( diff(dat$mean) / (sqrt(sum(dat$sd^2)) / 2) )
-}
-
-ttr_means <- d %>% group_by(Condition) %>%
-  summarise(mean = mean(TTR), sd = sd(TTR))
-cohens_d(ttr_means) # -1.68 - should we report this?
-```
-
-### Joint Attention
-
-```{r, e1ja-regressions, echo=F, include=F}
-load(paste(e1path,"joint_attention/Exp1_joint_attention_data.RData",sep=''))
-d$Condition <- factor(d$Condition, levels = c("con","exp"), labels = c("Control","Video"))
-
-lmer_data <- d %>%
-  filter(!is.na(AA), !is.na(EL), !is.na(RR)) %>%
-  mutate(Condition = factor(Condition), 
-         bids_tot = as.numeric(bids_tot),
-         EL = as.numeric(langcog::scale(EL, scale=FALSE)),
-         AA = as.numeric(langcog::scale(AA, scale=FALSE)),
-         RR = as.numeric(langcog::scale(RR, scale=FALSE)),
-         age = as.numeric(langcog::scale(age, scale=FALSE)),
-         gender = as.factor(gender),
-         Video = as.factor(Video))
-
-model_string =  "~ Condition * EL + Condition * AA + Condition * RR  + age + gender + parent_ed + (1| Video)"
-
-# Total number of bids
-bids_mod <- lmer(paste("bids_tot", model_string), data = lmer_data)
-summary(bids_mod) # condition beta = 3.51, t(40.3) = 2.95 p<.01, gender p=.05 ?
-e1bids = get_lmer_reporting_values(bids_mod)
-
-e1bids_M <- lmer_data %>% group_by(Condition) %>% 
-  summarise(mean = mean(bids), sd = sd(bids))
-
-# Episodes of coordinated joint attention.
-cja_mod <- lmer(paste("cja", model_string), data = lmer_data)
-summary(cja_mod) # NA
-
-# Episodes of passive joint attention.
-pja_mod <- lmer(paste("pja", model_string), data = lmer_data)
-summary(pja_mod) # marginal RR, beta=-1.07 p=.07, condition*RR beta=1.83 p<.05 t(41.5)=2.22
-e1pja = get_lmer_reporting_values(pja_mod)
-
-# Total duration of passive joint attention.
-pja_time_mod <- lmer(paste("pja_length", model_string), data = lmer_data)
-summary(pja_time_mod) # NA
-
-# Total duration of coordinated joint attention.
-cja_time_mod <- lmer(paste("cja_length", model_string), data = lmer_data)
-summary(cja_time_mod) # marginal parent education p=.09 - SINGULAR (do stan_glmer)
-```
-
-We fit a mixed-effects linear regression predicting the number of bids for joint attention (JA) as a function of fixed effects of condition, age (scaled and 0-centered), gender, parent's education level, and the subscales of the EPAQ: Early Learning (EL), Affection and Attachment (AA), and Rules and Respect (RR), along with interactions of condition and EL, AA, and RR.
-This lme4 model included random intercepts per video. 
-There were significantly more bids for JA in the Video condition (mean: `r round(subset(e1bids_M, Condition=="Video")$mean,2)`, sd: `r round(subset(e1bids_M, Condition=="Video")$sd,2)`) than in the Control condition (mean: `r round(subset(e1bids_M, Condition=="Control")$mean,2)`, sd: `r round(subset(e1bids_M, Condition=="Control")$sd,2)`, $\beta=`r e1bids["ConditionVideo","beta"]`$, t(`r e1bids["ConditionVideo","df"]`) = `r e1bids["ConditionVideo","tval"]`, *p*<.01).
-There were no other significant effects.
-
-Mixed-effects regressions with the same structure were performed predicting the number of episodes of coordinated and passive JA, and the total duration of time spent in coordinated and passive JA.
-There were no significant effects on the number or total duration of coordinated JA episodes, nor on the total duration of passive JA episodes. 
-For the regression predicting the number of passive JA episodes, the only significant effect was an interaction of condition and RR ($\beta=`r e1pja["ConditionVideo:RR","beta"]`$, t(`r e1pja["ConditionVideo:RR","df"]`) = `r e1pja["ConditionVideo:RR","tval"]`, *p*<.05), showing that for parents in the Video condition, those with higher Rules and Respect subscores engaged in more passive JA episodes.
-Figure \ref{fig:e1ja} shows the mean number bids for JA and episodes of JA by condition in Experiment 1.
-
-```{r fig:e1ja, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.5, fig.height=3.0, set.cap.width=T, num.cols.cap=1, fig.cap = "\\label{fig:e1ja} Mean number of bids (left) and episodes (right) of joint attention (JA) by condition in Experiment 1.
-Parents made significantly more bids for JA after watching an activity video, but this did not result in a greater number of episodes of JA."}
-
-ms_bids <- d %>% group_by(Condition) %>%
-  tidyboot_mean(bids_tot)
-
-e1bids <- ggplot(ms_bids, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
-  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
-  geom_point(data=d, aes(x=Condition, y=bids_tot), alpha=.2, position = position_jitterdodge()) +
-  xlab("Condition") + ylab("Mean Bids for Joint Attention") +
-  langcog::scale_fill_solarized() + ggthemes::theme_few() + 
-  theme(legend.position="none")
-
-# total joint attention episodes
-ms_tja <- d %>% group_by(Condition) %>%
-  tidyboot_mean(total_ja)
-
-e1tja <- ggplot(ms_tja, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
-  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
-  geom_point(data=d, aes(x=Condition, y=total_ja), alpha=.2, position = position_jitterdodge()) +
-  xlab("Condition") + ylab("Mean Episodes of Joint Attention") +
-  langcog::scale_fill_solarized() + ggthemes::theme_few() + 
-  theme(legend.position="none")
-
-multiplot(e1bids, e1tja, cols=2)
-```
-
-```{r fig:e1ja-pass-coord, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.5, fig.height=3.5, set.cap.width=T, num.cols.cap=1, fig.cap = "\\label{fig:e1ja-pass-coord} Mean number of passive (left) and coordinated episodes (right) of JA by condition in Experiment 1."}
-ms_pja <- d %>% group_by(Condition) %>%
-  tidyboot_mean(pja)
-
-e1pja <- ggplot(ms_pja, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
-  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
-  geom_point(data=d, aes(x=Condition, y=pja), alpha=.2, position = position_jitterdodge()) +
-  xlab("Condition") + ylab("Episodes of Passive Joint Attention") +
-  langcog::scale_fill_solarized() + ggthemes::theme_few() + theme(legend.position="none")
-
-#Episodes of coordinated joint attention
-ms_cja <- d %>% group_by(Condition) %>%
-  tidyboot_mean(cja)
-
-e1cja <- ggplot(ms_cja, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
-  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
-  geom_point(data=d, aes(x=Condition, y=cja), alpha=.2, position = position_jitterdodge()) +
-  xlab("Condition") + ylab("Episodes of Coordinated Joint Attention")  +
-  langcog::scale_fill_solarized() + ggthemes::theme_few() + theme(legend.position="none")
-
-multiplot(e1pja, e1cja, cols=2)
-```
-
-## Discussion
-
-In summary, while parents produced more word types and tokens after viewing the activity video, lexical diversity (both TTR and MTLD) was higher when parents were just asked to play as they normally would.
-It may be that parents in the Video condition, in their attempt to stick to the prescribed task, end up repeating themselves more.
-Demographics and EPAQ do not interact with condition, although there was a marginal effect of RR score on lexical diversity (lower diversity for higher RR scores), and marginal effects of parent education on word types and tokens (more types and tokens for higher parent education).
-
-Compared to parents in the Control condition, parents who watched an activity video made significantly more bids for JA with their child, although this did not result in a greater number of successful episodes of JA than dyads in the Control condition.
-No differences in the duration or number of episodes of passive or coordinated JA between conditions were found.
-
-There was a marginal effect of gender on bids for JA, with parents of males producing more bids. 
-There was an interaction between RR scores and condition on passive JA, such that Video condition increased the number of episodes of passive JA to a greater extent for people with high RR scores.
-While the electronically-delivered parenting advice increased the number of bids for JA by parents, it did not significantly affect the number or duration of episodes of JA. 
-It may be that children had a larger relative impact on the attainment of joint attention.
-
-# Experiment 2
-
-Experiment 1 found that parents who watched a Kinedu video spoke more words overall, but had lower lexical diversity compared to parents who played with their children as they normally would at home. 
-Parents who watched a Kinedu video also made more bids for joint attention, although these bids did not result in more episodes of joint attention compared to the control group. 
-Experiment 2 attempts to replicate these findings from with a restricted number of preregistered predictions.[^3]
-
-[^3]: Preregistration: [https://osf.io/2bpdf/](https://osf.io/2bpdf/).
-
-## Method
-
-```{r, echo=F}
-e2path = "../../parenting_obs_e2/"
-load(paste(e2path,"Exp2_cleaned_data.RData",sep=''))
-
-lmer_data <- d %>%
-  mutate(condition = factor(condition), 
-         MTLD = as.numeric(MTLD),
-         TTR = as.numeric(TTR),
-         age = as.numeric(langcog::scale(age, scale=FALSE)),
-         video = as.factor(video))
-
-e2_gender = table(d$gender)
-e2_ethnicity = table(d$ethnicity)
-e2_parent_ed = table(d$parent_ed)
-e2_12to18 = nrow(subset(d, age<1.5))
-e2_18to24 = nrow(subset(d, age>=1.5))
-```
-
-### Participants. 
-`r nrow(d)` infants (F = `r e2_gender['F']`, M = `r e2_gender['M']`) aged 12-24 months (`r e2_12to18` 12-17.9 month-olds, `r e2_18to24` 18-24 month-olds) and their parents participated in the same museum as Experiment 1.
-We included infants who were exposed to English at least 75 percent of the time or who were exposed less but whose participating parent reported that they primarily speak English with their child at home.
-Forty-nine percent of participants (n = 41) had been exposed to two or more languages as indicated by their parent. 
-Parents identified their children as White (n = 39), Asian (n = 20), African American/Black (n = 1), Biracial (n = 9), other (n = 7), or declined to state (n = 8).
-Sixteen parents reported their child was of Hispanic origin.
-Parents tended to be highly-educated, with reports of highest level of education ranging from some college (n = `r e2_parent_ed[3]`), four-year college (n = `r e2_parent_ed[4]`), some graduate school (n = `r e2_parent_ed[5]`), to completed graduate school (n = `r e2_parent_ed[6]`) or declined to state (n = 13).
-
-### Materials.
-
-The design of Experiment 2 was similar to that of Experiment 1, except that instead of No Video control condition, parents instead watched a video that was generally related to child development research, but did not give any specific instructions about how to interact with infants or children.
-This condition was included to control for the possibility that differences in language output and joint attention in Experiment 1 could be due to simply cueing parents to think about infants' learning and cognitive development.
-The videos presented in the Control Video condition were media clips (available on YouTube) of developmental psychologists explaining their research interleaved with footage of infants or toddlers engaged in developmental research studies.
-Thus, the content of the videos superficially matched those in the Activity Video condition, but did not suggest any particular activities.
-The videos were trimmed to approximately match the average video length in the Activity Video condition (close to 90 s).
-Details of the Kinedu videos used in the Activity Video conditions are in the Appendix.
-
-### Procedure. 
-The procedure for Experiment 2 matched that of Experiment 1, except that parents in the Control Video condition watched a control video before the play session. 
-Consistent with the No-Video control condition in Experiment 1, parents in the Control Video condition were told to play with their child as they would at home, and were not given additional instructions.
-The coding procedure also matched that of Experiment 1. 
-A second coder independently coded a third of the videos (i.e., 26 of the 84 videos, approximately equally distributed across ages) to establish reliability. 
-The two coders had a reliability of ICC = 0.80 with 95% confidence interval (CI) = [0.60,0.90] for number of parent bids for JA; ICC = 0.74 with 95% CI = [0.59,0.87] for number of passive JA episodes; ICC = 0.78 with 95% CI = [0.58,0.90] for number of coordinated JA episodes; ICC = 0.72 with 95% CI = [0.46,0.86] for total duration of passive JA episodes, and ICC = 0.88 with 95% CI = [0.75,0.94] for total duration of coordinated JA episodes.
-
-## Results
-
-Parents' child-directed speech was transcribed and processed, and bids and episodes of joint attention were coded according to the same procedure used in Experiment 1.
-We first report reregistered regressions predicting TTR and number of tokens, as well as an exploratory regression predicting MTLD.
-We then turn to preregistered regressions of parental bids for joint attention and the total number of JA episodes.
-As noted in the preregistration, we adopt an alpha level of .005 for statistical significance and will report alphas between .05 and .005 as suggestive.
-
-### Lexical Diversity
-```{r, e2-lexdiv-regressions, echo=F, include=F}
-# preregistered analyses:
-# The number of parent bids for joint attention, the number of episodes of joint attention, the number of word tokens produced by parents, and the lexical diversity of parent language output (word types/word tokens).
-# 1) bids, 2) total JA eps, 3) # tokens 4) TTR -- alpha level = .005
-# Mixed-effects linear regressions predicting the dependent variables with condition (video scaffolding vs.
-control) and age in months as fixed effects and participant and specific video as random effects.
-# DV ~ age * condition + (1 | participant) + (1 | video)
-# Lab standard operating procedures will be used for random effects pruning in case of non-convergence.
-# We will interpret condition main effects as well as age * condition interactions (positive or negative) as evidence for behavior changes caused by video scaffolding. 
-# Because of the larger number of coefficients of interest (4 models x 2 coefficients), we will adopt an alpha level of .005 for statistical significance and will report alpha between .05 and .005 as suggestive.
-# “secondary analyses"
-# We will analyze the proportion of coordinated vs. passive joint attention separately using the same model specification.
-
-# Notes: 
-# - including (1|sid) never works: "Error: number of levels of each grouping factor must be < number of observations", so we back off to (1|video)
-# Predicting lexical diversity based on experimental condition. 
-modTTR <- lmer(TTR ~ age * condition + (1 | video), data=lmer_data) 
-summary(modTTR) # condition beta=-.09  t(8.6) = 3.33 p=.009 (suggestive)
-e2TTR <- get_lmer_reporting_values(modTTR)
-
-# predict word tokens
-tokens_mod <- lmer(tokens ~ age * condition + (1 | video), data=lmer_data)
-summary(tokens_mod) # NA
-
-modMTLD <- lmer(MTLD ~ age * condition + (1 | video), data=lmer_data)
-summary(modMTLD) # NA
-
-e2_lexdiv <- lmer_data %>% group_by(condition) %>%
-  summarise(TTR=mean(TTR), MTLD=mean(MTLD), tokens=mean(tokens)) 
-# predict word types (NOT A PREREGISTERED REGRESSION)
-#types_mod <- lmer(types ~ age * condition + (1 | video), data=lmer_data)
-#summary(types_mod) # NA
-```
-
-We fit a mixed-effects linear regression predicting TTR as a function of age (0-centered) and condition with an interaction term, and with random intercepts per video using lme4 [@lme4].
-There was suggestively lower TTR in the Video condition (mean: `r round(e2_lexdiv[2,]$TTR, 2)`) than in the Control condition (mean: `r round(e2_lexdiv[1,]$TTR, 2)`, $\beta=`r e2TTR["conditionexp","beta"]`$, t(`r e2TTR["conditionexp","df"]`) = `r e2TTR["conditionexp","tval"]`, *p*=`r e2TTR["conditionexp","pval"]`).
-There was no significant effect of age, nor a significant interaction.
-The preregistered regression predicting the number of tokens used by parents revealed no significant effects. 
-An exploratory mixed-effects linear regression predicting MTLD found no significant effects of age or condition.
-Figure \ref{fig:e2lexdiv} shows the mean of each lexical diversity measure (TTR and MTLD) by condition.
-Regressions with the same structure predicting the number of words tokens found no significant effects of age or condition.
-The means of the lexical measures are shown in Table \ref{e2tab}.
-
-```{r e2tab, echo=F}
-d$Condition = factor(d$condition, levels = c("con", "exp"), labels = c("Control", "Video"))
-e2 <- d %>% group_by(Condition) %>%
-  summarise("Mean TTR"=mean(TTR), TTRsd=sd(TTR),
-            "Mean MTLD"=mean(MTLD), MTLDsd=sd(MTLD),
-            "Mean types"=mean(types), types.sd=sd(types),
-            "Mean tokens"= mean(tokens), tokens.sd=sd(tokens))
-names(e2) = c("Condition","TTR (M)", "(sd)", "MTLD (M)", "(sd)", "Types (M)", "(sd)", "Tokens (M)", "(sd)")
-kable(e2, digits=2, caption="\\label{e2tab} Lexical diversity measures in Experiment 2.")
-```
-
-```{r fig:e2lexdiv, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=5.5, fig.height=3, set.cap.width=T, num.cols.cap=1, fig.cap = "\\label{fig:e2lexdiv} Mean lexical diversity scores by condition (left: Type/Token ratio, middle: MTLD, right: word tokens) in Experiment 2."}
-
-ms_lex <- d %>% group_by(Condition) %>%
-  tidyboot_mean(TTR)
-
-e2ttr <- ggplot(ms_lex, aes(x=Condition, y=mean, fill=Condition)) + geom_bar(stat="identity") + 
-  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
-  geom_point(data=d, aes(x=Condition, y=TTR), alpha=.2, position = position_jitterdodge()) +
-  xlab("Condition") + ylab("TTR") +
-  langcog::scale_fill_solarized() + ggthemes::theme_few() +
-  theme(legend.position="none")
-
-ms_lex <- d %>% group_by(Condition) %>%
-  tidyboot_mean(MTLD)
-
-e2mtld <- ggplot(ms_lex, aes(x = Condition, y = mean, fill = Condition)) + 
-  geom_bar(stat="identity") + 
-  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
-  geom_point(data=d, aes(x=Condition, y=MTLD), alpha=.2, position = position_jitterdodge()) +
-  xlab("Condition") + ylab("MTLD") +
-  langcog::scale_fill_solarized() + ggthemes::theme_few() +
-  theme(legend.position="none")
-
-ms_tok <- d %>% group_by(Condition) %>%
-  tidyboot_mean(tokens)
-
-e2tokens <- ggplot(ms_tok, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
-  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
-  geom_point(data=d, aes(x=Condition, y=tokens), alpha=.2, position = position_jitterdodge()) +
-  xlab("Condition") + ylab("Total Number of Word Tokens") +
-  langcog::scale_fill_solarized() + ggthemes::theme_few() +
-  theme(legend.position="none")
-
-multiplot(e2ttr, e2mtld, e2tokens, cols=3)
-```
-
-```{r e2token-type, include=F, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.5, fig.height=3, set.cap.width=T, num.cols.cap=1, fig.cap = "Mean number of word types and word tokens by condition in Experiment 2."}
-
-ms_typ <- d %>% group_by(Condition) %>%
-  tidyboot_mean(types)
-
-e2types <- ggplot(ms_typ, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
-  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
-  geom_point(data=d, aes(x=Condition, y=types), alpha=.2, position = position_jitterdodge()) +
-  xlab("Condition") + ylab("Total Number of Word Types") +
-  langcog::scale_fill_solarized() + ggthemes::theme_few() +
-  theme(legend.position="none")
-
-#multiplot(e2tokens, e2types, cols=2)
-```
-
-```{r, e2-effect-size, echo=F, include=F}
-ttr_means <- d %>% group_by(Condition) %>%
-  summarise(mean = mean(TTR), sd = sd(TTR))
-cohens_d(ttr_means)
-```
-
-### Joint Attention
-```{r, e2ja-regressions, echo=F, include=F}
-load(paste(e2path,"joint_attention/Exp2_joint_attention_data.RData",sep=''))
-summary(d)
-# triplicate variables: gender.x/y, ethnicity, english, num_lang, parent_ed, Exclude
-d$Condition <- factor(d$condition, levels = c("con","exp"), labels = c("Control","Video"))
-
-e2ja <- d %>% mutate(bids = bids_tot,
-                     age = as.numeric(langcog::scale(age, scale=FALSE)),
-                     pja_length = pja_length/1000,
-                     cja_length = cja_length/1000,
-                     total_lja = total_lja/1000)
-
-# Total number of bids
-bids_mod <- lmer(bids ~ age * Condition + (1 | video), data = e2ja)
-summary(bids_mod) # singular fit, convergence code: 0 condition beta=3.11, t(80) = 3.52 p<.001
-e2bids <- get_lmer_reporting_values(bids_mod)
-bids_bmod <- stan_glmer(bids ~ age * Condition + (1|video), data=e2ja)
-summary(bids_bmod) # significant effect of condition! mean=3.1, 95%CI = [1.1, 5.0]
-
-tja_mod <- lmer(total_ja ~ age * Condition + (1 | video), data = e2ja)
-e2tja <- get_lmer_reporting_values(tja_mod)
-summary(tja_mod) # singular fit, convergence code: 0
-#                    Estimate Std. Error      df t value  Pr(>|t|) 
-# (Intercept)          7.2912     0.3898 80.0000  18.704  < 2e-16 ***
-# age                 -5.2687     1.5122 80.0000  -3.484 0.000804 ***
-# ConditionVideo       1.4893     0.5513 80.0000   2.701 0.008428 ** 
-# age:ConditionVideo   5.9189     2.2721 80.0000   2.605 0.010950 *
-
-tja_bmod <- stan_glmer(total_ja ~ age * Condition + (1|video), data=e2ja)
-summary(tja_bmod) # total episodes of joint attention -- age, age*condition, condition
-#                                        mean    sd     2.5%   25%    50%    75%    97.5%
-# (Intercept)                             7.3    0.4    6.4    7.0    7.3    7.6    8.2 
-# age                                    -5.0    1.7   -8.2   -6.1   -5.0   -3.9   -1.6 
-# ConditionVideo                          1.5    0.6    0.3    1.1    1.5    1.9    2.8 
-# age:ConditionVideo                      5.6    2.5    0.7    3.9    5.7    7.4   10.5
-
-e2_bids <- e2ja %>% group_by(Condition) %>%
-  tidyboot_mean(bids)
-e2_tja <- e2ja %>% group_by(Condition) %>%
-  tidyboot_mean(total_ja)
-
-```
-
-As preregistered, we fit mixed-effects linear regressions predicting the number of parental bids for joint attention and the total number of episodes of JA as a function of fixed effects of condition, age (0-centered), and their interaction, with random intercepts per video.
-Shown in Figure \ref{fig:e2ja} (left panel), parents made significantly more bids for JA after watching the Activity Video (mean: `r round(subset(e2_bids, Condition=="Video")$mean,2)`, bootstrapped 95% CI: `r round(subset(e2_bids, Condition=="Video")$ci_lower,2)`, `r round(subset(e2_bids, Condition=="Video")$ci_upper,2)`; $\beta=`r e2bids["ConditionVideo","beta"]`$, t(`r e2bids["ConditionVideo","df"]`) = `r e2bids["ConditionVideo","tval"]`, *p*=`r e2bids["ConditionVideo","pval"]`)) than after the Control Video (mean: `r round(subset(e2_bids, Condition=="Control")$mean,2)`, 95% CI: `r round(subset(e2_bids, Condition=="Control")$ci_lower,2)`, `r round(subset(e2_bids, Condition=="Control")$ci_upper,2)`, $\beta=`r e2bids["ConditionVideo","beta"]`$, t(`r e2bids["ConditionVideo","df"]`) = `r e2bids["ConditionVideo","tval"]`, *p*<.001).
-There were no other significant effects on parental bids for JA.
-
-In the regression predicting the number of episodes of JA, there was a significant main effect of condition ($\beta=`r e2tja["ConditionVideo","beta"]`$, t(`r e2tja["ConditionVideo","df"]`) = `r e2tja["ConditionVideo","tval"]`, *p*=`r e2tja["ConditionVideo","pval"]`), with more episodes of JA occurring after the Activity Video (mean: `r round(subset(e2_tja, Condition=="Video")$mean,2)`, 95% CI: `r round(subset(e2_tja, Condition=="Video")$ci_lower,2)`, `r round(subset(e2_tja, Condition=="Video")$ci_upper,2)`) than after the Control Video (mean: `r round(subset(e2_tja, Condition=="Control")$mean,2)`, 95% CI: `r round(subset(e2_tja, Condition=="Control")$ci_lower,2)`, `r round(subset(e2_tja, Condition=="Control")$ci_upper,2)`).
-There was also a significant main effect of age ($\beta=`r e2tja["age","beta"]`$, t(`r e2tja["age","df"]`) = `r e2tja["age","tval"]`, *p*=`r e2tja["age","pval"]`), showing that the number of episodes of JA decreased with the child's age.
-However, a significant interaction of age and condition ($\beta=`r e2tja["age:ConditionVideo","beta"]`$, t(`r e2tja["age:ConditionVideo","df"]`) = `r e2tja["age:ConditionVideo","tval"]`, *p*=`r e2tja["age:ConditionVideo","pval"]`), shown in the right panel of Figure \ref{fig:e2ja}, demonstrates that older children in the Activity Video condition did not see a decrease in the number of episodes of JA.
-
-```{r fig:e2ja, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=6, fig.height=3.0, set.cap.width=T, num.cols.cap=1, fig.cap = "\\label{fig:e2ja} Mean number of bids for JA by condition (left) and the number of episodes of JA by age and condition (right) in Experiment 2.
-After watching an activity video, parents made more bids for JA.
-Older children in the Activity Video condition showed no decrease in the number of episodes of JA, unlike children in the Control Video condition."}
-
-e2bids <- ggplot(e2_bids, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
-  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
-  geom_point(data=e2ja, aes(x=Condition, y=bids), alpha=.2, position = position_jitterdodge()) +
-  xlab("Condition") + ylab("Total Bids for Joint Attention") +
-  langcog::scale_fill_solarized() + ggthemes::theme_few() + 
-  theme(legend.position="none")
-
-# total JA episodes
-e2tja <- ggplot(e2_tja, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
-  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
-  geom_point(data=e2ja, aes(x=Condition, y=total_ja), alpha=.2, position = position_jitterdodge()) +
-  xlab("Condition") + ylab("Total Episodes of Joint Attention") +
-  langcog::scale_fill_solarized() + ggthemes::theme_few() + 
-  theme(legend.position="none")
-
-e2tja_age = ggplot(d, aes(x = age, y = total_ja, group=Condition, colour = Condition)) +
-  geom_point(alpha=.7) + geom_smooth(method='lm') + 
-  xlab("Age (years)") + ylab("Total Episodes of Joint Attention") +
-  langcog::scale_colour_solarized() +
-  ggthemes::theme_few()
-
-multiplot(e2bids, e2tja_age, cols=4, layout=matrix(c(1,2,2,2), nrow=1))
-```
-
-```{r e2ja-exploratory, echo=F, include=F}
-# EXPLORATORY ANALYSES (NOT PREREGISTERED)
-
-# Episodes of coordinated joint attention
-cja_mod <- lmer(cja ~ age * Condition + (1 | video), data = e2ja)
-summary(cja_mod) #  Condition: t(80) = 2.47 beta=1.37 p=.01; age*Condition beta=5.24 t(80) = 2.19 p=.02
-e2cja <- get_lmer_reporting_values(cja_mod)
-# also singular fit, convergence code: 0 - Bayesian regression confirms:
-cja_bmod <- stan_glmer(cja ~ age * Condition + (1|video), data=e2ja)
-summary(cja_bmod) # age n.s., sig effect of condition: mean=1.3 95% CI=[.1,2.6]; age*condition mean=5.1 CI=[.5,9.6]
-#                                        mean    sd     2.5%   25%    50%    75%    97.5%
-# (Intercept)                             5.3    0.4    4.5    5.0    5.3    5.6    6.2 
-# age                                    -2.0    1.4   -4.8   -2.9   -2.0   -1.1    0.9 
-# ConditionVideo                          1.3    0.6    0.1    0.9    1.3    1.7    2.6 
-# age:ConditionVideo                      5.1    2.3    0.5    3.5    5.1    6.5    9.6
-
-# Episodes of passive joint attention.
-pja_mod <- lmer(pja ~ age * Condition + (1 | video), data = e2ja)
-summary(pja_mod) # age beta=-2.88 t(13.4) = 2.53 p=.02
-e2pja <- get_lmer_reporting_values(pja_mod)
-
-# Total duration of passive joint attention.
-pja_time_mod <- lmer(pja_length ~ age * Condition + (1 | video), data = e2ja)
-summary(pja_time_mod) # singular - convergence code: 0, age beta=-18.89 t(80) = 2.72 p=.008
-e2pja_time <- get_lmer_reporting_values(pja_time_mod)
-pjat_bmod <- stan_glmer(pja_length ~ age * Condition + (1|video), data=e2ja)
-summary(pjat_bmod) # age: est: -17.9 95% CI = [-33.1,-2.2]
-
-# Total duration of coordinated joint attention.
-cja_time_mod <- lmer(cja_length ~ age * condition + (1 | video), data = e2ja)
-summary(cja_time_mod) # singular - convergence code: 0, marginal age: beta=37.35 t(80) = 1.95 p=.05
-cjat_bmod <- stan_glmer(cja_length ~ age * Condition + (1|video), data=e2ja)
-summary(cjat_bmod) # age: est: 35.3 95% CI = [-6.1,77.4] NOT SIGNIFICANT
-
-e2_cja <- e2ja %>% group_by(Condition) %>%
-  tidyboot_mean(cja)
-```
-
-### Exploratory Analyses
-
-Four additional exploratory regressions with a similar structure were carried out to predict the number and duration of coordinated and passive JA episodes.
-The regression predicting the number of episodes of coordinated JA found a significant main effect of condition ($\beta=`r e2cja["ConditionVideo","beta"]`$, t(`r e2cja["ConditionVideo","df"]`) = `r e2cja["ConditionVideo","tval"]`, *p*=`r e2cja["ConditionVideo","pval"]`), with more episodes of coordinated JA occurring after the Activity Video (mean: `r round(subset(e2_cja, Condition=="Video")$mean,2)`, 95% CI: `r round(subset(e2_cja, Condition=="Video")$ci_lower,2)`, `r round(subset(e2_cja, Condition=="Video")$ci_upper,2)`) than after the Control Video (mean: `r round(subset(e2_cja, Condition=="Control")$mean,2)`, 95% CI: `r round(subset(e2_cja, Condition=="Control")$ci_lower,2)`, `r round(subset(e2_cja, Condition=="Control")$ci_upper,2)`).
-There was no significant effect of age, but there was a significant interaction of age and condition ($\beta=`r e2cja["age:ConditionVideo","beta"]`$, t(`r e2cja["age:ConditionVideo","df"]`) = `r e2cja["age:ConditionVideo","tval"]`, *p*=`r e2cja["age:ConditionVideo","pval"]`), shown in Figure \ref{e2ja-coord}, revealing that older children in the Activity Video condition had more episodes of coordinated JA than children in the Control Video condition.
-The regression predicting the total duration of coordinated JA episodes revealed no significant effects.
-
-In the regression predicting the number of episodes of passive JA, there was a main effect of age ($\beta=`r e2pja["ConditionVideo","beta"]`$, t(`r e2pja["ConditionVideo","df"]`) = `r e2pja["ConditionVideo","tval"]`, *p*=`r e2pja["ConditionVideo","pval"]`), showing that older children had more episodes of passive JA with their caregiver.
-The regression predicting the total duration of passive JA revealed a main effect of age ($\beta=`r e2pja_time["ConditionVideo","beta"]`$, t(`r e2pja_time["ConditionVideo","df"]`) = `r e2pja_time["ConditionVideo","tval"]`, *p*=`r e2pja_time["ConditionVideo","pval"]`), revealing that older children spent more time in passive JA with their caregiver.
-Overall, these results show that the older children in our sample engage in more and longer episodes of joint attention with their caregivers, and suggest that the Activity Video strengthened this trend in the number of episodes of coordinated JA.
-
-```{r e2ja-coord, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=4.5, fig.height=3.5, set.cap.width=T, num.cols.cap=1, fig.cap = "\\label{fig:e2ja-coord} The number of episodes of coordinated JA by condition and age in Experiment 2.
-Older children in the Activity Video condition engaged in more episodes of coordinated JA with their caregiver than dyads in the Control Video condition."}
-
-#Episodes of coordinated joint attention
-ms_cja <- d %>% group_by(Condition) %>%
-  tidyboot_mean(cja)
-
-e2cja <- ggplot(ms_cja, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
-  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
-  geom_point(data=d, aes(x=Condition, y=cja), alpha=.2, position = position_jitterdodge()) +
-  xlab("Condition") + ylab("Episodes of Coordinated JA") +
-  langcog::scale_fill_solarized() + ggthemes::theme_few() + theme(legend.position="none")
-
-e2cja_age = ggplot(d, aes(x = age, y = cja, group=Condition, colour = Condition)) +
-  geom_point(alpha=.7) + geom_smooth(method='lm') + 
-  xlab("Age (years)") + ylab("Episodes of Coordinated JA") +
-  langcog::scale_colour_solarized() + ggthemes::theme_few()
-
-print(e2cja_age)
-#multiplot(e2cja, e2tja_age, cols=4, layout=matrix(c(1,2,2,2), nrow=1))
-```
-
-# Discussion
-
-In both experiments, the number of tokens was higher in the experimental condition, while the number of types and lexical diversity (Type/Token ratio) were higher in the control condition. 
-Parents may be relatively more repetetive in the experimental condition since they are attempting to stick to a specific prescribed task, but they talk more overall.
-
-# Acknowledgements
-
-This work was supported by a gift from Kinedu, Inc. 
-Thanks to members of the Language and Cognition Lab at Stanford for helpful discussion.
-
-# References
-
-```{r}
-# References will be generated automatically by Pandoc and included here.
-# The following code is some latex to format the bibliography. Do not remove it.
-```
-
-\setlength{\parindent}{-0.1in} 
-\setlength{\leftskip}{0.125in}
-\noindent
 

### 2019-08-12 paper/cogsci2019/manuscript.Rmd
fighting papaja

--- 2019-08-06 paper/cogsci2019/cogsci2019.Rmd
@@
 ---
-title: "Understanding the impacts of video-guided activities on parent-child interaction"
-author-information: "\\author{ \n  {\\large\\bf George~Kachergis}^1 (\\texttt{kachergis@stanford.edu})
-  \\\\\n  {\\large\\bf Emily~Hembacher}^2 (\\texttt{emily.hembacher@gmail.com}) \\\\\n
-  \ {\\large\\bf Veronica~Cristiano}^2 (\\texttt{CRISTIANO @gallaudet.edu}) \\\\\n
-  \ {\\large\\bf Hanwen Vivian~Zhang}^1 (\\texttt{vivian3@stanford.edu}) \\\\\n  {\\large\\bf
-  Michael C.~Frank}^1 (\\texttt{mcfrank@stanford.edu}) \\\\ \n^{1}Department of Psychology,
-  Stanford University \\\\  Stanford, CA 94305 USA \\\\ ^{2} Nextdoor, Inc., Burlingame,
-  CA \\\\ ^{3} Gallaudet University, Washington, D.C. }\n"
-bibliography: library.bib
-output:
-  pdf_document: default
-  word_document: default
-  html_document:
-    df_print: paged
-document-params: 10pt, letterpaper
-final-submission: \cogscifinalcopy
-header-includes: \usepackage{float}
-keywords: "digital parenting advice; joint attention; lexical diversity; guided play;
-  \n"
-csl: apa6.csl
+title             : "Understanding the impacts of video-guided activities on parent-child interaction"
+shorttitle        : "Impacts of videos on parent-child interaction"
+
+author: 
+  - name          : "George Kachergis"
+    affiliation   : "1"
+    corresponding : yes    # Define only one corresponding author
+    address       : "Stanford, CA 94305 USA"
+    email         : "kachergis@stanford.edu"
+  - name          : "Emily Hembacher"
+    affiliation   : "2"
+  - name          : "Veronica Cristiano"
+    affiliation   : "3"
+  - name          : "Hanwen Vivian Zhang"
+    affiliation   : "4"
+  - name          : "Michael C. Frank"
+    corresponding : yes
+    address       : "Stanford, CA 94305 USA"
+    email         : "mcfrank@stanford.edu"
+    affiliation   : "1"
+
+affiliation:
+  - id            : "1"
+    institution   : "Department of Psychology, Stanford University"
+  - id            : "2"
+    institution   : "Nextdoor, Inc."
+  - id            : "3"
+    insitution    : "Gallaudet University"
+  - id            : "4"
+    insitution    : "Cornell University"
+
+authornote: |
+  blah
+  blahblah
 abstract: |
@@
   Specifically, after watching the activity video, parents spoke more and made more bids for joint attention with the child.
+keywords          : "digital parenting advice; joint attention; lexical diversity; guided play"
+wordcount         : "4510"
+
+bibliography      : ["library.bib"]
+
+floatsintext      : yes
+figurelist        : no
+tablelist         : no
+footnotelist      : no
+linenumbers       : yes
+mask              : no
+draft             : no
+header-includes:
+  - \usepackage{float}
+documentclass     : "apa6"
+csl: apa6.csl
+classoption       : "man"
+output            : papaja::apa6_pdf
 ---
@@
                       fig.pos = "tb", fig.path='figs/',
-                      echo=F, warning=F, cache=F, 
+                      echo=F, warning=F, cache=T, 
                       message=F, sanitize = T)
@@
 
-```{r libraries, include=F}
+```{r setup, include = FALSE}
 suppressPackageStartupMessages(c("dplyr","langcog","tidyr","ggplot2","lme4"))
+library("papaja")
 library(png)
@@
 }
+```
+
+```{r analysis-preferences}
+# Seed for random number generation
+set.seed(42)
+knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
 ```
@@
 We also conducted similar regressions predicting the number of word tokens and types, finding only a significant effect of condition on the number of word tokens ($\beta= `r e1tokens["conditionexp","beta"]`$, t(40.4)=`r e1tokens["conditionexp","tval"]`, *p*<.05), with parents using more words in the Video condition (mean: `r round(subset(e1_lexdiv, condition=='exp')$tokens, 0)`, bootstrapped 95% confidence intervals (CI): [`r round(subset(ms_tok, Condition=="Activity Video")$ci_lower, 0)`,`r round(subset(ms_tok, Condition=="Activity Video")$ci_upper, 0)`]) than in the Control condition (mean: `r round(subset(e1_lexdiv, condition=='con')$tokens, 0)`, bootstrapped 95% CI: [`r round(subset(ms_tok, Condition=="No Video")$ci_lower, 0)`,`r round(subset(ms_tok, Condition=="No Video")$ci_upper, 0)`]).
-The means of the lexical diversity measures are reported in Table \ref{e1tab}.
+The means of the lexical diversity measures are reported in Table \ref{tab:e1tab}.
 
@@
 names(e1) = c("Condition","TTR (M)", "(sd)", "MTLD (M)", "(sd)", "Types (M)", "(sd)", "Tokens (M)", "(sd)")
-kable(e1, digits=2, caption="\\label{e1tab} Lexical diversity measures in Experiment 1.")
+kable(e1, digits=2, caption="Lexical diversity measures in Experiment 1.")
 ```
 
-```{r fig:e1lex_div, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=7, fig.height=3.0, set.cap.width=T, num.cols.cap=1, fig.cap = "\\label{fig:e1lex_div} Mean lexical diversity scores by condition (left: Type/Token ratio, right: MTLD) in Experiment 1.
-Both measures of lexical diversity were significantly lower after watching an activity video.
-Error bars show bootstrapped 95\\% confidence intervals (CIs), and gray dots indicate values for each participant."}
-
+```{r hiddenfigs, include=F}
 e1ttr <- ggplot(ms_lex, aes(x=Condition, y=mean, fill=Condition)) + geom_bar(stat="identity") + 
@@
   theme(legend.position="none")
+
+```
+
+```{r fig:e1lex_div, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=7, fig.height=3.0, fig.cap = "Mean lexical diversity scores by condition (left: Type/Token ratio, right: MTLD) in Experiment 1.
+Both measures of lexical diversity were significantly lower after watching an activity video.
+Error bars show bootstrapped 95\\% confidence intervals (CIs), and gray dots indicate values for each participant."}
 
@@
 For the regression predicting the number of passive JA episodes, the only significant effect was an interaction of condition and RR ($\beta=`r e1pja["ConditionActivity Video:RR","beta"]`$, t(`r e1pja["ConditionActivity Video:RR","df"]`) = `r e1pja["ConditionActivity Video:RR","tval"]`, *p*<.05), showing that for parents in the Video condition, those with higher Rules and Respect subscores engaged in more passive JA episodes.
-Figure \ref{fig:e1ja} shows the mean number bids for JA and episodes of JA by condition in Experiment 1.
+Figure \@ref(fig:e1ja) shows the mean number bids for JA and episodes of JA by condition in Experiment 1.
 
-```{r fig:e1ja, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=5.5, fig.height=3.0, set.cap.width=T, num.cols.cap=1, fig.cap = "\\label{fig:e1ja} Mean number of bids (left) and episodes (right) of joint attention (JA) by condition in Experiment 1.
+```{r e1ja, fig.cap = "Mean number of bids (left) and episodes (right) of joint attention (JA) by condition in Experiment 1.
 Parents made significantly more bids for JA after watching an activity video, but this did not result in a greater number of episodes of JA."}
+# fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=5.5, fig.height=3.0, f
 
@@
 
-```{r fig:e2lexdiv, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=5.5, fig.height=3, set.cap.width=T, num.cols.cap=1, fig.cap = "\\label{fig:e2lexdiv} Mean lexical diversity scores by condition (left: Type/Token ratio, middle: MTLD, right: word tokens) in Experiment 2."}
+```{r fig:e2lexdiv, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=6.5, fig.height=3, fig.cap = "\\label{fig:e2lexdiv} Mean lexical diversity scores by condition (left: Type/Token ratio, middle: MTLD, right: word tokens) in Experiment 2."}
 
@@
 
-e2ttr <- ggplot(ttr2, aes(x=Condition, y=mean, fill=Condition)) + geom_bar(stat="identity") + 
+e2ttr <- ggplot(ttr2, aes(x=Condition, y=mean, fill=Condition)) + geom_bar(stat="identity") + # labels=addline_format(c("Science Video", "Activity Video"))
   geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
@@
 
-```{r e2token-type, include=F, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=5.5, fig.height=3, set.cap.width=T, num.cols.cap=1, fig.cap = "Mean number of word types and word tokens by condition in Experiment 2."}
+```{r e2token-type, include=F}
 
@@
 
-```{r fig:e2ja, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=6.5, fig.height=3.0, set.cap.width=T, num.cols.cap=1, fig.cap = "\\label{fig:e2ja} Mean number of bids for JA by condition (left) and the number of episodes of JA by age and condition (right) in Experiment 2.
+```{r fig:e2ja, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=6.5, fig.height=3.0, fig.cap = "\\label{fig:e2ja} Mean number of bids for JA by condition (left) and the number of episodes of JA by age and condition (right) in Experiment 2.
 After watching an activity video, parents made more bids for JA.
@@
 
-multiplot(e2bids, e2tja_age, cols=4, layout=matrix(c(1,2,2,2), nrow=1))
+multiplot(e2bids, e2tja_age, cols=5, layout=matrix(c(1,1,2,2,2), nrow=1))
 ```
@@
 
-```{r e2ja-coord, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=5.5, fig.height=3.5, set.cap.width=T, num.cols.cap=1, fig.cap = "\\label{fig:e2ja-coord} The number of episodes of coordinated JA by condition and age in Experiment 2.
+```{r e2ja-coord, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=5.5, fig.height=3.5, fig.cap = "\\label{fig:e2ja-coord} The number of episodes of coordinated JA by condition and age in Experiment 2.
 Older children in the Activity Video condition engaged in more episodes of coordinated JA with their caregiver than dyads in the Control Video condition."}
@@
 Experiment 2 had similar lexical diversity results, finding suggestively lower Type-Token Ratio after the activity video, although the length-corrected lexical diversity measure (MTLD) did not differ significantly.
-However, the number of tokens did not significantly differ betwen condition in Experiment 2. [nor types -- exploratory regression]
-Overall, although it may seem worrisome that the activity videos lead to somewhat lower lexical diversity, this worry is  mitigated by the fact that this difference is explained not by fewer word types but by a greater number of word tokens used by parents after the activity video (significantly in Experiment 1, and numerically in Experiment 2).
+However, neither the number of tokens nor the number of types significantly differed betwen conditions in Experiment 2. 
+Although it may at first blush seem worrisome that the activity videos lead to somewhat lower lexical diversity, this worry is  mitigated by the fact that this difference is explained not by fewer word types but by a greater number of word tokens used by parents after the activity video (significantly in Experiment 1, and numerically in Experiment 2).
 It may be that parents are relatively more repetitive after watching the activity video in their attempt to stick to the prescribed task, but overall they talk more.
@@
 Taken together, the results of this study show that digital parenting interventions recommending particular play activities to parents of young children can influence both the quality and quantity of child-directed speech, as well as parents attempts to engage their children in joint attention---at least in the short term.
-[more limitations / recommendations for extensions]
-What do these results imply for a theory of change?
+Future studies should investigate whether these changes in parents' speech and attempts to engage their children continue after the treatment. 
+Another target for future study is to determine whether, over a longer treatment period, children begin to respond to the increased bids for joint attention and greater number of tokens by engaging more with their parent, and perhaps even beginning to play differently.
 
@@
 
+\newpage
+
 # References
-
-```{r}
-# References will be generated automatically by Pandoc and included here.
-# The following code is some latex to format the bibliography. Do not remove it.
+```{r create_r-references}
+r_refs(file = "library.bib")
 ```
 
-\setlength{\parindent}{-0.1in} 
-\setlength{\leftskip}{0.125in}
-\noindent
+\begingroup
+\setlength{\parindent}{-0.5in}
+\setlength{\leftskip}{0.5in}
 
-# Appendix
-
-## Experiment 1
-
-### Video A (6-11.9 months) "Pick it up"
-
-Parents are told to encourage their child to pick up and drop individual objects.
-They are also encouraged to place toys on a small cloth and show the child that they can drag the cloth towards them to reach the toys.
-
-Props: cloth, plastic horse, plastic sheep, plastic elephant, toy car
-
-### Video B (6-11.9 months) "Animal sounds"
-
-Parents are told to call different animals and imitate different sounds the animals make. They are also encourgaed to observe which animal the child prefers.
-
-Props: plastic sheep, plastic horse, plastic frog, plastic cow, bowls
-
-### Video C (12-17.9 months) "Give me the toy"
-
-Parents are told to ask their child to hand over individual toys.
-They are also encouraged to praise the child after they give them the toys, and repeat the process until the child could follow the verbal instructions.
-
-Props: toy boat, plastic frog, plastic elephant, toy bus
-
-### Video D (12-17.9 months) "Classifying my toys"
-
-Parents are told to place toys of different sizes (big or small) in two hoops. They are also encouraged to ask their child to distinguish between two objects and identify which one is larger.
-
-Props: two yellow and green rings, big car, small car, big horse, small horse
-
-### Video E (18-23.9 months) "My toys"
-
-Parents are told to show the child toys of the same shape but different sizes, to place one of the objects in a basket and to ask the child to take out the object.
-They are also encouraged to ask their child if the object is bigger or smaller compared to its pair.
-
-Props: two buckets, big car, small car, big horse, small horse
-
-### Video F (18-23.9 months) "The Orchestra"
-
-Parents are told to give their child a musical instrument to play. They are also encouraged to play a song and see if the child follows the rhythm.
-
-Props: maracas, drum, tambourine, clapper
-
-## Experiment 2
-
-### Video A (12-17.9 months) "Give me the toy"
-
-Parents are told to ask their child to hand over individual toys.
-They are also encouraged to praise the child after they give them the toys, and repeat the process until the child could follow the verbal instructions.
-
-Props: plastic pig, plastic horse, plastic dog, plastic cat, plastic cow
-
-### Video B (12-17.9 months) "Classifying my toys"
-
-Parents are told to place toys of different sizes (big or small) in two hoops. They are also encouraged to ask their child to distinguish between two objects and identify which one is larger.
-
-Props: two yellow and green rings, big car, small car, big horse, small horse
-
-### Video C (12-17.9 months) "Geometric shapes jigzsaw puzzle"
-
-Parents are told to encourage their child to name different shapes on a jigzsaw puzzle. Then they are told to undo the puzzle and invite the child to complete the puzzle.
-
-Props: A jigzsaw puzzle of geometric shapes
-
-### Video D (18-23.9 months) "My toys"
-
-Parents are told to show the child toys of the same shape but different sizes, to place one of the objects in a basket and to ask the child to take out the object.
-They are also encouraged to ask their child if the object is bigger or smaller compared to its pair.
-
-Props: two buckets, big car, small car, big horse, small horse
-
-### Video E (18-23.9 months) "The Orchestra"
-
-Parents are told to give their child a musical instrument to play. They are also encouraged to play a song and see if the child follows the rhythm.
-
-Props: maracas, drum, tambourine, clapper
-
-### Video F (18-23.9 months) "My Yellow Toys"
-
-Parents are told to show their child yellow toys and to ask, "What color are they?" They are also told to give the child toys of different colors, to ask them to only play with the yellow ones, and to praise the child after they do so.
-
-Props: blue car, yellow car, yellow block, red block, blue block, green block
+<div id = "refs"></div>
+\endgroup

### 2019-08-12 paper/cogsci2019/manuscript.tex
fighting papaja

--- 2019-08-12 paper/cogsci2019/manuscript.Rmd
@@
----
-title             : "Understanding the impacts of video-guided activities on parent-child interaction"
-shorttitle        : "Impacts of videos on parent-child interaction"
+\documentclass[man,floatsintext]{apa6}
+\usepackage{lmodern}
+\usepackage{amssymb,amsmath}
+\usepackage{ifxetex,ifluatex}
+\usepackage{fixltx2e} % provides \textsubscript
+\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
+  \usepackage[T1]{fontenc}
+  \usepackage[utf8]{inputenc}
+\else % if luatex or xelatex
+  \ifxetex
+    \usepackage{mathspec}
+  \else
+    \usepackage{fontspec}
+  \fi
+  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
+\fi
+% use upquote if available, for straight quotes in verbatim environments
+\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
+% use microtype if available
+\IfFileExists{microtype.sty}{%
+\usepackage{microtype}
+\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
+}{}
+\usepackage{hyperref}
+\hypersetup{unicode=true,
+            pdftitle={Understanding the impacts of video-guided activities on parent-child interaction},
+            pdfauthor={George Kachergis, Emily Hembacher, Veronica Cristiano, Hanwen Vivian Zhang, \& Michael C. Frank},
+            pdfkeywords={digital parenting advice; joint attention; lexical diversity; guided play},
+            pdfborder={0 0 0},
+            breaklinks=true}
+\urlstyle{same}  % don't use monospace font for urls
+\usepackage{graphicx,grffile}
+\makeatletter
+\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
+\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
+\makeatother
+% Scale images if necessary, so that they will not overflow the page
+% margins by default, and it is still possible to overwrite the defaults
+% using explicit options in \includegraphics[width, height, ...]{}
+\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
+\IfFileExists{parskip.sty}{%
+\usepackage{parskip}
+}{% else
+\setlength{\parindent}{0pt}
+\setlength{\parskip}{6pt plus 2pt minus 1pt}
+}
+\setlength{\emergencystretch}{3em}  % prevent overfull lines
+\providecommand{\tightlist}{%
+  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
+\setcounter{secnumdepth}{0}
+% Redefines (sub)paragraphs to behave more like sections
+\ifx\paragraph\undefined\else
+\let\oldparagraph\paragraph
+\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
+\fi
+\ifx\subparagraph\undefined\else
+\let\oldsubparagraph\subparagraph
+\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
+\fi
 
-author: 
-  - name          : "George Kachergis"
-    affiliation   : "1"
-    corresponding : yes    # Define only one corresponding author
-    address       : "Stanford, CA 94305 USA"
-    email         : "kachergis@stanford.edu"
-  - name          : "Emily Hembacher"
-    affiliation   : "2"
-  - name          : "Veronica Cristiano"
-    affiliation   : "3"
-  - name          : "Hanwen Vivian Zhang"
-    affiliation   : "4"
-  - name          : "Michael C. Frank"
-    corresponding : yes
-    address       : "Stanford, CA 94305 USA"
-    email         : "mcfrank@stanford.edu"
-    affiliation   : "1"
+%%% Use protect on footnotes to avoid problems with footnotes in titles
+\let\rmarkdownfootnote\footnote%
+\def\footnote{\protect\rmarkdownfootnote}
 
-affiliation:
-  - id            : "1"
-    institution   : "Department of Psychology, Stanford University"
-  - id            : "2"
-    institution   : "Nextdoor, Inc."
-  - id            : "3"
-    insitution    : "Gallaudet University"
-  - id            : "4"
-    insitution    : "Cornell University"
+  \title{Understanding the impacts of video-guided activities on parent-child interaction}
+    \author{George Kachergis\textsuperscript{1}, Emily Hembacher\textsuperscript{2}, Veronica Cristiano\textsuperscript{3}, Hanwen Vivian Zhang\textsuperscript{4}, \& Michael C.
+Frank\textsuperscript{1}}
+    \date{}
 
-authornote: |
-  blah
+\shorttitle{Impacts of videos on parent-child interaction}
+\affiliation{
+\vspace{0.5cm}
+\textsuperscript{1} Department of Psychology, Stanford University\\\textsuperscript{2} Nextdoor, Inc.\\\textsuperscript{3} \\\textsuperscript{4} }
+\keywords{digital parenting advice; joint attention; lexical diversity; guided play\newline\indent Word count: 4510}
+\usepackage{csquotes}
+\usepackage{upgreek}
+\captionsetup{font=singlespacing,justification=justified}
+
+\usepackage{longtable}
+\usepackage{lscape}
+\usepackage{multirow}
+\usepackage{tabularx}
+\usepackage[flushleft]{threeparttable}
+\usepackage{threeparttablex}
+
+\newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}
+
+\makeatletter
+\newcommand\LastLTentrywidth{1em}
+\newlength\longtablewidth
+\setlength{\longtablewidth}{1in}
+\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}
+
+\usepackage{lineno}
+
+\linenumbers
+\usepackage{float}
+
+\authornote{blah
 blahblah
-abstract: |
-  Early parenting practices play an important role in shaping the future  outcomes of young children [@Hart1995; @Heckman2006]. 
+
+Correspondence concerning this article should be addressed to George Kachergis, Stanford, CA 94305 USA. E-mail: \href{mailto:kachergis@stanford.edu}{\nolinkurl{kachergis@stanford.edu}}}
+
+\abstract{
+Early parenting practices play an important role in shaping the future outcomes of young children (Hart \& Risley, 1995; Heckman, 2006).
 In particular, high-quality early interactions and language input appear to facilitate language learning and result in higher levels of school performance.
-  The rise of phone- and tablet-based parenting applications ("apps") holds the promise of delivering  low-cost, positive interventions on parenting style to a wide variety of populations. 
+The rise of phone- and tablet-based parenting applications (``apps'') holds the promise of delivering low-cost, positive interventions on parenting style to a wide variety of populations.
 Of special interest are the parents of very young children, who are often difficult to reach in other ways.
@@
 Specifically, after watching the activity video, parents spoke more and made more bids for joint attention with the child.
-keywords          : "digital parenting advice; joint attention; lexical diversity; guided play"
-wordcount         : "4510"
 
-bibliography      : ["library.bib"]
+}
 
-floatsintext      : yes
-figurelist        : no
-tablelist         : no
-footnotelist      : no
-linenumbers       : yes
-mask              : no
-draft             : no
-header-includes:
-  - \usepackage{float}
-documentclass     : "apa6"
-csl: apa6.csl
-classoption       : "man"
-output            : papaja::apa6_pdf
----
+\begin{document}
+\maketitle
 
-```{r global_options, include=FALSE}
-knitr::opts_chunk$set(fig.width=4, fig.height=3, fig.crop = F, 
-                      fig.pos = "tb", fig.path='figs/',
-                      echo=F, warning=F, cache=T, 
-                      message=F, sanitize = T)
-```
+\hypertarget{introduction}{%
+\section{Introduction}\label{introduction}}
 
-```{r setup, include = FALSE}
-suppressPackageStartupMessages(c("dplyr","langcog","tidyr","ggplot2","lme4"))
-library("papaja")
-library(png)
-library(grid)
-library(ggplot2)
-library(xtable)
-library(psych)
-library(langcog)
-library(tidyverse)
-library(ggthemes)
-library(lme4)
-library(lmerTest)
-library(tidyboot)
-library(knitr)
-source("multiplot.R")
-
-select <- dplyr::select # masked by MASS
-theme_set(theme_few())
-
-# labels=addline_format(c("Activity Video", "Science Video"))
-addline_format <- function(x,...){
-    gsub('\\s','\n',x)
-}
-```
-
-```{r analysis-preferences}
-# Seed for random number generation
-set.seed(42)
-knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
-```
-
-# Introduction
-
-The quantity and quality of early language input has been found to be strongly associated with later language and academic outcomes [@Hart1995; @Marchman2008; @Cartmill2013; @HirshPasek2015].
-Thus, because of the potential for large downstream effects [@Heckman2006], there is tremendous interest in interventions that change children's language environment.
+The quantity and quality of early language input has been found to be strongly associated with later language and academic outcomes (Cartmill et al., 2013; Hart \& Risley, 1995; Hirsh-Pasek et al., 2015; Marchman \& Fernald, 2008).
+Thus, because of the potential for large downstream effects (Heckman, 2006), there is tremendous interest in interventions that change children's language environment.
 And because parents define a large portion of that environment, especially before the onset of formal schooling, parent behavior is a critical locus for such interventions.
-Many effective parenting interventions require large resource investments and require many hours of in-person contact [@Jamaica2014; @PerryPreschool2004], making implementation at scale a daunting proposition.
+Many effective parenting interventions require large resource investments and require many hours of in-person contact (Gertler et al., 2014; Schweinhart et al., 2004), making implementation at scale a daunting proposition.
 For this reason, many researchers targeting early language are interested in delivering parenting interventions remotely -- through texts, apps, and videos delivered on digital devices.
@@
 The content provided by digital parenting interventions runs the gamut from general parenting messages and facts from child development research to specific advice and suggested activities.
-A growing body of evidence suggests that these digital interventions can be effective across a range of cultures, income levels, and children's ages [for a review, see @Breitenstein2014].
-For example, in contrast to a face-to-face parent training intervention, a tablet-based version saw significantly higher session completion rates (51% attendance vs.
-85% module completion) and comparable or larger effect sizes on parents' and children's (aged 2 to 5 years) behavior [@Breitenstein2016].
+A growing body of evidence suggests that these digital interventions can be effective across a range of cultures, income levels, and children's ages (for a review, see Breitenstein, Gross, \& Christophersen, 2014).
+For example, in contrast to a face-to-face parent training intervention, a tablet-based version saw significantly higher session completion rates (51\% attendance vs.~85\% module completion) and comparable or larger effect sizes on parents' and children's (aged 2 to 5 years) behavior (Breitenstein, Fogg, Ocampo, Acosta, \& Gross, 2016).
 Often, however, the theory of change presupposed by such interventions is relatively vague.
@@
 This theory of change is typically grounded in ideas about guided play and early language stimulation.
-Child-directed speech varies not only in quantity (i.e., the number of total tokens), but also in quality in terms of the diversity of the tokens [@Malvern2004] or the context-appropriateness of the speech [@Cartmill2013], both of which have been linked to children's subsequent language development.
-Further, language learning -- especially the acquisition of early vocabulary in the first years -- appears to be supported preferentially by parents and children _jointly attending_ to some object or activity [@Baldwin1991; @Bigelow2004].
-Episodes of joint attention are frequent during guided play, when parents set goals and scaffold their child's activities [@Wood1976; @Weisberg2013].
+Child-directed speech varies not only in quantity (i.e., the number of total tokens), but also in quality in terms of the diversity of the tokens (Malvern, Richards, Chipere, \& Durán, 2004) or the context-appropriateness of the speech (Cartmill et al., 2013), both of which have been linked to children's subsequent language development.
+Further, language learning -- especially the acquisition of early vocabulary in the first years -- appears to be supported preferentially by parents and children \emph{jointly attending} to some object or activity (Baldwin, 1991; Bigelow, MacLean, \& Proctor, 2004).
+Episodes of joint attention are frequent during guided play, when parents set goals and scaffold their child's activities (Weisberg, Hirsh-Pasek, \& Golinkoff, 2013; Wood, Bruner, \& Ross, 1976).
 Thus, the current literature supports interventions that encourage parents to provide high-quality language and interaction through something like guided play -- whether via reading books or playing with a shape-sorter at home, or via a conversation about categories in the supermarket.
@@
 
-# Experiment 1
+\hypertarget{experiment-1}{%
+\section{Experiment 1}\label{experiment-1}}
 
 In Experiment 1, we invited parents of 6- to 24-month-old infants visiting the Children's Discovery Museum in San Jose to complete video-guided activities from a commerical parenting app that delivers digital parenting advice in the form of short videos.
-Parents were randomly assigned to the video condition or the control condition; parents in the _activity video_ condition watched a video from the app (matched to their child's age), and then performed the activity with their child using the props from the video.
-Parents in the _control_ condition did not watch an activity video, but were given a set of the same age-appropriate props and asked to play with their infants as they normally would at home.
+Parents were randomly assigned to the video condition or the control condition; parents in the \emph{activity video} condition watched a video from the app (matched to their child's age), and then performed the activity with their child using the props from the video.
+Parents in the \emph{control} condition did not watch an activity video, but were given a set of the same age-appropriate props and asked to play with their infants as they normally would at home.
 
-## Method
+\hypertarget{method}{%
+\subsection{Method}\label{method}}
 
-```{r, include=F}
-e1path = "../../parenting_obs_e1/"
-load(paste(e1path,"Exp1_cleaned_data.RData",sep='')) # merged dataframe ready for plotting
+\hypertarget{participants.}{%
+\subsubsection{Participants.}\label{participants.}}
 
-lmer_data <- d %>%
-  #filter(!is.na(AA), !is.na(EL), !is.na(RR))%>%
-  mutate(condition = factor(condition), 
-         MTLD = as.numeric(MTLD),
-         EL = as.numeric(langcog::scale(EL, scale=FALSE)),
-         AA = as.numeric(langcog::scale(AA, scale=FALSE)),
-         RR = as.numeric(langcog::scale(RR, scale=FALSE)),
-         age = as.numeric(langcog::scale(age, scale=FALSE)),
-         parent_ed = as.numeric(langcog::scale(parent_ed, scale=T)),
-         gender = as.factor(gender),
-         video = as.factor(video))
-
-e1_gender = table(d$gender)
-#table(cut_interval(d$age, n=2, breaks=c(.5,1.5,2.1), labels=F))
-#table(cut_number(d$age, n=3, breaks=c(.5,1.5,2.1)))
-e1_parent_ed = table(d$parent_ed)
-```
-
-### Participants. 
-`r nrow(d)` infants (F = `r e1_gender['F']`, M = `r e1_gender['M']`) aged 6-24 months (20 6-11.9 month-olds, 20 12-17.9 month-olds, and 20 18-24 month-olds) and their parents participated in a museum in northern California.
+60 infants (F = 43, M = 17) aged 6-24 months (20 6-11.9 month-olds, 20 12-17.9 month-olds, and 20 18-24 month-olds) and their parents participated in a museum in northern California.
 We included infants who were exposed to English at least 50 percent of the time (n = 58) or who were exposed less but whose participating parent reported that they primarily speak English with their child at home (n = 2).
-62% of participants (n = 37) had been exposed to two or more languages, as indicated by their parent. 
+62\% of participants (n = 37) had been exposed to two or more languages, as indicated by their parent.
 Parents identified their children as White (n = 25), Asian (n = 11), African American/Black (n = 2), Biracial (n = 12), other (n = 5), or declined to state (n = 5).
 Fifteen parents reported that their child was of Hispanic origin.
-Parents tended to be highly-educated, with reports of highest level of education ranging from completed high school (n = `r e1_parent_ed[1]`), some college (n = `r e1_parent_ed[2]`), four-year college (n = `r e1_parent_ed[3]`), some graduate school (n = `r e1_parent_ed[4]`), to completed graduate school (n = `r e1_parent_ed[5]`).
+Parents tended to be highly-educated, with reports of highest level of education ranging from completed high school (n = 5), some college (n = 7), four-year college (n = 16), some graduate school (n = 2), to completed graduate school (n = 30).
 
-### Materials.
+\hypertarget{materials.}{%
+\subsubsection{Materials.}\label{materials.}}
+
 Stimuli included activity videos from a commercial parenting application.
@@
 We selected two videos for each of three age groups in our sample (6-11.9 months, 12-17.9 months, 18-23.94 months).
-Participants were also given a set of toys corresponding to those in the video that they watched so that they could complete the activity.[^1]
+Participants were also given a set of toys corresponding to those in the video that they watched so that they could complete the activity.\footnote{Details of the specific videos used and the toys associated with each video are in the Appendix.}
 
-[^1]: Details of the specific videos used and the toys associated with each video are in the Appendix.
-
-Participants were randomly assigned to either the *Activity Video* condition or the *No Video* condition. 
+Participants were randomly assigned to either the \emph{Activity Video} condition or the \emph{No Video} condition.
 Parents participating in the Activity Video condition were assigned to watch one of the two activity videos available for their child's age group, while parents in the No Video condition watched no video, and were simply asked to play with their child as they normally would.
 The No Video condition was yoked to the Activity Video condition such that for every participant in the Video condition who saw a particular video and received the associated props, a participant in the No Video condition received the same props but did not watch the activity video.
-Parents also completed the Early Parenting Attitudes Questionnaire [EPAQ; @Hembacher2018]. 
+Parents also completed the Early Parenting Attitudes Questionnaire (EPAQ; Hembacher \& Frank, 2018).
 The EPAQ measures parents of young children's attitudes about parenting and child development along three dimensions: rules and respect, early learning, and affection and attachment.
 
-### Procedure.
+\hypertarget{procedure.}{%
+\subsubsection{Procedure.}\label{procedure.}}
+
 After providing informed consent, parents in the Activity Video condition watched the assigned activity video on a laptop with headphones.
@@
 Immediately following the video, each parent-child dyad was provided with the props to complete the video-guided activity that the parent had viewed.
-The toys were placed on a large foam play mat, and parents were instructed to sit on the mat with their child and re-create the activity they had viewed for a period of three minutes.[^2]
+The toys were placed on a large foam play mat, and parents were instructed to sit on the mat with their child and re-create the activity they had viewed for a period of three minutes.\footnote{Based on piloting, we estimated these activities would would only require three minutes to complete.}
 In the Control condition, after informed consent parents were told to play with their child as they would at home with the provided props for a period of three minutes.
 They were not given any additional instructions about how to use the props.
-
-[^2]: Based on piloting, we estimated these activities would would only require three minutes to complete.
 
@@
 
-### Joint Attention Coding Procedure.
-The video of each session was manually coded for episodes of joint attention (JA) using the Datavyu software [@datavyu]. 
+\hypertarget{joint-attention-coding-procedure.}{%
+\subsubsection{Joint Attention Coding Procedure.}\label{joint-attention-coding-procedure.}}
+
+The video of each session was manually coded for episodes of joint attention (JA) using the Datavyu software (Team, 2014).
 The video taken at floor level was coded by default, but the other video was referred to if the participants were occluded or if there was technical difficulty with the first camera.
@@
 If more than 3 seconds elapsed between bids, they were coded as separate attempts.
-An episode of joint attention was considered _passive_ if both participants visually focused on an object for 3 or more seconds but the child did not acknowledge the parent. 
+An episode of joint attention was considered \emph{passive} if both participants visually focused on an object for 3 or more seconds but the child did not acknowledge the parent.
 If either participant looked away from the object for less than 3 seconds and then returned to the same object it was considered part of the same episode of joint attention.
-A joint attention episode was considered _coordinated_ if both participants visually focused on an object for 3 or more seconds and at some point in the interaction the child indicated awareness of interaction with some overt behavior toward the parent such as looking at their face, gesturing, vocalizing, or turn-taking.
-Full details of our guidelines for coding joint attention are available in [SI](https://docs.google.com/document/d/1cZrT_Gjt6p0om19lXO-XcFnT09pb0giyhRQ-Pm1yoBU/edit?usp=sharing).
+A joint attention episode was considered \emph{coordinated} if both participants visually focused on an object for 3 or more seconds and at some point in the interaction the child indicated awareness of interaction with some overt behavior toward the parent such as looking at their face, gesturing, vocalizing, or turn-taking.
+Full details of our guidelines for coding joint attention are available in \href{https://docs.google.com/document/d/1cZrT_Gjt6p0om19lXO-XcFnT09pb0giyhRQ-Pm1yoBU/edit?usp=sharing}{SI}.
 
 A second coder independently coded a third of the videos (i.e., 20 of the 60 videos, approximately equally distributed across ages) to establish reliability.
-The two coders had a reliability of ICC = 0.80 with 95% confident interval (CI) = [0.57,0.92] for number of parent bids for JA; ICC = 0.20 with 95% CI = [-0.26,0.58] for number of passive JA episodes; ICC = 0.66 with 95% CI = [0.32,0.85] for number of coordinated JA episodes; ICC = 0.24 with 95% CI = [-0.21,0.61] for total duration of passive JA episodes, and ICC = 0.62 with 95% CI = [0.27,0.83] for total duration of coordinated JA episodes.
+The two coders had a reliability of ICC = 0.80 with 95\% confident interval (CI) = {[}0.57,0.92{]} for number of parent bids for JA; ICC = 0.20 with 95\% CI = {[}-0.26,0.58{]} for number of passive JA episodes; ICC = 0.66 with 95\% CI = {[}0.32,0.85{]} for number of coordinated JA episodes; ICC = 0.24 with 95\% CI = {[}-0.21,0.61{]} for total duration of passive JA episodes, and ICC = 0.62 with 95\% CI = {[}0.27,0.83{]} for total duration of coordinated JA episodes.
 
-## Results
+\hypertarget{results}{%
+\subsection{Results}\label{results}}
 
 Parents' child-directed speech during the play sessions was transcribed.
-The transcripts and hand-coded joint attention data were analyzed according to our preregistration[^3], with any deviations or extensions noted.
+The transcripts and hand-coded joint attention data were analyzed according to our preregistration\footnote{Preregistration: \url{https://osf.io/2bpdf/}{]}}, with any deviations or extensions noted.
 Below we first report the lexical diversity results, followed by the joint attention results.
 
-[^3]: Preregistration: [https://osf.io/2bpdf/](https://osf.io/2bpdf/)]
+\hypertarget{lexical-diversity}{%
+\subsubsection{Lexical Diversity}\label{lexical-diversity}}
 
-### Lexical Diversity
+For each transcript, the words were lemmatized using \texttt{spacy2} (Honnibal, 2017), and the word \emph{types} (unique words) and \emph{tokens} (total words) were then tallied and the type-token ratio (TTR) calculated as a measure of lexical diversity.
+Although TTR was our preregistered measure of lexical diversity as it has commonly been used, it has been noted that TTR is correlated with the length of a text, which has led to the development of new measures such as the measure of textual lexical diversity (MTLD; McCarthy \& Jarvis, 2010).
+Thus, we also measure lexical diversity with MTLD, which is calculated as the mean length of sequential word strings in a text that maintain a given TTR value (here we use the value proposed by McCarthy and Jarvis (2010): 0.720).
 
-For each transcript, the words were lemmatized using ``spacy2`` [@spacy2], and the word *types* (unique words) and *tokens* (total words) were then tallied and the type-token ratio (TTR) calculated as a measure of lexical diversity.
-Although TTR was our preregistered measure of lexical diversity as it has commonly been used, it has been noted that TTR is correlated with the length of a text, which has led to the development of new measures such as the measure of textual lexical diversity [MTLD; @McCarthy2010].
-Thus, we also measure lexical diversity with MTLD, which is calculated as the mean length of sequential word strings in a text that maintain a given TTR value (here we use the value proposed by @McCarthy2010: 0.720).
-
-```{r, e1-lexdiv-regressions, echo=F, include=F}
-get_lmer_reporting_values <- function(lmer.fit, digits=2) {
-  sm <- summary(lmer.fit)
-  Vcov <- vcov(lmer.fit, useScale = FALSE)
-  beta <- round(fixef(lmer.fit), digits)
-  se <- round(sqrt(diag(Vcov)), digits)
-  zval <- round(beta / se, digits)
-  pvalEst <- round(2 * pnorm(abs(zval), lower.tail = FALSE), 3)
-  pval <- round(sm$coefficients[,"Pr(>|t|)"], 3)
-  tval <- abs(round(sm$coefficients[,"t value"], digits))
-  df <- round(sm$coefficients[,"df"], 1)
-  return(cbind(beta, se, zval, tval, pval, pvalEst, df))
-}
-
-require("lmerTest")
-
-# Predicting lexical diversity based on experimental condition, PAQ, demographics. 
-modTTR <- lmer(TTR ~ condition + age + gender + parent_ed + (1|video), data=lmer_data)
-summary(modTTR) # condition:Exp -0.113 t(52.4) = 4.22 p<.001
-e1TTR = get_lmer_reporting_values(modTTR)
-
-modMTLD <- lmer(MTLD ~ condition + age + gender + parent_ed + (1|video), data=lmer_data)
- # , control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5)))
-summary(modMTLD) # condition -8.73 t(55) = 2.67 p=.001 !! singular fit
-e1MTLD = get_lmer_reporting_values(modMTLD)
-
-tt <- getME(modMTLD,"theta")
-ll <- getME(modMTLD,"lower")
-min(tt[ll==0]) # 0
-
-# Bayesian regression (stan_glmer in rstanarm) shows the same:
-require("rstanarm")
-bmodMTLD <- stan_glmer(MTLD ~ condition + age + gender + parent_ed + (1|video), data=lmer_data)
-summary(bmodMTLD) # condition mean=-8.6 sd=3.2 95% CI = [-14.9,-2.3]
-
-# predict word tokens
-tokens_mod <- lmer(tokens ~ condition*EL + condition*AA + condition*RR + age + gender + parent_ed + (1|video),  data=lmer_data) # only 54 parents completed the EPAQ
-summary(tokens_mod) # condition 56.02 t(40.4) = 2.30 p<.05
-e1tokens = get_lmer_reporting_values(tokens_mod)
-
-# predict word types
-types_mod <- lmer(types ~ condition*EL + condition*AA + condition*RR  + age + gender + parent_ed + (1|video), data=lmer_data,
-                  control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) # !! singular fit
-summary(types_mod) # nothing (hint: conditionexp:AA beta=19.04 p=.11)
-e1types = get_lmer_reporting_values(types_mod) 
-# verify with Bayesian regression:
-bmod_types <- stan_glmer(types ~ condition*EL + condition*AA + condition*RR  + age + gender + parent_ed + (1|video), data=lmer_data)
-summary(bmod_types) # nothing
-
-e1_lexdiv <- lmer_data %>% group_by(condition) %>%
-  summarise(TTR=mean(TTR), MTLD=mean(MTLD), tokens=mean(tokens)) 
-```
-
-We fit a mixed-effects linear regression predicting TTR as a function of condition, age (centered), gender, and parent's education level with a random intercept per video using lme4 [@lme4]. 
-There was significantly lower TTR in the Video condition (mean: `r round(subset(e1_lexdiv, condition=='exp')$TTR, 2)`) than in the Control condition (mean: `r round(subset(e1_lexdiv, condition=='con')$TTR, 2)`, $\beta=$`r e1TTR["conditionexp","beta"]`, t(52.4) = `r e1TTR["conditionexp","tval"]`, *p*<.001).
+We fit a mixed-effects linear regression predicting TTR as a function of condition, age (centered), gender, and parent's education level with a random intercept per video using lme4 (Bates, Mächler, Bolker, \& Walker, 2015).
+There was significantly lower TTR in the Video condition (mean: 0.32) than in the Control condition (mean: 0.43, \(\beta=\)-0.11, t(52.4) = 4.22, \emph{p}\textless{}.001).
 There were no significant effects of age, gender, or parent's level of education.
-A similar mixed-effects linear regression instead predicting MTLD also found significantly lower lexical diversity in the Video condition (mean MTLD: `r round(subset(e1_lexdiv, condition=='exp')$MTLD, 2)`) than in the Control condition (mean: `r round(subset(e1_lexdiv, condition=='exp')$TTR, 2)`, $\beta=$`r e1MTLD["conditionexp","beta"]`, t(55) = `r e1MTLD["conditionexp","tval"]`, *p*=.001), with no other significant effects.
+A similar mixed-effects linear regression instead predicting MTLD also found significantly lower lexical diversity in the Video condition (mean MTLD: 17.87) than in the Control condition (mean: 0.32, \(\beta=\)-8.73, t(55) = 2.67, \emph{p}=.001), with no other significant effects.
 Figure \ref{fig:e1lex_div} shows the mean of each lexical diversity measure (TTR and MTLD) by condition.
 
-```{r e1tokens, echo=F, include=F}
-d$Condition = factor(d$condition, levels = c("con", "exp"), labels = c("No Video", "Activity Video"))
-
-ms_lex_mtld <- d %>% group_by(Condition) %>%
-  tidyboot_mean(MTLD) 
-ms_lex <- d %>% group_by(Condition) %>%
-  tidyboot_mean(TTR) # Type/Token Ratio
-ms_tok <- d %>% group_by(Condition) %>%
-  tidyboot_mean(tokens) 
-ms_type <- d %>% group_by(Condition) %>%
-  tidyboot_mean(types)
-```
-
-We also conducted similar regressions predicting the number of word tokens and types, finding only a significant effect of condition on the number of word tokens ($\beta= `r e1tokens["conditionexp","beta"]`$, t(40.4)=`r e1tokens["conditionexp","tval"]`, *p*<.05), with parents using more words in the Video condition (mean: `r round(subset(e1_lexdiv, condition=='exp')$tokens, 0)`, bootstrapped 95% confidence intervals (CI): [`r round(subset(ms_tok, Condition=="Activity Video")$ci_lower, 0)`,`r round(subset(ms_tok, Condition=="Activity Video")$ci_upper, 0)`]) than in the Control condition (mean: `r round(subset(e1_lexdiv, condition=='con')$tokens, 0)`, bootstrapped 95% CI: [`r round(subset(ms_tok, Condition=="No Video")$ci_lower, 0)`,`r round(subset(ms_tok, Condition=="No Video")$ci_upper, 0)`]).
+We also conducted similar regressions predicting the number of word tokens and types, finding only a significant effect of condition on the number of word tokens (\(\beta= 56.01\), t(40.4)=2.30, \emph{p}\textless{}.05), with parents using more words in the Video condition (mean: 225, bootstrapped 95\% confidence intervals (CI): {[}199,253{]}) than in the Control condition (mean: 165, bootstrapped 95\% CI: {[}139,192{]}).
 The means of the lexical diversity measures are reported in Table \ref{tab:e1tab}.
 
-```{r e1tab, echo=FALSE}
-e1 <- d %>% group_by(Condition) %>%
-  summarise("Mean TTR"=mean(TTR), TTRsd=sd(TTR),
-            "Mean MTLD"=mean(MTLD), MTLDsd=sd(MTLD),
-            "Mean types"=mean(types), types.sd=sd(types),
-            "Mean tokens"= mean(tokens), tokens.sd=sd(tokens))
-names(e1) = c("Condition","TTR (M)", "(sd)", "MTLD (M)", "(sd)", "Types (M)", "(sd)", "Tokens (M)", "(sd)")
-kable(e1, digits=2, caption="Lexical diversity measures in Experiment 1.")
-```
+\begin{table}[t]
 
-```{r hiddenfigs, include=F}
-e1ttr <- ggplot(ms_lex, aes(x=Condition, y=mean, fill=Condition)) + geom_bar(stat="identity") + 
-  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .7)) +
-  geom_point(data=d, aes(x=Condition, y=TTR), alpha=.2, position = position_jitterdodge()) +
-  xlab("Condition") + ylab("Type/Token Ratio (TTR)") +
-  langcog::scale_fill_solarized() + ggthemes::theme_few() +
-  theme(legend.position="none")
+\caption{\label{tab:e1tab}Lexical diversity measures in Experiment 1.}
+\centering
+\begin{tabular}{l|r|r|r|r|r|r|r|r}
+\hline
+Condition & TTR (M) & (sd) & MTLD (M) & (sd) & Types (M) & (sd) & Tokens (M) & (sd)\\
+\hline
+No Video & 0.43 & 0.10 & 27.09 & 15.33 & 67.33 & 22.94 & 165.10 & 75.15\\
+\hline
+Activity Video & 0.32 & 0.09 & 17.87 & 6.28 & 67.37 & 19.01 & 225.43 & 76.07\\
+\hline
+\end{tabular}
+\end{table}
 
-e1mtld <- ggplot(ms_lex_mtld, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
-  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
-  geom_point(data=d, aes(x=Condition, y=MTLD), alpha=.2, position = position_jitterdodge()) +
-  xlab("Condition") + ylab("MTLD") +
-  langcog::scale_fill_solarized() + ggthemes::theme_few() + 
-  theme(legend.position="none")
+\textbackslash{}begin\{figure\}{[}H{]}
 
-e1tokens <- ggplot(ms_tok, aes(x=Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
-  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
-  geom_point(data=d, aes(x=Condition, y=tokens), alpha=.2, position = position_jitterdodge()) +
-  xlab("Condition") + ylab("Total Number of Word Tokens") +
-  langcog::scale_fill_solarized() + ggthemes::theme_few() +
-  theme(legend.position="none")
+\{\centering \includegraphics{figs/fig:e1lex_div-1}
 
-```
+\}
 
-```{r fig:e1lex_div, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=7, fig.height=3.0, fig.cap = "Mean lexical diversity scores by condition (left: Type/Token ratio, right: MTLD) in Experiment 1.
+\caption{Mean lexical diversity scores by condition (left: Type/Token ratio, right: MTLD) in Experiment 1.
 Both measures of lexical diversity were significantly lower after watching an activity video.
-Error bars show bootstrapped 95\\% confidence intervals (CIs), and gray dots indicate values for each participant."}
+Error bars show bootstrapped 95\% confidence intervals (CIs), and gray dots indicate values for each participant.}
 
-multiplot(e1ttr, e1mtld, e1tokens, cols=3)
-```
+(\#fig:fig:e1lex\_div)
+\textbackslash{}end\{figure\}
 
-```{r, e1-effect-size, echo=F, include=F}
-cohens_d <- function(dat) {
-  return( diff(dat$mean) / (sqrt(sum(dat$sd^2)) / 2) )
-}
-
-ttr_means <- d %>% group_by(Condition) %>%
-  summarise(mean = mean(TTR), sd = sd(TTR))
-cohens_d(ttr_means) # -1.68 - should we report this?
-```
-
-### Joint Attention
-
-```{r, e1ja-regressions, echo=F, include=F}
-load(paste(e1path,"joint_attention/Exp1_joint_attention_data.RData",sep=''))
-d$Condition <- factor(d$Condition, levels = c("con","exp"), labels = c("No Video","Activity Video"))
-
-lmer_data <- d %>%
-  filter(!is.na(AA), !is.na(EL), !is.na(RR)) %>%
-  mutate(Condition = factor(Condition), 
-         bids_tot = as.numeric(bids_tot),
-         EL = as.numeric(langcog::scale(EL, scale=FALSE)),
-         AA = as.numeric(langcog::scale(AA, scale=FALSE)),
-         RR = as.numeric(langcog::scale(RR, scale=FALSE)),
-         age = as.numeric(langcog::scale(age, scale=FALSE)),
-         gender = as.factor(gender),
-         Video = as.factor(Video))
-
-model_string =  "~ Condition * EL + Condition * AA + Condition * RR  + age + gender + parent_ed + (1| Video)"
-
-# Total number of bids
-bids_mod <- lmer(paste("bids_tot", model_string), data = lmer_data)
-summary(bids_mod) # condition beta = 3.51, t(40.3) = 2.95 p<.01, gender p=.05 ?
-e1bids = get_lmer_reporting_values(bids_mod)
-
-e1bids_M <- lmer_data %>% group_by(Condition) %>% 
-  summarise(mean = mean(bids), sd = sd(bids))
-
-# Episodes of coordinated joint attention.
-cja_mod <- lmer(paste("cja", model_string), data = lmer_data)
-summary(cja_mod) # NA
-
-# Episodes of passive joint attention.
-pja_mod <- lmer(paste("pja", model_string), data = lmer_data)
-summary(pja_mod) # marginal RR, beta=-1.07 p=.07, condition*RR beta=1.83 p<.05 t(41.5)=2.22
-e1pja = get_lmer_reporting_values(pja_mod)
-
-# Total duration of passive joint attention.
-pja_time_mod <- lmer(paste("pja_length", model_string), data = lmer_data)
-summary(pja_time_mod) # NA
-
-# Total duration of coordinated joint attention.
-cja_time_mod <- lmer(paste("cja_length", model_string), data = lmer_data,
-                     control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5)))
-summary(cja_time_mod) # marginal parent education p=.09 - SINGULAR (do stan_glmer)
-```
+\hypertarget{joint-attention}{%
+\subsubsection{Joint Attention}\label{joint-attention}}
 
@@
 This lme4 model included random intercepts per video.
-There were significantly more bids for JA in the Video condition (mean: `r round(subset(e1bids_M, Condition=="Activity Video")$mean,2)`, sd: `r round(subset(e1bids_M, Condition=="Activity Video")$sd,2)`) than in the Control condition (mean: `r round(subset(e1bids_M, Condition=="No Video")$mean,2)`, sd: `r round(subset(e1bids_M, Condition=="No Video")$sd,2)`, $\beta=`r e1bids["ConditionActivity Video","beta"]`$, t(`r e1bids["ConditionActivity Video","df"]`) = `r e1bids["ConditionActivity Video","tval"]`, *p*<.01).
+There were significantly more bids for JA in the Video condition (mean: 6.24, sd: 2.79) than in the Control condition (mean: 3.56, sd: 2.50, \(\beta=3.51\), t(40.30) = 2.95, \emph{p}\textless{}.01).
 There were no other significant effects.
@@
 There were no significant effects on the number or total duration of coordinated JA episodes, nor on the total duration of passive JA episodes.
-For the regression predicting the number of passive JA episodes, the only significant effect was an interaction of condition and RR ($\beta=`r e1pja["ConditionActivity Video:RR","beta"]`$, t(`r e1pja["ConditionActivity Video:RR","df"]`) = `r e1pja["ConditionActivity Video:RR","tval"]`, *p*<.05), showing that for parents in the Video condition, those with higher Rules and Respect subscores engaged in more passive JA episodes.
-Figure \@ref(fig:e1ja) shows the mean number bids for JA and episodes of JA by condition in Experiment 1.
+For the regression predicting the number of passive JA episodes, the only significant effect was an interaction of condition and RR (\(\beta=1.83\), t(41.50) = 2.22, \emph{p}\textless{}.05), showing that for parents in the Video condition, those with higher Rules and Respect subscores engaged in more passive JA episodes.
+Figure \ref{fig:e1ja} shows the mean number bids for JA and episodes of JA by condition in Experiment 1.
 
-```{r e1ja, fig.cap = "Mean number of bids (left) and episodes (right) of joint attention (JA) by condition in Experiment 1.
-Parents made significantly more bids for JA after watching an activity video, but this did not result in a greater number of episodes of JA."}
-# fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=5.5, fig.height=3.0, f
+\begin{figure}
+\centering
+\includegraphics{figs/e1ja-1.pdf}
+\caption{\label{fig:e1ja}Mean number of bids (left) and episodes (right) of joint attention (JA) by condition in Experiment 1.
+Parents made significantly more bids for JA after watching an activity video, but this did not result in a greater number of episodes of JA.}
+\end{figure}
 
-ms_bids1 <- d %>% group_by(Condition) %>%
-  tidyboot_mean(bids_tot)
-
-e1bids <- ggplot(ms_bids1, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
-  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
-  geom_point(data=d, aes(x=Condition, y=bids_tot), alpha=.2, position = position_jitterdodge()) +
-  xlab("Condition") + ylab("Mean Bids for Joint Attention") +
-  langcog::scale_fill_solarized() + ggthemes::theme_few() + 
-  theme(legend.position="none")
-
-# total joint attention episodes
-ms_tja1 <- d %>% group_by(Condition) %>%
-  tidyboot_mean(total_ja)
-
-e1tja <- ggplot(ms_tja1, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
-  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
-  geom_point(data=d, aes(x=Condition, y=total_ja), alpha=.2, position = position_jitterdodge()) +
-  xlab("Condition") + ylab("Mean Episodes of Joint Attention") +
-  langcog::scale_fill_solarized() + ggthemes::theme_few() + 
-  theme(legend.position="none")
-
-multiplot(e1bids, e1tja, cols=2)
-```
-
-## Discussion
+\hypertarget{discussion}{%
+\subsection{Discussion}\label{discussion}}
 
@@
 
-# Experiment 2
+\hypertarget{experiment-2}{%
+\section{Experiment 2}\label{experiment-2}}
 
@@
 Parents who watched an activity video also made more bids for joint attention, although these bids did not result in more episodes of joint attention compared to the control group.
-Experiment 2 attempts to replicate these findings from with a restricted number of preregistered predictions.[^4]
+Experiment 2 attempts to replicate these findings from with a restricted number of preregistered predictions.\footnote{Preregistration: \url{https://osf.io/2bpdf/}.}
 
-[^4]: Preregistration: [https://osf.io/2bpdf/](https://osf.io/2bpdf/).
+\hypertarget{method-1}{%
+\subsection{Method}\label{method-1}}
 
-## Method
+\hypertarget{participants.-1}{%
+\subsubsection{Participants.}\label{participants.-1}}
 
-```{r, echo=F}
-e2path = "../../parenting_obs_e2/"
-load(paste(e2path,"Exp2_cleaned_data.RData",sep=''))
-
-lmer_data <- d %>%
-  mutate(condition = factor(condition), 
-         MTLD = as.numeric(MTLD),
-         TTR = as.numeric(TTR),
-         age = as.numeric(langcog::scale(age, scale=FALSE)),
-         video = as.factor(video))
-
-e2_gender = table(d$gender)
-e2_ethnicity = table(d$ethnicity)
-e2_parent_ed = table(d$parent_ed)
-e2_12to18 = nrow(subset(d, age<1.5))
-e2_18to24 = nrow(subset(d, age>=1.5))
-```
-
-### Participants. 
-`r nrow(d)` infants (F = `r e2_gender['F']`, M = `r e2_gender['M']`) aged 12-24 months (`r e2_12to18` 12-17.9 month-olds, `r e2_18to24` 18-24 month-olds) and their parents participated in the same museum as Experiment 1.
+60 infants (F = 36, M = 46) aged 12-24 months (41 12-17.9 month-olds, 43 18-24 month-olds) and their parents participated in the same museum as Experiment 1.
 We included infants who were exposed to English at least 75 percent of the time or who were exposed less but whose participating parent reported that they primarily speak English with their child at home.
@@
 Sixteen parents reported their child was of Hispanic origin.
-Parents tended to be highly-educated, with reports of highest level of education ranging from some college (n = `r e2_parent_ed[3]`), four-year college (n = `r e2_parent_ed[4]`), some graduate school (n = `r e2_parent_ed[5]`), to completed graduate school (n = `r e2_parent_ed[6]`) or declined to state (n = 13).
+Parents tended to be highly-educated, with reports of highest level of education ranging from some college (n = 5), four-year college (n = 28), some graduate school (n = 2), to completed graduate school (n = 36) or declined to state (n = 13).
 
-### Materials.
+\hypertarget{materials.-1}{%
+\subsubsection{Materials.}\label{materials.-1}}
 
@@
 
-### Procedure. 
+\hypertarget{procedure.-1}{%
+\subsubsection{Procedure.}\label{procedure.-1}}
+
 The procedure for Experiment 2 matched that of Experiment 1, except that parents in the Control Video condition watched a control video before the play session.
@@
 A second coder independently coded a third of the videos (i.e., 26 of the 84 videos, approximately equally distributed across ages) to establish reliability.
-The two coders had a reliability of ICC = 0.80 with 95% confidence interval (CI) = [0.60,0.90] for number of parent bids for JA; ICC = 0.74 with 95% CI = [0.59,0.87] for number of passive JA episodes; ICC = 0.78 with 95% CI = [0.58,0.90] for number of coordinated JA episodes; ICC = 0.72 with 95% CI = [0.46,0.86] for total duration of passive JA episodes, and ICC = 0.88 with 95% CI = [0.75,0.94] for total duration of coordinated JA episodes.
+The two coders had a reliability of ICC = 0.80 with 95\% confidence interval (CI) = {[}0.60,0.90{]} for number of parent bids for JA; ICC = 0.74 with 95\% CI = {[}0.59,0.87{]} for number of passive JA episodes; ICC = 0.78 with 95\% CI = {[}0.58,0.90{]} for number of coordinated JA episodes; ICC = 0.72 with 95\% CI = {[}0.46,0.86{]} for total duration of passive JA episodes, and ICC = 0.88 with 95\% CI = {[}0.75,0.94{]} for total duration of coordinated JA episodes.
 
-## Results
+\hypertarget{results-1}{%
+\subsection{Results}\label{results-1}}
 
@@
 
-### Lexical Diversity
-```{r, e2-lexdiv-regressions, echo=F, include=F}
-# preregistered analyses:
-# The number of parent bids for joint attention, the number of episodes of joint attention, the number of word tokens produced by parents, and the lexical diversity of parent language output (word types/word tokens).
-# 1) bids, 2) total JA eps, 3) # tokens 4) TTR -- alpha level = .005
-# Mixed-effects linear regressions predicting the dependent variables with condition (video scaffolding vs.
-control) and age in months as fixed effects and participant and specific video as random effects.
-# DV ~ age * condition + (1 | participant) + (1 | video)
-# Lab standard operating procedures will be used for random effects pruning in case of non-convergence.
-# We will interpret condition main effects as well as age * condition interactions (positive or negative) as evidence for behavior changes caused by video scaffolding. 
-# Because of the larger number of coefficients of interest (4 models x 2 coefficients), we will adopt an alpha level of .005 for statistical significance and will report alpha between .05 and .005 as suggestive.
-# “secondary analyses"
-# We will analyze the proportion of coordinated vs. passive joint attention separately using the same model specification.
+\hypertarget{lexical-diversity-1}{%
+\subsubsection{Lexical Diversity}\label{lexical-diversity-1}}
 
-# Notes: 
-# - including (1|sid) never works: "Error: number of levels of each grouping factor must be < number of observations", so we back off to (1|video)
-# Predicting lexical diversity based on experimental condition. 
-modTTR <- lmer(TTR ~ age * condition + (1 | video), data=lmer_data) 
-summary(modTTR) # condition beta=-.09  t(8.6) = 3.33 p=.009 (suggestive)
-e2TTR <- get_lmer_reporting_values(modTTR)
-
-# predict word tokens
-tokens_mod <- lmer(tokens ~ age * condition + (1 | video), data=lmer_data)
-summary(tokens_mod) # NA
-
-modMTLD <- lmer(MTLD ~ age * condition + (1 | video), data=lmer_data)
-summary(modMTLD) # NA
-
-e2_lexdiv <- lmer_data %>% group_by(condition) %>%
-  summarise(TTR=mean(TTR), MTLD=mean(MTLD), tokens=mean(tokens)) 
-# predict word types (NOT A PREREGISTERED REGRESSION)
-#types_mod <- lmer(types ~ age * condition + (1 | video), data=lmer_data)
-#summary(types_mod) # NA
-```
-
-We fit a mixed-effects linear regression predicting TTR as a function of age (centered) and condition with an interaction term, and with random intercepts per video using lme4 [@lme4].
-There was suggestively lower TTR in the Video condition (mean: `r round(e2_lexdiv[2,]$TTR, 2)`) than in the Control condition (mean: `r round(e2_lexdiv[1,]$TTR, 2)`, $\beta=`r e2TTR["conditionexp","beta"]`$, t(`r e2TTR["conditionexp","df"]`) = `r e2TTR["conditionexp","tval"]`, *p*=`r e2TTR["conditionexp","pval"]`).
+We fit a mixed-effects linear regression predicting TTR as a function of age (centered) and condition with an interaction term, and with random intercepts per video using lme4 (Bates et al., 2015).
+There was suggestively lower TTR in the Video condition (mean: 0.38) than in the Control condition (mean: 0.48, \(\beta=-0.09\), t(8.60) = 3.33, \emph{p}=0.01).
 There was no significant effect of age, nor a significant interaction.
@@
 
-```{r e2tab, echo=F}
-d$Condition = factor(d$condition, levels = c("con", "exp"), labels = c("Science Video", "Activity Video"))
-e2 <- d %>% group_by(Condition) %>%
-  summarise("Mean TTR"=mean(TTR), TTRsd=sd(TTR),
-            "Mean MTLD"=mean(MTLD), MTLDsd=sd(MTLD),
-            "Mean types"=mean(types), types.sd=sd(types),
-            "Mean tokens"= mean(tokens), tokens.sd=sd(tokens))
-names(e2) = c("Condition","TTR (M)", "(sd)", "MTLD (M)", "(sd)", "Types (M)", "(sd)", "Tokens (M)", "(sd)")
-kable(e2, digits=2, caption="\\label{e2tab} Lexical diversity measures in Experiment 2.")
-```
+\begin{table}[t]
 
-```{r fig:e2lexdiv, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=6.5, fig.height=3, fig.cap = "\\label{fig:e2lexdiv} Mean lexical diversity scores by condition (left: Type/Token ratio, middle: MTLD, right: word tokens) in Experiment 2."}
+\caption{\label{tab:e2tab}\label{e2tab} Lexical diversity measures in Experiment 2.}
+\centering
+\begin{tabular}{l|r|r|r|r|r|r|r|r}
+\hline
+Condition & TTR (M) & (sd) & MTLD (M) & (sd) & Types (M) & (sd) & Tokens (M) & (sd)\\
+\hline
+Science Video & 0.48 & 0.08 & 22.45 & 10.57 & 86.83 & 26.87 & 191.38 & 72.08\\
+\hline
+Activity Video & 0.38 & 0.12 & 20.63 & 8.66 & 80.95 & 24.14 & 234.60 & 92.68\\
+\hline
+\end{tabular}
+\end{table}
 
-ttr2 <- d %>% group_by(Condition) %>%
-  tidyboot_mean(TTR)
+\begin{figure}[H]
 
-e2ttr <- ggplot(ttr2, aes(x=Condition, y=mean, fill=Condition)) + geom_bar(stat="identity") + # labels=addline_format(c("Science Video", "Activity Video"))
-  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
-  geom_point(data=d, aes(x=Condition, y=TTR), alpha=.2, position = position_jitterdodge()) +
-  xlab("Condition") + ylab("TTR") +
-  langcog::scale_fill_solarized() + ggthemes::theme_few() +
-  theme(legend.position="none")
+{\centering \includegraphics{figs/fig:e2lexdiv-1}
 
-mtld2 <- d %>% group_by(Condition) %>%
-  tidyboot_mean(MTLD)
+}
 
-e2mtld <- ggplot(mtld2, aes(x = Condition, y = mean, fill = Condition)) + 
-  geom_bar(stat="identity") + 
-  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
-  geom_point(data=d, aes(x=Condition, y=MTLD), alpha=.2, position = position_jitterdodge()) +
-  xlab("Condition") + ylab("MTLD") +
-  langcog::scale_fill_solarized() + ggthemes::theme_few() +
-  theme(legend.position="none")
+\caption{\label{fig:e2lexdiv} Mean lexical diversity scores by condition (left: Type/Token ratio, middle: MTLD, right: word tokens) in Experiment 2.}(\#fig:fig:e2lexdiv)
+\end{figure}
 
-ms_tok2 <- d %>% group_by(Condition) %>%
-  tidyboot_mean(tokens)
-
-e2tokens <- ggplot(ms_tok2, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
-  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
-  geom_point(data=d, aes(x=Condition, y=tokens), alpha=.2, position = position_jitterdodge()) +
-  xlab("Condition") + ylab("Total Number of Word Tokens") +
-  langcog::scale_fill_solarized() + ggthemes::theme_few() +
-  theme(legend.position="none")
-
-multiplot(e2ttr, e2mtld, e2tokens, cols=3)
-```
-
-```{r e2token-type, include=F}
-
-ms_typ <- d %>% group_by(Condition) %>%
-  tidyboot_mean(types)
-
-e2types <- ggplot(ms_typ, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
-  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
-  geom_point(data=d, aes(x=Condition, y=types), alpha=.2, position = position_jitterdodge()) +
-  xlab("Condition") + ylab("Total Number of Word Types") +
-  langcog::scale_fill_solarized() + ggthemes::theme_few() +
-  theme(legend.position="none")
-
-#multiplot(e2tokens, e2types, cols=2)
-```
-
-```{r, e2-effect-size, echo=F, include=F}
-ttr_means <- d %>% group_by(Condition) %>%
-  summarise(mean = mean(TTR), sd = sd(TTR))
-cohens_d(ttr_means)
-```
-
-### Joint Attention
-```{r, e2ja-regressions, echo=F, include=F}
-load(paste(e2path,"joint_attention/Exp2_joint_attention_data.RData",sep=''))
-summary(d)
-# triplicate variables: gender.x/y, ethnicity, english, num_lang, parent_ed, Exclude
-d$Condition <- factor(d$condition, levels = c("con","exp"), labels = c("Science Video","Activity Video"))
-
-e2ja <- d %>% mutate(bids = bids_tot,
-                     age = as.numeric(langcog::scale(age, scale=FALSE)),
-                     pja_length = pja_length/1000,
-                     cja_length = cja_length/1000,
-                     total_lja = total_lja/1000)
-
-# Total number of bids
-bids_mod <- lmer(bids ~ age * Condition + (1 | video), data = e2ja, 
-                 control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5)))
-summary(bids_mod) # singular fit, convergence code: 0 condition beta=3.11, t(80) = 3.52 p<.001
-e2bids <- get_lmer_reporting_values(bids_mod)
-bids_bmod <- stan_glmer(bids ~ age * Condition + (1|video), data=e2ja)
-summary(bids_bmod) # significant effect of condition! mean=3.1, 95%CI = [1.1, 5.0]
-
-tja_mod <- lmer(total_ja ~ age * Condition + (1 | video), data = e2ja,
-                control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5)))
-e2tja <- get_lmer_reporting_values(tja_mod)
-summary(tja_mod) # singular fit, convergence code: 0
-#                    Estimate Std. Error      df t value  Pr(>|t|) 
-# (Intercept)          7.2912     0.3898 80.0000  18.704  < 2e-16 ***
-# age                 -5.2687     1.5122 80.0000  -3.484 0.000804 ***
-# ConditionVideo       1.4893     0.5513 80.0000   2.701 0.008428 ** 
-# age:ConditionVideo   5.9189     2.2721 80.0000   2.605 0.010950 *
-
-tja_bmod <- stan_glmer(total_ja ~ age * Condition + (1|video), data=e2ja)
-summary(tja_bmod) # total episodes of joint attention -- age, age*condition, condition
-#                                        mean    sd     2.5%   25%    50%    75%    97.5%
-# (Intercept)                             7.3    0.4    6.4    7.0    7.3    7.6    8.2 
-# age                                    -5.0    1.7   -8.2   -6.1   -5.0   -3.9   -1.6 
-# ConditionVideo                          1.5    0.6    0.3    1.1    1.5    1.9    2.8 
-# age:ConditionVideo                      5.6    2.5    0.7    3.9    5.7    7.4   10.5
-
-e2_bids <- e2ja %>% group_by(Condition) %>%
-  tidyboot_mean(bids)
-e2_tja <- e2ja %>% group_by(Condition) %>%
-  tidyboot_mean(total_ja)
-
-```
+\hypertarget{joint-attention-1}{%
+\subsubsection{Joint Attention}\label{joint-attention-1}}
 
 As preregistered, we fit mixed-effects linear regressions predicting the number of parental bids for joint attention and the total number of episodes of JA as a function of fixed effects of condition, age (centered), and their interaction, with random intercepts per video.
-Shown in Figure \ref{fig:e2ja} (left panel), parents made significantly more bids for JA after watching the Activity Video (mean: `r round(subset(e2_bids, Condition=="Activity Video")$mean,2)`, bootstrapped 95% CI: `r round(subset(e2_bids, Condition=="Activity Video")$ci_lower,2)`, `r round(subset(e2_bids, Condition=="Activity Video")$ci_upper,2)`; $\beta=`r e2bids["ConditionActivity Video","beta"]`$, t(`r e2bids["ConditionActivity Video","df"]`) = `r e2bids["ConditionActivity Video","tval"]`, *p*=`r e2bids["ConditionActivity Video","pval"]`)) than after the Science Video (mean: `r round(subset(e2_bids, Condition=="Science Video")$mean,2)`, 95% CI: [`r round(subset(e2_bids, Condition=="Science Video")$ci_lower,2)`, `r round(subset(e2_bids, Condition=="Science Video")$ci_upper,2)`], $\beta=`r e2bids["ConditionActivity Video","beta"]`$, t(`r e2bids["ConditionActivity Video","df"]`) = `r e2bids["ConditionActivity Video","tval"]`, *p*<.001).
+Shown in Figure \ref{fig:e2ja} (left panel), parents made significantly more bids for JA after watching the Activity Video (mean: 12.98, bootstrapped 95\% CI: 11.77, 14.18; \(\beta=3.11\), t(80) = 3.52, \emph{p}=0.00)) than after the Science Video (mean: 9.88, 95\% CI: {[}8.69, 11.11{]}, \(\beta=3.11\), t(80) = 3.52, \emph{p}\textless{}.001).
 There were no other significant effects on parental bids for JA.
 
-In the regression predicting the number of episodes of JA, there was a significant main effect of condition ($\beta=`r e2tja["ConditionActivity Video","beta"]`$, t(`r e2tja["ConditionActivity Video","df"]`) = `r e2tja["ConditionActivity Video","tval"]`, *p*=`r e2tja["ConditionActivity Video","pval"]`), with more episodes of JA occurring after the Activity Video (mean: `r round(subset(e2_tja, Condition=="Activity Video")$mean,2)`, 95% CI: [`r round(subset(e2_tja, Condition=="Activity Video")$ci_lower,2)`, `r round(subset(e2_tja, Condition=="Activity Video")$ci_upper,2)`]) than after the Control Video (mean: `r round(subset(e2_tja, Condition=="Science Video")$mean,2)`, 95% CI: [`r round(subset(e2_tja, Condition=="Science Video")$ci_lower,2)`, `r round(subset(e2_tja, Condition=="Science Video")$ci_upper,2)`]).
-There was also a significant main effect of age ($\beta=`r e2tja["age","beta"]`$, t(`r e2tja["age","df"]`) = `r e2tja["age","tval"]`, *p*=`r e2tja["age","pval"]`), showing that the number of episodes of JA decreased with the child's age.
-However, a significant interaction of age and condition ($\beta=`r e2tja["age:ConditionActivity Video","beta"]`$, t(`r e2tja["age:ConditionActivity Video","df"]`) = `r e2tja["age:ConditionActivity Video","tval"]`, *p*=`r e2tja["age:ConditionActivity Video","pval"]`), shown in the right panel of Figure \ref{fig:e2ja}, demonstrates that older children in the Activity Video condition did not see a decrease in the number of episodes of JA.
+In the regression predicting the number of episodes of JA, there was a significant main effect of condition (\(\beta=1.49\), t(80) = 2.70, \emph{p}=0.01), with more episodes of JA occurring after the Activity Video (mean: 8.78, 95\% CI: {[}7.89, 9.67{]}) than after the Control Video (mean: 7.33, 95\% CI: {[}6.57, 8.06{]}).
+There was also a significant main effect of age (\(\beta=-5.27\), t(80) = 3.48, \emph{p}=0.00), showing that the number of episodes of JA decreased with the child's age.
+However, a significant interaction of age and condition (\(\beta=5.92\), t(80) = 2.61, \emph{p}=0.01), shown in the right panel of Figure \ref{fig:e2ja}, demonstrates that older children in the Activity Video condition did not see a decrease in the number of episodes of JA.
 
-```{r fig:e2ja, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=6.5, fig.height=3.0, fig.cap = "\\label{fig:e2ja} Mean number of bids for JA by condition (left) and the number of episodes of JA by age and condition (right) in Experiment 2.
+\begin{figure}[H]
+
+{\centering \includegraphics{figs/fig:e2ja-1}
+
+}
+
+\caption{\label{fig:e2ja} Mean number of bids for JA by condition (left) and the number of episodes of JA by age and condition (right) in Experiment 2.
 After watching an activity video, parents made more bids for JA.
-Older children in the Activity Video condition showed no decrease in the number of episodes of JA, unlike children in the Control Video condition."}
+Older children in the Activity Video condition showed no decrease in the number of episodes of JA, unlike children in the Control Video condition.}(\#fig:fig:e2ja)
+\end{figure}
 
-e2bids <- ggplot(e2_bids, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
-  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
-  geom_point(data=e2ja, aes(x=Condition, y=bids), alpha=.2, position = position_jitterdodge()) +
-  xlab("Condition") + ylab("Total Bids for Joint Attention") +
-  langcog::scale_fill_solarized() + ggthemes::theme_few() + 
-  theme(legend.position="none")
-
-# total JA episodes
-e2tja <- ggplot(e2_tja, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
-  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
-  geom_point(data=e2ja, aes(x=Condition, y=total_ja), alpha=.2, position = position_jitterdodge()) +
-  xlab("Condition") + ylab("Total Episodes of Joint Attention") +
-  langcog::scale_fill_solarized() + ggthemes::theme_few() + 
-  theme(legend.position="none")
-
-e2tja_age = ggplot(d, aes(x = age, y = total_ja, group=Condition, colour = Condition)) +
-  geom_point(alpha=.7) + geom_smooth(method='lm') + 
-  xlab("Age (years)") + ylab("Total Episodes of Joint Attention") +
-  langcog::scale_colour_solarized() +
-  ggthemes::theme_few()
-
-multiplot(e2bids, e2tja_age, cols=5, layout=matrix(c(1,1,2,2,2), nrow=1))
-```
-
-```{r e2ja-exploratory, echo=F, include=F}
-# EXPLORATORY ANALYSES (NOT PREREGISTERED)
-
-# Episodes of coordinated joint attention
-cja_mod <- lmer(cja ~ age * Condition + (1 | video), data = e2ja,
-                control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5)))
-summary(cja_mod) #  Condition: t(80) = 2.47 beta=1.37 p=.01; age*Condition beta=5.24 t(80) = 2.19 p=.02
-e2cja <- get_lmer_reporting_values(cja_mod)
-# also singular fit, convergence code: 0 - Bayesian regression confirms:
-cja_bmod <- stan_glmer(cja ~ age * Condition + (1|video), data=e2ja)
-summary(cja_bmod) # age n.s., sig effect of condition: mean=1.3 95% CI=[.1,2.6]; age*condition mean=5.1 CI=[.5,9.6]
-#                                        mean    sd     2.5%   25%    50%    75%    97.5%
-# (Intercept)                             5.3    0.4    4.5    5.0    5.3    5.6    6.2 
-# age                                    -2.0    1.4   -4.8   -2.9   -2.0   -1.1    0.9 
-# ConditionVideo                          1.3    0.6    0.1    0.9    1.3    1.7    2.6 
-# age:ConditionVideo                      5.1    2.3    0.5    3.5    5.1    6.5    9.6
-
-# Episodes of passive joint attention.
-pja_mod <- lmer(pja ~ age * Condition + (1 | video), data = e2ja)
-summary(pja_mod) # age beta=-2.88 t(13.4) = 2.53 p=.02
-e2pja <- get_lmer_reporting_values(pja_mod)
-
-# Total duration of passive joint attention.
-pja_time_mod <- lmer(pja_length ~ age * Condition + (1 | video), data = e2ja,
-                     control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5)))
-summary(pja_time_mod) # singular - convergence code: 0, age beta=-18.89 t(80) = 2.72 p=.008
-e2pja_time <- get_lmer_reporting_values(pja_time_mod)
-pjat_bmod <- stan_glmer(pja_length ~ age * Condition + (1|video), data=e2ja)
-summary(pjat_bmod) # age: est: -17.9 95% CI = [-33.1,-2.2]
-
-# Total duration of coordinated joint attention.
-cja_time_mod <- lmer(cja_length ~ age * condition + (1 | video), data = e2ja,
-                     control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5)))
-summary(cja_time_mod) # singular - convergence code: 0, marginal age: beta=37.35 t(80) = 1.95 p=.05
-cjat_bmod <- stan_glmer(cja_length ~ age * Condition + (1|video), data=e2ja)
-summary(cjat_bmod) # age: est: 35.3 95% CI = [-6.1,77.4] NOT SIGNIFICANT
-
-e2_cja <- e2ja %>% group_by(Condition) %>%
-  tidyboot_mean(cja)
-```
-
-### Exploratory Analyses
+\hypertarget{exploratory-analyses}{%
+\subsubsection{Exploratory Analyses}\label{exploratory-analyses}}
 
 Four additional exploratory regressions with a similar structure were carried out to predict the number and duration of coordinated and passive JA episodes.
-The regression predicting the number of episodes of coordinated JA found a significant main effect of condition ($\beta=`r e2cja["ConditionActivity Video","beta"]`$, t(`r e2cja["ConditionActivity Video","df"]`) = `r e2cja["ConditionActivity Video","tval"]`, *p*=`r e2cja["ConditionActivity Video","pval"]`), with more episodes of coordinated JA occurring after the Activity Video (mean: `r round(subset(e2_cja, Condition=="Activity Video")$mean,2)`, 95% CI: [`r round(subset(e2_cja, Condition=="Activity Video")$ci_lower,2)`, `r round(subset(e2_cja, Condition=="Activity Video")$ci_upper,2)`]) than after the Control Video (mean: `r round(subset(e2_cja, Condition=="Science Video")$mean,2)`, 95% CI: [`r round(subset(e2_cja, Condition=="Science Video")$ci_lower,2)`, `r round(subset(e2_cja, Condition=="Science Video")$ci_upper,2)`]).
-There was no significant effect of age, but there was a significant interaction of age and condition ($\beta=`r e2cja["age:ConditionActivity Video","beta"]`$, t(`r e2cja["age:ConditionActivity Video","df"]`) = `r e2cja["age:ConditionActivity Video","tval"]`, *p*=`r e2cja["age:ConditionActivity Video","pval"]`), shown in Figure \ref{fig:e2ja-coord}, revealing that older children in the Activity Video condition had more episodes of coordinated JA than children in the Control Video condition.
+The regression predicting the number of episodes of coordinated JA found a significant main effect of condition (\(\beta=1.37\), t(80) = 2.59, \emph{p}=0.01), with more episodes of coordinated JA occurring after the Activity Video (mean: 6.71, 95\% CI: {[}5.92, 7.61{]}) than after the Control Video (mean: 5.34, 95\% CI: {[}4.72, 5.98{]}).
+There was no significant effect of age, but there was a significant interaction of age and condition (\(\beta=5.24\), t(80) = 2.40, \emph{p}=0.02), shown in Figure \ref{fig:e2ja-coord}, revealing that older children in the Activity Video condition had more episodes of coordinated JA than children in the Control Video condition.
 The regression predicting the total duration of coordinated JA episodes revealed no significant effects.
 
-In the regression predicting the number of episodes of passive JA, there was a main effect of age ($\beta=`r e2pja["ConditionActivity Video","beta"]`$, t(`r e2pja["ConditionActivity Video","df"]`) = `r e2pja["ConditionActivity Video","tval"]`, *p*=`r e2pja["ConditionActivity Video","pval"]`), showing that older children had more episodes of passive JA with their caregiver.
-The regression predicting the total duration of passive JA revealed a main effect of age ($\beta=`r e2pja_time["ConditionActivity Video","beta"]`$, t(`r e2pja_time["ConditionActivity Video","df"]`) = `r e2pja_time["ConditionActivity Video","tval"]`, *p*=`r e2pja_time["ConditionActivity Video","pval"]`), revealing that older children spent more time in passive JA with their caregiver.
+In the regression predicting the number of episodes of passive JA, there was a main effect of age (\(\beta=0.11\), t(6.90) = 0.27, \emph{p}=0.80), showing that older children had more episodes of passive JA with their caregiver.
+The regression predicting the total duration of passive JA revealed a main effect of age (\(\beta=0.40\), t(80) = 0.16, \emph{p}=0.88), revealing that older children spent more time in passive JA with their caregiver.
 Overall, these results show that the older children in our sample engage in more and longer episodes of joint attention with their caregivers, and suggest that the Activity Video strengthened this trend in the number of episodes of coordinated JA.
 
-```{r e2ja-coord, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=5.5, fig.height=3.5, fig.cap = "\\label{fig:e2ja-coord} The number of episodes of coordinated JA by condition and age in Experiment 2.
-Older children in the Activity Video condition engaged in more episodes of coordinated JA with their caregiver than dyads in the Control Video condition."}
+\begin{figure}[H]
 
-#Episodes of coordinated joint attention
-ms_cja <- d %>% group_by(Condition) %>%
-  tidyboot_mean(cja)
+{\centering \includegraphics{figs/e2ja-coord-1}
 
-e2cja <- ggplot(ms_cja, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
-  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
-  geom_point(data=d, aes(x=Condition, y=cja), alpha=.2, position = position_jitterdodge()) +
-  xlab("Condition") + ylab("Episodes of Coordinated JA") +
-  langcog::scale_fill_solarized() + ggthemes::theme_few() + theme(legend.position="none")
+}
 
-e2cja_age = ggplot(d, aes(x = age, y = cja, group=Condition, colour = Condition)) +
-  geom_point(alpha=.7) + geom_smooth(method='lm') + 
-  xlab("Age (years)") + ylab("Episodes of Coordinated JA") +
-  langcog::scale_colour_solarized() + ggthemes::theme_few()
+\caption{\label{fig:e2ja-coord} The number of episodes of coordinated JA by condition and age in Experiment 2.
+Older children in the Activity Video condition engaged in more episodes of coordinated JA with their caregiver than dyads in the Control Video condition.}\label{fig:e2ja-coord}
+\end{figure}
 
-print(e2cja_age)
-#multiplot(e2cja, e2tja_age, cols=4, layout=matrix(c(1,2,2,2), nrow=1))
-```
-
-# Discussion
+\hypertarget{discussion-1}{%
+\section{Discussion}\label{discussion-1}}
 
@@
 
-# Acknowledgements
+\hypertarget{acknowledgements}{%
+\section{Acknowledgements}\label{acknowledgements}}
 
@@
 
-# References
-```{r create_r-references}
-r_refs(file = "library.bib")
-```
+\hypertarget{references}{%
+\section{References}\label{references}}
 
@@
 
-<div id = "refs"></div>
+\hypertarget{refs}{}
+\leavevmode\hypertarget{ref-Baldwin1991}{}%
+Baldwin, D. (1991). Infants' contribution to the achievement of joint reference. \emph{Child Development}, \emph{62}, 875--890.
+
+\leavevmode\hypertarget{ref-lme4}{}%
+Bates, D., Mächler, M., Bolker, B., \& Walker, S.
+(2015).
+Fitting linear mixed-effects models using lme4.
+\emph{Journal of Statistical Software}, \emph{67}(1), 1--48.
+\url{http://doi.org/10.18637/jss.v067.i01}
+
+\leavevmode\hypertarget{ref-Bigelow2004}{}%
+Bigelow, A. E., MacLean, K., \& Proctor, J. (2004). The role of joint attention in the development of infants' play with objects. \emph{Developmental Science}, \emph{7}, 518--526.
+
+\leavevmode\hypertarget{ref-Breitenstein2016}{}%
+Breitenstein, S.
+M., Fogg, L., Ocampo, E.
+V., Acosta, D.
+I., \& Gross, D.
+(2016).
+Parent use and efficacy of a self-administered, tablet-based parent training intervention: A randomized controlled trial.
+\emph{JMIR mHealth and uHealth}, \emph{4}(2), e36.
+\url{http://doi.org/10.2196/mhealth.5202}
+
+\leavevmode\hypertarget{ref-Breitenstein2014}{}%
+Breitenstein, S.
+M., Gross, D., \& Christophersen, R.
+(2014).
+Digital delivery methods of parenting training interventions: A systematic review.
+\emph{Worldviews on Evidence-Based Nursing}, \emph{11}, 168--176.
+
+\leavevmode\hypertarget{ref-Cartmill2013}{}%
+Cartmill, E.
+A., Armstrong, B.
+F., Gleitman, L.
+R., Goldin-Meadow, S., Medina, T.
+N., \& Trueswell, J.
+C.
+(2013).
+Quality of early parent input predicts child vocabulary 3 years later.
+\emph{Proceedings of the National Academy of Sciences}, \emph{110}(28), 11278--11283.
+\url{http://doi.org/10.1073/pnas.1309518110}
+
+\leavevmode\hypertarget{ref-Jamaica2014}{}%
+Gertler, P., Heckman, J., Pinto, R., Zanolini, A., Vermeersch, C., Walker, S., \ldots{} Grantham-McGregor, S.
+(2014).
+Labor market returns to an early childhood stimulation intervention in jamaica.
+\emph{Science}, \emph{344}(6187), 998--1001.
+\url{http://doi.org/10.1126/science.1251178}
+
+\leavevmode\hypertarget{ref-Hart1995}{}%
+Hart, B., \& Risley, T. R. (1995). \emph{Meaningful differences in the everyday experience of young american children}. Baltimore, MD: Brookes.
+
+\leavevmode\hypertarget{ref-Heckman2006}{}%
+Heckman, J. J. (2006). Skill formation and the economics of investing in disadvantaged children. \emph{Science}, \emph{312}(5782), 1900--1902. \url{http://doi.org/10.1126/science.1128898}
+
+\leavevmode\hypertarget{ref-Hembacher2018}{}%
+Hembacher, E., \& Frank, M.
+C.
+(2018).
+The early parenting attitudes questionnaire: Measuring intuitive theories of parenting and child development.
+\emph{PsyArXiv}.
+\url{http://doi.org/10.31234/osf.io/hxk3d}
+
+\leavevmode\hypertarget{ref-HirshPasek2015}{}%
+Hirsh-Pasek, K., Adamson, L.
+B., Bakeman, R., Owen, M.
+T., Golinkoff, R.
+M., Pace, A., \ldots{} Suma, K.
+(2015).
+The contribution of early communication quality to low-income children's language success.
+\emph{Psychological Science}, \emph{26}(7), 1071--1083.
+\url{http://doi.org/10.1177/0956797615581493}
+
+\leavevmode\hypertarget{ref-spacy2}{}%
+Honnibal, I., Matthew AND Montani. (2017). SpaCy 2: Natural language understanding with bloom embeddings, convolutional neural networks and incremental parsing. \emph{To Appear}.
+
+\leavevmode\hypertarget{ref-Malvern2004}{}%
+Malvern, D., Richards, B. J., Chipere, N., \& Durán, P. (2004). \emph{Lexical diversity and language development}. Palgrave Macmillan.
+
+\leavevmode\hypertarget{ref-Marchman2008}{}%
+Marchman, V.
+A., \& Fernald, A.
+(2008).
+Speed of word recognition and vocabulary knowledge in infancy predict cognitive and language outcomes in later childhood.
+\emph{Developmental Science}, \emph{11}, F9--F16.
+
+\leavevmode\hypertarget{ref-McCarthy2010}{}%
+McCarthy, P. M., \& Jarvis, S. (2010). MTLD, vocd-d, and hd-d: A validation study of sophisticated approaches to lexical diversity assessment. \emph{Behavior Research Methods}, \emph{42}(2), 381--392.
+
+\leavevmode\hypertarget{ref-PerryPreschool2004}{}%
+Schweinhart, L.
+J., Montie, J., Xiang, Z., Barnett, W.
+S., Belfield, C.
+R., \& Nores, M.
+(2004).
+\emph{Lifetime effects: The highscope perry preschool study through age 40}.
+Ypsilanti, MI: HighScope Press.
+
+\leavevmode\hypertarget{ref-datavyu}{}%
+Team, D. (2014). Datavyu: A video coding tool. \emph{Databrary Project}. Retrieved from \url{http://datavyu.org}
+
+\leavevmode\hypertarget{ref-Weisberg2013}{}%
+Weisberg, D. S., Hirsh-Pasek, K., \& Golinkoff, R. M. (2013). Guided play: Where curricular goals meet a playful pedagogy. \emph{Mind, Brain, and Education}, \emph{7}, 104--112.
+
+\leavevmode\hypertarget{ref-Wood1976}{}%
+Wood, D., Bruner, J. S., \& Ross, G. (1976). The role of tutoring in problem solving. \emph{Journal of Child Psychology and Psychiatry}, \emph{17}, 89--100.
+
 \endgroup
+
+\end{document}

### 2019-08-12 parenting_obs_e2/Lexical_Diversity_Analysis.Rmd
fighting papaja

@@
 ggplot(ms_lex, aes(x = condition, y = mean, fill = condition)) + 
-  ylim(0.0, 0.6)+
-  geom_bar(stat="identity") + 
+  ylim(0.0, 0.6) + geom_bar(stat="identity") + 
   geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
              position = position_dodge(width = .9))+
-  xlab("Condition") + 
-  ylab("TTR") +
-  langcog::scale_colour_solarized()  +
-  ggthemes::theme_few() 
+  xlab("Condition") + ylab("TTR") + langcog::scale_colour_solarized() + ggthemes::theme_few() 
 ggsave(file="figs/e2_TTR.pdf", width=3, height=3)
@@
 ```{r echo=FALSE}
+slen <- lmer(len_sentence ~ condition * age + (1|video), data=d)
+summary(slen)
+
 ms_length <- d %>%

### 2019-08-30 paper/appendix.tex
cleaning up repo, full switch to papaja

--- 2019-03-14 paper/cogsci2019/cogsci2019.tex
@@
-% Template for Cogsci submission with R Markdown
+\clearpage
+\makeatletter
+\efloat@restorefloats
+\makeatother
 
-% Stuff changed from original Markdown PLOS Template
-\documentclass[10pt, letterpaper]{article}
+\begin{appendix}
+\section{}
+\hypertarget{experiment-1}{%
+\subsection{Experiment 1}\label{experiment-1}}
 
-\usepackage{cogsci}
-\usepackage{pslatex}
-\usepackage{float}
-\usepackage{caption}
+\hypertarget{video-a-6-11.9-months-pick-it-up}{%
+\subsubsection{Video A (6-11.9 months) ``Pick it
+up''}\label{video-a-6-11.9-months-pick-it-up}}
 
-% amsmath package, useful for mathematical formulas
-\usepackage{amsmath}
+Parents are told to encourage their child to pick up and drop individual
+objects. They are also encouraged to place toys on a small cloth and
+show the child that they can drag the cloth towards them to reach the
+toys.
 
-% amssymb package, useful for mathematical symbols
-\usepackage{amssymb}
+Props: cloth, plastic horse, plastic sheep, plastic elephant, toy car
 
-% hyperref package, useful for hyperlinks
-\usepackage{hyperref}
+\hypertarget{video-b-6-11.9-months-animal-sounds}{%
+\subsubsection{Video B (6-11.9 months) ``Animal
+sounds''}\label{video-b-6-11.9-months-animal-sounds}}
 
-% graphicx package, useful for including eps and pdf graphics
-% include graphics with the command \includegraphics
-\usepackage{graphicx}
+Parents are told to call different animals and imitate different sounds
+the animals make. They are also encourgaed to observe which animal the
+child prefers.
 
-% Sweave(-like)
-\usepackage{fancyvrb}
-\DefineVerbatimEnvironment{Sinput}{Verbatim}{fontshape=sl}
-\DefineVerbatimEnvironment{Soutput}{Verbatim}{}
-\DefineVerbatimEnvironment{Scode}{Verbatim}{fontshape=sl}
-\newenvironment{Schunk}{}{}
-\DefineVerbatimEnvironment{Code}{Verbatim}{}
-\DefineVerbatimEnvironment{CodeInput}{Verbatim}{fontshape=sl}
-\DefineVerbatimEnvironment{CodeOutput}{Verbatim}{}
-\newenvironment{CodeChunk}{}{}
+Props: plastic sheep, plastic horse, plastic frog, plastic cow, bowls
 
-% cite package, to clean up citations in the main text. Do not remove.
-\usepackage{apacite}
+\hypertarget{video-c-12-17.9-months-give-me-the-toy}{%
+\subsubsection{Video C (12-17.9 months) ``Give me the
+toy''}\label{video-c-12-17.9-months-give-me-the-toy}}
 
-% KM added 1/4/18 to allow control of blind submission
-\cogscifinalcopy
+Parents are told to ask their child to hand over individual toys. They
+are also encouraged to praise the child after they give them the toys,
+and repeat the process until the child could follow the verbal
+instructions.
 
-\usepackage{color}
+Props: toy boat, plastic frog, plastic elephant, toy bus
 
-% Use doublespacing - comment out for single spacing
-%\usepackage{setspace}
-%\doublespacing
+\hypertarget{video-d-12-17.9-months-classifying-my-toys}{%
+\subsubsection{Video D (12-17.9 months) ``Classifying my
+toys''}\label{video-d-12-17.9-months-classifying-my-toys}}
 
-% % Text layout
-% \topmargin 0.0cm
-% \oddsidemargin 0.5cm
-% \evensidemargin 0.5cm
-% \textwidth 16cm
-% \textheight 21cm
+Parents are told to place toys of different sizes (big or small) in two
+hoops. They are also encouraged to ask their child to distinguish
+between two objects and identify which one is larger.
 
-\title{Understanding the impact of electronically-delivered parenting advice}
+Props: two yellow and green rings, big car, small car, big horse, small
+horse
 
-\author{{\large\bf Hanwen Vivian~Zhang} (\texttt{vivian3@stanford.edu}) \\ {\large\bf George~Kachergis} (\texttt{george.kachergis@gmail.com}) \\ {\large\bf Michael C.~Frank} (\texttt{mcfrank@stanford.edu}) \\  Department of Psychology, Stanford University \\  Stanford, CA 94305 USA}
+\hypertarget{video-e-18-23.9-months-my-toys}{%
+\subsubsection{Video E (18-23.9 months) ``My
+toys''}\label{video-e-18-23.9-months-my-toys}}
 
-\begin{document}
+Parents are told to show the child toys of the same shape but different
+sizes, to place one of the objects in a basket and to ask the child to
+take out the object. They are also encouraged to ask their child if the
+object is bigger or smaller compared to its pair.
 
-\maketitle
+Props: two buckets, big car, small car, big horse, small horse
 
-\begin{abstract}
-Early parenting practices play an important role in shaping the future
-outcomes of young children (Hart \& Risley, 1995; Heckman, 2006). In
-particular, high-quality early interactions and language input appear to
-facilitate language learning and result in higher levels of school
-performance. The rise of phone- and tablet-based parenting applications
-(``apps'') holds the promise of delivering low-cost, positive
-interventions on parenting style to a variety of different populations.
-Of special interest are the parents of very young children, who are
-often difficult to reach in other ways. Yet little is known about the
-effects of communicating to parents through app-based interventions. In
-a study of one commercial app offering a collection of age-appropriate
-activity videos, we find that the quality of parent-child interactions
-increases in some ways as a result of using the app. Specifically, the
-lexical diversity of parents' child-directed speech increases, and
-measures of joint attention show\ldots{}
+\hypertarget{video-f-18-23.9-months-the-orchestra}{%
+\subsubsection{Video F (18-23.9 months) ``The
+Orchestra''}\label{video-f-18-23.9-months-the-orchestra}}
 
-\textbf{Keywords:}
-digital parenting advice; joint attention; lexical diversity; guided
-play;
-\end{abstract}
+Parents are told to give their child a musical instrument to play. They
+are also encouraged to play a song and see if the child follows the
+rhythm.
 
-\section{Introduction}\label{introduction}
+Props: maracas, drum, tambourine, clapper
 
-Young children spend a large portion of their waking time at play,
-variously manipulating objects, exploring their environment, and
-interacting with caregivers and peers. Playing with objects allows them
-to discover hidden object properties and relations, and to build a
-causal understanding of how objects interact (e.g., Schulz \& Bonawitz,
-2007). Meanwhile, play also gives children an opportunity to set and
-achieve goals (e.g., build a tower) and to practice a wide range of
-motor skills (e.g., stacking) that will help them navigate the world
-(Singer, Golinkoff, \& Hirsh-Pasek, 2006). Social play can help children
-learn about human relationships, both through imitation of adult
-behaviors and by experiencing and learning to process emotional events
-such as failures (Singer et al., 2006). Of course, young children are
-rarely playing in isolation: caregivers often provide encouragement and
-guidance while scaffolding a child's play (Kaye, 1970; Wood, Bruner, \&
-Ross, 1976). Indeed, parenting practices early in childhood have been
-shown to play an important role in shaping the future outcomes of young
-children (Hart \& Risley, 1995; Heckman, 2006). While interventions
-often have trouble reaching many parents of very young children, the
-proliferation of mobile devices offers a good avenut for the digital
-delivery of parenting advice (Breitenstein, Gross, \& Christophersen,
-2014). However, the efficacy of digital parenting advice has not been
-widely proven.
+\hypertarget{experiment-2}{%
+\subsection{Experiment 2}\label{experiment-2}}
 
-\subsection{Guided Play Scaffolds
-Learning}\label{guided-play-scaffolds-learning}
+\hypertarget{video-a-12-17.9-months-give-me-the-toy}{%
+\subsubsection{Video A (12-17.9 months) ``Give me the
+toy''}\label{video-a-12-17.9-months-give-me-the-toy}}
 
-Children's early play behaviors are often assisted by more skilled and
-knowledgeable play partners such as their caregivers and older siblings
-(Kaye, 1970). Under such expert guidance, children are encouraged and
-motivated to engage in more advanced play, undertaking explorations that
-push the boundaries of what they would be able to do unaided (Vygotsky,
-1980). These tutorial interactions have been shown to be important
-components of child development (Wood et al., 1976). Thus, with the
-knowledge of both play and tutorial interactions, guided play, which
-consists of both active and enjoyable activities as well as close
-guidance of adults (Hirsh-Pasek \& Golinkoff, 2008) has drawn
-researchers' interest. A study of preschoolers showed that guided play
-scaffolds the environment while still allowing children to maintain a
-large degree of control, and it outperforms direct-instruction
-approaches in encouraging a variety of positive academic outcomes
-(Weisberg, Hirsh-Pasek, \& Golinkoff, 2013). Another study found that
-guided play could facilitate children's vocabulary and comprehensive
-language development and subsequent literacy skills (Massey, 2013).
+Parents are told to ask their child to hand over individual toys. They
+are also encouraged to praise the child after they give them the toys,
+and repeat the process until the child could follow the verbal
+instructions.
 
-\subsection{Improving Parenting Practices and Language
-Use}\label{improving-parenting-practices-and-language-use}
+Props: plastic pig, plastic horse, plastic dog, plastic cat, plastic cow
 
-Thus, including guided play in parenting practices early on is crucial
-and will help with children's later performances in academic and social
-situations. To intervene in parenting practices, Suskind and others did
-a parent-directed home-visiting intervention experiment in 2015 for
-children of low socioeconomic status. They showed that parents in
-experimental group have greater knowledge of language development and
-this effect sustained four months after the intervention. However,
-although a number of interactive measures increased during the
-experiment, including the number of word tokens, conversational turns,
-and child vocalizations, these increases did not sustain after the
-intervention (D. L. Suskind et al., 2015). That changes did not sustain
-could be due to the intervention itself, or could merely be that the
-methods of home-visiting is not sustainable enough for parents to easily
-and constantly get parenting advice. Thus, new methods of delivering
-parenting advice should be considered.
+\hypertarget{video-b-12-17.9-months-classifying-my-toys}{%
+\subsubsection{Video B (12-17.9 months) ``Classifying my
+toys''}\label{video-b-12-17.9-months-classifying-my-toys}}
 
-\subsection{Effectiveness of Digital
-Delivery}\label{effectiveness-of-digital-delivery}
+Parents are told to place toys of different sizes (big or small) in two
+hoops. They are also encouraged to ask their child to distinguish
+between two objects and identify which one is larger.
 
-With the widespread use of smartphones and tablets worldwide,
-digitally-delivered interventions could address many of the logistical
-barriers that have limited scaling up face-to-face delivery methods. A
-review of 11 studies verified that digital delivery is a promising means
-of effectively distributing interventions (Breitenstein et al., 2014).
-However, the parent and child outcomes assessed in the review
-(e.g.infant positive behaviors, satisfaction, emotional symptoms etc.)
-did not address the nature or quality of parent-infant interactions at a
-detailed level, like if the interventions lead to children paying more
-attention, or vocabulary changes in parents' language usages. Although
-digitally-delivered ac-tivities are designed to promote learning and
-cognitive development, it is unclear how they might affect these
-dimensions of parent-child interactions. Thus, we want to conduct this
-experiment to explore if and how digital scaffolding of activities
-affect the social and linguistic characteristics of parent-child
-ineractions. The quality of parent-child interactions can be measured by
-both the social engagement of parents (e.g., joint attention to objects
-in the environment)(Bigelow, MacLean, \& Proctor, 2004) and the quality
-of language (e.g., vocabulary diversity) (Malvern, Richards, Chipere, \&
-Durán, 2004).
+Props: two yellow and green rings, big car, small car, big horse, small
+horse
 
-\section{Experiment 1}\label{experiment-1}
+\hypertarget{video-c-12-17.9-months-geometric-shapes-jigzsaw-puzzle}{%
+\subsubsection{Video C (12-17.9 months) ``Geometric shapes jigzsaw
+puzzle''}\label{video-c-12-17.9-months-geometric-shapes-jigzsaw-puzzle}}
 
-In Experiment 1, we invited parents of 6- to 24-month-old infants
-visiting the Children's Discovery Museum in San Jose to complete
-activities from the Kinedu app. Parents were randomly assigned to the
-video group or the control group; parents in the video group watched a
-video from the Kinedu app (matched to their child's age), and then
-performed the activity with their child using the props from the video.
-Parents in the control group did not watch a Kinedu video, instead they
-were given the same props and were told to play with their infants as
-they would at home.
+Parents are told to encourage their child to name different shapes on a
+jigzsaw puzzle. Then they are told to undo the puzzle and invite the
+child to complete the puzzle.
 
-\subsection{Method}\label{method}
+Props: A jigzsaw puzzle of geometric shapes
 
-\subsubsection{Participants.}\label{participants.}
+\hypertarget{video-d-18-23.9-months-my-toys}{%
+\subsubsection{Video D (18-23.9 months) ``My
+toys''}\label{video-d-18-23.9-months-my-toys}}
 
-60 infants (F = 42, M = 18) aged 6-24 months (20 6-11.9 month-olds, 20
-12-17.9 month-olds, and 20 18-24 month-olds) and their parents
-participated in a museum in northern California. We included infants who
-were exposed to English at least 50 percent of the time (n = 58) or who
-were exposed less but whose participating parent reported that they
-primarily speak English with their child at home (n = 2). 61\% of
-participants (n = 37) had been exposed to two or more languages as
-indicated by their parent. Parents identified their children as White (n
-= 25), Asian (n = 11), African American/Black (n = 2), Biracial (n =
-12), other (n = 5), or declined to state (n = 5). Fifteen parents
-reported their child was of Hispanic origin. Parents tended to be
-highly-educated, with reports of highest level of education ranging from
-completed high school (n = 5), some college (n = 6), four-year college
-(n = 14), some graduate school (n = 1), to completed graduate school (n
-= 28) or declined to state (n = 6).
+Parents are told to show the child toys of the same shape but different
+sizes, to place one of the objects in a basket and to ask the child to
+take out the object. They are also encouraged to ask their child if the
+object is bigger or smaller compared to its pair.
 
-\subsubsection{Materials.}\label{materials.}
+Props: two buckets, big car, small car, big horse, small horse
 
-Stimuli included videos from the Kinedu (Kinedu Inc.) commercial
-parenting application. The videos were designed to show activities to
-parents that they could perform with their child in order to foster
-cognitive and physical development, and were targeted to the child's age
-and level of development. In each video, an adult and child perform the
-activity while a narrator explains the activity and its purpose. We
-selected two videos for each of three age groups in our sample (6-11.9
-months, 12-17.9 months, 18-23.94 months). More information about the
-specific videos is available in the Appendix. Participants were also
-given a set of props corresponding to those in the video they watched so
-that they could complete the activity. The props associated with each
-video are listed in the Appendix.
+\hypertarget{video-e-18-23.9-months-the-orchestra}{%
+\subsubsection{Video E (18-23.9 months) ``The
+Orchestra''}\label{video-e-18-23.9-months-the-orchestra}}
 
-Participants were randomly assigned to either the \emph{Video} condition
-or the \emph{Control} condition. Participating parents in the Video
-condition were assigned to watch one of the two activity videos
-available for their child's age group. Participating parents in the
-Control condition watched no activity video, and were merely asked to
-play with their child as they normally would. The Control condition was
-yoked to the Activity Video condition such that for every participant in
-the Video condition who saw a particular video and received the
-associated props, a participant in the Control condition received the
-same props but did not watch the activity video. Parents also completed
-the Parenting Attitudes Questionnaire (PAQ). The PAQ measures parents'
-attitudes about parenting and child development along three dimensions:
-rules and respect, early learning, and affection and attachment.
+Parents are told to give their child a musical instrument to play. They
+are also encouraged to play a song and see if the child follows the
+rhythm.
 
-\subsection{Procedure.}\label{procedure.}
+Props: maracas, drum, tambourine, clapper
 
-After providing informed consent, parents in the Video condition watched
-the assigned activity video on a laptop with headphones. To ensure that
-parents could give the video their full attention, the experimenter
-played with the infant with a set of toys (different from the
-experimental props used in the study) while the video was being played.
-Immediately following the video, each parent-child dyad was provided
-with the props to complete the activity they had viewed. The toys were
-placed on a large foam mat, and parents were instructed to sit on the
-mat with their child and re-create the activity they had viewed for a
-period of three minutes. In the Control condition, after consenting
-parents were told to play with their child as they would at home with
-the provided props for a period of three minutes. They were not given
-any additional instructions about how to use the props.
+\hypertarget{video-f-18-23.9-months-my-yellow-toys}{%
+\subsubsection{Video F (18-23.9 months) ``My Yellow
+Toys''}\label{video-f-18-23.9-months-my-yellow-toys}}
 
-In both conditions, two video cameras were used to record the play
-session from different angles, and parents were fitted with a wireless
-audio recorder to record their child-directed speech. After three
-minutes of play had elapsed, parents were told they could stop playing
-and cameras and audio were turned off. Parents were then asked to
-complete the PAQ before being debriefed.
+Parents are told to show their child yellow toys and to ask, ``What
+color are they?'' They are also told to give the child toys of different
+colors, to ask them to only play with the yellow ones, and to praise the
+child after they do so.
 
-\subsubsection{Joint Attention Coding
-Procedure.}\label{joint-attention-coding-procedure.}
-
-The video of each session was manually coded for episodes of joint
-attention using the Datavyu software (Team, 2014). The video taken at
-floor level was coded by default, but the other video was referred to if
-the participants were not visible or if there was technical difficulty
-with the first camera. Each session's video was coded for episodes of
-coordinated joint attention, episodes of passive joint attention, and
-parental bids for joint attention. Parental bids for joint attention
-were defined as any attempt to initiate joint attention (i.e labeling,
-pointing, or otherwise drawing attention to an object) that did not
-result in passive or coordinated joint attention. If more than 3 seconds
-elapsed between bids, they were coded as separate attempts. An episode
-of joint attention was considered passive if both participants visually
-focused on an object for a minimum of 3 seconds but the child did not
-acknowledge the parent. If either participant looked away from the
-object for less than 3 seconds and then returned to the same object it
-was considered part of the same period of joint attention. A joint
-attention episode was considered coordinated if both participants
-visually focused on an object for a minimum of 3 seconds and at some
-point in the interaction the child indicated awareness of interaction
-with some overt behavior toward the parent such as looking at their
-face, gesturing, vocalizing, or turn-taking.
-
-A second coder independently coded a third of the videos (i.e., 20 of
-the 60 videos, approximately equally distributed across ages) to
-establish reliability. The two coders had a reliability of ICC = 0.80
-with 95\% confident interval (CI) = {[}0.57,0.92{]} (p \textless{} 0.05)
-for number of parent bids for JA; ICC = 0.20 with 95\% CI =
-{[}-0.26,0.58{]} for number of passive JA episodes; ICC = 0.66 with 95\%
-CI = {[}0.32,0.85{]} (p \textless{} 0.05) for number of coordinated JA
-episodes; ICC = 0.24 with 95\% CI = {[}-0.21,0.61{]} for total duration
-of passive JA episodes, and ICC = 0.62 with 95\% CI = {[}0.27,0.83{]} (p
-\textless{} 0.05) for total duration of coordinated JA episodes.
-
-\section{Results}\label{results}
-
-The transcripts and hand-coded behavioral data was analyzed according to
-our preregistration\footnote{Preregistration:
-  \url{https://osf.io/2bpdf/}{]}}. Below we first describe the lexical
-diversity results, followed by the joint attention results.
-
-\subsection{Lexical Diversity}\label{lexical-diversity}
-
-Parents' child-directed speech during the play sessions was transcribed.
-For each transcript, the words were lemmatized using Honnibal (2017),
-and the word \emph{types} (unique words) and \emph{tokens} (total words)
-were then tallied and the type-token ratio (TTR) calculated as a measure
-of lexical diversity. Although TTR was our preregistered measure of
-lexical diversity, TTR is correlated with the length of a text, whereas
-the measure of textual lexical diversity (MTLD) is not (McCarthy \&
-Jarvis, 2010). Thus, we also measure lexical diversity with MTLD, which
-is calculated as the mean length of sequential word strings in a text
-that maintain a given TTR value (here, .720).
-
-We fit a mixed-effects linear regression predicting TTR as a function of
-condition, age (scaled and 0-centered), gender, and parent's education
-level with a random intercept per video using lme4 (Bates, Mächler,
-Bolker, \& Walker, 2015). There was significantly lower TTR in the Video
-condition (mean: 0.32) than in the Control condition (mean: 0.43,
-\(\beta=-.12\), t(39.9) = 4.25, \emph{p}\textless{}.001). There were no
-significant effects of age, gender, or parent's level of education. A
-similar mixed-effects linear regression instead predicting MTLD also
-found significantly lower lexical diversity in the Video condition
-(mean: 15.7) than in the Control condition (mean: 21.9,
-\(\beta=-11.67\), t(43) = 3.08, \emph{p}\textless{}.01), with no other
-significant effects. Figure 1 shows the mean of each lexical diversity
-measure (TTR and MTLD) by condition.
-
-We also conducted similar regressions predicting the number of word
-tokens and types, finding only a significant effect of condition on the
-number of word tokens (\(\beta=57.23\), t(34.4)=2.19,
-\emph{p}\textless{}.05), with parents using more words in the Video
-condition (mean: 225, 95\% CI: {[}197,252{]}) than in the Control
-condition (mean: 165, 95\% CI: {[}139,193{]}).
-
-(Table with mean and SD of tokens, types, and TTR)
-
-\begin{CodeChunk}
-\begin{figure}[H]
-
-{\centering \includegraphics{figs/e1lex_div-1}
-
-}
-
-\caption[Mean lexical diversity scores by condition (left]{Mean lexical diversity scores by condition (left: Type/Token ratio, right: MTLD) in Experiment 1.
-Error bars show bootstrapped 95 percent confidence intervals (CIs).}\label{fig:e1lex_div}
-\end{figure}
-\end{CodeChunk}
-
-Word tokens and word types
-
-\begin{CodeChunk}
-\begin{figure}[H]
-
-{\centering \includegraphics{figs/e1token_type-1}
-
-}
-
-\caption[Mean number of word types and word tokens by condition in Experiment 1]{Mean number of word types and word tokens by condition in Experiment 1.}\label{fig:e1token_type}
-\end{figure}
-\end{CodeChunk}
-
-\subsection{Joint Attention}\label{joint-attention}
-
-\begin{CodeChunk}
-\begin{figure}[H]
-
-{\centering \includegraphics{figs/e1ja-graphs-1}
-
-}
-
-\caption[Mean number of bids and episodes of Joint Attention in Experiment 1]{Mean number of bids and episodes of Joint Attention in Experiment 1.}\label{fig:e1ja-graphs}
-\end{figure}
-\end{CodeChunk}
-
-\begin{CodeChunk}
-\begin{figure}[H]
-
-{\centering \includegraphics{figs/e1ja-graphs-pass-coord-1}
-
-}
-
-\caption[Average number of passive and coordinated episodes of JA in Experiment 1]{Average number of passive and coordinated episodes of JA in Experiment 1.}\label{fig:e1ja-graphs-pass-coord}
-\end{figure}
-\end{CodeChunk}
-
-\subsection{Discussion}\label{discussion}
-
-Both the number of tokens and types are higher in the experimental
-condition, while lexical diversity (Type/Token ratio) is higher in the
-control condition. Parents may be relatively more repetetive in the
-experimental condition since they are attempting to stick to a specific
-prescribed task, but they talk more overall. Demographics and PAQ do not
-interact with condition, but there is a marginal effect of RR score on
-lexical diversity (lower diversity for higher RR scores), and marginal
-effects of parent education on word types and tokens (more types and
-tokens for higher parent education).
-
-There was a main effect of condition on total bids for joint attention.
-Parents in the experimental condition (i.e., those who saw a video
-demonstrating an activity) made a greater number of bids for joint
-attention with their child. There was no effect of condition on the
-number of episodes of either passive or coordinated joint attention, or
-the duration of these episodes. There is a marginal effect of gender on
-bids for joint attention, with parents of males producing more bids.
-There is a marginal interaction between RR scores and condition on
-passive joint attention, such that the experimental condition increased
-the number of episodes of PJA to a greater extent for people with high
-RR scores. While the electronically-delivered parenting advice increased
-the number of bids for joint attention by parents, it did not
-significantly effect the number or duration of episodes of joint
-attention. One possibility is that child variables had a comparatively
-larger impact on the attainment of joint attention.
-
-\section{Experiment 2}\label{experiment-2}
-
-Experiment 1 found that compared to parents who did not watch a video,
-parents who watched a Kinedu video spoke more words overall, but had
-lower lexical diversity. Parents who watched a video also made more bids
-for joint attention, although these bids did not result in more episodes
-of joint attention compared to the control group. In Experiment 2 we
-attempt to replicate the findings from Experiment 1 with a restricted
-number of preregistered predictions. We will additionally include a
-second control condition, in which the same activities are described in
-written form, rather than being demonstrated in video. This manipulation
-will help determine what the contribution of the video demonstration is
-in producing the observed effects on parent-child interactions.
-
-\subsection{Method}\label{method-1}
-
-\subsubsection{Participants.}\label{participants.-1}
-
-83 infants (F = 37, M = 47) aged 12-24 months (42 12-17.9 month-olds, 42
-18-24 month-olds) and their parents participated in the same museum as
-Experiment 1. We included infants who were exposed to English at least
-75 percent of the time or who were exposed less but whose participating
-parent reported that they primarily speak English with their child at
-home. Forty nine\% of participants (n = 41) had been exposed to two or
-more languages as indicated by their parent. Parents identified their
-children as White (n = 39), Asian (n = 20), African American/Black (n =
-1), Biracial (n = 9), other (n = 7), or declined to state (n = 8).
-Sixteen parents reported their child was of Hispanic origin. Parents
-tended to be highly- educated, with reports of highest level of
-education ranging from completed high school (n = 0), some college (n =
-5), four-year college (n = 28), some graduate school (n = 2), to
-completed graduate school (n = 35) or declined to state (n = 14).
-
-\subsubsection{Materials.}\label{materials.-1}
-
-The design of Experiment 2 was similar to that of Experiment 1, except
-that instead of a No-Video control condition, parents instead watched a
-video that was generally related to child development research, but did
-not give any specific instructions about how to interact with infants or
-children. This was to control for the possibility that differences in
-language output and joint attention in Experiment 1 could be due to
-simply cuing parents to think about infants' learning and cognitive
-development. The videos presented in the Control Video condition were
-media clips (available on YouTube) of developmental psychologists
-explaining their research interleaved with footage of infants or
-toddlers engaged in developmental research studies. Thus, the content of
-the videos superficially matched those in the Activity Video condition,
-but did not suggest any particular activities. The videos were trimmed
-to approximately match the average video length in the Activity Video
-condition around 1.5 minutes.
-
-\subsubsection{Procedure.}\label{procedure.-1}
-
-The procedure for Experiment 2 matched that of Experiment 1, except that
-parents in the Control Video condition watched a control video before
-the play session. Consistent with the No-Video control condition in
-Experiment 1, parents in the Control Video condition were told to play
-with their child as they would at home, and were not given additional
-instructions. The coding procedure also matched that of Experiment 1. A
-second coder independently coded a third of the videos (i.e., 26 of the
-84 videos, approximately equally distributed across ages) to establish
-reliability. The two coders had a reliability of ICC = 0.80 with 95\%
-confident interval (CI) = {[}0.60,0.90{]} (p \textless{} 0.05) for
-number of parent bids for JA; ICC = 0.74 with 95\% CI = {[}0.59,0.87{]}
-(p \textless{} 0.05) for number of passive JA episodes; ICC = 0.78 with
-95\% CI = {[}0.58,0.90{]} (p \textless{} 0.05) for number of coordinated
-JA episodes; ICC = 0.72 with 95\% CI = {[}0.46,0.86{]} (p \textless{}
-0.05) for total duration of passive JA episodes, and ICC = 0.88 with
-95\% CI = {[}0.75,0.94{]} (p \textless{} 0.05) for total duration of
-coordinated JA episodes.
-
-\section{Results}\label{results-1}
-
-Parents' child-directed speech was transcribed and processed in the same
-way as in Experiment 1.
-
-\subsection{Lexical Diversity}\label{lexical-diversity-1}
-
-We fit a mixed-effects linear regression predicting TTR and MTLD as a
-function of age (scaled and 0-centered) and condition with a random
-intercept per video using lme4 (Bates et al., 2015). There was
-significantly lower TTR in the Video condition (mean: 0.38) than in the
-Control condition (mean: 0.47, \(\beta=-.09\), t(8.7) = 3.06,
-\emph{p}=.01). There was no significant effect of age. A similar
-mixed-effects linear regression instead predicting MTLD found no
-significant effects of age or condition. Figure 1 shows the mean of each
-lexical diversity measure (TTR and MTLD) by condition.
-
-We also conducted similar regressions predicting the number of word
-tokens and types, finding no significant effects of of age or condition.
-
-(Table with mean and SD of tokens, types, and TTR)
-
-\begin{CodeChunk}
-\begin{figure}[H]
-
-{\centering \includegraphics{figs/e2lexdiv-1}
-
-}
-
-\caption[Mean lexical diversity scores by condition (left]{Mean lexical diversity scores by condition (left: Type/Token ratio, right: MTLD) in Experiment 2.}\label{fig:e2lexdiv}
-\end{figure}
-\end{CodeChunk}
-
-\begin{CodeChunk}
-\begin{figure}[H]
-
-{\centering \includegraphics{figs/e2token-type-1}
-
-}
-
-\caption[Mean number of word types and word tokens by condition in Experiment 2]{Mean number of word types and word tokens by condition in Experiment 2.}\label{fig:e2token-type}
-\end{figure}
-\end{CodeChunk}
-
-\subsection{Joint Attention}\label{joint-attention-1}
-
-\begin{CodeChunk}
-\begin{figure}[H]
-
-{\centering \includegraphics{figs/e2ja-graphs-1}
-
-}
-
-\caption[Mean number of bids and episodes of Joint Attention in Experiment 2]{Mean number of bids and episodes of Joint Attention in Experiment 2.}\label{fig:e2ja-graphs}
-\end{figure}
-\end{CodeChunk}
-
-\begin{CodeChunk}
-\begin{figure}[H]
-
-{\centering \includegraphics{figs/e2ja-graphs-pass-coord-1}
-
-}
-
-\caption[Average number of passive and coordinated episodes of JA in Experiment 2]{Average number of passive and coordinated episodes of JA in Experiment 2.}\label{fig:e2ja-graphs-pass-coord}
-\end{figure}
-\end{CodeChunk}
-
-\section{Discussion}\label{discussion-1}
-
-Similar to results in Experiment 1, the number of tokens was higher in
-the experimental condition, while the number of types and lexical
-diversity (Type/Token ratio) were higher in the control condition.
-Parents may be relatively more repetetive in the experimental condition
-since they are attempting to stick to a specific prescribed task, but
-they talk more overall. There was a marginal effect of condition on
-total bids for joint attention. Parents in the experimental condition
-(i.e., those who saw a video demonstrating an activity) made a greater
-number of bids for joint attention with their child. There was no effect
-of condition on the number of episodes of coordinated joint attention.
-There was no effect of condition on the number of episodes of either
-passive or coordinated joint attention, or the duration of these
-episodes. However, there was a main effect of age on number of episodes
-of passive joint attention, duration of passive and coordinated joint
-attention, with the older children having fewer episodes of passive
-joint attention, shorter duration of passive joint attention, and longer
-duration of coordinated joint attention. These results suggest that
-children become more socially engaging in interactions with their
-caregivers as they develop.
-
-\subsection{Two-column images}\label{two-column-images}
-
-You might want to display a wide figure across both columns. To do this,
-you change the \texttt{fig.env} chunk option to \texttt{figure*}. To
-align the image in the center of the page, set \texttt{fig.align} option
-to \texttt{center}. To format the width of your caption text, you set
-the \texttt{num.cols.cap} option to \texttt{2}.
-
-\section{References}\label{references}
-
-\setlength{\parindent}{-0.1in} \setlength{\leftskip}{0.125in} \noindent
-
-\hypertarget{refs}{}
-\hypertarget{ref-lme4}{}
-Bates, D., Mächler, M., Bolker, B., \& Walker, S. (2015). Fitting linear
-mixed-effects models using lme4. \emph{Journal of Statistical Software},
-\emph{67}(1), 1--48. \url{http://doi.org/10.18637/jss.v067.i01}
-
-\hypertarget{ref-Bigelow2004}{}
-Bigelow, A. E., MacLean, K., \& Proctor, J. (2004). The role of joint
-attention in the development of infants' play with objects.
-\emph{Developmental Science}, \emph{7}, 518--526.
-
-\hypertarget{ref-Breitenstein2014}{}
-Breitenstein, S. M., Gross, D., \& Christophersen, R. (2014). Digital
-delivery methods of parenting training interventions: A systematic
-review. \emph{Worldviews on Evidence-Based Nursing}, \emph{11},
-168--176.
-
-\hypertarget{ref-Hart1995}{}
-Hart, B., \& Risley, T. R. (1995). \emph{Meaningful differences in the
-everyday experience of young american children}. Baltimore, MD: Brookes.
-
-\hypertarget{ref-Heckman2006}{}
-Heckman, J. J. (2006). Skill formation and the economics of investing in
-disadvantaged children. \emph{Science}, \emph{312}(5782), 1900--1902.
-\url{http://doi.org/10.1126/science.1128898}
-
-\hypertarget{ref-Hirsh2008}{}
-Hirsh-Pasek, K., \& Golinkoff, R. M. (2008). Why play= learning.
-\emph{Encyclopedia on Early Childhood Development}, 1--7.
-
-\hypertarget{ref-spacy2}{}
-Honnibal, I., Matthew AND Montani. (2017). SpaCy 2: Natural language
-understanding with bloom embeddings, convolutional neural networks and
-incremental parsing. \emph{To Appear}.
-
-\hypertarget{ref-Kaye1970}{}
-Kaye, K. (1970). Mother-child instructional interaction.
-\emph{Unpublished Doctoral Thesis, Department of Psychology, Harvard
-University}.
-
-\hypertarget{ref-Malvern2004}{}
-Malvern, D., Richards, B. J., Chipere, N., \& Durán, P. (2004). Lexical
-diversity and language development.
-
-\hypertarget{ref-Massey2013}{}
-Massey, S. L. (2013). From the reading rug to the play center: Enhancing
-vocabulary and comprehensive language skills by connecting storybook
-reading and guided play. \emph{Early Childhood Education Journal},
-\emph{41}, 125--131.
-
-\hypertarget{ref-McCarthy2010}{}
-McCarthy, P. M., \& Jarvis, S. (2010). MTLD, vocd-d, and hd-d: A
-validation study of sophisticated approaches to lexical diversity
-assessment. \emph{Behavior Research Methods}, \emph{42}(2), 381--392.
-
-\hypertarget{ref-Schulz2007}{}
-Schulz, L., \& Bonawitz, E. (2007). Serious fun: Preschoolers engage in
-more exploratory play when evidence is confounded. \emph{Developmental
-Psychology}, \emph{43}(4), 1045--1050.
-
-\hypertarget{ref-Singer2006}{}
-Singer, D. G., Golinkoff, R. M., \& Hirsh-Pasek, K. (Eds.). (2006).
-\emph{Play = learning: How play motivates and enhances children's
-cognitive and social-emotional growth}. New York, NY: Oxford University
-Press.
-
-\hypertarget{ref-Suskind2015}{}
-Suskind, D. L., Leffel, K. R., Graf, E., Hernandez, M. W., Gunderson, E.
-A., Sapolich, S. G., \ldots{} Levine, S. C. (2015). A parent-directed
-language intervention for children of low socioeconomic status: A
-randomized controlled pilot study. \emph{Journal of Child Language}.
-\url{http://doi.org/10.1017/S0305000915000033}
-
-\hypertarget{ref-datavyu}{}
-Team, D. (2014). Datavyu: A video coding tool. \emph{Databrary Project}.
-Retrieved from \url{http://datavyu.org}
-
-\hypertarget{ref-Vygotsky1980}{}
-Vygotsky, L. S. (1980). Mind in society: The development of higher
-psychological processes.
-
-\hypertarget{ref-Weisberg2013}{}
-Weisberg, D. S., Hirsh-Pasek, K., \& Golinkoff, R. M. (2013). Guided
-play: Where curricular goals meet a playful pedagogy. \emph{Mind, Brain,
-and Education}, \emph{7}, 104--112.
-
-\hypertarget{ref-Wood1976}{}
-Wood, D., Bruner, J. S., \& Ross, G. (1976). The role of tutoring in
-problem solving. \emph{Journal of Child Psychology and Psychiatry},
-\emph{17}, 89--100.
-
-\bibliographystyle{apacite}
-
-\end{document}
+Props: blue car, yellow car, yellow block, red block, blue block, green
+block
+\end{appendix}

### 2019-08-30 paper/manuscript.Rmd
cleaning up repo, full switch to papaja

--- 2019-08-12 paper/cogsci2019/manuscript.Rmd
@@
     affiliation   : "1"
-    corresponding : yes    # Define only one corresponding author
     address       : "Stanford, CA 94305 USA"
@@
   - id            : "3"
-    insitution    : "Gallaudet University"
+    institution    : "Gallaudet University"
   - id            : "4"
-    insitution    : "Cornell University"
+    institution    : "Cornell University"
 
 authornote: |
-  blah
-  blahblah
+
 abstract: |
@@
 output            : papaja::apa6_pdf
+appendix: "appendix.Rmd"
 ---
@@
 ```{r, include=F}
-e1path = "../../parenting_obs_e1/"
+e1path = "../parenting_obs_e1/"
 load(paste(e1path,"Exp1_cleaned_data.RData",sep='')) # merged dataframe ready for plotting
@@
 A similar mixed-effects linear regression instead predicting MTLD also found significantly lower lexical diversity in the Video condition (mean MTLD: `r round(subset(e1_lexdiv, condition=='exp')$MTLD, 2)`) than in the Control condition (mean: `r round(subset(e1_lexdiv, condition=='exp')$TTR, 2)`, $\beta=$`r e1MTLD["conditionexp","beta"]`, t(55) = `r e1MTLD["conditionexp","tval"]`, *p*=.001), with no other significant effects.
-Figure \ref{fig:e1lex_div} shows the mean of each lexical diversity measure (TTR and MTLD) by condition.
+Figure \ref{fig:e1lexdiv} shows the mean of each lexical diversity measure (TTR and MTLD) by condition.
 
@@
 
-```{r fig:e1lex_div, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=7, fig.height=3.0, fig.cap = "Mean lexical diversity scores by condition (left: Type/Token ratio, right: MTLD) in Experiment 1.
+```{r fig:e1lexdiv, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=7, fig.height=3.0, fig.cap = "Mean lexical diversity scores by condition (left: Type/Token ratio, right: MTLD) in Experiment 1.
 Both measures of lexical diversity were significantly lower after watching an activity video.
@@
 ```{r, echo=F}
-e2path = "../../parenting_obs_e2/"
+e2path = "../parenting_obs_e2/"
 load(paste(e2path,"Exp2_cleaned_data.RData",sep=''))

### 2019-08-30 paper/manuscript.tex
cleaning up repo, full switch to papaja

--- 2019-08-12 paper/cogsci2019/manuscript.tex
@@
 \vspace{0.5cm}
-\textsuperscript{1} Department of Psychology, Stanford University\\\textsuperscript{2} Nextdoor, Inc.\\\textsuperscript{3} \\\textsuperscript{4} }
+\textsuperscript{1} Department of Psychology, Stanford University\\\textsuperscript{2} Nextdoor, Inc.\\\textsuperscript{3} Gallaudet University\\\textsuperscript{4} Cornell University}
 \keywords{digital parenting advice; joint attention; lexical diversity; guided play\newline\indent Word count: 4510}
@@
 
-\authornote{blah
-blahblah
+\authornote{
 
-Correspondence concerning this article should be addressed to George Kachergis, Stanford, CA 94305 USA. E-mail: \href{mailto:kachergis@stanford.edu}{\nolinkurl{kachergis@stanford.edu}}}
+Correspondence concerning this article should be addressed to Michael C. Frank, Stanford, CA 94305 USA. E-mail: \href{mailto:mcfrank@stanford.edu}{\nolinkurl{mcfrank@stanford.edu}}}
 
@@
 A similar mixed-effects linear regression instead predicting MTLD also found significantly lower lexical diversity in the Video condition (mean MTLD: 17.87) than in the Control condition (mean: 0.32, \(\beta=\)-8.73, t(55) = 2.67, \emph{p}=.001), with no other significant effects.
-Figure \ref{fig:e1lex_div} shows the mean of each lexical diversity measure (TTR and MTLD) by condition.
+Figure \ref{fig:e1lexdiv} shows the mean of each lexical diversity measure (TTR and MTLD) by condition.
 
@@
 
-\textbackslash{}begin\{figure\}{[}H{]}
+\begin{figure}[H]
 
-\{\centering \includegraphics{figs/fig:e1lex_div-1}
+{\centering \includegraphics{figs/fig:e1lexdiv-1}
 
-\}
+}
 
@@
 Both measures of lexical diversity were significantly lower after watching an activity video.
-Error bars show bootstrapped 95\% confidence intervals (CIs), and gray dots indicate values for each participant.}
-
-(\#fig:fig:e1lex\_div)
-\textbackslash{}end\{figure\}
+Error bars show bootstrapped 95\% confidence intervals (CIs), and gray dots indicate values for each participant.}(\#fig:fig:e1lexdiv)
+\end{figure}
 
@@
 
-60 infants (F = 36, M = 46) aged 12-24 months (41 12-17.9 month-olds, 43 18-24 month-olds) and their parents participated in the same museum as Experiment 1.
+84 infants (F = 36, M = 46) aged 12-24 months (41 12-17.9 month-olds, 43 18-24 month-olds) and their parents participated in the same museum as Experiment 1.
 We included infants who were exposed to English at least 75 percent of the time or who were exposed less but whose participating parent reported that they primarily speak English with their child at home.
@@
 
+\clearpage
+\makeatletter
+\efloat@restorefloats
+\makeatother
+
+\begin{appendix}
+\section{}
+\hypertarget{experiment-1}{%
+\subsection{Experiment 1}\label{experiment-1}}
+
+\hypertarget{video-a-6-11.9-months-pick-it-up}{%
+\subsubsection{Video A (6-11.9 months) ``Pick it
+up''}\label{video-a-6-11.9-months-pick-it-up}}
+
+Parents are told to encourage their child to pick up and drop individual
+objects. They are also encouraged to place toys on a small cloth and
+show the child that they can drag the cloth towards them to reach the
+toys.
+
+Props: cloth, plastic horse, plastic sheep, plastic elephant, toy car
+
+\hypertarget{video-b-6-11.9-months-animal-sounds}{%
+\subsubsection{Video B (6-11.9 months) ``Animal
+sounds''}\label{video-b-6-11.9-months-animal-sounds}}
+
+Parents are told to call different animals and imitate different sounds
+the animals make. They are also encourgaed to observe which animal the
+child prefers.
+
+Props: plastic sheep, plastic horse, plastic frog, plastic cow, bowls
+
+\hypertarget{video-c-12-17.9-months-give-me-the-toy}{%
+\subsubsection{Video C (12-17.9 months) ``Give me the
+toy''}\label{video-c-12-17.9-months-give-me-the-toy}}
+
+Parents are told to ask their child to hand over individual toys. They
+are also encouraged to praise the child after they give them the toys,
+and repeat the process until the child could follow the verbal
+instructions.
+
+Props: toy boat, plastic frog, plastic elephant, toy bus
+
+\hypertarget{video-d-12-17.9-months-classifying-my-toys}{%
+\subsubsection{Video D (12-17.9 months) ``Classifying my
+toys''}\label{video-d-12-17.9-months-classifying-my-toys}}
+
+Parents are told to place toys of different sizes (big or small) in two
+hoops. They are also encouraged to ask their child to distinguish
+between two objects and identify which one is larger.
+
+Props: two yellow and green rings, big car, small car, big horse, small
+horse
+
+\hypertarget{video-e-18-23.9-months-my-toys}{%
+\subsubsection{Video E (18-23.9 months) ``My
+toys''}\label{video-e-18-23.9-months-my-toys}}
+
+Parents are told to show the child toys of the same shape but different
+sizes, to place one of the objects in a basket and to ask the child to
+take out the object. They are also encouraged to ask their child if the
+object is bigger or smaller compared to its pair.
+
+Props: two buckets, big car, small car, big horse, small horse
+
+\hypertarget{video-f-18-23.9-months-the-orchestra}{%
+\subsubsection{Video F (18-23.9 months) ``The
+Orchestra''}\label{video-f-18-23.9-months-the-orchestra}}
+
+Parents are told to give their child a musical instrument to play. They
+are also encouraged to play a song and see if the child follows the
+rhythm.
+
+Props: maracas, drum, tambourine, clapper
+
+\hypertarget{experiment-2}{%
+\subsection{Experiment 2}\label{experiment-2}}
+
+\hypertarget{video-a-12-17.9-months-give-me-the-toy}{%
+\subsubsection{Video A (12-17.9 months) ``Give me the
+toy''}\label{video-a-12-17.9-months-give-me-the-toy}}
+
+Parents are told to ask their child to hand over individual toys. They
+are also encouraged to praise the child after they give them the toys,
+and repeat the process until the child could follow the verbal
+instructions.
+
+Props: plastic pig, plastic horse, plastic dog, plastic cat, plastic cow
+
+\hypertarget{video-b-12-17.9-months-classifying-my-toys}{%
+\subsubsection{Video B (12-17.9 months) ``Classifying my
+toys''}\label{video-b-12-17.9-months-classifying-my-toys}}
+
+Parents are told to place toys of different sizes (big or small) in two
+hoops. They are also encouraged to ask their child to distinguish
+between two objects and identify which one is larger.
+
+Props: two yellow and green rings, big car, small car, big horse, small
+horse
+
+\hypertarget{video-c-12-17.9-months-geometric-shapes-jigzsaw-puzzle}{%
+\subsubsection{Video C (12-17.9 months) ``Geometric shapes jigzsaw
+puzzle''}\label{video-c-12-17.9-months-geometric-shapes-jigzsaw-puzzle}}
+
+Parents are told to encourage their child to name different shapes on a
+jigzsaw puzzle. Then they are told to undo the puzzle and invite the
+child to complete the puzzle.
+
+Props: A jigzsaw puzzle of geometric shapes
+
+\hypertarget{video-d-18-23.9-months-my-toys}{%
+\subsubsection{Video D (18-23.9 months) ``My
+toys''}\label{video-d-18-23.9-months-my-toys}}
+
+Parents are told to show the child toys of the same shape but different
+sizes, to place one of the objects in a basket and to ask the child to
+take out the object. They are also encouraged to ask their child if the
+object is bigger or smaller compared to its pair.
+
+Props: two buckets, big car, small car, big horse, small horse
+
+\hypertarget{video-e-18-23.9-months-the-orchestra}{%
+\subsubsection{Video E (18-23.9 months) ``The
+Orchestra''}\label{video-e-18-23.9-months-the-orchestra}}
+
+Parents are told to give their child a musical instrument to play. They
+are also encouraged to play a song and see if the child follows the
+rhythm.
+
+Props: maracas, drum, tambourine, clapper
+
+\hypertarget{video-f-18-23.9-months-my-yellow-toys}{%
+\subsubsection{Video F (18-23.9 months) ``My Yellow
+Toys''}\label{video-f-18-23.9-months-my-yellow-toys}}
+
+Parents are told to show their child yellow toys and to ask, ``What
+color are they?'' They are also told to give the child toys of different
+colors, to ask them to only play with the yellow ones, and to praise the
+child after they do so.
+
+Props: blue car, yellow car, yellow block, red block, blue block, green
+block
+\end{appendix}
+
 \end{document}

### 2019-09-11 paper/manuscript.Rmd
switching to Bayesian regressions

@@
 
-```{r, include=F}
+```{r load-exp1-lexical-data, include=F}
 e1path = "../parenting_obs_e1/"
@@
 
-lmer_data <- d %>%
+e1ld <- d %>%
   #filter(!is.na(AA), !is.na(EL), !is.na(RR))%>%
@@
 
-e1_gender = table(d$gender)
+e1_gender = table(e1ld$gender)
 #table(cut_interval(d$age, n=2, breaks=c(.5,1.5,2.1), labels=F))
 #table(cut_number(d$age, n=3, breaks=c(.5,1.5,2.1)))
-e1_parent_ed = table(d$parent_ed)
+e1_parent_ed = table(e1ld$parent_ed)
 ```
@@
 A joint attention episode was considered _coordinated_ if both participants visually focused on an object for 3 or more seconds and at some point in the interaction the child indicated awareness of interaction with some overt behavior toward the parent such as looking at their face, gesturing, vocalizing, or turn-taking.
-Full details of our guidelines for coding joint attention are available in [SI](https://docs.google.com/document/d/1cZrT_Gjt6p0om19lXO-XcFnT09pb0giyhRQ-Pm1yoBU/edit?usp=sharing).
+Full details of our guidelines for coding joint attention are available in SI.
 
@@
 ```{r, e1-lexdiv-regressions, echo=F, include=F}
-get_lmer_reporting_values <- function(lmer.fit, digits=2) {
-  sm <- summary(lmer.fit)
-  Vcov <- vcov(lmer.fit, useScale = FALSE)
-  beta <- round(fixef(lmer.fit), digits)
-  se <- round(sqrt(diag(Vcov)), digits)
-  zval <- round(beta / se, digits)
-  pvalEst <- round(2 * pnorm(abs(zval), lower.tail = FALSE), 3)
-  pval <- round(sm$coefficients[,"Pr(>|t|)"], 3)
-  tval <- abs(round(sm$coefficients[,"t value"], digits))
-  df <- round(sm$coefficients[,"df"], 1)
-  return(cbind(beta, se, zval, tval, pval, pvalEst, df))
+require("rstanarm")
+# get estimated coefficient and 95% CI from Bayesian regression
+get_stan_glmer_reporting_values <- function(model, cond, digits=2) {
+  ci95 <- posterior_interval(model, prob = 0.95, pars = cond)
+  ci = round(ci95, digits)
+  names(ci) = c("95pLB","95pUB") # 95% lower and upper bounds
+  beta = round(model$coefficients[cond], digits)
+  return(c(beta,ci))
 }
 
-require("lmerTest")
+# Predicting lexical diversity based on experimental condition, PAQ, demographics. 
+modTTR <- stan_glmer(TTR ~ condition + age + gender + parent_ed + (1|video), data=e1ld)
+summary(modTTR) # condition:Exp -0.113 t(52.4) = 4.22 p<.001
+e1TTR = get_stan_glmer_reporting_values(modTTR, "conditionexp") #
 
-# Predicting lexical diversity based on experimental condition, PAQ, demographics. 
-modTTR <- lmer(TTR ~ condition + age + gender + parent_ed + (1|video), data=lmer_data)
-summary(modTTR) # condition:Exp -0.113 t(52.4) = 4.22 p<.001
-e1TTR = get_lmer_reporting_values(modTTR)
-
-modMTLD <- lmer(MTLD ~ condition + age + gender + parent_ed + (1|video), data=lmer_data)
- # , control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5)))
-summary(modMTLD) # condition -8.73 t(55) = 2.67 p=.001 !! singular fit
-e1MTLD = get_lmer_reporting_values(modMTLD)
-
-tt <- getME(modMTLD,"theta")
-ll <- getME(modMTLD,"lower")
-min(tt[ll==0]) # 0
-
-# Bayesian regression (stan_glmer in rstanarm) shows the same:
-require("rstanarm")
-bmodMTLD <- stan_glmer(MTLD ~ condition + age + gender + parent_ed + (1|video), data=lmer_data)
-summary(bmodMTLD) # condition mean=-8.6 sd=3.2 95% CI = [-14.9,-2.3]
+modMTLD <- stan_glmer(MTLD ~ condition + age + gender + parent_ed + (1|video), data=e1ld)
+summary(modMTLD) # condition -8.73 t(55) = 2.67 p=.001 !! singular fit, changing optimizer did not help
+e1MTLD = get_stan_glmer_reporting_values(modMTLD, "conditionexp") #
 
 # predict word tokens
-tokens_mod <- lmer(tokens ~ condition*EL + condition*AA + condition*RR + age + gender + parent_ed + (1|video),  data=lmer_data) # only 54 parents completed the EPAQ
-summary(tokens_mod) # condition 56.02 t(40.4) = 2.30 p<.05
-e1tokens = get_lmer_reporting_values(tokens_mod)
+tokens_mod <- stan_glmer(tokens ~ condition + age + gender + parent_ed + (1|video),  data=e1ld) 
+summary(tokens_mod)
+get_stan_glmer_reporting_values(tokens_mod, "conditionexp") # 55.7
+
+# follow-up on EPAQ
+tokens_modEPAQ <- stan_glmer(tokens ~ condition*EL + condition*AA + condition*RR + age + gender + parent_ed + (1|video),  data=e1ld) # only 54 parents completed the EPAQ
+summary(tokens_modEPAQ) # condition 56.02 t(40.4) = 2.30 p<.05
+e1tokens = get_stan_glmer_reporting_values(tokens_mod, "conditionexp") # 54.8
 
 # predict word types
-types_mod <- lmer(types ~ condition*EL + condition*AA + condition*RR  + age + gender + parent_ed + (1|video), data=lmer_data,
-                  control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))) # !! singular fit
-summary(types_mod) # nothing (hint: conditionexp:AA beta=19.04 p=.11)
-e1types = get_lmer_reporting_values(types_mod) 
-# verify with Bayesian regression:
-bmod_types <- stan_glmer(types ~ condition*EL + condition*AA + condition*RR  + age + gender + parent_ed + (1|video), data=lmer_data)
-summary(bmod_types) # nothing
+types_mod <- stan_glmer(types ~ condition*EL + condition*AA + condition*RR  + age + gender + parent_ed + (1|video), data=e1ld) 
+summary(types_mod) # nothing
 
@@
 
-We fit a mixed-effects linear regression predicting TTR as a function of condition, age (centered), gender, and parent's education level with a random intercept per video using lme4 [@lme4]. 
-There was significantly lower TTR in the Video condition (mean: `r round(subset(e1_lexdiv, condition=='exp')$TTR, 2)`) than in the Control condition (mean: `r round(subset(e1_lexdiv, condition=='con')$TTR, 2)`, $\beta=$`r e1TTR["conditionexp","beta"]`, t(52.4) = `r e1TTR["conditionexp","tval"]`, *p*<.001).
+We fit a Bayesian mixed-effects linear regression predicting TTR as a function of condition, age (centered), gender, and parent's education level with a random intercept per video using rstanarm [@rstanarm].
+For effects that are at least 95% likely to be non-zero according to the posterior distribution, we report estimated coefficients ($\beta$) as well as 95% Bayesian credible intervals (95% CI), demarcating the range within which 95% of the posterior predictive values fall.
+There was significantly lower TTR in the Video condition (mean: `r round(subset(e1_lexdiv, condition=='exp')$TTR, 2)`) than in the Control condition (mean: `r round(subset(e1_lexdiv, condition=='con')$TTR, 2)`, $\beta=$`r e1TTR["conditionexp"]`, 95% CI=[`r e1TTR['95pLB']`,`r e1TTR['95pUB']`]).
 There were no significant effects of age, gender, or parent's level of education.
-A similar mixed-effects linear regression instead predicting MTLD also found significantly lower lexical diversity in the Video condition (mean MTLD: `r round(subset(e1_lexdiv, condition=='exp')$MTLD, 2)`) than in the Control condition (mean: `r round(subset(e1_lexdiv, condition=='exp')$TTR, 2)`, $\beta=$`r e1MTLD["conditionexp","beta"]`, t(55) = `r e1MTLD["conditionexp","tval"]`, *p*=.001), with no other significant effects.
+A similar Bayesian mixed-effects linear regression instead predicting MTLD also found significantly lower lexical diversity in the Video condition (mean MTLD: `r round(subset(e1_lexdiv, condition=='exp')$MTLD, 2)`) than in the Control condition (mean: `r round(subset(e1_lexdiv, condition=='con')$MTLD, 2)`, $\beta=$`r e1MTLD["conditionexp"]`, 95% CI=[`r e1MTLD['95pLB']`,`r e1MTLD['95pUB']`]), with no other significant effects.
 Figure \ref{fig:e1lexdiv} shows the mean of each lexical diversity measure (TTR and MTLD) by condition.
@@
 ```{r e1tokens, echo=F, include=F}
-d$Condition = factor(d$condition, levels = c("con", "exp"), labels = c("No Video", "Activity Video"))
+e1ld$Condition = factor(e1ld$condition, levels = c("con", "exp"), labels = c("No Video", "Activity Video"))
 
-ms_lex_mtld <- d %>% group_by(Condition) %>%
+ms_lex_mtld <- e1ld %>% group_by(Condition) %>%
   tidyboot_mean(MTLD) 
-ms_lex <- d %>% group_by(Condition) %>%
+ms_lex <- e1ld %>% group_by(Condition) %>%
   tidyboot_mean(TTR) # Type/Token Ratio
-ms_tok <- d %>% group_by(Condition) %>%
+ms_tok <- e1ld %>% group_by(Condition) %>%
   tidyboot_mean(tokens) 
-ms_type <- d %>% group_by(Condition) %>%
+ms_type <- e1ld %>% group_by(Condition) %>%
   tidyboot_mean(types)
@@
 
-We also conducted similar regressions predicting the number of word tokens and types, finding only a significant effect of condition on the number of word tokens ($\beta= `r e1tokens["conditionexp","beta"]`$, t(40.4)=`r e1tokens["conditionexp","tval"]`, *p*<.05), with parents using more words in the Video condition (mean: `r round(subset(e1_lexdiv, condition=='exp')$tokens, 0)`, bootstrapped 95% confidence intervals (CI): [`r round(subset(ms_tok, Condition=="Activity Video")$ci_lower, 0)`,`r round(subset(ms_tok, Condition=="Activity Video")$ci_upper, 0)`]) than in the Control condition (mean: `r round(subset(e1_lexdiv, condition=='con')$tokens, 0)`, bootstrapped 95% CI: [`r round(subset(ms_tok, Condition=="No Video")$ci_lower, 0)`,`r round(subset(ms_tok, Condition=="No Video")$ci_upper, 0)`]).
-The means of the lexical diversity measures are reported in Table \ref{tab:e1tab}.
+We also conducted similar regressions predicting the number of word tokens and types, finding only a significant effect of condition on the number of word tokens ($\beta=$ `r e1tokens["conditionexp"]`, 95% CI=[`r e1tokens['95pLB']`,`r e1tokens['95pUB']`])), with parents using more words in the Video condition (mean: `r round(subset(e1_lexdiv, condition=='exp')$tokens, 0)`, bootstrapped 95% confidence intervals (CI): [`r round(subset(ms_tok, Condition=="Activity Video")$ci_lower, 0)`,`r round(subset(ms_tok, Condition=="Activity Video")$ci_upper, 0)`]) than in the Control condition (mean: `r round(subset(e1_lexdiv, condition=='con')$tokens, 0)`, bootstrapped 95% CI: [`r round(subset(ms_tok, Condition=="No Video")$ci_lower, 0)`,`r round(subset(ms_tok, Condition=="No Video")$ci_upper, 0)`]).
 
-```{r e1tab, echo=FALSE}
-e1 <- d %>% group_by(Condition) %>%
+```{r e1tab, echo=FALSE, include=F}
+e1 <- e1ld %>% group_by(Condition) %>%
   summarise("Mean TTR"=mean(TTR), TTRsd=sd(TTR),
@@
 
-lmer_data <- d %>%
+e1ja <- d %>%
   filter(!is.na(AA), !is.na(EL), !is.na(RR)) %>%
@@
 
+# Mike says this should be the follow-up regression (if we find a sig effect?)
 model_string =  "~ Condition * EL + Condition * AA + Condition * RR  + age + gender + parent_ed + (1| Video)"
@@
 # Total number of bids
-bids_mod <- lmer(paste("bids_tot", model_string), data = lmer_data)
-summary(bids_mod) # condition beta = 3.51, t(40.3) = 2.95 p<.01, gender p=.05 ?
-e1bids = get_lmer_reporting_values(bids_mod)
+e1bids_mod <- stan_glmer(paste("bids_tot", model_string), data = e1ja) # 1 divergent transitions after warmup. Increasing adapt_delta above 0.95 may help
+summary(e1bids_mod) # condition beta = 3.51, t(40.3) = 2.95 p<.01, gender p=.05 ?
+e1bids = get_stan_glmer_reporting_values(e1bids_mod, "ConditionActivity Video")
 
-e1bids_M <- lmer_data %>% group_by(Condition) %>% 
+e1bids_M <- e1ja %>% group_by(Condition) %>% 
   summarise(mean = mean(bids), sd = sd(bids))
@@
 # Episodes of coordinated joint attention.
-cja_mod <- lmer(paste("cja", model_string), data = lmer_data)
-summary(cja_mod) # NA
+e1cja_mod <- stan_lmer(paste("cja", model_string), data = e1ja)
+summary(e1cja_mod) # NA
 
 # Episodes of passive joint attention.
-pja_mod <- lmer(paste("pja", model_string), data = lmer_data)
-summary(pja_mod) # marginal RR, beta=-1.07 p=.07, condition*RR beta=1.83 p<.05 t(41.5)=2.22
-e1pja = get_lmer_reporting_values(pja_mod)
+e1pja_mod <- stan_lmer(paste("pja", model_string), data = e1ja)
+summary(e1pja_mod) # condition*RR beta=1.8 Bayes 95% Ci = [.1,3.5]
+e1pja = get_stan_glmer_reporting_values(e1pja_mod, "ConditionActivity Video:RR")
 
 # Total duration of passive joint attention.
-pja_time_mod <- lmer(paste("pja_length", model_string), data = lmer_data)
-summary(pja_time_mod) # NA
+e1pja_time_mod <- stan_lmer(paste("pja_length", model_string), data = e1ja)
+summary(e1pja_time_mod) # NA
 
 # Total duration of coordinated joint attention.
-cja_time_mod <- lmer(paste("cja_length", model_string), data = lmer_data,
-                     control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5)))
-summary(cja_time_mod) # marginal parent education p=.09 - SINGULAR (do stan_glmer)
+e1cja_time_mod <- stan_lmer(paste("cja_length", model_string), data = e1ja)
+summary(e1cja_time_mod) # NA
 ```
@@
 This lme4 model included random intercepts per video. 
-There were significantly more bids for JA in the Video condition (mean: `r round(subset(e1bids_M, Condition=="Activity Video")$mean,2)`, sd: `r round(subset(e1bids_M, Condition=="Activity Video")$sd,2)`) than in the Control condition (mean: `r round(subset(e1bids_M, Condition=="No Video")$mean,2)`, sd: `r round(subset(e1bids_M, Condition=="No Video")$sd,2)`, $\beta=`r e1bids["ConditionActivity Video","beta"]`$, t(`r e1bids["ConditionActivity Video","df"]`) = `r e1bids["ConditionActivity Video","tval"]`, *p*<.01).
-There were no other significant effects.
+There were significantly more bids for JA in the Video condition (mean: `r round(subset(e1bids_M, Condition=="Activity Video")$mean,2)`, sd: `r round(subset(e1bids_M, Condition=="Activity Video")$sd,2)`) than in the Control condition (mean: `r round(subset(e1bids_M, Condition=="No Video")$mean,2)`, sd: `r round(subset(e1bids_M, Condition=="No Video")$sd,2)`, $\beta=`r e1bids["ConditionActivity Video"]`$, 95% CI=[`r e1bids['95pLB']`,`r e1bids['95pUB']`]).
 
@@
 There were no significant effects on the number or total duration of coordinated JA episodes, nor on the total duration of passive JA episodes. 
-For the regression predicting the number of passive JA episodes, the only significant effect was an interaction of condition and RR ($\beta=`r e1pja["ConditionActivity Video:RR","beta"]`$, t(`r e1pja["ConditionActivity Video:RR","df"]`) = `r e1pja["ConditionActivity Video:RR","tval"]`, *p*<.05), showing that for parents in the Video condition, those with higher Rules and Respect subscores engaged in more passive JA episodes.
+For the regression predicting the number of passive JA episodes, the only significant effect was an interaction of condition and RR ($\beta=`r e1pja["ConditionActivity Video:RR"]`$, 95% CI=[`r e1pja['95pLB']`,`r e1pja['95pUB']`]), showing that for parents in the Video condition, those with higher Rules and Respect subscores engaged in more passive JA episodes.
 Figure \@ref(fig:e1ja) shows the mean number bids for JA and episodes of JA by condition in Experiment 1.
@@
 
-lmer_data <- d %>%
+e2data <- d %>%
   mutate(condition = factor(condition), 
@@
 ### Participants. 
-`r nrow(d)` infants (F = `r e2_gender['F']`, M = `r e2_gender['M']`) aged 12-24 months (`r e2_12to18` 12-17.9 month-olds, `r e2_18to24` 18-24 month-olds) and their parents participated in the same museum as Experiment 1.
+`r nrow(e2data)` infants (F = `r e2_gender['F']`, M = `r e2_gender['M']`) aged 12-24 months (`r e2_12to18` 12-17.9 month-olds, `r e2_18to24` 18-24 month-olds) and their parents participated in the same museum as Experiment 1.
 We included infants who were exposed to English at least 75 percent of the time or who were exposed less but whose participating parent reported that they primarily speak English with their child at home.
@@
 # Predicting lexical diversity based on experimental condition. 
-modTTR <- lmer(TTR ~ age * condition + (1 | video), data=lmer_data) 
-summary(modTTR) # condition beta=-.09  t(8.6) = 3.33 p=.009 (suggestive)
-e2TTR <- get_lmer_reporting_values(modTTR)
+e2TTR_m <- stan_lmer(TTR ~ age * condition + (1 | video), data=e2data) 
+summary(e2TTR_m) # conditionexp beta=-.1 95% CI=[-.2,0.0]
+e2TTR <- get_stan_glmer_reporting_values(e2TTR_m,"conditionexp")
 
 # predict word tokens
-tokens_mod <- lmer(tokens ~ age * condition + (1 | video), data=lmer_data)
-summary(tokens_mod) # NA
+e2tokens_m <- stan_lmer(tokens ~ age * condition + (1 | video), data=e2data)
+summary(e2tokens_m) # NA
 
-modMTLD <- lmer(MTLD ~ age * condition + (1 | video), data=lmer_data)
-summary(modMTLD) # NA
+e2MTLD_m <- stan_lmer(MTLD ~ age * condition + (1 | video), data=e2data)
+summary(e2MTLD_m) # NA
 
@@
 We fit a mixed-effects linear regression predicting TTR as a function of age (centered) and condition with an interaction term, and with random intercepts per video using lme4 [@lme4].
-There was suggestively lower TTR in the Video condition (mean: `r round(e2_lexdiv[2,]$TTR, 2)`) than in the Control condition (mean: `r round(e2_lexdiv[1,]$TTR, 2)`, $\beta=`r e2TTR["conditionexp","beta"]`$, t(`r e2TTR["conditionexp","df"]`) = `r e2TTR["conditionexp","tval"]`, *p*=`r e2TTR["conditionexp","pval"]`).
+There was suggestively lower TTR in the Video condition (mean: `r round(e2_lexdiv[2,]$TTR, 2)`) than in the Control condition (mean: `r round(e2_lexdiv[1,]$TTR, 2)`, $\beta=`r e2TTR["conditionexp"]`$, , 95% CI=[`r e2TTR['95pLB']`,`r e2TTR['95pUB']`]).
 There was no significant effect of age, nor a significant interaction.
@@
 
-ttr2 <- d %>% group_by(Condition) %>%
+ttr2 <- e2data %>% group_by(Condition) %>%
   tidyboot_mean(TTR)
@@
 
-mtld2 <- d %>% group_by(Condition) %>%
+mtld2 <- e2data %>% group_by(Condition) %>%
   tidyboot_mean(MTLD)
@@
 
-ms_tok2 <- d %>% group_by(Condition) %>%
+e2tok <- e2data %>% group_by(Condition) %>%
   tidyboot_mean(tokens)
 
-e2tokens <- ggplot(ms_tok2, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
+e2tokens <- ggplot(e2tok, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
   geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
@@
 
-ms_typ <- d %>% group_by(Condition) %>%
+e2typ <- e2data %>% group_by(Condition) %>%
   tidyboot_mean(types)
 
-e2types <- ggplot(ms_typ, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
+e2types <- ggplot(e2typ, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
   geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
@@
 summary(d)
-# triplicate variables: gender.x/y, ethnicity, english, num_lang, parent_ed, Exclude
 d$Condition <- factor(d$condition, levels = c("con","exp"), labels = c("Science Video","Activity Video"))
@@
 # Total number of bids
-bids_mod <- lmer(bids ~ age * Condition + (1 | video), data = e2ja, 
-                 control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5)))
-summary(bids_mod) # singular fit, convergence code: 0 condition beta=3.11, t(80) = 3.52 p<.001
-e2bids <- get_lmer_reporting_values(bids_mod)
-bids_bmod <- stan_glmer(bids ~ age * Condition + (1|video), data=e2ja)
-summary(bids_bmod) # significant effect of condition! mean=3.1, 95%CI = [1.1, 5.0]
+e2bids_m <- stan_lmer(bids ~ age * Condition + (1|video), data=e2ja)
+summary(e2bids_m) # significant effect of condition! mean=3.1, 95%CI = [1.1, 5.0]
+e2bids <- get_stan_glmer_reporting_values(e2bids_m, "ConditionActivity Video")
 
-tja_mod <- lmer(total_ja ~ age * Condition + (1 | video), data = e2ja,
-                control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5)))
-e2tja <- get_lmer_reporting_values(tja_mod)
-summary(tja_mod) # singular fit, convergence code: 0
-#                    Estimate Std. Error      df t value  Pr(>|t|) 
-# (Intercept)          7.2912     0.3898 80.0000  18.704  < 2e-16 ***
-# age                 -5.2687     1.5122 80.0000  -3.484 0.000804 ***
-# ConditionVideo       1.4893     0.5513 80.0000   2.701 0.008428 ** 
-# age:ConditionVideo   5.9189     2.2721 80.0000   2.605 0.010950 *
-
-tja_bmod <- stan_glmer(total_ja ~ age * Condition + (1|video), data=e2ja)
-summary(tja_bmod) # total episodes of joint attention -- age, age*condition, condition
+e2tja_m <- stan_glmer(total_ja ~ age * Condition + (1|video), data=e2ja)
+summary(e2tja_m) # total episodes of joint attention -- age, age*condition, condition
 #                                        mean    sd     2.5%   25%    50%    75%    97.5%
@@
 # age:ConditionVideo                      5.6    2.5    0.7    3.9    5.7    7.4   10.5 
+e2tjaAge = get_stan_glmer_reporting_values(e2tja_m, "age")
+e2tjaCond = get_stan_glmer_reporting_values(e2tja_m, "ConditionVideo")
+e2tjaAgeCond = get_stan_glmer_reporting_values(e2tja_m, "age:ConditionVideo")
 
@@
 As preregistered, we fit mixed-effects linear regressions predicting the number of parental bids for joint attention and the total number of episodes of JA as a function of fixed effects of condition, age (centered), and their interaction, with random intercepts per video.
-Shown in Figure \ref{fig:e2ja} (left panel), parents made significantly more bids for JA after watching the Activity Video (mean: `r round(subset(e2_bids, Condition=="Activity Video")$mean,2)`, bootstrapped 95% CI: `r round(subset(e2_bids, Condition=="Activity Video")$ci_lower,2)`, `r round(subset(e2_bids, Condition=="Activity Video")$ci_upper,2)`; $\beta=`r e2bids["ConditionActivity Video","beta"]`$, t(`r e2bids["ConditionActivity Video","df"]`) = `r e2bids["ConditionActivity Video","tval"]`, *p*=`r e2bids["ConditionActivity Video","pval"]`)) than after the Science Video (mean: `r round(subset(e2_bids, Condition=="Science Video")$mean,2)`, 95% CI: [`r round(subset(e2_bids, Condition=="Science Video")$ci_lower,2)`, `r round(subset(e2_bids, Condition=="Science Video")$ci_upper,2)`], $\beta=`r e2bids["ConditionActivity Video","beta"]`$, t(`r e2bids["ConditionActivity Video","df"]`) = `r e2bids["ConditionActivity Video","tval"]`, *p*<.001).
+Shown in Figure \ref{fig:e2ja} (left panel), parents made significantly more bids for JA after watching the Activity Video (mean: `r round(subset(e2_bids, Condition=="Activity Video")$mean,2)`, bootstrapped 95% CI: `r round(subset(e2_bids, Condition=="Activity Video")$ci_lower,2)`, `r round(subset(e2_bids, Condition=="Activity Video")$ci_upper,2)`; $\beta=`r e2bids["ConditionActivity Video"]`$, 95% CI = [`r e2bids["95pLB"]`,`r e2bids["95pUB"]`]) than after the Science Video (mean: `r round(subset(e2_bids, Condition=="Science Video")$mean,2)`, 95% CI: [`r round(subset(e2_bids, Condition=="Science Video")$ci_lower,2)`, `r round(subset(e2_bids, Condition=="Science Video")$ci_upper,2)`]).
 There were no other significant effects on parental bids for JA.
 
-In the regression predicting the number of episodes of JA, there was a significant main effect of condition ($\beta=`r e2tja["ConditionActivity Video","beta"]`$, t(`r e2tja["ConditionActivity Video","df"]`) = `r e2tja["ConditionActivity Video","tval"]`, *p*=`r e2tja["ConditionActivity Video","pval"]`), with more episodes of JA occurring after the Activity Video (mean: `r round(subset(e2_tja, Condition=="Activity Video")$mean,2)`, 95% CI: [`r round(subset(e2_tja, Condition=="Activity Video")$ci_lower,2)`, `r round(subset(e2_tja, Condition=="Activity Video")$ci_upper,2)`]) than after the Control Video (mean: `r round(subset(e2_tja, Condition=="Science Video")$mean,2)`, 95% CI: [`r round(subset(e2_tja, Condition=="Science Video")$ci_lower,2)`, `r round(subset(e2_tja, Condition=="Science Video")$ci_upper,2)`]).
+In the regression predicting the number of episodes of JA, there was a significant main effect of condition ($\beta=`r e2tjaCond["ConditionActivity Video"]`$, 95% CI = [`r e2tjaCond["95pLB"]`,`r e2tjaCond["95pUB"]`]), with more episodes of JA occurring after the Activity Video (mean: `r round(subset(e2_tja, Condition=="Activity Video")$mean,2)`, 95% CI: [`r round(subset(e2_tja, Condition=="Activity Video")$ci_lower,2)`, `r round(subset(e2_tja, Condition=="Activity Video")$ci_upper,2)`]) than after the Control Video (mean: `r round(subset(e2_tja, Condition=="Science Video")$mean,2)`, 95% CI: [`r round(subset(e2_tja, Condition=="Science Video")$ci_lower,2)`, `r round(subset(e2_tja, Condition=="Science Video")$ci_upper,2)`]).
 There was also a significant main effect of age ($\beta=`r e2tja["age","beta"]`$, t(`r e2tja["age","df"]`) = `r e2tja["age","tval"]`, *p*=`r e2tja["age","pval"]`), showing that the number of episodes of JA decreased with the child's age.

### 2019-09-11 paper/manuscript.Rmd
finished bayesian regression changes

@@
 In the regression predicting the number of episodes of JA, there was a significant main effect of condition ($\beta=`r e2tjaCond["ConditionActivity Video"]`$, 95% CI = [`r e2tjaCond["95pLB"]`,`r e2tjaCond["95pUB"]`]), with more episodes of JA occurring after the Activity Video (mean: `r round(subset(e2_tja, Condition=="Activity Video")$mean,2)`, 95% CI: [`r round(subset(e2_tja, Condition=="Activity Video")$ci_lower,2)`, `r round(subset(e2_tja, Condition=="Activity Video")$ci_upper,2)`]) than after the Control Video (mean: `r round(subset(e2_tja, Condition=="Science Video")$mean,2)`, 95% CI: [`r round(subset(e2_tja, Condition=="Science Video")$ci_lower,2)`, `r round(subset(e2_tja, Condition=="Science Video")$ci_upper,2)`]).
-There was also a significant main effect of age ($\beta=`r e2tja["age","beta"]`$, t(`r e2tja["age","df"]`) = `r e2tja["age","tval"]`, *p*=`r e2tja["age","pval"]`), showing that the number of episodes of JA decreased with the child's age.
-However, a significant interaction of age and condition ($\beta=`r e2tja["age:ConditionActivity Video","beta"]`$, t(`r e2tja["age:ConditionActivity Video","df"]`) = `r e2tja["age:ConditionActivity Video","tval"]`, *p*=`r e2tja["age:ConditionActivity Video","pval"]`), shown in the right panel of Figure \ref{fig:e2ja}, demonstrates that older children in the Activity Video condition did not see a decrease in the number of episodes of JA.
+There was also a significant main effect of age ($\beta=`r e2tjaAge["age"]`$, 95% CI = [`r e2bidsAge["95pLB"]`,`r e2bidsAge["95pUB"]`]), showing that the number of episodes of JA decreased with the child's age.
+However, a significant interaction of age and condition ($\beta=`r e2tjaAgeCond["age:ConditionActivity Video"]`$, 95% CI = [`r e2tjaAgeCond["95pLB"]`,`r e2tjaAgeCond["95pUB"]`]), shown in the right panel of Figure \ref{fig:e2ja}, demonstrates that older children in the Activity Video condition did not see a decrease in the number of episodes of JA.
 
@@
 
-e2tja_age = ggplot(d, aes(x = age, y = total_ja, group=Condition, colour = Condition)) +
+e2tja_age = ggplot(e2data, aes(x = age, y = total_ja, group=Condition, colour = Condition)) +
   geom_point(alpha=.7) + geom_smooth(method='lm') + 
@@
 # Episodes of coordinated joint attention
-cja_mod <- lmer(cja ~ age * Condition + (1 | video), data = e2ja,
-                control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5)))
-summary(cja_mod) #  Condition: t(80) = 2.47 beta=1.37 p=.01; age*Condition beta=5.24 t(80) = 2.19 p=.02
-e2cja <- get_lmer_reporting_values(cja_mod)
-# also singular fit, convergence code: 0 - Bayesian regression confirms:
-cja_bmod <- stan_glmer(cja ~ age * Condition + (1|video), data=e2ja)
-summary(cja_bmod) # age n.s., sig effect of condition: mean=1.3 95% CI=[.1,2.6]; age*condition mean=5.1 CI=[.5,9.6]
+e2cja_m <- stan_lmer(cja ~ age * Condition + (1 | video), data = e2ja)
+summary(e2cja_m) #  Condition: t(80) = 2.47 beta=1.37 p=.01; age*Condition beta=5.24 t(80) = 2.19 p=.02
+e2cjaCond <- get_stan_glmer_reporting_values(e2cja_m, "ConditionActivity Video")
+e2cjaAgeCond <- get_stan_glmer_reporting_values(e2cja_m, "age:ConditionActivity Video")
+# age n.s., sig effect of condition: mean=1.3 95% CI=[.1,2.6]; age*condition mean=5.1 CI=[.5,9.6]
 #                                        mean    sd     2.5%   25%    50%    75%    97.5%
@@
 # Episodes of passive joint attention.
-pja_mod <- lmer(pja ~ age * Condition + (1 | video), data = e2ja)
-summary(pja_mod) # age beta=-2.88 t(13.4) = 2.53 p=.02
-e2pja <- get_lmer_reporting_values(pja_mod)
+e2pja_m <- stan_lmer(pja ~ age * Condition + (1 | video), data = e2ja)
+summary(e2pja_m) # age beta=-2.7 95% CI=[-5.1,0.0]
+e2pja <- get_stan_glmer_reporting_values(e2pja_m, "age")
 
 # Total duration of passive joint attention.
-pja_time_mod <- lmer(pja_length ~ age * Condition + (1 | video), data = e2ja,
-                     control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5)))
-summary(pja_time_mod) # singular - convergence code: 0, age beta=-18.89 t(80) = 2.72 p=.008
-e2pja_time <- get_lmer_reporting_values(pja_time_mod)
-pjat_bmod <- stan_glmer(pja_length ~ age * Condition + (1|video), data=e2ja)
-summary(pjat_bmod) # age: est: -17.9 95% CI = [-33.1,-2.2]
+e2pjat_m <- stan_lmer(pja_length ~ age * Condition + (1|video), data=e2ja)
+summary(e2pjat_m) # age: est: -17.9 95% CI = [-33.1,-2.2] 
+e2pjat <- get_stan_glmer_reporting_values(e2pjat_m, "age")
 
 # Total duration of coordinated joint attention.
-cja_time_mod <- lmer(cja_length ~ age * condition + (1 | video), data = e2ja,
-                     control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5)))
-summary(cja_time_mod) # singular - convergence code: 0, marginal age: beta=37.35 t(80) = 1.95 p=.05
-cjat_bmod <- stan_glmer(cja_length ~ age * Condition + (1|video), data=e2ja)
-summary(cjat_bmod) # age: est: 35.3 95% CI = [-6.1,77.4] NOT SIGNIFICANT
+e2cjat_m <- stan_glmer(cja_length ~ age * Condition + (1|video), data=e2ja)
+summary(e2cjat_m) # age: est: 35.3 95% CI = [-6.1,77.4] ns
 
@@
 Four additional exploratory regressions with a similar structure were carried out to predict the number and duration of coordinated and passive JA episodes.
-The regression predicting the number of episodes of coordinated JA found a significant main effect of condition ($\beta=`r e2cja["ConditionActivity Video","beta"]`$, t(`r e2cja["ConditionActivity Video","df"]`) = `r e2cja["ConditionActivity Video","tval"]`, *p*=`r e2cja["ConditionActivity Video","pval"]`), with more episodes of coordinated JA occurring after the Activity Video (mean: `r round(subset(e2_cja, Condition=="Activity Video")$mean,2)`, 95% CI: [`r round(subset(e2_cja, Condition=="Activity Video")$ci_lower,2)`, `r round(subset(e2_cja, Condition=="Activity Video")$ci_upper,2)`]) than after the Control Video (mean: `r round(subset(e2_cja, Condition=="Science Video")$mean,2)`, 95% CI: [`r round(subset(e2_cja, Condition=="Science Video")$ci_lower,2)`, `r round(subset(e2_cja, Condition=="Science Video")$ci_upper,2)`]).
-There was no significant effect of age, but there was a significant interaction of age and condition ($\beta=`r e2cja["age:ConditionActivity Video","beta"]`$, t(`r e2cja["age:ConditionActivity Video","df"]`) = `r e2cja["age:ConditionActivity Video","tval"]`, *p*=`r e2cja["age:ConditionActivity Video","pval"]`), shown in Figure \ref{fig:e2ja-coord}, revealing that older children in the Activity Video condition had more episodes of coordinated JA than children in the Control Video condition.
+The regression predicting the number of episodes of coordinated JA found a significant main effect of condition ($\beta=`r e2cjaCond["ConditionActivity Video"]`$, 95% CI = [`r e2cjaCond["95pLB"]`,`r e2cjaCond["95pUB"]`]), with more episodes of coordinated JA occurring after the Activity Video (mean: `r round(subset(e2_cja, Condition=="Activity Video")$mean,2)`, 95% CI: [`r round(subset(e2_cja, Condition=="Activity Video")$ci_lower,2)`, `r round(subset(e2_cja, Condition=="Activity Video")$ci_upper,2)`]) than after the Control Video (mean: `r round(subset(e2_cja, Condition=="Science Video")$mean,2)`, 95% CI: [`r round(subset(e2_cja, Condition=="Science Video")$ci_lower,2)`, `r round(subset(e2_cja, Condition=="Science Video")$ci_upper,2)`]).
+There was no significant effect of age, but there was a significant interaction of age and condition ($\beta=`r e2cjaAgeCond["age:ConditionActivity Video"]`$, 95% CI = [`r e2cjaAgeCond["95pLB"]`,`r e2cjaAgeCond["95pUB"]`]), shown in Figure \ref{fig:e2ja-coord}, revealing that older children in the Activity Video condition had more episodes of coordinated JA than children in the Control Video condition.
 The regression predicting the total duration of coordinated JA episodes revealed no significant effects.
 
-In the regression predicting the number of episodes of passive JA, there was a main effect of age ($\beta=`r e2pja["ConditionActivity Video","beta"]`$, t(`r e2pja["ConditionActivity Video","df"]`) = `r e2pja["ConditionActivity Video","tval"]`, *p*=`r e2pja["ConditionActivity Video","pval"]`), showing that older children had more episodes of passive JA with their caregiver.
-The regression predicting the total duration of passive JA revealed a main effect of age ($\beta=`r e2pja_time["ConditionActivity Video","beta"]`$, t(`r e2pja_time["ConditionActivity Video","df"]`) = `r e2pja_time["ConditionActivity Video","tval"]`, *p*=`r e2pja_time["ConditionActivity Video","pval"]`), revealing that older children spent more time in passive JA with their caregiver.
+In the regression predicting the number of episodes of passive JA, there was a main effect of age ($\beta=`r e2pja["age"]`$, 95% CI = [`r e2pja["95pLB"]`,`r e2pja["95pUB"]`]), showing that older children had more episodes of passive JA with their caregiver.
+The regression predicting the total duration of passive JA revealed a main effect of age ($\beta=`r e2pjat["age"]`$, 95% CI = [`r e2pjat["95pLB"]`,`r e2pjat["95pUB"]`]), revealing that older children spent more time in passive JA with their caregiver.
 Overall, these results show that the older children in our sample engage in more and longer episodes of joint attention with their caregivers, and suggest that the Activity Video strengthened this trend in the number of episodes of coordinated JA.
@@
 #Episodes of coordinated joint attention
-ms_cja <- d %>% group_by(Condition) %>%
+e2cjad <- e2ja %>% group_by(Condition) %>%
   tidyboot_mean(cja)
 
-e2cja <- ggplot(ms_cja, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
+e2cja <- ggplot(e2cjad, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
   geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
@@
 
-e2cja_age = ggplot(d, aes(x = age, y = cja, group=Condition, colour = Condition)) +
+e2cja_age = ggplot(e2ja, aes(x = age, y = cja, group=Condition, colour = Condition)) +
   geom_point(alpha=.7) + geom_smooth(method='lm') + 

### 2019-09-16 paper/manuscript.Rmd
Bayesian regression reporting done

@@
 
-e1_lexdiv <- lmer_data %>% group_by(condition) %>%
+e1_lexdiv <- e1ld %>% group_by(condition) %>%
   summarise(TTR=mean(TTR), MTLD=mean(MTLD), tokens=mean(tokens)) 
@@
   geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .7)) +
-  geom_point(data=d, aes(x=Condition, y=TTR), alpha=.2, position = position_jitterdodge()) +
+  geom_point(data=e1ld, aes(x=Condition, y=TTR), alpha=.2, position = position_jitterdodge()) +
   xlab("Condition") + ylab("Type/Token Ratio (TTR)") +
@@
   geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
-  geom_point(data=d, aes(x=Condition, y=MTLD), alpha=.2, position = position_jitterdodge()) +
+  geom_point(data=e1ld, aes(x=Condition, y=MTLD), alpha=.2, position = position_jitterdodge()) +
   xlab("Condition") + ylab("MTLD") +
@@
   geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
-  geom_point(data=d, aes(x=Condition, y=tokens), alpha=.2, position = position_jitterdodge()) +
+  geom_point(data=e1ld, aes(x=Condition, y=tokens), alpha=.2, position = position_jitterdodge()) +
   xlab("Condition") + ylab("Total Number of Word Tokens") +
@@
 
-ttr_means <- d %>% group_by(Condition) %>%
+ttr_means <- e1ld %>% group_by(Condition) %>%
   summarise(mean = mean(TTR), sd = sd(TTR))
@@
   geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
-  geom_point(data=d, aes(x=Condition, y=bids_tot), alpha=.2, position = position_jitterdodge()) +
+  geom_point(data=e1ja, aes(x=Condition, y=bids_tot), alpha=.2, position = position_jitterdodge()) +
   xlab("Condition") + ylab("Mean Bids for Joint Attention") +
@@
   geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
-  geom_point(data=d, aes(x=Condition, y=total_ja), alpha=.2, position = position_jitterdodge()) +
+  geom_point(data=e1ja, aes(x=Condition, y=total_ja), alpha=.2, position = position_jitterdodge()) +
   xlab("Condition") + ylab("Mean Episodes of Joint Attention") +
@@
 
-e2_lexdiv <- lmer_data %>% group_by(condition) %>%
+e2_lexdiv <- e2data %>% group_by(condition) %>%
   summarise(TTR=mean(TTR), MTLD=mean(MTLD), tokens=mean(tokens)) 
@@
 ```{r e2tab, echo=F}
-d$Condition = factor(d$condition, levels = c("con", "exp"), labels = c("Science Video", "Activity Video"))
-e2 <- d %>% group_by(Condition) %>%
+e2data$Condition = factor(d$condition, levels = c("con", "exp"), labels = c("Science Video", "Activity Video"))
+e2 <- e2data %>% group_by(Condition) %>%
   summarise("Mean TTR"=mean(TTR), TTRsd=sd(TTR),
@@
   geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
-  geom_point(data=d, aes(x=Condition, y=TTR), alpha=.2, position = position_jitterdodge()) +
+  geom_point(data=e2data, aes(x=Condition, y=TTR), alpha=.2, position = position_jitterdodge()) +
   xlab("Condition") + ylab("TTR") +
@@
   geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
-  geom_point(data=d, aes(x=Condition, y=MTLD), alpha=.2, position = position_jitterdodge()) +
+  geom_point(data=e2data, aes(x=Condition, y=MTLD), alpha=.2, position = position_jitterdodge()) +
   xlab("Condition") + ylab("MTLD") +
@@
   geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
-  geom_point(data=d, aes(x=Condition, y=tokens), alpha=.2, position = position_jitterdodge()) +
+  geom_point(data=e2data, aes(x=Condition, y=tokens), alpha=.2, position = position_jitterdodge()) +
   xlab("Condition") + ylab("Total Number of Word Tokens") +
@@
   geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
-  geom_point(data=d, aes(x=Condition, y=types), alpha=.2, position = position_jitterdodge()) +
+  geom_point(data=e2data, aes(x=Condition, y=types), alpha=.2, position = position_jitterdodge()) +
   xlab("Condition") + ylab("Total Number of Word Types") +
@@
                      cja_length = cja_length/1000,
-                     total_lja = total_lja/1000)
+                     total_lja = total_lja/1000) # convert duration ms -> seconds
 
@@
 e2tjaAge = get_stan_glmer_reporting_values(e2tja_m, "age")
-e2tjaCond = get_stan_glmer_reporting_values(e2tja_m, "ConditionVideo")
-e2tjaAgeCond = get_stan_glmer_reporting_values(e2tja_m, "age:ConditionVideo")
+e2tjaCond = get_stan_glmer_reporting_values(e2tja_m, "ConditionActivity Video")
+e2tjaAgeCond = get_stan_glmer_reporting_values(e2tja_m, "age:ConditionActivity Video")
 
@@
 In the regression predicting the number of episodes of JA, there was a significant main effect of condition ($\beta=`r e2tjaCond["ConditionActivity Video"]`$, 95% CI = [`r e2tjaCond["95pLB"]`,`r e2tjaCond["95pUB"]`]), with more episodes of JA occurring after the Activity Video (mean: `r round(subset(e2_tja, Condition=="Activity Video")$mean,2)`, 95% CI: [`r round(subset(e2_tja, Condition=="Activity Video")$ci_lower,2)`, `r round(subset(e2_tja, Condition=="Activity Video")$ci_upper,2)`]) than after the Control Video (mean: `r round(subset(e2_tja, Condition=="Science Video")$mean,2)`, 95% CI: [`r round(subset(e2_tja, Condition=="Science Video")$ci_lower,2)`, `r round(subset(e2_tja, Condition=="Science Video")$ci_upper,2)`]).
-There was also a significant main effect of age ($\beta=`r e2tjaAge["age"]`$, 95% CI = [`r e2bidsAge["95pLB"]`,`r e2bidsAge["95pUB"]`]), showing that the number of episodes of JA decreased with the child's age.
+There was also a significant main effect of age ($\beta=`r e2tjaAge["age"]`$, 95% CI = [`r e2tjaAge["95pLB"]`,`r e2tjaAge["95pUB"]`]), showing that the number of episodes of JA decreased with the child's age.
 However, a significant interaction of age and condition ($\beta=`r e2tjaAgeCond["age:ConditionActivity Video"]`$, 95% CI = [`r e2tjaAgeCond["95pLB"]`,`r e2tjaAgeCond["95pUB"]`]), shown in the right panel of Figure \ref{fig:e2ja}, demonstrates that older children in the Activity Video condition did not see a decrease in the number of episodes of JA.
@@
 
-e2tja_age = ggplot(e2data, aes(x = age, y = total_ja, group=Condition, colour = Condition)) +
+e2tja_age = ggplot(e2ja, aes(x = age, y = total_ja, group=Condition, colour = Condition)) +
   geom_point(alpha=.7) + geom_smooth(method='lm') + 
@@
   tidyboot_mean(cja)
+
+e2tjat_m <- stan_glmer(total_lja ~ age * Condition + (1|video), data=e2ja)
+summary(e2tjat_m) # anything here?
+
 ```
@@
 
-```{r e2ja-coord, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=5.5, fig.height=3.5, fig.cap = "\\label{fig:e2ja-coord} The number of episodes of coordinated JA by condition and age in Experiment 2.
+```{r e2ja-coord, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=5.5, fig.height=3.5, fig.cap = "The number of episodes of coordinated JA by condition and age in Experiment 2.
 Older children in the Activity Video condition engaged in more episodes of coordinated JA with their caregiver than dyads in the Control Video condition."}
@@
   geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
-  geom_point(data=d, aes(x=Condition, y=cja), alpha=.2, position = position_jitterdodge()) +
+  geom_point(data=e2ja, aes(x=Condition, y=cja), alpha=.2, position = position_jitterdodge()) +
   xlab("Condition") + ylab("Episodes of Coordinated JA") +
@@
 \endgroup
+
+```{r echo = FALSE, results = 'asis'}
+render_appendix('appendix.Rmd')
+```

### 2019-09-16 paper/manuscript.tex
Bayesian regression reporting done

@@
 A joint attention episode was considered \emph{coordinated} if both participants visually focused on an object for 3 or more seconds and at some point in the interaction the child indicated awareness of interaction with some overt behavior toward the parent such as looking at their face, gesturing, vocalizing, or turn-taking.
-Full details of our guidelines for coding joint attention are available in \href{https://docs.google.com/document/d/1cZrT_Gjt6p0om19lXO-XcFnT09pb0giyhRQ-Pm1yoBU/edit?usp=sharing}{SI}.
+Full details of our guidelines for coding joint attention are available in SI.
 
@@
 
-We fit a mixed-effects linear regression predicting TTR as a function of condition, age (centered), gender, and parent's education level with a random intercept per video using lme4 (Bates, Mächler, Bolker, \& Walker, 2015).
-There was significantly lower TTR in the Video condition (mean: 0.32) than in the Control condition (mean: 0.43, \(\beta=\)-0.11, t(52.4) = 4.22, \emph{p}\textless{}.001).
+We fit a Bayesian mixed-effects linear regression predicting TTR as a function of condition, age (centered), gender, and parent's education level with a random intercept per video using rstanarm (Goodrich, Gabry, Ali, \& Brilleman, 2018).
+For effects that are at least 95\% likely to be non-zero according to the posterior distribution, we report estimated coefficients (\(\beta\)) as well as 95\% Bayesian credible intervals (95\% CI), demarcating the range within which 95\% of the posterior predictive values fall.
+There was significantly lower TTR in the Video condition (mean: 0.32) than in the Control condition (mean: 0.43, \(\beta=\)-0.11, 95\% CI={[}-0.16,-0.06{]}).
 There were no significant effects of age, gender, or parent's level of education.
-A similar mixed-effects linear regression instead predicting MTLD also found significantly lower lexical diversity in the Video condition (mean MTLD: 17.87) than in the Control condition (mean: 0.32, \(\beta=\)-8.73, t(55) = 2.67, \emph{p}=.001), with no other significant effects.
+A similar Bayesian mixed-effects linear regression instead predicting MTLD also found significantly lower lexical diversity in the Video condition (mean MTLD: 17.87) than in the Control condition (mean: 27.09, \(\beta=\)-8.62, 95\% CI={[}-15.15,-2.01{]}), with no other significant effects.
 Figure \ref{fig:e1lexdiv} shows the mean of each lexical diversity measure (TTR and MTLD) by condition.
 
-We also conducted similar regressions predicting the number of word tokens and types, finding only a significant effect of condition on the number of word tokens (\(\beta= 56.01\), t(40.4)=2.30, \emph{p}\textless{}.05), with parents using more words in the Video condition (mean: 225, bootstrapped 95\% confidence intervals (CI): {[}199,253{]}) than in the Control condition (mean: 165, bootstrapped 95\% CI: {[}139,192{]}).
-The means of the lexical diversity measures are reported in Table \ref{tab:e1tab}.
-
-\begin{table}[t]
-
-\caption{\label{tab:e1tab}Lexical diversity measures in Experiment 1.}
-\centering
-\begin{tabular}{l|r|r|r|r|r|r|r|r}
-\hline
-Condition & TTR (M) & (sd) & MTLD (M) & (sd) & Types (M) & (sd) & Tokens (M) & (sd)\\
-\hline
-No Video & 0.43 & 0.10 & 27.09 & 15.33 & 67.33 & 22.94 & 165.10 & 75.15\\
-\hline
-Activity Video & 0.32 & 0.09 & 17.87 & 6.28 & 67.37 & 19.01 & 225.43 & 76.07\\
-\hline
-\end{tabular}
-\end{table}
+We also conducted similar regressions predicting the number of word tokens and types, finding only a significant effect of condition on the number of word tokens (\(\beta=\) 56.36, 95\% CI={[}14.02,96.32{]})), with parents using more words in the Video condition (mean: 225, bootstrapped 95\% confidence intervals (CI): {[}199,252{]}) than in the Control condition (mean: 165, bootstrapped 95\% CI: {[}139,193{]}).
 
@@
 This lme4 model included random intercepts per video.
-There were significantly more bids for JA in the Video condition (mean: 6.24, sd: 2.79) than in the Control condition (mean: 3.56, sd: 2.50, \(\beta=3.51\), t(40.30) = 2.95, \emph{p}\textless{}.01).
-There were no other significant effects.
+There were significantly more bids for JA in the Video condition (mean: 6.24, sd: 2.79) than in the Control condition (mean: 3.56, sd: 2.50, \(\beta=3.44\), 95\% CI={[}1.12,5.80{]}).
 
@@
 There were no significant effects on the number or total duration of coordinated JA episodes, nor on the total duration of passive JA episodes.
-For the regression predicting the number of passive JA episodes, the only significant effect was an interaction of condition and RR (\(\beta=1.83\), t(41.50) = 2.22, \emph{p}\textless{}.05), showing that for parents in the Video condition, those with higher Rules and Respect subscores engaged in more passive JA episodes.
+For the regression predicting the number of passive JA episodes, the only significant effect was an interaction of condition and RR (\(\beta=1.84\), 95\% CI={[}0.23,3.44{]}), showing that for parents in the Video condition, those with higher Rules and Respect subscores engaged in more passive JA episodes.
 Figure \ref{fig:e1ja} shows the mean number bids for JA and episodes of JA by condition in Experiment 1.
@@
 
-We fit a mixed-effects linear regression predicting TTR as a function of age (centered) and condition with an interaction term, and with random intercepts per video using lme4 (Bates et al., 2015).
-There was suggestively lower TTR in the Video condition (mean: 0.38) than in the Control condition (mean: 0.48, \(\beta=-0.09\), t(8.60) = 3.33, \emph{p}=0.01).
+We fit a mixed-effects linear regression predicting TTR as a function of age (centered) and condition with an interaction term, and with random intercepts per video using lme4 (Bates, Mächler, Bolker, \& Walker, 2015).
+There was suggestively lower TTR in the Video condition (mean: 0.38) than in the Control condition (mean: 0.48, \(\beta=-0.09\), , 95\% CI={[}-0.15,-0.03{]}).
 There was no significant effect of age, nor a significant interaction.
@@
 As preregistered, we fit mixed-effects linear regressions predicting the number of parental bids for joint attention and the total number of episodes of JA as a function of fixed effects of condition, age (centered), and their interaction, with random intercepts per video.
-Shown in Figure \ref{fig:e2ja} (left panel), parents made significantly more bids for JA after watching the Activity Video (mean: 12.98, bootstrapped 95\% CI: 11.77, 14.18; \(\beta=3.11\), t(80) = 3.52, \emph{p}=0.00)) than after the Science Video (mean: 9.88, 95\% CI: {[}8.69, 11.11{]}, \(\beta=3.11\), t(80) = 3.52, \emph{p}\textless{}.001).
+Shown in Figure \ref{fig:e2ja} (left panel), parents made significantly more bids for JA after watching the Activity Video (mean: 12.96, bootstrapped 95\% CI: 11.74, 14.21; \(\beta=3.06\), 95\% CI = {[}0.96,5.06{]}) than after the Science Video (mean: 9.88, 95\% CI: {[}8.71, 11.07{]}).
 There were no other significant effects on parental bids for JA.
 
-In the regression predicting the number of episodes of JA, there was a significant main effect of condition (\(\beta=1.49\), t(80) = 2.70, \emph{p}=0.01), with more episodes of JA occurring after the Activity Video (mean: 8.78, 95\% CI: {[}7.89, 9.67{]}) than after the Control Video (mean: 7.33, 95\% CI: {[}6.57, 8.06{]}).
-There was also a significant main effect of age (\(\beta=-5.27\), t(80) = 3.48, \emph{p}=0.00), showing that the number of episodes of JA decreased with the child's age.
-However, a significant interaction of age and condition (\(\beta=5.92\), t(80) = 2.61, \emph{p}=0.01), shown in the right panel of Figure \ref{fig:e2ja}, demonstrates that older children in the Activity Video condition did not see a decrease in the number of episodes of JA.
+In the regression predicting the number of episodes of JA, there was a significant main effect of condition (\(\beta=1.49\), 95\% CI = {[}0.26,2.78{]}), with more episodes of JA occurring after the Activity Video (mean: 8.79, 95\% CI: {[}7.95, 9.67{]}) than after the Control Video (mean: 7.33, 95\% CI: {[}6.54, 8.05{]}).
+There was also a significant main effect of age (\(\beta=-5.02\), 95\% CI = {[}-8.23,-1.41{]}), showing that the number of episodes of JA decreased with the child's age.
+However, a significant interaction of age and condition (\(\beta=5.67\), 95\% CI = {[}0.50,10.71{]}), shown in the right panel of Figure \ref{fig:e2ja}, demonstrates that older children in the Activity Video condition did not see a decrease in the number of episodes of JA.
 
@@
 Four additional exploratory regressions with a similar structure were carried out to predict the number and duration of coordinated and passive JA episodes.
-The regression predicting the number of episodes of coordinated JA found a significant main effect of condition (\(\beta=1.37\), t(80) = 2.59, \emph{p}=0.01), with more episodes of coordinated JA occurring after the Activity Video (mean: 6.71, 95\% CI: {[}5.92, 7.61{]}) than after the Control Video (mean: 5.34, 95\% CI: {[}4.72, 5.98{]}).
-There was no significant effect of age, but there was a significant interaction of age and condition (\(\beta=5.24\), t(80) = 2.40, \emph{p}=0.02), shown in Figure \ref{fig:e2ja-coord}, revealing that older children in the Activity Video condition had more episodes of coordinated JA than children in the Control Video condition.
+The regression predicting the number of episodes of coordinated JA found a significant main effect of condition (\(\beta=1.36\), 95\% CI = {[}0.16,2.58{]}), with more episodes of coordinated JA occurring after the Activity Video (mean: 6.71, 95\% CI: {[}5.90, 7.56{]}) than after the Control Video (mean: 5.34, 95\% CI: {[}4.68, 6.02{]}).
+There was no significant effect of age, but there was a significant interaction of age and condition (\(\beta=5.34\), 95\% CI = {[}0.80,10.22{]}), shown in Figure \ref{fig:e2ja-coord}, revealing that older children in the Activity Video condition had more episodes of coordinated JA than children in the Control Video condition.
 The regression predicting the total duration of coordinated JA episodes revealed no significant effects.
 
-In the regression predicting the number of episodes of passive JA, there was a main effect of age (\(\beta=0.11\), t(6.90) = 0.27, \emph{p}=0.80), showing that older children had more episodes of passive JA with their caregiver.
-The regression predicting the total duration of passive JA revealed a main effect of age (\(\beta=0.40\), t(80) = 0.16, \emph{p}=0.88), revealing that older children spent more time in passive JA with their caregiver.
+In the regression predicting the number of episodes of passive JA, there was a main effect of age (\(\beta=-2.72\), 95\% CI = {[}-5.07,0.19{]}), showing that older children had more episodes of passive JA with their caregiver.
+The regression predicting the total duration of passive JA revealed a main effect of age (\(\beta=-17.70\), 95\% CI = {[}-32.73,-1.79{]}), revealing that older children spent more time in passive JA with their caregiver.
 Overall, these results show that the older children in our sample engage in more and longer episodes of joint attention with their caregivers, and suggest that the Activity Video strengthened this trend in the number of episodes of coordinated JA.
@@
 
-\caption{\label{fig:e2ja-coord} The number of episodes of coordinated JA by condition and age in Experiment 2.
+\caption{The number of episodes of coordinated JA by condition and age in Experiment 2.
 Older children in the Activity Video condition engaged in more episodes of coordinated JA with their caregiver than dyads in the Control Video condition.}\label{fig:e2ja-coord}
@@
 \url{http://doi.org/10.1126/science.1251178}
+
+\leavevmode\hypertarget{ref-rstanarm}{}%
+Goodrich, B., Gabry, J., Ali, I., \& Brilleman, S. (2018). Rstanarm: Bayesian applied regression modeling via Stan. Retrieved from \url{http://mc-stan.org/}
 

### 2019-09-16 paper/extra_text.R

@@ -1,3 +1,7 @@
+notes:
+  - replace bootstrapped 95pct CIs with Bayesian credibility interval?
+  -
+
 unused text
 
 Under such expert guidance, children are encouraged and motivated to engage in more advanced play, undertaking explorations that push the boundaries of what they would be able to do unaided [@Vygotsky1980].

### 2019-09-17 paper/manuscript.Rmd
combined Exp 1 and Exp 2 figures

@@
 
+```{r load-exp1-lexical-data, include=F}
+e1path = "../parenting_obs_e1/"
+load(paste(e1path,"Exp1_cleaned_data.RData",sep='')) # merged dataframe ready for plotting
+
+e1ld <- d %>%
+  #filter(!is.na(AA), !is.na(EL), !is.na(RR))%>%
+  mutate(condition = factor(condition), 
+         MTLD = as.numeric(MTLD),
+         EL = as.numeric(langcog::scale(EL, scale=FALSE)),
+         AA = as.numeric(langcog::scale(AA, scale=FALSE)),
+         RR = as.numeric(langcog::scale(RR, scale=FALSE)),
+         age = as.numeric(langcog::scale(age, scale=FALSE)),
+         parent_ed = as.numeric(langcog::scale(parent_ed, scale=T)),
+         gender = as.factor(gender),
+         video = as.factor(video))
+
+e1_gender = table(e1ld$gender)
+#table(cut_interval(d$age, n=2, breaks=c(.5,1.5,2.1), labels=F))
+#table(cut_number(d$age, n=3, breaks=c(.5,1.5,2.1)))
+e1_parent_ed = table(e1ld$parent_ed)
+```
+
+```{r load-exp1-joint-attention-data, echo=F}
+load(paste(e1path,"joint_attention/Exp1_joint_attention_data.RData",sep=''))
+d$Condition <- factor(d$Condition, levels = c("con","exp"), labels = c("No Video","Activity Video"))
+
+e1ja <- d %>%
+  #filter(!is.na(AA), !is.na(EL), !is.na(RR)) %>% # 6 parents NA -- don't want to remove from main analysis!
+  mutate(Condition = factor(Condition), 
+         bids_tot = as.numeric(bids_tot),
+         EL = as.numeric(langcog::scale(EL, scale=FALSE)),
+         AA = as.numeric(langcog::scale(AA, scale=FALSE)),
+         RR = as.numeric(langcog::scale(RR, scale=FALSE)),
+         age = as.numeric(langcog::scale(age, scale=FALSE)),
+         gender = as.factor(gender),
+         Video = as.factor(Video),
+         pja_length = pja_length/1000,
+         cja_length = cja_length/1000,
+         total_lja = total_lja/1000) # convert duration ms -> seconds
+```
+
+```{r load-exp2-lexical-data, echo=F}
+e2path = "../parenting_obs_e2/"
+load(paste(e2path,"Exp2_cleaned_data.RData",sep=''))
+
+e2data <- d %>%
+  mutate(condition = factor(condition), 
+         MTLD = as.numeric(MTLD),
+         TTR = as.numeric(TTR),
+         age = as.numeric(langcog::scale(age, scale=FALSE)),
+         video = as.factor(video))
+
+e2data$Condition = factor(d$condition, levels = c("con", "exp"), labels = c("Science Video", "Activity Video"))
+
+e2_gender = table(d$gender)
+e2_ethnicity = table(d$ethnicity)
+e2_parent_ed = table(d$parent_ed)
+e2_12to18 = nrow(subset(d, age<1.5))
+e2_18to24 = nrow(subset(d, age>=1.5))
+```
+
+```{r load-exp2-joint-attention-data, echo=F}
+load(paste(e2path,"joint_attention/Exp2_joint_attention_data.RData",sep=''))
+d$Condition <- factor(d$condition, levels = c("con","exp"), labels = c("Science Video","Activity Video"))
+d$Age = d$age 
+e2ja <- d %>% mutate(bids = bids_tot,
+                     age = as.numeric(langcog::scale(age, scale=FALSE)),
+                     pja_length = pja_length/1000,
+                     cja_length = cja_length/1000,
+                     total_lja = total_lja/1000) # convert duration ms -> seconds
+
+```
+
 ```{r analysis-preferences}
@@
 
-```{r load-exp1-lexical-data, include=F}
-e1path = "../parenting_obs_e1/"
-load(paste(e1path,"Exp1_cleaned_data.RData",sep='')) # merged dataframe ready for plotting
-
-e1ld <- d %>%
-  #filter(!is.na(AA), !is.na(EL), !is.na(RR))%>%
-  mutate(condition = factor(condition), 
-         MTLD = as.numeric(MTLD),
-         EL = as.numeric(langcog::scale(EL, scale=FALSE)),
-         AA = as.numeric(langcog::scale(AA, scale=FALSE)),
-         RR = as.numeric(langcog::scale(RR, scale=FALSE)),
-         age = as.numeric(langcog::scale(age, scale=FALSE)),
-         parent_ed = as.numeric(langcog::scale(parent_ed, scale=T)),
-         gender = as.factor(gender),
-         video = as.factor(video))
-
-e1_gender = table(e1ld$gender)
-#table(cut_interval(d$age, n=2, breaks=c(.5,1.5,2.1), labels=F))
-#table(cut_number(d$age, n=3, breaks=c(.5,1.5,2.1)))
-e1_parent_ed = table(e1ld$parent_ed)
-```
-
 ### Participants. 
-`r nrow(d)` infants (F = `r e1_gender['F']`, M = `r e1_gender['M']`) aged 6-24 months (20 6-11.9 month-olds, 20 12-17.9 month-olds, and 20 18-24 month-olds) and their parents participated in a museum in northern California.
+`r nrow(e1ld)` infants (F = `r e1_gender['F']`, M = `r e1_gender['M']`) aged 6-24 months (20 6-11.9 month-olds, 20 12-17.9 month-olds, and 20 18-24 month-olds) and their parents participated in a museum in northern California.
 We included infants who were exposed to English at least 50 percent of the time (n = 58) or who were exposed less but whose participating parent reported that they primarily speak English with their child at home (n = 2).
@@
 A similar Bayesian mixed-effects linear regression instead predicting MTLD also found significantly lower lexical diversity in the Video condition (mean MTLD: `r round(subset(e1_lexdiv, condition=='exp')$MTLD, 2)`) than in the Control condition (mean: `r round(subset(e1_lexdiv, condition=='con')$MTLD, 2)`, $\beta=$`r e1MTLD["conditionexp"]`, 95% CI=[`r e1MTLD['95pLB']`,`r e1MTLD['95pUB']`]), with no other significant effects.
-Figure \ref{fig:e1lexdiv} shows the mean of each lexical diversity measure (TTR and MTLD) by condition.
+Figure \ref{fig:lexdiv} shows the mean of each lexical diversity measure (TTR and MTLD) by condition.
 
@@
 
-ms_lex_mtld <- e1ld %>% group_by(Condition) %>%
+e1_mtld <- e1ld %>% group_by(Condition) %>%
   tidyboot_mean(MTLD) 
-ms_lex <- e1ld %>% group_by(Condition) %>%
+e1_lex <- e1ld %>% group_by(Condition) %>%
   tidyboot_mean(TTR) # Type/Token Ratio
-ms_tok <- e1ld %>% group_by(Condition) %>%
+e1_tok <- e1ld %>% group_by(Condition) %>%
   tidyboot_mean(tokens) 
-ms_type <- e1ld %>% group_by(Condition) %>%
+e1_type <- e1ld %>% group_by(Condition) %>%
   tidyboot_mean(types)
@@
 
-We also conducted similar regressions predicting the number of word tokens and types, finding only a significant effect of condition on the number of word tokens ($\beta=$ `r e1tokens["conditionexp"]`, 95% CI=[`r e1tokens['95pLB']`,`r e1tokens['95pUB']`])), with parents using more words in the Video condition (mean: `r round(subset(e1_lexdiv, condition=='exp')$tokens, 0)`, bootstrapped 95% confidence intervals (CI): [`r round(subset(ms_tok, Condition=="Activity Video")$ci_lower, 0)`,`r round(subset(ms_tok, Condition=="Activity Video")$ci_upper, 0)`]) than in the Control condition (mean: `r round(subset(e1_lexdiv, condition=='con')$tokens, 0)`, bootstrapped 95% CI: [`r round(subset(ms_tok, Condition=="No Video")$ci_lower, 0)`,`r round(subset(ms_tok, Condition=="No Video")$ci_upper, 0)`]).
+We also conducted similar regressions predicting the number of word tokens and types, finding only a significant effect of condition on the number of word tokens ($\beta=$ `r e1tokens["conditionexp"]`, 95% CI=[`r e1tokens['95pLB']`,`r e1tokens['95pUB']`])), with parents using more words in the Video condition (mean: `r round(subset(e1_lexdiv, condition=='exp')$tokens, 0)`, bootstrapped 95% confidence intervals (CI): [`r round(subset(e1_tok, Condition=="Activity Video")$ci_lower, 0)`,`r round(subset(e1_tok, Condition=="Activity Video")$ci_upper, 0)`]) than in the Control condition (mean: `r round(subset(e1_lexdiv, condition=='con')$tokens, 0)`, bootstrapped 95% CI: [`r round(subset(e1_tok, Condition=="No Video")$ci_lower, 0)`,`r round(subset(e1_tok, Condition=="No Video")$ci_upper, 0)`]).
 
@@
 ```{r hiddenfigs, include=F}
-e1ttr <- ggplot(ms_lex, aes(x=Condition, y=mean, fill=Condition)) + geom_bar(stat="identity") + 
+e1ttr <- ggplot(e1_lex, aes(x=Condition, y=mean, fill=Condition)) + geom_bar(stat="identity") + 
   geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .7)) +
@@
   langcog::scale_fill_solarized() + ggthemes::theme_few() +
-  theme(legend.position="none")
+  theme(legend.position="none") + ggtitle("Experiment 1")
 
-e1mtld <- ggplot(ms_lex_mtld, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
+e1mtld <- ggplot(e1_mtld, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
   geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
@@
   langcog::scale_fill_solarized() + ggthemes::theme_few() + 
-  theme(legend.position="none")
+  theme(legend.position="none") + ggtitle(" ")
 
-e1tokens <- ggplot(ms_tok, aes(x=Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
+e1tokens <- ggplot(e1_tok, aes(x=Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
   geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
@@
   langcog::scale_fill_solarized() + ggthemes::theme_few() +
-  theme(legend.position="none")
+  theme(legend.position="none") + ggtitle(" ")
 
@@
 
-```{r fig:e1lexdiv, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=7, fig.height=3.0, fig.cap = "Mean lexical diversity scores by condition (left: Type/Token ratio, right: MTLD) in Experiment 1.
-Both measures of lexical diversity were significantly lower after watching an activity video.
+```{r fig-lexdiv, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=6.5, fig.height=5.5, fig.cap = "\\label{fig:lexdiv} Mean lexical diversity scores (left: Type/Token ratio, middle: MTLD) and mean number of tokens used by condition in Experiment 1 (top) and Experiment 2 (bottom).
 Error bars show bootstrapped 95\\% confidence intervals (CIs), and gray dots indicate values for each participant."}
 
-multiplot(e1ttr, e1mtld, e1tokens, cols=3)
+ttr2 <- e2data %>% group_by(Condition) %>%
+  tidyboot_mean(TTR)
+
+e2ttr <- ggplot(ttr2, aes(x=Condition, y=mean, fill=Condition)) + geom_bar(stat="identity") + # labels=addline_format(c("Science Video", "Activity Video"))
+  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
+  geom_point(data=e2data, aes(x=Condition, y=TTR), alpha=.2, position = position_jitterdodge()) +
+  xlab("Condition") + ylab("Type/Token Ratio (TTR)") +
+  langcog::scale_fill_solarized() + ggthemes::theme_few() +
+  theme(legend.position="none") + ggtitle("Experiment 2")
+
+mtld2 <- e2data %>% group_by(Condition) %>%
+  tidyboot_mean(MTLD)
+
+e2mtld <- ggplot(mtld2, aes(x = Condition, y = mean, fill = Condition)) + 
+  geom_bar(stat="identity") + 
+  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
+  geom_point(data=e2data, aes(x=Condition, y=MTLD), alpha=.2, position = position_jitterdodge()) +
+  xlab("Condition") + ylab("MTLD") +
+  langcog::scale_fill_solarized() + ggthemes::theme_few() +
+  theme(legend.position="none") + ggtitle(" ")
+
+e2tok <- e2data %>% group_by(Condition) %>%
+  tidyboot_mean(tokens)
+
+e2tokens <- ggplot(e2tok, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
+  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
+  geom_point(data=e2data, aes(x=Condition, y=tokens), alpha=.2, position = position_jitterdodge()) +
+  xlab("Condition") + ylab("Total Number of Word Tokens") +
+  langcog::scale_fill_solarized() + ggthemes::theme_few() +
+  theme(legend.position="none") + ggtitle(" ")
+
+#multiplot(e1ttr, e1mtld, e1tokens, cols=3) # Exp1 LD graph
+#multiplot(e2ttr, e2mtld, e2tokens, cols=3) # Exp2 LD graph
+
+multiplot(e1ttr, e1mtld, e1tokens, 
+          e2ttr, e2mtld, e2tokens, cols=3, layout=matrix(c(1,2,3, 4,5,6), nrow=2, byrow=T)) 
 ```
@@
 ```{r, e1ja-regressions, echo=F, include=F}
-load(paste(e1path,"joint_attention/Exp1_joint_attention_data.RData",sep=''))
-d$Condition <- factor(d$Condition, levels = c("con","exp"), labels = c("No Video","Activity Video"))
 
-e1ja <- d %>%
-  filter(!is.na(AA), !is.na(EL), !is.na(RR)) %>%
-  mutate(Condition = factor(Condition), 
-         bids_tot = as.numeric(bids_tot),
-         EL = as.numeric(langcog::scale(EL, scale=FALSE)),
-         AA = as.numeric(langcog::scale(AA, scale=FALSE)),
-         RR = as.numeric(langcog::scale(RR, scale=FALSE)),
-         age = as.numeric(langcog::scale(age, scale=FALSE)),
-         gender = as.factor(gender),
-         Video = as.factor(Video))
+model_string = "~ Condition * age + (1| Video)" # + gender + parent_ed
+# Total number of bids
+e1bids_mod <- stan_glmer(paste("bids_tot", model_string), data = e1ja) # 
+summary(e1bids_mod) # condition beta = 2.6, t(40.3) = 2.95 p<.01, gender p=.05 ?
+e1bids = get_stan_glmer_reporting_values(e1bids_mod, "ConditionActivity Video")
 
-# Mike says this should be the follow-up regression (if we find a sig effect?)
+e1bids_M <- e1ja %>% group_by(Condition) %>% 
+  summarise(mean = mean(bids), sd = sd(bids))
+
+e1tja_mod <- stan_lmer(paste("total_ja", model_string), data = e1ja)
+summary(e1tja_mod) # NA
+e1tjadur_mod <- stan_lmer(paste("total_lja", model_string), control = list(adapt_delta = 0.99), data = e1ja)
+summary(e1tjadur_mod) #
+
+# Episodes of passive joint attention.
+e1pja_mod <- stan_lmer(paste("pja", model_string), data = e1ja)
+summary(e1pja_mod) # NA
+# Episodes of coordinated joint attention.
+e1cja_mod <- stan_lmer(paste("cja", model_string), control = list(adapt_delta = 0.99), data = e1ja) 
+summary(e1cja_mod) # NA
+
+# Total duration of passive joint attention.
+e1pja_time_mod <- stan_lmer(paste("pja_length", model_string), data = e1ja)
+summary(e1pja_time_mod) # NA
+# Total duration of coordinated joint attention.
+e1cja_time_mod <- stan_lmer(paste("cja_length", model_string), data = e1ja)
+summary(e1cja_time_mod) # NA
+```
+
+```{r e1ja-epaq-regressions, include=F, echo=F}
+# follow-up regression (if we find a sig effect?)
 model_string =  "~ Condition * EL + Condition * AA + Condition * RR  + age + gender + parent_ed + (1| Video)"
@@
 For the regression predicting the number of passive JA episodes, the only significant effect was an interaction of condition and RR ($\beta=`r e1pja["ConditionActivity Video:RR"]`$, 95% CI=[`r e1pja['95pLB']`,`r e1pja['95pUB']`]), showing that for parents in the Video condition, those with higher Rules and Respect subscores engaged in more passive JA episodes.
-Figure \@ref(fig:e1ja) shows the mean number bids for JA and episodes of JA by condition in Experiment 1.
+Figure \@ref(fig:JA) (top) shows the mean number bids for JA and episodes of JA by condition in Experiment 1.
 
-```{r e1ja, fig.cap = "Mean number of bids (left) and episodes (right) of joint attention (JA) by condition in Experiment 1.
-Parents made significantly more bids for JA after watching an activity video, but this did not result in a greater number of episodes of JA."}
-# fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=5.5, fig.height=3.0, f
+```{r fig-JA, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=6.5, fig.height=5.5, fig.cap = "\\label{fig:JA} Mean number of bids (left) and episodes (right) of joint attention (JA) by condition in Experiment 1 (top).
+For Experiment 2 (bottom), mean number of bids for JA by condition (left) and the number of episodes of JA by age and condition (right)."}
+# Parents made significantly more bids for JA after watching an activity video, but this did not result in a greater number of episodes of JA.
 
-ms_bids1 <- d %>% group_by(Condition) %>%
+ms_bids1 <- e1ja %>% group_by(Condition) %>%
   tidyboot_mean(bids_tot)
@@
   langcog::scale_fill_solarized() + ggthemes::theme_few() + 
-  theme(legend.position="none")
-
+  theme(legend.position="none") + ggtitle("Experiment 1")
+ # theme(plot.title = element_text(size = 13, face = "bold"))
 # total joint attention episodes
-ms_tja1 <- d %>% group_by(Condition) %>%
+ms_tja1 <- e1ja %>% group_by(Condition) %>%
   tidyboot_mean(total_ja)
@@
   langcog::scale_fill_solarized() + ggthemes::theme_few() + 
-  theme(legend.position="none")
+  theme(legend.position="none") + ggtitle(" ")
 
-multiplot(e1bids, e1tja, cols=2)
+e2_cja <- e2ja %>% group_by(Condition) %>%
+  tidyboot_mean(cja)
+
+e2_bids <- e2ja %>% group_by(Condition) %>%
+  tidyboot_mean(bids)
+e2bids <- ggplot(e2_bids, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
+  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
+  geom_point(data=e2ja, aes(x=Condition, y=bids), alpha=.2, position = position_jitterdodge()) +
+  xlab("Condition") + ylab("Total Bids for Joint Attention") +
+  langcog::scale_fill_solarized() + ggthemes::theme_few() + 
+  theme(legend.position="none") + ggtitle("Experiment 2")
+
+# total JA episodes
+e2_tja <- e2ja %>% group_by(Condition) %>%
+  tidyboot_mean(total_ja) 
+e2tja <- ggplot(e2_tja, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
+  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
+  geom_point(data=e2ja, aes(x=Condition, y=total_ja), alpha=.2, position = position_jitterdodge()) +
+  xlab("Condition") + ylab("Total Episodes of Joint Attention") +
+  langcog::scale_fill_solarized() + ggthemes::theme_few() + 
+  theme(legend.position="none") + ggtitle(" ")
+
+e2tja_age = ggplot(e2ja, aes(x = Age, y = total_ja, group=Condition, colour = Condition)) +
+  geom_point(alpha=.7) + geom_smooth(method='lm') + 
+  xlab("Age (years)") + ylab("Total Episodes of Joint Attention") +
+  langcog::scale_colour_solarized() +
+  ggthemes::theme_few() + ggtitle(" ")
+
+# multiplot(e1bids, e1tja, cols=2) # old Exp1
+# multiplot(e2bids, e2tja_age, cols=5, layout=matrix(c(1,1,2,2,2), nrow=1))
+multiplot(e1bids, e1tja, e2bids, e2tja_age, 
+          cols=6, layout=matrix(c(1,1,1,2,2,2, 3,3,4,4,4,4), nrow=2, byrow=T)) 
 ```
@@
 In summary, while parents produced more word types and tokens after viewing the activity video, lexical diversity (both TTR and MTLD) was higher when parents were just asked to play as they normally would.
-It may be that parents in the Video condition, in their attempt to stick to the prescribed task, end up repeating themselves more.
-Demographics and EPAQ do not interact with condition, although there was a marginal effect of RR score on lexical diversity (lower diversity for higher RR scores), and marginal effects of parent education on word types and tokens (higher education yielding more types and tokens).
+It may be that parents in the Activity Video condition, in their attempt to stick to the prescribed task, end up repeating themselves more. 
+Looking at the most frequent content words parents used after the Activity Video, ...
+In contrast, the most frequent content words parents used in the Control condition were...
 
@@
 
-There was an interactive effect of RR scores and condition on passive JA, such that for parents with high RR scores, the activity video increased the number of episodes of passive JA to a greater extent than for parents in the no video condition.
+After the activity video, parents with higher RR scores showed an increased number of passive JA episodes than high-RR parents did after no video.
 While the electronically-delivered parenting advice increased the number of bids for JA by parents, it did not significantly affect the number or duration of episodes of JA. 
+RELATE BACK TO HYPOTHESES
 
@@
 Experiment 1 found that parents who watched an activity video spoke more words overall, but had lower lexical diversity compared to parents who played with their children as they normally would at home.
-Parents who watched an activity video also made more bids for joint attention, although these bids did not result in more episodes of joint attention compared to the control group. 
+Might it be that parents who are focused on a specific activity show reduced lexical diversity due to their focus on engaging their child in the activity?
+Parents who watched an activity video made more bids for joint attention, although these bids did not result in more episodes of joint attention compared to the control group. 
 Experiment 2 attempts to replicate these findings from with a restricted number of preregistered predictions.[^4]
@@
 ## Method
-
-```{r, echo=F}
-e2path = "../parenting_obs_e2/"
-load(paste(e2path,"Exp2_cleaned_data.RData",sep=''))
-
-e2data <- d %>%
-  mutate(condition = factor(condition), 
-         MTLD = as.numeric(MTLD),
-         TTR = as.numeric(TTR),
-         age = as.numeric(langcog::scale(age, scale=FALSE)),
-         video = as.factor(video))
-
-e2_gender = table(d$gender)
-e2_ethnicity = table(d$ethnicity)
-e2_parent_ed = table(d$parent_ed)
-e2_12to18 = nrow(subset(d, age<1.5))
-e2_18to24 = nrow(subset(d, age>=1.5))
-```
 
@@
 An exploratory mixed-effects linear regression predicting MTLD found no significant effects of age or condition.
-Figure \ref{fig:e2lexdiv} shows the mean of each lexical diversity measure (TTR and MTLD) by condition.
+Figure \ref{fig:lexdiv} (bottom left and middle) shows the mean of each lexical diversity measure (TTR and MTLD) by condition.
 Regressions with the same structure predicting the number of words tokens found no significant effects of age or condition.
@@
 ```{r e2tab, echo=F}
-e2data$Condition = factor(d$condition, levels = c("con", "exp"), labels = c("Science Video", "Activity Video"))
 e2 <- e2data %>% group_by(Condition) %>%
@@
 
-```{r fig:e2lexdiv, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=6.5, fig.height=3, fig.cap = "\\label{fig:e2lexdiv} Mean lexical diversity scores by condition (left: Type/Token ratio, middle: MTLD, right: word tokens) in Experiment 2."}
-
-ttr2 <- e2data %>% group_by(Condition) %>%
-  tidyboot_mean(TTR)
-
-e2ttr <- ggplot(ttr2, aes(x=Condition, y=mean, fill=Condition)) + geom_bar(stat="identity") + # labels=addline_format(c("Science Video", "Activity Video"))
-  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
-  geom_point(data=e2data, aes(x=Condition, y=TTR), alpha=.2, position = position_jitterdodge()) +
-  xlab("Condition") + ylab("TTR") +
-  langcog::scale_fill_solarized() + ggthemes::theme_few() +
-  theme(legend.position="none")
-
-mtld2 <- e2data %>% group_by(Condition) %>%
-  tidyboot_mean(MTLD)
-
-e2mtld <- ggplot(mtld2, aes(x = Condition, y = mean, fill = Condition)) + 
-  geom_bar(stat="identity") + 
-  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
-  geom_point(data=e2data, aes(x=Condition, y=MTLD), alpha=.2, position = position_jitterdodge()) +
-  xlab("Condition") + ylab("MTLD") +
-  langcog::scale_fill_solarized() + ggthemes::theme_few() +
-  theme(legend.position="none")
-
-e2tok <- e2data %>% group_by(Condition) %>%
-  tidyboot_mean(tokens)
-
-e2tokens <- ggplot(e2tok, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
-  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
-  geom_point(data=e2data, aes(x=Condition, y=tokens), alpha=.2, position = position_jitterdodge()) +
-  xlab("Condition") + ylab("Total Number of Word Tokens") +
-  langcog::scale_fill_solarized() + ggthemes::theme_few() +
-  theme(legend.position="none")
-
-multiplot(e2ttr, e2mtld, e2tokens, cols=3)
-```
-
 ```{r e2token-type, include=F}
-
+# NOT INCLUDED
 e2typ <- e2data %>% group_by(Condition) %>%
@@
 ```{r, e2-effect-size, echo=F, include=F}
-ttr_means <- d %>% group_by(Condition) %>%
+ttr_means <- e2data %>% group_by(Condition) %>%
   summarise(mean = mean(TTR), sd = sd(TTR))
@@
 ```{r, e2ja-regressions, echo=F, include=F}
-load(paste(e2path,"joint_attention/Exp2_joint_attention_data.RData",sep=''))
-summary(d)
-d$Condition <- factor(d$condition, levels = c("con","exp"), labels = c("Science Video","Activity Video"))
-
-e2ja <- d %>% mutate(bids = bids_tot,
-                     age = as.numeric(langcog::scale(age, scale=FALSE)),
-                     pja_length = pja_length/1000,
-                     cja_length = cja_length/1000,
-                     total_lja = total_lja/1000) # convert duration ms -> seconds
 
@@
 
-e2_bids <- e2ja %>% group_by(Condition) %>%
-  tidyboot_mean(bids)
-e2_tja <- e2ja %>% group_by(Condition) %>%
-  tidyboot_mean(total_ja)
-
 ```
@@
 As preregistered, we fit mixed-effects linear regressions predicting the number of parental bids for joint attention and the total number of episodes of JA as a function of fixed effects of condition, age (centered), and their interaction, with random intercepts per video.
-Shown in Figure \ref{fig:e2ja} (left panel), parents made significantly more bids for JA after watching the Activity Video (mean: `r round(subset(e2_bids, Condition=="Activity Video")$mean,2)`, bootstrapped 95% CI: `r round(subset(e2_bids, Condition=="Activity Video")$ci_lower,2)`, `r round(subset(e2_bids, Condition=="Activity Video")$ci_upper,2)`; $\beta=`r e2bids["ConditionActivity Video"]`$, 95% CI = [`r e2bids["95pLB"]`,`r e2bids["95pUB"]`]) than after the Science Video (mean: `r round(subset(e2_bids, Condition=="Science Video")$mean,2)`, 95% CI: [`r round(subset(e2_bids, Condition=="Science Video")$ci_lower,2)`, `r round(subset(e2_bids, Condition=="Science Video")$ci_upper,2)`]).
+Shown in Figure \ref{fig:JA} (left bottom), parents made significantly more bids for JA after watching the Activity Video (mean: `r round(subset(e2_bids, Condition=="Activity Video")$mean,2)`, bootstrapped 95% CI: `r round(subset(e2_bids, Condition=="Activity Video")$ci_lower,2)`, `r round(subset(e2_bids, Condition=="Activity Video")$ci_upper,2)`; $\beta=`r e2bids["ConditionActivity Video"]`$, 95% CI = [`r e2bids["95pLB"]`,`r e2bids["95pUB"]`]) than after the Science Video (mean: `r round(subset(e2_bids, Condition=="Science Video")$mean,2)`, 95% CI: [`r round(subset(e2_bids, Condition=="Science Video")$ci_lower,2)`, `r round(subset(e2_bids, Condition=="Science Video")$ci_upper,2)`]).
 There were no other significant effects on parental bids for JA.
@@
 There was also a significant main effect of age ($\beta=`r e2tjaAge["age"]`$, 95% CI = [`r e2tjaAge["95pLB"]`,`r e2tjaAge["95pUB"]`]), showing that the number of episodes of JA decreased with the child's age.
-However, a significant interaction of age and condition ($\beta=`r e2tjaAgeCond["age:ConditionActivity Video"]`$, 95% CI = [`r e2tjaAgeCond["95pLB"]`,`r e2tjaAgeCond["95pUB"]`]), shown in the right panel of Figure \ref{fig:e2ja}, demonstrates that older children in the Activity Video condition did not see a decrease in the number of episodes of JA.
-
-```{r fig:e2ja, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=6.5, fig.height=3.0, fig.cap = "\\label{fig:e2ja} Mean number of bids for JA by condition (left) and the number of episodes of JA by age and condition (right) in Experiment 2.
-After watching an activity video, parents made more bids for JA.
-Older children in the Activity Video condition showed no decrease in the number of episodes of JA, unlike children in the Control Video condition."}
-
-e2bids <- ggplot(e2_bids, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
-  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
-  geom_point(data=e2ja, aes(x=Condition, y=bids), alpha=.2, position = position_jitterdodge()) +
-  xlab("Condition") + ylab("Total Bids for Joint Attention") +
-  langcog::scale_fill_solarized() + ggthemes::theme_few() + 
-  theme(legend.position="none")
-
-# total JA episodes
-e2tja <- ggplot(e2_tja, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
-  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
-  geom_point(data=e2ja, aes(x=Condition, y=total_ja), alpha=.2, position = position_jitterdodge()) +
-  xlab("Condition") + ylab("Total Episodes of Joint Attention") +
-  langcog::scale_fill_solarized() + ggthemes::theme_few() + 
-  theme(legend.position="none")
-
-e2tja_age = ggplot(e2ja, aes(x = age, y = total_ja, group=Condition, colour = Condition)) +
-  geom_point(alpha=.7) + geom_smooth(method='lm') + 
-  xlab("Age (years)") + ylab("Total Episodes of Joint Attention") +
-  langcog::scale_colour_solarized() +
-  ggthemes::theme_few()
-
-multiplot(e2bids, e2tja_age, cols=5, layout=matrix(c(1,1,2,2,2), nrow=1))
-```
+However, a significant interaction of age and condition ($\beta=`r e2tjaAgeCond["age:ConditionActivity Video"]`$, 95% CI = [`r e2tjaAgeCond["95pLB"]`,`r e2tjaAgeCond["95pUB"]`]), shown in Figure \ref{fig:JA} (right bottom), demonstrates that older children in the Activity Video condition did not see a decrease in the number of episodes of JA.
 
@@
 summary(e2cjat_m) # age: est: 35.3 95% CI = [-6.1,77.4] ns
-
-e2_cja <- e2ja %>% group_by(Condition) %>%
-  tidyboot_mean(cja)
 
@@
 ```
+
+```{r echo = FALSE, results = 'asis'}
+render_appendix('appendix.Rmd')
+```

### 2019-09-17 paper/manuscript.tex
combined Exp 1 and Exp 2 figures

@@
 A similar Bayesian mixed-effects linear regression instead predicting MTLD also found significantly lower lexical diversity in the Video condition (mean MTLD: 17.87) than in the Control condition (mean: 27.09, \(\beta=\)-8.62, 95\% CI={[}-15.15,-2.01{]}), with no other significant effects.
-Figure \ref{fig:e1lexdiv} shows the mean of each lexical diversity measure (TTR and MTLD) by condition.
+Figure \ref{fig:lexdiv} shows the mean of each lexical diversity measure (TTR and MTLD) by condition.
 
@@
 
-{\centering \includegraphics{figs/fig:e1lexdiv-1}
+{\centering \includegraphics{figs/fig-lexdiv-1}
 
@@
 
-\caption{Mean lexical diversity scores by condition (left: Type/Token ratio, right: MTLD) in Experiment 1.
-Both measures of lexical diversity were significantly lower after watching an activity video.
-Error bars show bootstrapped 95\% confidence intervals (CIs), and gray dots indicate values for each participant.}(\#fig:fig:e1lexdiv)
+\caption{\label{fig:lexdiv} Mean lexical diversity scores (left: Type/Token ratio, middle: MTLD) and mean number of tokens used by condition in Experiment 1 (top) and Experiment 2 (bottom).
+Error bars show bootstrapped 95\% confidence intervals (CIs), and gray dots indicate values for each participant.}\label{fig:fig-lexdiv}
 \end{figure}
@@
 This lme4 model included random intercepts per video.
-There were significantly more bids for JA in the Video condition (mean: 6.24, sd: 2.79) than in the Control condition (mean: 3.56, sd: 2.50, \(\beta=3.44\), 95\% CI={[}1.12,5.80{]}).
+There were significantly more bids for JA in the Video condition (mean: 6.30, sd: 2.76) than in the Control condition (mean: 3.73, sd: 2.74, \(\beta=3.40\), 95\% CI={[}1.03,5.73{]}).
 
@@
 There were no significant effects on the number or total duration of coordinated JA episodes, nor on the total duration of passive JA episodes.
-For the regression predicting the number of passive JA episodes, the only significant effect was an interaction of condition and RR (\(\beta=1.84\), 95\% CI={[}0.23,3.44{]}), showing that for parents in the Video condition, those with higher Rules and Respect subscores engaged in more passive JA episodes.
-Figure \ref{fig:e1ja} shows the mean number bids for JA and episodes of JA by condition in Experiment 1.
+For the regression predicting the number of passive JA episodes, the only significant effect was an interaction of condition and RR (\(\beta=1.82\), 95\% CI={[}0.20,3.48{]}), showing that for parents in the Video condition, those with higher Rules and Respect subscores engaged in more passive JA episodes.
+Figure \ref{fig:JA} (top) shows the mean number bids for JA and episodes of JA by condition in Experiment 1.
 
-\begin{figure}
-\centering
-\includegraphics{figs/e1ja-1.pdf}
-\caption{\label{fig:e1ja}Mean number of bids (left) and episodes (right) of joint attention (JA) by condition in Experiment 1.
-Parents made significantly more bids for JA after watching an activity video, but this did not result in a greater number of episodes of JA.}
+\begin{figure}[H]
+
+{\centering \includegraphics{figs/fig-JA-1}
+
+}
+
+\caption{\label{fig:JA} Mean number of bids (left) and episodes (right) of joint attention (JA) by condition in Experiment 1 (top).
+For Experiment 2 (bottom), mean number of bids for JA by condition (left) and the number of episodes of JA by age and condition (right).}\label{fig:fig-JA}
 \end{figure}
@@
 In summary, while parents produced more word types and tokens after viewing the activity video, lexical diversity (both TTR and MTLD) was higher when parents were just asked to play as they normally would.
-It may be that parents in the Video condition, in their attempt to stick to the prescribed task, end up repeating themselves more.
-Demographics and EPAQ do not interact with condition, although there was a marginal effect of RR score on lexical diversity (lower diversity for higher RR scores), and marginal effects of parent education on word types and tokens (higher education yielding more types and tokens).
+It may be that parents in the Activity Video condition, in their attempt to stick to the prescribed task, end up repeating themselves more.
+Looking at the most frequent content words parents used after the Activity Video, \ldots{}
+In contrast, the most frequent content words parents used in the Control condition were\ldots{}
 
@@
 
-There was an interactive effect of RR scores and condition on passive JA, such that for parents with high RR scores, the activity video increased the number of episodes of passive JA to a greater extent than for parents in the no video condition.
+After the activity video, parents with higher RR scores showed an increased number of passive JA episodes than high-RR parents did after no video.
 While the electronically-delivered parenting advice increased the number of bids for JA by parents, it did not significantly affect the number or duration of episodes of JA.
+RELATE BACK TO HYPOTHESES
 
@@
 Experiment 1 found that parents who watched an activity video spoke more words overall, but had lower lexical diversity compared to parents who played with their children as they normally would at home.
-Parents who watched an activity video also made more bids for joint attention, although these bids did not result in more episodes of joint attention compared to the control group.
+Might it be that parents who are focused on a specific activity show reduced lexical diversity due to their focus on engaging their child in the activity?
+Parents who watched an activity video made more bids for joint attention, although these bids did not result in more episodes of joint attention compared to the control group.
 Experiment 2 attempts to replicate these findings from with a restricted number of preregistered predictions.\footnote{Preregistration: \url{https://osf.io/2bpdf/}.}
@@
 
-\begin{figure}[H]
-
-{\centering \includegraphics{figs/fig:e2lexdiv-1}
-
-}
-
-\caption{\label{fig:e2lexdiv} Mean lexical diversity scores by condition (left: Type/Token ratio, middle: MTLD, right: word tokens) in Experiment 2.}(\#fig:fig:e2lexdiv)
-\end{figure}
-
 \hypertarget{joint-attention-1}{%
@@
 As preregistered, we fit mixed-effects linear regressions predicting the number of parental bids for joint attention and the total number of episodes of JA as a function of fixed effects of condition, age (centered), and their interaction, with random intercepts per video.
-Shown in Figure \ref{fig:e2ja} (left panel), parents made significantly more bids for JA after watching the Activity Video (mean: 12.96, bootstrapped 95\% CI: 11.74, 14.21; \(\beta=3.06\), 95\% CI = {[}0.96,5.06{]}) than after the Science Video (mean: 9.88, 95\% CI: {[}8.71, 11.07{]}).
+Shown in Figure \ref{fig:JA} (left bottom), parents made significantly more bids for JA after watching the Activity Video (mean: 12.96, bootstrapped 95\% CI: 11.79, 14.24; \(\beta=3.07\), 95\% CI = {[}1.15,5.06{]}) than after the Science Video (mean: 9.89, 95\% CI: {[}8.73, 11.10{]}).
 There were no other significant effects on parental bids for JA.
 
-In the regression predicting the number of episodes of JA, there was a significant main effect of condition (\(\beta=1.49\), 95\% CI = {[}0.26,2.78{]}), with more episodes of JA occurring after the Activity Video (mean: 8.79, 95\% CI: {[}7.95, 9.67{]}) than after the Control Video (mean: 7.33, 95\% CI: {[}6.54, 8.05{]}).
-There was also a significant main effect of age (\(\beta=-5.02\), 95\% CI = {[}-8.23,-1.41{]}), showing that the number of episodes of JA decreased with the child's age.
-However, a significant interaction of age and condition (\(\beta=5.67\), 95\% CI = {[}0.50,10.71{]}), shown in the right panel of Figure \ref{fig:e2ja}, demonstrates that older children in the Activity Video condition did not see a decrease in the number of episodes of JA.
-
-\begin{figure}[H]
-
-{\centering \includegraphics{figs/fig:e2ja-1}
-
-}
-
-\caption{\label{fig:e2ja} Mean number of bids for JA by condition (left) and the number of episodes of JA by age and condition (right) in Experiment 2.
-After watching an activity video, parents made more bids for JA.
-Older children in the Activity Video condition showed no decrease in the number of episodes of JA, unlike children in the Control Video condition.}(\#fig:fig:e2ja)
-\end{figure}
+In the regression predicting the number of episodes of JA, there was a significant main effect of condition (\(\beta=1.48\), 95\% CI = {[}0.15,2.78{]}), with more episodes of JA occurring after the Activity Video (mean: 8.80, 95\% CI: {[}7.97, 9.63{]}) than after the Control Video (mean: 7.33, 95\% CI: {[}6.58, 8.11{]}).
+There was also a significant main effect of age (\(\beta=-5\), 95\% CI = {[}-8.27,-1.41{]}), showing that the number of episodes of JA decreased with the child's age.
+However, a significant interaction of age and condition (\(\beta=5.60\), 95\% CI = {[}0.46,10.37{]}), shown in Figure \ref{fig:JA} (right bottom), demonstrates that older children in the Activity Video condition did not see a decrease in the number of episodes of JA.
 
@@
 Four additional exploratory regressions with a similar structure were carried out to predict the number and duration of coordinated and passive JA episodes.
-The regression predicting the number of episodes of coordinated JA found a significant main effect of condition (\(\beta=1.36\), 95\% CI = {[}0.16,2.58{]}), with more episodes of coordinated JA occurring after the Activity Video (mean: 6.71, 95\% CI: {[}5.90, 7.56{]}) than after the Control Video (mean: 5.34, 95\% CI: {[}4.68, 6.02{]}).
-There was no significant effect of age, but there was a significant interaction of age and condition (\(\beta=5.34\), 95\% CI = {[}0.80,10.22{]}), shown in Figure \ref{fig:e2ja-coord}, revealing that older children in the Activity Video condition had more episodes of coordinated JA than children in the Control Video condition.
+The regression predicting the number of episodes of coordinated JA found a significant main effect of condition (\(\beta=1.35\), 95\% CI = {[}0.17,2.61{]}), with more episodes of coordinated JA occurring after the Activity Video (mean: 6.72, 95\% CI: {[}5.91, 7.56{]}) than after the Control Video (mean: 5.33, 95\% CI: {[}4.70, 5.97{]}).
+There was no significant effect of age, but there was a significant interaction of age and condition (\(\beta=5.28\), 95\% CI = {[}0.52,10.02{]}), shown in Figure \ref{fig:e2ja-coord}, revealing that older children in the Activity Video condition had more episodes of coordinated JA than children in the Control Video condition.
 The regression predicting the total duration of coordinated JA episodes revealed no significant effects.
 
-In the regression predicting the number of episodes of passive JA, there was a main effect of age (\(\beta=-2.72\), 95\% CI = {[}-5.07,0.19{]}), showing that older children had more episodes of passive JA with their caregiver.
-The regression predicting the total duration of passive JA revealed a main effect of age (\(\beta=-17.70\), 95\% CI = {[}-32.73,-1.79{]}), revealing that older children spent more time in passive JA with their caregiver.
+In the regression predicting the number of episodes of passive JA, there was a main effect of age (\(\beta=-2.70\), 95\% CI = {[}-5.07,0.08{]}), showing that older children had more episodes of passive JA with their caregiver.
+The regression predicting the total duration of passive JA revealed a main effect of age (\(\beta=-18.32\), 95\% CI = {[}-33.50,-2.91{]}), revealing that older children spent more time in passive JA with their caregiver.
 Overall, these results show that the older children in our sample engage in more and longer episodes of joint attention with their caregivers, and suggest that the Activity Video strengthened this trend in the number of episodes of coordinated JA.
@@
 \section{}
-\hypertarget{experiment-1}{%
-\subsection{Experiment 1}\label{experiment-1}}
+\hypertarget{experiment-1-activities}{%
+\subsection{Experiment 1 Activities}\label{experiment-1-activities}}
 
@@
 
-\hypertarget{experiment-2}{%
-\subsection{Experiment 2}\label{experiment-2}}
+\hypertarget{experiment-2-activities}{%
+\subsection{Experiment 2 Activities}\label{experiment-2-activities}}
 

### 2019-09-17 paper/extra_text.R

@@ -57,3 +57,7 @@ Thus, new methods of delivering parenting advice should be considered.
 But does providing such information change parents' behavior towards young children? 
 And is this advice effective in producing change along the desired dimension? 
 An alternative might be that asking parents to focus on a specific activity that may be novel to them may tax their cognitive resources, resulting in decreases in the quality of their child-directed speech, or in less flexible, lower-quality social interactions.
+
+
+Exp 1 Discussion
+Demographics and EPAQ do not interact with condition, although there was a marginal effect of RR score on lexical diversity (lower diversity for higher RR scores), and marginal effects of parent education on word types and tokens (higher education yielding more types and tokens).

### 2019-09-17 paper/manuscript.Rmd
tweaked combined plots

@@
 
-```{r hiddenfigs, include=F}
+```{r e1ld-figs, include=F}
+small_text = theme(
+  plot.title = element_text(size = 12, face="bold"),
+  axis.title.x = element_text(size = 10),
+  axis.text.x = element_text(size = 8),
+  axis.title.y = element_text(size = 10),
+  axis.text.y = element_text(size = 8))
+
 e1ttr <- ggplot(e1_lex, aes(x=Condition, y=mean, fill=Condition)) + geom_bar(stat="identity") + 
@@
   langcog::scale_fill_solarized() + ggthemes::theme_few() +
-  theme(legend.position="none") + ggtitle("Experiment 1")
+  theme(legend.position="none") + ggtitle("Experiment 1") + small_text
+# want carriage return in Condition labels..
 
@@
   langcog::scale_fill_solarized() + ggthemes::theme_few() + 
-  theme(legend.position="none") + ggtitle(" ")
+  theme(legend.position="none") + ggtitle(" ") + small_text
 
@@
   langcog::scale_fill_solarized() + ggthemes::theme_few() +
-  theme(legend.position="none") + ggtitle(" ")
+  theme(legend.position="none") + ggtitle(" ") + small_text
 
@@
 
-```{r fig-lexdiv, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=6.5, fig.height=5.5, fig.cap = "\\label{fig:lexdiv} Mean lexical diversity scores (left: Type/Token ratio, middle: MTLD) and mean number of tokens used by condition in Experiment 1 (top) and Experiment 2 (bottom).
+```{r fig-lexdiv, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=6.5, fig.height=5.5, fig.cap = "\\label{fig:lexdiv} Mean lexical diversity scores (left: Type/Token ratio, middle: MTLD) and mean number of tokens used by condition (right) in Experiment 1 (top) and Experiment 2 (bottom).
 Error bars show bootstrapped 95\\% confidence intervals (CIs), and gray dots indicate values for each participant."}
@@
   langcog::scale_fill_solarized() + ggthemes::theme_few() +
-  theme(legend.position="none") + ggtitle("Experiment 2")
+  theme(legend.position="none") + ggtitle("Experiment 2") + small_text
 
@@
 We fit a mixed-effects linear regression predicting the number of bids for joint attention (JA) as a function of fixed effects of condition, age (centered), gender, parent's education level, and the subscales of the EPAQ: Early Learning (EL), Affection and Attachment (AA), and Rules and Respect (RR), along with interactions of condition and EL, AA, and RR.
-This lme4 model included random intercepts per video. 
+This model included random intercepts per video. 
 There were significantly more bids for JA in the Video condition (mean: `r round(subset(e1bids_M, Condition=="Activity Video")$mean,2)`, sd: `r round(subset(e1bids_M, Condition=="Activity Video")$sd,2)`) than in the Control condition (mean: `r round(subset(e1bids_M, Condition=="No Video")$mean,2)`, sd: `r round(subset(e1bids_M, Condition=="No Video")$sd,2)`, $\beta=`r e1bids["ConditionActivity Video"]`$, 95% CI=[`r e1bids['95pLB']`,`r e1bids['95pUB']`]).
@@
   langcog::scale_fill_solarized() + ggthemes::theme_few() + 
-  theme(legend.position="none") + ggtitle("Experiment 1")
- # theme(plot.title = element_text(size = 13, face = "bold"))
+  theme(legend.position="none") + ggtitle("Experiment 1") + small_text
+
 # total joint attention episodes
@@
 
+library("scales")
+#show_col(solarized_pal()(2)) # blue, red
+sol_colors = solarized_pal()(2)
+
 e2_bids <- e2ja %>% group_by(Condition) %>%
   tidyboot_mean(bids)
-e2bids <- ggplot(e2_bids, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
+e2bids <- ggplot(e2_bids, aes(x = Condition, y = mean, fill = str_wrap(Condition, 8))) + geom_bar(stat="identity") + 
   geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
+  labs(fill="Condition") + 
   geom_point(data=e2ja, aes(x=Condition, y=bids), alpha=.2, position = position_jitterdodge()) +
   xlab("Condition") + ylab("Total Bids for Joint Attention") + 
-  langcog::scale_fill_solarized() + ggthemes::theme_few() + 
-  theme(legend.position="none") + ggtitle("Experiment 2")
+  scale_fill_manual(values=sol_colors) + ggthemes::theme_few() + ggtitle("Experiment 2") + small_text +
+  theme(legend.key.height=unit(1.2, "cm"), legend.text=element_text(size=9))
 
-# total JA episodes
+# total JA episodes (not currently graphed)
 e2_tja <- e2ja %>% group_by(Condition) %>%
@@
   langcog::scale_fill_solarized() + ggthemes::theme_few() + 
-  theme(legend.position="none") + ggtitle(" ")
+  ggtitle(" ") + small_text + theme(legend.position="none")
 
-e2tja_age = ggplot(e2ja, aes(x = Age, y = total_ja, group=Condition, colour = Condition)) +
-  geom_point(alpha=.7) + geom_smooth(method='lm') + 
+e2tja_age = ggplot(e2ja, aes(x = Age, y = total_ja, group=Condition, colour=Condition)) +
+  geom_point(alpha=.8) + geom_smooth(method='lm') + scale_colour_manual(values=rev(sol_colors)) +
   xlab("Age (years)") + ylab("Total Episodes of Joint Attention") +
-  langcog::scale_colour_solarized() +
-  ggthemes::theme_few() + ggtitle(" ")
+  ggthemes::theme_few() + ggtitle(" ") + small_text + theme(legend.position="none")
 
@@
 multiplot(e1bids, e1tja, e2bids, e2tja_age, 
-          cols=6, layout=matrix(c(1,1,1,2,2,2, 3,3,4,4,4,4), nrow=2, byrow=T)) 
+          cols=6, layout=matrix(c(1,1,1,2,2,2, 3,3,3,4,4,4), nrow=2, byrow=T)) 
 ```

### 2019-09-17 paper/manuscript.tex
tweaked combined plots

@@
 
-\caption{\label{fig:lexdiv} Mean lexical diversity scores (left: Type/Token ratio, middle: MTLD) and mean number of tokens used by condition in Experiment 1 (top) and Experiment 2 (bottom).
+\caption{\label{fig:lexdiv} Mean lexical diversity scores (left: Type/Token ratio, middle: MTLD) and mean number of tokens used by condition (right) in Experiment 1 (top) and Experiment 2 (bottom).
 Error bars show bootstrapped 95\% confidence intervals (CIs), and gray dots indicate values for each participant.}\label{fig:fig-lexdiv}
@@
 We fit a mixed-effects linear regression predicting the number of bids for joint attention (JA) as a function of fixed effects of condition, age (centered), gender, parent's education level, and the subscales of the EPAQ: Early Learning (EL), Affection and Attachment (AA), and Rules and Respect (RR), along with interactions of condition and EL, AA, and RR.
-This lme4 model included random intercepts per video.
+This model included random intercepts per video.
 There were significantly more bids for JA in the Video condition (mean: 6.30, sd: 2.76) than in the Control condition (mean: 3.73, sd: 2.74, \(\beta=3.40\), 95\% CI={[}1.03,5.73{]}).

### 2019-09-24 paper/manuscript.Rmd
updated Exp 1 exploratory regressions

@@
 In Experiment 1, we invited parents of 6- to 24-month-old infants visiting the Children's Discovery Museum in San Jose to complete video-guided activities from a commerical parenting app that delivers digital parenting advice in the form of short videos.
-Parents were randomly assigned to the video condition or the control condition; parents in the _activity video_ condition watched a video from the app (matched to their child's age), and then performed the activity with their child using the props from the video.
-Parents in the _control_ condition did not watch an activity video, but were given a set of the same age-appropriate props and asked to play with their infants as they normally would at home.
+Parents were randomly assigned to one of two conditions: parents in the _Activity Video_ condition watched a video from the app (matched to their child's age), and then performed the activity with their child using the props from the video.
+Parents in the _No Video_ condition did not watch an activity video, but were given a set of the same age-appropriate props and asked to play with their infants as they normally would at home.
 
@@
 The toys were placed on a large foam play mat, and parents were instructed to sit on the mat with their child and re-create the activity they had viewed for a period of three minutes.[^2]
-In the Control condition, after informed consent parents were told to play with their child as they would at home with the provided props for a period of three minutes. 
+In the No Video condition, after informed consent parents were told to play with their child as they would at home with the provided props for a period of three minutes. 
 They were not given any additional instructions about how to use the props.
@@
 Parents' child-directed speech during the play sessions was transcribed.
-The transcripts and hand-coded joint attention data were analyzed according to our preregistration[^3], with any deviations or extensions noted.
+The transcripts and hand-coded joint attention data were analyzed according to our preregistration[^3], with any deviations or exploratory analyses noted.
 Below we first report the lexical diversity results, followed by the joint attention results.
@@
 
-# Predicting lexical diversity based on experimental condition, PAQ, demographics. 
-modTTR <- stan_glmer(TTR ~ condition + age + gender + parent_ed + (1|video), data=e1ld)
-summary(modTTR) # condition:Exp -0.113 t(52.4) = 4.22 p<.001
-e1TTR = get_stan_glmer_reporting_values(modTTR, "conditionexp") #
+modTTR <- stan_glmer(TTR ~ condition * age + (1|video), data=e1ld)
+summary(modTTR) 
+e1TTR = get_stan_glmer_reporting_values(modTTR, "conditionexp") # -.11
 
-modMTLD <- stan_glmer(MTLD ~ condition + age + gender + parent_ed + (1|video), data=e1ld)
-summary(modMTLD) # condition -8.73 t(55) = 2.67 p=.001 !! singular fit, changing optimizer did not help
-e1MTLD = get_stan_glmer_reporting_values(modMTLD, "conditionexp") #
+modMTLD <- stan_glmer(MTLD ~ condition * age + (1|video), data=e1ld)
+summary(modMTLD) 
+e1MTLD = get_stan_glmer_reporting_values(modMTLD, "conditionexp") # -9.19
 
 # predict word tokens
-tokens_mod <- stan_glmer(tokens ~ condition + age + gender + parent_ed + (1|video),  data=e1ld) 
+tokens_mod <- stan_glmer(tokens ~ condition * age + (1|video), control = list(adapt_delta = 0.99), data=e1ld) 
 summary(tokens_mod)
-get_stan_glmer_reporting_values(tokens_mod, "conditionexp") # 55.7
-
-# follow-up on EPAQ
-tokens_modEPAQ <- stan_glmer(tokens ~ condition*EL + condition*AA + condition*RR + age + gender + parent_ed + (1|video),  data=e1ld) # only 54 parents completed the EPAQ
-summary(tokens_modEPAQ) # condition 56.02 t(40.4) = 2.30 p<.05
-e1tokens = get_stan_glmer_reporting_values(tokens_mod, "conditionexp") # 54.8
+e1tokens = get_stan_glmer_reporting_values(tokens_mod, "conditionexp") # 59.41
 
 # predict word types
-types_mod <- stan_glmer(types ~ condition*EL + condition*AA + condition*RR  + age + gender + parent_ed + (1|video), data=e1ld) 
+types_mod <- stan_glmer(types ~ condition * age + (1|video), control = list(adapt_delta = 0.99), data=e1ld)
 summary(types_mod) # nothing
@@
 
-We fit a Bayesian mixed-effects linear regression predicting TTR as a function of condition, age (centered), gender, and parent's education level with a random intercept per video using rstanarm [@rstanarm].
+```{r, e1ld-exploratory, echo=F, include=F}
+# Predicting lexical diversity based on experimental condition, PAQ, demographics. 
+e1model_string = "~ condition*EL + condition*AA + condition*RR  + age + gender + parent_ed + (1|video)"
+# only 54 parents completed the EPAQ
+modTTRE <- stan_glmer(paste("TTR", e1model_string), data=e1ld)
+summary(modTTRE) #
+
+modMTLDE <- stan_glmer(paste("MTLD", e1model_string), data=e1ld)
+summary(modMTLDE) #
+
+tokens_modE <- stan_glmer(paste("tokens", e1model_string),  data=e1ld) 
+summary(tokens_modE) # condition 54.4
+
+# predict word types
+types_modE <- stan_glmer(paste("types", e1model_string), data=e1ld) 
+summary(types_modE) # 
+```
+
+We fit a Bayesian mixed-effects linear regression predicting TTR as a function of condition, age (centered), and their interaction with a random intercept per video using rstanarm [@rstanarm]. 
 For effects that are at least 95% likely to be non-zero according to the posterior distribution, we report estimated coefficients ($\beta$) as well as 95% Bayesian credible intervals (95% CI), demarcating the range within which 95% of the posterior predictive values fall.
-There was significantly lower TTR in the Video condition (mean: `r round(subset(e1_lexdiv, condition=='exp')$TTR, 2)`) than in the Control condition (mean: `r round(subset(e1_lexdiv, condition=='con')$TTR, 2)`, $\beta=$`r e1TTR["conditionexp"]`, 95% CI=[`r e1TTR['95pLB']`,`r e1TTR['95pUB']`]).
+There was significantly lower TTR in the Video condition (mean: `r round(subset(e1_lexdiv, condition=='exp')$TTR, 2)`) than in the No Video condition (mean: `r round(subset(e1_lexdiv, condition=='con')$TTR, 2)`, $\beta=$`r e1TTR["conditionexp"]`, 95% CI=[`r e1TTR['95pLB']`,`r e1TTR['95pUB']`]).
 There were no significant effects of age, gender, or parent's level of education.
-A similar Bayesian mixed-effects linear regression instead predicting MTLD also found significantly lower lexical diversity in the Video condition (mean MTLD: `r round(subset(e1_lexdiv, condition=='exp')$MTLD, 2)`) than in the Control condition (mean: `r round(subset(e1_lexdiv, condition=='con')$MTLD, 2)`, $\beta=$`r e1MTLD["conditionexp"]`, 95% CI=[`r e1MTLD['95pLB']`,`r e1MTLD['95pUB']`]), with no other significant effects.
+A similar Bayesian mixed-effects linear regression instead predicting MTLD also found significantly lower lexical diversity in the Activity Video condition (mean MTLD: `r round(subset(e1_lexdiv, condition=='exp')$MTLD, 2)`) than in the No Video condition (mean: `r round(subset(e1_lexdiv, condition=='con')$MTLD, 2)`, $\beta=$`r e1MTLD["conditionexp"]`, 95% CI=[`r e1MTLD['95pLB']`,`r e1MTLD['95pUB']`]), with no other significant effects.
 Figure \ref{fig:lexdiv} shows the mean of each lexical diversity measure (TTR and MTLD) by condition.
@@
 
-We also conducted similar regressions predicting the number of word tokens and types, finding only a significant effect of condition on the number of word tokens ($\beta=$ `r e1tokens["conditionexp"]`, 95% CI=[`r e1tokens['95pLB']`,`r e1tokens['95pUB']`])), with parents using more words in the Video condition (mean: `r round(subset(e1_lexdiv, condition=='exp')$tokens, 0)`, bootstrapped 95% confidence intervals (CI): [`r round(subset(e1_tok, Condition=="Activity Video")$ci_lower, 0)`,`r round(subset(e1_tok, Condition=="Activity Video")$ci_upper, 0)`]) than in the Control condition (mean: `r round(subset(e1_lexdiv, condition=='con')$tokens, 0)`, bootstrapped 95% CI: [`r round(subset(e1_tok, Condition=="No Video")$ci_lower, 0)`,`r round(subset(e1_tok, Condition=="No Video")$ci_upper, 0)`]).
+We also conducted similar regressions predicting the number of word tokens and types, finding only a significant effect of condition on the number of word tokens ($\beta=$ `r e1tokens["conditionexp"]`, 95% CI=[`r e1tokens['95pLB']`,`r e1tokens['95pUB']`])), with parents using more words in the Activity Video condition (mean: `r round(subset(e1_lexdiv, condition=='exp')$tokens, 0)`, bootstrapped 95% confidence intervals (CI): [`r round(subset(e1_tok, Condition=="Activity Video")$ci_lower, 0)`,`r round(subset(e1_tok, Condition=="Activity Video")$ci_upper, 0)`]) than in the No Video condition (mean: `r round(subset(e1_lexdiv, condition=='con')$tokens, 0)`, bootstrapped 95% CI: [`r round(subset(e1_tok, Condition=="No Video")$ci_lower, 0)`,`r round(subset(e1_tok, Condition=="No Video")$ci_upper, 0)`]).
 
@@
 e1bids_mod <- stan_glmer(paste("bids_tot", model_string), data = e1ja) # 
-summary(e1bids_mod) # condition beta = 2.6, t(40.3) = 2.95 p<.01, gender p=.05 ?
-e1bids = get_stan_glmer_reporting_values(e1bids_mod, "ConditionActivity Video")
+summary(e1bids_mod) 
+e1bids = get_stan_glmer_reporting_values(e1bids_mod, "ConditionActivity Video") # 2.59
 
@@
 summary(e1tja_mod) # NA
+
 e1tjadur_mod <- stan_lmer(paste("total_lja", model_string), control = list(adapt_delta = 0.99), data = e1ja)
-summary(e1tjadur_mod) #
+summary(e1tjadur_mod) # NA
 
@@
 summary(e1pja_mod) # NA
+
 # Episodes of coordinated joint attention.
@@
 summary(e1cja_mod) # NA
-
-# Total duration of passive joint attention.
-e1pja_time_mod <- stan_lmer(paste("pja_length", model_string), data = e1ja)
-summary(e1pja_time_mod) # NA
-# Total duration of coordinated joint attention.
-e1cja_time_mod <- stan_lmer(paste("cja_length", model_string), data = e1ja)
-summary(e1cja_time_mod) # NA
-```
-
-```{r e1ja-epaq-regressions, include=F, echo=F}
-# follow-up regression (if we find a sig effect?)
-model_string =  "~ Condition * EL + Condition * AA + Condition * RR  + age + gender + parent_ed + (1| Video)"
-
-# Total number of bids
-e1bids_mod <- stan_glmer(paste("bids_tot", model_string), data = e1ja) # 1 divergent transitions after warmup. Increasing adapt_delta above 0.95 may help
-summary(e1bids_mod) # condition beta = 3.51, t(40.3) = 2.95 p<.01, gender p=.05 ?
-e1bids = get_stan_glmer_reporting_values(e1bids_mod, "ConditionActivity Video")
-
-e1bids_M <- e1ja %>% group_by(Condition) %>% 
-  summarise(mean = mean(bids), sd = sd(bids))
-
-# Episodes of coordinated joint attention.
-e1cja_mod <- stan_lmer(paste("cja", model_string), data = e1ja)
-summary(e1cja_mod) # NA
-
-# Episodes of passive joint attention.
-e1pja_mod <- stan_lmer(paste("pja", model_string), data = e1ja)
-summary(e1pja_mod) # condition*RR beta=1.8 Bayes 95% Ci = [.1,3.5]
-e1pja = get_stan_glmer_reporting_values(e1pja_mod, "ConditionActivity Video:RR")
 
@@
 
-We fit a mixed-effects linear regression predicting the number of bids for joint attention (JA) as a function of fixed effects of condition, age (centered), gender, parent's education level, and the subscales of the EPAQ: Early Learning (EL), Affection and Attachment (AA), and Rules and Respect (RR), along with interactions of condition and EL, AA, and RR.
-This model included random intercepts per video. 
-There were significantly more bids for JA in the Video condition (mean: `r round(subset(e1bids_M, Condition=="Activity Video")$mean,2)`, sd: `r round(subset(e1bids_M, Condition=="Activity Video")$sd,2)`) than in the Control condition (mean: `r round(subset(e1bids_M, Condition=="No Video")$mean,2)`, sd: `r round(subset(e1bids_M, Condition=="No Video")$sd,2)`, $\beta=`r e1bids["ConditionActivity Video"]`$, 95% CI=[`r e1bids['95pLB']`,`r e1bids['95pUB']`]).
+```{r e1ja-epaq-regressions, include=F, echo=F}
+# follow-up regression (if we find a sig effect?)
+model_stringE =  "~ Condition * EL + Condition * AA + Condition * RR  + age + gender + parent_ed + (1| Video)"
 
+# Total number of bids
+e1bids_modE <- stan_glmer(paste("bids_tot", model_stringE), data = e1ja) 
+summary(e1bids_modE) # cond, gender close
+
+# Episodes of coordinated joint attention.
+e1cja_modE <- stan_lmer(paste("cja", model_stringE), data = e1ja)
+summary(e1cja_modE) # NA
+
+# Episodes of passive joint attention.
+e1pja_modE <- stan_lmer(paste("pja", model_stringE), data = e1ja)
+summary(e1pja_modE) # condition*RR beta=1.8, RR close
+get_stan_glmer_reporting_values(e1pja_modE, "RR") # -1.08, 95% CI = [-2.18,0.07]
+e1pjaE = get_stan_glmer_reporting_values(e1pja_modE, "ConditionActivity Video:RR")
+
+# Total duration of passive joint attention.
+e1pja_time_modE <- stan_lmer(paste("pja_length", model_stringE), data = e1ja)
+summary(e1pja_time_modE) # NA
+
+# Total duration of coordinated joint attention.
+e1cja_time_modE <- stan_lmer(paste("cja_length", model_stringE), data = e1ja)
+summary(e1cja_time_modE) # NA
+```
+
+We fit a Bayesian mixed-effects linear regression predicting the number of bids for joint attention (JA) as a function of fixed effects of condition, age (centered), and their interaction, with random intercepts per video.
+There were significantly more bids for JA in the Video condition (mean: `r round(subset(e1bids_M, Condition=="Activity Video")$mean,2)`, sd: `r round(subset(e1bids_M, Condition=="Activity Video")$sd,2)`) than in the No Video condition (mean: `r round(subset(e1bids_M, Condition=="No Video")$mean,2)`, sd: `r round(subset(e1bids_M, Condition=="No Video")$sd,2)`, $\beta=`r e1bids["ConditionActivity Video"]`$, 95% CI=[`r e1bids['95pLB']`,`r e1bids['95pUB']`]).
 Mixed-effects regressions with the same structure were performed predicting the number of episodes of coordinated and passive JA, and the total duration of time spent in coordinated and passive JA.
-There were no significant effects on the number or total duration of coordinated JA episodes, nor on the total duration of passive JA episodes. 
-For the regression predicting the number of passive JA episodes, the only significant effect was an interaction of condition and RR ($\beta=`r e1pja["ConditionActivity Video:RR"]`$, 95% CI=[`r e1pja['95pLB']`,`r e1pja['95pUB']`]), showing that for parents in the Video condition, those with higher Rules and Respect subscores engaged in more passive JA episodes.
+There were no significant effects on the number of or total duration of coordinated or passive JA episodes.
 Figure \@ref(fig:JA) (top) shows the mean number bids for JA and episodes of JA by condition in Experiment 1.
+
+### Exploratory Analyses
+
+We also fit Bayesian mixed-effects linear regression models predicting each of the above lexical diversity and joint attention dependent variables as a function of fixed effects of condition, age (centered), gender, parent's education level, and the subscales of the EPAQ: Early Learning (EL), Affection and Attachment (AA), and Rules and Respect (RR), along with interactions of condition and EL, AA, and RR.
+These models included random intercepts per video. 
+Of these exploratory regressions, only the regression predicting the number of passive JA episodes produced a significant effect involving these demographic variables: an interaction of condition and RR ($\beta=`r e1pjaE["ConditionActivity Video:RR"]`$, 95% CI=[`r e1pjaE['95pLB']`,`r e1pjaE['95pUB']`]), shows that for parents in the Activity Video condition, those with higher Rules and Respect subscores engaged in more passive JA episodes.
 
@@
 Looking at the most frequent content words parents used after the Activity Video, ...
-In contrast, the most frequent content words parents used in the Control condition were...
+In contrast, the most frequent content words parents used in the No Video condition were...
 
@@
 There was also a significant main effect of age ($\beta=`r e2tjaAge["age"]`$, 95% CI = [`r e2tjaAge["95pLB"]`,`r e2tjaAge["95pUB"]`]), showing that the number of episodes of JA decreased with the child's age.
-However, a significant interaction of age and condition ($\beta=`r e2tjaAgeCond["age:ConditionActivity Video"]`$, 95% CI = [`r e2tjaAgeCond["95pLB"]`,`r e2tjaAgeCond["95pUB"]`]), shown in Figure \ref{fig:JA} (right bottom), demonstrates that older children in the Activity Video condition did not see a decrease in the number of episodes of JA.
+However, a significant interaction of age and condition ($\beta=`r e2tjaAgeCond["age:ConditionActivity Video"]`$, 95% CI = [`r e2tjaAgeCond["95pLB"]`,`r e2tjaAgeCond["95pUB"]`]), shown in Figure \ref{fig:JA} (right bottom), demonstrates that there were more episodes of JA for older children in the Activity Video condition (comparable to episodes of JA for younger children).
 
@@
 
-This work was supported by a gift from Kinedu, Inc. 
+This work was supported by a gift and a contract from Kinedu, Inc. to the Language and Cognition Lab. 
 Thanks to members of the Language and Cognition Lab at Stanford for helpful discussion.

### 2019-09-24 paper/manuscript.tex
updated Exp 1 exploratory regressions

@@
 In Experiment 1, we invited parents of 6- to 24-month-old infants visiting the Children's Discovery Museum in San Jose to complete video-guided activities from a commerical parenting app that delivers digital parenting advice in the form of short videos.
-Parents were randomly assigned to the video condition or the control condition; parents in the \emph{activity video} condition watched a video from the app (matched to their child's age), and then performed the activity with their child using the props from the video.
-Parents in the \emph{control} condition did not watch an activity video, but were given a set of the same age-appropriate props and asked to play with their infants as they normally would at home.
+Parents were randomly assigned to one of two conditions: parents in the \emph{Activity Video} condition watched a video from the app (matched to their child's age), and then performed the activity with their child using the props from the video.
+Parents in the \emph{No Video} condition did not watch an activity video, but were given a set of the same age-appropriate props and asked to play with their infants as they normally would at home.
 
@@
 The toys were placed on a large foam play mat, and parents were instructed to sit on the mat with their child and re-create the activity they had viewed for a period of three minutes.\footnote{Based on piloting, we estimated these activities would would only require three minutes to complete.}
-In the Control condition, after informed consent parents were told to play with their child as they would at home with the provided props for a period of three minutes.
+In the No Video condition, after informed consent parents were told to play with their child as they would at home with the provided props for a period of three minutes.
 They were not given any additional instructions about how to use the props.
@@
 Parents' child-directed speech during the play sessions was transcribed.
-The transcripts and hand-coded joint attention data were analyzed according to our preregistration\footnote{Preregistration: \url{https://osf.io/2bpdf/}{]}}, with any deviations or extensions noted.
+The transcripts and hand-coded joint attention data were analyzed according to our preregistration\footnote{Preregistration: \url{https://osf.io/2bpdf/}{]}}, with any deviations or exploratory analyses noted.
 Below we first report the lexical diversity results, followed by the joint attention results.
@@
 
-We fit a Bayesian mixed-effects linear regression predicting TTR as a function of condition, age (centered), gender, and parent's education level with a random intercept per video using rstanarm (Goodrich, Gabry, Ali, \& Brilleman, 2018).
+We fit a Bayesian mixed-effects linear regression predicting TTR as a function of condition, age (centered), and their interaction with a random intercept per video using rstanarm (Goodrich, Gabry, Ali, \& Brilleman, 2018).
 For effects that are at least 95\% likely to be non-zero according to the posterior distribution, we report estimated coefficients (\(\beta\)) as well as 95\% Bayesian credible intervals (95\% CI), demarcating the range within which 95\% of the posterior predictive values fall.
-There was significantly lower TTR in the Video condition (mean: 0.32) than in the Control condition (mean: 0.43, \(\beta=\)-0.11, 95\% CI={[}-0.16,-0.06{]}).
+There was significantly lower TTR in the Video condition (mean: 0.32) than in the No Video condition (mean: 0.43, \(\beta=\)-0.11, 95\% CI={[}-0.16,-0.06{]}).
 There were no significant effects of age, gender, or parent's level of education.
-A similar Bayesian mixed-effects linear regression instead predicting MTLD also found significantly lower lexical diversity in the Video condition (mean MTLD: 17.87) than in the Control condition (mean: 27.09, \(\beta=\)-8.62, 95\% CI={[}-15.15,-2.01{]}), with no other significant effects.
+A similar Bayesian mixed-effects linear regression instead predicting MTLD also found significantly lower lexical diversity in the Activity Video condition (mean MTLD: 17.87) than in the No Video condition (mean: 27.09, \(\beta=\)-9.30, 95\% CI={[}-15.37,-3.18{]}), with no other significant effects.
 Figure \ref{fig:lexdiv} shows the mean of each lexical diversity measure (TTR and MTLD) by condition.
 
-We also conducted similar regressions predicting the number of word tokens and types, finding only a significant effect of condition on the number of word tokens (\(\beta=\) 56.36, 95\% CI={[}14.02,96.32{]})), with parents using more words in the Video condition (mean: 225, bootstrapped 95\% confidence intervals (CI): {[}199,252{]}) than in the Control condition (mean: 165, bootstrapped 95\% CI: {[}139,193{]}).
+We also conducted similar regressions predicting the number of word tokens and types, finding only a significant effect of condition on the number of word tokens (\(\beta=\) 59.07, 95\% CI={[}19.58,97.44{]})), with parents using more words in the Activity Video condition (mean: 225, bootstrapped 95\% confidence intervals (CI): {[}199,252{]}) than in the No Video condition (mean: 165, bootstrapped 95\% CI: {[}139,193{]}).
 
@@
 
-We fit a mixed-effects linear regression predicting the number of bids for joint attention (JA) as a function of fixed effects of condition, age (centered), gender, parent's education level, and the subscales of the EPAQ: Early Learning (EL), Affection and Attachment (AA), and Rules and Respect (RR), along with interactions of condition and EL, AA, and RR.
-This model included random intercepts per video.
-There were significantly more bids for JA in the Video condition (mean: 6.30, sd: 2.76) than in the Control condition (mean: 3.73, sd: 2.74, \(\beta=3.40\), 95\% CI={[}1.03,5.73{]}).
+We fit a Bayesian mixed-effects linear regression predicting the number of bids for joint attention (JA) as a function of fixed effects of condition, age (centered), and their interaction, with random intercepts per video.
+There were significantly more bids for JA in the Video condition (mean: 6.30, sd: 2.76) than in the No Video condition (mean: 3.73, sd: 2.74, \(\beta=2.56\), 95\% CI={[}0.74,4.44{]}).
+Mixed-effects regressions with the same structure were performed predicting the number of episodes of coordinated and passive JA, and the total duration of time spent in coordinated and passive JA.
+There were no significant effects on the number of or total duration of coordinated or passive JA episodes.
+Figure \ref{fig:JA} (top) shows the mean number bids for JA and episodes of JA by condition in Experiment 1.
 
-Mixed-effects regressions with the same structure were performed predicting the number of episodes of coordinated and passive JA, and the total duration of time spent in coordinated and passive JA.
-There were no significant effects on the number or total duration of coordinated JA episodes, nor on the total duration of passive JA episodes.
-For the regression predicting the number of passive JA episodes, the only significant effect was an interaction of condition and RR (\(\beta=1.82\), 95\% CI={[}0.20,3.48{]}), showing that for parents in the Video condition, those with higher Rules and Respect subscores engaged in more passive JA episodes.
-Figure \ref{fig:JA} (top) shows the mean number bids for JA and episodes of JA by condition in Experiment 1.
+\hypertarget{exploratory-analyses}{%
+\subsubsection{Exploratory Analyses}\label{exploratory-analyses}}
+
+We also fit Bayesian mixed-effects linear regression models predicting each of the above lexical diversity and joint attention dependent variables as a function of fixed effects of condition, age (centered), gender, parent's education level, and the subscales of the EPAQ: Early Learning (EL), Affection and Attachment (AA), and Rules and Respect (RR), along with interactions of condition and EL, AA, and RR.
+These models included random intercepts per video.
+Of these exploratory regressions, only the regression predicting the number of passive JA episodes produced a significant effect involving these demographic variables: an interaction of condition and RR (\(\beta=1.82\), 95\% CI={[}0.20,3.48{]}), shows that for parents in the Activity Video condition, those with higher Rules and Respect subscores engaged in more passive JA episodes.
 
@@
 Looking at the most frequent content words parents used after the Activity Video, \ldots{}
-In contrast, the most frequent content words parents used in the Control condition were\ldots{}
+In contrast, the most frequent content words parents used in the No Video condition were\ldots{}
 
@@
 There was also a significant main effect of age (\(\beta=-5\), 95\% CI = {[}-8.27,-1.41{]}), showing that the number of episodes of JA decreased with the child's age.
-However, a significant interaction of age and condition (\(\beta=5.60\), 95\% CI = {[}0.46,10.37{]}), shown in Figure \ref{fig:JA} (right bottom), demonstrates that older children in the Activity Video condition did not see a decrease in the number of episodes of JA.
+However, a significant interaction of age and condition (\(\beta=5.60\), 95\% CI = {[}0.46,10.37{]}), shown in Figure \ref{fig:JA} (right bottom), demonstrates that there were more episodes of JA for older children in the Activity Video condition (comparable to episodes of JA for younger children).
 
-\hypertarget{exploratory-analyses}{%
-\subsubsection{Exploratory Analyses}\label{exploratory-analyses}}
+\hypertarget{exploratory-analyses-1}{%
+\subsubsection{Exploratory Analyses}\label{exploratory-analyses-1}}
 
@@
 
-This work was supported by a gift from Kinedu, Inc.
+This work was supported by a gift and a contract from Kinedu, Inc.~to the Language and Cognition Lab.
 Thanks to members of the Language and Cognition Lab at Stanford for helpful discussion.

### 2019-09-28 paper/manuscript.Rmd
full draft -- rewrite discussion

@@
 keywords          : "digital parenting advice; joint attention; lexical diversity; guided play"
-wordcount         : "4510"
+wordcount         : "4569"
 
@@
 Parents participating in the Activity Video condition were assigned to watch one of the two activity videos available for their child's age group, while parents in the No Video condition watched no video, and were simply asked to play with their child as they normally would.
-The No Video condition was yoked to the Activity Video condition such that for every participant in the Video condition who saw a particular video and received the associated props, a participant in the No Video condition received the same props but did not watch the activity video.
+The two conditions were yoked: for each Activity Video participant who saw a particular video and received the associated props, a participant in the No Video condition received the same props to use without seeing the video.
 Parents also completed the Early Parenting Attitudes Questionnaire [EPAQ; @Hembacher2018]. 
-The EPAQ measures parents of young children's attitudes about parenting and child development along three dimensions: rules and respect, early learning, and affection and attachment.
+The EPAQ measures parents of young children's attitudes about parenting and child development along three dimensions: rules and respect, early learning, and affection and attachment (see SI).
 
@@
 A second coder independently coded a third of the videos (i.e., 20 of the 60 videos, approximately equally distributed across ages) to establish reliability. 
-The two coders had a reliability of ICC = 0.80 with 95% confident interval (CI) = [0.57,0.92] for number of parent bids for JA; ICC = 0.20 with 95% CI = [-0.26,0.58] for number of passive JA episodes; ICC = 0.66 with 95% CI = [0.32,0.85] for number of coordinated JA episodes; ICC = 0.24 with 95% CI = [-0.21,0.61] for total duration of passive JA episodes, and ICC = 0.62 with 95% CI = [0.27,0.83] for total duration of coordinated JA episodes.
+The two coders had a reliability of ICC = 0.80 with 95% confidence interval (CI) = [0.57,0.92] for number of parent bids for JA; ICC = 0.20 with 95% CI = [-0.26,0.58] for number of passive JA episodes; ICC = 0.66 with 95% CI = [0.32,0.85] for number of coordinated JA episodes; ICC = 0.24 with 95% CI = [-0.21,0.61] for total duration of passive JA episodes, and ICC = 0.62 with 95% CI = [0.27,0.83] for total duration of coordinated JA episodes.
 
@@
 For effects that are at least 95% likely to be non-zero according to the posterior distribution, we report estimated coefficients ($\beta$) as well as 95% Bayesian credible intervals (95% CI), demarcating the range within which 95% of the posterior predictive values fall.
-There was significantly lower TTR in the Video condition (mean: `r round(subset(e1_lexdiv, condition=='exp')$TTR, 2)`) than in the No Video condition (mean: `r round(subset(e1_lexdiv, condition=='con')$TTR, 2)`, $\beta=$`r e1TTR["conditionexp"]`, 95% CI=[`r e1TTR['95pLB']`,`r e1TTR['95pUB']`]).
+There was significantly lower TTR in the Activity Video condition (mean: `r round(subset(e1_lexdiv, condition=='exp')$TTR, 2)`) than in the No Video condition (mean: `r round(subset(e1_lexdiv, condition=='con')$TTR, 2)`, $\beta=$`r e1TTR["conditionexp"]`, 95% CI=[`r e1TTR['95pLB']`,`r e1TTR['95pUB']`]).
 There were no significant effects of age, gender, or parent's level of education.
@@
 
-We also conducted similar regressions predicting the number of word tokens and types, finding only a significant effect of condition on the number of word tokens ($\beta=$ `r e1tokens["conditionexp"]`, 95% CI=[`r e1tokens['95pLB']`,`r e1tokens['95pUB']`])), with parents using more words in the Activity Video condition (mean: `r round(subset(e1_lexdiv, condition=='exp')$tokens, 0)`, bootstrapped 95% confidence intervals (CI): [`r round(subset(e1_tok, Condition=="Activity Video")$ci_lower, 0)`,`r round(subset(e1_tok, Condition=="Activity Video")$ci_upper, 0)`]) than in the No Video condition (mean: `r round(subset(e1_lexdiv, condition=='con')$tokens, 0)`, bootstrapped 95% CI: [`r round(subset(e1_tok, Condition=="No Video")$ci_lower, 0)`,`r round(subset(e1_tok, Condition=="No Video")$ci_upper, 0)`]).
+We also conducted similar regressions predicting the number of word tokens and types, finding only a significant effect of condition on the number of word tokens ($\beta=$ `r e1tokens["conditionexp"]`, 95% CI=[`r e1tokens['95pLB']`,`r e1tokens['95pUB']`])), with parents using more words in the Activity Video condition (mean: `r round(subset(e1_lexdiv, condition=='exp')$tokens, 0)`, bootstrapped 95% confidence intervals: [`r round(subset(e1_tok, Condition=="Activity Video")$ci_lower, 0)`,`r round(subset(e1_tok, Condition=="Activity Video")$ci_upper, 0)`]) than in the No Video condition (mean: `r round(subset(e1_lexdiv, condition=='con')$tokens, 0)`, bootstrapped 95% confidence intervals: [`r round(subset(e1_tok, Condition=="No Video")$ci_lower, 0)`,`r round(subset(e1_tok, Condition=="No Video")$ci_upper, 0)`]).
 
@@
 ```{r fig-lexdiv, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=6.5, fig.height=5.5, fig.cap = "\\label{fig:lexdiv} Mean lexical diversity scores (left: Type/Token ratio, middle: MTLD) and mean number of tokens used by condition (right) in Experiment 1 (top) and Experiment 2 (bottom).
-Error bars show bootstrapped 95\\% confidence intervals (CIs), and gray dots indicate values for each participant."}
+Error bars show bootstrapped 95\\% confidence intervals, and gray dots indicate values for each participant."}
 
@@
 We fit a Bayesian mixed-effects linear regression predicting the number of bids for joint attention (JA) as a function of fixed effects of condition, age (centered), and their interaction, with random intercepts per video.
-There were significantly more bids for JA in the Video condition (mean: `r round(subset(e1bids_M, Condition=="Activity Video")$mean,2)`, sd: `r round(subset(e1bids_M, Condition=="Activity Video")$sd,2)`) than in the No Video condition (mean: `r round(subset(e1bids_M, Condition=="No Video")$mean,2)`, sd: `r round(subset(e1bids_M, Condition=="No Video")$sd,2)`, $\beta=`r e1bids["ConditionActivity Video"]`$, 95% CI=[`r e1bids['95pLB']`,`r e1bids['95pUB']`]).
+There were significantly more bids for JA in the Activity Video condition (mean: `r round(subset(e1bids_M, Condition=="Activity Video")$mean,2)`, sd: `r round(subset(e1bids_M, Condition=="Activity Video")$sd,2)`) than in the No Video condition (mean: `r round(subset(e1bids_M, Condition=="No Video")$mean,2)`, sd: `r round(subset(e1bids_M, Condition=="No Video")$sd,2)`, $\beta=`r e1bids["ConditionActivity Video"]`$, 95% CI=[`r e1bids['95pLB']`,`r e1bids['95pUB']`]).
 Mixed-effects regressions with the same structure were performed predicting the number of episodes of coordinated and passive JA, and the total duration of time spent in coordinated and passive JA.
@@
 Of these exploratory regressions, only the regression predicting the number of passive JA episodes produced a significant effect involving these demographic variables: an interaction of condition and RR ($\beta=`r e1pjaE["ConditionActivity Video:RR"]`$, 95% CI=[`r e1pjaE['95pLB']`,`r e1pjaE['95pUB']`]), shows that for parents in the Activity Video condition, those with higher Rules and Respect subscores engaged in more passive JA episodes.
+
+To better understand the intervention's effect on language use, we analyzed which words are characteristic of parents' speech in each condition, comparing the differency in frequency rank of each word (lemma) in the two conditions, as well as contrasting the corpus overall with a general English-language word frequency list (see SI for the interactive corpus characteristic plot).
+Words that are strongly indicative of being from the Activity Video condition include "give", "big", "small", "thank", "have", "which", and "school", while words that are most characteristic of the No Video condition include "ready", "on", "oh", "see", "going", "let", and "are".
 
@@
 In summary, while parents produced more word types and tokens after viewing the activity video, lexical diversity (both TTR and MTLD) was higher when parents were just asked to play as they normally would.
-It may be that parents in the Activity Video condition, in their attempt to stick to the prescribed task, end up repeating themselves more. 
-Looking at the most frequent content words parents used after the Activity Video, ...
-In contrast, the most frequent content words parents used in the No Video condition were...
-
-Parents who watched an activity video made significantly more bids for JA with their child, although this did not result in a greater number of successful episodes of JA than dyads in the no video condition.
-No differences in the duration or number of episodes of passive or coordinated JA between conditions were found.
-
-After the activity video, parents with higher RR scores showed an increased number of passive JA episodes than high-RR parents did after no video.
-While the electronically-delivered parenting advice increased the number of bids for JA by parents, it did not significantly affect the number or duration of episodes of JA. 
-RELATE BACK TO HYPOTHESES
+It may be that parents in the Activity Video condition, in their attempt to stick to the prescribed task, end up repeating themselves more, and indeed some differences in speech acts were notable: 
+after the Activity Video, parents used more words related to requests (e.g., "Can I have X?
+/ Give me X.
+Thank you!"), whereas after no intervention parents' language related more to invitations (e.g., "Are you ready?" / "Let's see.").
+However, parents who watched an activity video also made significantly more bids for JA with their child, although this did not result in a greater number of successful episodes of JA--passive or coordinated--than dyads in the no video condition.
+In sum, the results of Experiment 1 suggest that digital parenting advice can increase parents' efforts to engage their child in joint attention, the volume if not diversity of their speech, and can shift the type of speech acts towards more requests.
 
@@
 
-Experiment 1 found that parents who watched an activity video spoke more words overall, but had lower lexical diversity compared to parents who played with their children as they normally would at home.
+Experiment 1 found that parents who watched an activity video made more bids for joint attention and spoke more words overall to their children, but had lower lexical diversity compared to parents who played with their children as they normally would at home.
 Might it be that parents who are focused on a specific activity show reduced lexical diversity due to their focus on engaging their child in the activity?
-Parents who watched an activity video made more bids for joint attention, although these bids did not result in more episodes of joint attention compared to the control group. 
 Experiment 2 attempts to replicate these findings from with a restricted number of preregistered predictions.[^4]
@@
 
-The design of Experiment 2 was similar to that of Experiment 1, except that instead of No Video control condition, parents instead watched a video that was generally related to child development research, but did not give any specific instructions about how to interact with infants or children.
+The design of Experiment 2 was similar to that of Experiment 1, except that instead of seeing no video in the control condition, parents instead watched a video that was generally related to child development research, but did not give any specific instructions about how to interact with infants or children.
 This condition was included to control for the possibility that differences in language output and joint attention in Experiment 1 could be due to simply cueing parents to think about infants' learning and cognitive development.
@@
 Parents' child-directed speech was transcribed and processed, and bids and episodes of joint attention were coded according to the same procedure used in Experiment 1.
-We first report reregistered regressions predicting TTR and number of tokens, as well as an exploratory regression predicting MTLD.
+We first report preregistered regressions[^5] predicting TTR and number of tokens, as well as an exploratory regression predicting MTLD.
 We then turn to preregistered regressions of parental bids for joint attention and the total number of JA episodes.
-As noted in the preregistration, we adopt an alpha level of .005 for statistical significance and will report alphas between .05 and .005 as suggestive.
+
+[^5]: Although the preregistration implied the use of standard linear mixed-effects regression through the specification of adopting an alpha level of .005 for statistical significance, the non-convergence of some of the below regressions led us to switch to Bayesian regression.
+Using a Bayesian analysis also has the added benefit of not requiring arbitrary decisions about changing alpha levels to attempt to correct for multiple comparisons (Gelman, 2008).
 
@@
 # The number of parent bids for joint attention, the number of episodes of joint attention, the number of word tokens produced by parents, and the lexical diversity of parent language output (word types/word tokens).
-# 1) bids, 2) total JA eps, 3) # tokens 4) TTR -- alpha level = .005
+# 1) bids, 2) total JA eps, 3) # tokens 4) TTR 
 # Mixed-effects linear regressions predicting the dependent variables with condition (video scaffolding vs.
@@
 We fit a mixed-effects linear regression predicting TTR as a function of age (centered) and condition with an interaction term, and with random intercepts per video using lme4 [@lme4].
-There was suggestively lower TTR in the Video condition (mean: `r round(e2_lexdiv[2,]$TTR, 2)`) than in the Control condition (mean: `r round(e2_lexdiv[1,]$TTR, 2)`, $\beta=`r e2TTR["conditionexp"]`$, , 95% CI=[`r e2TTR['95pLB']`,`r e2TTR['95pUB']`]).
+There was suggestively lower TTR after the Activity Video (mean: `r round(e2_lexdiv[2,]$TTR, 2)`) than after the Science Video (mean: `r round(e2_lexdiv[1,]$TTR, 2)`, $\beta=`r e2TTR["conditionexp"]`$, , 95% CI=[`r e2TTR['95pLB']`,`r e2TTR['95pUB']`]).
 There was no significant effect of age, nor a significant interaction.
@@
 As preregistered, we fit mixed-effects linear regressions predicting the number of parental bids for joint attention and the total number of episodes of JA as a function of fixed effects of condition, age (centered), and their interaction, with random intercepts per video.
-Shown in Figure \ref{fig:JA} (left bottom), parents made significantly more bids for JA after watching the Activity Video (mean: `r round(subset(e2_bids, Condition=="Activity Video")$mean,2)`, bootstrapped 95% CI: `r round(subset(e2_bids, Condition=="Activity Video")$ci_lower,2)`, `r round(subset(e2_bids, Condition=="Activity Video")$ci_upper,2)`; $\beta=`r e2bids["ConditionActivity Video"]`$, 95% CI = [`r e2bids["95pLB"]`,`r e2bids["95pUB"]`]) than after the Science Video (mean: `r round(subset(e2_bids, Condition=="Science Video")$mean,2)`, 95% CI: [`r round(subset(e2_bids, Condition=="Science Video")$ci_lower,2)`, `r round(subset(e2_bids, Condition=="Science Video")$ci_upper,2)`]).
+Shown in Figure \ref{fig:JA} (left bottom), parents made significantly more bids for JA after watching the Activity Video (mean: `r round(subset(e2_bids, Condition=="Activity Video")$mean,2)`, bootstrapped 95% confidence intervals: `r round(subset(e2_bids, Condition=="Activity Video")$ci_lower,2)`, `r round(subset(e2_bids, Condition=="Activity Video")$ci_upper,2)`; $\beta=`r e2bids["ConditionActivity Video"]`$, 95% CI = [`r e2bids["95pLB"]`,`r e2bids["95pUB"]`]) than after the Science Video (mean: `r round(subset(e2_bids, Condition=="Science Video")$mean,2)`, 95% CI: [`r round(subset(e2_bids, Condition=="Science Video")$ci_lower,2)`, `r round(subset(e2_bids, Condition=="Science Video")$ci_upper,2)`]).
 There were no other significant effects on parental bids for JA.
@@
 
-```{r e2ja-coord, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=5.5, fig.height=3.5, fig.cap = "The number of episodes of coordinated JA by condition and age in Experiment 2.
-Older children in the Activity Video condition engaged in more episodes of coordinated JA with their caregiver than dyads in the Control Video condition."}
+As for Experiment 1, we conducted a corpus characteristic analysis to examine differences parents' language use in the two conditions.
+The words that are strongly indicative of being from the Activity Video condition include "big", "little", "give", "small", "yellow", "take", and "put", while words that are most characteristic of the Science Video condition include "beep", "like", "say", "does", "uhoh", "for", and "neigh".
+
+```{r e2ja-coord, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=5.5, fig.height=3.5, fig.cap = "The number of episodes of coordinated JA by condition and age in Experiment 2."}
+# Older children in the Activity Video condition engaged in more episodes of coordinated JA with their caregiver than dyads in the Control Video condition. (no interpretation in PsychSci captions)
 
@@
 This study investigated how parents change their interactions with their young children on the basis of one of several short video parenting messages from a commercial parenting app, which suggest interactive toy-based activities (e.g., learning animal sounds), along with a scientific justification.
-Parents in the control conditions received either no video (Experiment 1) or a video of a recent finding in developmental psychology (Experiment 2), but played with the same sets of toys given to those in the experimental conditions.
-After completing the videos, parents were videotaped playing with their children for two minutes. 
+Parents in the control conditions received either no video (Experiment 1) or a video of a recent finding in developmental psychology (Experiment 2), and then played with their child for three minutes using the same sets of toys given to those in the experimental conditions.
 The quality of parents' interactions with their children were measured by the lexical diversity of their child-directed speech, and through behavioral coding of bids for and episodes of joint attention (JA).

### 2019-09-28 paper/manuscript.tex
full draft -- rewrite discussion

@@
 \textsuperscript{1} Department of Psychology, Stanford University\\\textsuperscript{2} Nextdoor, Inc.\\\textsuperscript{3} Gallaudet University\\\textsuperscript{4} Cornell University}
-\keywords{digital parenting advice; joint attention; lexical diversity; guided play\newline\indent Word count: 4510}
+\keywords{digital parenting advice; joint attention; lexical diversity; guided play\newline\indent Word count: 4569}
 \usepackage{csquotes}
@@
 Parents participating in the Activity Video condition were assigned to watch one of the two activity videos available for their child's age group, while parents in the No Video condition watched no video, and were simply asked to play with their child as they normally would.
-The No Video condition was yoked to the Activity Video condition such that for every participant in the Video condition who saw a particular video and received the associated props, a participant in the No Video condition received the same props but did not watch the activity video.
+The two conditions were yoked: for each Activity Video participant who saw a particular video and received the associated props, a participant in the No Video condition received the same props to use without seeing the video.
 Parents also completed the Early Parenting Attitudes Questionnaire (EPAQ; Hembacher \& Frank, 2018).
-The EPAQ measures parents of young children's attitudes about parenting and child development along three dimensions: rules and respect, early learning, and affection and attachment.
+The EPAQ measures parents of young children's attitudes about parenting and child development along three dimensions: rules and respect, early learning, and affection and attachment (see SI).
 
@@
 A second coder independently coded a third of the videos (i.e., 20 of the 60 videos, approximately equally distributed across ages) to establish reliability.
-The two coders had a reliability of ICC = 0.80 with 95\% confident interval (CI) = {[}0.57,0.92{]} for number of parent bids for JA; ICC = 0.20 with 95\% CI = {[}-0.26,0.58{]} for number of passive JA episodes; ICC = 0.66 with 95\% CI = {[}0.32,0.85{]} for number of coordinated JA episodes; ICC = 0.24 with 95\% CI = {[}-0.21,0.61{]} for total duration of passive JA episodes, and ICC = 0.62 with 95\% CI = {[}0.27,0.83{]} for total duration of coordinated JA episodes.
+The two coders had a reliability of ICC = 0.80 with 95\% confidence interval (CI) = {[}0.57,0.92{]} for number of parent bids for JA; ICC = 0.20 with 95\% CI = {[}-0.26,0.58{]} for number of passive JA episodes; ICC = 0.66 with 95\% CI = {[}0.32,0.85{]} for number of coordinated JA episodes; ICC = 0.24 with 95\% CI = {[}-0.21,0.61{]} for total duration of passive JA episodes, and ICC = 0.62 with 95\% CI = {[}0.27,0.83{]} for total duration of coordinated JA episodes.
 
@@
 For effects that are at least 95\% likely to be non-zero according to the posterior distribution, we report estimated coefficients (\(\beta\)) as well as 95\% Bayesian credible intervals (95\% CI), demarcating the range within which 95\% of the posterior predictive values fall.
-There was significantly lower TTR in the Video condition (mean: 0.32) than in the No Video condition (mean: 0.43, \(\beta=\)-0.11, 95\% CI={[}-0.16,-0.06{]}).
+There was significantly lower TTR in the Activity Video condition (mean: 0.32) than in the No Video condition (mean: 0.43, \(\beta=\)-0.11, 95\% CI={[}-0.16,-0.06{]}).
 There were no significant effects of age, gender, or parent's level of education.
@@
 
-We also conducted similar regressions predicting the number of word tokens and types, finding only a significant effect of condition on the number of word tokens (\(\beta=\) 59.07, 95\% CI={[}19.58,97.44{]})), with parents using more words in the Activity Video condition (mean: 225, bootstrapped 95\% confidence intervals (CI): {[}199,252{]}) than in the No Video condition (mean: 165, bootstrapped 95\% CI: {[}139,193{]}).
+We also conducted similar regressions predicting the number of word tokens and types, finding only a significant effect of condition on the number of word tokens (\(\beta=\) 59.07, 95\% CI={[}19.58,97.44{]})), with parents using more words in the Activity Video condition (mean: 225, bootstrapped 95\% confidence intervals: {[}199,252{]}) than in the No Video condition (mean: 165, bootstrapped 95\% confidence intervals: {[}139,193{]}).
 
@@
 \caption{\label{fig:lexdiv} Mean lexical diversity scores (left: Type/Token ratio, middle: MTLD) and mean number of tokens used by condition (right) in Experiment 1 (top) and Experiment 2 (bottom).
-Error bars show bootstrapped 95\% confidence intervals (CIs), and gray dots indicate values for each participant.}\label{fig:fig-lexdiv}
+Error bars show bootstrapped 95\% confidence intervals, and gray dots indicate values for each participant.}\label{fig:fig-lexdiv}
 \end{figure}
@@
 We fit a Bayesian mixed-effects linear regression predicting the number of bids for joint attention (JA) as a function of fixed effects of condition, age (centered), and their interaction, with random intercepts per video.
-There were significantly more bids for JA in the Video condition (mean: 6.30, sd: 2.76) than in the No Video condition (mean: 3.73, sd: 2.74, \(\beta=2.56\), 95\% CI={[}0.74,4.44{]}).
+There were significantly more bids for JA in the Activity Video condition (mean: 6.30, sd: 2.76) than in the No Video condition (mean: 3.73, sd: 2.74, \(\beta=2.56\), 95\% CI={[}0.74,4.44{]}).
 Mixed-effects regressions with the same structure were performed predicting the number of episodes of coordinated and passive JA, and the total duration of time spent in coordinated and passive JA.
@@
 Of these exploratory regressions, only the regression predicting the number of passive JA episodes produced a significant effect involving these demographic variables: an interaction of condition and RR (\(\beta=1.82\), 95\% CI={[}0.20,3.48{]}), shows that for parents in the Activity Video condition, those with higher Rules and Respect subscores engaged in more passive JA episodes.
+
+To better understand the intervention's effect on language use, we analyzed which words are characteristic of parents' speech in each condition, comparing the differency in frequency rank of each word (lemma) in the two conditions, as well as contrasting the corpus overall with a general English-language word frequency list (see SI for the interactive corpus characteristic plot).
+Words that are strongly indicative of being from the Activity Video condition include \enquote{give}, \enquote{big}, \enquote{small}, \enquote{thank}, \enquote{have}, \enquote{which}, and \enquote{school}, while words that are most characteristic of the No Video condition include \enquote{ready}, \enquote{on}, \enquote{oh}, \enquote{see}, \enquote{going}, \enquote{let}, and \enquote{are}.
 
@@
 In summary, while parents produced more word types and tokens after viewing the activity video, lexical diversity (both TTR and MTLD) was higher when parents were just asked to play as they normally would.
-It may be that parents in the Activity Video condition, in their attempt to stick to the prescribed task, end up repeating themselves more.
-Looking at the most frequent content words parents used after the Activity Video, \ldots{}
-In contrast, the most frequent content words parents used in the No Video condition were\ldots{}
-
-Parents who watched an activity video made significantly more bids for JA with their child, although this did not result in a greater number of successful episodes of JA than dyads in the no video condition.
-No differences in the duration or number of episodes of passive or coordinated JA between conditions were found.
-
-After the activity video, parents with higher RR scores showed an increased number of passive JA episodes than high-RR parents did after no video.
-While the electronically-delivered parenting advice increased the number of bids for JA by parents, it did not significantly affect the number or duration of episodes of JA.
-RELATE BACK TO HYPOTHESES
+It may be that parents in the Activity Video condition, in their attempt to stick to the prescribed task, end up repeating themselves more, and indeed some differences in speech acts were notable:
+after the Activity Video, parents used more words related to requests (e.g., \enquote{Can I have X?
+/ Give me X.
+Thank you!}), whereas after no intervention parents' language related more to invitations (e.g., \enquote{Are you ready?} / \enquote{Let's see.}).
+However, parents who watched an activity video also made significantly more bids for JA with their child, although this did not result in a greater number of successful episodes of JA--passive or coordinated--than dyads in the no video condition.
+In sum, the results of Experiment 1 suggest that digital parenting advice can increase parents' efforts to engage their child in joint attention, the volume if not diversity of their speech, and can shift the type of speech acts towards more requests.
 
@@
 
-Experiment 1 found that parents who watched an activity video spoke more words overall, but had lower lexical diversity compared to parents who played with their children as they normally would at home.
+Experiment 1 found that parents who watched an activity video made more bids for joint attention and spoke more words overall to their children, but had lower lexical diversity compared to parents who played with their children as they normally would at home.
 Might it be that parents who are focused on a specific activity show reduced lexical diversity due to their focus on engaging their child in the activity?
-Parents who watched an activity video made more bids for joint attention, although these bids did not result in more episodes of joint attention compared to the control group.
 Experiment 2 attempts to replicate these findings from with a restricted number of preregistered predictions.\footnote{Preregistration: \url{https://osf.io/2bpdf/}.}
@@
 Parents' child-directed speech was transcribed and processed, and bids and episodes of joint attention were coded according to the same procedure used in Experiment 1.
-We first report reregistered regressions predicting TTR and number of tokens, as well as an exploratory regression predicting MTLD.
+We first report preregistered regressions\footnote{Although the preregistration implied the use of standard linear mixed-effects regression through the specification of adopting an alpha level of .005 for statistical significance, the non-convergence of some of the below regressions led us to switch to Bayesian regression.
+Using a Bayesian analysis also has the added benefit of not requiring arbitrary decisions about changing alpha levels to attempt to correct for multiple comparisons (Gelman, 2008).} predicting TTR and number of tokens, as well as an exploratory regression predicting MTLD.
 We then turn to preregistered regressions of parental bids for joint attention and the total number of JA episodes.
-As noted in the preregistration, we adopt an alpha level of .005 for statistical significance and will report alphas between .05 and .005 as suggestive.
 
@@
 We fit a mixed-effects linear regression predicting TTR as a function of age (centered) and condition with an interaction term, and with random intercepts per video using lme4 (Bates, Mächler, Bolker, \& Walker, 2015).
-There was suggestively lower TTR in the Video condition (mean: 0.38) than in the Control condition (mean: 0.48, \(\beta=-0.09\), , 95\% CI={[}-0.15,-0.03{]}).
+There was suggestively lower TTR after the Activity Video (mean: 0.38) than after the Science Video (mean: 0.48, \(\beta=-0.09\), , 95\% CI={[}-0.16,-0.03{]}).
 There was no significant effect of age, nor a significant interaction.
@@
 As preregistered, we fit mixed-effects linear regressions predicting the number of parental bids for joint attention and the total number of episodes of JA as a function of fixed effects of condition, age (centered), and their interaction, with random intercepts per video.
-Shown in Figure \ref{fig:JA} (left bottom), parents made significantly more bids for JA after watching the Activity Video (mean: 12.96, bootstrapped 95\% CI: 11.79, 14.24; \(\beta=3.07\), 95\% CI = {[}1.15,5.06{]}) than after the Science Video (mean: 9.89, 95\% CI: {[}8.73, 11.10{]}).
+Shown in Figure \ref{fig:JA} (left bottom), parents made significantly more bids for JA after watching the Activity Video (mean: 12.96, bootstrapped 95\% confidence intervals: 11.79, 14.24; \(\beta=3.07\), 95\% CI = {[}1.15,5.06{]}) than after the Science Video (mean: 9.89, 95\% CI: {[}8.73, 11.10{]}).
 There were no other significant effects on parental bids for JA.
@@
 
+As for Experiment 1, we conducted a corpus characteristic analysis to examine differences parents' language use in the two conditions.
+The words that are strongly indicative of being from the Activity Video condition include \enquote{big}, \enquote{little}, \enquote{give}, \enquote{small}, \enquote{yellow}, \enquote{take}, and \enquote{put}, while words that are most characteristic of the Science Video condition include \enquote{beep}, \enquote{like}, \enquote{say}, \enquote{does}, \enquote{uhoh}, \enquote{for}, and \enquote{neigh}.
+
 \begin{figure}[H]
@@
 
-\caption{The number of episodes of coordinated JA by condition and age in Experiment 2.
-Older children in the Activity Video condition engaged in more episodes of coordinated JA with their caregiver than dyads in the Control Video condition.}\label{fig:e2ja-coord}
+\caption{The number of episodes of coordinated JA by condition and age in Experiment 2.}\label{fig:e2ja-coord}
 \end{figure}
@@
 This study investigated how parents change their interactions with their young children on the basis of one of several short video parenting messages from a commercial parenting app, which suggest interactive toy-based activities (e.g., learning animal sounds), along with a scientific justification.
-Parents in the control conditions received either no video (Experiment 1) or a video of a recent finding in developmental psychology (Experiment 2), but played with the same sets of toys given to those in the experimental conditions.
-After completing the videos, parents were videotaped playing with their children for two minutes.
+Parents in the control conditions received either no video (Experiment 1) or a video of a recent finding in developmental psychology (Experiment 2), and then played with their child for three minutes using the same sets of toys given to those in the experimental conditions.
 The quality of parents' interactions with their children were measured by the lexical diversity of their child-directed speech, and through behavioral coding of bids for and episodes of joint attention (JA).

### 2019-10-01 paper/manuscript.Rmd
re-did discussion

@@
 keywords          : "digital parenting advice; joint attention; lexical diversity; guided play"
-wordcount         : "4569"
+wordcount         : "4576"
 
@@
 There was significantly lower TTR in the Activity Video condition (mean: `r round(subset(e1_lexdiv, condition=='exp')$TTR, 2)`) than in the No Video condition (mean: `r round(subset(e1_lexdiv, condition=='con')$TTR, 2)`, $\beta=$`r e1TTR["conditionexp"]`, 95% CI=[`r e1TTR['95pLB']`,`r e1TTR['95pUB']`]).
-There were no significant effects of age, gender, or parent's level of education.
-A similar Bayesian mixed-effects linear regression instead predicting MTLD also found significantly lower lexical diversity in the Activity Video condition (mean MTLD: `r round(subset(e1_lexdiv, condition=='exp')$MTLD, 2)`) than in the No Video condition (mean: `r round(subset(e1_lexdiv, condition=='con')$MTLD, 2)`, $\beta=$`r e1MTLD["conditionexp"]`, 95% CI=[`r e1MTLD['95pLB']`,`r e1MTLD['95pUB']`]), with no other significant effects.
+A similar regression instead predicting MTLD also found significantly lower lexical diversity in the Activity Video condition (mean MTLD: `r round(subset(e1_lexdiv, condition=='exp')$MTLD, 2)`) than in the No Video condition (mean: `r round(subset(e1_lexdiv, condition=='con')$MTLD, 2)`, $\beta=$`r e1MTLD["conditionexp"]`, 95% CI=[`r e1MTLD['95pLB']`,`r e1MTLD['95pUB']`]), with no other significant effects.
 Figure \ref{fig:lexdiv} shows the mean of each lexical diversity measure (TTR and MTLD) by condition.
@@
 
-We also conducted similar regressions predicting the number of word tokens and types, finding only a significant effect of condition on the number of word tokens ($\beta=$ `r e1tokens["conditionexp"]`, 95% CI=[`r e1tokens['95pLB']`,`r e1tokens['95pUB']`])), with parents using more words in the Activity Video condition (mean: `r round(subset(e1_lexdiv, condition=='exp')$tokens, 0)`, bootstrapped 95% confidence intervals: [`r round(subset(e1_tok, Condition=="Activity Video")$ci_lower, 0)`,`r round(subset(e1_tok, Condition=="Activity Video")$ci_upper, 0)`]) than in the No Video condition (mean: `r round(subset(e1_lexdiv, condition=='con')$tokens, 0)`, bootstrapped 95% confidence intervals: [`r round(subset(e1_tok, Condition=="No Video")$ci_lower, 0)`,`r round(subset(e1_tok, Condition=="No Video")$ci_upper, 0)`]).
+We also conducted similar regressions predicting the number of word tokens and types, finding only a significant effect of condition on the number of word tokens ($\beta=$ `r e1tokens["conditionexp"]`, 95% CI=[`r e1tokens['95pLB']`,`r e1tokens['95pUB']`]), with parents using more words in the Activity Video condition (mean: `r round(subset(e1_lexdiv, condition=='exp')$tokens, 0)`, bootstrapped 95% confidence intervals: [`r round(subset(e1_tok, Condition=="Activity Video")$ci_lower, 0)`,`r round(subset(e1_tok, Condition=="Activity Video")$ci_upper, 0)`]) than in the No Video condition (mean: `r round(subset(e1_lexdiv, condition=='con')$tokens, 0)`, bootstrapped 95% confidence intervals: [`r round(subset(e1_tok, Condition=="No Video")$ci_lower, 0)`,`r round(subset(e1_tok, Condition=="No Video")$ci_upper, 0)`]).
 
@@
 summary(e2tokens_m) # NA 
+#get_stan_glmer_reporting_values(e2tokens_m,"conditionexp")
 
@@
 
-We fit a mixed-effects linear regression predicting TTR as a function of age (centered) and condition with an interaction term, and with random intercepts per video using lme4 [@lme4].
-There was suggestively lower TTR after the Activity Video (mean: `r round(e2_lexdiv[2,]$TTR, 2)`) than after the Science Video (mean: `r round(e2_lexdiv[1,]$TTR, 2)`, $\beta=`r e2TTR["conditionexp"]`$, , 95% CI=[`r e2TTR['95pLB']`,`r e2TTR['95pUB']`]).
+We fit a Bayesian mixed-effects linear regression predicting TTR as a function of age (centered) and condition with an interaction term, and with random intercepts per video.
+There was lower TTR after the Activity Video (mean: `r round(e2_lexdiv[2,]$TTR, 2)`) than after the Science Video (mean: `r round(e2_lexdiv[1,]$TTR, 2)`, $\beta=`r e2TTR["conditionexp"]`$, , 95% CI=[`r e2TTR['95pLB']`,`r e2TTR['95pUB']`]).
 There was no significant effect of age, nor a significant interaction.
@@
 In the regression predicting the number of episodes of JA, there was a significant main effect of condition ($\beta=`r e2tjaCond["ConditionActivity Video"]`$, 95% CI = [`r e2tjaCond["95pLB"]`,`r e2tjaCond["95pUB"]`]), with more episodes of JA occurring after the Activity Video (mean: `r round(subset(e2_tja, Condition=="Activity Video")$mean,2)`, 95% CI: [`r round(subset(e2_tja, Condition=="Activity Video")$ci_lower,2)`, `r round(subset(e2_tja, Condition=="Activity Video")$ci_upper,2)`]) than after the Control Video (mean: `r round(subset(e2_tja, Condition=="Science Video")$mean,2)`, 95% CI: [`r round(subset(e2_tja, Condition=="Science Video")$ci_lower,2)`, `r round(subset(e2_tja, Condition=="Science Video")$ci_upper,2)`]).
-There was also a significant main effect of age ($\beta=`r e2tjaAge["age"]`$, 95% CI = [`r e2tjaAge["95pLB"]`,`r e2tjaAge["95pUB"]`]), showing that the number of episodes of JA decreased with the child's age.
+There was also a significant main effect of age ($\beta=`r e2tjaAge["age"]`$, 95% CI = [`r e2tjaAge["95pLB"]`,`r e2tjaAge["95pUB"]`]), showing that older children participated in fewer episodes of JA.
 However, a significant interaction of age and condition ($\beta=`r e2tjaAgeCond["age:ConditionActivity Video"]`$, 95% CI = [`r e2tjaAgeCond["95pLB"]`,`r e2tjaAgeCond["95pUB"]`]), shown in Figure \ref{fig:JA} (right bottom), demonstrates that there were more episodes of JA for older children in the Activity Video condition (comparable to episodes of JA for younger children).
@@
 The regression predicting the total duration of passive JA revealed a main effect of age ($\beta=`r e2pjat["age"]`$, 95% CI = [`r e2pjat["95pLB"]`,`r e2pjat["95pUB"]`]), revealing that older children spent more time in passive JA with their caregiver.
-Overall, these results show that the older children in our sample engage in more and longer episodes of joint attention with their caregivers, and suggest that the Activity Video strengthened this trend in the number of episodes of coordinated JA.
+Overall, these results show that the older children in our sample engage in more and longer episodes of joint attention with their caregivers, and that activity videos in particular lead to more episodes of coordinated JA.
 
@@
 
+```{r meta-analysis, include=F}
+
+```
+
 # Discussion
 
-This study investigated how parents change their interactions with their young children on the basis of one of several short video parenting messages from a commercial parenting app, which suggest interactive toy-based activities (e.g., learning animal sounds), along with a scientific justification.
-Parents in the control conditions received either no video (Experiment 1) or a video of a recent finding in developmental psychology (Experiment 2), and then played with their child for three minutes using the same sets of toys given to those in the experimental conditions.
-The quality of parents' interactions with their children were measured by the lexical diversity of their child-directed speech, and through behavioral coding of bids for and episodes of joint attention (JA).
-
-Experiment 1 investigated 6--24-month-olds, and found a greater number of bids for JA from parents after watching the activity video, but no difference in the number of JA episodes. 
-Experiment 2 (12--24-month-olds) replicated this greater number of bids for JA after the activity video, and moreover found that while the number of JA episodes dwindled for older infants in the control condition, dyads in the activity video condition achieved an overall higher and constant number of JA episodes.
+This study investigated whether and how digital parenting advice alters parents' interactions with their toddlers during a 3-minute play period.
+In Experiment 1, parents of 6--24-month-olds made more bids for JA after watching the activity video as compared to no video, which was also found in the parents of 12--24-month-olds in Experiment 2 in comparison to a science video control.
+Experiment 2 moreover found fewer JA episodes for parents of older infants after a science video, while parents of older children engaged in more JA after the activity video.
 In combination, these results suggest that short parenting messages suggesting activities can encourage parents to make more attempts to engage their child in joint attention, and that in some cases--especially in older children--these bids are successful in increasing engagement.
 
-Experiment 1 found lower lexical diversity in parents' speech after watching the activity video, but the average number of word tokens used was higher after the activity video, and the number of word types was the same in both conditions.
-Experiment 2 had similar lexical diversity results, finding suggestively lower Type-Token Ratio after the activity video, although the length-corrected lexical diversity measure (MTLD) did not differ significantly.
-However, neither the number of tokens nor the number of types significantly differed betwen conditions in Experiment 2. 
-Although it may at first blush seem worrisome that the activity videos lead to somewhat lower lexical diversity, this worry is  mitigated by the fact that this difference is explained not by fewer word types but by a greater number of word tokens used by parents after the activity video (significantly in Experiment 1, and numerically in Experiment 2).
-It may be that parents are relatively more repetitive after watching the activity video in their attempt to stick to the prescribed task, but overall they talk more.
+Both experiments also found that activity videos led to lower lexical diversity in parents' child-directed speech (TTR in both; MTLD only in Exp.
+1).
+However, activity videos resulted in parents using more word tokens (significant in Exp.
+1; numerical in Exp.
+2), while the number of word types did not differ significantly across conditions.
+Thus, although activity videos led to lower lexical diversity during play, this resulted not from fewer word types but from the use of more word tokens.
+Taken together with the greater number of bids for joint attention from parents, we suggest that the activity videos may lead parents to more persistently and repetitively attempt to engage their child in the prescribed activity.
+Indeed, the words identified by the corpus analysis as being words most characteristic of the activity videos were related to requests (e.g., "give", "put", "take"), whereas words characteristic of the control conditions were more invitational (e.g., "say", "let", "like").
 
-Taken together, the results of this study show that digital parenting interventions recommending particular play activities to parents of young children can influence both the quality and quantity of child-directed speech, as well as parents attempts to engage their children in joint attention---at least in the short term.
-Future studies should investigate whether these changes in parents' speech and attempts to engage their children continue after the treatment. 
+In sum, the results of this study show that digital parenting interventions recommending particular play activities to parents of young children can influence both the quality and quantity of child-directed speech, as well as parents attempts to engage their children in joint attention---at least in the short term.
+Future studies should investigate whether these changes in parents' speech and attempts to engage their children persist after the treatment. 
 Another target for future study is to determine whether, over a longer treatment period, children begin to respond to the increased bids for joint attention and greater number of tokens by engaging more with their parent, and perhaps even beginning to play differently.
@@
 ```
-
-```{r echo = FALSE, results = 'asis'}
-render_appendix('appendix.Rmd')
-```

### 2019-10-01 paper/manuscript.tex
re-did discussion

@@
 \textsuperscript{1} Department of Psychology, Stanford University\\\textsuperscript{2} Nextdoor, Inc.\\\textsuperscript{3} Gallaudet University\\\textsuperscript{4} Cornell University}
-\keywords{digital parenting advice; joint attention; lexical diversity; guided play\newline\indent Word count: 4569}
+\keywords{digital parenting advice; joint attention; lexical diversity; guided play\newline\indent Word count: 4576}
 \usepackage{csquotes}
@@
 There was significantly lower TTR in the Activity Video condition (mean: 0.32) than in the No Video condition (mean: 0.43, \(\beta=\)-0.11, 95\% CI={[}-0.16,-0.06{]}).
-There were no significant effects of age, gender, or parent's level of education.
-A similar Bayesian mixed-effects linear regression instead predicting MTLD also found significantly lower lexical diversity in the Activity Video condition (mean MTLD: 17.87) than in the No Video condition (mean: 27.09, \(\beta=\)-9.30, 95\% CI={[}-15.37,-3.18{]}), with no other significant effects.
+A similar regression instead predicting MTLD also found significantly lower lexical diversity in the Activity Video condition (mean MTLD: 17.87) than in the No Video condition (mean: 27.09, \(\beta=\)-9.30, 95\% CI={[}-15.37,-3.18{]}), with no other significant effects.
 Figure \ref{fig:lexdiv} shows the mean of each lexical diversity measure (TTR and MTLD) by condition.
 
-We also conducted similar regressions predicting the number of word tokens and types, finding only a significant effect of condition on the number of word tokens (\(\beta=\) 59.07, 95\% CI={[}19.58,97.44{]})), with parents using more words in the Activity Video condition (mean: 225, bootstrapped 95\% confidence intervals: {[}199,252{]}) than in the No Video condition (mean: 165, bootstrapped 95\% confidence intervals: {[}139,193{]}).
+We also conducted similar regressions predicting the number of word tokens and types, finding only a significant effect of condition on the number of word tokens (\(\beta=\) 59.07, 95\% CI={[}19.58,97.44{]}), with parents using more words in the Activity Video condition (mean: 225, bootstrapped 95\% confidence intervals: {[}199,252{]}) than in the No Video condition (mean: 165, bootstrapped 95\% confidence intervals: {[}139,193{]}).
 
@@
 
-We fit a mixed-effects linear regression predicting TTR as a function of age (centered) and condition with an interaction term, and with random intercepts per video using lme4 (Bates, Mächler, Bolker, \& Walker, 2015).
-There was suggestively lower TTR after the Activity Video (mean: 0.38) than after the Science Video (mean: 0.48, \(\beta=-0.09\), , 95\% CI={[}-0.16,-0.03{]}).
+We fit a Bayesian mixed-effects linear regression predicting TTR as a function of age (centered) and condition with an interaction term, and with random intercepts per video.
+There was lower TTR after the Activity Video (mean: 0.38) than after the Science Video (mean: 0.48, \(\beta=-0.09\), , 95\% CI={[}-0.16,-0.03{]}).
 There was no significant effect of age, nor a significant interaction.
@@
 In the regression predicting the number of episodes of JA, there was a significant main effect of condition (\(\beta=1.48\), 95\% CI = {[}0.15,2.78{]}), with more episodes of JA occurring after the Activity Video (mean: 8.80, 95\% CI: {[}7.97, 9.63{]}) than after the Control Video (mean: 7.33, 95\% CI: {[}6.58, 8.11{]}).
-There was also a significant main effect of age (\(\beta=-5\), 95\% CI = {[}-8.27,-1.41{]}), showing that the number of episodes of JA decreased with the child's age.
+There was also a significant main effect of age (\(\beta=-5\), 95\% CI = {[}-8.27,-1.41{]}), showing that older children participated in fewer episodes of JA.
 However, a significant interaction of age and condition (\(\beta=5.60\), 95\% CI = {[}0.46,10.37{]}), shown in Figure \ref{fig:JA} (right bottom), demonstrates that there were more episodes of JA for older children in the Activity Video condition (comparable to episodes of JA for younger children).
@@
 The regression predicting the total duration of passive JA revealed a main effect of age (\(\beta=-18.32\), 95\% CI = {[}-33.50,-2.91{]}), revealing that older children spent more time in passive JA with their caregiver.
-Overall, these results show that the older children in our sample engage in more and longer episodes of joint attention with their caregivers, and suggest that the Activity Video strengthened this trend in the number of episodes of coordinated JA.
+Overall, these results show that the older children in our sample engage in more and longer episodes of joint attention with their caregivers, and that activity videos in particular lead to more episodes of coordinated JA.
 
@@
 
-This study investigated how parents change their interactions with their young children on the basis of one of several short video parenting messages from a commercial parenting app, which suggest interactive toy-based activities (e.g., learning animal sounds), along with a scientific justification.
-Parents in the control conditions received either no video (Experiment 1) or a video of a recent finding in developmental psychology (Experiment 2), and then played with their child for three minutes using the same sets of toys given to those in the experimental conditions.
-The quality of parents' interactions with their children were measured by the lexical diversity of their child-directed speech, and through behavioral coding of bids for and episodes of joint attention (JA).
-
-Experiment 1 investigated 6--24-month-olds, and found a greater number of bids for JA from parents after watching the activity video, but no difference in the number of JA episodes.
-Experiment 2 (12--24-month-olds) replicated this greater number of bids for JA after the activity video, and moreover found that while the number of JA episodes dwindled for older infants in the control condition, dyads in the activity video condition achieved an overall higher and constant number of JA episodes.
+This study investigated whether and how digital parenting advice alters parents' interactions with their toddlers during a 3-minute play period.
+In Experiment 1, parents of 6--24-month-olds made more bids for JA after watching the activity video as compared to no video, which was also found in the parents of 12--24-month-olds in Experiment 2 in comparison to a science video control.
+Experiment 2 moreover found fewer JA episodes for parents of older infants after a science video, while parents of older children engaged in more JA after the activity video.
 In combination, these results suggest that short parenting messages suggesting activities can encourage parents to make more attempts to engage their child in joint attention, and that in some cases--especially in older children--these bids are successful in increasing engagement.
 
-Experiment 1 found lower lexical diversity in parents' speech after watching the activity video, but the average number of word tokens used was higher after the activity video, and the number of word types was the same in both conditions.
-Experiment 2 had similar lexical diversity results, finding suggestively lower Type-Token Ratio after the activity video, although the length-corrected lexical diversity measure (MTLD) did not differ significantly.
-However, neither the number of tokens nor the number of types significantly differed betwen conditions in Experiment 2.
-Although it may at first blush seem worrisome that the activity videos lead to somewhat lower lexical diversity, this worry is mitigated by the fact that this difference is explained not by fewer word types but by a greater number of word tokens used by parents after the activity video (significantly in Experiment 1, and numerically in Experiment 2).
-It may be that parents are relatively more repetitive after watching the activity video in their attempt to stick to the prescribed task, but overall they talk more.
+Both experiments also found that activity videos led to lower lexical diversity in parents' child-directed speech (TTR in both; MTLD only in Exp.
+1).
+However, activity videos resulted in parents using more word tokens (significant in Exp.
+1; numerical in Exp.
+2), while the number of word types did not differ significantly across conditions.
+Thus, although activity videos led to lower lexical diversity during play, this resulted not from fewer word types but from the use of more word tokens.
+Taken together with the greater number of bids for joint attention from parents, we suggest that the activity videos may lead parents to more persistently and repetitively attempt to engage their child in the prescribed activity.
+Indeed, the words identified by the corpus analysis as being words most characteristic of the activity videos were related to requests (e.g., \enquote{give}, \enquote{put}, \enquote{take}), whereas words characteristic of the control conditions were more invitational (e.g., \enquote{say}, \enquote{let}, \enquote{like}).
 
-Taken together, the results of this study show that digital parenting interventions recommending particular play activities to parents of young children can influence both the quality and quantity of child-directed speech, as well as parents attempts to engage their children in joint attention---at least in the short term.
-Future studies should investigate whether these changes in parents' speech and attempts to engage their children continue after the treatment.
+In sum, the results of this study show that digital parenting interventions recommending particular play activities to parents of young children can influence both the quality and quantity of child-directed speech, as well as parents attempts to engage their children in joint attention---at least in the short term.
+Future studies should investigate whether these changes in parents' speech and attempts to engage their children persist after the treatment.
 Another target for future study is to determine whether, over a longer treatment period, children begin to respond to the increased bids for joint attention and greater number of tokens by engaging more with their parent, and perhaps even beginning to play differently.
@@
 Baldwin, D. (1991). Infants' contribution to the achievement of joint reference. \emph{Child Development}, \emph{62}, 875--890.
-
-\leavevmode\hypertarget{ref-lme4}{}%
-Bates, D., Mächler, M., Bolker, B., \& Walker, S.
-(2015).
-Fitting linear mixed-effects models using lme4.
-\emph{Journal of Statistical Software}, \emph{67}(1), 1--48.
-\url{http://doi.org/10.18637/jss.v067.i01}
 

### 2019-10-01 paper/extra_text.R

@@ -61,3 +61,7 @@ An alternative might be that asking parents to focus on a specific activity that
 
 Exp 1 Discussion
 Demographics and EPAQ do not interact with condition, although there was a marginal effect of RR score on lexical diversity (lower diversity for higher RR scores), and marginal effects of parent education on word types and tokens (higher education yielding more types and tokens).
+
+Discussion
+
+Parents in the control conditions received either no video (Experiment 1) or a video of a recent finding in developmental psychology (Experiment 2), and then played with their child for three minutes using the same sets of toys given to those in the experimental conditions.

### 2019-10-03 paper/manuscript.Rmd
cleaned transcripts, rewrote discussion

@@
 keywords          : "digital parenting advice; joint attention; lexical diversity; guided play"
-wordcount         : "4576"
+wordcount         : "4706"
 
@@
 e1path = "../parenting_obs_e1/"
-load(paste(e1path,"Exp1_cleaned_data.RData",sep='')) # merged dataframe ready for plotting
+#load(paste(e1path,"Exp1_cleaned_data.RData",sep='')) # merged dataframe ready for plotting
+d <- read.csv(paste(e1path,"exp1_conditions2.csv",sep=''))
+
+d$MTLD = d$MTLD2
+d$TTR = d$TTR2
+d$types = d$types2
+d$tokens = d$tokens2
 
@@
   mutate(condition = factor(condition), 
-         MTLD = as.numeric(MTLD),
+         MTLD = as.numeric(MTLD2),
          EL = as.numeric(langcog::scale(EL, scale=FALSE)),
@@
 e2path = "../parenting_obs_e2/"
-load(paste(e2path,"Exp2_cleaned_data.RData",sep=''))
+#load(paste(e2path,"Exp2_cleaned_data.RData",sep=''))
+
+d <- read.csv(paste(e2path,"exp2_conditions2.csv",sep=''))
+d$MTLD = d$MTLD2
+d$TTR = d$TTR2
+d$types = d$types2
+d$tokens = d$tokens2
 
@@
 e2_parent_ed = table(d$parent_ed)
-e2_12to18 = nrow(subset(d, age<1.5))
+e2_12to18 = nrow(subset(d, age<1.5)) # wrong now that age is scaled
 e2_18to24 = nrow(subset(d, age>=1.5))
@@
 
-## Results
+## Results and Discussion
 
@@
 summary(modTTR) 
-e1TTR = get_stan_glmer_reporting_values(modTTR, "conditionexp") # -.11
+e1TTR = get_stan_glmer_reporting_values(modTTR, "conditionexp") # -.10
 
@@
 summary(modMTLD) 
-e1MTLD = get_stan_glmer_reporting_values(modMTLD, "conditionexp") # -9.19
+e1MTLD = get_stan_glmer_reporting_values(modMTLD, "conditionexp") # -6.27
 
@@
 summary(tokens_mod)
-e1tokens = get_stan_glmer_reporting_values(tokens_mod, "conditionexp") # 59.41
+e1tokens = get_stan_glmer_reporting_values(tokens_mod, "conditionexp") # 57.1
 
@@
 modTTRE <- stan_glmer(paste("TTR", e1model_string), data=e1ld)
-summary(modTTRE) #
+summary(modTTRE) # conditionexp, RR, genderM, parent_ed 
+get_stan_glmer_reporting_values(modTTRE, 'conditionexp') # -.11
 
@@
 For effects that are at least 95% likely to be non-zero according to the posterior distribution, we report estimated coefficients ($\beta$) as well as 95% Bayesian credible intervals (95% CI), demarcating the range within which 95% of the posterior predictive values fall.
-There was significantly lower TTR in the Activity Video condition (mean: `r round(subset(e1_lexdiv, condition=='exp')$TTR, 2)`) than in the No Video condition (mean: `r round(subset(e1_lexdiv, condition=='con')$TTR, 2)`, $\beta=$`r e1TTR["conditionexp"]`, 95% CI=[`r e1TTR['95pLB']`,`r e1TTR['95pUB']`]).
-A similar regression instead predicting MTLD also found significantly lower lexical diversity in the Activity Video condition (mean MTLD: `r round(subset(e1_lexdiv, condition=='exp')$MTLD, 2)`) than in the No Video condition (mean: `r round(subset(e1_lexdiv, condition=='con')$MTLD, 2)`, $\beta=$`r e1MTLD["conditionexp"]`, 95% CI=[`r e1MTLD['95pLB']`,`r e1MTLD['95pUB']`]), with no other significant effects.
+There was lower TTR in the Activity Video condition (mean: `r round(subset(e1_lexdiv, condition=='exp')$TTR, 2)`) than in the No Video condition (mean: `r round(subset(e1_lexdiv, condition=='con')$TTR, 2)`, $\beta=$`r e1TTR["conditionexp"]`, 95% CI=[`r e1TTR['95pLB']`,`r e1TTR['95pUB']`]).
+A similar regression instead predicting MTLD also found lower lexical diversity in the Activity Video condition (mean MTLD: `r round(subset(e1_lexdiv, condition=='exp')$MTLD, 2)`) than in the No Video condition (mean: `r round(subset(e1_lexdiv, condition=='con')$MTLD, 2)`, $\beta=$`r e1MTLD["conditionexp"]`, 95% CI=[`r e1MTLD['95pLB']`,`r e1MTLD['95pUB']`]), with no predicted influence of age.
 Figure \ref{fig:lexdiv} shows the mean of each lexical diversity measure (TTR and MTLD) by condition.
@@
 
-We also conducted similar regressions predicting the number of word tokens and types, finding only a significant effect of condition on the number of word tokens ($\beta=$ `r e1tokens["conditionexp"]`, 95% CI=[`r e1tokens['95pLB']`,`r e1tokens['95pUB']`]), with parents using more words in the Activity Video condition (mean: `r round(subset(e1_lexdiv, condition=='exp')$tokens, 0)`, bootstrapped 95% confidence intervals: [`r round(subset(e1_tok, Condition=="Activity Video")$ci_lower, 0)`,`r round(subset(e1_tok, Condition=="Activity Video")$ci_upper, 0)`]) than in the No Video condition (mean: `r round(subset(e1_lexdiv, condition=='con')$tokens, 0)`, bootstrapped 95% confidence intervals: [`r round(subset(e1_tok, Condition=="No Video")$ci_lower, 0)`,`r round(subset(e1_tok, Condition=="No Video")$ci_upper, 0)`]).
+We also conducted similar regressions predicting the number of word tokens and types, finding an effect of condition on the number of word tokens ($\beta=$ `r e1tokens["conditionexp"]`, 95% CI=[`r e1tokens['95pLB']`,`r e1tokens['95pUB']`]), with parents using more words in the Activity Video condition (mean: `r round(subset(e1_lexdiv, condition=='exp')$tokens, 0)`, bootstrapped 95% confidence intervals: [`r round(subset(e1_tok, Condition=="Activity Video")$ci_lower, 0)`,`r round(subset(e1_tok, Condition=="Activity Video")$ci_upper, 0)`]) than in the No Video condition (mean: `r round(subset(e1_lexdiv, condition=='con')$tokens, 0)`, bootstrapped 95% confidence intervals: [`r round(subset(e1_tok, Condition=="No Video")$ci_lower, 0)`,`r round(subset(e1_tok, Condition=="No Video")$ci_upper, 0)`]).
 
@@
 We fit a Bayesian mixed-effects linear regression predicting the number of bids for joint attention (JA) as a function of fixed effects of condition, age (centered), and their interaction, with random intercepts per video.
-There were significantly more bids for JA in the Activity Video condition (mean: `r round(subset(e1bids_M, Condition=="Activity Video")$mean,2)`, sd: `r round(subset(e1bids_M, Condition=="Activity Video")$sd,2)`) than in the No Video condition (mean: `r round(subset(e1bids_M, Condition=="No Video")$mean,2)`, sd: `r round(subset(e1bids_M, Condition=="No Video")$sd,2)`, $\beta=`r e1bids["ConditionActivity Video"]`$, 95% CI=[`r e1bids['95pLB']`,`r e1bids['95pUB']`]).
+There were more bids for JA in the Activity Video condition (mean: `r round(subset(e1bids_M, Condition=="Activity Video")$mean,2)`, sd: `r round(subset(e1bids_M, Condition=="Activity Video")$sd,2)`) than in the No Video condition (mean: `r round(subset(e1bids_M, Condition=="No Video")$mean,2)`, sd: `r round(subset(e1bids_M, Condition=="No Video")$sd,2)`, $\beta=`r e1bids["ConditionActivity Video"]`$, 95% CI=[`r e1bids['95pLB']`,`r e1bids['95pUB']`]).
 Mixed-effects regressions with the same structure were performed predicting the number of episodes of coordinated and passive JA, and the total duration of time spent in coordinated and passive JA.
-There were no significant effects on the number of or total duration of coordinated or passive JA episodes.
+There were no predicted effects on the number of or total duration of coordinated or passive JA episodes.
 Figure \@ref(fig:JA) (top) shows the mean number bids for JA and episodes of JA by condition in Experiment 1.
@@
 These models included random intercepts per video. 
-Of these exploratory regressions, only the regression predicting the number of passive JA episodes produced a significant effect involving these demographic variables: an interaction of condition and RR ($\beta=`r e1pjaE["ConditionActivity Video:RR"]`$, 95% CI=[`r e1pjaE['95pLB']`,`r e1pjaE['95pUB']`]), shows that for parents in the Activity Video condition, those with higher Rules and Respect subscores engaged in more passive JA episodes.
+Of these exploratory regressions, only the regression predicting the number of passive JA episodes showed an effect involving these demographic variables: an interaction of condition and RR ($\beta=`r e1pjaE["ConditionActivity Video:RR"]`$, 95% CI=[`r e1pjaE['95pLB']`,`r e1pjaE['95pUB']`]), shows that for parents in the Activity Video condition, those with higher Rules and Respect subscores engaged in more passive JA episodes.
 
@@
 
-## Discussion
+### Discussion
 
@@
 
-As preregistered, we fit mixed-effects linear regressions predicting the number of parental bids for joint attention and the total number of episodes of JA as a function of fixed effects of condition, age (centered), and their interaction, with random intercepts per video.
+We fit Bayesian mixed-effects linear regressions predicting the number of parental bids for joint attention and the total number of episodes of JA as a function of fixed effects of condition, age (centered), and their interaction, with random intercepts per video.
 Shown in Figure \ref{fig:JA} (left bottom), parents made significantly more bids for JA after watching the Activity Video (mean: `r round(subset(e2_bids, Condition=="Activity Video")$mean,2)`, bootstrapped 95% confidence intervals: `r round(subset(e2_bids, Condition=="Activity Video")$ci_lower,2)`, `r round(subset(e2_bids, Condition=="Activity Video")$ci_upper,2)`; $\beta=`r e2bids["ConditionActivity Video"]`$, 95% CI = [`r e2bids["95pLB"]`,`r e2bids["95pUB"]`]) than after the Science Video (mean: `r round(subset(e2_bids, Condition=="Science Video")$mean,2)`, 95% CI: [`r round(subset(e2_bids, Condition=="Science Video")$ci_lower,2)`, `r round(subset(e2_bids, Condition=="Science Video")$ci_upper,2)`]).
@@
 
-```{r meta-analysis, include=F}
+# General Discussion
 
-```
+We were interested in how digital parenting advice alters parents' interactions with their children. 
+We specifically set out to test whether activity suggestions lead to higher-quality play, a presupposition of many early parenting interventions. 
+Our experiments explored this question by randomly assigning parents to different advice conditions and then observing their behavior in short free-play sessions, with quality of play assessed through measures of parent language and joint attention.
+In two experiments, we found that activity videos increased parent bids for joint attention as compared with no video (Experiment 1) and a comparable science video (Experiment 2). 
+In some cases--especially in older children--these bids were successful in increasing engagement. 
+We also observed differences in parents' talk that were broadly similar across both experiments, with a greater quantity of language but a similar breadth of vocabulary (leading to lower measures of lexical diversity).
+Exploratory corpus analysis identified the words most characteristic of the activity videos as being related to requests (e.g., "give", "put", "take") whereas control conditions featured more invitational words (e.g., "say", "let", "like").
 
-# Discussion
+The short, activity-oriented parenting messages we used encouraged parents to make more attempts -- both verbal and non-verbal -- to engage their child, supporting their use as a component of interventions.
+Why were they successful? 
+When parents are asked to play with their children in the presence of new toys, they may choose to follow their child's lead and engage in free play.
+While free play is positive, it nevertheless results in less scaffolded activity than when parents are given a goal that suggests a repertoire of ways to guide their child. 
+Parents may also persist in providing opportunities for their child to complete the activity, leading to more repetitive language but also more offers of engagement.
 
-This study investigated whether and how digital parenting advice alters parents' interactions with their toddlers during a 3-minute play period.
-In Experiment 1, parents of 6--24-month-olds made more bids for JA after watching the activity video as compared to no video, which was also found in the parents of 12--24-month-olds in Experiment 2 in comparison to a science video control.
-Experiment 2 moreover found fewer JA episodes for parents of older infants after a science video, while parents of older children engaged in more JA after the activity video.
-In combination, these results suggest that short parenting messages suggesting activities can encourage parents to make more attempts to engage their child in joint attention, and that in some cases--especially in older children--these bids are successful in increasing engagement.
+Our study has a number of limitations related to design and sample, each of which suggests possible future directions. 
+First, our design was intentionally short and minimal; future studies should investigate whether changes in parents' speech and attempts to engage their children could persist across a longer timespan (perhaps with a broader set of activities being provisioned).
+A longer-term study would also be able to measure whether consistent increases in parent bids would lead children to respond by engaging more with their parent.
+Second, our design assumes that parents have access not only to activities but also to the materials to complete them; this assumption may be unrealistic for any parent, but especially for the parents who are most likely to be targeted for early parenting interventions.
+Providing materials may be critical for the success of activity suggestions. 
+Finally, our sample is a convenience sample drawn from a museum, but it skews towards higher socio-economic status households as well as those families who are well-disposed towards visiting a museum (perhaps because they value education) and are interested in participating in research.
+A key goal for future research is to assess the generality of these findings across populations.
 
-Both experiments also found that activity videos led to lower lexical diversity in parents' child-directed speech (TTR in both; MTLD only in Exp.
+<!-- Taken together with the greater number of bids for joint attention from parents, we suggest that the activity videos may lead parents to more persistently and repetitively attempt to engage their child in the prescribed activity.
+-->
+
+<!-- Both experiments also found that activity videos led to lower lexical diversity in parents' child-directed speech (TTR in both; MTLD only in Exp.
 1).
@@
 2), while the number of word types did not differ significantly across conditions.
-Thus, although activity videos led to lower lexical diversity during play, this resulted not from fewer word types but from the use of more word tokens.
-Taken together with the greater number of bids for joint attention from parents, we suggest that the activity videos may lead parents to more persistently and repetitively attempt to engage their child in the prescribed activity.
-Indeed, the words identified by the corpus analysis as being words most characteristic of the activity videos were related to requests (e.g., "give", "put", "take"), whereas words characteristic of the control conditions were more invitational (e.g., "say", "let", "like").
+-->
+<!-- Thus, although activity videos led to lower lexical diversity during play, this resulted not from fewer word types but from the use of more word tokens. -->
 
-In sum, the results of this study show that digital parenting interventions recommending particular play activities to parents of young children can influence both the quality and quantity of child-directed speech, as well as parents attempts to engage their children in joint attention---at least in the short term.
-Future studies should investigate whether these changes in parents' speech and attempts to engage their children persist after the treatment. 
-Another target for future study is to determine whether, over a longer treatment period, children begin to respond to the increased bids for joint attention and greater number of tokens by engaging more with their parent, and perhaps even beginning to play differently.
+In sum, the results of this study show that digital parenting videos recommending play activities can lead to short-term increases in parents' attempts to engage their young children, both verbally and non-verbally.
 

### 2019-10-03 paper/manuscript.tex
cleaned transcripts, rewrote discussion

@@
 
-\hypertarget{results}{%
-\subsection{Results}\label{results}}
+\hypertarget{results-and-discussion}{%
+\subsection{Results and Discussion}\label{results-and-discussion}}
 
@@
 For effects that are at least 95\% likely to be non-zero according to the posterior distribution, we report estimated coefficients (\(\beta\)) as well as 95\% Bayesian credible intervals (95\% CI), demarcating the range within which 95\% of the posterior predictive values fall.
-There was significantly lower TTR in the Activity Video condition (mean: 0.32) than in the No Video condition (mean: 0.43, \(\beta=\)-0.11, 95\% CI={[}-0.16,-0.06{]}).
-A similar regression instead predicting MTLD also found significantly lower lexical diversity in the Activity Video condition (mean MTLD: 17.87) than in the No Video condition (mean: 27.09, \(\beta=\)-9.30, 95\% CI={[}-15.37,-3.18{]}), with no other significant effects.
+There was significantly lower TTR in the Activity Video condition (mean: 0.32) than in the No Video condition (mean: 0.42, \(\beta=\)-0.10, 95\% CI={[}-0.15,-0.05{]}).
+A similar regression instead predicting MTLD also found significantly lower lexical diversity in the Activity Video condition (mean MTLD: 16.81) than in the No Video condition (mean: 23.04, \(\beta=\)-6.27, 95\% CI={[}-11.54,-1.03{]}), with no other significant effects.
 Figure \ref{fig:lexdiv} shows the mean of each lexical diversity measure (TTR and MTLD) by condition.
 
-We also conducted similar regressions predicting the number of word tokens and types, finding only a significant effect of condition on the number of word tokens (\(\beta=\) 59.07, 95\% CI={[}19.58,97.44{]}), with parents using more words in the Activity Video condition (mean: 225, bootstrapped 95\% confidence intervals: {[}199,252{]}) than in the No Video condition (mean: 165, bootstrapped 95\% confidence intervals: {[}139,193{]}).
+We also conducted similar regressions predicting the number of word tokens and types, finding only a significant effect of condition on the number of word tokens (\(\beta=\) 56.94, 95\% CI={[}17.67,95.19{]}), with parents using more words in the Activity Video condition (mean: 228, bootstrapped 95\% confidence intervals: {[}199,252{]}) than in the No Video condition (mean: 169, bootstrapped 95\% confidence intervals: {[}139,193{]}).
 
@@
 \hypertarget{discussion}{%
-\subsection{Discussion}\label{discussion}}
+\subsubsection{Discussion}\label{discussion}}
 
@@
 
-84 infants (F = 36, M = 46) aged 12-24 months (41 12-17.9 month-olds, 43 18-24 month-olds) and their parents participated in the same museum as Experiment 1.
+84 infants (F = 36, M = 46) aged 12-24 months (84 12-17.9 month-olds, 0 18-24 month-olds) and their parents participated in the same museum as Experiment 1.
 We included infants who were exposed to English at least 75 percent of the time or who were exposed less but whose participating parent reported that they primarily speak English with their child at home.
@@
 Sixteen parents reported their child was of Hispanic origin.
-Parents tended to be highly-educated, with reports of highest level of education ranging from some college (n = 5), four-year college (n = 28), some graduate school (n = 2), to completed graduate school (n = 36) or declined to state (n = 13).
+Parents tended to be highly-educated, with reports of highest level of education ranging from some college (n = 2), four-year college (n = 36), some graduate school (n = NA), to completed graduate school (n = NA) or declined to state (n = 13).
 
@@
 
-\hypertarget{results-1}{%
-\subsection{Results}\label{results-1}}
+\hypertarget{results-and-discussion-1}{%
+\subsection{Results and Discussion}\label{results-and-discussion-1}}
 
@@
 
-As preregistered, we fit mixed-effects linear regressions predicting the number of parental bids for joint attention and the total number of episodes of JA as a function of fixed effects of condition, age (centered), and their interaction, with random intercepts per video.
+We fit Bayesian mixed-effects linear regressions predicting the number of parental bids for joint attention and the total number of episodes of JA as a function of fixed effects of condition, age (centered), and their interaction, with random intercepts per video.
 Shown in Figure \ref{fig:JA} (left bottom), parents made significantly more bids for JA after watching the Activity Video (mean: 12.96, bootstrapped 95\% confidence intervals: 11.79, 14.24; \(\beta=3.07\), 95\% CI = {[}1.15,5.06{]}) than after the Science Video (mean: 9.89, 95\% CI: {[}8.73, 11.10{]}).
@@
 
-\hypertarget{discussion-1}{%
-\section{Discussion}\label{discussion-1}}
+\hypertarget{general-discussion}{%
+\section{General Discussion}\label{general-discussion}}
 
-This study investigated whether and how digital parenting advice alters parents' interactions with their toddlers during a 3-minute play period.
-In Experiment 1, parents of 6--24-month-olds made more bids for JA after watching the activity video as compared to no video, which was also found in the parents of 12--24-month-olds in Experiment 2 in comparison to a science video control.
-Experiment 2 moreover found fewer JA episodes for parents of older infants after a science video, while parents of older children engaged in more JA after the activity video.
-In combination, these results suggest that short parenting messages suggesting activities can encourage parents to make more attempts to engage their child in joint attention, and that in some cases--especially in older children--these bids are successful in increasing engagement.
+We were interested in how digital parenting advice alters parents' interactions with their children.
+We specifically set out to test whether activity suggestions lead to higher-quality play, a presupposition of many early parenting interventions.
+Our experiments explored this question by randomly assigning parents to different advice conditions and then observing their behavior in short free-play sessions, with quality of play assessed through measures of parent language and joint attention.
+In two experiments, we found that activity videos increased parent bids for joint attention as compared with no video (Experiment 1) and a comparable science video (Experiment 2).
+In some cases--especially in older children--these bids were successful in increasing engagement.
+We also observed differences in parents' talk that were broadly similar across both experiments, with a greater quantity of language but a similar breadth of vocabulary (leading to lower measures of lexical diversity).
+Exploratory corpus analysis identified the words most characteristic of the activity videos as being related to requests (e.g., \enquote{give}, \enquote{put}, \enquote{take}) whereas control conditions featured more invitational words (e.g., \enquote{say}, \enquote{let}, \enquote{like}).
 
-Both experiments also found that activity videos led to lower lexical diversity in parents' child-directed speech (TTR in both; MTLD only in Exp.
-1).
-However, activity videos resulted in parents using more word tokens (significant in Exp.
-1; numerical in Exp.
-2), while the number of word types did not differ significantly across conditions.
-Thus, although activity videos led to lower lexical diversity during play, this resulted not from fewer word types but from the use of more word tokens.
-Taken together with the greater number of bids for joint attention from parents, we suggest that the activity videos may lead parents to more persistently and repetitively attempt to engage their child in the prescribed activity.
-Indeed, the words identified by the corpus analysis as being words most characteristic of the activity videos were related to requests (e.g., \enquote{give}, \enquote{put}, \enquote{take}), whereas words characteristic of the control conditions were more invitational (e.g., \enquote{say}, \enquote{let}, \enquote{like}).
+The short, activity-oriented parenting messages we used encouraged parents to make more attempts -- both verbal and non-verbal -- to engage their child, supporting their use as a component of interventions.
+Why were they successful?
+When parents are asked to play with their children in the presence of new toys, they may choose to follow their child's lead and engage in free play.
+While free play is positive, it nevertheless results in less scaffolded activity than when parents are given a goal that suggests a repertoire of ways to guide their child.
+Parents may also persist in providing opportunities for their child to complete the activity, leading to more repetitive language but also more offers of engagement.
 
-In sum, the results of this study show that digital parenting interventions recommending particular play activities to parents of young children can influence both the quality and quantity of child-directed speech, as well as parents attempts to engage their children in joint attention---at least in the short term.
-Future studies should investigate whether these changes in parents' speech and attempts to engage their children persist after the treatment.
-Another target for future study is to determine whether, over a longer treatment period, children begin to respond to the increased bids for joint attention and greater number of tokens by engaging more with their parent, and perhaps even beginning to play differently.
+Our study has a number of limitations related to design and sample, each of which suggests possible future directions.
+First, our design was intentionally short and minimal; future studies should investigate whether changes in parents' speech and attempts to engage their children could persist across a longer timespan (perhaps with a broader set of activities being provisioned).
+A longer-term study would also be able to measure whether consistent increases in parent bids would lead children to respond by engaging more with their parent.
+Second, our design assumes that parents have access not only to activities but also to the materials to complete them; this assumption may be unrealistic for any parent, but especially for the parents who are most likely to be targeted for early parenting interventions.
+Providing materials may be critical for the success of activity suggestions.
+Finally, our sample is a convenience sample drawn from a museum, but it skews towards higher socio-economic status households as well as those families who are well-disposed towards visiting a museum (perhaps because they value education) and are interested in participating in research.
+A key goal for future research is to assess the generality of these findings across populations.
+
+In sum, the results of this study show that digital parenting videos recommending play activities can lead to short-term increases in parents' attempts to engage their young children, both verbally and non-verbally.
 

### 2019-10-04 paper/manuscript.Rmd
clean up discussion and tweak figure

@@
 keywords          : "digital parenting advice; joint attention; lexical diversity; guided play"
-wordcount         : "4706"
+wordcount         : "4629"
 
@@
 e1path = "../parenting_obs_e1/"
-#load(paste(e1path,"Exp1_cleaned_data.RData",sep='')) # merged dataframe ready for plotting
-d <- read.csv(paste(e1path,"exp1_conditions2.csv",sep=''))
-
-d$MTLD = d$MTLD2
-d$TTR = d$TTR2
-d$types = d$types2
-d$tokens = d$tokens2
+load(paste(e1path,"Exp1_cleaned_data.RData",sep='')) # merged dataframe ready for plotting
+e1_parent_ed = table(d$parent_ed)
+#d <- read.csv(paste(e1path,"exp1_conditions2.csv",sep=''))
+d = read.csv("exp1_lexical_diversity_data.csv")
 
 e1ld <- d %>%
-  #filter(!is.na(AA), !is.na(EL), !is.na(RR))%>%
   mutate(condition = factor(condition), 
-         MTLD = as.numeric(MTLD2),
-         EL = as.numeric(langcog::scale(EL, scale=FALSE)),
-         AA = as.numeric(langcog::scale(AA, scale=FALSE)),
-         RR = as.numeric(langcog::scale(RR, scale=FALSE)),
-         age = as.numeric(langcog::scale(age, scale=FALSE)),
-         parent_ed = as.numeric(langcog::scale(parent_ed, scale=T)),
          gender = as.factor(gender),
@@
 e1_gender = table(e1ld$gender)
-#table(cut_interval(d$age, n=2, breaks=c(.5,1.5,2.1), labels=F))
-#table(cut_number(d$age, n=3, breaks=c(.5,1.5,2.1)))
-e1_parent_ed = table(e1ld$parent_ed)
 ```
@@
          age = as.numeric(langcog::scale(age, scale=FALSE)),
+         parent_ed = langcog::scale(parent_ed, scale=TRUE),
          gender = as.factor(gender),
@@
 e2path = "../parenting_obs_e2/"
-#load(paste(e2path,"Exp2_cleaned_data.RData",sep=''))
-
-d <- read.csv(paste(e2path,"exp2_conditions2.csv",sep=''))
-d$MTLD = d$MTLD2
-d$TTR = d$TTR2
-d$types = d$types2
-d$tokens = d$tokens2
+load(paste(e2path,"Exp2_cleaned_data.RData",sep=''))
+e2_parent_ed = table(d$parent_ed) # unscaled parent_ed
+d = read.csv("exp2_lexical_diversity_data.csv")
 
 e2data <- d %>%
-  mutate(condition = factor(condition), 
-         MTLD = as.numeric(MTLD),
-         TTR = as.numeric(TTR),
-         age = as.numeric(langcog::scale(age, scale=FALSE)),
+  mutate(condition = as.factor(condition), 
+         gender = as.factor(gender),
          video = as.factor(video))
@@
 e2_gender = table(d$gender)
-e2_ethnicity = table(d$ethnicity)
-e2_parent_ed = table(d$parent_ed)
-e2_12to18 = nrow(subset(d, age<1.5)) # wrong now that age is scaled
-e2_18to24 = nrow(subset(d, age>=1.5))
+e2_12to18 = nrow(subset(d, Age<1.5)) # wrong now that age is scaled
+e2_18to24 = nrow(subset(d, Age>=1.5))
 ```
@@
   ci95 <- posterior_interval(model, prob = 0.95, pars = cond)
-  ci = round(ci95, digits)
-  names(ci) = c("95pLB","95pUB") # 95% lower and upper bounds
+  ci89 <- posterior_interval(model, prob = 0.89, pars = cond) # 89% CIs as recommended by Kruschke and others
+  ci = round(c(ci95,ci89), digits)
+  names(ci) = c("95pLB","95pUB","89pLB","89pUB") # 95% and 89% lower and upper bounds
   beta = round(model$coefficients[cond], digits)
@@
 
-We also conducted similar regressions predicting the number of word tokens and types, finding an effect of condition on the number of word tokens ($\beta=$ `r e1tokens["conditionexp"]`, 95% CI=[`r e1tokens['95pLB']`,`r e1tokens['95pUB']`]), with parents using more words in the Activity Video condition (mean: `r round(subset(e1_lexdiv, condition=='exp')$tokens, 0)`, bootstrapped 95% confidence intervals: [`r round(subset(e1_tok, Condition=="Activity Video")$ci_lower, 0)`,`r round(subset(e1_tok, Condition=="Activity Video")$ci_upper, 0)`]) than in the No Video condition (mean: `r round(subset(e1_lexdiv, condition=='con')$tokens, 0)`, bootstrapped 95% confidence intervals: [`r round(subset(e1_tok, Condition=="No Video")$ci_lower, 0)`,`r round(subset(e1_tok, Condition=="No Video")$ci_upper, 0)`]).
+We also conducted similar regressions predicting the number of word tokens and types, finding an effect of condition on the number of word tokens ($\beta=$ `r e1tokens["conditionexp"]`, 95% CI=[`r e1tokens['95pLB']`,`r e1tokens['95pUB']`]), with parents using more words in the Activity Video condition (mean: `r round(subset(e1_lexdiv, condition=='exp')$tokens, 0)`, bootstrapped 95% confidence interval (conf.
+int.): [`r round(subset(e1_tok, Condition=="Activity Video")$ci_lower, 0)`,`r round(subset(e1_tok, Condition=="Activity Video")$ci_upper, 0)`]) than in the No Video condition (mean: `r round(subset(e1_lexdiv, condition=='con')$tokens, 0)`, 95% conf.
+int.: [`r round(subset(e1_tok, Condition=="No Video")$ci_lower, 0)`,`r round(subset(e1_tok, Condition=="No Video")$ci_upper, 0)`]).
 
@@
 e1bids_modE <- stan_glmer(paste("bids_tot", model_stringE), data = e1ja) 
-summary(e1bids_modE) # cond, gender close
+summary(e1bids_modE) # cond, almost gender
 
@@
 summary(e1pja_modE) # condition*RR beta=1.8, RR close
-get_stan_glmer_reporting_values(e1pja_modE, "RR") # -1.08, 95% CI = [-2.18,0.07]
+get_stan_glmer_reporting_values(e1pja_modE, "RR") # -1.09, 95% CI = [-2.22,0.07] % report % posterior <0?
 e1pjaE = get_stan_glmer_reporting_values(e1pja_modE, "ConditionActivity Video:RR")
@@
 To better understand the intervention's effect on language use, we analyzed which words are characteristic of parents' speech in each condition, comparing the differency in frequency rank of each word (lemma) in the two conditions, as well as contrasting the corpus overall with a general English-language word frequency list (see SI for the interactive corpus characteristic plot).
-Words that are strongly indicative of being from the Activity Video condition include "give", "big", "small", "thank", "have", "which", and "school", while words that are most characteristic of the No Video condition include "ready", "on", "oh", "see", "going", "let", and "are".
+Words that are strongly indicative of being from the Activity Video condition include "give", "big", "small", "ribbit", "thank", "have", and "bus", while words that are most characteristic of the No Video condition include "shake", "ready", "oh", "on", "going", "going", "see", "let", and the child's name.
 
@@
   scale_fill_manual(values=sol_colors) + ggthemes::theme_few() + ggtitle("Experiment 2") + small_text +
-  theme(legend.key.height=unit(1.2, "cm"), legend.text=element_text(size=9))
+  theme(legend.position="none")
+  #theme(legend.key.height=unit(1.2, "cm"), legend.text=element_text(size=9))
 
@@
   xlab("Age (years)") + ylab("Total Episodes of Joint Attention") +
-  ggthemes::theme_few() + ggtitle(" ") + small_text + theme(legend.position="none")
+  ggthemes::theme_few() + ggtitle(" ") + small_text + 
+  theme(legend.position="bottom", legend.text=element_text(size=9), 
+        legend.margin=margin(0,0,5,0),
+        legend.box.margin=margin(-10,-10,-5,-10))
+  #theme(legend.position="none")
 
@@
 multiplot(e1bids, e1tja, e2bids, e2tja_age, 
-          cols=6, layout=matrix(c(1,1,1,2,2,2, 3,3,3,4,4,4), nrow=2, byrow=T)) 
+          cols=6, layout=matrix(c(1,1,1,2,2,2, 3,3,4,4,4,4), nrow=2, byrow=T)) 
 ```
@@
 Thank you!"), whereas after no intervention parents' language related more to invitations (e.g., "Are you ready?" / "Let's see.").
-However, parents who watched an activity video also made significantly more bids for JA with their child, although this did not result in a greater number of successful episodes of JA--passive or coordinated--than dyads in the no video condition.
+However, parents who watched an activity video also made more bids for JA with their child, although this did not result in a greater number of successful episodes of JA--passive or coordinated--than dyads in the No Video condition.
 In sum, the results of Experiment 1 suggest that digital parenting advice can increase parents' efforts to engage their child in joint attention, the volume if not diversity of their speech, and can shift the type of speech acts towards more requests.
@@
 We fit a Bayesian mixed-effects linear regression predicting TTR as a function of age (centered) and condition with an interaction term, and with random intercepts per video.
-There was lower TTR after the Activity Video (mean: `r round(e2_lexdiv[2,]$TTR, 2)`) than after the Science Video (mean: `r round(e2_lexdiv[1,]$TTR, 2)`, $\beta=`r e2TTR["conditionexp"]`$, , 95% CI=[`r e2TTR['95pLB']`,`r e2TTR['95pUB']`]).
-There was no significant effect of age, nor a significant interaction.
-The preregistered regression predicting the number of tokens used by parents revealed no significant effects. 
-An exploratory mixed-effects linear regression predicting MTLD found no significant effects of age or condition.
+This revealed lower TTR after the Activity Video (mean: `r round(e2_lexdiv[2,]$TTR, 2)`) than after the Science Video (mean: `r round(e2_lexdiv[1,]$TTR, 2)`, $\beta=`r e2TTR["conditionexp"]`$, , 95% CI=[`r e2TTR['95pLB']`,`r e2TTR['95pUB']`]).
+The preregistered regression predicting the number of tokens used by parents revealed no effects. 
+An exploratory mixed-effects linear regression predicting MTLD found no effect of age or condition.
 Figure \ref{fig:lexdiv} (bottom left and middle) shows the mean of each lexical diversity measure (TTR and MTLD) by condition.
-Regressions with the same structure predicting the number of words tokens found no significant effects of age or condition.
+Regressions with the same structure predicting the number of words tokens found no effect of age or condition.
 The means of the lexical measures are shown in Table \ref{e2tab}.
@@
 e2bids_m <- stan_lmer(bids ~ age * Condition + (1|video), data=e2ja)
-summary(e2bids_m) # significant effect of condition! mean=3.1, 95%CI = [1.1, 5.0]
+summary(e2bids_m) # condition mean=3.1, 95%CI = [1.1, 5.0]
 e2bids <- get_stan_glmer_reporting_values(e2bids_m, "ConditionActivity Video")
@@
 We fit Bayesian mixed-effects linear regressions predicting the number of parental bids for joint attention and the total number of episodes of JA as a function of fixed effects of condition, age (centered), and their interaction, with random intercepts per video.
-Shown in Figure \ref{fig:JA} (left bottom), parents made significantly more bids for JA after watching the Activity Video (mean: `r round(subset(e2_bids, Condition=="Activity Video")$mean,2)`, bootstrapped 95% confidence intervals: `r round(subset(e2_bids, Condition=="Activity Video")$ci_lower,2)`, `r round(subset(e2_bids, Condition=="Activity Video")$ci_upper,2)`; $\beta=`r e2bids["ConditionActivity Video"]`$, 95% CI = [`r e2bids["95pLB"]`,`r e2bids["95pUB"]`]) than after the Science Video (mean: `r round(subset(e2_bids, Condition=="Science Video")$mean,2)`, 95% CI: [`r round(subset(e2_bids, Condition=="Science Video")$ci_lower,2)`, `r round(subset(e2_bids, Condition=="Science Video")$ci_upper,2)`]).
-There were no other significant effects on parental bids for JA.
+Shown in Figure \ref{fig:JA} (left bottom), parents made notably more bids for JA after watching the Activity Video (mean: `r round(subset(e2_bids, Condition=="Activity Video")$mean,2)`, 95% conf.
+int.: `r round(subset(e2_bids, Condition=="Activity Video")$ci_lower,2)`, `r round(subset(e2_bids, Condition=="Activity Video")$ci_upper,2)`; $\beta=`r e2bids["ConditionActivity Video"]`$, 95% CI = [`r e2bids["95pLB"]`,`r e2bids["95pUB"]`]) than after the Science Video (mean: `r round(subset(e2_bids, Condition=="Science Video")$mean,2)`, 95% conf.
+int.: [`r round(subset(e2_bids, Condition=="Science Video")$ci_lower,2)`, `r round(subset(e2_bids, Condition=="Science Video")$ci_upper,2)`]).
+There were no other effects on parental bids for JA.
 
-In the regression predicting the number of episodes of JA, there was a significant main effect of condition ($\beta=`r e2tjaCond["ConditionActivity Video"]`$, 95% CI = [`r e2tjaCond["95pLB"]`,`r e2tjaCond["95pUB"]`]), with more episodes of JA occurring after the Activity Video (mean: `r round(subset(e2_tja, Condition=="Activity Video")$mean,2)`, 95% CI: [`r round(subset(e2_tja, Condition=="Activity Video")$ci_lower,2)`, `r round(subset(e2_tja, Condition=="Activity Video")$ci_upper,2)`]) than after the Control Video (mean: `r round(subset(e2_tja, Condition=="Science Video")$mean,2)`, 95% CI: [`r round(subset(e2_tja, Condition=="Science Video")$ci_lower,2)`, `r round(subset(e2_tja, Condition=="Science Video")$ci_upper,2)`]).
-There was also a significant main effect of age ($\beta=`r e2tjaAge["age"]`$, 95% CI = [`r e2tjaAge["95pLB"]`,`r e2tjaAge["95pUB"]`]), showing that older children participated in fewer episodes of JA.
-However, a significant interaction of age and condition ($\beta=`r e2tjaAgeCond["age:ConditionActivity Video"]`$, 95% CI = [`r e2tjaAgeCond["95pLB"]`,`r e2tjaAgeCond["95pUB"]`]), shown in Figure \ref{fig:JA} (right bottom), demonstrates that there were more episodes of JA for older children in the Activity Video condition (comparable to episodes of JA for younger children).
+The regression predicting the number of episodes of JA revealed an effect of condition ($\beta=`r e2tjaCond["ConditionActivity Video"]`$, 95% CI = [`r e2tjaCond["95pLB"]`,`r e2tjaCond["95pUB"]`]), with more episodes of JA occurring after the Activity Video (mean: `r round(subset(e2_tja, Condition=="Activity Video")$mean,2)`, 95% conf.
+int.: [`r round(subset(e2_tja, Condition=="Activity Video")$ci_lower,2)`, `r round(subset(e2_tja, Condition=="Activity Video")$ci_upper,2)`]) than after the Control Video (mean: `r round(subset(e2_tja, Condition=="Science Video")$mean,2)`, 95% conf.
+int.: [`r round(subset(e2_tja, Condition=="Science Video")$ci_lower,2)`, `r round(subset(e2_tja, Condition=="Science Video")$ci_upper,2)`]).
+Older children also participated in fewer episodes of JA ($\beta=`r e2tjaAge["age"]`$, 95% CI = [`r e2tjaAge["95pLB"]`,`r e2tjaAge["95pUB"]`]). 
+However, this age effect was moderated in the Activity Video condition ($\beta=`r e2tjaAgeCond["age:ConditionActivity Video"]`$, 95% CI = [`r e2tjaAgeCond["95pLB"]`,`r e2tjaAgeCond["95pUB"]`]): shown in Figure \ref{fig:JA} (right bottom), older children did not engage in fewer episodes of JA after an activity video.
 
@@
 e2pjat_m <- stan_lmer(pja_length ~ age * Condition + (1|video), data=e2ja)
-summary(e2pjat_m) # age: est: -17.9 95% CI = [-33.1,-2.2] 
+summary(e2pjat_m) # age: est: -17.97 95% CI = [-33.37,-2.41] 
 e2pjat <- get_stan_glmer_reporting_values(e2pjat_m, "age")
@@
 e2cjat_m <- stan_glmer(cja_length ~ age * Condition + (1|video), data=e2ja)
-summary(e2cjat_m) # age: est: 35.3 95% CI = [-6.1,77.4] ns
+summary(e2cjat_m) # age: est: 35.3 89% CI = [1.57,67.4] 
+e2cjat <- get_stan_glmer_reporting_values(e2cjat_m, "age")
 
@@
 Four additional exploratory regressions with a similar structure were carried out to predict the number and duration of coordinated and passive JA episodes.
-The regression predicting the number of episodes of coordinated JA found a significant main effect of condition ($\beta=`r e2cjaCond["ConditionActivity Video"]`$, 95% CI = [`r e2cjaCond["95pLB"]`,`r e2cjaCond["95pUB"]`]), with more episodes of coordinated JA occurring after the Activity Video (mean: `r round(subset(e2_cja, Condition=="Activity Video")$mean,2)`, 95% CI: [`r round(subset(e2_cja, Condition=="Activity Video")$ci_lower,2)`, `r round(subset(e2_cja, Condition=="Activity Video")$ci_upper,2)`]) than after the Control Video (mean: `r round(subset(e2_cja, Condition=="Science Video")$mean,2)`, 95% CI: [`r round(subset(e2_cja, Condition=="Science Video")$ci_lower,2)`, `r round(subset(e2_cja, Condition=="Science Video")$ci_upper,2)`]).
-There was no significant effect of age, but there was a significant interaction of age and condition ($\beta=`r e2cjaAgeCond["age:ConditionActivity Video"]`$, 95% CI = [`r e2cjaAgeCond["95pLB"]`,`r e2cjaAgeCond["95pUB"]`]), shown in Figure \ref{fig:e2ja-coord}, revealing that older children in the Activity Video condition had more episodes of coordinated JA than children in the Control Video condition.
-The regression predicting the total duration of coordinated JA episodes revealed no significant effects.
+The regression predicting the number of episodes of coordinated JA found an effect of condition ($\beta=`r e2cjaCond["ConditionActivity Video"]`$, 95% CI = [`r e2cjaCond["95pLB"]`,`r e2cjaCond["95pUB"]`]), with more episodes of coordinated JA occurring after the Activity Video (mean: `r round(subset(e2_cja, Condition=="Activity Video")$mean,2)`, 95% CI: [`r round(subset(e2_cja, Condition=="Activity Video")$ci_lower,2)`, `r round(subset(e2_cja, Condition=="Activity Video")$ci_upper,2)`]) than after the Control Video (mean: `r round(subset(e2_cja, Condition=="Science Video")$mean,2)`, 95% CI: [`r round(subset(e2_cja, Condition=="Science Video")$ci_lower,2)`, `r round(subset(e2_cja, Condition=="Science Video")$ci_upper,2)`]).
+There was an interaction of age and condition ($\beta=`r e2cjaAgeCond["age:ConditionActivity Video"]`$, 95% CI = [`r e2cjaAgeCond["95pLB"]`,`r e2cjaAgeCond["95pUB"]`]), shown in Figure \ref{fig:e2ja-coord}, revealing that older children in the Activity Video condition had more episodes of coordinated JA than children in the Control Video condition.
+The regression predicting the total duration of coordinated JA episodes found no notable effects.
 
-In the regression predicting the number of episodes of passive JA, there was a main effect of age ($\beta=`r e2pja["age"]`$, 95% CI = [`r e2pja["95pLB"]`,`r e2pja["95pUB"]`]), showing that older children had more episodes of passive JA with their caregiver.
-The regression predicting the total duration of passive JA revealed a main effect of age ($\beta=`r e2pjat["age"]`$, 95% CI = [`r e2pjat["95pLB"]`,`r e2pjat["95pUB"]`]), revealing that older children spent more time in passive JA with their caregiver.
+Older children both engaged in more episodes of passive JA with their caregiver ($\beta=`r e2pja["age"]`$, 95% CI = [`r e2pja["95pLB"]`,`r e2pja["95pUB"]`]), and spent more total time in passive JA with their caregiver ($\beta=`r e2pjat["age"]`$, 95% CI = [`r e2pjat["95pLB"]`,`r e2pjat["95pUB"]`]).
 Overall, these results show that the older children in our sample engage in more and longer episodes of joint attention with their caregivers, and that activity videos in particular lead to more episodes of coordinated JA.
@@
 As for Experiment 1, we conducted a corpus characteristic analysis to examine differences parents' language use in the two conditions.
-The words that are strongly indicative of being from the Activity Video condition include "big", "little", "give", "small", "yellow", "take", and "put", while words that are most characteristic of the Science Video condition include "beep", "like", "say", "does", "uhoh", "for", and "neigh".
+The words that are strongly indicative of being from the Activity Video condition include "big", "little", "give", "small", "cow", "yellow", "take", and "put", while words that are most characteristic of the Science Video condition include "beep", "like", "neigh", "uhoh", "say", "for", "does", and "did".
 
@@
 We also observed differences in parents' talk that were broadly similar across both experiments, with a greater quantity of language but a similar breadth of vocabulary (leading to lower measures of lexical diversity).
-Exploratory corpus analysis identified the words most characteristic of the activity videos as being related to requests (e.g., "give", "put", "take") whereas control conditions featured more invitational words (e.g., "say", "let", "like").
+Exploratory corpus analysis identified the words most characteristic of the activity videos as being related to requests (e.g., "give", "put", "take") whereas control conditions featured more invitational words (e.g., "say", "let", "like"), often asking about animal noises ("What does the X say?").
 
@@
 First, our design was intentionally short and minimal; future studies should investigate whether changes in parents' speech and attempts to engage their children could persist across a longer timespan (perhaps with a broader set of activities being provisioned).
-A longer-term study would also be able to measure whether consistent increases in parent bids would lead children to respond by engaging more with their parent.
-Second, our design assumes that parents have access not only to activities but also to the materials to complete them; this assumption may be unrealistic for any parent, but especially for the parents who are most likely to be targeted for early parenting interventions.
+A longer-term study would also address whether consistent increases in parent bids would lead children to respond by engaging more with their parent.
+Second, our design assumes that parents have access to the materials needed to complete the suggested activities; this assumption may be unrealistic for any parent, but especially for the parents who are most likely to be targeted for early parenting interventions.
 Providing materials may be critical for the success of activity suggestions. 
@@
 1).
-However, activity videos resulted in parents using more word tokens (significant in Exp.
-1; numerical in Exp.
-2), while the number of word types did not differ significantly across conditions.
+However, activity videos resulted in parents using more word tokens, while the number of word types did not differ significantly across conditions.
 -->

### 2019-10-04 paper/manuscript.tex
clean up discussion and tweak figure

@@
 \textsuperscript{1} Department of Psychology, Stanford University\\\textsuperscript{2} Nextdoor, Inc.\\\textsuperscript{3} Gallaudet University\\\textsuperscript{4} Cornell University}
-\keywords{digital parenting advice; joint attention; lexical diversity; guided play\newline\indent Word count: 4576}
+\keywords{digital parenting advice; joint attention; lexical diversity; guided play\newline\indent Word count: 4629}
 \usepackage{csquotes}
@@
 For effects that are at least 95\% likely to be non-zero according to the posterior distribution, we report estimated coefficients (\(\beta\)) as well as 95\% Bayesian credible intervals (95\% CI), demarcating the range within which 95\% of the posterior predictive values fall.
-There was significantly lower TTR in the Activity Video condition (mean: 0.32) than in the No Video condition (mean: 0.42, \(\beta=\)-0.10, 95\% CI={[}-0.15,-0.05{]}).
-A similar regression instead predicting MTLD also found significantly lower lexical diversity in the Activity Video condition (mean MTLD: 16.81) than in the No Video condition (mean: 23.04, \(\beta=\)-6.27, 95\% CI={[}-11.54,-1.03{]}), with no other significant effects.
+There was lower TTR in the Activity Video condition (mean: 0.32) than in the No Video condition (mean: 0.42, \(\beta=\)-0.10, 95\% CI={[}-0.15,-0.05{]}).
+A similar regression instead predicting MTLD also found lower lexical diversity in the Activity Video condition (mean MTLD: 16.81) than in the No Video condition (mean: 23.04, \(\beta=\)-6.40, 95\% CI={[}-11.69,-0.95{]}), with no predicted influence of age.
 Figure \ref{fig:lexdiv} shows the mean of each lexical diversity measure (TTR and MTLD) by condition.
 
-We also conducted similar regressions predicting the number of word tokens and types, finding only a significant effect of condition on the number of word tokens (\(\beta=\) 56.94, 95\% CI={[}17.67,95.19{]}), with parents using more words in the Activity Video condition (mean: 228, bootstrapped 95\% confidence intervals: {[}199,252{]}) than in the No Video condition (mean: 169, bootstrapped 95\% confidence intervals: {[}139,193{]}).
+We also conducted similar regressions predicting the number of word tokens and types, finding an effect of condition on the number of word tokens (\(\beta=\) 56.45, 95\% CI={[}16.76,95.90{]}), with parents using more words in the Activity Video condition (mean: 228, bootstrapped 95\% confidence interval (conf.
+int.): {[}201,256{]}) than in the No Video condition (mean: 169, 95\% conf.
+int.: {[}145,197{]}).
 
@@
 We fit a Bayesian mixed-effects linear regression predicting the number of bids for joint attention (JA) as a function of fixed effects of condition, age (centered), and their interaction, with random intercepts per video.
-There were significantly more bids for JA in the Activity Video condition (mean: 6.30, sd: 2.76) than in the No Video condition (mean: 3.73, sd: 2.74, \(\beta=2.56\), 95\% CI={[}0.74,4.44{]}).
+There were more bids for JA in the Activity Video condition (mean: 6.30, sd: 2.76) than in the No Video condition (mean: 3.73, sd: 2.74, \(\beta=2.56\), 95\% CI={[}0.70,4.38{]}).
 Mixed-effects regressions with the same structure were performed predicting the number of episodes of coordinated and passive JA, and the total duration of time spent in coordinated and passive JA.
-There were no significant effects on the number of or total duration of coordinated or passive JA episodes.
+There were no predicted effects on the number of or total duration of coordinated or passive JA episodes.
 Figure \ref{fig:JA} (top) shows the mean number bids for JA and episodes of JA by condition in Experiment 1.
@@
 These models included random intercepts per video.
-Of these exploratory regressions, only the regression predicting the number of passive JA episodes produced a significant effect involving these demographic variables: an interaction of condition and RR (\(\beta=1.82\), 95\% CI={[}0.20,3.48{]}), shows that for parents in the Activity Video condition, those with higher Rules and Respect subscores engaged in more passive JA episodes.
+Of these exploratory regressions, only the regression predicting the number of passive JA episodes showed an effect involving these demographic variables: an interaction of condition and RR (\(\beta=1.86\), 95\% CI={[}0.14,3.46{]}), shows that for parents in the Activity Video condition, those with higher Rules and Respect subscores engaged in more passive JA episodes.
 
 To better understand the intervention's effect on language use, we analyzed which words are characteristic of parents' speech in each condition, comparing the differency in frequency rank of each word (lemma) in the two conditions, as well as contrasting the corpus overall with a general English-language word frequency list (see SI for the interactive corpus characteristic plot).
-Words that are strongly indicative of being from the Activity Video condition include \enquote{give}, \enquote{big}, \enquote{small}, \enquote{thank}, \enquote{have}, \enquote{which}, and \enquote{school}, while words that are most characteristic of the No Video condition include \enquote{ready}, \enquote{on}, \enquote{oh}, \enquote{see}, \enquote{going}, \enquote{let}, and \enquote{are}.
+Words that are strongly indicative of being from the Activity Video condition include \enquote{give}, \enquote{big}, \enquote{small}, \enquote{ribbit}, \enquote{thank}, \enquote{have}, and \enquote{bus}, while words that are most characteristic of the No Video condition include \enquote{shake}, \enquote{ready}, \enquote{oh}, \enquote{on}, \enquote{going}, \enquote{going}, \enquote{see}, \enquote{let}, and the child's name.
 
@@
 Thank you!}), whereas after no intervention parents' language related more to invitations (e.g., \enquote{Are you ready?} / \enquote{Let's see.}).
-However, parents who watched an activity video also made significantly more bids for JA with their child, although this did not result in a greater number of successful episodes of JA--passive or coordinated--than dyads in the no video condition.
+However, parents who watched an activity video also made more bids for JA with their child, although this did not result in a greater number of successful episodes of JA--passive or coordinated--than dyads in the No Video condition.
 In sum, the results of Experiment 1 suggest that digital parenting advice can increase parents' efforts to engage their child in joint attention, the volume if not diversity of their speech, and can shift the type of speech acts towards more requests.
@@
 
-84 infants (F = 36, M = 46) aged 12-24 months (84 12-17.9 month-olds, 0 18-24 month-olds) and their parents participated in the same museum as Experiment 1.
+84 infants (F = 36, M = 46) aged 12-24 months (40 12-17.9 month-olds, 44 18-24 month-olds) and their parents participated in the same museum as Experiment 1.
 We included infants who were exposed to English at least 75 percent of the time or who were exposed less but whose participating parent reported that they primarily speak English with their child at home.
@@
 Sixteen parents reported their child was of Hispanic origin.
-Parents tended to be highly-educated, with reports of highest level of education ranging from some college (n = 2), four-year college (n = 36), some graduate school (n = NA), to completed graduate school (n = NA) or declined to state (n = 13).
+Parents tended to be highly-educated, with reports of highest level of education ranging from some college (n = 5), four-year college (n = 28), some graduate school (n = 2), to completed graduate school (n = 36) or declined to state (n = 13).
 
@@
 We fit a Bayesian mixed-effects linear regression predicting TTR as a function of age (centered) and condition with an interaction term, and with random intercepts per video.
-There was lower TTR after the Activity Video (mean: 0.38) than after the Science Video (mean: 0.48, \(\beta=-0.09\), , 95\% CI={[}-0.16,-0.03{]}).
-There was no significant effect of age, nor a significant interaction.
-The preregistered regression predicting the number of tokens used by parents revealed no significant effects.
-An exploratory mixed-effects linear regression predicting MTLD found no significant effects of age or condition.
+This revealed lower TTR after the Activity Video (mean: 0.36) than after the Science Video (mean: 0.46, \(\beta=-0.10\), , 95\% CI={[}-0.16,-0.04{]}).
+The preregistered regression predicting the number of tokens used by parents revealed no effects.
+An exploratory mixed-effects linear regression predicting MTLD found no effect of age or condition.
 Figure \ref{fig:lexdiv} (bottom left and middle) shows the mean of each lexical diversity measure (TTR and MTLD) by condition.
-Regressions with the same structure predicting the number of words tokens found no significant effects of age or condition.
+Regressions with the same structure predicting the number of words tokens found no effect of age or condition.
 The means of the lexical measures are shown in Table \ref{e2tab}.
 
-\begin{table}[t]
+\begin{table}
 
@@
 \centering
-\begin{tabular}{l|r|r|r|r|r|r|r|r}
+\begin{tabular}[t]{l|r|r|r|r|r|r|r|r}
 \hline
@@
 \hline
-Science Video & 0.48 & 0.08 & 22.45 & 10.57 & 86.83 & 26.87 & 191.38 & 72.08\\
+Science Video & 0.46 & 0.07 & 22.54 & 11.09 & 90.21 & 24.52 & 201.33 & 67.88\\
 \hline
-Activity Video & 0.38 & 0.12 & 20.63 & 8.66 & 80.95 & 24.14 & 234.60 & 92.68\\
+Activity Video & 0.36 & 0.11 & 20.46 & 7.85 & 83.26 & 23.38 & 246.21 & 86.05\\
 \hline
@@
 We fit Bayesian mixed-effects linear regressions predicting the number of parental bids for joint attention and the total number of episodes of JA as a function of fixed effects of condition, age (centered), and their interaction, with random intercepts per video.
-Shown in Figure \ref{fig:JA} (left bottom), parents made significantly more bids for JA after watching the Activity Video (mean: 12.96, bootstrapped 95\% confidence intervals: 11.79, 14.24; \(\beta=3.07\), 95\% CI = {[}1.15,5.06{]}) than after the Science Video (mean: 9.89, 95\% CI: {[}8.73, 11.10{]}).
-There were no other significant effects on parental bids for JA.
+Shown in Figure \ref{fig:JA} (left bottom), parents made notably more bids for JA after watching the Activity Video (mean: 12.96, 95\% conf.
+int.: 11.73, 14.23; \(\beta=3.10\), 95\% CI = {[}1,5.11{]}) than after the Science Video (mean: 9.88, 95\% conf.
+int.: {[}8.74, 11.10{]}).
+There were no other effects on parental bids for JA.
 
-In the regression predicting the number of episodes of JA, there was a significant main effect of condition (\(\beta=1.48\), 95\% CI = {[}0.15,2.78{]}), with more episodes of JA occurring after the Activity Video (mean: 8.80, 95\% CI: {[}7.97, 9.63{]}) than after the Control Video (mean: 7.33, 95\% CI: {[}6.58, 8.11{]}).
-There was also a significant main effect of age (\(\beta=-5\), 95\% CI = {[}-8.27,-1.41{]}), showing that older children participated in fewer episodes of JA.
-However, a significant interaction of age and condition (\(\beta=5.60\), 95\% CI = {[}0.46,10.37{]}), shown in Figure \ref{fig:JA} (right bottom), demonstrates that there were more episodes of JA for older children in the Activity Video condition (comparable to episodes of JA for younger children).
+The regression predicting the number of episodes of JA revealed an effect of condition (\(\beta=1.48\), 95\% CI = {[}0.24,2.67{]}), with more episodes of JA occurring after the Activity Video (mean: 8.80, 95\% conf.
+int.: {[}7.97, 9.66{]}) than after the Control Video (mean: 7.33, 95\% conf.
+int.: {[}6.62, 8.05{]}).
+Older children also participated in fewer episodes of JA (\(\beta=-5.07\), 95\% CI = {[}-8.32,-1.58{]}).
+However, this age effect was moderated in the Activity Video condition (\(\beta=5.69\), 95\% CI = {[}0.71,10.41{]}): shown in Figure \ref{fig:JA} (right bottom), older children did not engage in fewer episodes of JA after an activity video.
 
@@
 Four additional exploratory regressions with a similar structure were carried out to predict the number and duration of coordinated and passive JA episodes.
-The regression predicting the number of episodes of coordinated JA found a significant main effect of condition (\(\beta=1.35\), 95\% CI = {[}0.17,2.61{]}), with more episodes of coordinated JA occurring after the Activity Video (mean: 6.72, 95\% CI: {[}5.91, 7.56{]}) than after the Control Video (mean: 5.33, 95\% CI: {[}4.70, 5.97{]}).
-There was no significant effect of age, but there was a significant interaction of age and condition (\(\beta=5.28\), 95\% CI = {[}0.52,10.02{]}), shown in Figure \ref{fig:e2ja-coord}, revealing that older children in the Activity Video condition had more episodes of coordinated JA than children in the Control Video condition.
-The regression predicting the total duration of coordinated JA episodes revealed no significant effects.
+The regression predicting the number of episodes of coordinated JA found an effect of condition (\(\beta=1.36\), 95\% CI = {[}0.15,2.62{]}), with more episodes of coordinated JA occurring after the Activity Video (mean: 6.72, 95\% CI: {[}5.96, 7.53{]}) than after the Control Video (mean: 5.34, 95\% CI: {[}4.73, 6{]}).
+There was an interaction of age and condition (\(\beta=5.41\), 95\% CI = {[}0.62,10.34{]}), shown in Figure \ref{fig:e2ja-coord}, revealing that older children in the Activity Video condition had more episodes of coordinated JA than children in the Control Video condition.
+The regression predicting the total duration of coordinated JA episodes found no notable effects.
 
-In the regression predicting the number of episodes of passive JA, there was a main effect of age (\(\beta=-2.70\), 95\% CI = {[}-5.07,0.08{]}), showing that older children had more episodes of passive JA with their caregiver.
-The regression predicting the total duration of passive JA revealed a main effect of age (\(\beta=-18.32\), 95\% CI = {[}-33.50,-2.91{]}), revealing that older children spent more time in passive JA with their caregiver.
+Older children both engaged in more episodes of passive JA with their caregiver (\(\beta=-2.71\), 95\% CI = {[}-5.06,0.07{]}), and spent more total time in passive JA with their caregiver (\(\beta=-18.03\), 95\% CI = {[}-33.55,-2.03{]}).
 Overall, these results show that the older children in our sample engage in more and longer episodes of joint attention with their caregivers, and that activity videos in particular lead to more episodes of coordinated JA.
@@
 As for Experiment 1, we conducted a corpus characteristic analysis to examine differences parents' language use in the two conditions.
-The words that are strongly indicative of being from the Activity Video condition include \enquote{big}, \enquote{little}, \enquote{give}, \enquote{small}, \enquote{yellow}, \enquote{take}, and \enquote{put}, while words that are most characteristic of the Science Video condition include \enquote{beep}, \enquote{like}, \enquote{say}, \enquote{does}, \enquote{uhoh}, \enquote{for}, and \enquote{neigh}.
+The words that are strongly indicative of being from the Activity Video condition include \enquote{big}, \enquote{little}, \enquote{give}, \enquote{small}, \enquote{cow}, \enquote{yellow}, \enquote{take}, and \enquote{put}, while words that are most characteristic of the Science Video condition include \enquote{beep}, \enquote{like}, \enquote{neigh}, \enquote{uhoh}, \enquote{say}, \enquote{for}, \enquote{does}, and \enquote{did}.
 
@@
 We also observed differences in parents' talk that were broadly similar across both experiments, with a greater quantity of language but a similar breadth of vocabulary (leading to lower measures of lexical diversity).
-Exploratory corpus analysis identified the words most characteristic of the activity videos as being related to requests (e.g., \enquote{give}, \enquote{put}, \enquote{take}) whereas control conditions featured more invitational words (e.g., \enquote{say}, \enquote{let}, \enquote{like}).
+Exploratory corpus analysis identified the words most characteristic of the activity videos as being related to requests (e.g., \enquote{give}, \enquote{put}, \enquote{take}) whereas control conditions featured more invitational words (e.g., \enquote{say}, \enquote{let}, \enquote{like}), often asking about animal noises (\enquote{What does the X say?}).
 
@@
 First, our design was intentionally short and minimal; future studies should investigate whether changes in parents' speech and attempts to engage their children could persist across a longer timespan (perhaps with a broader set of activities being provisioned).
-A longer-term study would also be able to measure whether consistent increases in parent bids would lead children to respond by engaging more with their parent.
-Second, our design assumes that parents have access not only to activities but also to the materials to complete them; this assumption may be unrealistic for any parent, but especially for the parents who are most likely to be targeted for early parenting interventions.
+A longer-term study would also address whether consistent increases in parent bids would lead children to respond by engaging more with their parent.
+Second, our design assumes that parents have access to the materials needed to complete the suggested activities; this assumption may be unrealistic for any parent, but especially for the parents who are most likely to be targeted for early parenting interventions.
 Providing materials may be critical for the success of activity suggestions.

### 2019-10-17 paper/manuscript.Rmd
minor edits

@@
 Parents' child-directed speech during the play sessions was transcribed.
-The transcripts and hand-coded joint attention data were analyzed according to our preregistration[^3], with any deviations or exploratory analyses noted.
+Although Experiment 1 was not preregistered, for consistency the transcripts and hand-coded joint attention data were analyzed according to our preregistration for Experiment 2[^3], with any deviations or exploratory analyses noted.
 Below we first report the lexical diversity results, followed by the joint attention results.
@@
 require("rstanarm")
+require(bayestestR)
 # get estimated coefficient and 95% CI from Bayesian regression
@@
   ci89 <- posterior_interval(model, prob = 0.89, pars = cond) # 89% CIs as recommended by Kruschke and others
-  ci = round(c(ci95,ci89), digits)
-  names(ci) = c("95pLB","95pUB","89pLB","89pUB") # 95% and 89% lower and upper bounds
+  pd = p_direction(model)
+  pd = pd[which(pd$Parameter==cond),]$pd
+  ci = round(c(ci95,ci89,pd), digits)
+  names(ci) = c("95pLB","95pUB","89pLB","89pUB","pd") # 95% and 89% lower and upper bounds
   beta = round(model$coefficients[cond], digits)
@@
 e1TTR = get_stan_glmer_reporting_values(modTTR, "conditionexp") # -.10
+p_direction(modTTR, effects="all") # orchestra 73.9%
 
@@
 e1MTLD = get_stan_glmer_reporting_values(modMTLD, "conditionexp") # -6.27
+p_direction(modMTLD, effects="all")
 
@@
 e1tokens = get_stan_glmer_reporting_values(tokens_mod, "conditionexp") # 57.1
+p_direction(tokens_mod, effects="all") # orchestra 84.2%
 
@@
 summary(types_mod) # nothing 
+p_direction(types_mod, effects="all")
 
@@
 get_stan_glmer_reporting_values(modTTRE, 'conditionexp') # -.11
+p_direction(modTTRE, effects="all") # EL 84.9%, RR 83.3%, parent_ed 91.7%
 
@@
 summary(modMTLDE) #
+p_direction(modMTLDE, effects="all") # EL 78.5% AA 89.2% RR 86.6% genderM 87.8% parent_ed 91.5%
 
@@
 summary(tokens_modE) # condition 54.4 
+get_stan_glmer_reporting_values(tokens_modE, 'parent_ed') # SHOULD REPORT
+p_direction(tokens_modE, effects="all") # RR 75.7% parent_ed 95.1%
 
@@
 types_modE <- stan_glmer(paste("types", e1model_string), data=e1ld) 
-summary(types_modE) # 
+summary(types_modE) 
+p_direction(types_modE, effects="all") # EL 87.2% AA 77.7% genderM 88.3%, parent_ed 91.7% cond:AA 94.5%
+get_stan_glmer_reporting_values(types_modE, 'parent_ed') 
+get_stan_glmer_reporting_values(types_modE, 'conditionexp:AA') 
 ```
@@
 We fit a Bayesian mixed-effects linear regression predicting TTR as a function of condition, age (centered), and their interaction with a random intercept per video using rstanarm [@rstanarm]. 
-For effects that are at least 95% likely to be non-zero according to the posterior distribution, we report estimated coefficients ($\beta$) as well as 95% Bayesian credible intervals (95% CI), demarcating the range within which 95% of the posterior predictive values fall.
+For effects that are at least 95% likely to be non-zero according to the posterior distribution, we report estimated coefficients ($\beta$) as well as 95% Bayesian credible intervals (95% CI), demarcating the range within which 95% of the posterior falls.
 There was lower TTR in the Activity Video condition (mean: `r round(subset(e1_lexdiv, condition=='exp')$TTR, 2)`) than in the No Video condition (mean: `r round(subset(e1_lexdiv, condition=='con')$TTR, 2)`, $\beta=$`r e1TTR["conditionexp"]`, 95% CI=[`r e1TTR['95pLB']`,`r e1TTR['95pUB']`]).
@@
 
-```{r e1tab, echo=FALSE, include=F}
+```{r e1tab, echo=F, include=F}
 e1 <- e1ld %>% group_by(Condition) %>%
@@
 Mixed-effects regressions with the same structure were performed predicting the number of episodes of coordinated and passive JA, and the total duration of time spent in coordinated and passive JA.
-There were no predicted effects on the number of or total duration of coordinated or passive JA episodes.
+There were no notable effects on the number of or total duration of coordinated or passive JA episodes.
 Figure \@ref(fig:JA) (top) shows the mean number bids for JA and episodes of JA by condition in Experiment 1.
@@
 
-To better understand the intervention's effect on language use, we analyzed which words are characteristic of parents' speech in each condition, comparing the differency in frequency rank of each word (lemma) in the two conditions, as well as contrasting the corpus overall with a general English-language word frequency list (see SI for the interactive corpus characteristic plot).
+To better understand the intervention's effect on language use, we analyzed which words are characteristic of parents' speech in each condition, comparing the difference in frequency rank of each word (lemma) in the two conditions, as well as contrasting the corpus overall with a general English-language word frequency list (see SI for the interactive corpus characteristic plot).
 Words that are strongly indicative of being from the Activity Video condition include "give", "big", "small", "ribbit", "thank", "have", and "bus", while words that are most characteristic of the No Video condition include "shake", "ready", "oh", "on", "going", "going", "see", "let", and the child's name.
@@
 Thank you!"), whereas after no intervention parents' language related more to invitations (e.g., "Are you ready?" / "Let's see.").
-However, parents who watched an activity video also made more bids for JA with their child, although this did not result in a greater number of successful episodes of JA--passive or coordinated--than dyads in the No Video condition.
+However, parents who watched an activity video also made more bids for JA with their child.
+While this did not result in a greater number of successful episodes of JA--passive or coordinated--than dyads in the No Video condition, it should be noted that low reliability for coding of passive JA episodes may have limited our power to find an effect, leading us to refine our coding procedure for Experiment 2.
 In sum, the results of Experiment 1 suggest that digital parenting advice can increase parents' efforts to engage their child in joint attention, the volume if not diversity of their speech, and can shift the type of speech acts towards more requests.
@@
 # predict word tokens
-e2tokens_m <- stan_lmer(tokens ~ age * condition + (1 | video), data=e2data)
+e2tokens_m <- stan_lmer(log(tokens) ~ age * condition + (1 | video), data=e2data)
 summary(e2tokens_m) # NA 
-#get_stan_glmer_reporting_values(e2tokens_m,"conditionexp")
+print(e2tokens_m, digits=2)
+p_direction(e2tokens_m, effects="all") 
+# conditionexp 90.3%, age:conditionexp 83.1%  video:big_small 96.3%, video:orchestra 94.5%
+launch_shinystan(e2tokens_m, ppd = FALSE)
+summary(e2tokens_m, 
+        pars = c("(Intercept)", "age", "conditionexp", "age:conditionexp"),
+        probs = c(0.025, 0.975),
+        digits = 2)
+plot(e2tokens_m)
+#prior_summary(object = e2tokens_m)
+get_stan_glmer_reporting_values(e2tokens_m,"conditionexp")
+
+# require(bayesplot)
+# bayesplot_grid(
+#   plot(e2tokens_m, plotfun = "intervals", pars = c("(Intercept)", "age", "conditionexp", "age:conditionexp"), prob = 0.5, prob_outer = 0.89, point_est = "median") + ggtitle("Marginal Posterior Parameter Estimates"),
+#   plot(e2tokens_m, plotfun = "areas", pars = c("(Intercept)", "age", "conditionexp", "age:conditionexp"), prob = 0.5, prob_outer = 0.89, point_est = "median") + ggtitle("Marginal Posterior Parameter Estimates"),
+#   grid_args = list(ncol = 2)
+# )
 
@@
 Shown in Figure \ref{fig:JA} (left bottom), parents made notably more bids for JA after watching the Activity Video (mean: `r round(subset(e2_bids, Condition=="Activity Video")$mean,2)`, 95% conf.
-int.: `r round(subset(e2_bids, Condition=="Activity Video")$ci_lower,2)`, `r round(subset(e2_bids, Condition=="Activity Video")$ci_upper,2)`; $\beta=`r e2bids["ConditionActivity Video"]`$, 95% CI = [`r e2bids["95pLB"]`,`r e2bids["95pUB"]`]) than after the Science Video (mean: `r round(subset(e2_bids, Condition=="Science Video")$mean,2)`, 95% conf.
+int.: [`r round(subset(e2_bids, Condition=="Activity Video")$ci_lower,2)`, `r round(subset(e2_bids, Condition=="Activity Video")$ci_upper,2)`]; $\beta=`r e2bids["ConditionActivity Video"]`$, 95% CI = [`r e2bids["95pLB"]`,`r e2bids["95pUB"]`]) than after the Science Video (mean: `r round(subset(e2_bids, Condition=="Science Video")$mean,2)`, 95% conf.
 int.: [`r round(subset(e2_bids, Condition=="Science Video")$ci_lower,2)`, `r round(subset(e2_bids, Condition=="Science Video")$ci_upper,2)`]).
